### 2014-10-27 parallel acceleration of FCSD based on cuda/draft.tex
add the latex version of the Parallel FCSD

%% bare_conf.tex
%% V1.4
%% 2012/12/27
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex,
%%                    bare_jrnl_transmag.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[12pt,a4paper,final]{article}
%\documentclass[conference]{IEEEtrans}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}
%\usepackage[pdftex]{graphicx}
\usepackage{psfrag}
\usepackage{color}
\usepackage{epsfig}
\usepackage{appendix}
\usepackage{caption}
\usepackage{cite}
\usepackage{ifpdf}
\usepackage[cmex10]{amsmath}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{stfloats}
\usepackage{url}
\usepackage{fixltx2e}
\usepackage{setspace} 
\usepackage{multirow}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
%\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
%\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
%\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Parallel Acceleration of Fixed Complexity Sphere Decoder for Large MIMO Uplink System based on GPU}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{Tianpei Chen}
%\IEEEauthorblockA{ID: 25504946\\Department of Electrical and\\Computer Engineering\\
%McGill University\\
%Montreal, Quebec}}
\author{Tianpei Chen, Harry Leib\\
 Department of Electrical and Computer Engineering\\
 McGill University\\
 Montreal, Quebec}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

\begin{document}
% make the title area
\begin{spacing}{2.5}
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The large MIMO system which is a scaling up of conventional MIMO systems with several hundreds of antennas at the base station serving several tens of terminals at the same time,  which is thought to be a big idea for the next generation wireless communication system. However the detection of the large MIMO system acquires a long time to get optimum or sub-optimum solutions, In order to accelerate the real-time decoder for large MIMO system, in this paper we present General Purpose Graphic Processing Units (GPGPU) implementation of Fixed Complexity Sphere Decoder (FCSD) for the large scale MIMO system based on the dominant propriety framework of GPGPU-Computed Unified Device Architecture (CUDA). The simulation shows a up to nearly $5$ times acceleration for $32\times 32$ array of whole application CPU version, furthermore, the proposed CUDA-FCSD algorithm shows a increasing speedup performance for a increasing array size. 
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
%\IEEEpeerreviewmaketitle

\section{Introduction}
 The common challenge that all the researchers, engineers and industrial companies are now facing in wireless communication area is the sharp contrast between the increasing demand of the mobile network speed for the transmission of rich media content and better QoS (quality of service) and the limited bandwidth of the radio frequency spectrum and a complex space time varying wireless environment, moreover in foreseeable future this demand will continue grow. Multiple Input Multiple Output (MIMO) has become a very promising technology that can help to solve this problem, the core idea of MIMO is to use multiple antennas both at the transmitting end and receiving end, the spatial domain sampled signal can be combined to provide parallel data pipes so that it can provide array gain, spatial diversity gain, spatial multiplexing gain, and interference reduction\cite{oestges2010mimo}. LTE standard support up to 8 antennas at the base station\cite{dahlman20103g}, The large scale MIMO (also named massive MIMO) is a system with hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}, originated from multiuser MIMO (MU-MIMO)\cite{larsson2013massive}. Large scale MIMO will inherit and enhance all the advantages of conventional MIMO (array gain, spatial diversity gain, spatial multiplexing gain and interference reduction), as well as reduction of latency, improvement of the whole system robustness. 
 As a classical list based decoder for MIMO system, Sphere decoder (SD) can reach the optimum diversity gain as maximum likelihood (ML) detection with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}, however, there are two major problems of this decoder is the varied complexity with signal to noise ratio and sequential nature, which is contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system. Fixed Complexity Sphere Decoder (FCSD), overcomes this two disadvantage of the SD by searching the solution along the fixed number independent multiple paths\cite{barbero2008fixing}.
GPGPU (General purpose Graphic processing Units Computing) has become a big idea in the industry and research of a variety of areas that needs massive data analysis and computation such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}. Comparing to CPU, The GPU has been designed as computational intensive, with most of the hardware resource be allocated for data processing and parallel computation rather than caching and flow control. In recent years GPU has reached huge advantages in data processing speed over CPU\cite{nvidia2008programming}.  CUDA (Computed unified Device Architecture) is a programming model for GPGPU that proposed by Nvidia which has becoming the dominant proprietary framework for GPGPU programming, it is based on popular programming languages(C, C++, java, python, Fortran, Direct Compute) so that the application developers in different areas do not need to learn a new programming language or get to know the hardware details. The core essence of the CUDA is the Single Instruction Multiple Threads (SIMT) programming model, enables GPU can accelerate a lot of applications with the large dataset by implementing parallel data processing of complex computations. CUDA has become a parallel computing platform for wide community of different application developers in different areas.  
\section{MIMO System Model}\label{system}
% no \IEEEPARstart
%This demo file is intended to serve as a ``starter file''
%for IEEE conference papers produced under \LaTeX\ using
%IEEEtran.cls version 1.8 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
%I wish you the best of success.
%\hfill mds
%\hfill December 27, 2012
We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive antennas and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, in the flat fading channel the corresponding discrete time model is given:
\begin{equation}
y=\mathbf{H}s+n   \label{formula 1}
\end{equation}
$s\in \mathbb{C}^{N_{t}\times 1}$ is the transmit symbol vector, the symbol in $s$ are mutually independent and taken from the signal constellation $\mathbb{O}$ (BPSK, QPSK, M-QAM), $M$ is the signal constellation size, all the transmit symbol vectors forms a $N_{t}$-dimensional signal constellation $\mathbb{O}^{N_{t}}$. $\varepsilon[ss^{H}]=I_{N_t}E_{s}$, $E_{s}$ denotes the symbol average energy where $\varepsilon$ denotes the mean operation.  $y\in \mathbb{C}^{N_{r}\times 1}$ is the receive symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean elements of unit variance, $n\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean elements of variance $\varepsilon[nn^{H}]=I_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise energy, $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR). \\
  Assume we have the perfect channel state information (CSI)  $\quad \mathbf{H}$, receive symbol vector $y$, and we had already known the SNR, the task of decoder for MIMO system is to estimate $s$ in \ref{formula 1} based on CSI and received signal.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.

% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results.}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

\section{CUDA GPU Architecture and  Programming Model} \label{programming model}
  CUDA programming model is the C programming extension, with special defined syntax and structure, CUDA divide the CPU and GPU as host and device, the serial code executes on the host (CPU) side and parallel data processing is performed on the device (GPU) side, which is defined as heterogeneous programming model. The code executes on the device side is defined as $\mathit{kernel}$ function, which is a single instruction invoked at host side but with a massive parallel data processing threads execution on the device (SIMT), This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branching the behavior of each threads so that reach thread-level parallelism, thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share a memory called shared memory that all the threads in the block have the access to this pitch of memory, the GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU, Another function of the thread block is all the thread execute in one block can synchronize their action. The warp is the basic schedule unit with a constant number of threads  (for current version of CUDA device, the warp size is 32), when one warp are waiting for data loading the other warps just begin to execute. In a word CPU cores are designed to minimize latency for each thread at a time , whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput. Blocks are grouped into a one-dimensional, two-dimensional, or three-dimensional grid, similarly, one thread block can also be organized into one-dimentional, two-dimensional or three-dimensional. The organization of the block and grid shape and dimension is determined by the concrete application, Figure \ref{figure1} shows the 3 dimensional thread hierarchy of CUDA.
\begin{figure}[htb]
\centering
\includegraphics[scale=0.5]{CUDA_programming_hierachy.eps}
\caption{CUDA 3D thread hierachy\\ $5\times 5\times 5$ grid and each block contains $5\times 5\times 5$ threads\\}
\label{figure1}
\end{figure}
In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU. The GPU works as a coprocessor system, consists of Stream Multiprocessors (SM), GeForce GTX 760 has 6 SM performs the multiply-add arithmetic operation and furthermore, each SM has the special functional units(SFU) that can perform more complex arithmetic operation such as trigonometric functions and reciprocal square root. the shared memory is also called on-chip memory which is located at SM that has low latency and limited capacity. Global memory, which is off-chip located memory of GPU with long latency and large capacity, another two types of the memory is called texture memory and constant memory, which are located off-chip , but cached, therefore the loading speed of the data located at these two type of memory space will be much faster than the that from global memory, for constant memory, it is read only and the memory latency is approximately as small as the registers.  The variables invoked in kernel functions can be stored in either of the these 4 types of memories. Registers are allocated dynamically to threads.\\
   Since the resource limitation of SM the total number of threads that we can define in one block is limited, on current CUDA supported GPUs, one block can contains up to 1024 threads, in addition all the blocks are executed on SMs, thus the total number of threads we can make use of is $T_{total}=Num_{SM}\times Num_{threads/SM}$, GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$, although in concrete application, the programmer can allocate more than 12288 threads for a kernel, but the threads will work in serial, which will influence the performance of program. 
\begin{figure}[htb]
\centering
\includegraphics[scale=0.5]{High_view_of_CUDA_GPU_microarchitecture.eps}
\caption{High View of CUDA CPU Microarchitecture}
\label{figure2}
\end{figure}   
% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.
\section{GPU Based Acceleration of FCSD}
In this section we present the parallel implementation of fixed complexity sphere decoder by GPU, first from (\ref{formula 1}), the maximum likelihood (ML) solution is given by:
\begin{equation}
s_{ML}=arg\min_{s\in \mathbb{O}^{N_{t}}}||y-\mathbf{H}s||^{2} \label{formula 2}
\end{equation}
we consider the array $N_{t}=N_{r}$, performing QR decomposition to channel propagation matrix
\begin{equation}
 \mathbf{H}=\mathbf{Q}\mathbf{R}  \label{QR}
\end{equation}
where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is the unitary matrix, $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is the upper triangular matrix, the basing on \cite{matrix theory}, the (\ref{formula 2}) can be changed to
\begin{eqnarray}
\nonumber
s_{ML}&=&arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}y-\mathbf{Q}^{H}\mathbf{H}s||^{2}\\
&=& arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}y-\mathbf{R}s||^{2} \label{formula 3}
\end{eqnarray}
Consider the unconstrained estimation of $s$, $\hat{s}=\mathbf{G}y$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$ denotes the zero forcing equalizer, basing on \ref{QR}, we have  
\begin{equation}
\hat{s}=\mathbf{G}y=(\mathbf{R}^{H}\mathbf{R})^{-1}\mathbf{R}^{H}\mathbf{Q}^{H}y=\mathbf{R}^{-1}\mathbf{Q}^{H}y 
\label{unconstrained estimation}
\end{equation} 
Therefore $\mathbf{Q}^{H}y=\mathbf{R}\hat{s}$, the \ref{formula 3} can be changed to
\begin{equation}
s_{ML}=arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\hat{s}-s)||^{2} \label{formula 4}
\end{equation}
the Fixed Complexity Sphere Decoder works as a constant number of multiple path tree searching.
\begin{figure}[tb]
\centering
\includegraphics[scale=0.5]{FCSD_tree_searching.eps}
\caption{Tree searching of QPSK FCSD for 8x8 MIMO system}
\label{figure4}
\end{figure}
As shown in Figure \ref{figure4}, just like SD the FCSD also performs depth first searching, at the first $\rho$ level the FCSD search all the possible signal symbols $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$ in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) level, the remain $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back equalization (DFE), from (\ref{formula 4}) the solution of FCSD can be given:
\begin{equation}
\hat{s}_{FCSD}=arg\min_{s\in \mathbb{O}^{N_{t}}}\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s_{j})|^{2}  \label{formula 5}
\end{equation} 
$i\in [1,2\dots N_{t}]$, $r_{ij}$ denotes the element at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$, this process is called Single Expansion (FE).
thus the FCSD solution $s_{FCSD}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
\begin{displaymath}
s_{FCSD}^{i}=\left\lbrace\begin{array}{c}
\in \mathbb{O}^{\rho}      \quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
\mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}}-s_{FCSD}^{i})] \quad i=N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
\end{array}\right.
\end{displaymath}
$\mathbb{Q}[]$ denotes the signal constellation based quantization. At the post processing stage, FCSD takes the symbol vector candidate with the minimum Euclidean metric $E_{metric}$:
\begin{equation}
E_{metric}=||\mathbf{R}(\hat{s}-\widetilde{s})||^{2}
\end{equation} 
The $\widetilde{s}$ denotes the symbol vector candidate, the total number of candidates is: 
\begin{equation}
M^{\rho}     \label{path number}
\end{equation} 
\subsection{CUDA-FCSD Pre-Prossing}
As shown in figure.4, each path of the FCSD searching has a serial execution nature, in order to avoid error propagation of decoder, FCSD ordering was applied to the propagation channel based on post processing signal to noise ratio\cite{Vblas}, which can be expressed as:
\begin{equation}
\varphi_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}}  \label{ppsnr}
\end{equation}
$\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inversion of $HHH$ matrix $\mathbf{H}^{H}\mathbf{H}$, thus when the SNR is determined, the post processing SNR is only determined by $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$, for the FE stage the robustness of detector performance is not influenced by the post processing SNR thus at FE stage the "weakest" data stream is detected first, that is, the data stream with the smaller $\varphi$ is detected earlier. At SE stage, because of the single searching path of the symbol, the performance is tightly related to the post processing SNR, therefore at SE stage the data streams with the larger post processing SNR is detected earlier in order to avoiding the error propagation, in conclusion the FCSD ordering works iteratively  and obeys the following rule:
At the $j$th step ($j=1,2\dots N_{t}-1$), $s_{p}$ denotes the symbol to be detected, where 
\begin{displaymath}
p=\left\lbrace \begin{array}{c}
arg \max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE stage\\
arg \min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE stage \\  \label{the ordering}
\end{array}\right.  
\end{displaymath}  
$\mathbf{H}_{j}\in \mathbb{C}^{N_{r}\times (N_{t}-j+1)}$ denotes the renewed channel matrix, at the $j$th iteration with the column corresponding to previous detected data streams removed from $\mathbf{H}_{j-1}$.
the unconstrained estimation $\hat{s}$ in \ref{unconstrained estimation}  in is given by:
\begin{equation}
 \hat{s}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y \label{shat}
\end{equation}

Although the FCSD pre-processing has a serial nature and can not be vectorized, the computational consumptive operations \ref{the ordering} \ref{shat} can be implement by the CUDA Basic Linear Algebra Subprograms(cuBLAS), the matrix inverse(Gaussian Jordan Elimination) and cholesky factorization(Row Major Factorization) are also implemented by GPU, as shown in Table \ref{table 1}.
\begin{table}[htb]
\caption{Parallel Computation Operation of FCSD Pre-processing}
\centering
\begin{tabular}{|c|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
\hline
Operations & complex matrix-matrix multiplication & complex matrix-vector multiplication & matrix inverse & cholesky factorization \\
\hline
GPU subroutine & $\mathit{cublasCgemm}$  & $\mathit{cublasCgemv}$ & $\mathit{GJE}$ & $\mathit{chol}$\\
\hline
Formula   &  $\mathbf{H}^{H}\mathbf{H}$ & $(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y$ & $\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1} $ & $\mathbf{H}^{H}\mathbf{H}=\mathbf{R}^{H}\mathbf{R}$ 
\\
\hline
  \label{table 1}
\end{tabular}
\end{table}

Figure \ref{block diagram} shows the block diagram of the CUDA-FCSD implementation, as mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
\begin{figure}[htb]
\centering
\includegraphics[scale=0.8]{CUDA_FCSD_block_diagram.eps}
\caption{Block Diagram of CUDA-FCSD Implementation}
\label{block diagram}
\end{figure}
\subsection{Parallel Acceleration of Blocked-Paths Searching}
  We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt[2]{N_{t}}-1\rceil$, as mentioned in section \ref{programming model} the maximum number of threads that can be used in GPU is limited by the number of SM and maximum number of threads per SM, as to GeForce GTX 760. we have $12288$ threads totally.   For each path, decision feedback path searching has a serial nature, therefore we match path to one thread, in order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks, for largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads. At each path, we perform the following data operation:\\
1. \emph{Decision Feedback Equalization}\\
\begin{eqnarray}
\nonumber
{s}_{i}^{k}\in \mathbb{O}^{\rho}      \quad if\quad i&=&N_{t},N_{t}-1,\dots N_{t}-\rho+1\quad FE\\
\nonumber
{s}_{i}^{k}=\hat{s}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}^{k}}-s_{j}^{k})\quad if\quad i &=& N_{t}-\rho,N_{t}-\rho-1,\dots 2,1\quad SE\\  \label{path searching}
\end{eqnarray}
$s_{j}^{k}$ denotes the $j$th symbol of the $k$th symbol vector candidate.\\
2. \emph{Euclidean Metric Calculation}\\
\begin{equation}
E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s_{j}}-s_{j})\label{Eu metric}
\end{equation}
$E_{u}^{k}$ denotes the $k$th Euclidean metric of the corresponding symbol vector candidate $\widetilde{s}^{k}$. Then we take the symbol vector $s^{\theta}$ as the solution, where 
\begin{equation}
\theta=arg\min_{m}(E_{u}^{m})\quad m=1,2\dots M^{\rho} \label{Eu candidate}
\end{equation}

\subsubsection{Data Preparation}
There are three major factors that will influence the configuration of the data set configuration in memory space.\\
1. Amount of Reading$\&$Writing operation per thread.\\
2. Program scope of the data.\\
3. Storage Requirement of data.\\
The memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influence the application performance because the GPU is data processing intensive and only has small cache for special memory space(constant, texture), another consideration is the validation life circle of data, local memory which is invoked in kernel function is valid in one thread, share memory is valid in one block, constant, texture and global memory are valid both at host side and device side. On the other hand different from global memory (2047 MBytes in GeForce GTX 760), the constant and share memory are all capacity limited (only $65536$ bytes totally and $49152$ bytes per block in GeForce GTX 760), so that for our application the configuration of memory is determined by the capacity requirement of the data. Here in table \ref{amount of R/W operation} we present the amount of R/W operations and the storage that needed for critical data variables in FCSD path searching. The amount of the R/W operation is calculated based on the (\ref{path searching}) and ((ref{Eu metric}), for complex value ($\mathbf{R}$,$\hat{s}$, $\mathit{s_{pontential matrix}}$,$\mathit{s_{kernel}}$ ) is stored use $\mathit{float2}$ which counts 8 bytes, floating point data set $E_{u}$ is stored in $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored use $\mathit{int}$, which counts 1 byte. \\
 At host side we set 4 vector data set that are stored linearly in global memory which has program scope for both host side and device side, $\mathit{s_{potential matrix}}$ is used to store the $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope is through the whole kernel function. $\mathit{s_{index}}$, which is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.  $\mathit{E_{u}}$ is a $M^{\rho}$ floating point vector that is used to store the Euclidean metric of all the symbol vector candidates, obviously the valid scope of it is for the whole kernel function. $\mathit{s_{kernel}}$ is a complex vector used to store the FCSD solution which length is $N_{t}$ and has to be transferred to host side, thus it is also needed to be stored in global memory. \\
  On the other hand,   upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\hat{s}$ in (\ref{unconstrained estimation})  requires a large amount of R operations and are read only. (for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\hat{s}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\hat{s}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section (\ref{programming model}), the constant memory is cached so that it is much faster than global memory.
 \begin{table}[htb]  
 \caption{Amount of R/W Operations and Storage Requirement of Different Data Set}
 \centering
\begin{tabular}{|p{3cm}|p{3cm}|l|p{3cm}|l|l|l|}
\hline
data & $\mathbf{R}$ & $\hat{s}$ & $\mathit{s_{pontential matrix}}$ & $\mathit{s_{index}}$ & $\mathit{E_{u}}$ & $\mathit{s_{kernel}}$ \\
\hline
R/W operations/thread & $(\frac{3}{2}(N_{t})^{2}-\frac{N_{t}}{2}+\rho-\rho^{2})$ & $(\frac{2(N_{t})^{2}+2N_{t}-\rho^{2}-\rho}{2})$ & $\rho$ & $N_{t}$ &$N_{t} $ & $N_{t}$ \\
\hline
Storage/bytes  & $4(N_{t}+1)N_{t}$ & $8N_{t}$ & $8M^{\rho}N_{t}$ & $N_{t}M^{\rho}$ & $4N_{t}M^{\rho}$ & $8N_{t}$\\
\hline  \label{amount of R/W operation} 
\end{tabular} 
\end{table} 
\subsubsection{Memory Accesss Pattern}
  When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.\\
  Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W data by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible, for GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Figure \ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{potential matrix}}$ as an example to illustrate how we coalesce the the global memory,
we store $\mathit{s_{potential matrix}}$ in one pitch of linear global memory, with each row store one $N_{t}=16$ complex symbol vector solution candidate of $\hat{s}_{FCSD}$ in (\ref{formula 5}), totally there are $M^{\rho}=4096$ rows, this matrix is stored in column major. As mentioned before we operate one path in one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256 bytes$, counts for two times of DRAM access.
\begin{figure}[htb]
\centering
\includegraphics[scale=0.63]{coalescing_global_memory.eps}
\caption{Global Memory Access Pattern of $\mathit{s_{potential matrix}}$}
\label{coalesce global memory}
\end{figure}
 Another available resource for memory bandwidth increase is to make use of share memory, for all the transient variables that used for accumulator in (\ref{path searching}) and (\ref{Eu metric}), because of the small capacity consumption and large amount of R/W operations.   
\subsubsection{Data Transfer Minimization}   
The data transfer between the host side and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $y$ in (\ref{formula 1}) as well as the index list $\mathit{s_{index}}$ at FE stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to avoid the transferring of $E_{u}$ in (\ref{Eu metric}).  
\subsection{Going to Larger MIMO System}
  Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, from \ref{path number}, the path number that need to be searched is $16^{5}=1048576$, as mentioned in section (\ref{programming model}), the maximum number of threads that can be execute in kernel function of GeForce GTX 760 is 12288, therefore we need to consider serial the one kernel into a certain times of loop, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense. Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the kernel function for 86 times and get the final solution.
\section{Simulation Results}
\subsection{Environment}
\subsubsection{Device}
\emph{Graphic Processing Units}: GeForce GTX 760, GPU clock rate: 1.08 GHz , memory clock rate: 3 GHz , number of SM: 6, maximum number of threads per stream multiprocessor: 2048, total amount of global memory: 2 GB, total amount of share memory per block: 49 KB, total amount of constant memory: 66 KB. \\
\emph{Central Processing Units-Modigliani}: Intel Core i5-4th generation, 4 cores 3.20 GHz CPU clock rate, 8 GB RAM\\
\emph{Central Processing Units-Monet} : Intel Core i7-3rd generation, 12 cores 3.20 GHz CPU clock rate, 32 GB RAM\\
\subsection{Software}
CUDA Driver Version / Runtime Version      6.5 / 6.0\\
Nsight Eclipse Version 6.5
\subsection{Performance and Evaluation}
\begin{table}[htb]
\caption{Speedup Performance of different MIMO Array size}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{ Array size} & \multicolumn{3}{|c|}{Time/s} & \multicolumn{2}{|c|}{Speedup}\\
\cline{2-6}
&GTX 760 & modigliani & monet & GTX/modigliani  & GTX/monet \\
\hline
$8\time 8$& 0.46& 0.09&0.08 & 0.20& 0.17\\
\hline
$16\time 16$&1.56 &3.2&3.57& 2.05& 2.29\\
\hline
$20\time 20$&31 & 74& 81& 2.39& 2.61\\
\hline
$25\time 25$& 38& 112& 122& 2.94& 3.21\\
\hline
$32\time 32$& 611&2836&3033&4.64& 4.96 \\
\hline
\label{speedup}
\end{tabular}
\end{table}
  \quad We test 5 array sizes and make comparison between GTX 760 and two kinds of CPU, all the operation times we test is based on 100 channel realizations, the transmitted data is generated randomly and modulated by $16$ QAM modulation scheme,  as we can see in \ref{speedup}, for small size array, like $8\times 8$, GPU has no advantage over CPU, for small array size, the number of path that need to be searched is relatively small, the CPU has already had a good performance, there is a short time for GPU to "warm up", for data transferring, launch kernel function and host device synchronization, further more, for small number of threads, the memory R/W latency is not well hided. When the array size grows large, a large parallelism is achieved so that the GPU begin to display its data processing power, and with the array size increasing, this speedup tends to be much more considerable.
\section{Conclusion}
In this paper, we present the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional platform, we have reached up to nearly 5 times acceleration of FCSD and this speedup grows higher with the increasing array size. In addition, the GPU and CPU can work independently, the data processing power of GPU computing is an extra bonus of the traditional simulation platform. This shows the potential of GPU computing for the simulation and consumptive computational work of large MIMO area.      
% conference papers do not normally have an appendix

% use section* for acknowledgement
%\section*{Acknowledgment}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

% that's all folks
\end{spacing}
\bibliographystyle{IEEEtran}
\bibliography{citation}
\end{document}

### 2014-10-27 parallel acceleration of FCSD based on cuda/Acceleration_Figure.m

@@ -1,0 +1,14 @@
+X=[0.46,0.09,0.07;1.56,3.2,3.57;31,74,78;38,112,122;611,2836,3033];    %this is the operation time by second
+Y=[8,16,20,25,32];   %this is the array size
+figure(1)
+plot(1:5,X(:,1),'-^');
+hold on
+figure(1)
+plot(1:5,X(:,2),'-o');
+hold on
+figure(1)
+plot(1:5,X(:,3),'-*'); legend('GPU','CPU-modigaliani','CPU-monet');
+hold off
+bar(X);
+
+

### 2014-10-28 parallel acceleration of FCSD based on cuda/draft.tex
revised the latex draft

@@
 \begin{abstract}
-The large MIMO system which is a scaling up of conventional MIMO systems with several hundreds of antennas at the base station serving several tens of terminals at the same time,  which is thought to be a big idea for the next generation wireless communication system.
-However the detection of the large MIMO system acquires a long time to get optimum or sub-optimum solutions, In order to accelerate the real-time decoder for large MIMO system, in this paper we present General Purpose Graphic Processing Units (GPGPU) implementation of Fixed Complexity Sphere Decoder (FCSD) for the large scale MIMO system based on the dominant propriety framework of GPGPU-Computed Unified Device Architecture (CUDA).
-The simulation shows a up to nearly $5$ times acceleration for $32\times 32$ array of whole application CPU version, furthermore, the proposed CUDA-FCSD algorithm shows a increasing speedup performance for a increasing array size.
+Large MIMO constitutes a principal techniques for next generation wireless communication systems.
+Detection algorithms for large MIMO tend to require long simulation times and on conventional computer systems, In order to reduce the simulation times for decoders of large MIMO systems.
+In this paper we propose to use General Purpose Graphic Processing Units (GPGPU)to implement Fixed Complexity Sphere Decoder (FCSD) for the large scale MIMO system based on the dominant framework of GPGPU-Computed Unified Device Architecture (CUDA).
+The proposed CUDA-FCSD can chieve up to five times speedup over conventional CPU implementation while reaching the same Bit Error Rate (BER) performance.
+Furthermore the proposed algorithm demonstrates great potential to accelerate large MIMO systems.
 \end{abstract}
@@
 \section{Introduction}
- The common challenge that all the researchers, engineers and industrial companies are now facing in wireless communication area is the sharp contrast between the increasing demand of the mobile network speed for the transmission of rich media content and better QoS (quality of service) and the limited bandwidth of the radio frequency spectrum and a complex space time varying wireless environment, moreover in foreseeable future this demand will continue grow.
-Multiple Input Multiple Output (MIMO) has become a very promising technology that can help to solve this problem, the core idea of MIMO is to use multiple antennas both at the transmitting end and receiving end, the spatial domain sampled signal can be combined to provide parallel data pipes so that it can provide array gain, spatial diversity gain, spatial multiplexing gain, and interference reduction\cite{oestges2010mimo}.
-LTE standard support up to 8 antennas at the base station\cite{dahlman20103g}, The large scale MIMO (also named massive MIMO) is a system with hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}, originated from multiuser MIMO (MU-MIMO)\cite{larsson2013massive}.
-Large scale MIMO will inherit and enhance all the advantages of conventional MIMO (array gain, spatial diversity gain, spatial multiplexing gain and interference reduction), as well as reduction of latency, improvement of the whole system robustness.
- As a classical list based decoder for MIMO system, Sphere decoder (SD) can reach the optimum diversity gain as maximum likelihood (ML) detection with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}, however, there are two major problems of this decoder is the varied complexity with signal to noise ratio and sequential nature, which is contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system.
-Fixed Complexity Sphere Decoder (FCSD), overcomes this two disadvantage of the SD by searching the solution along the fixed number independent multiple paths\cite{barbero2008fixing}.
-GPGPU (General purpose Graphic processing Units Computing) has become a big idea in the industry and research of a variety of areas that needs massive data analysis and computation such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
-Comparing to CPU, The GPU has been designed as computational intensive, with most of the hardware resource be allocated for data processing and parallel computation rather than caching and flow control.
-In recent years GPU has reached huge advantages in data processing speed over CPU\cite{nvidia2008programming}.
-CUDA (Computed unified Device Architecture) is a programming model for GPGPU that proposed by Nvidia which has becoming the dominant proprietary framework for GPGPU programming, it is based on popular programming languages(C, C++, java, python, Fortran, Direct Compute) so that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
-The core essence of the CUDA is the Single Instruction Multiple Threads (SIMT) programming model, enables GPU can accelerate a lot of applications with the large dataset by implementing parallel data processing of complex computations.
-CUDA has become a parallel computing platform for wide community of different application developers in different areas.
+ \paragraph{} The present challenge in the wireless communication area is the sharp contrast between the increasing demand of mobile network speed for the transmission of rich media content with better QoS (quality of service), and the shortage of radio frequency spectrum.
+Multiple Input Multiple Output (MIMO) is thought to be a very promising technology that can help to solve this problem owing to several advantages it can offer.
+The core idea of MIMO is to use multiple antennas that at the transmitting and receiving sides that provide parallel data pipes in space resulting in spatial multiplexing gains\cite{oestges2010mimo}.
+For example the LTE standard supports up to 8 antennas at the base station\cite{dahlman20103g}.
+ \paragraph{} Large scale MIMO (also named massive MIMO) systems employ hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}.
+This technology originated from multiuser MIMO (MU-MIMO) systems\cite{larsson2013massive}.
+Large scale MIMO will inherit and enhance all the advantages of conventional MIMO (spatial diversity gain and spatial multiplexing gain), as well as reduction of latency and improvement of system robustness.
+ A common decoder for MIMO system is the Sphere Decoder (SD) that perform as well as a Maximum Likelihood (ML) decoder with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}.
+There are two major problems with the traditional SD decoder: complexity depending on Signal to Noise Ratio (SNR), and sequential nature, which is contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system.
+The Fixed Complexity Sphere Decoder (FCSD) overcomes these two disadvantages of the SD decoder by searching the solution along a fixed number of independent paths\cite{barbero2008fixing}.
+\paragraph{}General purpose Graphic processing Units Computing (GPGPU) has become a common trend in industry and research in areas that need massive computations such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
+Compared to CPU, the GPU can naturally cope with computational intensive tasks, since most of the hardware resource are allocated for data processing and parallel computation, rather than caching and flow control.
+In recent years GPU computing has provided significant advantages in data processing speeds over CPU computations\cite{nvidia2008programming}.
+Computed unified Device Architecture (CUDA) is a programming model for GPGPU that was proposed by Nvidia and is becoming the dominant framework for GPGPU programming.
+It is based on popular programming languages(C, C++, Java, Python, Fortran, Direct Compute), such that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
+CUDA employs the Single Instruction Multiple Threads (SIMT) programming model, enables a GPU implement parallel data processing, and has become a parallel computing platform for wide community of different applications.
+\paragraph{}In this paper, a GPU based implementation of Fixed Complexity Sphere Decoder is proposed, A heterogeneous programming solution for FCSD preprocessing and blocked parallel path searching solution are presented, the speedup results of different influence factors are presented and analyzed, The proposed CUDA-FCSD implementation demonstrates a great potential for large MIMO systems.
+\paragraph{}The rest of the paper is organized as follows.
+Section \ref{system} describes the MIMO systems model.
+Section \ref{programming model} introduces CUDA GPU architecture and the programming model.
+In section \ref{GPUFCSD}, we present details of the implementation of CUDA-FCSD.
+In section \ref{simulation}, the speedup and bit error rate (BER) performance of CUDA-FCSD are presented and analyzed.
+Finally conclusions are drawn in section \ref{conclusion}.
 \section{MIMO System Model}\label{system}
@@
 \section{CUDA GPU Architecture and  Programming Model} \label{programming model}
-  CUDA programming model is the C programming extension, with special defined syntax and structure, CUDA divide the CPU and GPU as host and device, the serial code executes on the host (CPU) side and parallel data processing is performed on the device (GPU) side, which is defined as heterogeneous programming model.
-The code executes on the device side is defined as $\mathit{kernel}$ function, which is a single instruction invoked at host side but with a massive parallel data processing threads execution on the device (SIMT), This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branching the behavior of each threads so that reach thread-level parallelism, thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share a memory called shared memory that all the threads in the block have the access to this pitch of memory, the GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU, Another function of the thread block is all the thread execute in one block can synchronize their action.
-The warp is the basic schedule unit with a constant number of threads  (for current version of CUDA device, the warp size is 32), when one warp are waiting for data loading the other warps just begin to execute.
-In a word CPU cores are designed to minimize latency for each thread at a time , whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput.
-Blocks are grouped into a one-dimensional, two-dimensional, or three-dimensional grid, similarly, one thread block can also be organized into one-dimentional, two-dimensional or three-dimensional.
-The organization of the block and grid shape and dimension is determined by the concrete application, Figure \ref{figure1} shows the 3 dimensional thread hierarchy of CUDA.
+\subsection{Memory Hierarchy}  
+CUDA programming model is the C programming extension, with special defined syntax and structure.
+The serial code executes on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side, is defined as a heterogeneous programming model.
+A thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share one pitch of on chip memory (shared memory), all the threads executed in one block can synchronize their action meaning the threads are permitted to run to the next instruction only when all the threads have reached the same instruction node.
+Blocks can be grouped into a one-dimensional, two-dimensional, or three-dimensional grid.
+Similarly, The threads can also be organized into one-dimensional, two-dimensional or three-dimensional blocks.
+The organization of the block and grid shape and dimension is determined by the application, Figure \ref{figure1} illustrates the 3 dimensional thread hierarchy of CUDA.
 \begin{figure}[htb]
@@
 \end{figure}
-In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
-The GPU works as a coprocessor system, consists of Stream Multiprocessors (SM), GeForce GTX 760 has 6 SM performs the multiply-add arithmetic operation and furthermore, each SM has the special functional units(SFU) that can perform more complex arithmetic operation such as trigonometric functions and reciprocal square root.
-the shared memory is also called on-chip memory which is located at SM that has low latency and limited capacity.
-Global memory, which is off-chip located memory of GPU with long latency and large capacity, another two types of the memory is called texture memory and constant memory, which are located off-chip , but cached, therefore the loading speed of the data located at these two type of memory space will be much faster than the that from global memory, for constant memory, it is read only and the memory latency is approximately as small as the registers.
-The variables invoked in kernel functions can be stored in either of the these 4 types of memories.
-Registers are allocated dynamically to threads.\\
-   Since the resource limitation of SM the total number of threads that we can define in one block is limited, on current CUDA supported GPUs, one block can contains up to 1024 threads, in addition all the blocks are executed on SMs, thus the total number of threads we can make use of is $T_{total}=Num_{SM}\times Num_{threads/SM}$, GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$, although in concrete application, the programmer can allocate more than 12288 threads for a kernel, but the threads will work in serial, which will influence the performance of program.
+
+\subsection{Single Instruction Multiple Thread (SIMT) Model} Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT).
+This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branch the behavior of each threads to achieve thread-level parallelism.
+The GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU, in a word CPU cores are designed to minimize latency for each thread at a time, whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput.
+\subsection{Mircroarchitecture of GPU} In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
+The GPU works as a coprocessor system, consisting of Stream Multiprocessors (SM).
+The GeForce GTX 760 has 6 SM that perform the multiply-add arithmetic operation.
+Furthermore, each SM has the special functional units(SFU) that can perform more complex arithmetics such as trigonometric functions and reciprocal square root.
+The shared memory is on chip memory located at SM and has low latency and limited capacity.
+Global memory, which is off-chip memory of the GPU with long latency and large capacity.
+Another two types of the memory, called texture memory and constant memory, are located off-chip, but cached.
+Therefore the loading speed of the data located in these two type of memory space is much faster than that from global memory.
+Constant memory is read only and with latency approximately as small as the registers.
+The variables invoked in kernel functions can be stored in either of the these four types of memories.
+Registers are allocated dynamically to threads.
+\paragraph{}Because of the resource limitation of SM the total number of threads can be defined in one block is limited.
+On current CUDA supported GPUs, one block can contains up to 1024 threads, and all the blocks are executed on SM.
+Thus the total number of threads ($T_{total}$) we can make use of is $T_{total}=N_{threads}\times N_{threads/SM} $, $N_{SM}$ and $N_{threads/SM}$ denote the number of SM and number of threads per SM.
+The GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$.
+In concrete applications, the programmer can allocate more than 12288 threads for a kernel, but the threads will work in serial, which will influence the program performance.
 \begin{figure}[htb]
@@
 % command of the stfloats package.
-\section{GPU Based Acceleration of FCSD}
+\section{GPU Based Acceleration of FCSD}\label{GPUFCSD}
 In this section we present the parallel implementation of fixed complexity sphere decoder by GPU, first from (\ref{formula 1}), the maximum likelihood (ML) solution is given by:
@@
 Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the kernel function for 86 times and get the final solution.
-\section{Simulation Results}
+\section{Simulation Results}\label{simulation}
 \subsection{Environment}
@@
 When the array size grows large, a large parallelism is achieved so that the GPU begin to display its data processing power, and with the array size increasing, this speedup tends to be much more considerable.
-\section{Conclusion}
+\section{Conclusion}\label{conclusion}
 In this paper, we present the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional platform, we have reached up to nearly 5 times acceleration of FCSD and this speedup grows higher with the increasing array size.

### 2014-10-28 FCSD_BER_CPU/src/common.h

@@ -20,7 +20,7 @@
 #include <time.h>
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_complex_math.h>
-#define MATRIX_SIZE 8
+#define MATRIX_SIZE 16
 #define IDC2D(i,j,row)    (i)*row+j
 #define Constellationsize 4
 //void FCSD_detection(

### 2014-10-28 FCSD_BER_CPU/src/communication_line.cpp

@@ -77,7 +77,7 @@
 #define miniteration 1e5               //the minimum number of channel realizations
 #define minSymbolError 500          //the minimum number of symbol error
 #define epsilon 1e-5               //the accuracy
-#define SNRnum 6                    //the point number of signal to noise ratio per bit
+#define SNRnum 3                    //the point number of signal to noise ratio per bit
 void data_generator(gsl_vector_ulong *pdata, gsl_rng *pr, unsigned long Q);
 void grayencoder(gsl_vector_ulong *pgraydata, gsl_vector_ulong *pgrayindexes,
 		unsigned long Q);
@@ -152,12 +152,20 @@ int main(void) {
 	durationKernel_CPU = (float*) malloc(sizeof(float));
 	durationKernel_GPU = (float*) malloc(sizeof(float));
 	printf("the program for %dX%d %d QAM begin!!\n", MATRIX_SIZE,MATRIX_SIZE,M);
+	printf("the SNR per bit is:\n");
+//	fprintf(cfile1,"this is the SNR %d %f\n", 2*SNRnum, SNR[SNRnum] );
+	for(count1=0;count1<=SNRnum;count1++)
+	{
+	printf("%d ", 2*count1);
+	}
+	printf("\n");
 	fprintf(cfile1,"\n");
+	fprintf(cfile2,"\n");
 	fprintf(cfile1, "this is the bit error rate of %d X %d MIMO \n",
 			MATRIX_SIZE, MATRIX_SIZE);
 	fprintf(cfile1,"this is %d QAM modulation\n", M);
 	fprintf(cfile1, "the SNR per bit is:\n");
-	fprintf(cfile1,"this is the SNR %d %f\n", 2*SNRnum, SNR[SNRnum] );
+//	fprintf(cfile1,"this is the SNR %d %f\n", 2*SNRnum, SNR[SNRnum] );
 	for(count1=0;count1<=SNRnum;count1++)
 	{
 	fprintf(cfile1,"%d ", 2*count1);
@@ -173,7 +181,7 @@ int main(void) {
 			MATRIX_SIZE, MATRIX_SIZE);
 	fprintf(cfile2,"this is %d QAM modulation\n", M);
 	fprintf(cfile2, "the SNR per bit is:\n");
-	fprintf(cfile2,"this is SNR %d %f\n", 2*SNRnum, SNR[SNRnum]);
[…]

### 2014-10-29 parallel acceleration of FCSD based on cuda/draft.tex
revise the latex version

@@
 %\hfill December 27, 2012
-We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive antennas and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, in the flat fading channel the corresponding discrete time model is given:
+\paragraph{}We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel, corresponding to the discrete time model:
 \begin{equation}
-y=\mathbf{H}s+n   \label{formula 1}
+\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n}   \label{formula 1}
 \end{equation}
-$s\in \mathbb{C}^{N_{t}\times 1}$ is the transmit symbol vector, the symbol in $s$ are mutually independent and taken from the signal constellation $\mathbb{O}$ (BPSK, QPSK, M-QAM), $M$ is the signal constellation size, all the transmit symbol vectors forms a $N_{t}$-dimensional signal constellation $\mathbb{O}^{N_{t}}$.
-$\varepsilon[ss^{H}]=I_{N_t}E_{s}$, $E_{s}$ denotes the symbol average energy where $\varepsilon$ denotes the mean operation.
-$y\in \mathbb{C}^{N_{r}\times 1}$ is the receive symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean elements of unit variance, $n\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean elements of variance $\varepsilon[nn^{H}]=I_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise energy, $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR).
+$\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from the signal constellation $\mathbb{O}$ (4-QAM, 16-QAM, 64-QAM), of size $M$.
+The transmitted symbol vectors forms a $N_{t}$ complex signal vector space $\mathbb{O}^{N_{t}}$.
+$\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
+Furthermore,  $\mathbf{y}\in \mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean components of unit variance, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise power spectrum density and $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR).
 \\
-  Assume we have the perfect channel state information (CSI)  $\quad \mathbf{H}$, receive symbol vector $y$, and we had already known the SNR, the task of decoder for MIMO system is to estimate $s$ in \ref{formula 1} based on CSI and received signal.
+
+\paragraph{} Assume we have the perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known at the receiver, as well as the SNR.
+The task of MIMO decoder is to estimate $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
 

### 2014-10-29 FCSD_BER_CPU/src/FCSD_detection_CPU.h

@@ -568,19 +568,19 @@ for(count1=0;count1<pathNum;count1++)
 					                   gsl_complex QAM64_temp;
 								    	 d=sqrt(3/(2* (float)(Nt*(M-1))));
 								    	 //real part
-								    	 if(S_temp.dat[0]<(-6*d))
+								    	 if(S_temp.dat[0]<=(-6*d))
 								    	 {
 								    		 GSL_SET_REAL(&QAM64_temp,-7*d);
 								    	 }
-								    	 else if(S_temp.dat[0]<=(-4*d)&&S_temp.dat[0]>=(-6*d))
+								    	 else if(S_temp.dat[0]<=(-4*d)&&S_temp.dat[0]>(-6*d))
 								    	 {
 								    		 GSL_SET_REAL(&QAM64_temp,-5*d);
 								    	 }
-								    	 else if(S_temp.dat[0]<=(-2*d)&&S_temp.dat[0]>=(-4*d))
+								    	 else if(S_temp.dat[0]<=(-2*d)&&S_temp.dat[0]>(-4*d))
 								    	 {
 								    		 GSL_SET_REAL(&QAM64_temp,-3*d);
 								    	 }
-								    	 else if(S_temp.dat[0]<=(0)&&S_temp.dat[0]>=(-2*d))
+								    	 else if(S_temp.dat[0]<=(0)&&S_temp.dat[0]>(-2*d))
 								    	 {
 								    		 GSL_SET_REAL(&QAM64_temp,-d);
 								    	 }
@@ -588,32 +588,32 @@ for(count1=0;count1<pathNum;count1++)
 								    	 {
 								    		 GSL_SET_REAL(&QAM64_temp,7*d);
 								    	 }
-								    	 else if(S_temp.dat[0]<=(6*d)&&S_temp.dat[0]>=(4*d))
+								    	 else if(S_temp.dat[0]<=(6*d)&&S_temp.dat[0]>(4*d))
 								    	 {
 								    		 GSL_SET_REAL(&QAM64_temp,5*d);
 								    	 }
-								    	 else if(S_temp.dat[0]<=(4*d)&&S_temp.dat[0]>=(2*d))
+								    	 else if(S_temp.dat[0]<=(4*d)&&S_temp.dat[0]>(2*d))
 								    	 {
 								    		 GSL_SET_REAL(&QAM64_temp,3*d);
 								    	 }
[…]

### 2014-10-29 FCSD_BER_CPU/src/communication_line.cpp

@@ -78,7 +78,7 @@
 #define miniteration 1e5               //the minimum number of channel realizations
 #define minSymbolError 500          //the minimum number of symbol error
 #define epsilon 1e-5               //the accuracy
-#define SNRnum 3                    //the point number of signal to noise ratio per bit
+#define SNRnum 12                    //the point number of signal to noise ratio per bit
 void data_generator(gsl_vector_ulong *pdata, gsl_rng *pr, unsigned long Q);
 void grayencoder(gsl_vector_ulong *pgraydata, gsl_vector_ulong *pgrayindexes,
 		unsigned long Q);

### 2014-10-30 parallel_acceleration_of_FCSD_based_on_cuda/draft.tex
revised up to page 13

--- 2014-10-29 parallel acceleration of FCSD based on cuda/draft.tex
@@
 \section{GPU Based Acceleration of FCSD}\label{GPUFCSD}
-In this section we present the parallel implementation of fixed complexity sphere decoder by GPU, first from (\ref{formula 1}), the maximum likelihood (ML) solution is given by:
+\paragraph{}In this section we present the parallel implementation of fixed complexity sphere decoder using GPU, From (\ref{formula 1}), the maximum likelihood (ML) detector for a MIMO system is specified by:
 \begin{equation}
-s_{ML}=arg\min_{s\in \mathbb{O}^{N_{t}}}||y-\mathbf{H}s||^{2} \label{formula 2}
+s_{ML}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{y}-\mathbf{H}\mathbf{s}||^{2} \label{formula 2}
 \end{equation}
-we consider the array $N_{t}=N_{r}$, performing QR decomposition to channel propagation matrix
+We consider a MIMO system with  $N_{t}=N_{r}$. Performing the QR decomposition to the channel propagation matrix
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is the unitary matrix, $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is the upper triangular matrix, the basing on \cite{matrix theory}, the (\ref{formula 2}) can be changed to
+where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is an unitary matrix and $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is an upper triangular matrix, the basing on \cite{matrix theory}, we can write (\ref{formula 2}) as:
 \begin{eqnarray}
 \nonumber
-s_{ML}&=&arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}y-\mathbf{Q}^{H}\mathbf{H}s||^{2}\\
-&=& arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}y-\mathbf{R}s||^{2} \label{formula 3}
+\mathbf{s}_{ML}&=&arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}\mathbf{y}-\mathbf{Q}^{H}\mathbf{H}\mathbf{s}||^{2}\\
+&=& arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}\mathbf{y}-\mathbf{R}\mathbf{s}||^{2} \label{formula 3}
 \end{eqnarray}
-Consider the unconstrained estimation of $s$, $\hat{s}=\mathbf{G}y$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$ denotes the zero forcing equalizer, basing on \ref{QR}, we have  
+Consider the unconstrained estimation of $\mathbf{s}$, $\mathbf{\hat{s}}=\mathbf{G}\mathbf{y}$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$ based on \ref{QR}, we have  
 \begin{equation}
-\hat{s}=\mathbf{G}y=(\mathbf{R}^{H}\mathbf{R})^{-1}\mathbf{R}^{H}\mathbf{Q}^{H}y=\mathbf{R}^{-1}\mathbf{Q}^{H}y 
+\mathbf{\hat{s}}=\mathbf{G}\mathbf{y}=(\mathbf{R}^{H}\mathbf{R})^{-1}\mathbf{R}^{H}\mathbf{Q}^{H}\mathbf{y}
+=\mathbf{R}^{-1}\mathbf{Q}^{H}\mathbf{y}
 \label{unconstrained estimation}
 \end{equation} 
-Therefore $\mathbf{Q}^{H}y=\mathbf{R}\hat{s}$, the \ref{formula 3} can be changed to
+Therefore $\mathbf{Q}^{H}\mathbf{y}=\mathbf{R}\mathbf{\hat{s}}$, and \ref{formula 3} can be written as
 \begin{equation}
-s_{ML}=arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\hat{s}-s)||^{2} \label{formula 4}
+\mathbf{s_{ML}}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{s})||^{2} \label{formula 4}
 \end{equation}
-the Fixed Complexity Sphere Decoder works as a constant number of multiple path tree searching.
 \begin{figure}[tb]
@@
 \includegraphics[scale=0.5]{FCSD_tree_searching.eps}
-\caption{Tree searching of QPSK FCSD for 8x8 MIMO system}
+\caption{Tree searching of 4-QAM FCSD for 8x8 MIMO system}
 \label{figure4}
 \end{figure}
-As shown in Figure \ref{figure4}, just like SD the FCSD also performs depth first searching, at the first $\rho$ level the FCSD search all the possible signal symbols $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$ in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) level, the remain $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back equalization (DFE), from (\ref{formula 4}) the solution of FCSD can be given:
+\paragraph{}Just like SD the FCSD also performs depth first searching, at the first $\rho$ node levels the FCSD search all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) stage, therefore for the symbol nodes $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$, the FCSD has $M$ branches expansion at each symbol node,  as shown in Figure \ref{figure4}, there are $\rho=2$ FE nodes and each level has $M=4$ branches.
+(\ref{formula 4}) can be written in the form:
 \begin{equation}
-\hat{s}_{FCSD}=arg\min_{s\in \mathbb{O}^{N_{t}}}\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s_{j})|^{2}  \label{formula 5}
+\hat{s}_{FCSD}=arg\min_{s\in \mathbb{O}^{N_{t}}}\{\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s_{j})|^{2}\}  \label{formula 5}
 \end{equation} 
-$i\in [1,2\dots N_{t}]$, $r_{ij}$ denotes the element at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$, this process is called Single Expansion (FE).
-thus the FCSD solution $s_{FCSD}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
+$i\in [1,2\dots N_{t}]$, $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$,  based on \ref{formula 5} at the remaining $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back, therefore there are only $1$ branch expansion for each symbol node at this stage, this stage is called Single Expansion (SE).
+thus the total number of the branches is fixed (For example in Figure (\ref{figure4}) the total branch number is $4^{2}$), the FCSD works as a constant number of multiple path tree searching algorithm.
+In conclusion the FCSD solution $s_{FCSD}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
 \begin{displaymath}
 s_{FCSD}^{i}=\left\lbrace\begin{array}{c}
-\in \mathbb{O}^{\rho}      \quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
+\Omega\in  \mathbb{O}^{\rho}      \quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
 \mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}}-s_{FCSD}^{i})] \quad i=N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
@@
 \end{displaymath}
-$\mathbb{Q}[]$ denotes the signal constellation based quantization. At the post processing stage, FCSD takes the symbol vector candidate with the minimum Euclidean metric $E_{metric}$:
+$\mathbb{Q}[\cdot]$ denotes the signal constellation quantization.
+At the post processing stage, FCSD compares the Euclidean metric of all the symbol vector candidates $E_{metric}$, which, according to \ref{formula 4}, is defined as:
 \begin{equation}
-E_{metric}=||\mathbf{R}(\hat{s}-\widetilde{s})||^{2}
+E_{metric}=||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{\widetilde{s}})||^{2}
 \end{equation} 
-The $\widetilde{s}$ denotes the symbol vector candidate, the total number of candidates is: 
+Where the $\mathbf{\widetilde{s}}$ denotes the symbol vector candidate. The total number of candidates is: 
 \begin{equation}
@@
 \end{equation} 
-\subsection{CUDA-FCSD Pre-Prossing}
-As shown in figure.4, each path of the FCSD searching has a serial execution nature, in order to avoid error propagation of decoder, FCSD ordering was applied to the propagation channel based on post processing signal to noise ratio\cite{Vblas}, which can be expressed as:
+The symbol vector candidate with the minimum $E_{metric}$ is chosen as the solution.
+\subsection{CUDA-FCSD Preprossing}
+\paragraph{}As shown in Figure \ref{figure4}, each path of the FCSD searching has a serial execution nature.
+In order to avoid error propagation, FCSD ordering was applied to the propagation channel based on post processing signal to noise ratio\cite{wolniansky1998v}:
 \begin{equation}
@@
 \end{equation}
-$\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inversion of $HHH$ matrix $\mathbf{H}^{H}\mathbf{H}$, thus when the SNR is determined, the post processing SNR is only determined by $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$, for the FE stage the robustness of detector performance is not influenced by the post processing SNR thus at FE stage the "weakest" data stream is detected first, that is, the data stream with the smaller $\varphi$ is detected earlier.
-At SE stage, because of the single searching path of the symbol, the performance is tightly related to the post processing SNR, therefore at SE stage the data streams with the larger post processing SNR is detected earlier in order to avoiding the error propagation, in conclusion the FCSD ordering works iteratively  and obeys the following rule:
-At the $j$th step ($j=1,2\dots N_{t}-1$), $s_{p}$ denotes the symbol to be detected, where 
+where $\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, and $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inversion of $\mathbf{H}^{H}\mathbf{H}$.
+When the SNR is determined, the post processing SNR is only determined by $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$, From the heuristic in \cite{barbero2008fixing} for the FE stage the robustness of detector performance is not influenced by the post processing SNR.
+Thus at FE stage the "weakest" data stream, that is, the data stream with the smallest $\varphi$, is detected first.
+At SE stage, because of the single searching path of the symbol, the performance is tightly related to the post processing SNR.
+Therefore at SE stage the data streams with the larger post processing SNR is detected earlier in order to avoiding error propagation, In conclusion the FCSD ordering works iteratively  and obeys the following rule:
+at the $j$th step ($j=1,2\dots N_{t}-1$), $s_{p}$ denotes the symbol to be detected, where 
 \begin{displaymath}
 p=\left\lbrace \begin{array}{c}
-arg \max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE stage\\
-arg \min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE stage \\  \label{the ordering}
+arg \max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE\quad stage\\
+arg \min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE\quad stage   \label{the ordering}
 \end{array}\right.  
 \end{displaymath}  
-$\mathbf{H}_{j}\in \mathbb{C}^{N_{r}\times (N_{t}-j+1)}$ denotes the renewed channel matrix, at the $j$th iteration with the column corresponding to previous detected data streams removed from $\mathbf{H}_{j-1}$.
-the unconstrained estimation $\hat{s}$ in \ref{unconstrained estimation}  in is given by:
-\begin{equation}
- \hat{s}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y \label{shat}
-\end{equation}
+and $\mathbf{H}_{j}\in \mathbb{C}^{N_{r}\times (N_{t}-j+1)}$ denotes the renewed channel matrix.
+At the $j$th iteration with the column corresponding to previous detected data streams removed from $\mathbf{H}_{j-1}$.
+the unconstrained estimation $\mathbf{\hat{s}}$  is given in (\ref{unconstrained estimation}):
 
-Although the FCSD pre-processing has a serial nature and can not be vectorized, the computational consumptive operations \ref{the ordering} \ref{shat} can be implement by the CUDA Basic Linear Algebra Subprograms(cuBLAS), the matrix inverse(Gaussian Jordan Elimination) and cholesky factorization(Row Major Factorization) are also implemented by GPU, as shown in Table \ref{table 1}.
+\paragraph{}Although the FCSD pre-processing has a serial nature and can not be vectorized, the computational consumptive operations \ref{the ordering} \ref{shat} can be implement by the CUDA Basic Linear Algebra Subprograms(cuBLAS), the matrix inverse(Gaussian Jordan Elimination) and cholesky factorization(Row Major Factorization) are also implemented by GPU, as shown in Table \ref{table 1}.
 \begin{table}[htb]

### 2014-10-31 parallel_acceleration_of_FCSD_based_on_cuda/draft.tex
revised the conference paper Parallel Acceleration and code

@@
 \subsection{Memory Hierarchy}  
-CUDA programming model is the C programming extension, with special defined syntax and structure.
+\paragraph{}CUDA programming model is the C programming extension, with special defined syntax and structure.
 The serial code executes on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side, is defined as a heterogeneous programming model.
@@
 
-\subsection{Single Instruction Multiple Thread (SIMT) Model} Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT).
+\subsection{Single Instruction Multiple Thread (SIMT) Model} 
+\paragraph{}Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT).
 This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branch the behavior of each threads to achieve thread-level parallelism.
 The GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU, in a word CPU cores are designed to minimize latency for each thread at a time, whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput.
-\subsection{Mircroarchitecture of GPU} In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
+\subsection{Mircroarchitecture of GPU} 
+\paragraph{}In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
 The GPU works as a coprocessor system, consisting of Stream Multiprocessors (SM).
@@
 \centering
-\includegraphics[scale=0.5]{High_view_of_CUDA_GPU_microarchitecture.eps}
+\includegraphics[scale=0.6]{High_view_of_CUDA_GPU_microarchitecture.eps}
 \caption{High View of CUDA CPU Microarchitecture}
@@
 \end{equation}
-where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is an unitary matrix and $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is an upper triangular matrix, the basing on \cite{matrix theory}, we can write (\ref{formula 2}) as:
+where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is an unitary matrix and $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is an upper triangular matrix, the basing on \cite{golub2012matrix}, we can write (\ref{formula 2}) as:
 \begin{eqnarray}
@@
 $\mathbb{Q}[\cdot]$ denotes the signal constellation quantization.
-At the post processing stage, FCSD compares the Euclidean metric of all the symbol vector candidates $E_{metric}$, which, according to \ref{formula 4}, is defined as:
+At the post processing stage, FCSD compares the Euclidean distance of all the symbol vector candidates $E_{metric}$, which, according to \ref{formula 2}, can be written as:
 \begin{equation}
@@
 
-\paragraph{}Although the FCSD pre-processing has a serial nature and can not be vectorized, the computational consumptive operations \ref{the ordering} \ref{shat} can be implement by the CUDA Basic Linear Algebra Subprograms(cuBLAS), the matrix inverse(Gaussian Jordan Elimination) and cholesky factorization(Row Major Factorization) are also implemented by GPU, as shown in Table \ref{table 1}.
+\paragraph{}As mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
+Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational consumptive operations can be performed by the CUDA Basic Linear Algebra Subprograms(cuBLAS) and corresponding GPU program implementations, as shown in Table \ref{table 1}.
 \begin{table}[htb]
-\caption{Parallel Computation Operation of FCSD Pre-processing}
+\caption{Parallel Computation Operation of FCSD Preprocessing}
 \centering
@@
 
-Figure \ref{block diagram} shows the block diagram of the CUDA-FCSD implementation, as mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
+Figure \ref{block diagram} shows the block diagram of the CUDA-FCSD implementation. 
 \begin{figure}[htb]
 \centering
-\includegraphics[scale=0.8]{CUDA_FCSD_block_diagram.eps}
+\includegraphics[width=0.85\textwidth]{CUDA_FCSD_block_diagram.eps}
 \caption{Block Diagram of CUDA-FCSD Implementation}
@@
 \subsection{Parallel Acceleration of Blocked-Paths Searching}
-  We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt[2]{N_{t}}-1\rceil$, as mentioned in section \ref{programming model} the maximum number of threads that can be used in GPU is limited by the number of SM and maximum number of threads per SM, as to GeForce GTX 760.
+  \paragraph{}We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt[2]{N_{t}}-1\rceil$, as mentioned in section \ref{programming model} the maximum number of threads that can be used in GPU is limited by the number of SM and maximum number of threads per SM, as to GeForce GTX 760.
 we have $12288$ threads totally.
-For each path, decision feedback path searching has a serial nature, therefore we match path to one thread, in order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks, for largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads.
-At each path, we perform the following data operation:\\
+The decision feedback searching paths have serial nature, we match one path to one thread.
+In order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks.
+For largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads which is the maximum number of thread allowing per block.
+At each FCSD searching path, we perform the following data operation:\\
 1. \emph{Decision Feedback Equalization}\\
@@
 \nonumber
-{s}_{i}^{k}\in \mathbb{O}^{\rho}      \quad if\quad i&=&N_{t},N_{t}-1,\dots N_{t}-\rho+1\quad FE\\
+{s}_{i}^{k}\in \mathbb{O}^{\rho}      \quad if\quad i&=&N_{t},N_{t}-1,\dots N_{t}-\rho+1\quad FE \quad stage\\
 \nonumber
-{s}_{i}^{k}=\hat{s}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}^{k}}-s_{j}^{k})\quad if\quad i &=& N_{t}-\rho,N_{t}-\rho-1,\dots 2,1\quad SE\\  \label{path searching}
+\mathbf{s}_{i}^{k}=\mathbf{\hat{s}}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\mathbf{\hat{s}}_{j}^{k}-\mathbf{s}_{j}^{k})\quad if\quad i &=& N_{t}-\rho,N_{t}-\rho-1,\dots 2,1\quad SE\quad stage\\  \label{path searching}
 \end{eqnarray}
-$s_{j}^{k}$ denotes the $j$th symbol of the $k$th symbol vector candidate.\\
-2. \emph{Euclidean Metric Calculation}\\
+$\mathbf{s}_{j}^{k}$ denotes the $j$th symbol of the $k$th symbol vector candidate.\\
+2. \emph{Euclidean distance Calculation}\\
 \begin{equation}
-E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s_{j}}-s_{j})\label{Eu metric}
+E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\mathbf{\hat{s}}_{j}-\mathbf{s}_{j})\label{Eu metric}
 \end{equation}
-$E_{u}^{k}$ denotes the $k$th Euclidean metric of the corresponding symbol vector candidate $\widetilde{s}^{k}$. Then we take the symbol vector $s^{\theta}$ as the solution, where 
-\begin{equation}
-\theta=arg\min_{m}(E_{u}^{m})\quad m=1,2\dots M^{\rho} \label{Eu candidate}
-\end{equation}
-
+$E_{u}^{k}$ denotes the $k$th Euclidean distance of the corresponding symbol vector candidate. The symbol vector candidate with minimum Euclidean distance is chosen as the solution.  
 \subsubsection{Data Preparation}
-There are three major factors that will influence the configuration of the data set configuration in memory space.\\
-1. Amount of Reading$\&$Writing operation per thread.\\
-2. Program scope of the data.\\
-3. Storage Requirement of data.\\
-The memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influence the application performance because the GPU is data processing intensive and only has small cache for special memory space(constant, texture), another consideration is the validation life circle of data, local memory which is invoked in kernel function is valid in one thread, share memory is valid in one block, constant, texture and global memory are valid both at host side and device side.
-On the other hand different from global memory (2047 MBytes in GeForce GTX 760), the constant and share memory are all capacity limited (only $65536$ bytes totally and $49152$ bytes per block in GeForce GTX 760), so that for our application the configuration of memory is determined by the capacity requirement of the data.
-Here in table \ref{amount of R/W operation} we present the amount of R/W operations and the storage that needed for critical data variables in FCSD path searching.
-The amount of the R/W operation is calculated based on the (\ref{path searching}) and ((ref{Eu metric}), for complex value ($\mathbf{R}$,$\hat{s}$, $\mathit{s_{pontential matrix}}$,$\mathit{s_{kernel}}$ ) is stored use $\mathit{float2}$ which counts 8 bytes, floating point data set $E_{u}$ is stored in $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored use $\mathit{int}$, which counts 1 byte.
+\paragraph{}There are three major factors that will influence the configuration of the data sets configuration in memory space.\\
+1. Amount of Reading$\&$Writing (R/W) operation per thread.\\
+2. Valid scope\\
+3. Storage occupancy\\
+\paragraph{}GPU is computation intensive and only has small cache for special memory space (texture, constant).
+Thus the memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influences the application performance.
+Different memory types has different valid scope, local memory which is invoked in kernel function is valid only in one thread, share memory is valid in one block, constant, texture and global memory are valid both at host side and device side.
+On the other hand different from global memory (2047 MBytes in GeForce GTX 760), the constant and share memory are all capacity limited (only $65536$ bytes totally and $49152$ bytes per block in GeForce GTX 760).
+Thus the occupancy of memory is one determinant factor needed to be considered.
+In table \ref{amount of R/W operation} we present the amount of R/W operations and the storage that needed for critical data variables in FCSD path searching.
+The amount of the R/W operation is calculated based on the (\ref{path searching}) and (\ref{Eu metric}), for complex values ($\mathbf{R}$ $\mathbf{\hat{s}}$, $\mathit{s_{pm}}$, $\mathit{s_{kernel}}$ ) are stored using CUDA build in variable data type $\mathit{cuComplex}$ which counts 8 bytes.
+Floating point data set $E_{u}$ is stored using variable type $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored using variable type $\mathit{int}$, which counts 1 byte.\\
+ \paragraph{}At host side we set 4 data sets that are stored in global memory which are storage consumptive and have valid life circle for both host side and device side, $\mathit{s_{pm}}$ is a $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid life circle should be during the whole kernel execution.
+$\mathit{s_{index}}$ is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.
+$\mathit{E_{u}}$ is a $M^{\rho}$ floating point vector that is used to store the Euclidean distance of all the symbol vector candidates.
+$\mathit{s_{kernel}}$ is a complex vector used to store the FCSD solution which length is $N_{t}$ and has to be transferred to host side.
 \\
- At host side we set 4 vector data set that are stored linearly in global memory which has program scope for both host side and device side, $\mathit{s_{potential matrix}}$ is used to store the $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope is through the whole kernel function.
-$\mathit{s_{index}}$, which is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.
-$\mathit{E_{u}}$ is a $M^{\rho}$ floating point vector that is used to store the Euclidean metric of all the symbol vector candidates, obviously the valid scope of it is for the whole kernel function.
-$\mathit{s_{kernel}}$ is a complex vector used to store the FCSD solution which length is $N_{t}$ and has to be transferred to host side, thus it is also needed to be stored in global memory.
-\\
-  On the other hand,   upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\hat{s}$ in (\ref{unconstrained estimation})  requires a large amount of R operations and are read only.
-(for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\hat{s}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\hat{s}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section (\ref{programming model}), the constant memory is cached so that it is much faster than global memory.
+ \paragraph{} On the other hand, upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\mathbf{\hat{s}}$ in (\ref{unconstrained estimation}), require a large amount of read operations and are read only.
+(for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\mathbf{\hat{s}}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\hat{s}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section \ref{programming model}, the constant memory is cached so that it is much faster than global memory.
  \begin{table}[htb]  
@@
 \hline
-data & $\mathbf{R}$ & $\hat{s}$ & $\mathit{s_{pontential matrix}}$ & $\mathit{s_{index}}$ & $\mathit{E_{u}}$ & $\mathit{s_{kernel}}$ \\
+data & $\mathbf{R}$ & $\mathbf{\hat{s}}$ & $\mathit{s_{pm}}$ & $\mathit{s_{index}}$ & $\mathit{E_{u}}$ & $\mathit{s_{kernel}}$ \\
 \hline
-R/W operations/thread & $(\frac{3}{2}(N_{t})^{2}-\frac{N_{t}}{2}+\rho-\rho^{2})$ & $(\frac{2(N_{t})^{2}+2N_{t}-\rho^{2}-\rho}{2})$ & $\rho$ & $N_{t}$ &$N_{t} $ & $N_{t}$ \\
+R/W operations/thread & $(\frac{3}{2}(N_{t})^{2}-\frac{N_{t}}{2}+\rho-\rho^{2})$ & $(\frac{2(N_{t})^{2}+2N_{t}-\rho^{2}-\rho}{2})$ & $N_{t}$ & $\rho$ &$N_{t}$ & $N_{t}$ \\
 \hline
@@
 we store $\mathit{s_{potential matrix}}$ in one pitch of linear global memory, with each row store one $N_{t}=16$ complex symbol vector solution candidate of $\hat{s}_{FCSD}$ in (\ref{formula 5}), totally there are $M^{\rho}=4096$ rows, this matrix is stored in column major.
-As mentioned before we operate one path in one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256 bytes$, counts for two times of DRAM access.
+As mentioned before we operate one path in one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256$ bytes, counts for two times of DRAM access.
 \begin{figure}[htb]
@@
 \includegraphics[scale=0.63]{coalescing_global_memory.eps}
-\caption{Global Memory Access Pattern of $\mathit{s_{potential matrix}}$}
+\caption{Global Memory Access Pattern of $\mathit{s_{pm}}$}
 \label{coalesce global memory}
 \end{figure}
- Another available resource for memory bandwidth increase is to make use of share memory, for all the transient variables that used for accumulator in (\ref{path searching}) and (\ref{Eu metric}), because of the small capacity consumption and large amount of R/W operations.
+ \paragraph{}Another available resource for memory bandwidth increase is to make use of share memory, for all the transient variables that used for accumulator in (\ref{path searching}) and (\ref{Eu metric}), because of the small storage consumption and large amount of R/W operations.
 \subsubsection{Data Transfer Minimization}   
-The data transfer between the host side and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $y$ in (\ref{formula 1}) as well as the index list $\mathit{s_{index}}$ at FE stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
+\paragraph{}The data transfer between the host side and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the index list $\mathit{s_{index}}$ at FE stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
 \subsection{Going to Larger MIMO System}
-  Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, from \ref{path number}, the path number that need to be searched is $16^{5}=1048576$, as mentioned in section (\ref{programming model}), the maximum number of threads that can be execute in kernel function of GeForce GTX 760 is 12288, therefore we need to consider serial the one kernel into a certain times of loop, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
+  \paragraph{}Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, the path number that need to be searched is $M^{\rho}=16^{5}=1048576$.
+The maximum number of threads that can be execute in kernel function of GeForce GTX 760 is 12288, therefore we need to consider execute the kernel function serially, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
 Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the kernel function for 86 times and get the final solution.
+The same strategy can be applied to CUDA-FCSD for larger size MIMO systems.
 \section{Simulation Results}\label{simulation}
@@
 \cline{2-6}
-&GTX 760 & modigliani & monet & GTX/modigliani  & GTX/monet \\
+&GTX 760 & modigliani & monet & GTX 760/modigliani  & GTX 760/monet \\
 \hline
@@
 \end{table}
-  \quad We test 5 array sizes and make comparison between GTX 760 and two kinds of CPU, all the operation times we test is based on 100 channel realizations, the transmitted data is generated randomly and modulated by $16$ QAM modulation scheme,  as we can see in \ref{speedup}, for small size array, like $8\times 8$, GPU has no advantage over CPU, for small array size, the number of path that need to be searched is relatively small, the CPU has already had a good performance, there is a short time for GPU to "warm up", for data transferring, launch kernel function and host device synchronization, further more, for small number of threads, the memory R/W latency is not well hided.
-When the array size grows large, a large parallelism is achieved so that the GPU begin to display its data processing power, and with the array size increasing, this speedup tends to be much more considerable.
+\paragraph{} We make simulation to different array sizes and signal constellation and make comparison between GTX 760 and two kinds of CPU, all the operation times we test is based on 100 channel realizations, the transmitted data is generated randomly and modulated by $M$ QAM modulation scheme,  as we can see in Table \ref{speedup}, for small size of array and signal constellation, like $8\times 8$ array $4$-QAM, GPU has no advantage over CPU, for small array size and signal constellation, the number of path that need to be searched is relatively small, the CPU has already had a good performance, there is a short time for GPU to "warm up", for data transferring, launch kernel function and host device synchronization, further more, for small number of threads, the memory R/W latency is not well hided.
+When the size of array or signal constellation size  grows large, a large parallelism is achieved so that the GPU begin to display its data processing power, For example , and with the size of array and signal constellation increasing, this speedup tends to be much more considerable.
 \section{Conclusion}\label{conclusion}
-In this paper, we present the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional platform, we have reached up to nearly 5 times acceleration of FCSD and this speedup grows higher with the increasing array size.
+\paragraph{}This paper presents the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional computation platform, we have reached considerable acceleration of FCSD and this speedup grows larger for large MIMO system.
 In addition, the GPU and CPU can work independently, the data processing power of GPU computing is an extra bonus of the traditional simulation platform.
-This shows the potential of GPU computing for the simulation and consumptive computational work of large MIMO area.
+This shows the potential of GPU computing for computational consumptive simulation in large MIMO area.
 % conference papers do not normally have an appendix

### 2014-10-31 FCSD_BER_CPU/src/communication_line.cpp

@@ -78,7 +78,7 @@
 #define miniteration 1e5               //the minimum number of channel realizations
 #define minSymbolError 500          //the minimum number of symbol error
 #define epsilon 1e-5               //the accuracy
-#define SNRnum 12                    //the point number of signal to noise ratio per bit
+#define SNRnum 6                     //the point number of signal to noise ratio per bit
 void data_generator(gsl_vector_ulong *pdata, gsl_rng *pr, unsigned long Q);
 void grayencoder(gsl_vector_ulong *pgraydata, gsl_vector_ulong *pgrayindexes,
 		unsigned long Q);
@@ -154,7 +154,7 @@ int main(void) {
 	durationKernel_GPU = (float*) malloc(sizeof(float));
 	printf("the program for %dX%d %d QAM begin!!\n", MATRIX_SIZE,MATRIX_SIZE,M);
 	printf("the SNR per bit is:\n");
-//	fprintf(cfile1,"this is the SNR %d %f\n", 2*SNRnum, SNR[SNRnum] );
+	fprintf(cfile1,"this is the SNR %d %f\n", 2*SNRnum, SNR[SNRnum] );
 	for(count1=0;count1<=SNRnum;count1++)
 	{
 	printf("%d ", 2*count1);
@@ -166,7 +166,7 @@ int main(void) {
 			MATRIX_SIZE, MATRIX_SIZE);
 	fprintf(cfile1,"this is %d QAM modulation\n", M);
 	fprintf(cfile1, "the SNR per bit is:\n");
-//	fprintf(cfile1,"this is the SNR %d %f\n", 2*SNRnum, SNR[SNRnum] );
+	fprintf(cfile1,"this is the SNR %d %f\n", 2*SNRnum, SNR[SNRnum] );
 	for(count1=0;count1<=SNRnum;count1++)
 	{
 	fprintf(cfile1,"%d ", 2*count1);
@@ -198,7 +198,7 @@ int main(void) {
 	fclose(cfile3);
 	fclose(cfile4);
 	time1 = clock();
-	for (count = 0; count <=SNRnum; count++) {
+	for (count = SNRnum; count <=SNRnum; count++) {
 		iteration = 0;
 		bitError = 0;
 		symbolError = 0;

### 2014-11-02 parallel_acceleration_of_FCSD_based_on_cuda/draft.tex
running the MT simulation on GPU

@@
 \begin{table}[htb]
-\caption{Speedup Performance of different MIMO Array size}
+\caption{Speedup Performance of Different Sizes of MIMO Array for 4 QAM}
 \centering
@@
 \cline{2-6}
-&GTX 760 & modigliani & monet & GTX 760/modigliani  & GTX 760/monet \\
+&GeForce GTX 760 & modigliani & monet &  GTX 760/modigliani  &  GTX 760/monet \\
 \hline
-$8\time 8$& 0.46& 0.09&0.08 & 0.20& 0.17\\
+$8\times 8$& 1.88& 0.10&0.11 & 0.05& 0.06\\
 \hline
-$16\time 16$&1.56 &3.2&3.57& 2.05& 2.29\\
+$16\times 16$&6.12 & 0.92&0.98& 0.15& 0.16\\
 \hline
-$20\time 20$&31 & 74& 81& 2.39& 2.61\\
+$32\times 32$&38.32 & 31.27& 34.60& 0.82& 0.90\\
 \hline
-$25\time 25$& 38& 112& 122& 2.94& 3.21\\
+$48\times 48$&113.80& 262.00& 285.14& 2.30& 2.51\\
 \hline
-$32\time 32$& 611&2836&3033&4.64& 4.96 \\
+$64\times 64$& 537.41&1753.30&1940.10&3.26& 3.61 \\
 \hline
-\label{speedup}
+$72\times 72 $&2294.32&8727.69 &9641.80 &3.80 &4.20 \\
+\hline
+\label{speedup1}
+
 \end{tabular}
 \end{table}
-\paragraph{} We make simulation to different array sizes and signal constellation and make comparison between GTX 760 and two kinds of CPU, all the operation times we test is based on 100 channel realizations, the transmitted data is generated randomly and modulated by $M$ QAM modulation scheme,  as we can see in Table \ref{speedup}, for small size of array and signal constellation, like $8\times 8$ array $4$-QAM, GPU has no advantage over CPU, for small array size and signal constellation, the number of path that need to be searched is relatively small, the CPU has already had a good performance, there is a short time for GPU to "warm up", for data transferring, launch kernel function and host device synchronization, further more, for small number of threads, the memory R/W latency is not well hided.
+
+\begin{table}[htb]
+\caption{Speedup Performance of Different Sizes of MIMO Array for 16 QAM}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{ Array size} & \multicolumn{3}{|c|}{Time/s} & \multicolumn{2}{|c|}{Speedup}\\
+\cline{2-6}
+&GeForce GTX 760 & modigliani & monet &  GTX 760/modigliani  &  GTX 760/monet \\
+\hline
+$8\times 8$&2.60& 0.67&0.93 & 0.26&0.36 \\
+\hline
+$16\times 16$&26.80 & 31.68&41.95& 1.18& 1.57\\
+\hline
+$20\times 20$&478.40 & 740.50& 978.26& 1.55& 2.04\\
+\hline
+$32\times 32$&12330.05& 28209.53& 38106.00& 2.29& 3.09\\
+\hline
+$36\times 36$& 13480.01&35240.16&47290.00&2.61& 3.51 \\
+
+\hline
+\label{speedup1}
+
+\end{tabular}
+\end{table}
+
+\begin{table}[htb]
+\caption{Speedup Performance of Different Sizes of MIMO Array for 64 QAM}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*}{ Array size} & \multicolumn{3}{|c|}{Time/s} & \multicolumn{2}{|c|}{Speedup}\\
+\cline{2-6}
+&GeForce GTX 760 & modigliani & monet &  GTX 760/modigliani  &  GTX 760/monet \\
+\hline
+$8\times 8$&12.28& 10.69&13.38 & 0.87&1.09 \\
+\hline
+$16\times 16$&1460.11 & 2066.08&2689.00& 1.42& 1.84\\
+
+\hline
+\label{speedup1}
+
+\end{tabular}
+\end{table}
+\paragraph{} We made simulation to different sizes of array and signal constellation and make comparison between GTX 760 and two kinds of CPU, all the operation times we test is based on $1000$ channel realizations, the transmitted data is generated randomly and modulated by $M$ quadrature amplitude modulation (QAM) scheme.
+In Table \ref{speedup1}, for small size of array and signal constellation, like $8\times 8$ array $4$-QAM, GPU has no advantage over CPU, for small array size and signal constellation, the number of path that need to be searched is relatively small, the CPU has already had a good performance, there is a short time for GPU to "warm up", for data transferring, launch kernel function and host device synchronization, further more, for small number of threads, the memory R/W latency is not well hided.
 When the size of array or signal constellation size  grows large, a large parallelism is achieved so that the GPU begin to display its data processing power, For example , and with the size of array and signal constellation increasing, this speedup tends to be much more considerable.

### 2014-11-02 FCSD_BER_CPU/src/common.h

@@ -20,9 +20,9 @@
 #include <time.h>
 #include <gsl/gsl_complex.h>
 #include <gsl/gsl_complex_math.h>
-#define MATRIX_SIZE 8
+#define MATRIX_SIZE 16
 #define IDC2D(i,j,row)    (i)*row+j
-#define Constellationsize 4
+#define Constellationsize 64
 //void FCSD_detection(
 //		cuComplex *sigRec,   //received signal vector
 //		cuComplex *pH,        //propagation matrix

### 2014-11-02 FCSD_GPU/protection/FCSD_decodingwithoutloop.cu

@@ -75,8 +75,8 @@ __global__ void FEpath(
 
 	error_t error;
 	int count1, count2, count3, count4;
-	__shared__ float d; //the minimum distance unit between the signal constellation, the distance is usually 2d
-	__shared__ cuComplex alpha, beta;
+	 float d; //the minimum distance unit between the signal constellation, the distance is usually 2d
+	 cuComplex alpha, beta;
 	alpha.x = 1;
 	alpha.y = 0;
 	beta.x = 0;

### 2014-11-02 FCSD_GPU/src/communication_line.cpp

@@ -75,10 +75,10 @@
 #define SER "symbol_error_rate.txt"  //the file to store the symbol error rate
 #define timeused "time.txt"              //the file to store operation time of detection algorithm
 #define GFLOPS "GFLOPS.txt"          //the file to store the Giga flops operated per second
-#define miniteration 1e5               //the minimum number of channel realizations
-#define minSymbolError 500          //the minimum number of symbol error
+#define miniteration 1e4               //the minimum number of channel realizations
+#define minSymbolError 300          //the minimum number of symbol error
 #define epsilon 1e-5               //the accuracy
-#define SNRnum 6                     //the point number of signal to noise ratio per bit
+#define SNRnum 4                     //the point number of signal to noise ratio per bit
 void data_generator(gsl_vector_ulong *pdata, gsl_rng *pr, unsigned long Q);
 void grayencoder(gsl_vector_ulong *pgraydata, gsl_vector_ulong *pgrayindexes,
 		unsigned long Q);
@@ -119,7 +119,7 @@ int main(void) {
 	GSL_SET_COMPLEX(&one, 1.0, 0.0);
 	gsl_complex zero;
 	GSL_SET_COMPLEX(&zero, 0.0, 0.0);
-	SNR = (float*) malloc(11 * sizeof(float));
+	SNR = (float*) malloc((SNRnum+1) * sizeof(float));
 	for (count1 = 0; count1 <=SNRnum; count1++) {
 		SNR[count1] = pow(10, float(((count1) * 2) / float(10))); //test the SNR from 2 to 20 the step is 2
 	}
@@ -198,12 +198,14 @@ int main(void) {
 	fclose(cfile3);
 	fclose(cfile4);
 	time1 = clock();
-	for (count = SNRnum; count <=SNRnum; count++) {
+	for (count = 0; count <=SNRnum; count++) {
 		iteration = 0;
 		bitError = 0;
 		symbolError = 0;
 		BitErrorRate = 0;
 		SymbolErrorRate = 0;
+		duration_GPU=0;
+		duration_CPU=0;
 		cfile1 = fopen(BER, "a");
 		cfile2 = fopen(SER, "a");
 		cfile3 = fopen(timeused, "a");
@@ -254,17 +256,17 @@ int main(void) {
[…]

### 2014-11-02 parallel_acceleration_of_FCSD_based_on_cuda/draft.tex
add BER curve

@@
 $E_{u}^{k}$ denotes the $k$th Euclidean distance of the corresponding symbol vector candidate. The symbol vector candidate with minimum Euclidean distance is chosen as the solution.  
-\subsubsection{Data Preparation}
+\subsubsection{Data Preparation}\label{data preparation}
 \paragraph{}There are three major factors that will influence the configuration of the data sets configuration in memory space.\\
@@
 The maximum number of threads that can be execute in kernel function of GeForce GTX 760 is 12288, therefore we need to consider execute the kernel function serially, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
-Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the kernel function for 86 times and get the final solution.
-The same strategy can be applied to CUDA-FCSD for larger size MIMO systems.
+Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the kernel function for 86 times and get the final solution,  when it comes to the large MIMO systems and large signal constellations such as $36\times 36$ $16$QAM, $144\times 144$ $4$QAM, $20\times 20$ $64$QAM, the global memory that need to used to store $s_{pm}$ in section (\ref{data preparation}) will out of bound (2 GB), multiple kernels with each one deal with a small subset of symbol vector candidates and kernel concurrency\cite{nvidia2008programming} can be applied for solving this problem.
 \section{Simulation Results}\label{simulation}
@@
 \begin{table}[htb]
-\caption{Speedup Performance of Different Sizes of MIMO Array for 4 QAM}
+
 \centering
@@
 \hline
+\end{tabular}
+\caption{speedup performance of different MIMO systems using 4 QAM}
 \label{speedup1}
-
-\end{tabular}
 \end{table}
@@
 \begin{table}[htb]
-\caption{Speedup Performance of Different Sizes of MIMO Array for 16 QAM}
 \centering
@@
 $36\times 36$& 13480.01&35240.16&47290.00&2.61& 3.51 \\
-
 \hline
-\label{speedup1}
-
 \end{tabular}
+\caption{speedup performance of different MIMO systems using 16 QAM}
+\label{speedup2}
 \end{table}
@@
 \begin{table}[htb]
-\caption{Speedup Performance of Different Sizes of MIMO Array for 64 QAM}
 \centering
@@
 \hline
-\label{speedup1}
 
 \end{tabular}
+\caption{speedup performance of different MIMO systems using 64 QAM}
+\label{speedup3}
 \end{table}
-\paragraph{} We made simulation to different sizes of array and signal constellation and make comparison between GTX 760 and two kinds of CPU, all the operation times we test is based on $1000$ channel realizations, the transmitted data is generated randomly and modulated by $M$ quadrature amplitude modulation (QAM) scheme.
-In Table \ref{speedup1}, for small size of array and signal constellation, like $8\times 8$ array $4$-QAM, GPU has no advantage over CPU, for small array size and signal constellation, the number of path that need to be searched is relatively small, the CPU has already had a good performance, there is a short time for GPU to "warm up", for data transferring, launch kernel function and host device synchronization, further more, for small number of threads, the memory R/W latency is not well hided.
-When the size of array or signal constellation size  grows large, a large parallelism is achieved so that the GPU begin to display its data processing power, For example , and with the size of array and signal constellation increasing, this speedup tends to be much more considerable.
+
+\paragraph{} We made simulation to different sizes MIMO systems and signal constellation and comparison is made between Geforce GTX 760 and two kinds of CPU, the speedup performance is presented in table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
+All the operation times we test is based on $1000$ channel realizations, the transmitted data is generated randomly and modulated by $M$ quadrature amplitude modulation (QAM) scheme.
+In table \ref{speedup1}, for small MIMO systems $8\times 8$ and $16\times 16$, the speed performance of GPU implementation is even worse than that of CPU, for both antenna configurations the the number of path that need to be searched is relatively small ($16$ for $8\times 8$ system and $64$ for $16\times 16$ system), the CPU implementation has already had a good performance, there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
+Furthermore, for small number of threads, the memory R/W latency is not well hided.
+For the $32\times 32$ systems, the speed performance of GPU and CPU implementation is close, when comes to larger MIMO systems $48\times 48$, $64\times 64$, $72\times 72$, a large parallelism is achieved so that the GPU begin to display its data processing power, the speedup can be from $2.50$ to $4.20$.
+\paragraph{}In table \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM is considered, the speedup of GPU implementation is reached from a small MIMO size, For $16\times 16$ system using $16$QAM $1.18$ over modigliani and $1.57$ over monet.
+For $8\times 8$, $64$QAM, $0.87$ over modigliani and $1.09$ over monet.
+This is because for lager signal constellation, the massive parallelism can be reached for relatively small MIMO systems.
+\paragraph{}It can be observed from table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, GPU implementation shows its speed advantage over CPU implementation for increasing size of MIMO systems and signal constellations, indicating this GPU implementation's suitability for large MIMO system and large signal constellation.
+\paragraph{}Figure \ref{BER curve} shows the Monte Carlo simulation results of bit error rate per bit (BER per bit) performance for different MIMO systems and constellation sizes, we consider uncoded spatial multiplexing MIMO systems, the transmitted binary sequence is generated randomly and  mutually independent, modulated by $M$QAM modulation scheme, the results have been obtained using $100000$ channel realizations and $500$ symbol errors accumulated.
+\begin{figure}[htb]
+\centering
+\includegraphics[scale=0.7]{BER_curves.eps}
+\caption{BER performance of different sizes of MIMO systems and modulation scheme by CUDA-FCSD}
+\label{BER curve}
+\end{figure}
 \section{Conclusion}\label{conclusion}
-\paragraph{}This paper presents the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional computation platform, we have reached considerable acceleration of FCSD and this speedup grows larger for large MIMO system.
+\paragraph{}This paper presents the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional computation platform.
+In order to exploit the computational capability of GPU in the simulation of large MIMO systems, the utilization of heterogeneous programming model, thread resource limitation and memory configuration are considered in a comprehensive way.
+The simulation shows considerable acceleration of GPU implementation of FCSD can be reached for large MIMO systems and large signal constellation sizes while the same BER performance can be obtained.
 In addition, the GPU and CPU can work independently, the data processing power of GPU computing is an extra bonus of the traditional simulation platform.
 This shows the potential of GPU computing for computational consumptive simulation in large MIMO area.
+The future work contains taking into consider the kernel execution and data transferring concurrence in order to optimize memory allocation strategy for large MIMO systems.
+\newpage
 % conference papers do not normally have an appendix

### 2014-11-02 FCSD_GPU_48_4/src/FCSD_detection_CPU.h

@@ -1,0 +1,731 @@
+/* *
+ * Copyright 1993-2012 NVIDIA Corporation.  All rights reserved.
+ *
+ * Please refer to the NVIDIA end user license agreement (EULA) associated
+ * with this source code for terms and conditions that govern your use of
+ * this software. Any use, reproduction, disclosure, or distribution of
+ * this software and related documentation outside the terms of the EULA
+ * is strictly prohibited.
+ */
+#include <stdio.h>
+#include <stdlib.h>
+#include<string.h>
+#include <math.h>
+#include <gsl/gsl_rng.h>
+#include <time.h>
+#include <gsl/gsl_vector.h>
+#include <gsl/gsl_vector_ulong.h>
+#include <gsl/gsl_vector_int.h>
+#include <gsl/gsl_vector_complex.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#include <gsl/gsl_matrix_complex_float.h>
+#include <gsl/gsl_randist.h>
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_linalg.h>
+#include <gsl/gsl_combination.h>
+#include <gsl/gsl_eigen.h>
+#include<gsl/gsl_math.h>
+#include<gsl/gsl_sort.h>
+#include<gsl/gsl_sort_vector.h>
+#include<gsl/gsl_permutation.h>
+//#include"fullfactorial.h"
+#include"common.h"
+void FCSD_CPU(
+		gsl_vector_complex *preceived,   //received signal vector
+		gsl_matrix_complex *pH,        //propagation matrix
+				int Nt,             //number of transmit antennas
+				int Nr,              //number of receive antennas
+				int M,               //modulation scheme
+		gsl_vector_complex *psymbolconstellation, //the symbol constellation
+				float SNR,          //signal to noise ratio in decimal
+		gsl_vector_complex *symOut,    //output symbol vector
+		float *durationKernel
+		)
+{
+	int count1, count2,count3, count4;
+	int *list;
+	list=(int*)calloc(1,MATRIX_SIZE*sizeof(int));
[…]

### 2014-11-02 FCSD_GPU_48_4/src/MATRIX_INVERSE_GJE.cu

@@ -1,0 +1,261 @@
+/**
+ * Copyright 1993-2012 NVIDIA Corporation.  All rights reserved.
+ *
+ * Please refer to the NVIDIA end user license agreement (EULA) associated
+ * with this source code for terms and conditions that govern your use of
+ * this software. Any use, reproduction, disclosure, or distribution of
+ * this software and related documentation outside the terms of the EULA
+ * is strictly prohibited.
+ */
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <cuda_runtime.h>
+#include "cu_complex_operation.cuh"
+#include <cuComplex.h>
+#include <cuda.h>
+//#include<helper_cuda.h>
+//#include<helper_functions.h>
+#include<time.h>
+#include<cuda_profiler_api.h>
+#include"common.h"
+
+
+
+
+//pivot row normal1600ization
+__global__ void normalizePivotRow( cuComplex *H, int index, int lda ) {
+	int tid=threadIdx.x;
+__shared__ cuComplex pivotValue;
+if(tid==0)
+{
+//	printf("check the propagation matrix\n");
+//	for(int count1=0;count1<N1;count1++)
+//	{
+//		for(int count2=0;count2<2*N1;count2++)
+//		{
+//			printf("%0.4f%+0.4fi ", H[IDC2D(count1,count2,lda)].x, H[IDC2D(count1,count2,lda)].y);
+//		}
+//		printf("\n");
+//	}
+	}
+ if(tid<lda){
+
+			if ( tid == 0 ) // First thread of each block loads pivotValue
+			{
+			pivotValue = H[ IDC2D( index, index, lda) ];
+			}
+			__syncthreads();
+
+//			printf("the pivot value is %0.4f%+0.4fi :\n", pivotValue.x,pivotValue.y);
+			H[ IDC2D( index, tid, lda )]=complex_div(H[ IDC2D( index, tid, lda )],pivotValue);
+			__syncthreads();
+ }
+
+//printf("the thread Id of matrix iverse is:\n");
+//printf("%d ", tid);
+//printf("the row of the pivot H is:\n");
[…]

### 2014-11-02 FCSD_GPU_48_4/src/chol_without_onchipmem.cu

@@ -1,0 +1,188 @@
+/* *
+ * Copyright 1993-2012 NVIDIA Corporation.  All rights reserved.
+ *
+ * Please refer to the NVIDIA end user license agreement (EULA) associated
+ * with this source code for terms and conditions that govern your use of
+ * this software. Any use, reproduction, disclosure, or distribution of
+ * this software and related documentation outside the terms of the EULA
+ * is strictly prohibited.
+ */
+//#include <assert.h>
+//includes system
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include<math.h>
+//#include<cuda.h>
+// includes CUDA
+#include<cuda_runtime.h>
+#include<cuda.h>
+//#include<cutil.h>
+//includes project
+//#include<helper_cuda.h>
+//#include<helper_functions.h>
+#include"cu_complex_operation.cuh"
+#include"common.h"
+#include<cuComplex.h>
+#include<time.h>
+#include<cuda_profiler_api.h>
+#define BLOCKNUM 32
+ __global__ void chol_kernel_optimized
+ (
+		 cuComplex *R
+ )
+ {
+//	 int MATRIX_SIZE=N1;
+//	 extern __shared__ cuComplex R[];
+      cuComplex pivot;
+      cuComplex update;
+	 int count1,count2,count3;
+	 int tid=threadIdx.x;
+//	 bid=blockIdx.x;
+//	 tid=threadIdx.x;
+	  cuComplex zero;
+	 zero.x=0;
+	 zero.y=0;
+	 //cholesky factorization row by row
+	 for (count1=0;count1<MATRIX_SIZE;count1++)
+	 {
+//		 R[tid]=matrix[IDC2D(count1,tid,MATRIX_SIZE)];
+		 //pivoting step
+			if(tid==0)
+			{
+				if(count1==0)
+				{
+					R[IDC2D(count1,count1,MATRIX_SIZE)].x=sqrt(R[IDC2D(count1,count1,MATRIX_SIZE)].x);
+					R[IDC2D(count1,count1,MATRIX_SIZE)].y=0;
[…]

### 2014-11-02 FCSD_GPU_72_4/src/FCSD_decoding.cu

@@ -1,0 +1,491 @@
+/* *
+ * Copyright 1993-2012 NVIDIA Corporation.  All rights reserved.
+ *
+ * Please refer to the NVIDIA end user license agreement (EULA) associated
+ * with this source code for terms and conditions that govern your use of
+ * this software. Any use, reproduction, disclosure, or distribution of
+ * this software and related documentation outside the terms of the EULA
+ * is strictly prohibited.
+ */
+/*
+ * this function implement fixed complexity sphere decoding
+ * INPUT:
+ * y: received signal
+ * H: permuted propagation matrix
+ * M: modulation scheme, (2: BPSK 4: QPSK, 16: 16QAM, 64: 64QAM)
+ * psymbolconstellation: the symbol constellation
+ * OUTPUT:
+ * s: detection result
+ * Eu: Euclidean distance
+ */
+#include <stdio.h>
+#include <stdlib.h>
+#include<cuComplex.h>
+#include <string.h>
+#include<math.h>
+#include<cuda_runtime.h>
+#include<cuda.h>
+#include<cublas_v2.h>
+#include<time.h>
+#include"cu_complex_operation.cuh"
+#include"common.h"
+#include<cuda_runtime.h>
+#include<cuda.h>
+#include<cudaProfiler.h>
+#include<cuda_profiler_api.h>
+#include<device_functions.h>
+#define threadNum 1024
+#define blockNum 16
+#define stride 3
+/*
+ * in this version I applied colesced memory accesss to all the vector and matrix, with all the matrix stored in row major different threads reading one column
+ * with all the matrix stored in column major, different threads reading one row
+ * uitilize consecutive computation power
+ */__constant__ cuComplex d_R[MATRIX_SIZE * MATRIX_SIZE],
+		d_psymbolconstellation[16], d_constant_shat[MATRIX_SIZE];
+__constant__ int d_list[MATRIX_SIZE];
+__global__ void FEpath(
+//		cuComplex *d_R,  //upper triangular matrix after cholesky factorization
[…]

### 2014-11-02 FCSD_GPU_72_4/src/FCSD_ordering.cu

@@ -1,0 +1,206 @@
+/*
+ * FCSD_ordering.c
+ *this function implement the channel ordering of fixed complexity sphere decoding algorithm
+ *INPUT:
+ *pH: original propagation channel matrix
+ *list: permutation list
+ *pH_permuted: permuted propagation channel matrix
+ *  Created on: Jun 26, 2014
+ *      Author: Tianpei Chen
+ *      Email: tianpei.chen@mail.mcgill.ca
+ */
+
+//#ifndef FCSD_ORDERING_H_
+//#define FCSD_ORDERING_H_
+#include"common.h"
+#include<cublas_v2.h>
+#include<cuComplex.h>
+#include<cuda_runtime.h>
+#include<stdlib.h>
+#include<stdio.h>
+#include <math.h>
+#include<assert.h>
+#include<string.h>
+#include<cuda.h>
+void FCSD_ordering(
+		cuComplex *pH,
+		int *list,
+		cuComplex *d_pH_permuted
+)
+{
+
+	int count, count1,count2,count3;
+	int mm,*j,*list_temp;
+	j=(int*)malloc(sizeof(int));
+	list_temp=(int*)malloc(MATRIX_SIZE*sizeof(int));
+//	int *d_j;
+//	cudaMalloc((void**) &d_j, sizeof(int));
+	cuComplex *pH_loop;
+	pH_loop=(cuComplex*)malloc(MATRIX_SIZE*MATRIX_SIZE*sizeof(cuComplex));
+	int N=ceil(sqrt(MATRIX_SIZE)-1);//
+	cublasHandle_t handle;
+	cublasStatus_t ret;
+	cudaError_t error;
+	ret=cublasCreate(&handle);
+
+    cuComplex *d_pH, *d_Pprod, *d_Pinv;
+    cuComplex alpha,beta;
+    alpha.x=1;
+    alpha.y=0;
+    beta.x=0;
+    beta.y=0;
+	  clock_t start,end;
+	  start=clock();
+		error=cudaMalloc((void**) &d_Pprod, (MATRIX_SIZE)*(MATRIX_SIZE)*sizeof(cuComplex));//store the wishart matrix
+			if(error!=cudaSuccess)
+			{
+				printf("cudaMalloc d_Pprod returned error code %d, line %d\n", error, __LINE__);
+//				exit(EXIT_FAILURE);
+			}
[…]

### 2014-11-02 FCSD_GPU_72_4/src/binaryerrors.h

@@ -1,0 +1,21 @@
+unsigned long binaryerrors (unsigned long input, unsigned long output, unsigned long Q)
+{
+	unsigned long count=0UL, errors=0UL, temp=0UL, temp2=0UL;
+
+	int M=0;
+	M = (int) log2(static_cast<double>(Q));
+
+	temp = input^output;
+	errors = 0L;
+	for (count=0; count<M; count++)
+	  {
+		temp2 = temp%2;
+		temp = temp/2;
+		if (temp2 != 0)
+		 	errors = errors+1;
+
+	  } 
+	//printf ("\n input = %ld, \t output = %ld, \t errors = %ld", input, output, errors);
+
+	return errors;
+}

### 2014-11-02 FCSD_GPU_72_4/src/communication_line.cpp

@@ -1,0 +1,443 @@
+/**
+ * Copyright 1993-2012 NVIDIA Corporation.  All rights reserved.
+ *
+ * Please refer to the NVIDIA end user license agreement (EULA) associated
+ * with this source code for terms and conditions that govern your use of
+ * this software. Any use, reproduction, disclosure, or distribution of
+ * this software and related documentation outside the terms of the EULA
+ * is strictly prohibited.
+ */
+/**
+ *This is the communication line performing the fixed complexity sphere decoding algorithm
+ * * This function implement a complete communication line including: data generation, modulation,
+ * channel generation, detection, decoding, print the result, speed and bit error rate
+ * Tianpei chen
+ * Email:tianpei.chen@mail.mcgill.ca
+ * 2014.08.19
+ * pdata: the transmitted gray data in decimal
+ * pgraycode: find the indexes of symbol according to graycode
+ * pgrayindex: find the graycode according to the indexes of the symbol
+ * pgraydata: find the indexes according to the pdata
+ * ptransmitted: find the complex symbol corresponding to he pgraydata
+ */
+#include <stdio.h>
+#include <stdlib.h>
+#include<string.h>
+#include <math.h>
+#include <gsl/gsl_rng.h>
+#include <time.h>
+#include <gsl/gsl_vector.h>
+#include <gsl/gsl_vector_ulong.h>
+#include <gsl/gsl_vector_int.h>
+#include <gsl/gsl_vector_complex.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+/*#include <gsl/gsl_matrix.h>*/
+#include <gsl/gsl_matrix_complex_float.h>
+#include <gsl/gsl_randist.h>
+/*#include <gsl/gsl_cblas.h>*/
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_linalg.h>
+#include <gsl/gsl_combination.h>
+#include <gsl/gsl_eigen.h>
+#include<gsl/gsl_math.h>
+#include<gsl/gsl_sort.h>
+#include<gsl/gsl_sort_vector.h>
+#include<cuda_runtime.h>
+#include<assert.h>
+#include<time.h>
+#include"channel_generator.h"
[…]

### 2014-11-02 FCSD_GPU_72_4/src/row_column_transformation.cu

@@ -1,0 +1,78 @@
+/*
+ * row_column_transformation.cu
+ *
+ *  Created on: Jul 7, 2014
+ *      Author: tianpei.chen@mail.mcgill.ca
+ */
+#include"common.h"
+#include<cuComplex.h>
+#include<cuda.h>
+#include<stdio.h>
+#include<stdlib.h>
+#include<cuda_runtime.h>
+#include"cu_complex_operation.cuh"
+
+
+
+__global__ void MATRIX_ROWCOLUMNT_kernel(cuComplex *Hr,
+		cuComplex *Hc, int row, int column)
+{
+	int i=blockIdx.x;
+	int j=threadIdx.x;
+
+
+     Hc[IDC2D(j,i,row)]=Hr[IDC2D(j,i,column)];
+     __syncthreads();
+
+}
+
+
+
+
+__global__ void MATRIX_COLUMNROWT_kernel(cuComplex *Hc,
+		cuComplex *Hr, int row, int column)
+{
+	int i=blockIdx.x;
+	int j=threadIdx.x;
+
+
+     Hr[IDC2D(i,j,column)]=Hc[IDC2D(i,j,row)];
+     __syncthreads();
+
+
+}
+
+
+
+
+
+void MATRIX_COLUMNROWT(cuComplex *Hc, cuComplex *Hr, int row, int column){
+
+	cuComplex *d_pCC, *d_pCCR;
+
+	cudaMalloc((void**)&d_pCCR,row*column*sizeof(cuComplex));
+	cudaMalloc((void**)&d_pCC,row*column*sizeof(cuComplex));
+	cudaMemcpy(d_pCC,Hc,row*column*sizeof(cuComplex),cudaMemcpyHostToDevice);
+	dim3 blockDim(column,1);
+	MATRIX_COLUMNROWT_kernel<<<row,column,0>>>(d_pCC, d_pCCR, row, column);
+	cudaDeviceSynchronize();
+	cudaMemcpy(Hr,d_pCCR,row*column*sizeof(cuComplex),cudaMemcpyDeviceToHost);
+	cudaFree(d_pCC);
+	cudaFree(d_pCCR);
+
+}
+void MATRIX_ROWCOLUMNT(cuComplex *Hr, cuComplex *Hc, int row,int column){
+
+	cuComplex *d_pCC, *d_pCCR;
+
[…]

### 2014-11-03 parallel_acceleration_of_FCSD_based_on_cuda/draft.tex
upload the 2nd draft of GPU paper

@@
 % Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
+% should be used if it is desired that the figures are to be displayed inft.tex
+
 % draft mode.
@@
 %
-% If IEEEtran.cls has not been installed into the LaTeX system files,
+% If IEEEtran.cls has not been installed into the LaTeX system files,ft.tex
+
 % manually specify the path to it like:
@@
 % Do not put math or special symbols in the title.
-\title{Parallel Acceleration of Fixed Complexity Sphere Decoder for Large MIMO Uplink System based on GPU}
+\title{GPU Acceleration of Fixed Complexity Sphere Decoder for Large MIMO Uplink Systems}
 
@@
 \begin{spacing}{2.5}
+\date{}
 \maketitle
@@
 Large MIMO constitutes a principal techniques for next generation wireless communication systems.
-Detection algorithms for large MIMO tend to require long simulation times and on conventional computer systems, In order to reduce the simulation times for decoders of large MIMO systems.
-In this paper we propose to use General Purpose Graphic Processing Units (GPGPU)to implement Fixed Complexity Sphere Decoder (FCSD) for the large scale MIMO system based on the dominant framework of GPGPU-Computed Unified Device Architecture (CUDA).
-The proposed CUDA-FCSD can chieve up to five times speedup over conventional CPU implementation while reaching the same Bit Error Rate (BER) performance.
+Detection algorithms for large MIMO tend to require long simulation times on conventional computer systems, In order to reduce the simulation times for decoders of large MIMO systems, we propose to use General Purpose Graphic Processing Units (GPGPU).
+In this paper Fixed Complexity Sphere Decoder (FCSD) is implemented for the large scale MIMO system based on the dominant framework of GPGPU-Computed Unified Device Architecture (CUDA).
+The proposed CUDA-FCSD can achieve considerable speedup over conventional CPU implementation while reaching the same Bit Error Rate (BER) performance.
 Furthermore the proposed algorithm demonstrates great potential to accelerate large MIMO systems.
@@
 Multiple Input Multiple Output (MIMO) is thought to be a very promising technology that can help to solve this problem owing to several advantages it can offer.
-The core idea of MIMO is to use multiple antennas that at the transmitting and receiving sides that provide parallel data pipes in space resulting in spatial multiplexing gains\cite{oestges2010mimo}.
+The core idea of MIMO is to use multiple antennas that at the transmitting and receiving sides, that provide parallel data pipes in space resulting in spatial multiplexing gains\cite{oestges2010mimo}.
 For example the LTE standard supports up to 8 antennas at the base station\cite{dahlman20103g}.
@@
 Large scale MIMO will inherit and enhance all the advantages of conventional MIMO (spatial diversity gain and spatial multiplexing gain), as well as reduction of latency and improvement of system robustness.
- A common decoder for MIMO system is the Sphere Decoder (SD) that perform as well as a Maximum Likelihood (ML) decoder with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}.
-There are two major problems with the traditional SD decoder: complexity depending on Signal to Noise Ratio (SNR), and sequential nature, which is contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system.
+ A common detector for MIMO system is the Sphere Decoder (SD) that perform as well as a Maximum Likelihood detector (MLD) with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}.
+There are two major problems with the traditional SD decoder: complexity depending on Signal to Noise Ratio (SNR), and sequential nature, which are contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system.
 The Fixed Complexity Sphere Decoder (FCSD) overcomes these two disadvantages of the SD decoder by searching the solution along a fixed number of independent paths\cite{barbero2008fixing}.
@@
 It is based on popular programming languages(C, C++, Java, Python, Fortran, Direct Compute), such that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
-CUDA employs the Single Instruction Multiple Threads (SIMT) programming model, enables a GPU implement parallel data processing, and has become a parallel computing platform for wide community of different applications.
-\paragraph{}In this paper, a GPU based implementation of Fixed Complexity Sphere Decoder is proposed, A heterogeneous programming solution for FCSD preprocessing and blocked parallel path searching solution are presented, the speedup results of different influence factors are presented and analyzed, The proposed CUDA-FCSD implementation demonstrates a great potential for large MIMO systems.
+CUDA employs the Single Instruction Multiple Threads (SIMT) programming model, enables a GPU to implement parallel data processing, and has become a parallel computing platform for wide community of different applications.
+\paragraph{}In this paper, a GPU based implementation of Fixed Complexity Sphere Decoder is proposed, A heterogeneous programming solution for FCSD preprocessing and blocked parallel path searching solution are presented, the speedup as well as Bit Error Rate (BER) performance of different sizes of MIMO systems and signal constellations are presented and analyzed, The proposed CUDA-FCSD implementation demonstrates a great potential for large MIMO systems.
 \paragraph{}The rest of the paper is organized as follows.
@@
 The transmitted symbol vectors forms a $N_{t}$ complex signal vector space $\mathbb{O}^{N_{t}}$.
-$\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
+$\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
 Furthermore,  $\mathbf{y}\in \mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean components of unit variance, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise power spectrum density and $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR).
@@
 \subsection{Memory Hierarchy}  
-\paragraph{}CUDA programming model is the C programming extension, with special defined syntax and structure.
-The serial code executes on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side, is defined as a heterogeneous programming model.
+\paragraph{}CUDA programming model is a C programming extension, with special defined syntax and structure.
+The serial code is executed on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side, this is defined as a heterogeneous programming model.
 A thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share one pitch of on chip memory (shared memory), all the threads executed in one block can synchronize their action meaning the threads are permitted to run to the next instruction only when all the threads have reached the same instruction node.
@@
 \centering
-\includegraphics[scale=0.5]{CUDA_programming_hierachy.eps}
+\includegraphics[scale=0.7]{CUDA_programming_hierachy.eps}
 \caption{CUDA 3D thread hierachy\\ $5\times 5\times 5$ grid and each block contains $5\times 5\times 5$ threads\\}
@@
 \subsection{Single Instruction Multiple Thread (SIMT) Model} 
-\paragraph{}Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT).
+\paragraph{}Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT) model.
 This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branch the behavior of each threads to achieve thread-level parallelism.
-The GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU, in a word CPU cores are designed to minimize latency for each thread at a time, whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput.
+The GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU.
+In a word CPU cores are designed to minimize latency for each thread at a time, whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput.
 \subsection{Mircroarchitecture of GPU} 
@@
 Furthermore, each SM has the special functional units(SFU) that can perform more complex arithmetics such as trigonometric functions and reciprocal square root.
-The shared memory is on chip memory located at SM and has low latency and limited capacity.
-Global memory, which is off-chip memory of the GPU with long latency and large capacity.
-Another two types of the memory, called texture memory and constant memory, are located off-chip, but cached.
+The shared memory, also called on-chip memory located on SM and has low latency and limited capacity.
+Global memory, which is off-chip memory of the GPU has long latency and large capacity.
+Another two types of the memory, texture memory and constant memory, are located off-chip, but cached.
 Therefore the loading speed of the data located in these two type of memory space is much faster than that from global memory.
 Constant memory is read only and with latency approximately as small as the registers.
-The variables invoked in kernel functions can be stored in either of the these four types of memories.
+The variables invoked in $\mathit{kernel}$ functions can be stored in either of the these four types of memories.
 Registers are allocated dynamically to threads.
@@
 On current CUDA supported GPUs, one block can contains up to 1024 threads, and all the blocks are executed on SM.
-Thus the total number of threads ($T_{total}$) we can make use of is $T_{total}=N_{threads}\times N_{threads/SM} $, $N_{SM}$ and $N_{threads/SM}$ denote the number of SM and number of threads per SM.
+Thus the total number of threads ($T_{total}$) we can make use of is $T_{total}=N_{SM}\times N_{threads/SM} $, $N_{SM}$ and $N_{threads/SM}$ denote the number of SM and number of threads per SM.
 The GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$.
@@
 \section{GPU Based Acceleration of FCSD}\label{GPUFCSD}
-\paragraph{}In this section we present the parallel implementation of fixed complexity sphere decoder using GPU, From (\ref{formula 1}), the maximum likelihood (ML) detector for a MIMO system is specified by:
+\paragraph{}In this section we present the parallel implementation of fixed complexity sphere decoder using GPU, From (\ref{formula 1}), the maximum likelihood detector (MLD) for a MIMO system is specified by:
 \begin{equation}
-s_{ML}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{y}-\mathbf{H}\mathbf{s}||^{2} \label{formula 2}
+\mathbf{s}_{ML}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{y}-\mathbf{H}\mathbf{s}||^{2} \label{formula 2}
 \end{equation}
@@
 \end{eqnarray}
-Consider the unconstrained estimation of $\mathbf{s}$, $\mathbf{\hat{s}}=\mathbf{G}\mathbf{y}$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$ based on \ref{QR}, we have  
+Consider the unconstrained estimation of $\mathbf{s}$, $\mathbf{\hat{s}}=\mathbf{G}\mathbf{y}$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$ based on (\ref{QR}), we have  
 \begin{equation}
@@
 \end{equation} 
-Therefore $\mathbf{Q}^{H}\mathbf{y}=\mathbf{R}\mathbf{\hat{s}}$, and \ref{formula 3} can be written as
+Therefore $\mathbf{Q}^{H}\mathbf{y}=\mathbf{R}\mathbf{\hat{s}}$, and (\ref{formula 3}) can be written as
 \begin{equation}
-\mathbf{s_{ML}}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{s})||^{2} \label{formula 4}
+\mathbf{s}_{ML}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{s})||^{2} \label{formula 4}
 \end{equation}
-\begin{figure}[tb]
+\paragraph{}Just like SD the FCSD also performs depth first searching, at the first $\rho$ node levels the FCSD search all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) stage, therefore for the symbol nodes $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$, the FCSD has $M$ branches expansion at each symbol node,  as shown in Figure \ref{figure4}, there are $\rho=2$ FE nodes and each node level has $M=4$ branches.
+(\ref{formula 4}) can be written in the form:
+\begin{equation}
+\hat{s}^{F}_{i}=arg\min_{s\in \mathbb{O}^{N_{t}}}\{\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s_{j})|^{2}\}  \label{formula 5}
+\end{equation} 
+$i\in [1,2\dots N_{t}]$, where $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$,  based on (\ref{formula 5}) at the remaining $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back, therefore there are only $1$ branch expansion for each symbol node at this stage, this stage is called Single Expansion (SE).
+Thus the total number of the branches is fixed (For example in Figure \ref{figure4} the total branch number is $4^{2}$), the FCSD works as a constant number of multiple path tree searching algorithm.
+\begin{figure}[htb]
 \centering
-\includegraphics[scale=0.5]{FCSD_tree_searching.eps}
+\includegraphics[scale=0.8]{FCSD_tree_searching.eps}
 \caption{Tree searching of 4-QAM FCSD for 8x8 MIMO system}
@@
 \end{figure}
-\paragraph{}Just like SD the FCSD also performs depth first searching, at the first $\rho$ node levels the FCSD search all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) stage, therefore for the symbol nodes $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$, the FCSD has $M$ branches expansion at each symbol node,  as shown in Figure \ref{figure4}, there are $\rho=2$ FE nodes and each level has $M=4$ branches.
-(\ref{formula 4}) can be written in the form:
-\begin{equation}
-\hat{s}_{FCSD}=arg\min_{s\in \mathbb{O}^{N_{t}}}\{\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s_{j})|^{2}\}  \label{formula 5}
-\end{equation} 
-$i\in [1,2\dots N_{t}]$, $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$,  based on \ref{formula 5} at the remaining $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back, therefore there are only $1$ branch expansion for each symbol node at this stage, this stage is called Single Expansion (SE).
-thus the total number of the branches is fixed (For example in Figure (\ref{figure4}) the total branch number is $4^{2}$), the FCSD works as a constant number of multiple path tree searching algorithm.
-In conclusion the FCSD solution $s_{FCSD}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
+In conclusion the FCSD symbol vector candidate $s^{F}_{i}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
 \begin{displaymath}
-s_{FCSD}^{i}=\left\lbrace\begin{array}{c}
+s^{F}_{i}=\left\lbrace\begin{array}{c}
 \Omega\in  \mathbb{O}^{\rho}      \quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
-\mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}}-s_{FCSD}^{i})] \quad i=N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
+\mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}}-s_{F}^{i})] \quad i=N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
 \end{array}\right.
@@
 where $\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, and $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inversion of $\mathbf{H}^{H}\mathbf{H}$.
-When the SNR is determined, the post processing SNR is only determined by $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$, From the heuristic in \cite{barbero2008fixing} for the FE stage the robustness of detector performance is not influenced by the post processing SNR.
+When the SNR is determined, the post processing SNR is only determined by $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$.
+From the heuristic in \cite{barbero2008fixing},  for the FE stage the robustness of detector performance is not influenced by the post processing SNR.
 Thus at FE stage the "weakest" data stream, that is, the data stream with the smallest $\varphi$, is detected first.
-At SE stage, because of the single searching path of the symbol, the performance is tightly related to the post processing SNR.
-Therefore at SE stage the data streams with the larger post processing SNR is detected earlier in order to avoiding error propagation, In conclusion the FCSD ordering works iteratively  and obeys the following rule:
+At SE stage, because of the single searching path branch of the node, the performance is tightly related to the post processing SNR.
+Therefore at SE stage the data streams with the larger post processing SNR is detected first in order to avoiding error propagation.
+In conclusion the FCSD ordering works iteratively  and obeys the following rule:
 at the $j$th step ($j=1,2\dots N_{t}-1$), $s_{p}$ denotes the symbol to be detected, where 
@@
 At the $j$th iteration with the column corresponding to previous detected data streams removed from $\mathbf{H}_{j-1}$.
-the unconstrained estimation $\mathbf{\hat{s}}$  is given in (\ref{unconstrained estimation}):
 
 \paragraph{}As mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
-Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational consumptive operations can be performed by the CUDA Basic Linear Algebra Subprograms(cuBLAS) and corresponding GPU program implementations, as shown in Table \ref{table 1}.
+Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational consumptive operations can be performed by the CUDA Basic Linear Algebra Subprograms(cuBLAS) and corresponding GPU program implementations, as shown in table \ref{table1}.
 \begin{table}[htb]
-\caption{Parallel Computation Operation of FCSD Preprocessing}
 \centering
@@
 \hline
-  \label{table 1}
 \end{tabular}
+\caption{Parallel Computation Operation of FCSD Preprocessing}
+\label{table1}
 \end{table}
 
-Figure \ref{block diagram} shows the block diagram of the CUDA-FCSD implementation. 
+Figure \ref{block diagram} illustrates the block diagram of the CUDA-FCSD implementation. 
 \begin{figure}[htb]
@@
 \subsection{Parallel Acceleration of Blocked-Paths Searching}
-  \paragraph{}We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt[2]{N_{t}}-1\rceil$, as mentioned in section \ref{programming model} the maximum number of threads that can be used in GPU is limited by the number of SM and maximum number of threads per SM, as to GeForce GTX 760.
+  \paragraph{}We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the number of path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt[2]{N_{t}}-1\rceil$, as mentioned in section \ref{programming model} the maximum number of threads that can be used in GPU is limited by the number of SM and maximum number of threads per SM, as to GeForce GTX 760.
 we have $12288$ threads totally.
@@
 For largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads which is the maximum number of thread allowing per block.
-At each FCSD searching path, we perform the following data operation:\\
+At each FCSD searching path, the following data operation is performed in one thread:\\
 1. \emph{Decision Feedback Equalization}\\
@@
 \nonumber
-\mathbf{s}_{i}^{k}=\mathbf{\hat{s}}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\mathbf{\hat{s}}_{j}^{k}-\mathbf{s}_{j}^{k})\quad if\quad i &=& N_{t}-\rho,N_{t}-\rho-1,\dots 2,1\quad SE\quad stage\\  \label{path searching}
+{s}_{i}^{k}=\mathbb{Q}[\hat{s}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s}_{j}^{k}-s_{j}^{k})]\quad if\quad i &=& N_{t}-\rho,N_{t}-\rho-1,\dots 2,1\quad SE\quad stage\\  \label{path searching}
 \end{eqnarray}
@@
 \begin{equation}
-E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\mathbf{\hat{s}}_{j}-\mathbf{s}_{j})\label{Eu metric}
+E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s}_{j}-s_{j})\label{Eu metric}
 \end{equation}
@@
 Thus the occupancy of memory is one determinant factor needed to be considered.
-In table \ref{amount of R/W operation} we present the amount of R/W operations and the storage that needed for critical data variables in FCSD path searching.
-The amount of the R/W operation is calculated based on the (\ref{path searching}) and (\ref{Eu metric}), for complex values ($\mathbf{R}$ $\mathbf{\hat{s}}$, $\mathit{s_{pm}}$, $\mathit{s_{kernel}}$ ) are stored using CUDA build in variable data type $\mathit{cuComplex}$ which counts 8 bytes.
-Floating point data set $E_{u}$ is stored using variable type $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored using variable type $\mathit{int}$, which counts 1 byte.\\
- \paragraph{}At host side we set 4 data sets that are stored in global memory which are storage consumptive and have valid life circle for both host side and device side, $\mathit{s_{pm}}$ is a $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid life circle should be during the whole kernel execution.
+ \paragraph{}At host side we set 4 data sets that are stored in global memory which are storage consumptive and must have valid scope for both host and device side, $\mathit{s_{pm}}$ is a $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope should be during the whole $\mathit{kernel}$ execution.
 $\mathit{s_{index}}$ is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.
@@
 \\
- \paragraph{} On the other hand, upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\mathbf{\hat{s}}$ in (\ref{unconstrained estimation}), require a large amount of read operations and are read only.
-(for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\mathbf{\hat{s}}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\hat{s}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section \ref{programming model}, the constant memory is cached so that it is much faster than global memory.
+ \paragraph{} On the other hand, upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\mathbf{\hat{s}}$ in (\ref{unconstrained estimation}) are read only and require large amount of read operations.
+(for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\mathbf{\hat{s}}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\mathbf{\hat{s}}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section \ref{programming model}, the constant memory is cached so that it is much faster than global memory.
+ \paragraph{}In table \ref{amount of R/W operation} we present the amount of R/W operations and the storage that needed for different data variables in FCSD path searching.
+The amount of the R/W operation is calculated based on the (\ref{path searching}) and (\ref{Eu metric}), for complex values ($\mathbf{R}$ $\mathbf{\hat{s}}$, $\mathit{s_{pm}}$, $\mathit{s_{kernel}}$ ) are stored using CUDA build in variable data type $\mathit{cuComplex}$ which counts 8 bytes.
+Floating point data set $E_{u}$ is stored using variable type $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored using variable type $\mathit{int}$, which counts 1 byte.\\
  \begin{table}[htb]  
- \caption{Amount of R/W Operations and Storage Requirement of Different Data Set}
+ \renewcommand{\arraystretch}{1.3}
  \centering
+
 \begin{tabular}{|p{3cm}|p{3cm}|l|p{3cm}|l|l|l|}
@@
 Storage/bytes  & $4(N_{t}+1)N_{t}$ & $8N_{t}$ & $8M^{\rho}N_{t}$ & $N_{t}M^{\rho}$ & $4N_{t}M^{\rho}$ & $8N_{t}$\\
-\hline  \label{amount of R/W operation} 
+\hline
+
 \end{tabular} 
+ \label{amount of R/W operation} 
+ \caption{Amount of R/W Operations and Storage Requirement of Different Data Set}
 \end{table} 
 \subsubsection{Memory Accesss Pattern}
-  When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.\\
-  Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W data by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible, for GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Figure \ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{potential matrix}}$ as an example to illustrate how we coalesce the the global memory,
-we store $\mathit{s_{potential matrix}}$ in one pitch of linear global memory, with each row store one $N_{t}=16$ complex symbol vector solution candidate of $\hat{s}_{FCSD}$ in (\ref{formula 5}), totally there are $M^{\rho}=4096$ rows, this matrix is stored in column major.
-As mentioned before we operate one path in one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256$ bytes, counts for two times of DRAM access.
-\begin{figure}[htb]
+  \paragraph{}When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.\\
+  \paragraph{}Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W operations are performed by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible.
+For the GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Figure \ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{pm}}$ as an example to illustrate how we coalesce the the global memory.
+  \begin{figure}[tb]
 \centering
@@
 \end{figure}
+We store $\mathit{s_{pm}}$ in one pitch of linear global memory, with each row store one $N_{t}=16$ complex symbol vector solution candidate of $\mathbf{\hat{s}}^{F}$ in (\ref{formula 5}), totally there are $M^{\rho}=4096$ rows, this matrix is stored in column major.
+As mentioned before one path searching is performed by one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256$ bytes, counts for two times of DRAM access.
+
  \paragraph{}Another available resource for memory bandwidth increase is to make use of share memory, for all the transient variables that used for accumulator in (\ref{path searching}) and (\ref{Eu metric}), because of the small storage consumption and large amount of R/W operations.
 \subsubsection{Data Transfer Minimization}   
-\paragraph{}The data transfer between the host side and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the index list $\mathit{s_{index}}$ at FE stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
+\paragraph{}The data transfer between the host and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
 \subsection{Going to Larger MIMO System}
   \paragraph{}Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, the path number that need to be searched is $M^{\rho}=16^{5}=1048576$.
-The maximum number of threads that can be execute in kernel function of GeForce GTX 760 is 12288, therefore we need to consider execute the kernel function serially, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
-Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the kernel function for 86 times and get the final solution,  when it comes to the large MIMO systems and large signal constellations such as $36\times 36$ $16$QAM, $144\times 144$ $4$QAM, $20\times 20$ $64$QAM, the global memory that need to used to store $s_{pm}$ in section (\ref{data preparation}) will out of bound (2 GB), multiple kernels with each one deal with a small subset of symbol vector candidates and kernel concurrency\cite{nvidia2008programming} can be applied for solving this problem.
+The maximum number of threads that can be execute in $\mathit{kernel}$ function of the GeForce GTX 760 is 12288, therefore we need to consider execute the $\mathit{kernel}$ function in loop, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
+Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the $\mathit{kernel}$ function for 86 times and get the final solution,  when it comes to the large MIMO systems and large signal constellations such as $36\times 36$ $16$QAM, $144\times 144$ $4$QAM, $20\times 20$ $64$QAM, the global memory that need to used to store $s_{pm}$ in section (\ref{data preparation}) will out of bound (2 GB), multiple kernels with each one deal with a small subset of symbol vector candidates and kernel concurrency\cite{nvidia2008programming} can be applied to solve this problem.
 \section{Simulation Results}\label{simulation}
@@
 \emph{Central Processing Units-Modigliani}: Intel Core i5-4th generation, 4 cores 3.20 GHz CPU clock rate, 8 GB RAM\\
-\emph{Central Processing Units-Monet} : Intel Core i7-3rd generation, 12 cores 3.20 GHz CPU clock rate, 32 GB RAM\\
-\subsection{Software}
+\emph{Central Processing Units-Monet} : Intel Core i7-3rd generation, 12 cores 3.20 GHz CPU clock rate, 32 GB RAM
+\subsubsection{Software}
 CUDA Driver Version / Runtime Version      6.5 / 6.0\\
@@
 \begin{table}[htb]
-
 \centering
@@
 \cline{2-6}
-&GeForce GTX 760 & modigliani & monet &  GTX 760/modigliani  &  GTX 760/monet \\
+&GeForce GTX 760 & Modigliani & Monet &  GTX 760/Modigliani  &  GTX 760/Monet \\
 \hline
@@
 
-\begin{table}[htb]
+\begin{table}[tb]
 \centering
@@
 
-\paragraph{} We made simulation to different sizes MIMO systems and signal constellation and comparison is made between Geforce GTX 760 and two kinds of CPU, the speedup performance is presented in table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
+\paragraph{} We made simulation to different sizes MIMO systems and signal constellation and comparison is made between the Geforce GTX 760 and two kinds of CPU, the speedup performance is presented in table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
 All the operation times we test is based on $1000$ channel realizations, the transmitted data is generated randomly and modulated by $M$ quadrature amplitude modulation (QAM) scheme.
-In table \ref{speedup1}, for small MIMO systems $8\times 8$ and $16\times 16$, the speed performance of GPU implementation is even worse than that of CPU, for both antenna configurations the the number of path that need to be searched is relatively small ($16$ for $8\times 8$ system and $64$ for $16\times 16$ system), the CPU implementation has already had a good performance, there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
+\paragraph{} In table \ref{speedup1}, for small MIMO systems $8\times 8$ and $16\times 16$, the speed performance of GPU implementation is even worse than that of CPU.
+The number of path of these antenna configurations that need to be searched is relatively small ($16$ for $8\times 8$ system and $64$ for $16\times 16$ system), the CPU implementation has already had a good performance, there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
 Furthermore, for small number of threads, the memory R/W latency is not well hided.
 For the $32\times 32$ systems, the speed performance of GPU and CPU implementation is close, when comes to larger MIMO systems $48\times 48$, $64\times 64$, $72\times 72$, a large parallelism is achieved so that the GPU begin to display its data processing power, the speedup can be from $2.50$ to $4.20$.
-\paragraph{}In table \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM is considered, the speedup of GPU implementation is reached from a small MIMO size, For $16\times 16$ system using $16$QAM $1.18$ over modigliani and $1.57$ over monet.
-For $8\times 8$, $64$QAM, $0.87$ over modigliani and $1.09$ over monet.
-This is because for lager signal constellation, the massive parallelism can be reached for relatively small MIMO systems.
+\paragraph{}In table \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM are considered, the speedup of GPU implementation is reached from a small MIMO size, For $16\times 16$ system using $16$QAM $1.18$ speedup over Modigliani and $1.57$ speedup over Monet.
+For $8\times 8$, $64$QAM, $0.87$ speedup over Modigliani and $1.09$ speedup over Monet.
+For lager signal constellation, the massive parallelism can be reached for relatively small MIMO systems.
 \paragraph{}It can be observed from table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, GPU implementation shows its speed advantage over CPU implementation for increasing size of MIMO systems and signal constellations, indicating this GPU implementation's suitability for large MIMO system and large signal constellation.
-\paragraph{}Figure \ref{BER curve} shows the Monte Carlo simulation results of bit error rate per bit (BER per bit) performance for different MIMO systems and constellation sizes, we consider uncoded spatial multiplexing MIMO systems, the transmitted binary sequence is generated randomly and  mutually independent, modulated by $M$QAM modulation scheme, the results have been obtained using $100000$ channel realizations and $500$ symbol errors accumulated.
 \begin{figure}[htb]
 \centering
-\includegraphics[scale=0.7]{BER_curves.eps}
-\caption{BER performance of different sizes of MIMO systems and modulation scheme by CUDA-FCSD}
+\includegraphics[scale=0.65]{BER_curves.eps}
+\caption{BER performance of different sizes of MIMO systems and modulation scheme by GPU}
 \label{BER curve}
 \end{figure}
+\paragraph{}Figure \ref{BER curve} shows the Monte Carlo simulation results of bit error rate (BER) performance for different MIMO systems and constellation sizes, we consider uncoded spatial multiplexing MIMO systems, the transmitted binary sequence is generated randomly and  mutually independent, modulated by $M$-QAM modulation scheme, the results have been obtained using $100000$ channel realizations and $500$ symbol errors accumulated.
 \section{Conclusion}\label{conclusion}

### 2014-11-05 parallel_acceleration_of_FCSD_based_on_cuda/draft.tex
solve the crush problem and revise the report

@@
 The Fixed Complexity Sphere Decoder (FCSD) overcomes these two disadvantages of the SD decoder by searching the solution along a fixed number of independent paths\cite{barbero2008fixing}.
-\paragraph{}General purpose Graphic processing Units Computing (GPGPU) has become a common trend in industry and research in areas that need massive computations such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
+\paragraph{}General purpose Graphic processing Units Computing (GPGPU) has become a common trend in industry and research in areas that need massive computations, such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
 Compared to CPU, the GPU can naturally cope with computational intensive tasks, since most of the hardware resource are allocated for data processing and parallel computation, rather than caching and flow control.
 In recent years GPU computing has provided significant advantages in data processing speeds over CPU computations\cite{nvidia2008programming}.
-Computed unified Device Architecture (CUDA) is a programming model for GPGPU that was proposed by Nvidia and is becoming the dominant framework for GPGPU programming.
+In 2011, the NVIDIA GPUs have become the fastest supercomputer in the world\cite{cook2013cuda},  Computed unified Device Architecture (CUDA) is a programming model for GPGPU that was proposed by NIVIDIA and has become the dominant framework for GPGPU programming.
 It is based on popular programming languages(C, C++, Java, Python, Fortran, Direct Compute), such that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
@@
 The variables invoked in $\mathit{kernel}$ functions can be stored in either of the these four types of memories.
-Registers are allocated dynamically to threads.
+Registers are allocated dynamically and privately to threads, the access speed of registers is the faster than all the other four types of memories.
 \paragraph{}Because of the resource limitation of SM the total number of threads can be defined in one block is limited.
@@
 
-\paragraph{}As mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
+\paragraph{}As mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle-achieving performance with a mix of CPU and GPU technology, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
 Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational consumptive operations can be performed by the CUDA Basic Linear Algebra Subprograms(cuBLAS) and corresponding GPU program implementations, as shown in table \ref{table1}.
@@
 3. Storage occupancy\\
-\paragraph{}GPU is computation intensive and only has small cache for special memory space (texture, constant).
+\paragraph{}Unlike CPUs that have a flat memory model meaning the CPU core can access any memory location without restriction, GPUs are computation intensive and only have small cache for special memory space (texture, constant).
 Thus the memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influences the application performance.
@@
 (for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\mathbf{\hat{s}}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\mathbf{\hat{s}}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section \ref{programming model}, the constant memory is cached so that it is much faster than global memory.
- \paragraph{}In table \ref{amount of R/W operation} we present the amount of R/W operations and the storage that needed for different data variables in FCSD path searching.
+ \paragraph{}In table \ref{amountofR/Woperations}  we present the amount of R/W operations and the storage that needed for different data variables in FCSD path searching.
 The amount of the R/W operation is calculated based on the (\ref{path searching}) and (\ref{Eu metric}), for complex values ($\mathbf{R}$ $\mathbf{\hat{s}}$, $\mathit{s_{pm}}$, $\mathit{s_{kernel}}$ ) are stored using CUDA build in variable data type $\mathit{cuComplex}$ which counts 8 bytes.
@@
  \begin{table}[htb]  
- \renewcommand{\arraystretch}{1.3}
  \centering
-
 \begin{tabular}{|p{3cm}|p{3cm}|l|p{3cm}|l|l|l|}
@@
 \hline  
-
 \end{tabular} 
- \label{amount of R/W operation} 
  \caption{Amount of R/W Operations and Storage Requirement of Different Data Set}
+  \label{amountofR/Woperations} 
 \end{table}  
@@
 
- \paragraph{}Another available resource for memory bandwidth increase is to make use of share memory, for all the transient variables that used for accumulator in (\ref{path searching}) and (\ref{Eu metric}), because of the small storage consumption and large amount of R/W operations.
+ \paragraph{}As we mentioned in section (\ref{programming model}), the registers are allocated to the threads dynamically and have much faster access speed than that of global memory.
+Therefore, for all the transient data that used for accumulator in (\ref{path searching}), (\ref{Eu metric}), and the symbol vector candidate during the path searching process of each thread, are stored temporarily in registers to hide the latency of R/W of global memory.
 \subsubsection{Data Transfer Minimization}   
-\paragraph{}The data transfer between the host and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
+\paragraph{}The data transfer between the host and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage.
+Loop fusion is applied to post processing stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to reduce the iteration times per thread and avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
 \subsection{Going to Larger MIMO System}
@@
 \paragraph{} In table \ref{speedup1}, for small MIMO systems $8\times 8$ and $16\times 16$, the speed performance of GPU implementation is even worse than that of CPU.
-The number of path of these antenna configurations that need to be searched is relatively small ($16$ for $8\times 8$ system and $64$ for $16\times 16$ system), the CPU implementation has already had a good performance, there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
+The number of path of these antenna configurations that need to be searched is relatively small ($16$ for $8\times 8$ system and $64$ for $16\times 16$ system), the CPU implementation has already had a good performance, the CPUs are designed for serial code execution with the special hardwares (branch prediction units, multiple caches, etc) and have extremely good performance at it, however the GPUs can achieve a good performance only when they are utilized in parallel manner, there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
 Furthermore, for small number of threads, the memory R/W latency is not well hided.

### 2014-11-05 FCSD_GPU/src/FCSD_decoding.cu

@@ -35,8 +35,8 @@
 #include<cuda_profiler_api.h>
 #include<device_functions.h>
 #define threadNum 1024
-#define blockNum 16
-#define stride 63
+#define blockNum 1
+#define stride 0
 /*
  * in this version I applied colesced memory accesss to all the vector and matrix, with all the matrix stored in row major different threads reading one column
  * with all the matrix stored in column major, different threads reading one row
@@ -164,7 +164,6 @@ __global__ void FEpath(
 				} else if (M == 16)  //16QAM
 						{
 
-
 					d = sqrt(float(3) / (2 * (float) (Nt * (M - 1))));
 					if (s_temp.x < (-2 * d)) {
 						s_potential_matrix[IDC2D(count1,index*blockNum*threadNum+tx,pathNum)].x =
@@ -200,53 +199,57 @@ __global__ void FEpath(
 					d = sqrt(float(3) / (2 * (float) (Nt * (M - 1))));
 					//real part
 					if (s_temp.x < (-6 * d)) {
-						s_potential_matrix[IDC2D(count1,index*blockNum*threadNum+tx,pathNum)].x=(-7*d);
-					} else if (s_temp.x < (-4 * d)
-							&& s_temp.x > (-6 * d)) {
-						s_potential_matrix[IDC2D(count1,index*blockNum*threadNum+tx,pathNum)].x=(-5*d);
-					} else if (s_temp.x < (-2 * d)
-							&& s_temp.x > (-4 * d)) {
-						s_potential_matrix[IDC2D(count1,index*blockNum*threadNum+tx,pathNum)].x=(-3*d);
-					} else if (s_temp.x < (0)
-							&& s_temp.x > (-2 * d)) {
-						s_potential_matrix[IDC2D(count1,index*blockNum*threadNum+tx,pathNum)].x=(-d);
+						s_potential_matrix[IDC2D(count1,index*blockNum*threadNum+tx,pathNum)].x =
+								(-7 * d);
+					} else if (s_temp.x < (-4 * d) && s_temp.x > (-6 * d)) {
+						s_potential_matrix[IDC2D(count1,index*blockNum*threadNum+tx,pathNum)].x =
+								(-5 * d);
[…]

### 2014-11-05 FCSD_GPU_48_4/src/FCSD_decoding.cu

@@ -1,4 +1,5 @@
 /* *
+ /* *
  * Copyright 1993-2012 NVIDIA Corporation.  All rights reserved.
  *
  * Please refer to the NVIDIA end user license agreement (EULA) associated
@@ -34,6 +35,7 @@
 #include<cudaProfiler.h>
 #include<cuda_profiler_api.h>
 #include<device_functions.h>
+#include"fullfactorial.h"
 #define threadNum 1024
 #define blockNum 1
 #define stride 0
@@ -44,8 +46,6 @@
  */__constant__ cuComplex d_R[MATRIX_SIZE * MATRIX_SIZE],
 		d_psymbolconstellation[16], d_constant_shat[MATRIX_SIZE];
 __constant__ int d_list[MATRIX_SIZE];
-
-
 __global__ void FEpath(
 //		cuComplex *d_R,  //upper triangular matrix after cholesky factorization
 //		cuComplex *d_constant_shat,  //unconstrained estimation of transmitted symbol vector s
@@ -73,15 +73,11 @@ __global__ void FEpath(
 
 //allocate shared memory
 //	extern __shared__ cuComplex array[];
-	 cuComplex s_single[MATRIX_SIZE];
-	 cuComplex R_Eu_share[MATRIX_SIZE];
-	 cuComplex s_temp;
-	 cuComplex Eu_norm_share;
-	 cuComplex alpha, beta;
-	 float Eu_t;
+
 	error_t error;
 	int count1, count2, count3, count4;
 	float d; //the minimum distance unit between the signal constellation, the distance is usually 2d
+	cuComplex alpha, beta;
 	alpha.x = 1;
 	alpha.y = 0;
 	beta.x = 0;
@@ -89,13 +85,14 @@ __global__ void FEpath(
 //	__shared__ cuComplex d_constant_shat[MATRIX_SIZE];
 //	__shared__ cuComplex d_R[MATRpIX_SIZE*MATRIX_SIZE];
 //    __shared__ cuComplex s_temp[threadNum];
-
+	cuComplex s_temp;
+	cuComplex Eu_norm_share;
 //   __shared__ cuComplex Eu_norm_share[threadNum];
-
-
+	cuComplex R_Eu_share[MATRIX_SIZE];
+	cuComplex s_single[MATRIX_SIZE];
 //    cudaMemset(R_Eu_share,0,Nt*sizeof(cuComplex));
 //    __shared__ float Eu_t[threadNum];
[…]

### 2014-11-05 FCSD_GPU_48_4/src/FCSD_detection_GPU.cpp

@@ -81,21 +81,8 @@ void FCSD_detection(cuComplex *sigRec,   //received signal vector
 //	cudaProfilerStart();
 //    FCSD_ordering(pH, list, d_pH);
 	FCSD_ordering_CPU(pH, list, d_pH);
-//    cudaProfilerStop();
 	end = clock();
 	duration = double(end - start);
-//printf("hey the ordering time is:\n");
-//printf("%0.4f ", duration);
-//printf("the list of GPU is:\n");
-//for(count1=0;count1<MATRIX_SIZE;count1++)
-//{
-//	printf("%d ", list[count1]);
-//}
-//    for (count1=0;count1<Nt; count1++)
-//    {
-//    	list_temp=sigRec[list[count1]];
-//    	sigRec[Nt-1-count1]=list_temp;
-//    }
 	//cholesky factorization
 
 	//FCSD decoding
@@ -204,7 +191,6 @@ void FCSD_detection(cuComplex *sigRec,   //received signal vector
 	duration1 = double((end - start) / CLOCKS_PER_SEC);
 	gsl_matrix_complex_free(g_pR);
 	free(c_pR);
-//    	           printf("the duration of chol GPU is %0.4f:\n", duration1);
 	ret = cublasCgemm(handle, CUBLAS_OP_N, CUBLAS_OP_C, Nt, Nt, Nr, &one, d_pH,
 			Nt, d_pH, Nt, &snr, d_I, Nt);
 	if (ret != CUBLAS_STATUS_SUCCESS) {
@@ -250,7 +236,6 @@ void FCSD_detection(cuComplex *sigRec,   //received signal vector
 //    MATRIX_INVERSE(d_I,d_pW,Nr,Nt);
 	end = clock();
 	duration2 = double((end - start) / CLOCKS_PER_SEC);
-//    printf("the duration of matrix inverse GPU is %0.4f:\n", duration2);
 	ret = cublasCgemm(handle, CUBLAS_OP_C, CUBLAS_OP_N, Nt, Nt, Nr, &one, d_pH,
 			Nt, d_pW, Nt, &zero, d_pW1, Nr);
 	ret = cublasCgemv(handle, CUBLAS_OP_T, Nt, Nr, &one, d_pW1, Nr, d_sigRec, 1,
[…]

### 2014-11-05 FCSD_GPU_48_4/src/communication_line.cpp

@@ -155,7 +155,7 @@ int main(void) {
 	printf("the program for %dX%d %d QAM begin!!\n", MATRIX_SIZE,MATRIX_SIZE,M);
 	printf("the SNR per bit is:\n");
 	fprintf(cfile1,"this is the SNR %d %f\n", 2*SNRnum, SNR[SNRnum] );
-	for(count1=1;count1<=SNRnum;count1++)
+	for(count1=0;count1<=SNRnum;count1++)
 	{
 	printf("%d ", 2*count1);
 	}
@@ -225,12 +225,12 @@ int main(void) {
 			preceived = gsl_vector_complex_calloc(Nr);
 			pH = gsl_matrix_complex_calloc(Nr, Nt);
 			symOut = gsl_vector_complex_calloc(Nt);
-			ptransmitted_cu = (cuComplex*) malloc(Nt * sizeof(cuComplex));
-			psymbolconstellation_cu = (cuComplex*) malloc(
+			ptransmitted_cu = (cuComplex*) calloc(1,Nt * sizeof(cuComplex));
+			psymbolconstellation_cu = (cuComplex*) calloc(1,
 					M * sizeof(cuComplex));
-			sigRec = (cuComplex*) malloc(Nr * sizeof(cuComplex));
-			pH_cu = (cuComplex*) malloc(Nr * Nt * sizeof(cuComplex));
-			symOut_cu = (cuComplex*) malloc(Nt * sizeof(cuComplex));
+			sigRec = (cuComplex*) calloc(1,Nr * sizeof(cuComplex));
+			pH_cu = (cuComplex*) calloc(1,Nr * Nt * sizeof(cuComplex));
+			symOut_cu = (cuComplex*) calloc(1,Nt * sizeof(cuComplex));
 			//data generation and channel generation
 			data_generator(pdata, pr, M); //pdata is the indexes
 			for (count2 = 0; count2 < Nt; count2++) {
@@ -390,8 +390,9 @@ int main(void) {
 			symOut_cu = NULL;
 		} while ((symbolError < minSymbolError) || (iteration < miniteration));
 
-//		}while(iteration<1e1);
+//		}while(iteration<1e2);
 		printf("now we reach the SNR per bit point %d", 2*count);
+		printf("\n");
 		BitErrorRate = float(bitError)/float(iteration*MATRIX_SIZE*log2(M));
 		SymbolErrorRate=float(symbolError)/float(iteration*MATRIX_SIZE);
 		fprintf(cfile1, "%f ", BitErrorRate);

### 2014-11-05 FCSD_GPU_72_4/src/communication_line.cpp

@@ -198,7 +198,7 @@ int main(void) {
 	fclose(cfile3);
 	fclose(cfile4);
 	time1 = clock();
-	for (count = 0; count <=SNRnum; count++) {
+	for (count = SNRnum; count <=SNRnum; count++) {
 		iteration = 0;
 		bitError = 0;
 		symbolError = 0;
@@ -388,9 +388,9 @@ int main(void) {
 			pH_cu = NULL;
 			free(symOut_cu);
 			symOut_cu = NULL;
-		} while ((symbolError < minSymbolError) || (iteration < miniteration));
+//		} while ((symbolError < minSymbolError) || (iteration < miniteration));
 
-//		}while(iteration<1);
+		}while(iteration<1);
 		printf("now we reach the SNR per bit point %d \n", 2*count);
 		printf("\n");
 		BitErrorRate = float(bitError)/float(iteration*MATRIX_SIZE*log2(M));

### 2014-11-20 Parallel Acceleration of Fixed Complexity Sphere Decoder Based on GPU/conf_draft/conference draft.tex
conference draft 1
first conference draft, need to revise more

--- 2014-11-05 parallel_acceleration_of_FCSD_based_on_cuda/draft.tex
@@
 % draft mode.
-%
-\documentclass[12pt,a4paper,final]{article}
+\documentclass[a4paper, 10pt, conference]{IEEEconf}
+%\documentclass[12pt,a4paper,final]{article}
+%\IEEEoverridecommandlockouts
+%\overrideIEEEmargins
 %\documentclass[conference]{IEEEtrans}
@@
 % manually specify the path to it like:
-\usepackage[latin1]{inputenc}
-\usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{amsthm}
-\usepackage{fullpage}
+\usepackage{caption}
+\usepackage{multirow}
 \usepackage{setspace}
-\usepackage{graphicx}
-%\usepackage[pdftex]{graphicx}
-\usepackage{psfrag}
-\usepackage{color}
-\usepackage{epsfig}
-\usepackage{appendix}
-\usepackage{caption}
-\usepackage{cite}
-\usepackage{ifpdf}
-\usepackage[cmex10]{amsmath}
-\usepackage{algorithmic}
-\usepackage{array}
-\usepackage{stfloats}
-\usepackage{url}
-\usepackage{fixltx2e}
-\usepackage{setspace} 
-\usepackage{multirow}
-
+\usepackage{epstopdf}
 % Some very useful LaTeX packages include:
@@
 %
-%\usepackage{ifpdf}
+\usepackage{ifpdf}
 % Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
@@
 %
-%\usepackage{cite}
+\usepackage{cite}
 % cite.sty was written by Donald Arseneau
@@
   % driver is specified.
-  % \usepackage[dvips]{graphicx}
+   \usepackage[dvips]{graphicx}
   % declare the path(s) where your graphic files are
@@
 %
-%\usepackage[cmex10]{amsmath}
+\usepackage[cmex10]{amsmath}
 % A popular package from the American Mathematical Society that provides
@@
 %
-%\usepackage{algorithmic}
+\usepackage{algorithmic}
 % algorithmic.sty was written by Peter Williams and Rogerio Brito.
@@
 %
-%\usepackage{array}
+\usepackage{array}
 % Frank Mittelbach's and David Carlisle's array.sty patches and improves
@@
 %\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
+  \usepackage[caption=false,font=footnotesize]{subfig}
 %\fi
@@
 %
-% \usepackage{dblfloatfix}
+ \usepackage{dblfloatfix}
 % The latest version can be found at:
@@
 %
-%\usepackage{url}
+\usepackage{url}
 % url.sty was written by Donald Arseneau. It provides better support for
@@
 % Do not put math or special symbols in the title.
-\title{GPU Acceleration of Fixed Complexity Sphere Decoder for Large MIMO Uplink Systems}
+\title{\LARGE \bf GPU Acceleration of Fixed Complexity Sphere Decoder for Large MIMO Uplink Systems}
 
@@
 % affiliations
-%\author{\IEEEauthorblockN{Tianpei Chen}
+%\author{\IEEEauthorblockN{Tianpei Chen} and 
+%\IEEEauthorblockN{Harry Leib}}
 %\IEEEauthorblockA{ID: 25504946\\Department of Electrical and\\Computer Engineering\\
@@
 %Montreal, Quebec}}
-\author{Tianpei Chen, Harry Leib\\
- Department of Electrical and Computer Engineering\\
- McGill University\\
- Montreal, Quebec}
+\author{Tianpei Chen and Harry Leib}
+ %Department of Electrical and Computer Engineering\\
+ %McGill University\\
+% Montreal, Quebec}
 
@@
 
+%\author{\IEEEauthorblockN{Tianpei Chen and
+%Harry Leib
+%}
+%\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
+%McGill University, Montreal, Quebec, Canada}}
+
 % use for special paper notices
@@
 % make the title area
-\begin{spacing}{2.5}
+%\begin{spacing}{2.5}
 \date{}
 \maketitle
-
+\thispagestyle{empty}
+\pagestyle{empty}
 % As a general rule, do not put math, special symbols or citations
@@
 Large MIMO constitutes a principal techniques for next generation wireless communication systems.
-Detection algorithms for large MIMO tend to require long simulation times on conventional computer systems, In order to reduce the simulation times for decoders of large MIMO systems, we propose to use General Purpose Graphic Processing Units (GPGPU).
+Detection algorithms for large MIMO tend to require long simulation times on conventional computer systems, in order to reduce the simulation times for decoders of large MIMO systems, we propose to use General Purpose Graphic Processing Units (GPGPU).
 In this paper Fixed Complexity Sphere Decoder (FCSD) is implemented for the large scale MIMO system based on the dominant framework of GPGPU-Computed Unified Device Architecture (CUDA).
 The proposed CUDA-FCSD can achieve considerable speedup over conventional CPU implementation while reaching the same Bit Error Rate (BER) performance.
-Furthermore the proposed algorithm demonstrates great potential to accelerate large MIMO systems.
+Furthermore the proposed algorithm demonstrates great potential to accelerate large MIMO systems.\\
+\textbf{ Keywords: Large MIMO, FCSD, GPGPU, CUDA}
 \end{abstract}
@@
 \section{Introduction}
- \paragraph{} The present challenge in the wireless communication area is the sharp contrast between the increasing demand of mobile network speed for the transmission of rich media content with better QoS (quality of service), and the shortage of radio frequency spectrum.
+The present challenge in the wireless communication area is the sharp contrast between the increasing demand of mobile network speed for the transmission of rich media content with better QoS (Quality of Service), and the shortage of radio frequency spectrum.
 Multiple Input Multiple Output (MIMO) is thought to be a very promising technology that can help to solve this problem owing to several advantages it can offer.
@@
 For example the LTE standard supports up to 8 antennas at the base station\cite{dahlman20103g}.
- \paragraph{} Large scale MIMO (also named massive MIMO) systems employ hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}.
+
+Large scale MIMO (also named massive MIMO) systems employ hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}.
 This technology originated from multiuser MIMO (MU-MIMO) systems\cite{larsson2013massive}.
-Large scale MIMO will inherit and enhance all the advantages of conventional MIMO (spatial diversity gain and spatial multiplexing gain), as well as reduction of latency and improvement of system robustness.
- A common detector for MIMO system is the Sphere Decoder (SD) that perform as well as a Maximum Likelihood detector (MLD) with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}.
+Large scale MIMO will achieve the full potential of conventional MIMO systems (spatial diversity gain and spatial multiplexing gain), as well as provide additional reduction of latency and improvement of system robustness.
+Detector is one of the key component of MIMO systems,
+ a well known detector for MIMO system is the Sphere Decoder (SD) that perform as well as a Maximum Likelihood detector (MLD) with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}.
 There are two major problems with the traditional SD decoder: complexity depending on Signal to Noise Ratio (SNR), and sequential nature, which are contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system.
 The Fixed Complexity Sphere Decoder (FCSD) overcomes these two disadvantages of the SD decoder by searching the solution along a fixed number of independent paths\cite{barbero2008fixing}.
-\paragraph{}General purpose Graphic processing Units Computing (GPGPU) has become a common trend in industry and research in areas that need massive computations, such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
+
+General purpose Graphic processing Units Computing (GPGPU) has become a common trend in industry and research in areas that need massive computations, such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
 Compared to CPU, the GPU can naturally cope with computational intensive tasks, since most of the hardware resource are allocated for data processing and parallel computation, rather than caching and flow control.
@@
 CUDA employs the Single Instruction Multiple Threads (SIMT) programming model, enables a GPU to implement parallel data processing, and has become a parallel computing platform for wide community of different applications.
-\paragraph{}In this paper, a GPU based implementation of Fixed Complexity Sphere Decoder is proposed, A heterogeneous programming solution for FCSD preprocessing and blocked parallel path searching solution are presented, the speedup as well as Bit Error Rate (BER) performance of different sizes of MIMO systems and signal constellations are presented and analyzed, The proposed CUDA-FCSD implementation demonstrates a great potential for large MIMO systems.
-\paragraph{}The rest of the paper is organized as follows.
+
+In this paper, a GPU based implementation of Fixed Complexity Sphere Decoder is proposed, which is referred to as CUDA-FCSD.
+A heterogeneous programming solution for FCSD preprocessing and integrated blocked parallel path searching and decision maker solution are presented, the speedup as well as Bit Error Rate (BER) performance of different sizes of MIMO systems and signal constellations are presented and analyzed.
+The proposed CUDA-FCSD implementation demonstrates a great potential for large MIMO systems.
+
+The rest of the paper is organized as follows.
 Section \ref{system} describes the MIMO systems model.
-Section \ref{programming model} introduces CUDA GPU architecture and the programming model.
+Section \ref{programming model} introduces CUDA, GPU architecture and the programming model.
 In section \ref{GPUFCSD}, we present details of the implementation of CUDA-FCSD.
@@
 Finally conclusions are drawn in section \ref{conclusion}.
-\section{MIMO System Model}\label{system}
-% no \IEEEPARstart
-%This demo file is intended to serve as a ``starter file''
-%for IEEE conference papers produced under \LaTeX\ using
-%IEEEtran.cls version 1.8 and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-%I wish you the best of success.
-%\hfill mds
-%\hfill December 27, 2012
-\paragraph{}We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel, corresponding to the discrete time model:
-\begin{equation}
-\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n}   \label{formula 1}
-\end{equation}
-$\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from the signal constellation $\mathbb{O}$ (4-QAM, 16-QAM, 64-QAM), of size $M$.
-The transmitted symbol vectors forms a $N_{t}$ complex signal vector space $\mathbb{O}^{N_{t}}$.
-$\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
-Furthermore,  $\mathbf{y}\in \mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean components of unit variance, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise power spectrum density and $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR).
-\\
-
-\paragraph{} Assume we have the perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known at the receiver, as well as the SNR.
-The task of MIMO decoder is to estimate $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
-
 % An example of a floating figure using the graphicx package.
@@
 \subsection{Memory Hierarchy}  
-\paragraph{}CUDA programming model is a C programming extension, with special defined syntax and structure.
+CUDA programming model is a C programming extension, with special defined syntax and structure.
 The serial code is executed on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side, this is defined as a heterogeneous programming model.
-A thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share one pitch of on chip memory (shared memory), all the threads executed in one block can synchronize their action meaning the threads are permitted to run to the next instruction only when all the threads have reached the same instruction node.
+A thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share one pitch of on chip memory (shared memory), all the threads executed in one block can synchronize their action meaning the threads are permitted to execute the next instruction only when all the threads have reached the same instruction node.
 Blocks can be grouped into a one-dimensional, two-dimensional, or three-dimensional grid.
 Similarly, The threads can also be organized into one-dimensional, two-dimensional or three-dimensional blocks.
-The organization of the block and grid shape and dimension is determined by the application, Figure \ref{figure1} illustrates the 3 dimensional thread hierarchy of CUDA.
+The organization of the block and grid shape and dimension is determined by the application, Figure \ref{figure1}  simply illustrates the three dimensional thread hierarchy of CUDA.
 \begin{figure}[htb]
 \centering
-\includegraphics[scale=0.7]{CUDA_programming_hierachy.eps}
+\includegraphics[width=0.5\textwidth]{CUDA_programming_hierachy.eps}
 \caption{CUDA 3D thread hierachy\\ $5\times 5\times 5$ grid and each block contains $5\times 5\times 5$ threads\\}
@@
 \subsection{Single Instruction Multiple Thread (SIMT) Model} 
-\paragraph{}Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT) model.
+Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT) model.
 This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branch the behavior of each threads to achieve thread-level parallelism.
@@
 \subsection{Mircroarchitecture of GPU} 
-\paragraph{}In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
+In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
 The GPU works as a coprocessor system, consisting of Stream Multiprocessors (SM).
@@
 Constant memory is read only and with latency approximately as small as the registers.
-The variables invoked in $\mathit{kernel}$ functions can be stored in either of the these four types of memories.
 Registers are allocated dynamically and privately to threads, the access speed of registers is the faster than all the other four types of memories.
-\paragraph{}Because of the resource limitation of SM the total number of threads can be defined in one block is limited.
+The variables invoked in $\mathit{kernel}$ functions can be stored in either of the these five types of memories.
+
+Because of the resource limitation of SM the total number of threads can be defined in one block is limited.
 On current CUDA supported GPUs, one block can contains up to 1024 threads, and all the blocks are executed on SM.
 Thus the total number of threads ($T_{total}$) we can make use of is $T_{total}=N_{SM}\times N_{threads/SM} $, $N_{SM}$ and $N_{threads/SM}$ denote the number of SM and number of threads per SM.
-The GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$.
-In concrete applications, the programmer can allocate more than 12288 threads for a kernel, but the threads will work in serial, which will influence the program performance.
+For example the GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$.
 \begin{figure}[htb]
 \centering
-\includegraphics[scale=0.6]{High_view_of_CUDA_GPU_microarchitecture.eps}
+\includegraphics[width=0.5\textwidth]{High_view_of_CUDA_GPU_microarchitecture.eps}
 \caption{High View of CUDA CPU Microarchitecture}
@@
 \section{GPU Based Acceleration of FCSD}\label{GPUFCSD}
-\paragraph{}In this section we present the parallel implementation of fixed complexity sphere decoder using GPU, From (\ref{formula 1}), the maximum likelihood detector (MLD) for a MIMO system is specified by:
+\subsection{MIMO System Model}\label{system}
+% no \IEEEPARstart
+%This demo file is intended to serve as a ``starter file''
+%for IEEE conference papers produced under \LaTeX\ using
+%IEEEtran.cls version 1.8 and later.
+% You must have at least 2 lines in the paragraph with the drop letter
+% (should never be an issue)
+%I wish you the best of success.
+%\hfill mds
+%\hfill December 27, 2012
+
+We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel, corresponding to the discrete time model, the $\mathbb{y}\in\mathbb{C}^{N_{r}\times 1}$ received symbol vecot can be written as:
+\begin{equation}
+\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n}   \label{formula 1}
+\end{equation}
+$\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from the signal constellation $\mathbb{O}$ (4-QAM, 16-QAM, 64-QAM), of size $M$.
+All the possible transmitted symbol vectors forms a $N_{t}$ complex signal vector space $\mathbb{O}^{N_{t}}$.
+$\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
+$\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean components of unit variance, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise power spectrum density and $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR).
+
+Assume we have the perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known at the receiver, as well as the SNR.
+The task of MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
+\subsection{Fixed Complexity Sphere Decoder}
+From (\ref{formula 1}), the maximum likelihood detector (MLD) for a MIMO system is specified by:
 \begin{equation}
@@
 \end{equation}
-\paragraph{}Just like SD the FCSD also performs depth first searching, at the first $\rho$ node levels the FCSD search all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) stage, therefore for the symbol nodes $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$, the FCSD has $M$ branches expansion at each symbol node,  as shown in Figure \ref{figure4}, there are $\rho=2$ FE nodes and each node level has $M=4$ branches.
-(\ref{formula 4}) can be written in the form:
+
+Just like SD the FCSD also performs depth first searching, at the first $\rho$ node levels (\cite{barbero2008fixing} shows when $N_{r}=N_{t}$ the FCSD can achieve the same diversity as the MLD if $\rho\geq \sqrt{N_{t}}-1$) the FCSD search all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) stage, therefore for the symbol nodes $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$, the FCSD has $M$ branches expansion at each symbol node,  as shown in Figure \ref{figure4}, there are $\rho=2$ FE node levels and each node level has $M=4$ branches.
+According to (\ref{formula 4}), we have:
 \begin{equation}
@@
 \centering
-\includegraphics[scale=0.8]{FCSD_tree_searching.eps}
+\includegraphics[width=0.5\textwidth]{FCSD_tree_searching.eps}
 \caption{Tree searching of 4-QAM FCSD for 8x8 MIMO system}
@@
 \end{array}\right.
+\label{FCSD solution}
 \end{displaymath}
 $\mathbb{Q}[\cdot]$ denotes the signal constellation quantization.
-At the post processing stage, FCSD compares the Euclidean distance of all the symbol vector candidates $E_{metric}$, which, according to \ref{formula 2}, can be written as:
+At the post processing stage, FCSD compares the Euclidean distance of all the symbol vector candidates $E_{metric}$, which can be written as:
 \begin{equation}
@@
 \subsection{CUDA-FCSD Preprossing}
-\paragraph{}As shown in Figure \ref{figure4}, each path of the FCSD searching has a serial execution nature.
-In order to avoid error propagation, FCSD ordering was applied to the propagation channel based on post processing signal to noise ratio\cite{wolniansky1998v}:
+As shown in Figure \ref{figure4}, a FCSD channel ordering strategy to avoid error propagation in serial path searching process is presented in \ref{barbero2008fixing}, this channel ordering strategy is based on post processing signal to noise ratio\cite{wolniansky1998v}:
 \begin{equation}
@@
 
-\paragraph{}As mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle-achieving performance with a mix of CPU and GPU technology, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
-Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational consumptive operations can be performed by the CUDA Basic Linear Algebra Subprograms(cuBLAS) and corresponding GPU program implementations, as shown in table \ref{table1}.
-\begin{table}[htb]
+As mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle-achieving performance with a mix of CPU and GPU technology, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
+Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational consumptive operations can be performed by the CUDA Basic Linear Algebra Subprograms(cuBLAS)\cite{nvidia2013basic} and corresponding GPU program implementations, as shown in table \ref{table1}.
+\begin{table*}[htb]
 \centering
@@
 \hline
-Formula   &  $\mathbf{H}^{H}\mathbf{H}$ & $(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y$ & $\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1} $ & $\mathbf{H}^{H}\mathbf{H}=\mathbf{R}^{H}\mathbf{R}$ 
+Formula   &  $\mathbf{H}^{H}\mathbf{H}$ & $(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y$ & $(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1} $ & $\mathbf{H}^{H}\mathbf{H}=\mathbf{R}^{H}\mathbf{R}$ 
 \\
@@
 \label{table1}
-\end{table}
+\end{table*}
 
@@
 \centering
-\includegraphics[width=0.85\textwidth]{CUDA_FCSD_block_diagram.eps}
+\includegraphics[width=0.5\textwidth]{CUDA_FCSD_block_diagram.eps}
 \caption{Block Diagram of CUDA-FCSD Implementation}
@@
 \subsection{Parallel Acceleration of Blocked-Paths Searching}
-  \paragraph{}We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the number of path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt[2]{N_{t}}-1\rceil$, as mentioned in section \ref{programming model} the maximum number of threads that can be used in GPU is limited by the number of SM and maximum number of threads per SM, as to GeForce GTX 760.
-we have $12288$ threads totally.
 The decision feedback searching paths have serial nature, we match one path to one thread.
 In order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks.
-For largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads which is the maximum number of thread allowing per block.
+For example We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the number of path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt{N_{t}}-1\rceil$, where $\lceil x\rceil$ represent the smallest integer larger than $x$, for largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads which is the maximum number of thread allowing per block.
 At each FCSD searching path, the following data operation is performed in one thread:\\
-1. \emph{Decision Feedback Equalization}\\
-\begin{eqnarray}
-\nonumber
-{s}_{i}^{k}\in \mathbb{O}^{\rho}      \quad if\quad i&=&N_{t},N_{t}-1,\dots N_{t}-\rho+1\quad FE \quad stage\\
-\nonumber
-{s}_{i}^{k}=\mathbb{Q}[\hat{s}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s}_{j}^{k}-s_{j}^{k})]\quad if\quad i &=& N_{t}-\rho,N_{t}-\rho-1,\dots 2,1\quad SE\quad stage\\  \label{path searching}
-\end{eqnarray}
-$\mathbf{s}_{j}^{k}$ denotes the $j$th symbol of the $k$th symbol vector candidate.\\
+1. \emph{Path searching}\\
+According to (\ref{FCSD solution}).
 2. \emph{Euclidean distance Calculation}\\
@@
 \end{equation}
-$E_{u}^{k}$ denotes the $k$th Euclidean distance of the corresponding symbol vector candidate. The symbol vector candidate with minimum Euclidean distance is chosen as the solution.  
+$E_{u}^{k}$ denotes the $k$th Euclidean distance of the corresponding symbol vector candidate.
+Loop fusion is applied, we integrate the post processing (\ref{Eu metric}) into path searching process (\ref{FCSD solution}) to reduce the iteration times per thread.
 \subsubsection{Data Preparation}\label{data preparation}
-\paragraph{}There are three major factors that will influence the configuration of the data sets configuration in memory space.\\
+There are three major factors that will influence the configuration of the data sets configuration in memory space.\\
 1. Amount of Reading$\&$Writing (R/W) operation per thread.\\
 2. Valid scope\\
-3. Storage occupancy\\
-\paragraph{}Unlike CPUs that have a flat memory model meaning the CPU core can access any memory location without restriction, GPUs are computation intensive and only have small cache for special memory space (texture, constant).
+3. Storage occupancy
+
+Unlike CPUs that have a flat memory model meaning the CPU core can access any memory location without restriction, GPUs are computation intensive and only have small cache for special memory space (texture, constant).
 Thus the memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influences the application performance.
@@
 Thus the occupancy of memory is one determinant factor needed to be considered.
- \paragraph{}At host side we set 4 data sets that are stored in global memory which are storage consumptive and must have valid scope for both host and device side, $\mathit{s_{pm}}$ is a $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope should be during the whole $\mathit{kernel}$ execution.
+
+At host side we set 4 data sets that are stored in global memory which are storage consumptive and must have valid scope for both host and device side, $\mathit{s_{pm}}$ is a $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope should be during the whole $\mathit{kernel}$ execution.
 $\mathit{s_{index}}$ is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.
@@
 $\mathit{s_{kernel}}$ is a complex vector used to store the FCSD solution which length is $N_{t}$ and has to be transferred to host side.
-\\
- \paragraph{} On the other hand, upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\mathbf{\hat{s}}$ in (\ref{unconstrained estimation}) are read only and require large amount of read operations.
+
+On the other hand, upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\mathbf{\hat{s}}$ in (\ref{unconstrained estimation}) are read only and require large amount of read operations.
 (for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\mathbf{\hat{s}}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\mathbf{\hat{s}}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section \ref{programming model}, the constant memory is cached so that it is much faster than global memory.
- \paragraph{}In table \ref{amountofR/Woperations}  we present the amount of R/W operations and the storage that needed for different data variables in FCSD path searching.
+
+In table \ref{amountofR/Woperations}  we present the amount of R/W operations and the storage that needed for different data variables in FCSD path searching.
 The amount of the R/W operation is calculated based on the (\ref{path searching}) and (\ref{Eu metric}), for complex values ($\mathbf{R}$ $\mathbf{\hat{s}}$, $\mathit{s_{pm}}$, $\mathit{s_{kernel}}$ ) are stored using CUDA build in variable data type $\mathit{cuComplex}$ which counts 8 bytes.
 Floating point data set $E_{u}$ is stored using variable type $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored using variable type $\mathit{int}$, which counts 1 byte.\\
- \begin{table}[htb]  
+ \begin{table*}[htb]  
  \centering
-\begin{tabular}{|p{3cm}|p{3cm}|l|p{3cm}|l|l|l|}
+\begin{tabular}{|l|l|l|l|l|l|l|}
 \hline
@@
   \label{amountofR/Woperations} 
-\end{table}  
+\end{table*}  
 \subsubsection{Memory Accesss Pattern}
-  \paragraph{}When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.\\
-  \paragraph{}Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W operations are performed by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible.
+When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.
+
+Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W operations are performed by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible.
 For the GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Figure \ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{pm}}$ as an example to illustrate how we coalesce the the global memory.
-  \begin{figure}[tb]
+  \begin{figure}[htb]
 \centering
-\includegraphics[scale=0.63]{coalescing_global_memory.eps}
+\includegraphics[width=0.5\textwidth]{coalescing_global_memory.eps}
 \caption{Global Memory Access Pattern of $\mathit{s_{pm}}$}
@@
 
- \paragraph{}As we mentioned in section (\ref{programming model}), the registers are allocated to the threads dynamically and have much faster access speed than that of global memory.
+As we mentioned in section (\ref{programming model}), the registers are allocated to the threads dynamically and have much faster access speed than that of global memory.
 Therefore, for all the transient data that used for accumulator in (\ref{path searching}), (\ref{Eu metric}), and the symbol vector candidate during the path searching process of each thread, are stored temporarily in registers to hide the latency of R/W of global memory.
 \subsubsection{Data Transfer Minimization}   
-\paragraph{}The data transfer between the host and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage.
-Loop fusion is applied to post processing stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to reduce the iteration times per thread and avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
-\subsection{Going to Larger MIMO System}
-  \paragraph{}Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, the path number that need to be searched is $M^{\rho}=16^{5}=1048576$.
+The data transfer between the host and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage.
+\subsection{Larger MIMO Systems and Constellation Sizes}
+Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, the path number that need to be searched is $M^{\rho}=16^{5}=1048576$.
 The maximum number of threads that can be execute in $\mathit{kernel}$ function of the GeForce GTX 760 is 12288, therefore we need to consider execute the $\mathit{kernel}$ function in loop, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
@@
 \subsection{Performance and Evaluation}
-\begin{table}[htb]
+\begin{table*}[htb]
 \centering
@@
 \hline
-$8\times 8$& 1.88& 0.10&0.11 & 0.05& 0.06\\
+$8\times 8$& 7.39& 0.10&0.11 & 0.01& 0.01\\
 \hline
-$16\times 16$&6.12 & 0.92&0.98& 0.15& 0.16\\
+$16\times 16$&16.26 & 0.92&0.98& 0.06& 0.06\\
 \hline
@@
 \hline
-$48\times 48$&113.80& 262.00& 285.14& 2.30& 2.51\\
+$48\times 48$&71.95& 262.00& 285.14& 3.64& 3.96\\
 \hline
-$64\times 64$& 537.41&1753.30&1940.10&3.26& 3.61 \\
+$64\times 64$& 322.90&1753.30&1940.10&5.43& 6.01 \\
 \hline
-$72\times 72 $&2294.32&8727.69 &9641.80 &3.80 &4.20 \\
+$72\times 72 $&1285.41&8727.69 &9641.80 &6.79 &7.50 \\
+\hline
+$84\times 84$ &6454.02&47095.33&49962.01&7.30&7.74\\
 \hline
@@
 \label{speedup1}
-\end{table}
-
-\begin{table}[htb]
+\end{table*}
+\begin{table*}[htb]
 \centering
@@
 \hline
-$8\times 8$&2.60& 0.67&0.93 & 0.26&0.36 \\
+$8\times 8$&13.20& 0.67&0.93 & 0.05&0.07\\
 \hline
@@
 \hline
-$20\times 20$&478.40 & 740.50& 978.26& 1.55& 2.04\\
+$20\times 20$&192.70 & 740.50& 978.26& 3.84& 5.08\\
 \hline
-$32\times 32$&12330.05& 28209.53& 38106.00& 2.29& 3.09\\
+$32\times 32$&4980.13& 28209.53& 38106.00& 5.66& 7.65\\
 \hline
-$36\times 36$& 13480.01&35240.16&47290.00&2.61& 3.51 \\
+$36\times 36$& 5568.26&35240.16&47290.00&6.33& 8.61 \\
 \hline
@@
 \label{speedup2}
-\end{table}
-
-\begin{table}[tb]
+\end{table*}
+\begin{table*}[h]
 \centering
@@
 \hline
-$16\times 16$&1460.11 & 2066.08&2689.00& 1.42& 1.84\\
+$16\times 16$&468.92 & 2066.08&2689.00& 4.41& 5.73\\
 
@@
 \label{speedup3}
-\end{table}
+\end{table*}
 
-\paragraph{} We made simulation to different sizes MIMO systems and signal constellation and comparison is made between the Geforce GTX 760 and two kinds of CPU, the speedup performance is presented in table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
+We made simulation to different sizes MIMO systems and signal constellation and comparison is made between the Geforce GTX 760 and two kinds of CPU, the speedup performance is presented in table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
 All the operation times we test is based on $1000$ channel realizations, the transmitted data is generated randomly and modulated by $M$ quadrature amplitude modulation (QAM) scheme.
-\paragraph{} In table \ref{speedup1}, for small MIMO systems $8\times 8$ and $16\times 16$, the speed performance of GPU implementation is even worse than that of CPU.
+
+In table \ref{speedup1}, for small MIMO systems $8\times 8$ and $16\times 16$, the speed performance of GPU implementation is even worse than that of CPU.
 The number of path of these antenna configurations that need to be searched is relatively small ($16$ for $8\times 8$ system and $64$ for $16\times 16$ system), the CPU implementation has already had a good performance, the CPUs are designed for serial code execution with the special hardwares (branch prediction units, multiple caches, etc) and have extremely good performance at it, however the GPUs can achieve a good performance only when they are utilized in parallel manner, there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
@@
 For the $32\times 32$ systems, the speed performance of GPU and CPU implementation is close, when comes to larger MIMO systems $48\times 48$, $64\times 64$, $72\times 72$, a large parallelism is achieved so that the GPU begin to display its data processing power, the speedup can be from $2.50$ to $4.20$.
-\paragraph{}In table \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM are considered, the speedup of GPU implementation is reached from a small MIMO size, For $16\times 16$ system using $16$QAM $1.18$ speedup over Modigliani and $1.57$ speedup over Monet.
+
+In table \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM are considered, the speedup of GPU implementation is reached from a small MIMO size, For $16\times 16$ system using $16$QAM $1.18$ speedup over Modigliani and $1.57$ speedup over Monet.
 For $8\times 8$, $64$QAM, $0.87$ speedup over Modigliani and $1.09$ speedup over Monet.
 For lager signal constellation, the massive parallelism can be reached for relatively small MIMO systems.
-\paragraph{}It can be observed from table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, GPU implementation shows its speed advantage over CPU implementation for increasing size of MIMO systems and signal constellations, indicating this GPU implementation's suitability for large MIMO system and large signal constellation.
-\begin{figure}[htb]
+
+It can be observed from table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, GPU implementation shows its speed advantage over CPU implementation for increasing size of MIMO systems and signal constellations, indicating this GPU implementation's suitability for large MIMO system and large signal constellation.
+\begin{figure}[h]
 \centering
-\includegraphics[scale=0.65]{BER_curves.eps}
+\includegraphics[width=0.5\textwidth]{BER_curves.eps}
 \caption{BER performance of different sizes of MIMO systems and modulation scheme by GPU}
@@
 \end{figure}
-\paragraph{}Figure \ref{BER curve} shows the Monte Carlo simulation results of bit error rate (BER) performance for different MIMO systems and constellation sizes, we consider uncoded spatial multiplexing MIMO systems, the transmitted binary sequence is generated randomly and  mutually independent, modulated by $M$-QAM modulation scheme, the results have been obtained using $100000$ channel realizations and $500$ symbol errors accumulated.
+Figure \ref{BER curve} shows the Monte Carlo simulation results of bit error rate (BER) performance for different MIMO systems and constellation sizes, we consider uncoded spatial multiplexing MIMO systems, the transmitted binary sequence is generated randomly and  mutually independent, modulated by $M$-QAM modulation scheme, the results have been obtained using $100000$ channel realizations and $500$ symbol errors accumulated.
 \section{Conclusion}\label{conclusion}
-\paragraph{}This paper presents the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional computation platform.
+This paper presents the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional computation platform.
 In order to exploit the computational capability of GPU in the simulation of large MIMO systems, the utilization of heterogeneous programming model, thread resource limitation and memory configuration are considered in a comprehensive way.
@@
 The future work contains taking into consider the kernel execution and data transferring concurrence in order to optimize memory allocation strategy for large MIMO systems.
-\newpage
 % conference papers do not normally have an appendix
@@
 % that's all folks
-\end{spacing}
+%\end{spacing}
 \bibliographystyle{IEEEtran}
-\bibliography{citation}
+\bibliography{citation_conf}
 \end{document}

### 2014-11-23 FCSD_GPU_tex/conference draft.tex
conference draft 2

--- 2014-11-20 Parallel Acceleration of Fixed Complexity Sphere Decoder Based on GPU/conf_draft/conference draft.tex
@@
 % draft mode.
-\documentclass[a4paper, 10pt, conference]{IEEEconf}
+\documentclass[a4paper, 10pt, conference]{ieeeconf}
+%\documentclass[letterpaper, 10pt, conference]{ieeeconf}
 %\documentclass[12pt,a4paper,final]{article}
@@
 \usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{caption}
+%\usepackage{amsthm}
+%\usepackage{caption}
 \usepackage{multirow}
@@
 \usepackage{epstopdf}
+%\usepackage{graphics} % for pdf, bitmapped graphics files
+%\usepackage{epsfig} % for postscript graphics files
+\usepackage{mathptmx} % assumes new font selection scheme installed
+%\usepackage{times} % assumes new font selection scheme installed
+%\usepackage{amsmath} % assumes amsmath package installed
+\usepackage{amssymb}  % assumes amsmath package installed
 % Some very useful LaTeX packages include:
@@
 %
- \usepackage{dblfloatfix}
+% \usepackage{dblfloatfix}
 % The latest version can be found at:
@@
 Large MIMO constitutes a principal techniques for next generation wireless communication systems.
-Detection algorithms for large MIMO tend to require long simulation times on conventional computer systems, in order to reduce the simulation times for decoders of large MIMO systems, we propose to use General Purpose Graphic Processing Units (GPGPU).
+Detection algorithms for large MIMO tend to require long simulation times on conventional computer systems, in order to improve simulation efficiency for the decoders of large MIMO systems, we propose to use General Purpose Graphic Processing Units (GPGPU).
 In this paper Fixed Complexity Sphere Decoder (FCSD) is implemented for the large scale MIMO system based on the dominant framework of GPGPU-Computed Unified Device Architecture (CUDA).
 The proposed CUDA-FCSD can achieve considerable speedup over conventional CPU implementation while reaching the same Bit Error Rate (BER) performance.
-Furthermore the proposed algorithm demonstrates great potential to accelerate large MIMO systems.\\
+Furthermore the proposed algorithm demonstrates great potential to accelerate large MIMO systems.
+
 \textbf{ Keywords: Large MIMO, FCSD, GPGPU, CUDA}
@@
 The present challenge in the wireless communication area is the sharp contrast between the increasing demand of mobile network speed for the transmission of rich media content with better QoS (Quality of Service), and the shortage of radio frequency spectrum.
-Multiple Input Multiple Output (MIMO) is thought to be a very promising technology that can help to solve this problem owing to several advantages it can offer.
-The core idea of MIMO is to use multiple antennas that at the transmitting and receiving sides, that provide parallel data pipes in space resulting in spatial multiplexing gains\cite{oestges2010mimo}.
-For example the LTE standard supports up to 8 antennas at the base station\cite{dahlman20103g}.
+Multiple Input Multiple Output (MIMO) is of immense research interest that can help to solve this problem owing to several advantages it can offer.
+The core idea of MIMO is to use multiple antennas that at the transmitting and receiving sides, that provide parallel data pipes in space resulting in spatial multiplexing and spatial diversity gains\cite{oestges2010mimo}.
 
-Large scale MIMO (also named massive MIMO) systems employ hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}.
+Large scale MIMO (also named massive MIMO) systems employ tens to hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}.
 This technology originated from multiuser MIMO (MU-MIMO) systems\cite{larsson2013massive}.
-Large scale MIMO will achieve the full potential of conventional MIMO systems (spatial diversity gain and spatial multiplexing gain), as well as provide additional reduction of latency and improvement of system robustness.
+Large scale MIMO can achieve the full potential of conventional MIMO systems, as well as provide additional reduction of latency and improvement of system robustness.
 Detector is one of the key component of MIMO systems,
@@
 General purpose Graphic processing Units Computing (GPGPU) has become a common trend in industry and research in areas that need massive computations, such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
-Compared to CPU, the GPU can naturally cope with computational intensive tasks, since most of the hardware resource are allocated for data processing and parallel computation, rather than caching and flow control.
+Compared to CPU, the GPU can naturally cope with computational intensive tasks, since most of the hardware resource are allocated for data processing and parallel computation, rather than caching and flow control\cite{cook2013cuda}.
 In recent years GPU computing has provided significant advantages in data processing speeds over CPU computations\cite{nvidia2008programming}.
@@
 The rest of the paper is organized as follows.
-Section \ref{system} describes the MIMO systems model.
-Section \ref{programming model} introduces CUDA, GPU architecture and the programming model.
+Section \ref{programming model} briefly introduces CUDA, GPU architecture and the programming model.
 In section \ref{GPUFCSD}, we present details of the implementation of CUDA-FCSD.
@@
 
-\section{CUDA GPU Architecture and  Programming Model} \label{programming model}
-\subsection{Memory Hierarchy}  
+\section{CUDA Programming Model and GPU Architecture} \label{programming model} 
+\subsection{Single Instruction Multiple Thread (SIMT) Model}
 CUDA programming model is a C programming extension, with special defined syntax and structure.
 The serial code is executed on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side, this is defined as a heterogeneous programming model.
-A thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share one pitch of on chip memory (shared memory), all the threads executed in one block can synchronize their action meaning the threads are permitted to execute the next instruction only when all the threads have reached the same instruction node.
-Blocks can be grouped into a one-dimensional, two-dimensional, or three-dimensional grid.
-Similarly, The threads can also be organized into one-dimensional, two-dimensional or three-dimensional blocks.
-The organization of the block and grid shape and dimension is determined by the application, Figure \ref{figure1}  simply illustrates the three dimensional thread hierarchy of CUDA.
+A thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, the threads in one block can synchronize their behavior and communicate.
+Fig.
+\ref{figure1} simply illustrate CUDA memory hierachy model.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{CUDA_programming_hierachy.eps}
-\caption{CUDA 3D thread hierachy\\ $5\times 5\times 5$ grid and each block contains $5\times 5\times 5$ threads\\}
+\includegraphics[width=0.45\textwidth]{CUDA_programming_hierachy.eps}
+\caption{ CUDA 3D memory hierachy $5\times 5\times 5$ grid and each block contains $5\times 5\times 5$ threads
+\small  The threads can be organized into one-dimensional, two-dimensional or three-dimensional blocks.
+Similarly, blocks can also be grouped into a one-dimensional, two-dimensional, or three-dimensional grid.
+}
 \label{figure1}
@@
 
-\subsection{Single Instruction Multiple Thread (SIMT) Model} 
 Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT) model.
@@
 \subsection{Mircroarchitecture of GPU} 
-In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
-The GPU works as a coprocessor system, consisting of Stream Multiprocessors (SM).
-The GeForce GTX 760 has 6 SM that perform the multiply-add arithmetic operation.
+In Fig.
+\ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
+The GPU works as a coprocessor system, consisting of Stream Multiprocessors (SM), which perform the multiply-add arithmetic operation.
 Furthermore, each SM has the special functional units(SFU) that can perform more complex arithmetics such as trigonometric functions and reciprocal square root.
-The shared memory, also called on-chip memory located on SM and has low latency and limited capacity.
-Global memory, which is off-chip memory of the GPU has long latency and large capacity.
-Another two types of the memory, texture memory and constant memory, are located off-chip, but cached.
-Therefore the loading speed of the data located in these two type of memory space is much faster than that from global memory.
-Constant memory is read only and with latency approximately as small as the registers.
-Registers are allocated dynamically and privately to threads, the access speed of registers is the faster than all the other four types of memories.
-The variables invoked in $\mathit{kernel}$ functions can be stored in either of the these five types of memories.
+the blocks are executed on SM.
+There are five types of memory, register, shared memory, global memory, constant memory and texture memory.
+Registers are allocated dynamically and privately to threads, which has most rapid access speed.
+The shared memory, also called on-chip memory, which are located on SM and can be shared among the threads in one block, it has low latency and limited capacity.
+Global memory, which is off-chip memory has large latency and large capacity.
+Another two types of the memory, constant memory and texture memory, are located off-chip, but cached.
+Therefore the access speed of these two type of memory space is much faster than that from global memory.
+The variables invoked in \textit{kernel} functions can be stored in either of the these five types of memories.
 
@@
 Thus the total number of threads ($T_{total}$) we can make use of is $T_{total}=N_{SM}\times N_{threads/SM} $, $N_{SM}$ and $N_{threads/SM}$ denote the number of SM and number of threads per SM.
-For example the GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{High_view_of_CUDA_GPU_microarchitecture.eps}
-\caption{High View of CUDA CPU Microarchitecture}
+\includegraphics[width=0.45\textwidth]{High_view_of_CUDA_GPU_microarchitecture.eps}
+\caption{ High View of CUDA CPU Microarchitecture
+The GeForce GTX 760 has 6 SM  and the maximum number of threads allowed on each SM is 2048, thus the total number of threads that can work in parallel is $2048\times 6=12288$.
+}
 \label{figure2}
@@
 
-We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel, corresponding to the discrete time model, the $\mathbb{y}\in\mathbb{C}^{N_{r}\times 1}$ received symbol vecot can be written as:
+We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel, corresponding to the discrete time model, the $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector can be written as:
 \begin{equation}
@@
 
-Assume we have the perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known at the receiver, as well as the SNR.
+Assume the receiver has the perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known at the receiver, as well as the SNR.
 The task of MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
@@
 \end{equation}
-where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is an unitary matrix and $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is an upper triangular matrix, the basing on \cite{golub2012matrix}, we can write (\ref{formula 2}) as:
+where $\mathbf{Q}\in \mathbb{C}^{N_{t}\times N_{t}}$ is an unitary matrix and $\mathbf{R}\in \mathbb{C}^{N_{t}\times N_{t}}$, is an upper triangular matrix, the basing on \cite{golub2012matrix}, we can write (\ref{formula 2}) as:
 \begin{eqnarray}
@@
 
-Just like SD the FCSD also performs depth first searching, at the first $\rho$ node levels (\cite{barbero2008fixing} shows when $N_{r}=N_{t}$ the FCSD can achieve the same diversity as the MLD if $\rho\geq \sqrt{N_{t}}-1$) the FCSD search all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) stage, therefore for the symbol nodes $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$, the FCSD has $M$ branches expansion at each symbol node,  as shown in Figure \ref{figure4}, there are $\rho=2$ FE node levels and each node level has $M=4$ branches.
+Just like SD the FCSD also performs depth first searching, at the first $\rho$ node levels\footnote{when $N_{r}=N_{t}$ the FCSD can achieve the same diversity as the MLD if $\rho\geq \sqrt{N_{t}}-1$ \cite{barbero2008fixing}} the FCSD search all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) stage, therefore for the symbols $\widetilde{s}_{N_{t}}, \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$, the FCSD has $M$ branches expansion at each symbol node,  as shown in Fig.
+\ref{figure4}, there are $\rho=2$ FE node levels and each node level has $M=4$ branches.
 According to (\ref{formula 4}), we have:
@@
 \end{equation} 
-$i\in [1,2\dots N_{t}]$, where $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$,  based on (\ref{formula 5}) at the remaining $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back, therefore there are only $1$ branch expansion for each symbol node at this stage, this stage is called Single Expansion (SE).
-Thus the total number of the branches is fixed (For example in Figure \ref{figure4} the total branch number is $4^{2}$), the FCSD works as a constant number of multiple path tree searching algorithm.
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.5\textwidth]{FCSD_tree_searching.eps}
-\caption{Tree searching of 4-QAM FCSD for 8x8 MIMO system}
-\label{figure4}
-\end{figure}
+$i\in [1,2\dots N_{t}]$, where $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$, $\hat{s}_{i}^{F}$ denotes the FCSD solution symbol.
+Based on (\ref{formula 5}) at the remaining $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back, therefore there are only one branch expansion for each symbol node at this stage, this stage is called Single Expansion (SE).
+Thus the total number of the branches is fixed, the FCSD works as a constant number of multiple path tree searching algorithm.
+
 In conclusion the FCSD symbol vector candidate $s^{F}_{i}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
-\begin{displaymath}
-s^{F}_{i}=\left\lbrace\begin{array}{c}
-\Omega\in  \mathbb{O}^{\rho}      \quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
-\mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}}-s_{F}^{i})] \quad i=N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
-\end{array}\right.
-\label{FCSD solution}
-\end{displaymath}
+\begin{equation}
+\begin{split}
+&{s}_{i}^{F}\in    \mathbb{O}^{\rho}  \quad if\quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
+&FE \quad stage\\
+&{s}_{i}^{F}=\mathbb{Q}[\hat{s}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s}_{j}^{k}-s_{j}^{k})] \quad if\quad i = N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
+& SE\quad stage\\  \label{FCSD solution}
+\end{split}
+\end{equation}
 $\mathbb{Q}[\cdot]$ denotes the signal constellation quantization.
@@
 The symbol vector candidate with the minimum $E_{metric}$ is chosen as the solution.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{FCSD_tree_searching.eps}
+\caption{Tree searching of 4-QAM FCSD for 8$\times$8 MIMO system the total branch number is $4^{2}$}
+\label{figure4}
+\end{figure}
 \subsection{CUDA-FCSD Preprossing}
-As shown in Figure \ref{figure4}, a FCSD channel ordering strategy to avoid error propagation in serial path searching process is presented in \ref{barbero2008fixing}, this channel ordering strategy is based on post processing signal to noise ratio\cite{wolniansky1998v}:
+A FCSD channel ordering strategy is used in order to avoid error propagation in serial path searching process, this channel ordering strategy is based on post processing signal to noise ratio\cite{wolniansky1998v}:
 \begin{equation}
@@
 at the $j$th step ($j=1,2\dots N_{t}-1$), $s_{p}$ denotes the symbol to be detected, where 
-\begin{displaymath}
+\begin{equation}
 p=\left\lbrace \begin{array}{c}
-arg \max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE\quad stage\\
-arg \min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE\quad stage   \label{the ordering}
+arg\max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE\quad stage\\
+arg\min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE\quad stage   \label{the ordering}
 \end{array}\right.  
-\end{displaymath}  
+\end{equation}  
 and $\mathbf{H}_{j}\in \mathbb{C}^{N_{r}\times (N_{t}-j+1)}$ denotes the renewed channel matrix.
@@
 \centering
+\caption{Parallel Computation Operation of FCSD Preprocessing}
 \begin{tabular}{|c|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
@@
 \end{tabular}
-\caption{Parallel Computation Operation of FCSD Preprocessing}
 \label{table1}
@@
 
-Figure \ref{block diagram} illustrates the block diagram of the CUDA-FCSD implementation. 
+\subsection{Parallel Acceleration of Blocked-Paths Searching}
+The decision feedback searching paths have serial nature, we match one path to one thread.
+In order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks.
+For example We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the number of path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt{N_{t}}-1\rceil$, where $\lceil x\rceil$ represent the smallest integer larger than $x$, for largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads which is the maximum number of thread allowing per block.
+At each FCSD searching path, the following data operation is performed in one thread:
+\begin{itemize}
+\item \emph{Path searching}\\
+As we mentioned in (\ref{FCSD solution}).
+\item \emph{Euclidean Distance Calculation}
+\begin{equation}
+E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s}_{j}-s_{j})\label{Eu metric}
+\end{equation}
+$E_{u}^{k}$ denotes the $k$th Euclidean distance of the corresponding symbol vector candidate.
+Loop fusion is applied, we integrate the post processing (\ref{Eu metric}) into path searching process (\ref{FCSD solution}) to reduce the iteration times per thread.
+
+In order to avoid low speed host-device data transfer, we reduce the data transfer time as small as possible, as shown in Fig.
+\ref{block diagram} we make data transfer only two times, For host to device, propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage are transferred, for device to host, FCSD symbol vector solution $\mathbf{s}^{F}$ is transferred.
+\end{itemize}
 \begin{figure}[htb]
@@
 \end{figure}
-\subsection{Parallel Acceleration of Blocked-Paths Searching}
-The decision feedback searching paths have serial nature, we match one path to one thread.
-In order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks.
-For example We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the number of path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt{N_{t}}-1\rceil$, where $\lceil x\rceil$ represent the smallest integer larger than $x$, for largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads which is the maximum number of thread allowing per block.
-At each FCSD searching path, the following data operation is performed in one thread:\\
-1. \emph{Path searching}\\
-According to (\ref{FCSD solution}).
-2. \emph{Euclidean distance Calculation}\\
-\begin{equation}
-E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s}_{j}-s_{j})\label{Eu metric}
-\end{equation}
-$E_{u}^{k}$ denotes the $k$th Euclidean distance of the corresponding symbol vector candidate.
-Loop fusion is applied, we integrate the post processing (\ref{Eu metric}) into path searching process (\ref{FCSD solution}) to reduce the iteration times per thread.
 \subsubsection{Data Preparation}\label{data preparation}
-There are three major factors that will influence the configuration of the data sets configuration in memory space.\\
-1. Amount of Reading$\&$Writing (R/W) operation per thread.\\
-2. Valid scope\\
-3. Storage occupancy
-
-Unlike CPUs that have a flat memory model meaning the CPU core can access any memory location without restriction, GPUs are computation intensive and only have small cache for special memory space (texture, constant).
-Thus the memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influences the application performance.
-Different memory types has different valid scope, local memory which is invoked in kernel function is valid only in one thread, share memory is valid in one block, constant, texture and global memory are valid both at host side and device side.
-On the other hand different from global memory (2047 MBytes in GeForce GTX 760), the constant and share memory are all capacity limited (only $65536$ bytes totally and $49152$ bytes per block in GeForce GTX 760).
+There are three major factors that will influence the configuration of the data sets configuration in memory space.
+\begin{itemize}
+\item Amount of Reading$\&$Writing (R/W) operation
+\item Valid scope
+\item Storage occupancy
+\end{itemize}
+Unlike CPUs that have a flat memory model that is, the CPU core can access any memory location by a near clock rate speed, GPUs are computation intensive.
+Thus the memory reading$\&$writing (R/W) is time consuming that influences the application performance.
+Furthermore different memory types have different valid scopes, local memory which is invoked in kernel function is valid only in one thread, share memory is valid in one block, constant, texture and global memory are valid both at host side and device side.
+On the other hand different from global memory, the constant and share memory are all capacity limited.
 Thus the occupancy of memory is one determinant factor needed to be considered.
 
-At host side we set 4 data sets that are stored in global memory which are storage consumptive and must have valid scope for both host and device side, $\mathit{s_{pm}}$ is a $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope should be during the whole $\mathit{kernel}$ execution.
+At host side we set four data sets that are stored in global memory, $\mathit{s_{pm}}$ is a $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope should be during the whole $\mathit{kernel}$ execution.
 $\mathit{s_{index}}$ is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.
@@
 
-On the other hand, upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\mathbf{\hat{s}}$ in (\ref{unconstrained estimation}) are read only and require large amount of read operations.
-(for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\mathbf{\hat{s}}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\mathbf{\hat{s}}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section \ref{programming model}, the constant memory is cached so that it is much faster than global memory.
+On the other hand, upper triangular matrix $\mathbf{R}$ and unconstrained estimation $\mathbf{\hat{s}}$ in (\ref{formula 4})  are read only and require large amount of read operations, these two data set need small size of storage.
+Constant memory, which is cached and read only   is used to store them.
+\subsubsection{Memory Accesss Pattern}
+When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high\footnote{the theoretical bandwidth of GeForce GTX 760 is 192GB/s}, however the effect memory bandwidth can only be achieved by proper R/W strategy.
 
-In table \ref{amountofR/Woperations}  we present the amount of R/W operations and the storage that needed for different data variables in FCSD path searching.
-The amount of the R/W operation is calculated based on the (\ref{path searching}) and (\ref{Eu metric}), for complex values ($\mathbf{R}$ $\mathbf{\hat{s}}$, $\mathit{s_{pm}}$, $\mathit{s_{kernel}}$ ) are stored using CUDA build in variable data type $\mathit{cuComplex}$ which counts 8 bytes.
-Floating point data set $E_{u}$ is stored using variable type $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored using variable type $\mathit{int}$, which counts 1 byte.\\
- \begin{table*}[htb]  
- \centering
-\begin{tabular}{|l|l|l|l|l|l|l|}
-\hline
-data & $\mathbf{R}$ & $\mathbf{\hat{s}}$ & $\mathit{s_{pm}}$ & $\mathit{s_{index}}$ & $\mathit{E_{u}}$ & $\mathit{s_{kernel}}$ \\
-\hline
-R/W operations/thread & $(\frac{3}{2}(N_{t})^{2}-\frac{N_{t}}{2}+\rho-\rho^{2})$ & $(\frac{2(N_{t})^{2}+2N_{t}-\rho^{2}-\rho}{2})$ & $N_{t}$ & $\rho$ &$N_{t}$ & $N_{t}$ \\
-\hline
-Storage/bytes  & $4(N_{t}+1)N_{t}$ & $8N_{t}$ & $8M^{\rho}N_{t}$ & $N_{t}M^{\rho}$ & $4N_{t}M^{\rho}$ & $8N_{t}$\\
-\hline  
-\end{tabular} 
- \caption{Amount of R/W Operations and Storage Requirement of Different Data Set}
-  \label{amountofR/Woperations} 
-\end{table*}  
-\subsubsection{Memory Accesss Pattern}
-When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.
-
-Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W operations are performed by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible.
-For the GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Figure \ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{pm}}$ as an example to illustrate how we coalesce the the global memory.
+Global memory access is implemented by dynamic random access memory (DRAM) whose R/W is a extremely slow process, modern DRAM R/W operations are performed by access a pitch of consecutive memory location, as mentioned in section \ref{programming model}, the warp is the basic schedule unit of device, instructions are executed warp by warp, thus the most effective global memory access pattern is to keep one warp of threads that access consecutive memory space.
+For the GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Fig.
+\ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{pm}}$ as an example to illustrate how we coalesce the the global memory.
   \begin{figure}[htb]
@@
 \end{figure}
-We store $\mathit{s_{pm}}$ in one pitch of linear global memory, with each row store one $N_{t}=16$ complex symbol vector solution candidate of $\mathbf{\hat{s}}^{F}$ in (\ref{formula 5}), totally there are $M^{\rho}=4096$ rows, this matrix is stored in column major.
-As mentioned before one path searching is performed by one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256$ bytes, counts for two times of DRAM access.
+$\mathit{s_{pm}}$ is stored in one pitch of linear global memory, with each row store one $N_{t}$ complex symbol vector solution candidate of $\mathbf{\hat{s}}^{F}$ in (\ref{formula 5}), totally there are $M^{\rho}$ rows, this matrix is stored in column major.
+As mentioned before one path searching is performed by one thread, thus the address distance between two consecutive symbol operated in one thread is $M^{\rho}$, however for consecutive threads in one warp the address they reach is continues as shown in Fig.
+\ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256$ bytes, counts for two times of DRAM access.
 
-As we mentioned in section (\ref{programming model}), the registers are allocated to the threads dynamically and have much faster access speed than that of global memory.
-Therefore, for all the transient data that used for accumulator in (\ref{path searching}), (\ref{Eu metric}), and the symbol vector candidate during the path searching process of each thread, are stored temporarily in registers to hide the latency of R/W of global memory.
-\subsubsection{Data Transfer Minimization}   
-The data transfer between the host and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage.
+All the  thread level transient data that are used in accumulator in (\ref{FCSD solution}), (\ref{Eu metric}), and the symbol vector candidate during the path searching process, are stored temporarily in registers to get near clock rate access speed.
+
 \subsection{Larger MIMO Systems and Constellation Sizes}
-Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, the path number that need to be searched is $M^{\rho}=16^{5}=1048576$.
-The maximum number of threads that can be execute in $\mathit{kernel}$ function of the GeForce GTX 760 is 12288, therefore we need to consider execute the $\mathit{kernel}$ function in loop, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
-Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the $\mathit{kernel}$ function for 86 times and get the final solution,  when it comes to the large MIMO systems and large signal constellations such as $36\times 36$ $16$QAM, $144\times 144$ $4$QAM, $20\times 20$ $64$QAM, the global memory that need to used to store $s_{pm}$ in section (\ref{data preparation}) will out of bound (2 GB), multiple kernels with each one deal with a small subset of symbol vector candidates and kernel concurrency\cite{nvidia2008programming} can be applied to solve this problem.
+There are two problems that need to be considered for larger MIMO systems and constellation size:
+\begin{itemize}
+\item Thread resource limitation:
+The number of threads that can be executed in parallelism is limited.
+When the size of MIMO systems and constellation grows larger, it becomes impossible to parallel all the searching path in one \textit{kernel} execution, for example, $32\times 32$ MIMO system with $16$QAM modulation scheme, the path number that need to be searched is $M^{\rho}=16^{5}=1048576$.
+\item Global memory limitation:
+Large MIMO systems and large signal constellations requires a mass of global memory space to store the symbol vector candidates, For example the systems $36\times 36$ $16$QAM, $144\times 144$ $4$QAM, $20\times 20$ $64$QAM, the space that need to used to store $s_{pm}$ in section \ref{data preparation} will out of bound (2 GB)
+\end{itemize}
+One solution to these two problems is the partial parallelism, the detection task is divided into several times of \textit{kernel} execution, for each \textit{kernel} execution only one potential symbol vector solution as well as its corresponding Euclidean distance are preserved, so that the global memory space is reused to avoid exceeding the bound of global memory.
 \section{Simulation Results}\label{simulation}
@@
 \subsubsection{Device}
-\emph{Graphic Processing Units}: GeForce GTX 760, GPU clock rate: 1.08 GHz , memory clock rate: 3 GHz , number of SM: 6, maximum number of threads per stream multiprocessor: 2048, total amount of global memory: 2 GB, total amount of share memory per block: 49 KB, total amount of constant memory: 66 KB.
-\\
-\emph{Central Processing Units-Modigliani}: Intel Core i5-4th generation, 4 cores 3.20 GHz CPU clock rate, 8 GB RAM\\
-\emph{Central Processing Units-Monet} : Intel Core i7-3rd generation, 12 cores 3.20 GHz CPU clock rate, 32 GB RAM
+\begin{itemize}
+\item \emph{Graphic Processing Units}: GeForce GTX 760, GPU clock rate: 1.08 GHz , memory clock rate: 3 GHz , number of SM: 6, maximum number of threads per stream multiprocessor: 2048, total amount of global memory: 2 GB, total amount of share memory per block: 49 KB, total amount of constant memory: 66 KB.
+\item \emph{Central Processing Units-Modigliani}: Intel Core i5-4th generation, 4 cores 3.20 GHz CPU clock rate, 8 GB RAM
+\item \emph{Central Processing Units-Monet} : Intel Core i7-3rd generation, 12 cores 3.20 GHz CPU clock rate, 32 GB RAM
+\end{itemize}
 \subsubsection{Software}
@@
 \centering
+\caption{ speedup performance of different MIMO systems using 4 QAM}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 \end{tabular}
-\caption{speedup performance of different MIMO systems using 4 QAM}
 \label{speedup1}
@@
 \centering
+\caption{ speedup performance of different MIMO systems using 16 QAM}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 \end{tabular}
-\caption{speedup performance of different MIMO systems using 16 QAM}
 \label{speedup2}
 \end{table*}
-\begin{table*}[h]
+\begin{table*}[htb]
 \centering
+\caption{ speedup performance of different MIMO systems using 64 QAM}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 $16\times 16$&468.92 & 2066.08&2689.00& 4.41& 5.73\\
-
 \hline
-
 \end{tabular}
-\caption{speedup performance of different MIMO systems using 64 QAM}
 \label{speedup3}
@@
 
-We made simulation to different sizes MIMO systems and signal constellation and comparison is made between the Geforce GTX 760 and two kinds of CPU, the speedup performance is presented in table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
-All the operation times we test is based on $1000$ channel realizations, the transmitted data is generated randomly and modulated by $M$ quadrature amplitude modulation (QAM) scheme.
+Simulations are made for different sizes MIMO systems and signal constellation and comparison is made between the Geforce GTX 760 and two kinds of CPU, the speedup performance is presented in table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
+All the operation times we test is based on $1000$ channel realizations.
 
 In table \ref{speedup1}, for small MIMO systems $8\times 8$ and $16\times 16$, the speed performance of GPU implementation is even worse than that of CPU.
-The number of path of these antenna configurations that need to be searched is relatively small ($16$ for $8\times 8$ system and $64$ for $16\times 16$ system), the CPU implementation has already had a good performance, the CPUs are designed for serial code execution with the special hardwares (branch prediction units, multiple caches, etc) and have extremely good performance at it, however the GPUs can achieve a good performance only when they are utilized in parallel manner, there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
-Furthermore, for small number of threads, the memory R/W latency is not well hided.
-For the $32\times 32$ systems, the speed performance of GPU and CPU implementation is close, when comes to larger MIMO systems $48\times 48$, $64\times 64$, $72\times 72$, a large parallelism is achieved so that the GPU begin to display its data processing power, the speedup can be from $2.50$ to $4.20$.
+The number of path of these antenna configurations that need to be searched is relatively small\footnote{$8\times 8$ MIMO system has $16$ paths and $16\times 16$ MIMO system has $64$ paths}, the CPU implementation has already had a good performance, the CPUs are designed for serial code execution with the special hardwares (branch prediction units, multiple caches, etc) and have extremely good performance at it, however the GPUs can achieve a good performance only when they are utilized in massive parallel manner, Furthermore there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
+For the $32\times 32$ systems, the speed performance of GPU and CPU implementation is close, when comes to larger MIMO systems $48\times 48$, $64\times 64$, $72\times 72$, a large parallelism is achieved so that the GPU begin to display its data processing power.
 
-In table \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM are considered, the speedup of GPU implementation is reached from a small MIMO size, For $16\times 16$ system using $16$QAM $1.18$ speedup over Modigliani and $1.57$ speedup over Monet.
-For $8\times 8$, $64$QAM, $0.87$ speedup over Modigliani and $1.09$ speedup over Monet.
-For lager signal constellation, the massive parallelism can be reached for relatively small MIMO systems.
+In table \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM are considered, the speedup of GPU implementation is reached from a small MIMO size.
+For $16\times 16$ system, $16$QAM modulation, GTX 760 has $1.18$ speedup over Modigliani and $1.57$ speedup over Monet.
+For $16\times 16$ system, $64$QAM modulation, GTX 760 can reach $4.41$ speedup over Modiliani and $5.73$ speedup over Monet.
+The nature of FCSD determine that for lager signal constellation, the massive parallelism can be reached for relatively small MIMO systems.
 
 It can be observed from table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, GPU implementation shows its speed advantage over CPU implementation for increasing size of MIMO systems and signal constellations, indicating this GPU implementation's suitability for large MIMO system and large signal constellation.
-\begin{figure}[h]
+
+Fig.
+\ref{BER curve} shows the Monte Carlo simulation results of bit error rate (BER) performance for different MIMO systems and constellation sizes, we consider uncoded complex spatial multiplexing MIMO systems, the transmitted binary sequence is generated randomly and  mutually independent, modulated by $M$-QAM modulation scheme, the results have been obtained using $100000$ channel realizations and $500$ symbol errors accumulated.
+The simulation result shows FCSD-CUDA can reach the same BER performance as CPU version.
+\begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{BER_curves.eps}
-\caption{BER performance of different sizes of MIMO systems and modulation scheme by GPU}
+\includegraphics*[width=0.5\textwidth]{BER_curves.eps}
+\caption{ BER performance of different sizes of MIMO systems and modulation scheme by GPU}
 \label{BER curve}
 \end{figure}
-Figure \ref{BER curve} shows the Monte Carlo simulation results of bit error rate (BER) performance for different MIMO systems and constellation sizes, we consider uncoded spatial multiplexing MIMO systems, the transmitted binary sequence is generated randomly and  mutually independent, modulated by $M$-QAM modulation scheme, the results have been obtained using $100000$ channel realizations and $500$ symbol errors accumulated.
 \section{Conclusion}\label{conclusion}
@@
 In order to exploit the computational capability of GPU in the simulation of large MIMO systems, the utilization of heterogeneous programming model, thread resource limitation and memory configuration are considered in a comprehensive way.
-The simulation shows considerable acceleration of GPU implementation of FCSD can be reached for large MIMO systems and large signal constellation sizes while the same BER performance can be obtained.
+The simulation shows considerable acceleration of GPU implementation of FCSD can be reached for large MIMO systems and signal constellation sizes while the same BER performance can be obtained.
 In addition, the GPU and CPU can work independently, the data processing power of GPU computing is an extra bonus of the traditional simulation platform.
 This shows the potential of GPU computing for computational consumptive simulation in large MIMO area.
-The future work contains taking into consider the kernel execution and data transferring concurrence in order to optimize memory allocation strategy for large MIMO systems.
+
 % conference papers do not normally have an appendix
@@
 \bibliographystyle{IEEEtran}
-\bibliography{citation_conf}
+\bibliography{IEEEabrv,citationconf}
 \end{document}

### 2015-01-05 Parallel Acceleration of Fixed Complexity Sphere Decoder Based on GPU/conf_draft/conference draft.tex
this is the final version of Parallel Acceleration of FCSD paper

@@
 % draft mode.
-\documentclass[a4paper, 10pt, conference]{IEEEconf}
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}
+\documentclass[letterpaper, 10pt, conference]{ieeeconf}
 %\documentclass[12pt,a4paper,final]{article}
@@
 \usepackage{epstopdf}
+%\usepackage{graphics} % for pdf, bitmapped graphics files
+%\usepackage{epsfig} % for postscript graphics files
+\usepackage{mathptmx} % assumes new font selection scheme installed
+%\usepackage{times} % assumes new font selection scheme installed
+%\usepackage{amsmath} % assumes amsmath package installed
+\usepackage{amssymb}  % assumes amsmath package installed
+\usepackage{fancyhdr}
 % Some very useful LaTeX packages include:
@@
 % Do not put math or special symbols in the title.
-\title{\LARGE \bf GPU Acceleration of Fixed Complexity Sphere Decoder for Large MIMO Uplink Systems}
+\title{\LARGE \bf GPU Acceleration for Fixed Complexity Sphere Decoder in Large MIMO Uplink Systems}
 
@@
 %Montreal, Quebec}}
-\author{Tianpei Chen and Harry Leib}
+\author{Tianpei Chen and Harry Leib\\
+Department of Electrical and Computer Engineering, McGill University, Montreal, Quebec\\
+tianpei.chen@mail.mcgill.ca harry.leib@mcgill.ca}
  %Department of Electrical and Computer Engineering\\
@@
 %\begin{spacing}{2.5}
-\date{}
+%\date{}
 \maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
+\thispagestyle{fancy} % IEEE模板在\maketitle后会自动声明\thispagestyle{plain}，  
+                      % 导致第一页什么都没有。所以得把plain更改为fancy  
+\lhead{} % 页眉左，需要东西的话就在{}内添加  
+\chead{} % 页眉中  
+\rhead{\thepage} % 页眉右  
+\lfoot{} % 页眉左  
+\cfoot{} % 页眉中  
+\rfoot{} %页眉右，\thepage 表示当前页码  
+\renewcommand{\headrulewidth}{0pt} %改为0pt即可去掉页眉下面的横线  
+\renewcommand{\footrulewidth}{0pt} %改为0pt即可去掉页脚上面的横线  
+\pagestyle{fancy}  
+\rhead{\thepage}
+%\thispagestyle{empty}
+%\pagestyle{empty}
 % As a general rule, do not put math, special symbols or citations
@@
 \begin{abstract}
-Large MIMO constitutes a principal techniques for next generation wireless communication systems.
-Detection algorithms for large MIMO tend to require long simulation times on conventional computer systems, in order to reduce the simulation times for decoders of large MIMO systems, we propose to use General Purpose Graphic Processing Units (GPGPU).
-In this paper Fixed Complexity Sphere Decoder (FCSD) is implemented for the large scale MIMO system based on the dominant framework of GPGPU-Computed Unified Device Architecture (CUDA).
-The proposed CUDA-FCSD can achieve considerable speedup over conventional CPU implementation while reaching the same Bit Error Rate (BER) performance.
-Furthermore the proposed algorithm demonstrates great potential to accelerate large MIMO systems.\\
-\textbf{ Keywords: Large MIMO, FCSD, GPGPU, CUDA}
+Large MIMO constitutes a principal technology for next generation wireless communication systems.
+Detection algorithms for large MIMO schemes tend to require long simulation times on conventional computer systems.
+In order to improve simulation efficiency of decoders in large MIMO systems, we propose to use General Purpose Graphic Processing Units (GPGPU).
+This paper considers the implementation of a Fixed Complexity Sphere Decoder (FCSD) for large scale MIMO systems using the framework of GPGPU-Computed Unified Device Architecture (CUDA).
+The proposed CUDA-FCSD can achieve considerable speedups over conventional CPU implementation while providing the same Bit Error Rate (BER) performance.
+Furthermore the proposed algorithm demonstrates the great potential of GPGPU to accelerate the simulation of large MIMO systems.
+
+\textbf{ Keywords: Large MIMO, fixed complexity sphere decoder (FCSD), general purpose graphic processing units (GPGPU), computed unified device architecture (CUDA)}
 \end{abstract}
@@
 \section{Introduction}
-The present challenge in the wireless communication area is the sharp contrast between the increasing demand of mobile network speed for the transmission of rich media content with better QoS (Quality of Service), and the shortage of radio frequency spectrum.
-Multiple Input Multiple Output (MIMO) is thought to be a very promising technology that can help to solve this problem owing to several advantages it can offer.
-The core idea of MIMO is to use multiple antennas that at the transmitting and receiving sides, that provide parallel data pipes in space resulting in spatial multiplexing gains\cite{oestges2010mimo}.
-For example the LTE standard supports up to 8 antennas at the base station\cite{dahlman20103g}.
+A present challenge in the wireless communication area is to bridge the sharp contrast between the increasing demand of mobile network speed for the transmission of rich media content with better QoS (Quality of Service), and the shortage of radio frequency spectrum.
+Multiple Input Multiple Output (MIMO) technology is of immense research interest since it can help solving this problem owing to several advantages it offers.
+The core idea of MIMO is to use multiple antennas at the transmitting and receiving sides, that provide parallel data pipes, resulting in spatial multiplexing and diversity gains\cite{oestges2010mimo}.
 
-Large scale MIMO (also named massive MIMO) systems employ hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}.
-This technology originated from multiuser MIMO (MU-MIMO) systems\cite{larsson2013massive}.
-Large scale MIMO will achieve the full potential of conventional MIMO systems (spatial diversity gain and spatial multiplexing gain), as well as provide additional reduction of latency and improvement of system robustness.
-Detector is one of the key component of MIMO systems,
- a well known detector for MIMO system is the Sphere Decoder (SD) that perform as well as a Maximum Likelihood detector (MLD) with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}.
-There are two major problems with the traditional SD decoder: complexity depending on Signal to Noise Ratio (SNR), and sequential nature, which are contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system.
-The Fixed Complexity Sphere Decoder (FCSD) overcomes these two disadvantages of the SD decoder by searching the solution along a fixed number of independent paths\cite{barbero2008fixing}.
+Large scale MIMO (also named massive MIMO) systems employ tens to hundreds of low-power low-price antennas at the base station, that serve many terminals at the same time\cite{rusek2013scaling}.
+Large scale MIMO can achieve the full potential of conventional MIMO systems, as well as provide additional reduction of latency and improvement of system robustness.
+The detector is one of the key components of MIMO systems.
+ A well known detector for MIMO systems is the Sphere Decoder (SD) that performs as well as a Maximum Likelihood detector (MLD), with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}.
+There are two major problems with the traditional SD decoder: complexity depending on Signal to Noise Ratio (SNR), and sequential nature, which conflict with the requirement of a constant data processing throughput and parallel implementation for practical systems.
+The Fixed Complexity Sphere Decoder (FCSD) overcomes these problems of the SD decoder by searching the solution along a fixed number of independent paths\cite{barbero2008fixing}.
 
-General purpose Graphic processing Units Computing (GPGPU) has become a common trend in industry and research in areas that need massive computations, such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
-Compared to CPU, the GPU can naturally cope with computational intensive tasks, since most of the hardware resource are allocated for data processing and parallel computation, rather than caching and flow control.
+General Purpose Graphic Processing Units (GPGPU) computing is a common trend in industry and research in areas that need massive computations, such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435}, and finance\cite{grauer2013accelerating}.
+Compared to a CPU, a GPU can naturally cope with computational intensive tasks, since most of the hardware resources are allocated for data processing and parallel computation, rather than caching and flow control\cite{cook2013cuda}.
 In recent years GPU computing has provided significant advantages in data processing speeds over CPU computations\cite{nvidia2008programming}.
-In 2011, the NVIDIA GPUs have become the fastest supercomputer in the world\cite{cook2013cuda},  Computed unified Device Architecture (CUDA) is a programming model for GPGPU that was proposed by NIVIDIA and has become the dominant framework for GPGPU programming.
-It is based on popular programming languages(C, C++, Java, Python, Fortran, Direct Compute), such that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
-CUDA employs the Single Instruction Multiple Threads (SIMT) programming model, enables a GPU to implement parallel data processing, and has become a parallel computing platform for wide community of different applications.
+The Computed unified Device Architecture (CUDA)\cite{cook2013cuda}\cite{nvidia2008programming} is a programming model for GPGPU that was proposed by NIVIDIA and has become the dominant framework for GPGPU programming.
+It is based on popular programming languages (C, C++, Java, Python, Fortran, Direct Compute), such that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
+CUDA employs the Single Instruction Multiple Threads (SIMT) programming model, enables a GPU to implement parallel data processing, and has become a parallel computing platform for different applications.
 
-In this paper, a GPU based implementation of Fixed Complexity Sphere Decoder is proposed, which is referred to as CUDA-FCSD.
-A heterogeneous programming solution for FCSD preprocessing and integrated blocked parallel path searching and decision maker solution are presented, the speedup as well as Bit Error Rate (BER) performance of different sizes of MIMO systems and signal constellations are presented and analyzed.
+In this paper, a GPU based implementation of Fixed Complexity Sphere Decoder (FCSD) is proposed, which is referred to as CUDA-FCSD.
+A heterogeneous programming solution for FCSD preprocessing and integrated blocked parallel path searching and decision making are presented.
+Using this implementation the speedup as well as Bit Error Rate (BER) performance of different sizes of MIMO systems and signal constellations are analyzed.
 The proposed CUDA-FCSD implementation demonstrates a great potential for large MIMO systems.
@@
 The rest of the paper is organized as follows.
-Section \ref{system} describes the MIMO systems model.
-Section \ref{programming model} introduces CUDA, GPU architecture and the programming model.
+Section \ref{programming model} briefly introduces CUDA, the GPU architecture and the programming model.
 In section \ref{GPUFCSD}, we present details of the implementation of CUDA-FCSD.
-In section \ref{simulation}, the speedup and bit error rate (BER) performance of CUDA-FCSD are presented and analyzed.
-Finally conclusions are drawn in section \ref{conclusion}.
+In section \ref{simulation}, the speedup and bit error rate (BER) performance of CUDA-FCSD are considered.
+Finally, conclusions are drawn in section \ref{conclusion}.
 % An example of a floating figure using the graphicx package.
@@
 
-\section{CUDA GPU Architecture and  Programming Model} \label{programming model}
-\subsection{Memory Hierarchy}  
-CUDA programming model is a C programming extension, with special defined syntax and structure.
-The serial code is executed on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side, this is defined as a heterogeneous programming model.
-A thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share one pitch of on chip memory (shared memory), all the threads executed in one block can synchronize their action meaning the threads are permitted to execute the next instruction only when all the threads have reached the same instruction node.
-Blocks can be grouped into a one-dimensional, two-dimensional, or three-dimensional grid.
-Similarly, The threads can also be organized into one-dimensional, two-dimensional or three-dimensional blocks.
-The organization of the block and grid shape and dimension is determined by the application, Figure \ref{figure1}  simply illustrates the three dimensional thread hierarchy of CUDA.
+\section{CUDA Programming Model and GPU Architecture} \label{programming model} 
+\subsection{Single Instruction Multiple Thread Model}
+The CUDA programming model is a C programming extension with special defined syntax and structure.
+The serial code is executed on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side.
+Such an approach is defined as a heterogeneous programming model.
+A thread is the basic programming unit of CUDA.
+A block of cooperative threads form a thread block, where they can synchronize their behavior and communicate.
+Fig.
+\ref{figure1} illustrates a simple CUDA memory hierachy model.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{CUDA_programming_hierachy.eps}
-\caption{CUDA 3D thread hierachy\\ $5\times 5\times 5$ grid and each block contains $5\times 5\times 5$ threads\\}
+\includegraphics*[width=0.5\textwidth]{CUDA_programming_hierachy.eps}
+\caption{ CUDA 3D memory hierachy $5\times 5\times 5$ grid, with each block composed of $5\times 5\times 5$ threads.
+The threads can be organized into one-dimensional, two-dimensional or three-dimensional blocks.
+Similarly, blocks can also be grouped into a one-dimensional, two-dimensional, or three-dimensional grid.
+}
 \label{figure1}
@@
 
-\subsection{Single Instruction Multiple Thread (SIMT) Model} 
-Threads are scheduled, managed, created and executed in a group of 32 threads called warp, the programs executes on the device side are defined as $\mathit{kernel}$ function, when a $\mathit{kernel}$ function is invoked, the thread blocks are partitioned into warps, the threads in one warps executes the same instruction simultaneously, the different warps are scheduled by warp scheduler, when one warp is waiting for data loading the other warps begin to execute, this is called Single Instruction Multiple Thread (SIMT) model.
-This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branch the behavior of each threads to achieve thread-level parallelism.
-The GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU.
-In a word CPU cores are designed to minimize latency for each thread at a time, whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput.
+Threads are scheduled, managed, created and executed in a group of 32, called warp.
+The programs that execute on the device side are defined as \textit{kernel} functions.
+When a \textit{kernel} function is invoked, the thread blocks are partitioned into warps.
+The threads in one warp execute the same instruction simultaneously.
+The different warps are scheduled by a warp scheduler.
+When one warp is waiting for data loading, the other warps begin to execute.
+Such an approach is called a Single Instruction Multiple Thread (SIMT) model.
+This programming architecture is akin to a Single Instruction Multiple Data (SIMD) scheme, however unlike SIMD vectoring machines, the SIMT can branch the behavior of each threads to achieve thread-level parallelism.
+The GPU uses a massive number of threads to hide the long latency of a global memory, instead of using a large cache as CPU.
+A CPU core is designed to minimize the latency for each thread at a time, whereas a GPU is designed to handle a large number of concurrent lightweight threads, in order to maximize throughput.
 \subsection{Mircroarchitecture of GPU} 
-In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
-The GPU works as a coprocessor system, consisting of Stream Multiprocessors (SM).
-The GeForce GTX 760 has 6 SM that perform the multiply-add arithmetic operation.
-Furthermore, each SM has the special functional units(SFU) that can perform more complex arithmetics such as trigonometric functions and reciprocal square root.
-The shared memory, also called on-chip memory located on SM and has low latency and limited capacity.
-Global memory, which is off-chip memory of the GPU has long latency and large capacity.
-Another two types of the memory, texture memory and constant memory, are located off-chip, but cached.
-Therefore the loading speed of the data located in these two type of memory space is much faster than that from global memory.
-Constant memory is read only and with latency approximately as small as the registers.
-Registers are allocated dynamically and privately to threads, the access speed of registers is the faster than all the other four types of memories.
-The variables invoked in $\mathit{kernel}$ functions can be stored in either of the these five types of memories.
+We present the GPU-GeForce GTX 760 microarchitecture in Fig.
+\ref{figure2} as an example.
+The GPU works as a coprocessor system, consisting of Stream Multiprocessors (SMs), which perform multiply-add arithmetic operations.
+Furthermore, each SM has the special functional units (SFU) that can perform more complex operations such as trigonometric functions and reciprocal square root.
+There are five types of memories: registers, shared memory, global memory, constant memory and texture memory.
+Registers are allocated dynamically and privately to threads, and provide most rapid access speeds.
+The shared memory, also called on-chip memory, is located on the SMs and can be shared among the threads in one block.
+Shared memory has low latency and limited capacity.
+Global memory, which is off-chip has large latency and large capacity.
+The other two types of memories, constant memory and texture memory, are located off-chip, but cached.
+Therefore the access speed of these two type of memory space is much faster than that of global memory.
+The variables invoked by \textit{kernel} functions can be stored in either of the these five types of memories.
 
-Because of the resource limitation of SM the total number of threads can be defined in one block is limited.
-On current CUDA supported GPUs, one block can contains up to 1024 threads, and all the blocks are executed on SM.
-Thus the total number of threads ($T_{total}$) we can make use of is $T_{total}=N_{SM}\times N_{threads/SM} $, $N_{SM}$ and $N_{threads/SM}$ denote the number of SM and number of threads per SM.
-For example the GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$.
+Because of the resource limitation of SM, the total number of threads that can be defined in one block is limited.
+On current CUDA supported GPUs, one block contains up to 1024 threads.
+Thus the total number of threads ($T_{total}$) we can use is $T_{total}=N_{SM}\times N_{threads/SM} $, where $N_{SM}$ and $N_{threads/SM}$ denote the number of SMs and number of threads per SM.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{High_view_of_CUDA_GPU_microarchitecture.eps}
-\caption{High View of CUDA CPU Microarchitecture}
+\includegraphics[width=0.45\textwidth]{High_view_of_CUDA_GPU_microarchitecture.eps}
+\caption{ High View of CUDA CPU Microarchitecture
+The GeForce GTX 760 has 6 SMs and the maximum number of threads allowed on each SM is 2048. Thus the total number of threads that can work in parallel is $2048\times 6=12288$.
+}
 \label{figure2}
@@
 
-We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel, corresponding to the discrete time model, the $\mathbb{y}\in\mathbb{C}^{N_{r}\times 1}$ received symbol vecot can be written as:
+We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel.
+Using a discrete time model, $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector written as:
 \begin{equation}
-\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n}   \label{formula 1}
+\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{formula 1}
 \end{equation}
-$\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from the signal constellation $\mathbb{O}$ (4-QAM, 16-QAM, 64-QAM), of size $M$.
-All the possible transmitted symbol vectors forms a $N_{t}$ complex signal vector space $\mathbb{O}^{N_{t}}$.
-$\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
-$\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean components of unit variance, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise power spectrum density and $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR).
+where $\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from a signal constellation $\mathbb{O}$ (4-QAM, 16-QAM, 64-QAM) of size $M$.
+All the possible transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, with $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed (i.i.d) circularly symmetric complex Gaussian components of zero mean and unit variance.
+Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
 
-Assume we have the perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known at the receiver, as well as the SNR.
-The task of MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
+Assume the receiver has the perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known by receiver, as well as the SNR.
+The task of the MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
 \subsection{Fixed Complexity Sphere Decoder}
@@
 \begin{equation}
-\mathbf{s}_{ML}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{y}-\mathbf{H}\mathbf{s}||^{2} \label{formula 2}
+\mathbf{s}_{ML}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{y}-\mathbf{H}\mathbf{s}||^{2}. \label{formula 2}
 \end{equation}
-We consider a MIMO system with  $N_{t}=N_{r}$. Performing the QR decomposition to the channel propagation matrix
+We consider a MIMO system with  $N_{t}=N_{r}$. Performing the QR decomposition of the channel propagation matrix
 \begin{equation}
- \mathbf{H}=\mathbf{Q}\mathbf{R}  \label{QR}
+ \mathbf{H}=\mathbf{Q}\mathbf{R},  \label{QR}
 \end{equation}
-where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is an unitary matrix and $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is an upper triangular matrix, the basing on \cite{golub2012matrix}, we can write (\ref{formula 2}) as:
+where $\mathbf{Q}\in \mathbb{C}^{N_{t}\times N_{t}}$ is a unitary matrix and $\mathbf{R}\in \mathbb{C}^{N_{t}\times N_{t}}$, is an upper triangular matrix \cite{golub2012matrix}, we can write (\ref{formula 2}) as:
 \begin{eqnarray}
@@
 \mathbf{s}_{ML}&=&arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}\mathbf{y}-\mathbf{Q}^{H}\mathbf{H}\mathbf{s}||^{2}\\
-&=& arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}\mathbf{y}-\mathbf{R}\mathbf{s}||^{2} \label{formula 3}
+&=& arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}\mathbf{y}-\mathbf{R}\mathbf{s}||^{2}. \label{formula 3}
 \end{eqnarray}
-Consider the unconstrained estimation of $\mathbf{s}$, $\mathbf{\hat{s}}=\mathbf{G}\mathbf{y}$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$ based on (\ref{QR}), we have  
+Using the unconstrained estimator of $\mathbf{s}$, $\mathbf{\hat{s}}=\mathbf{G}\mathbf{y}$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$, and (\ref{QR}), we have  
 \begin{equation}
 \mathbf{\hat{s}}=\mathbf{G}\mathbf{y}=(\mathbf{R}^{H}\mathbf{R})^{-1}\mathbf{R}^{H}\mathbf{Q}^{H}\mathbf{y}
-=\mathbf{R}^{-1}\mathbf{Q}^{H}\mathbf{y}
+=\mathbf{R}^{-1}\mathbf{Q}^{H}\mathbf{y}.
 \label{unconstrained estimation}
@@
 \begin{equation}
-\mathbf{s}_{ML}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{s})||^{2} \label{formula 4}
+\mathbf{s}_{ML}=arg\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{s})||^{2}. \label{formula 4}
 \end{equation}
 
-Just like SD the FCSD also performs depth first searching, at the first $\rho$ node levels (\cite{barbero2008fixing} shows when $N_{r}=N_{t}$ the FCSD can achieve the same diversity as the MLD if $\rho\geq \sqrt{N_{t}}-1$) the FCSD search all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) stage, therefore for the symbol nodes $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$, the FCSD has $M$ branches expansion at each symbol node,  as shown in Figure \ref{figure4}, there are $\rho=2$ FE node levels and each node level has $M=4$ branches.
+Similarly to SD the FCSD also performs depth first searching.
+At the first $\rho$ node levels\footnote{when $N_{r}=N_{t}$ the FCSD can achieve the same diversity as the MLD if $\rho\geq \sqrt{N_{t}}-1$ \cite{barbero2008fixing}} the FCSD searches all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, a process called the Full Expansion (FE) stage.
+Let $\mathbf{s}^{F}$ denote FCSD symbol vector candidates.
+For the symbols $s^{F}_{N_{t}}, s^{F}_{N_{t}-1}\dots s^{F}_{N_{t}-\rho+1}$, the FCSD has $M$ branch expansions at each symbol node.
+As shown in Fig.
+\ref{figure4}, there are $\rho=2$ FE node levels and each node level has $M=4$ branches.
 According to (\ref{formula 4}), we have:
 \begin{equation}
-\hat{s}^{F}_{i}=arg\min_{s\in \mathbb{O}^{N_{t}}}\{\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s_{j})|^{2}\}  \label{formula 5}
+s^{F}_{i}=arg\min_{s\in \mathbb{O}^{N_{t}}}\{\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s^{F}_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s^{F}_{j})|^{2}\},  \label{formula 5}
 \end{equation} 
-$i\in [1,2\dots N_{t}]$, where $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$,  based on (\ref{formula 5}) at the remaining $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back, therefore there are only $1$ branch expansion for each symbol node at this stage, this stage is called Single Expansion (SE).
-Thus the total number of the branches is fixed (For example in Figure \ref{figure4} the total branch number is $4^{2}$), the FCSD works as a constant number of multiple path tree searching algorithm.
+$i\in [1,2\dots N_{t}]$, where $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$.
+Based on (\ref{formula 5}) at the remaining $N_{t}-\rho$ levels of symbols, the FCSD employs decision feedback, and therefore there are only one branch expansion for each symbol node at this stage.
+This stage is called Single Expansion (SE).
+Thus the total number of the branches is fixed, and the FCSD works as a constant number of multiple path tree searching algorithm.
+
+In conclusion the FCSD symbol vector candidate $s^{F}_{i}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
+\begin{equation}
+\begin{split}
+&FE \quad stage:\\
+&{s}_{i}^{F}\in    \mathbb{O}^{\rho},  \quad if\quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
+& SE\quad stage:\\
+&{s}_{i}^{F}=\mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s}_{j}-s_{j}^{F})], \quad if\quad \\
+& i = N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 
+  \label{FCSD solution}
+\end{split}
+\end{equation}
+where $\mathbb{Q}[\cdot]$ denotes the operation of signal constellation quantization. At the post processing stage, the FCSD compares the Euclidean distance of all the symbol vector candidates
+\begin{equation}
+E_{metric}=||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{s}^{F})||^{2},
+\end{equation} 
+where $\mathbf{s}^{F}$ denotes the symbol vector candidate. The symbol vector candidate with minimum $E_{metric}$ is chosen as the solution. The total number of candidates is $M^{\rho}$.  
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{FCSD_tree_searching.eps}
-\caption{Tree searching of 4-QAM FCSD for 8x8 MIMO system}
+\includegraphics[width=0.5\textwidth, height=8cm]{FCSD_tree_searching.eps}
+\caption{Tree searching of 4-QAM FCSD for 8$\times$8 MIMO system. The total number of branches is $4^{2}$}
 \label{figure4}
 \end{figure}
-In conclusion the FCSD symbol vector candidate $s^{F}_{i}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
-\begin{displaymath}
-s^{F}_{i}=\left\lbrace\begin{array}{c}
-\Omega\in  \mathbb{O}^{\rho}      \quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
-\mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}}-s_{F}^{i})] \quad i=N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
-\end{array}\right.
-\label{FCSD solution}
-\end{displaymath}
-$\mathbb{Q}[\cdot]$ denotes the signal constellation quantization.
-At the post processing stage, FCSD compares the Euclidean distance of all the symbol vector candidates $E_{metric}$, which can be written as:
+\subsection{CUDA-FCSD Preprocessing}
+A FCSD channel ordering strategy is used in order to avoid error propagation in the serial path searching process.
+This channel ordering strategy is based on post processing signal to noise ratio\cite{wolniansky1998v}
 \begin{equation}
-E_{metric}=||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{\widetilde{s}})||^{2}
+\varphi_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}},  \label{ppsnr}
 \end{equation}
-Where the $\mathbf{\widetilde{s}}$ denotes the symbol vector candidate. The total number of candidates is: 
-\begin{equation}
-M^{\rho}     \label{path number}
-\end{equation} 
-The symbol vector candidate with the minimum $E_{metric}$ is chosen as the solution.
-\subsection{CUDA-FCSD Preprossing}
-As shown in Figure \ref{figure4}, a FCSD channel ordering strategy to avoid error propagation in serial path searching process is presented in \ref{barbero2008fixing}, this channel ordering strategy is based on post processing signal to noise ratio\cite{wolniansky1998v}:
-\begin{equation}
-\varphi_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}}  \label{ppsnr}
-\end{equation}
-where $\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, and $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inversion of $\mathbf{H}^{H}\mathbf{H}$.
-When the SNR is determined, the post processing SNR is only determined by $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$.
-From the heuristic in \cite{barbero2008fixing}, for the FE stage the robustness of detector performance is not influenced by the post processing SNR.
-Thus at FE stage the "weakest" data stream, that is, the data stream with the smallest $\varphi$, is detected first.
-At SE stage, because of the single searching path branch of the node, the performance is tightly related to the post processing SNR.
-Therefore at SE stage the data streams with the larger post processing SNR is detected first in order to avoiding error propagation.
+where $\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, and $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inverse of $\mathbf{H}^{H}\mathbf{H}$.
+The post processing SNR depends only on $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$.
+From \cite{barbero2008fixing}, at the FE stage the "weakest" data stream, that is the data stream with the smallest $\varphi_{m}$, is detected first.
+At the SE stage, because of the single searching branch of the node, the performance is tightly related to the post processing SNR.
+Therefore at the SE stage the data stream with the largest post processing SNR is detected first in order to avoiding error propagation.
 In conclusion the FCSD ordering works iteratively  and obeys the following rule:
 at the $j$th step ($j=1,2\dots N_{t}-1$), $s_{p}$ denotes the symbol to be detected, where 
-\begin{displaymath}
+\begin{equation}
 p=\left\lbrace \begin{array}{c}
-arg \max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE\quad stage\\
-arg \min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE\quad stage   \label{the ordering}
+arg\max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE\quad stage\\
+arg\min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE\quad stage   \label{the ordering}
 \end{array}\right.  
-\end{displaymath}  
-and $\mathbf{H}_{j}\in \mathbb{C}^{N_{r}\times (N_{t}-j+1)}$ denotes the renewed channel matrix.
-At the $j$th iteration with the column corresponding to previous detected data streams removed from $\mathbf{H}_{j-1}$.
+\end{equation}  
+and $\mathbf{H}_{j}\in \mathbb{C}^{N_{r}\times (N_{t}-j+1)}$ denotes the renewed channel matrix with the column corresponding to previous detected data streams removed from $\mathbf{H}_{j-1}$.
 
-As mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle-achieving performance with a mix of CPU and GPU technology, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
-Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational consumptive operations can be performed by the CUDA Basic Linear Algebra Subprograms(cuBLAS)\cite{nvidia2013basic} and corresponding GPU program implementations, as shown in table \ref{table1}.
+As mentioned in section \ref{programming model}, our implementation is based on the heterogeneous programming principle, employing a mix of CPU and GPU technology.
+The flow control and logical operations reside at the host side, while the compute intensive work is implemented at the device side.
+Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational intensive operations can be performed by the CUDA Basic Linear Algebra Subprograms (cuBLAS)\cite{nvidia2013basic} and corresponding GPU program implementations, as shown in Table \ref{table1}.
 \begin{table*}[htb]
 \centering
+\caption{Parallel Computation Operation of FCSD Preprocessing}
 \begin{tabular}{|c|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
 \hline
-Operations & complex matrix-matrix multiplication & complex matrix-vector multiplication & matrix inverse & cholesky factorization \\
+Operations & complex matrix-matrix multiplication & complex matrix-vector multiplication & matrix inverse & Cholesky factorization \\
 \hline
@@
 
-Figure \ref{block diagram} illustrates the block diagram of the CUDA-FCSD implementation. 
+\subsection{Parallel Acceleration of Paths Searching}
+Since the decision feedback searching paths have a serial nature, we match one path to one thread.
+In order to have the largest number of threads that can be parallelized, we use one dimensional blocks for widest expansion, and organize all the paths into several such blocks.
+For example for a $16\times 16$ MIMO system with $16$QAM, the number of paths we need to search is $M^{\rho}=16^{3}=4096$, since $\rho=\lceil \sqrt{N_{t}}-1\rceil$, where $\lceil x\rceil$ represent the smallest integer greater than or equal to $x$.
+For largest SM occupancy we use 4 blocks for the path searching kernel where each block has 1024 threads which is the maximum number allowed per block.
+At each FCSD searching path, the following operations are performed in one thread:
+\begin{itemize}
+\item \emph{Path searching}\\
+As in (\ref{FCSD solution}).
+\item \emph{Euclidean Distance Calculation}
+\begin{equation}
+E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s}_{j}-s^{F}_{j}), \label{Eu metric}
+\end{equation}
+\end{itemize}
+where $E_{u}^{k}$ denotes the Euclidean distance of the $k$th symbol vector candidate.
+We integrate the post processing (\ref{Eu metric}) into the path searching process (\ref{FCSD solution}) to reduce the iteration times per thread.
+
+In order to avoid low speed host-device data transfer, we reduce data transfers as much as possible.
+As shown in Fig.
+\ref{block diagram} we perform data transfer only two times.
+For host to device, the propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$, as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage, are transferred.
+For device to host, the FCSD symbol vector solution $\mathbf{s}^{F}$ is transferred.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{CUDA_FCSD_block_diagram.eps}
+\includegraphics[width=0.5\textwidth, height=5.1cm]{CUDA_FCSD_block_diagram.eps}
 \caption{Block Diagram of CUDA-FCSD Implementation}
@@
 \end{figure}
-\subsection{Parallel Acceleration of Blocked-Paths Searching}
-The decision feedback searching paths have serial nature, we match one path to one thread.
-In order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks.
-For example We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the number of path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt{N_{t}}-1\rceil$, where $\lceil x\rceil$ represent the smallest integer larger than $x$, for largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads which is the maximum number of thread allowing per block.
-At each FCSD searching path, the following data operation is performed in one thread:\\
-1. \emph{Path searching}\\
-According to (\ref{FCSD solution}).
-2. \emph{Euclidean distance Calculation}\\
-\begin{equation}
-E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s}_{j}-s_{j})\label{Eu metric}
-\end{equation}
-$E_{u}^{k}$ denotes the $k$th Euclidean distance of the corresponding symbol vector candidate.
-Loop fusion is applied, we integrate the post processing (\ref{Eu metric}) into path searching process (\ref{FCSD solution}) to reduce the iteration times per thread.
 \subsubsection{Data Preparation}\label{data preparation}
-There are three major factors that will influence the configuration of the data sets configuration in memory space.\\
-1. Amount of Reading$\&$Writing (R/W) operation per thread.\\
-2. Valid scope\\
-3. Storage occupancy
+There are three major factors that influence the configuration of the data sets in memory space.
+\begin{itemize}
+\item Number of Reading Writing (R/W) operations
+\item Valid program scope
+\item Storage occupancy
+\end{itemize}
 
-Unlike CPUs that have a flat memory model meaning the CPU core can access any memory location without restriction, GPUs are computation intensive and only have small cache for special memory space (texture, constant).
-Thus the memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influences the application performance.
-Different memory types has different valid scope, local memory which is invoked in kernel function is valid only in one thread, share memory is valid in one block, constant, texture and global memory are valid both at host side and device side.
-On the other hand different from global memory (2047 MBytes in GeForce GTX 760), the constant and share memory are all capacity limited (only $65536$ bytes totally and $49152$ bytes per block in GeForce GTX 760).
-Thus the occupancy of memory is one determinant factor needed to be considered.
+Unlike CPUs that have a flat memory model (the CPU core can access any memory location by a near clock rate speed) GPUs are computation intensive.
+Thus the memory R/W operations are time consuming that influence performance.
+Furthermore different memory types have different program scopes.
+Local memory, which is invoked in \textit{kernel} functions is valid only in one thread.
+Shared memory is valid in one block.
+Constant, texture and global memories are valid both at host side and device side.
+On the other hand different from global memory, the constant and share memory are all capacity limited.
+Thus the memory occupancy is an important factor that needs to be considered.
 
-At host side we set 4 data sets that are stored in global memory which are storage consumptive and must have valid scope for both host and device side, $\mathit{s_{pm}}$ is a $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope should be during the whole $\mathit{kernel}$ execution.
-$\mathit{s_{index}}$ is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.
-$\mathit{E_{u}}$ is a $M^{\rho}$ floating point vector that is used to store the Euclidean distance of all the symbol vector candidates.
-$\mathit{s_{kernel}}$ is a complex vector used to store the FCSD solution which length is $N_{t}$ and has to be transferred to host side.
+At the host side we set four data sets that are stored in global memory.
+The $M^{\rho}\times N_{t}$ complex matrix $\mathit{s_{pm}}$ that stores in each row one symbol vector candidate and its program scope should be during the whole \textit{kernel} execution.
+The matrix $\mathit{s_{index}}$ is used to store the index of all the possible sub-symbol vectors for  FE stage using the full factorial method and requires a $\rho\times M^{\rho}$  integer matrix space.
+The $M^{\rho}$ dimensional floating point vector is used to store the Euclidean distance of all the symbol vector candidates.
+The $N_{t}$ dimensional complex vector $\mathit{s_{kernel}}$ is used to store the FCSD solutions and has to be transferred to host side.
 
-On the other hand, upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\mathbf{\hat{s}}$ in (\ref{unconstrained estimation}) are read only and require large amount of read operations.
-(for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\mathbf{\hat{s}}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\mathbf{\hat{s}}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section \ref{programming model}, the constant memory is cached so that it is much faster than global memory.
+On the other hand, the upper triangular matrix $\mathbf{R}$ and the unconstrained estimator $\mathbf{\hat{s}}$ of (\ref{unconstrained estimation}) are read only and require large numbers of read operations.
+Since these two data sets need small sizes of storage, the constant memory, which is cached and read only, is used to store them.
+\subsubsection{Memory Accesss Pattern}
+When considering a large MIMO system, the large number of required R/W operations make the memory bandwidth a major bottleneck for performance.
+Although the off-chip memory theoretical bandwidth is extremely high (the theoretical bandwidth of GeForce GTX 760 is 192GB/s), in practice it can only be achieved by a proper R/W strategy.
 
-In table \ref{amountofR/Woperations}  we present the amount of R/W operations and the storage that needed for different data variables in FCSD path searching.
-The amount of the R/W operation is calculated based on the (\ref{path searching}) and (\ref{Eu metric}), for complex values ($\mathbf{R}$ $\mathbf{\hat{s}}$, $\mathit{s_{pm}}$, $\mathit{s_{kernel}}$ ) are stored using CUDA build in variable data type $\mathit{cuComplex}$ which counts 8 bytes.
-Floating point data set $E_{u}$ is stored using variable type $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored using variable type $\mathit{int}$, which counts 1 byte.\\
- \begin{table*}[htb]  
- \centering
-\begin{tabular}{|l|l|l|l|l|l|l|}
-\hline
-data & $\mathbf{R}$ & $\mathbf{\hat{s}}$ & $\mathit{s_{pm}}$ & $\mathit{s_{index}}$ & $\mathit{E_{u}}$ & $\mathit{s_{kernel}}$ \\
-\hline
-R/W operations/thread & $(\frac{3}{2}(N_{t})^{2}-\frac{N_{t}}{2}+\rho-\rho^{2})$ & $(\frac{2(N_{t})^{2}+2N_{t}-\rho^{2}-\rho}{2})$ & $N_{t}$ & $\rho$ &$N_{t}$ & $N_{t}$ \\
-\hline
-Storage/bytes  & $4(N_{t}+1)N_{t}$ & $8N_{t}$ & $8M^{\rho}N_{t}$ & $N_{t}M^{\rho}$ & $4N_{t}M^{\rho}$ & $8N_{t}$\\
-\hline  
-\end{tabular} 
- \caption{Amount of R/W Operations and Storage Requirement of Different Data Set}
-  \label{amountofR/Woperations} 
-\end{table*}  
-\subsubsection{Memory Accesss Pattern}
-When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.
-
-Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W operations are performed by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible.
-For the GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Figure \ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{pm}}$ as an example to illustrate how we coalesce the the global memory.
+Global memory access is implemented by a dynamic random access memory (DRAM) whose R/W is an extremely slow process.
+In a modern DRAM the R/W operations are performed by accessing a piece of consecutive memory location.
+As mentioned in section \ref{programming model}, the warp is the basic schedule unit of a device, and memory space is accessed warp by warp.
+Thus the most effective global memory access pattern is to ensure a warp of threads can access a consecutive memory space.
+For the GeForce GTX 760, the DRAM will access a consecutive memory space of 128 bytes at one time.
+In Fig.
+\ref{coalesce global memory} we present the global access pattern of $\mathit{s_{pm}}$ as an example to illustrate global memory access pattern.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{coalescing_global_memory.eps}
+\includegraphics[width=0.5\textwidth, height=8cm]{coalescing_global_memory.eps}
 \caption{Global Memory Access Pattern of $\mathit{s_{pm}}$}
@@
 \end{figure}
-We store $\mathit{s_{pm}}$ in one pitch of linear global memory, with each row store one $N_{t}=16$ complex symbol vector solution candidate of $\mathbf{\hat{s}}^{F}$ in (\ref{formula 5}), totally there are $M^{\rho}=4096$ rows, this matrix is stored in column major.
-As mentioned before one path searching is performed by one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256$ bytes, counts for two times of DRAM access.
 
-As we mentioned in section (\ref{programming model}), the registers are allocated to the threads dynamically and have much faster access speed than that of global memory.
-Therefore, for all the transient data that used for accumulator in (\ref{path searching}), (\ref{Eu metric}), and the symbol vector candidate during the path searching process of each thread, are stored temporarily in registers to hide the latency of R/W of global memory.
-\subsubsection{Data Transfer Minimization}   
-The data transfer between the host and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $\mathbf{y}$ in (\ref{formula 1}) as well as the sub symbol vector index list $\mathit{s_{index}}$ at FE stage.
+The complex matrix $\mathit{s_{pm}}$ is stored in one piece of linear global memory, where each row represents one $N_{t}$ complex symbols solution candidates of $\mathbf{\hat{s}}^{F}$ in (\ref{formula 5}).
+There are $M^{\rho}$ rows, and this matrix is stored in column major (first column in the first piece of memory space and the second in the second piece of memory space etc.).
+As mentioned before, one path searching is performed by one thread, and therefore the address distance between two consecutive symbols in one thread is $M^{\rho}$.
+However for consecutive threads in one warp, the address they reach is continuous as shown in Fig.
+\ref{coalesce global memory}.
+Every 32 threads in one warp can confirm R/W operations to a piece of memory that is consecutive, and reduce DRAM access as much as possible resulting in a better memory bandwidth.
+
+All the thread level temporary data that is used in (\ref{FCSD solution}), (\ref{Eu metric}), and the symbol vector candidate during the path searching process, are stored in registers to get near clock rate access speed.
+
 \subsection{Larger MIMO Systems and Constellation Sizes}
-Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, the path number that need to be searched is $M^{\rho}=16^{5}=1048576$.
-The maximum number of threads that can be execute in $\mathit{kernel}$ function of the GeForce GTX 760 is 12288, therefore we need to consider execute the $\mathit{kernel}$ function in loop, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
-Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the $\mathit{kernel}$ function for 86 times and get the final solution,  when it comes to the large MIMO systems and large signal constellations such as $36\times 36$ $16$QAM, $144\times 144$ $4$QAM, $20\times 20$ $64$QAM, the global memory that need to used to store $s_{pm}$ in section (\ref{data preparation}) will out of bound (2 GB), multiple kernels with each one deal with a small subset of symbol vector candidates and kernel concurrency\cite{nvidia2008programming} can be applied to solve this problem.
+There are two problems that need to be considered for large MIMO systems and constellation size:
+\begin{itemize}
+\item Thread resource limitation:
+The number of threads that can be executed in parallel is limited.
+When the size of a MIMO system and constellation increases, it becomes impossible to parallelize all the searching paths in one \textit{kernel} execution.
+For example, in a $32\times 32$ MIMO system with $16$QAM modulation, the number of paths that need to be searched is $M^{\rho}=16^{5}=1048576$.
+\item Global memory limitation:
+Large MIMO systems and large signal constellations require a large global memory space to store the symbol vector candidates.
+For example, for the systems $36\times 36$ with $16$QAM, $144\times 144$ with $4$QAM, $20\times 20$ with $64$QAM, the required space of storing $s_{pm}$ of section \ref{data preparation} exceeds the limit (2 GB).
+\end{itemize}
+
+One solution to these problems is to employ partial parallelism.
+The detection task is divided into several \textit{kernel} executions, where for each, only one potential symbol vector solution, as well as its corresponding Euclidean distance are preserved.
+This allows the global memory space to be reused to avoid exceeding its limit.
 \section{Simulation Results}\label{simulation}
@@
 \subsubsection{Device}
-\emph{Graphic Processing Units}: GeForce GTX 760, GPU clock rate: 1.08 GHz , memory clock rate: 3 GHz , number of SM: 6, maximum number of threads per stream multiprocessor: 2048, total amount of global memory: 2 GB, total amount of share memory per block: 49 KB, total amount of constant memory: 66 KB.
-\\
-\emph{Central Processing Units-Modigliani}: Intel Core i5-4th generation, 4 cores 3.20 GHz CPU clock rate, 8 GB RAM\\
-\emph{Central Processing Units-Monet} : Intel Core i7-3rd generation, 12 cores 3.20 GHz CPU clock rate, 32 GB RAM
+\begin{itemize}
+\item \emph{Graphic Processing Units}: GeForce GTX 760, GPU clock rate: 1.08 GHz , memory clock rate 3 GHz , number of SM 6, maximum number of threads per stream multiprocessor 2048, total amount of global memory 2 GB, total amount of share memory per block 49 KB, total amount of constant memory 66 KB.
+\item \emph{Central Processing Units-Modigliani}: Intel Core I5-4th generation, 4 physical cores, 3.20 GHz CPU clock rate, 8 GB RAM.
+\item \emph{Central Processing Units-Monet} : Intel Core I7-3rd generation, 6 physical cores, 3.20 GHz CPU clock rate, 32 GB RAM.
+\end{itemize}
 \subsubsection{Software}
-CUDA Driver Version / Runtime Version      6.5 / 6.0\\
-Nsight Eclipse Version 6.5
-\subsection{Performance and Evaluation}
+\begin{itemize}
+\item CUDA Driver Version / Runtime Version      6.5 / 6.0
+\item Integrated software environment for source code editing, automatic building and debugging: Nsight Eclipse Version 6.5
+\end{itemize}
+\subsection{Performance Evaluation}
 \begin{table*}[htb]
 \centering
+\caption{ Speedup Performance of Different MIMO Systems using 4 QAM}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 \cline{2-6}
-&GeForce GTX 760 & Modigliani & Monet &  GTX 760/Modigliani  &  GTX 760/Monet \\
+&GeForce GTX 760 & Modigliani & Monet &  $\vartheta_{GTX 760}/\vartheta_{Modigliani}$  & $\vartheta_{GTX 760}/\vartheta_{Monet}$ \\
 \hline
@@
 \centering
+\caption{ Speedup Performance of Different MIMO Systems using 16 QAM}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 \cline{2-6}
-&GeForce GTX 760 & Modigliani & Monet &  GTX 760/Modigliani  &  GTX 760/Monet \\
+&GeForce GTX 760 & Modigliani & Monet &  $\vartheta_{GTX 760}/\vartheta_{Modigliani}$  &  $\vartheta_{GTX 760}/\vartheta_{Monet}$ \\
 \hline
@@
 \end{tabular}
-\caption{speedup performance of different MIMO systems using 16 QAM}
 \label{speedup2}
 \end{table*}
-\begin{table*}[h]
+\begin{table*}[htb]
 \centering
+\caption{Speedup Performance of Different MIMO Systems using 64 QAM}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 $16\times 16$&468.92 & 2066.08&2689.00& 4.41& 5.73\\
-
 \hline
-
 \end{tabular}
-\caption{speedup performance of different MIMO systems using 64 QAM}
 \label{speedup3}
 \end{table*}
+Monte-Carlo simulations were conducted for MIMO systems of different sizes and signal constellation.
+In this work the speedup is defined as $\vartheta_{GPU}/\vartheta_{CPU}$, where $\vartheta_{GPU}$ and $\vartheta_{CPU}$ denotes the number of symbols detected on GPU and CPU per second.
+Comparison is made between the GeForce GTX 760 and two types of CPUs, with speedup performance presented in Tables \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
+All the operation times correspond to $1000$ channel realizations.
 
-We made simulation to different sizes MIMO systems and signal constellation and comparison is made between the Geforce GTX 760 and two kinds of CPU, the speedup performance is presented in table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
-All the operation times we test is based on $1000$ channel realizations, the transmitted data is generated randomly and modulated by $M$ quadrature amplitude modulation (QAM) scheme.
+From Table \ref{speedup1}, we see that for small MIMO systems of $8\times 8$, $16\times 16$, and $32\times 32$ with $4$QAM, the speed performance of GPU implementation is worse than that of CPU.
+The number of paths of these MIMO configurations that need to be searched is relatively small\footnote{$8\times 8$ MIMO system with $4$QAM has $16$ paths, $16\times 16$ MIMO system with $4$QAM has $64$ paths and $32\times 32$ MIMO system with $4$QAM has $1024$ paths}.
+The CPUs are designed for serial code execution with special hardware (branch prediction units, multiple caches, etc.) that provide extremely good performance, while the GPUs can achieve good performance only when they are utilized in a massive parallel manner.
+Furthermore there is a short time for GPU to "warm up", for host-device data transmission, \textit{kernel} function  launching and host device synchronization.
+When comes to larger MIMO systems of $48\times 48$, $64\times 64$, $72\times 72$, a large parallelism is achieved allowing the GPU to begin displaying its data processing power.
 
-In table \ref{speedup1}, for small MIMO systems $8\times 8$ and $16\times 16$, the speed performance of GPU implementation is even worse than that of CPU.
-The number of path of these antenna configurations that need to be searched is relatively small ($16$ for $8\times 8$ system and $64$ for $16\times 16$ system), the CPU implementation has already had a good performance, the CPUs are designed for serial code execution with the special hardwares (branch prediction units, multiple caches, etc) and have extremely good performance at it, however the GPUs can achieve a good performance only when they are utilized in parallel manner, there is a short time for GPU to "warm up", for host-device data transmission, launch kernel function and host device synchronization.
-Furthermore, for small number of threads, the memory R/W latency is not well hided.
-For the $32\times 32$ systems, the speed performance of GPU and CPU implementation is close, when comes to larger MIMO systems $48\times 48$, $64\times 64$, $72\times 72$, a large parallelism is achieved so that the GPU begin to display its data processing power, the speedup can be from $2.50$ to $4.20$.
+In Tables \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM are considered.
+We see that speedups larger than 1 can be achieved with GPU implementation also with smaller MIMO systems.
+For a $16\times 16$ system with $16$QAM modulation, GTX 760 provides a $1.18$ speedup over Modigliani and $1.57$ speedup over Monet.
+For a $16\times 16$ system with $64$QAM, GTX 760 provides a $4.41$ speedup over Modigliani and $5.73$ speedup over Monet.
+The nature of FCSD is such that for lager signal constellations, massive parallelism can be reached also for small MIMO systems that are not extremely large.
 
-In table \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM are considered, the speedup of GPU implementation is reached from a small MIMO size, For $16\times 16$ system using $16$QAM $1.18$ speedup over Modigliani and $1.57$ speedup over Monet.
-For $8\times 8$, $64$QAM, $0.87$ speedup over Modigliani and $1.09$ speedup over Monet.
-For lager signal constellation, the massive parallelism can be reached for relatively small MIMO systems.
+It can be observed from Tables \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, that the GPU implementation shows its speed advantage over CPU implementation for increasing size of MIMO systems and signal constellations, indicating that GPUs provide advantages for large MIMO system with large signal constellations.
 
-It can be observed from table \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, GPU implementation shows its speed advantage over CPU implementation for increasing size of MIMO systems and signal constellations, indicating this GPU implementation's suitability for large MIMO system and large signal constellation.
-\begin{figure}[h]
+In Fig.
+\ref{BER curve} we present Monte Carlo simulation results for bit error rate (BER) performance, using the GPU implementation of different MIMO system configurations and constellation sizes.
+We consider uncoded complex MIMO systems with $M$QAM, where each antenna transmits different streams of binary data generated randomly and independently.
+The results have been obtained by using $100000$ channel realizations with at least $500$ symbol errors accumulated.
+The simulation results show that FCSD-CUDA provides the same BER performance as its CPU version\cite{barbero2008fixing}.
+\begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{BER_curves.eps}
-\caption{BER performance of different sizes of MIMO systems and modulation scheme by GPU}
+\includegraphics*[width=0.56\textwidth]{BER_curves.eps}
+\caption{BER performance for MIMO systems with various modulation schemes using the GPU implementation}
 \label{BER curve}
 \end{figure}
-Figure \ref{BER curve} shows the Monte Carlo simulation results of bit error rate (BER) performance for different MIMO systems and constellation sizes, we consider uncoded spatial multiplexing MIMO systems, the transmitted binary sequence is generated randomly and  mutually independent, modulated by $M$-QAM modulation scheme, the results have been obtained using $100000$ channel realizations and $500$ symbol errors accumulated.
-\section{Conclusion}\label{conclusion}
-This paper presents the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional computation platform.
-In order to exploit the computational capability of GPU in the simulation of large MIMO systems, the utilization of heterogeneous programming model, thread resource limitation and memory configuration are considered in a comprehensive way.
-The simulation shows considerable acceleration of GPU implementation of FCSD can be reached for large MIMO systems and large signal constellation sizes while the same BER performance can be obtained.
-In addition, the GPU and CPU can work independently, the data processing power of GPU computing is an extra bonus of the traditional simulation platform.
-This shows the potential of GPU computing for computational consumptive simulation in large MIMO area.
-The future work contains taking into consider the kernel execution and data transferring concurrence in order to optimize memory allocation strategy for large MIMO systems.
+\section{Conclusions}\label{conclusion}
+This paper presents a GPU implementation of the fixed complexity sphere decoder (FCSD) for large MIMO systems.
+In order to exploit the computational capability of GPU in the simulation of large MIMO systems, the utilization of a heterogeneous programming model, accounting for resource limitations and memory configuration must be considered.
+The simulation results show that a considerable acceleration of the GPU implementation of FCSD can be reached for large MIMO systems and signal constellation sizes over CPU implementation, while maintaining the same BER performance.
+Since the GPU and CPU can work independently, the data processing power of GPU computing is an additional advantages provided by the traditional simulation platforms.
+This shows the potential of GPU computing to reduce the time associated with intensive simulations of large MIMO systems.
+
 % conference papers do not normally have an appendix

### 2015-02-02 FCSD-CUDA project/parallel_acceleration_of_FCSD_based_on_cuda/ccece-latex-sample.tex
revised version after acceptance 1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

%\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
%\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
Preparation of Papers for IEEE Sponsored Conferences \& Symposia
}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Huibert Kwakernaak and Pradeep Misra% <-this % stops a space
\thanks{This work was not supported by any organization}% <-this % stops a space
\thanks{H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small h.kwakernaak@autsubmit.com}}%
\thanks{P. Misra is with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small pmisra@cs.wright.edu}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

These instructions provide basic guidelines for preparing camera-ready (CR)
Proceedings-style papers. This document is itself an example of the
desired layout for CR papers (inclusive of this abstract). The document
contains information regarding desktop publishing format, type sizes, and
type faces. Style rules are provided that explain how to handle equations,
units, figures, tables, references, abbreviations, and acronyms. Sections
are also devoted to the preparation of the references and acknowledgments.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

Your goal is to simulate, as closely as possible, the usual appearance of typeset
 papers. This document provides an example of the desired layout and contains
 information regarding desktop publishing format, type sizes, and type faces.

\subsection{Full-Size Camera-Ready (CR) Copy}

If you have desktop publishing facilities, (the use of a computer to aid
 in the assembly of words and illustrations on pages) prepare your CR paper
  in full-size format, on paper 21.6 x 27.9 cm (8.5 x 11 in or 51 x 66 picas).
  It must be output on a printer (e.g., laser printer) having 300 dots/in, or
  better, resolution. Lesser quality printers, such as dot matrix printers,
   are not acceptable, as the manuscript will not reproduce the desired quality.

\subsubsection{Typefaces and Sizes:} There are many different typefaces and a large
variety of fonts (a complete set of characters in the same typeface, style,
 and size). Please use a proportional serif typeface such as Times Roman,
 or Dutch. If these are not available to you, use the closest typeface you
  can. The minimum typesize for the body of the text is 10 point. The minimum
  size for applications like table captions, footnotes, and text subscripts
  is 8 point. As an aid in gauging type size, 1 point is about 0.35 mm (1/72in).
   Examples are as follows:

\subsubsection{Format:} In formatting your original 8.5" x 11" page, set top and
bottom margins to 25 mm (1 in or 6 picas), and left and right margins
to about 18 mm (0.7 in or 4 picas). The column width is 88 mm (3.5 in or 21 picas).
 The space between the two columns is 5 mm(0.2 in or 1 pica). Paragraph
 indentation is about 3.5 mm (0.14 in or 1 pica). Left- and right-justify your
 columns. Cut A4 papers to 28 cm. Use either one or two spaces between sections,
 and between text and tables or figures, to adjust the column length.
  On the last page of your paper, try to adjust the lengths of the
  two-columns so that they are the same. Use automatic hyphenation and
   check spelling. Either digitize or paste your figures.

\begin{table}
\caption{An Example of a Table}
\label{table_example}
\begin{center}
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{UNITS}

Metric units are preferred for use in IEEE publications in light of their
international readership and the inherent convenience of these units in many fields.
In particular, the use of the International System of Units (SI Units) is advocated.
 This system includes a subsystem the MKSA units, which are based on the
 meter, kilogram, second, and ampere. British units may be used as secondary units
 (in parenthesis). An exception is when British units are used as identifiers in trade,
 such as, 3.5 inch disk drive.

\addtolength{\textheight}{-3cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ADDITIONAL REQUIREMENTS}

\subsection{Figures and Tables}

Position figures and tables at the tops and bottoms of columns.
Avoid placing them in the middle of columns. Large figures and tables
may span across both columns. Figure captions should be below the figures;
 table captions should be above the tables. Avoid placing figures and tables
  before their first mention in the text. Use the abbreviation ``Fig. 1'',
  even at the beginning of a sentence.
Figure axis labels are often a source of confusion.
Try to use words rather then symbols. As an example write the quantity ``Inductance",
 or ``Inductance L'', not just.
 Put units in parentheses. Do not label axes only with units.
 In the example, write ``Inductance (mH)'', or ``Inductance L (mH)'', not just ``mH''.
 Do not label axes with the ratio of quantities and units.
 For example, write ``Temperature (K)'', not ``Temperature/K''.

\subsection{Numbering}

Number reference citations consecutively in square brackets \cite{c1}.
 The sentence punctuation follows the brackets \cite{c2}.
 Refer simply to the reference number, as in \cite{c3}.
 Do not use ``ref. \cite{c3}'' or ``reference \cite{c3}''.
Number footnotes separately in superscripts\footnote{This is a footnote}
Place the actual footnote at the bottom of the column in which it is cited.
Do not put footnotes in the reference list.
Use letters for table footnotes (see Table I).

\subsection{Abbreviations and Acronyms}

Define abbreviations and acronyms the first time they are used in the text,
even after they have been defined in the abstract. Abbreviations such as
IEEE, SI, CGS, ac, dc, and rms do not have to be defined. Do not use
abbreviations in the title unless they are unavoidable.

\subsection{Equations}

Number equations consecutively with equation numbers in parentheses flush
 with the right margin, as in (1). To make your equations more compact
 you may use the solidus (/), the exp. function, or appropriate exponents.
  Italicize Roman symbols for quantities and variables, but not Greek symbols.
   Use a long dash rather then hyphen for a minus sign. Use parentheses to avoid
    ambiguities in the denominator.
Punctuate equations with commas or periods when they are part of a sentence:
$$\Gamma_2 a^2 + \Gamma_3 a^3 + \Gamma_4 a^4 + ... = \lambda \Lambda(x),$$
where $\lambda$ is an auxiliary parameter.

Be sure that the symbols in your equation have been defined before the
equation appears or immediately following.
Use ``(1),'' not ``Eq. (1)'' or ``Equation (1),''
except at the beginning of a sentence: ``Equation (1) is ...''.

   \begin{figure}[thpb]
      \centering
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONCLUSIONS AND FUTURE WORKS}

\subsection{Conclusions}

This is a repeat.
Position figures and tables at the tops and bottoms of columns.
Avoid placing them in the middle of columns. Large figures and tables
may span across both columns. Figure captions should be below the figures;
 table captions should be above the tables. Avoid placing figures and tables
  before their first mention in the text. Use the abbreviation ``Fig. 1'',
  even at the beginning of a sentence.
Figure axis labels are often a source of confusion.
Try to use words rather then symbols. As an example write the quantity ``Inductance",
 or ``Inductance L'', not just.
 Put units in parentheses. Do not label axes only with units.
 In the example, write ``Inductance (mH)'', or ``Inductance L (mH)'', not just ``mH''.
 Do not label axes with the ratio of quantities and units.
 For example, write ``Temperature (K)'', not ``Temperature/K''.

\subsection{Future Works}

This is a repeat.
Position figures and tables at the tops and bottoms of columns.
Avoid placing them in the middle of columns. Large figures and tables
may span across both columns. Figure captions should be below the figures;
 table captions should be above the tables. Avoid placing figures and tables
  before their first mention in the text. Use the abbreviation ``Fig. 1'',
  even at the beginning of a sentence.
Figure axis labels are often a source of confusion.
Try to use words rather then symbols. As an example write the quantity ``Inductance",
 or ``Inductance L'', not just.
 Put units in parentheses. Do not label axes only with units.
 In the example, write ``Inductance (mH)'', or ``Inductance L (mH)'', not just ``mH''.
 Do not label axes with the ratio of quantities and units.
 For example, write ``Temperature (K)'', not ``Temperature/K''.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ACKNOWLEDGMENTS}

The authors gratefully acknowledge the contribution of National Research Organization and reviewers' comments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

\begin{thebibliography}{99}

\bibitem{c1}
J.G.F. Francis, The QR Transformation I, {\it Comput. J.}, vol. 4, 1961, pp 265-271.

\bibitem{c2}
H. Kwakernaak and R. Sivan, {\it Modern Signals and Systems}, Prentice Hall, Englewood Cliffs, NJ; 1991.

\bibitem{c3}
D. Boley and R. Maier, "A Parallel QR Algorithm for the Non-Symmetric Eigenvalue Algorithm", {\it in Third SIAM Conference on Applied Linear Algebra}, Madison, WI, 1988, pp. A20.

\end{thebibliography}

\end{document}

### 2015-02-02 FCSD-CUDA project/parallel_acceleration_of_FCSD_based_on_cuda/SNR_BER_new.m

@@ -1,0 +1,43 @@
+%this is for ploting the figure of SNR-BER curve
+sim8_4_0_12=[0.22589062154, 0.15894874930, 0.08640749753, 0.03090812452, 0.00636250013, 0.00079124997, 0.00005481876,0.00000279009];
+sim8_16_0_16=[0.25537124276, 0.22414547205, 0.19270686805, 0.15720969439, 0.10538093746, 0.04198125005, 0.00701593747, 0.00052656251,0.00004961727, 0.00000235999];
+sim8_64_0_24=[0.30989542603, 0.28304228187, 0.25555500388, 0.22751520574, 0.19991666079, 0.16876062751, 0.12789249420, 0.07114583254, 0.02219000086, 0.00312604173, 0.00018895834,0.00000633392 ];
+sim16_4_0_6=[0.23751124740, 0.17347000539, 0.09674874693, 0.03350968659, 0.00618375000, 0.00060968747, 0.00002066603  ];
+sim16_16_0_12=[0.25537124276, 0.22414547205, 0.19270686805, 0.15720969439, 0.10538093746, 0.04198125005, 0.00701593747, 0.00052656251,0.00002031656];
+sim32_4_0_4=[0.24545359612, 0.18672686815, 0.11097452790, 0.04044124857, 0.00811937544, 0.00093781250,0.00005755865];
+sim48_4_0_4=[0.25442603230, 0.19931979477, 0.12637500465, 0.05224249884, 0.01231614593, 0.00185479166, 0.00016166667,0.00000549426];
+
+fig1=figure;
+Xsize=12;Ysize=11;
+%Xleft=(8-Xsize)/2;Ytop=(12-Ysize)/2;
+Xleft=0;
+Ytop=0;
+set(gcf,'Units','inches');
+set(gcf,'position', [Xleft,Ytop,Xsize,Ysize]);
+set(gcf,'PaperUnits','inches');
+set(gcf,'PaperPosition',[Xleft+0.8,Ytop,Xsize,Ysize]);
+set(gca,'fontsize',25);
+
+figure (1)
+fig1=semilogy(0:2:14,sim8_4_0_12,'-*k','MarkerSize',23,'LineWidth',1.5);xlabel('SNR per bit (dB)'),ylabel('BER');
+hold on;
[…]

### 2015-02-04 FCSD-CUDA project/The final draft of CUDA paper/conf_draft/conference draft.tex
Revise after acceptance version 2

--- 2015-01-05 Parallel Acceleration of Fixed Complexity Sphere Decoder Based on GPU/conf_draft/conference draft.tex
@@
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}
-\documentclass[letterpaper, 10pt, conference]{ieeeconf}
+\documentclass[letterpaper, 10pt, conference,twoside]{ieeeconf}
 %\documentclass[12pt,a4paper,final]{article}
@@
 \usepackage{fancyhdr}
+\usepackage{lastpage}
 % Some very useful LaTeX packages include:
@@
                       % 导致第一页什么都没有。所以得把plain更改为fancy
+%\fancyhead{\thepage} % 奇数页右侧，偶数页左侧显示页码 
 \lhead{} % 页眉左，需要东西的话就在{}内添加  
 \chead{} % 页眉中  
-\rhead{\thepage} % 页眉右  
+\rhead{} % 页眉右  
 \lfoot{} % 页眉左  
@@
 \pagestyle{fancy}  
-\rhead{\thepage}
+\fancyhead[RO,LE]{\thepage}  
+%\rhead{\thepage}
 %\thispagestyle{empty}
@@
 This paper considers the implementation of a Fixed Complexity Sphere Decoder (FCSD) for large scale MIMO systems using the framework of GPGPU-Computed Unified Device Architecture (CUDA).
-The proposed CUDA-FCSD can achieve considerable speedups over conventional CPU implementation while providing the same Bit Error Rate (BER) performance.
-Furthermore the proposed algorithm demonstrates the great potential of GPGPU to accelerate the simulation of large MIMO systems.
+Significant speedups were formed for large MIMO systems and constellation sizes over conventional CPU implementation while providing the same Bit Error Rate (BER) performance, hence the proposed algorithm provides great potential for GPGPU to accelerate the simulation of large MIMO systems.
 
@@
 
-General Purpose Graphic Processing Units (GPGPU) computing is a common trend in industry and research in areas that need massive computations, such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435}, and finance\cite{grauer2013accelerating}.
+General Purpose Graphic Processing Units (GPGPU) computing is a common trend in industry and research in areas that need massive computations.
 Compared to a CPU, a GPU can naturally cope with computational intensive tasks, since most of the hardware resources are allocated for data processing and parallel computation, rather than caching and flow control\cite{cook2013cuda}.
 In recent years GPU computing has provided significant advantages in data processing speeds over CPU computations\cite{nvidia2008programming}.
+GPU computing has been applied to different research fields such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435}, and finance\cite{grauer2013accelerating}.
 The Computed unified Device Architecture (CUDA)\cite{cook2013cuda}\cite{nvidia2008programming} is a programming model for GPGPU that was proposed by NIVIDIA and has become the dominant framework for GPGPU programming.
@@
 
-In this paper, a GPU based implementation of Fixed Complexity Sphere Decoder (FCSD) is proposed, which is referred to as CUDA-FCSD.
+ \cite{hongyuan2010fixed} presents an interesting implementation of Fixed Complexity Sphere Decoder (FCSD) based on GPU, however only parallel implementation of multiple decoders is considered rather than exploiting the attribute of parallelism of the algorithm itself.
+In this paper, a GPU based implementation of single FCSD is proposed, which is referred to as CUDA-FCSD.
 A heterogeneous programming solution for FCSD preprocessing and integrated blocked parallel path searching and decision making are presented.
@@
 The threads in one warp execute the same instruction simultaneously.
-The different warps are scheduled by a warp scheduler.
 When one warp is waiting for data loading, the other warps begin to execute.
-Such an approach is called a Single Instruction Multiple Thread (SIMT) model.
-This programming architecture is akin to a Single Instruction Multiple Data (SIMD) scheme, however unlike SIMD vectoring machines, the SIMT can branch the behavior of each threads to achieve thread-level parallelism.
+Such an approach is called a Single Instruction Multiple Thread (SIMT) model, whereby the behavior of each thread can be branched to achieve thread level parallelism.
 The GPU uses a massive number of threads to hide the long latency of a global memory, instead of using a large cache as CPU.
@@
 The post processing SNR depends only on $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$.
-From \cite{barbero2008fixing}, at the FE stage the "weakest" data stream, that is the data stream with the smallest $\varphi_{m}$, is detected first.
-At the SE stage, because of the single searching branch of the node, the performance is tightly related to the post processing SNR.
-Therefore at the SE stage the data stream with the largest post processing SNR is detected first in order to avoiding error propagation.
+From \cite{barbero2008fixing}, at FE stage the data stream with minimum post processing SNR is detected first, while at the SE stage the data stream with maximum post processing SNR is detected first.
 In conclusion the FCSD ordering works iteratively and obeys the following rule:
@@
 \centering
-\includegraphics[width=0.5\textwidth, height=8cm]{coalescing_global_memory.eps}
+\includegraphics[width=0.5\textwidth, height=6cm]{coalescing_global_memory.eps}
 \caption{Global Memory Access Pattern of $\mathit{s_{pm}}$}
@@
 \ref{BER curve} we present Monte Carlo simulation results for bit error rate (BER) performance, using the GPU implementation of different MIMO system configurations and constellation sizes.
-We consider uncoded complex MIMO systems with $M$QAM, where each antenna transmits different streams of binary data generated randomly and independently.
-The results have been obtained by using $100000$ channel realizations with at least $500$ symbol errors accumulated.
-The simulation results show that FCSD-CUDA provides the same BER performance as its CPU version\cite{barbero2008fixing}.
+We consider uncoded complex MIMO systems with $M$ QAM, where each antenna transmits different streams of binary data generated randomly and independently.
+The results have been obtained by using $10^{5}$ channel realizations with at least $500$ symbol errors accumulated.
+The simulation results show that FCSD-CUDA provides the same BER performance as its CPU version, due to the space limitation we do not present the results of CPU implementation, \cite{barbero2008fixing} provides some of the referable results.
 \begin{figure}[htb]
 \centering
-\includegraphics*[width=0.56\textwidth]{BER_curves.eps}
+\includegraphics*[width=0.5\textwidth, height=10cm]{BER_curves.eps}
 \caption{BER performance for MIMO systems with various modulation schemes using the GPU implementation}
@@
 In order to exploit the computational capability of GPU in the simulation of large MIMO systems, the utilization of a heterogeneous programming model, accounting for resource limitations and memory configuration must be considered.
-The simulation results show that a considerable acceleration of the GPU implementation of FCSD can be reached for large MIMO systems and signal constellation sizes over CPU implementation, while maintaining the same BER performance.
+The simulation results show that significant accelerations of the GPU implementation of FCSD can be reached for large MIMO systems and signal constellation sizes over CPU implementation, while maintaining the same BER performance.
 Since the GPU and CPU can work independently, the data processing power of GPU computing is an additional advantages provided by the traditional simulation platforms.

### 2015-04-14 Lattice Reduction/Report April 2015/Report_draft.tex
First draft of April report

--- 2014-10-27 parallel acceleration of FCSD based on cuda/draft.tex
@@
 %
-\documentclass[12pt,a4paper,final]{article}
-%\documentclass[conference]{IEEEtrans}
+\documentclass[12pt,letter,final]{article}
 % Add the compsoc option for Computer Society conferences.
@@
 \usepackage{setspace} 
-\usepackage{multirow}
+\usepackage{diagbox}
+\usepackage{subfigure}
 
@@
 % Do not put math or special symbols in the title.
-\title{Parallel Acceleration of Fixed Complexity Sphere Decoder for Large MIMO Uplink System based on GPU}
+\title{Report}
 
@@
 %Montreal, Quebec}}
-\author{Tianpei Chen, Harry Leib\\
+\author{Tianpei Chen\\
  Department of Electrical and Computer Engineering\\
- McGill University\\
- Montreal, Quebec}
+ McGill University}
 
@@
 %\IEEEspecialpapernotice{(Invited Paper)}
-
 \begin{document}
@@
 \maketitle
+\section{Introduction}
+Detection algorithm is one of the key components of Multiple-Input Multiple-Output (MIMO) systems.
+Designing of high performance and low complexity detector has become a bottleneck of Large MIMO systems.
+Recently, academia has found a property of large MIMO channel called channel hardening phenomenon \cite{hochwald2004multiple}\cite{tse2005fundamentals}\cite{marvcenko1967distribution}\cite{tulino2004random}, which states the phenomenon that with the number of receiving or transmitting antennas increasing, the variances of channel mutual information decrease.
+Simply saying, the channel "hardens".
+An useful aspect of channel hardening phenomenon is the off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$ matrix becomes more and more ignorable comparing to diagonal elements when the number of receiving antennas or transmitting antennas becomes large.
 
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
-\begin{abstract}
-The large MIMO system which is a scaling up of conventional MIMO systems with several hundreds of antennas at the base station serving several tens of terminals at the same time,  which is thought to be a big idea for the next generation wireless communication system.
-However the detection of the large MIMO system acquires a long time to get optimum or sub-optimum solutions, In order to accelerate the real-time decoder for large MIMO system, in this paper we present General Purpose Graphic Processing Units (GPGPU) implementation of Fixed Complexity Sphere Decoder (FCSD) for the large scale MIMO system based on the dominant propriety framework of GPGPU-Computed Unified Device Architecture (CUDA).
-The simulation shows a up to nearly $5$ times acceleration for $32\times 32$ array of whole application CPU version, furthermore, the proposed CUDA-FCSD algorithm shows a increasing speedup performance for a increasing array size.
-\end{abstract}
+ Channel hardening phenomenon provides an opportunity for designing computationally economical detection algorithms.
+For example, linear detectors (LDs) such as zero forcing (ZF) and minimum mean square error (MMSE) detectors need to calculate the inverse of $\mathbf{H}^{H}\mathbf{H}$ matrix.
+This process can be accelerated by approximate matrix inversion using series expansion techniques and deterministic approximations in large dimensions\cite{wu2013approximate}.
+Channel hardening phenomenon can also provide computational advances to machine learning based detectors, e.g.
+probability data association (PDA)\cite{fricke1900impact}\cite{pham2004generalized} and message passing detectors\cite{som2011low}\cite{goldberger2011mimo}\cite{lakshmi2013channel} and Monte-Carlo Markov Chain (MCMC) MIMO detectors\cite{farhang2006markov}\cite{datta2012novel}.
+This type of algorithms work well in large sparse systems.
 
-% no keywords
+In this report, we propose some useful insights of the orthogonal properties of channel.
+We define orthogonality measurement (om), which is a well round metric that considers both diagonal and off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$.
 
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-%\IEEEpeerreviewmaketitle
+The rest of the report is organized as follows, section \ref{system model} introduces system model.
+Section \ref{preliminary} provides some preliminaries of the definition of orthogonality measurement.
+Section \ref{log expectation of om} discusses the derivation of logarithmic expectation of orthogonality measurement.
+In section \ref{pdf of om} we obtain probability density function of orthogonality measurement.
+Some computer simulation results are presented in section \ref{computer simulation}.
 
-\section{Introduction}
- The common challenge that all the researchers, engineers and industrial companies are now facing in wireless communication area is the sharp contrast between the increasing demand of the mobile network speed for the transmission of rich media content and better QoS (quality of service) and the limited bandwidth of the radio frequency spectrum and a complex space time varying wireless environment, moreover in foreseeable future this demand will continue grow.
-Multiple Input Multiple Output (MIMO) has become a very promising technology that can help to solve this problem, the core idea of MIMO is to use multiple antennas both at the transmitting end and receiving end, the spatial domain sampled signal can be combined to provide parallel data pipes so that it can provide array gain, spatial diversity gain, spatial multiplexing gain, and interference reduction\cite{oestges2010mimo}.
-LTE standard support up to 8 antennas at the base station\cite{dahlman20103g}, The large scale MIMO (also named massive MIMO) is a system with hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}, originated from multiuser MIMO (MU-MIMO)\cite{larsson2013massive}.
-Large scale MIMO will inherit and enhance all the advantages of conventional MIMO (array gain, spatial diversity gain, spatial multiplexing gain and interference reduction), as well as reduction of latency, improvement of the whole system robustness.
- As a classical list based decoder for MIMO system, Sphere decoder (SD) can reach the optimum diversity gain as maximum likelihood (ML) detection with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}, however, there are two major problems of this decoder is the varied complexity with signal to noise ratio and sequential nature, which is contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system.
-Fixed Complexity Sphere Decoder (FCSD), overcomes this two disadvantage of the SD by searching the solution along the fixed number independent multiple paths\cite{barbero2008fixing}.
-GPGPU (General purpose Graphic processing Units Computing) has become a big idea in the industry and research of a variety of areas that needs massive data analysis and computation such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
-Comparing to CPU, The GPU has been designed as computational intensive, with most of the hardware resource be allocated for data processing and parallel computation rather than caching and flow control.
-In recent years GPU has reached huge advantages in data processing speed over CPU\cite{nvidia2008programming}.
-CUDA (Computed unified Device Architecture) is a programming model for GPGPU that proposed by Nvidia which has becoming the dominant proprietary framework for GPGPU programming, it is based on popular programming languages(C, C++, java, python, Fortran, Direct Compute) so that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
-The core essence of the CUDA is the Single Instruction Multiple Threads (SIMT) programming model, enables GPU can accelerate a lot of applications with the large dataset by implementing parallel data processing of complex computations.
-CUDA has become a parallel computing platform for wide community of different application developers in different areas.
-\section{MIMO System Model}\label{system}
-% no \IEEEPARstart
-%This demo file is intended to serve as a ``starter file''
-%for IEEE conference papers produced under \LaTeX\ using
-%IEEEtran.cls version 1.8 and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-%I wish you the best of success.
-%\hfill mds
-%\hfill December 27, 2012
-We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive antennas and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, in the flat fading channel the corresponding discrete time model is given:
+\section{System Model}\label{system model}
+We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel.
+Using a discrete time model, $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector written as:
 \begin{equation}
-y=\mathbf{H}s+n   \label{formula 1}
+\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{formula 1}
 \end{equation}
-$s\in \mathbb{C}^{N_{t}\times 1}$ is the transmit symbol vector, the symbol in $s$ are mutually independent and taken from the signal constellation $\mathbb{O}$ (BPSK, QPSK, M-QAM), $M$ is the signal constellation size, all the transmit symbol vectors forms a $N_{t}$-dimensional signal constellation $\mathbb{O}^{N_{t}}$.
-$\varepsilon[ss^{H}]=I_{N_t}E_{s}$, $E_{s}$ denotes the symbol average energy where $\varepsilon$ denotes the mean operation.
-$y\in \mathbb{C}^{N_{r}\times 1}$ is the receive symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean elements of unit variance, $n\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean elements of variance $\varepsilon[nn^{H}]=I_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise energy, $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR).
-\\
-  Assume we have the perfect channel state information (CSI)  $\quad \mathbf{H}$, receive symbol vector $y$, and we had already known the SNR, the task of decoder for MIMO system is to estimate $s$ in \ref{formula 1} based on CSI and received signal.
+where $\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
+4-QAM, 16-QAM, 64-QAM) of size $M$.
+The possible transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian components of zero mean and unit variance.
+Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
+Assume the receiver has perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known, as well as the SNR.
+The task of the MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
+\section{Preliminaries}\label{preliminary}
+Orthogonality deficiency measures the how orthogonal a matrix is \cite{ma2008performance}, which is defined by
+\begin{equation}
+\phi_{od}=1-\frac{det(\mathbf{W})}{\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||^{2}},
+\label{formula1}
+\end{equation}
+where $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$ denotes Wishart matrix, $\mathbf{h}_{i}$ denotes the $i$ th column of $\mathbf{H}$, $det(\cdot)$ denotes determinant operation, $||\cdot||^{2}$ denotes 2-norm operation.
+In (\ref{formula1}), $||\mathbf{h}_{i}||^{2}=\sum_{i=1}^{N_{t}}|\mathbf{H}_{ij}|^{2}$, $\mathbf{H}_{ij}$ denotes the component of $\mathbf{H}$ at $i$ th row and $j$ th column.
+$\mathbf{H}_{ij}\sim Rayleigh(1/\sqrt{2})$, therefore $||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},1)$\cite{papoulis1996stochastic}.
+$Gamma(k,\theta)$ denotes Gamma distribution, with $k$ degrees of freedom.
+Furthermore, we have:
+\begin{equation}
+2||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},2)\sim\chi^{2}_{2N_{r}},
+\label{formula2}
+\end{equation} 
+$\chi^{2}_{k}$ denotes chi-square distribution with $k$ degrees of freedom. For the sake of simplicity, (\ref{formula1}) can be changed to:
+\begin{equation}
+\phi_{om}=\frac{det(\mathbf{W})}{\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||^{2}}=\frac{2^{N_{t}}det(\mathbf{W})}{\prod_{i=1}^{N_{t}}2||\mathbf{h}_{i}||^{2}}.
+\label{formula3}
+\end{equation}
+Taking logarithmic operation to $\phi_{om}$ we have 
+\begin{equation}
+\ln(\phi_{om})=N_{t}\ln(2)+\ln(det(\mathbf{W}))-\sum_{i=1}^{N_{t}}\ln(2||\mathbf{h}_{i}||^{2}),
+\label{formula4}
+\end{equation}
+$\phi_{om}$ in (\ref{formula3}) is defined as Orthogonality Measure.
+Based on Hadamard's inequality ($\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||\geq det(\mathbf{H})$).
+$\phi_{om}\in [0,1]$.
+If $\phi_{om}$ is more closer to 1, $\mathbf{H}$ is closer to orthogonal matrix.
 
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results.}
-%\label{fig_sim}
-%\end{figure}
+Because $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$, do QR factorization to $\mathbf{H}$ 
+\begin{equation}
+\mathbf{H}=\mathbf{Q}\mathbf{R},
+\label{formula5} 
+ \end{equation}
+where $\mathbf{Q}\in\mathbb{C}^{N_{r}\times N_{t}}$ is a unitary matrix and $\mathbf{R}\in\mathbb{C}^{N_{t}\times N_{t}}$ is the upper triangular matrix.
+Using (\ref{formula5}), we have $\mathbf{W}=\mathbf{R}^{H}\mathbf{R}$.
+$r_{ii}$ denotes the $i$ th diagonal component of $\mathbf{R}$, thus $det(\mathbf{W})$ can be rewritten as:
+\begin{equation}
+det(\mathbf{W})=det(\mathbf{R}^{H}\mathbf{R})=det(\mathbf{R}^{H})det(\mathbf{R})\\=\prod_{i=1}^{N_{t}}r_{ii}^{H}\prod_{i=1}^{N_{t}}r_{ii}=\prod_{i=1}^{N_{t}}|r_{ii}|^{2}.
+\label{formula6}
+\end{equation}  
+Notice that $\mathbf{R}$ can be viewed as the Cholesky factorization of $\mathbf{W}$. Therefore, we have
+\begin{equation}
+ ||\mathbf{h}_{i}||^{2}=\mathbf{W}_{ii}=\sum^{i-1}_{j=1}|r_{ji}|^{2}+|r_{ii}|^{2},
+\label{formula7}
+ \end{equation}
+ where $\mathbf{W}_{ii}$ denotes the $i$ th diagonal element of $\mathbf{W}$.
+ Thus based on (\ref{formula6}) and (\ref{formula7}), (\ref{formula3}) can be rewritten as:
+\begin{equation}
+\phi_{om}=\prod_{i=1}^{N_{t}}\frac{|r_{ii}|^{2}}{|r_{ii}|^{2}+\sum^{i-1}_{j=1}|r_{ji}|^{2}}.
+\label{formula9}
+\end{equation}  
+\section{Logarithmic Expectation of Orthogonality Measurement}\label{log expectation of om}
 
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
+Taking expectation of (\ref{formula4}), we have 
+\begin{equation}
+\mathbb{E}[\ln(\phi_{om})]=N_{t}\ln(2)+\mathbb{E}[\ln(det(\mathbf{W}))]-\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(2||\mathbf{h}_{i}||^{2})].
+\label{formula11}
+\end{equation}
+Consider $\mathbf{H}=[\mathbf{h}_{1}^{'},\mathbf{h}_{2}^{'},\cdots \mathbf{h}_{N_{r}}^{'}]^{'}$, where $\mathbf{h}_{i}$ denotes the $i$ th row of $\mathbf{H}$, because each component of $\mathbf{H}$ is mutually independent and subject to circularly symmetric complex Gaussian distribution, i.e.
+$h_{i}\sim \mathbb{C}N(\mathbf{0},\mathbf{I}_{N_{t}})$.
+Therefore, $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}\sim \mathbb{C}W(N_{r}, \mathbf{I}_{N_{t}})$, $\mathbb{C}W(n,\mathbf{\Sigma})$ denotes complex Wishart distribution with $n$ degrees of freedom and covariance matrix $\mathbf{\Sigma}$.
+The logarithmic expectation of $\mathbf{W}$ can be rewritten as
+\begin{equation}
+\mathbb{E}[\ln(det(\mathbf{W}))]=\frac{\tilde{\Gamma}^{'}_{N_{t}}(N_{r})}{\tilde{\Gamma}_{N_{t}}(N_{r})}=\sum_{i=1}^{N_{t}}\psi(N_{r}-i+1),
+\label{formula12}
+\end{equation}
+where $\tilde{\Gamma}_{m}(n)$ denotes the multivariate Gamma function. Proof: see Appendix A.
 
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
+Because the logarithmic expectation of a Gamma distribution variable $\mathbb{g}\sim Gamma(n,\theta)$ can be written as:
+\begin{equation}
+\mathbb{E}[\ln(\mathbb{g})]=\psi(n)+\ln(\theta),
+\end{equation}
+where $\psi(n)$ denotes Digamma function. Thus according to (\ref{formula2}), we have:
+\begin{equation}
+\mathbb{E}[\ln(2||\mathbf{h}_{i}||^{2})]=\psi(N_{r})+\ln(2).
+\label{formula14}
+\end{equation}
+Proof: see Appendix B
+Based on (\ref{formula11})(\ref{formula12})(\ref{formula14}), The logarithmic expectation of $\phi_{om}$ can be written as:
+\begin{eqnarray}
+\nonumber
+\mathbb{E}[\ln(\phi_{om})]&=&N_{t}\ln(2)+\sum_{i=1}^{N_{t}}\psi(N_{r}-i+1)-N_{t}\psi(N_{r})-N_{t}\ln(2)\\
+&=& \sum_{i=1}^{N_{t}}\psi(N_{r}-i+1)-N_{t}\psi(N_{r})
+\label{formula15}
+\end{eqnarray}
+\section{Probability Density Function of Orthogonality Measurement}\label{pdf of om}
+Recall (\ref{formula9})
+\begin{equation}
+\phi_{om}=\prod_{i=1}^{N_{t}}\frac{|r_{ii}|^{2}}{|r_{ii}|^{2}+\sum_{j<i}|r_{ji}|^{2}}.
+\end{equation}
+All the components in $\mathbf{R}$ are independently distributed and $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma((N_{r}-i+1),1)$ \cite{nagar2011expectations}.
+Because $|r_{ji}|\sim Rayleigh(1/\sqrt{2})$, $\sum_{j<i}|r_{ji}|^{2}\sim Gamma(i-1, 1)$.
+Defining $\alpha_{i}=\sum_{j<i}|r_{ji}|^{2}$ and $\beta_{i}=|r_{ii}|^{2}$, $\alpha_{i}$ and $\beta_{i}$ are mutually independent, therefore (\ref{formula9}) can be rewritten to
+\begin{equation}
+\phi_{om}=\prod_{i=1}^{N_{t}}\frac{\beta_{i}}{\alpha_{i}+\beta_{i}},
+\label{formula21}
+\end{equation}
+From \cite{gupta2004handbook}, if $X\sim Gamma(k_{1},\theta)$ and $Y\sim Gamma(k_{2},\theta)$, then $\frac{X}{X+Y}\sim B(k_{1},k_{2})$, where $B$ denotes Beta distribution.
+Therefore $\frac{\beta_{i}}{\beta_{i}+\alpha_{i}}\sim B(k^{i}_{1}, k^{i}_{2})$, where $k^{i}_{1}=N_{r}-i+1$, $k^{i}_{2}=i-1$.
+we define $\eta_{i}=\frac{\beta_{i}}{\beta_{i}+\alpha_{i}}$, it is obvious that $\eta_{i}$ are independently distributed.
+Based on (\ref{formula21}), we have
+\begin{equation}
+\phi_{om}=\prod_{i=1}^{N_{t}}\eta_{i}.
+\label{formula22}
+\end{equation}
+Therefore the density function of $\phi_{om}$ can be defined as
+\begin{equation}
+f_{\phi_{om}}(x)=\frac{1}{x}\sum_{\mathbf{j}}(\prod_{i=1}^{N_{t}}c(k_{1}^{i}k,k_{2}^{i},j^{i}))f(\ln(x)|\mathbf{k_{1}}+\mathbf{j}), 
+\label{formula23}
+\end{equation}
+where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{N_{t}}}$, the range of $j^{i}\in [0, k_{2}^{i}-1]$, $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
+$f(\ln(x)|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})\ln(x))/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$.
+$\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1},\cdots k_{1}^{N_{t}-1}+j^{N_{t}-1},k_{1}^{N_{t}}+j^{N_{t}}]$.
+Proof: see Appendix C.
 
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
+Consider logarithmic expectation of $\phi_{om}$, we have
+\begin{equation}
+E[\ln(\phi_{om})]=\sum_{i=1}^{N_{t}}E[\ln(\eta_{i})],
+\label{formula24}
+\end{equation}
+where $E[\ln(\eta_{i})]=\psi(k^{i}_{1})-\psi(k^{i}_{1}+k^{i}_{2})$, thus we have 
+\begin{equation}
+E[\ln(\phi_{om})]=\sum_{i=1}^{N_{t}}\psi(N_{r}-i+1)-N_{t}\psi(N_{r}).
+\label{formula25}
+\end{equation}
+we can find (\ref{formula25}) is consistent with (\ref{formula15}).
 
-\section{CUDA GPU Architecture and  Programming Model} \label{programming model}
-  CUDA programming model is the C programming extension, with special defined syntax and structure, CUDA divide the CPU and GPU as host and device, the serial code executes on the host (CPU) side and parallel data processing is performed on the device (GPU) side, which is defined as heterogeneous programming model.
-The code executes on the device side is defined as $\mathit{kernel}$ function, which is a single instruction invoked at host side but with a massive parallel data processing threads execution on the device (SIMT), This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branching the behavior of each threads so that reach thread-level parallelism, thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share a memory called shared memory that all the threads in the block have the access to this pitch of memory, the GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU, Another function of the thread block is all the thread execute in one block can synchronize their action.
-The warp is the basic schedule unit with a constant number of threads  (for current version of CUDA device, the warp size is 32), when one warp are waiting for data loading the other warps just begin to execute.
-In a word CPU cores are designed to minimize latency for each thread at a time , whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput.
-Blocks are grouped into a one-dimensional, two-dimensional, or three-dimensional grid, similarly, one thread block can also be organized into one-dimentional, two-dimensional or three-dimensional.
-The organization of the block and grid shape and dimension is determined by the concrete application, Figure \ref{figure1} shows the 3 dimensional thread hierarchy of CUDA.
+\section{Computer Simulations}\label{computer simulation}
+ Computer simulations are made for different sizes of V-BLAST MIMO systems, with $5\leq N_{r} \leq 100, 5 \leq N_{t} \leq N_{r}$, the empirical estimation of logarithmic expectation of $\phi_{om}$, $E[\ln(\phi_{om})]_{em}$, is calculated by taking average over $1e4$ channel realizations for each size of MIMO systems, as shown in Fig.
+\ref{figure1}, the Theoretical logarithmic expectation of $\phi_{om}$ $E[\ln(\phi_{om})]_{t}$ in (\ref{formula25}) is plotted in Fig.
+\ref{figure2}.
+Average deviation between $E[\ln(\phi_{om})]_{em}$ and $E[\ln(\phi_{om})]_{t}$ is also calculated, $V_{em-t}= 7.3043e-04$.
+
 \begin{figure}[htb]
 \centering
-\includegraphics[scale=0.5]{CUDA_programming_hierachy.eps}
-\caption{CUDA 3D thread hierachy\\ $5\times 5\times 5$ grid and each block contains $5\times 5\times 5$ threads\\}
+\includegraphics[scale=0.6]{NtE.eps}
+\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
+\label{figure3}
+\end{figure}
+
+Fig.
+\ref{figure3} demonstrates the relation between the number of users ($N_{t}$) and $E[\ln(\phi_{om})]_{t}$ under cases of different numbers of antennas at base station ($N_{r}$).
+From Fig.
+\ref{figure3}, we can see, on the one hand, with $N_{r}$ fixed, $E[\ln(\phi_{om})]$ decreases while $N_{t}$ increases, however the gradient of each curve becomes more and more gentle.
+On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
+\begin{figure}[htb]
+\centering
+\centering\includegraphics[width=0.7\textwidth, height=5cm]{LogE_om_em.eps}
+\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
 \label{figure1}
 \end{figure}
-In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
-The GPU works as a coprocessor system, consists of Stream Multiprocessors (SM), GeForce GTX 760 has 6 SM performs the multiply-add arithmetic operation and furthermore, each SM has the special functional units(SFU) that can perform more complex arithmetic operation such as trigonometric functions and reciprocal square root.
-the shared memory is also called on-chip memory which is located at SM that has low latency and limited capacity.
-Global memory, which is off-chip located memory of GPU with long latency and large capacity, another two types of the memory is called texture memory and constant memory, which are located off-chip , but cached, therefore the loading speed of the data located at these two type of memory space will be much faster than the that from global memory, for constant memory, it is read only and the memory latency is approximately as small as the registers.
-The variables invoked in kernel functions can be stored in either of the these 4 types of memories.
-Registers are allocated dynamically to threads.\\
-   Since the resource limitation of SM the total number of threads that we can define in one block is limited, on current CUDA supported GPUs, one block can contains up to 1024 threads, in addition all the blocks are executed on SMs, thus the total number of threads we can make use of is $T_{total}=Num_{SM}\times Num_{threads/SM}$, GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$, although in concrete application, the programmer can allocate more than 12288 threads for a kernel, but the threads will work in serial, which will influence the performance of program.
+
 \begin{figure}[htb]
 \centering
-\includegraphics[scale=0.5]{High_view_of_CUDA_GPU_microarchitecture.eps}
-\caption{High View of CUDA CPU Microarchitecture}
+\includegraphics[width=0.7\textwidth, height=5cm]{LogE_om_t.eps}
+\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
 \label{figure2}
 \end{figure}
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
-\section{GPU Based Acceleration of FCSD}
-In this section we present the parallel implementation of fixed complexity sphere decoder by GPU, first from (\ref{formula 1}), the maximum likelihood (ML) solution is given by:
+
+\begin{appendices}
+\section{Appendix A}
+Let $\mathbf{A}\in \mathbb{C}^{m\times m}$, $A\sim \mathbb{C}W(n, \mathbf{\Sigma})$, $\mathbb{C}W(n, \mathbf{\Sigma})$ denotes complex Wishart distribution with $n$ degrees of freedom and covariance matrix $\mathbf{\Sigma}$.
+It is obvious $\mathbf{A}$ is Hermition positive definite matrix, $\mathbf{A}=\mathbf{A}^{H}>0$.
+
+The p.d.f function of $\mathbf{A}$ can be written as\cite{nagar2011expectations}:
 \begin{equation}
-s_{ML}=arg\min_{s\in \mathbb{O}^{N_{t}}}||y-\mathbf{H}s||^{2} \label{formula 2}
+f(A)=\{\tilde{\Gamma}_{m}(n)det(\mathbf{\Sigma})^{n} \}^{-1}det(A)^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A}),
+\label{Appendequa1}
 \end{equation}
-we consider the array $N_{t}=N_{r}$, performing QR decomposition to channel propagation matrix
+where $\tilde{\Gamma}_{m}(\beta)$ denotes multivariate complex Gamma function defined by:
 \begin{equation}
- \mathbf{H}=\mathbf{Q}\mathbf{R}  \label{QR}
+\tilde{\Gamma}_{m}(\beta)=\pi^{\frac{m(m-1)}{2}}\prod_{i=1}^{m}\Gamma(\beta-i+1)\quad Re(\beta)>m-1.
+\label{Appendequa2}
 \end{equation}
-where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is the unitary matrix, $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is the upper triangular matrix, the basing on \cite{matrix theory}, the (\ref{formula 2}) can be changed to
+Furthermore,from \cite{nagar2011expectations}, we have
+
+\begin{equation}
+\tilde{\Gamma}_{m}(\beta)=\int_{\mathbf{X}=\mathbf{X}^{H}>0}etr(-\mathbf{X})det(\mathbf{X})^{\beta-m}d
+\mathbf{X} \quad Re(\beta)>m-1.
+\label{Appendequa3}
+\end{equation}
+We derive logarithmic expectation of $det(\mathbf{A})$
 \begin{eqnarray}
 \nonumber
-s_{ML}&=&arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}y-\mathbf{Q}^{H}\mathbf{H}s||^{2}\\
-&=& arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}y-\mathbf{R}s||^{2} \label{formula 3}
+E[\ln(det(\mathbf{A}))]&=&\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))f(\mathbf{A})d\mathbf{A}\\
+\nonumber
+&=&\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))\{\tilde{\Gamma}_{m}(n)det(\mathbf{\Sigma})^{n} \}^{-1}det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A})d\mathbf{A}\\
+&=&\frac{det(\mathbf{\Sigma})^{-n}}{\tilde{\Gamma}_{m}(n)}\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A})d\mathbf{A},
+\label{Appendequa4}
 \end{eqnarray}
-Consider the unconstrained estimation of $s$, $\hat{s}=\mathbf{G}y$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$ denotes the zero forcing equalizer, basing on \ref{QR}, we have  
+if $\mathbf{\Sigma}=\mathbf{I}$, \ref{Appendequa4} can be written as 
 \begin{equation}
-\hat{s}=\mathbf{G}y=(\mathbf{R}^{H}\mathbf{R})^{-1}\mathbf{R}^{H}\mathbf{Q}^{H}y=\mathbf{R}^{-1}\mathbf{Q}^{H}y 
-\label{unconstrained estimation}
+E[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A})d\mathbf{A}.
+\label{Appendequa5}
 \end{equation}
-Therefore $\mathbf{Q}^{H}y=\mathbf{R}\hat{s}$, the \ref{formula 3} can be changed to
+Because $\frac{d}{dn}[det(\mathbf{A})]^{n-m}=\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}$, (\ref{Appendequa5}) can be rewritten as
 \begin{equation}
-s_{ML}=arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\hat{s}-s)||^{2} \label{formula 4}
+E[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\frac{d}{dn}\int_{\mathbf{A}=\mathbf{A}^{H}>0}det(\mathbf{A})^{n-m}etr(-\mathbf{A})d\mathbf{A},
+\label{Appendequa6}
 \end{equation}
-the Fixed Complexity Sphere Decoder works as a constant number of multiple path tree searching.
-\begin{figure}[tb]
-\centering
-\includegraphics[scale=0.5]{FCSD_tree_searching.eps}
-\caption{Tree searching of QPSK FCSD for 8x8 MIMO system}
-\label{figure4}
-\end{figure}
-As shown in Figure \ref{figure4}, just like SD the FCSD also performs depth first searching, at the first $\rho$ level the FCSD search all the possible signal symbols $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$ in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) level, the remain $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back equalization (DFE), from (\ref{formula 4}) the solution of FCSD can be given:
+using (\ref{Appendequa3}), (\ref{Appendequa6}) can be rewritten as 
 \begin{equation}
-\hat{s}_{FCSD}=arg\min_{s\in \mathbb{O}^{N_{t}}}\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s_{j})|^{2}  \label{formula 5}
+E[\ln(\mathbf{A})]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}.
+\label{Appendequa7}
 \end{equation}
-$i\in [1,2\dots N_{t}]$, $r_{ij}$ denotes the element at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$, this process is called Single Expansion (FE).
-thus the FCSD solution $s_{FCSD}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
-\begin{displaymath}
-s_{FCSD}^{i}=\left\lbrace\begin{array}{c}
-\in \mathbb{O}^{\rho}      \quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
-\mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}}-s_{FCSD}^{i})] \quad i=N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
-\end{array}\right.
-\end{displaymath}
-$\mathbb{Q}[]$ denotes the signal constellation based quantization. At the post processing stage, FCSD takes the symbol vector candidate with the minimum Euclidean metric $E_{metric}$:
+Based on (\ref{Appendequa2}), we have 
+\begin{eqnarray}
+\tilde{\Gamma}^{'}_{m}(n)=\pi^{\frac{m(m-1)}{2}}\prod_{i=1}^{m}\Gamma^{'}(\beta-i+1),
+\end{eqnarray}
+Thus we have 
 \begin{equation}
-E_{metric}=||\mathbf{R}(\hat{s}-\widetilde{s})||^{2}
+E[\ln(det(\mathbf{A}))]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}=\prod_{i=1}^{m}\psi(n-i+1),
+\label{Appendequa8}
 \end{equation}
-The $\widetilde{s}$ denotes the symbol vector candidate, the total number of candidates is: 
+where $\psi$ denotes Digamma function.
+\section{Appendix B}
+If $x\sim Gamma(n, \theta)$, with shape parameter $k$ and scale parameter $\theta$, $x>0$, $\Gamma(k)$ denotes Gamma function, the density function of Gamma distribution is
 \begin{equation}
-M^{\rho}     \label{path number}
+f(x,k,\theta)=\frac{x^{k-1}e^{-x/\theta}}{\Gamma(k)\theta^{k}}.
+\label{Appendequa9}
 \end{equation}
-\subsection{CUDA-FCSD Pre-Prossing}
-As shown in figure.4, each path of the FCSD searching has a serial execution nature, in order to avoid error propagation of decoder, FCSD ordering was applied to the propagation channel based on post processing signal to noise ratio\cite{Vblas}, which can be expressed as:
+Thus we have 
 \begin{equation}
-\varphi_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}}  \label{ppsnr}
+E[\ln(x)]=\frac{1}{\Gamma(k)}\int_{0}^{\infty}\ln(x)x^{k-1}e^{-x/\theta}\theta^{-k}dx,
+\label{Appendequa10}
 \end{equation}
-$\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inversion of $HHH$ matrix $\mathbf{H}^{H}\mathbf{H}$, thus when the SNR is determined, the post processing SNR is only determined by $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$, for the FE stage the robustness of detector performance is not influenced by the post processing SNR thus at FE stage the "weakest" data stream is detected first, that is, the data stream with the smaller $\varphi$ is detected earlier.
-At SE stage, because of the single searching path of the symbol, the performance is tightly related to the post processing SNR, therefore at SE stage the data streams with the larger post processing SNR is detected earlier in order to avoiding the error propagation, in conclusion the FCSD ordering works iteratively  and obeys the following rule:
-At the $j$th step ($j=1,2\dots N_{t}-1$), $s_{p}$ denotes the symbol to be detected, where 
-\begin{displaymath}
-p=\left\lbrace \begin{array}{c}
-arg \max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE stage\\
-arg \min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE stage \\  \label{the ordering}
-\end{array}\right.  
-\end{displaymath}  
-$\mathbf{H}_{j}\in \mathbb{C}^{N_{r}\times (N_{t}-j+1)}$ denotes the renewed channel matrix, at the $j$th iteration with the column corresponding to previous detected data streams removed from $\mathbf{H}_{j-1}$.
-the unconstrained estimation $\hat{s}$ in \ref{unconstrained estimation}  in is given by:
+define $z=x/\theta$ and since $\Gamma(k)=\int_{0}^{\infty}x^{k-1}e^{-x}dx$, (\ref{Appendequa10}) can be rewritten as
 \begin{equation}
- \hat{s}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y \label{shat}
+E[\ln(x)]=\ln(\theta)+\frac{1}{\Gamma(k)}\int_{0}^{\infty}\ln(z)z^{k-1}e^{-z}dz.
+\label{Appendequa11}
+\end{equation}
+Because $\frac{d(z^{k-1})}{dk}=\ln(z)z^{k-1}$, (\ref{Appendequa11}) can be rewritten as
+\begin{eqnarray}
+\nonumber
+E[\ln(z)]&=&\ln(\theta)+\frac{1}{\Gamma(k)}\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz\\
+\nonumber
+&=&\ln(\theta)+\frac{\Gamma^{'}(k)}{\Gamma(k)}\\
+\nonumber
+&=&\ln(\theta)+\psi(k),
+\label{Appendequa12}
+\end{eqnarray}
+where $\psi(k)$ denotes Digamma function.
+\section{Appendix C}
+$x_{1}, x_{2}, \cdots x_{N_{t}}$ are independent beta variables, the probability density function (pdf) can be written as: 
+\begin{equation}
+f(x_{i})=\frac{1}{\mathbb{B}(k_{1}^{i}, k_{2}^{i})}x_{i}^{k_{1}^{i}-1}(1-x_{i})^{k_{2}^{i}-1},
+\label{Appendequal13}
+\end{equation}
+define $y_{i}=-\ln(x_{i})=g(x_{i})$, Based on Jacobian transformation, we have 
+\begin{equation}
+f_{y_{i}}((y)=|\frac{dy_{i}}{dx_{i}}|^{-1}f_{x_{i}}(g^{-1}(x_{i}))=\frac{1}{\mathbb{B}(k_{1}^{i},k_{2}^{i})}e^{-k_{1}^{i}y_{i}}(1-e^{-y_{i}})^{k_{1}^{i}-1}.
+\label{Appendequal14}
+\end{equation}
+where (\ref{Appendequal14}) can be alternatively expressed as \cite{bhargava1981distribution}
+\begin{equation}
+f_{y_{i}}(y)=\sum_{j^{i}=0}^{k_{2}^{i}-1}c(k_{1}^{i},k_{2}^{i}, j^{i})(k_{1}^{i}+j^{i})exp(-(k_{1}^{i}+j^{i})y_{i}).
+\label{Appendequal15}
+\end{equation} 
+Based on the lemma 1 of \cite{bhargava1981distribution}, if $a_{1}, a_{2}, \cdots a_{n}$ are independent exponentially distributed random variables, with pdf given by
+\begin{equation}
+t_{i}exp(-t_{i}a_{i})，
+\label{Appendequal16}
+\end{equation} 
+then $a=\sum_{i=1}^{n}a_{i}$ can be written as
+\begin{equation}
+f(a|\mathbf{t})=\prod_{i=1}^{n}\sum_{i=1}^{n}[exp(-t_{i}a)\prod_{j=1\\ j\neq i}^{j=n}t_{j}-t_{i}],
+\label{Appendequal17}
+\end{equation}
+where $t=[t_{1}, t_{2}, \cdots t_{n}]$.
+The pdf of $y_{i}$ can be viewed as the weighting summation of exponential distribution functions, define $y=\sum_{i=1}^{n}y_{i}$, based on (\ref{Appendequal17}), the pdf of $y$ is given by
+\begin{equation}
+f_{y}(m)=\sum_{\mathbf{j}}(\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i}, j^{i}))f(m|\mathbf{k_{1}}+\mathbf{j}),
+\label{Appendequal18}
+\end{equation}
+where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{n}}$, the range of $j^{i}$ is defined by $j^{i}\in [0, k_{2}^{i}]$, $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
+$f(m|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})m)/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$, $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1}, k_{1}^{2}+j^{2} \cdots k_{1}^{n}+j^{n}]$.
+we define $U=exp(-y)=\prod_{i=1}^{n}x_{i}$, using Jacobian transformation, the pdf of $U$ is given by
+\begin{equation}
+f_{U}(u)=|\frac{du}{dy}|^{-1}f_{y}(-\ln(u))=\frac{1}{u}\sum_{\mathbf{j}}f(-\ln(u)|\mathbf{k_{1}}+\mathbf{j}).
+\label{Appendequal19}
 \end{equation}
 
-Although the FCSD pre-processing has a serial nature and can not be vectorized, the computational consumptive operations \ref{the ordering} \ref{shat} can be implement by the CUDA Basic Linear Algebra Subprograms(cuBLAS), the matrix inverse(Gaussian Jordan Elimination) and cholesky factorization(Row Major Factorization) are also implemented by GPU, as shown in Table \ref{table 1}.
-\begin{table}[htb]
-\caption{Parallel Computation Operation of FCSD Pre-processing}
-\centering
-\begin{tabular}{|c|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
-\hline
-Operations & complex matrix-matrix multiplication & complex matrix-vector multiplication & matrix inverse & cholesky factorization \\
-\hline
-GPU subroutine & $\mathit{cublasCgemm}$  & $\mathit{cublasCgemv}$ & $\mathit{GJE}$ & $\mathit{chol}$\\
-\hline
-Formula   &  $\mathbf{H}^{H}\mathbf{H}$ & $(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y$ & $\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1} $ & $\mathbf{H}^{H}\mathbf{H}=\mathbf{R}^{H}\mathbf{R}$ 
-\\
-\hline
-  \label{table 1}
-\end{tabular}
-\end{table}
+\end{appendices}
 
-Figure \ref{block diagram} shows the block diagram of the CUDA-FCSD implementation, as mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
-\begin{figure}[htb]
-\centering
-\includegraphics[scale=0.8]{CUDA_FCSD_block_diagram.eps}
-\caption{Block Diagram of CUDA-FCSD Implementation}
-\label{block diagram}
-\end{figure}
-\subsection{Parallel Acceleration of Blocked-Paths Searching}
-  We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt[2]{N_{t}}-1\rceil$, as mentioned in section \ref{programming model} the maximum number of threads that can be used in GPU is limited by the number of SM and maximum number of threads per SM, as to GeForce GTX 760.
-we have $12288$ threads totally.
-For each path, decision feedback path searching has a serial nature, therefore we match path to one thread, in order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks, for largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads.
-At each path, we perform the following data operation:\\
-1. \emph{Decision Feedback Equalization}\\
-\begin{eqnarray}
-\nonumber
-{s}_{i}^{k}\in \mathbb{O}^{\rho}      \quad if\quad i&=&N_{t},N_{t}-1,\dots N_{t}-\rho+1\quad FE\\
-\nonumber
-{s}_{i}^{k}=\hat{s}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}^{k}}-s_{j}^{k})\quad if\quad i &=& N_{t}-\rho,N_{t}-\rho-1,\dots 2,1\quad SE\\  \label{path searching}
-\end{eqnarray}
-$s_{j}^{k}$ denotes the $j$th symbol of the $k$th symbol vector candidate.\\
-2. \emph{Euclidean Metric Calculation}\\
-\begin{equation}
-E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s_{j}}-s_{j})\label{Eu metric}
-\end{equation}
-$E_{u}^{k}$ denotes the $k$th Euclidean metric of the corresponding symbol vector candidate $\widetilde{s}^{k}$. Then we take the symbol vector $s^{\theta}$ as the solution, where 
-\begin{equation}
-\theta=arg\min_{m}(E_{u}^{m})\quad m=1,2\dots M^{\rho} \label{Eu candidate}
-\end{equation}
-
-\subsubsection{Data Preparation}
-There are three major factors that will influence the configuration of the data set configuration in memory space.\\
-1. Amount of Reading$\&$Writing operation per thread.\\
-2. Program scope of the data.\\
-3. Storage Requirement of data.\\
-The memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influence the application performance because the GPU is data processing intensive and only has small cache for special memory space(constant, texture), another consideration is the validation life circle of data, local memory which is invoked in kernel function is valid in one thread, share memory is valid in one block, constant, texture and global memory are valid both at host side and device side.
-On the other hand different from global memory (2047 MBytes in GeForce GTX 760), the constant and share memory are all capacity limited (only $65536$ bytes totally and $49152$ bytes per block in GeForce GTX 760), so that for our application the configuration of memory is determined by the capacity requirement of the data.
-Here in table \ref{amount of R/W operation} we present the amount of R/W operations and the storage that needed for critical data variables in FCSD path searching.
-The amount of the R/W operation is calculated based on the (\ref{path searching}) and ((ref{Eu metric}), for complex value ($\mathbf{R}$,$\hat{s}$, $\mathit{s_{pontential matrix}}$,$\mathit{s_{kernel}}$ ) is stored use $\mathit{float2}$ which counts 8 bytes, floating point data set $E_{u}$ is stored in $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored use $\mathit{int}$, which counts 1 byte.
-\\
- At host side we set 4 vector data set that are stored linearly in global memory which has program scope for both host side and device side, $\mathit{s_{potential matrix}}$ is used to store the $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope is through the whole kernel function.
-$\mathit{s_{index}}$, which is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.
-$\mathit{E_{u}}$ is a $M^{\rho}$ floating point vector that is used to store the Euclidean metric of all the symbol vector candidates, obviously the valid scope of it is for the whole kernel function.
-$\mathit{s_{kernel}}$ is a complex vector used to store the FCSD solution which length is $N_{t}$ and has to be transferred to host side, thus it is also needed to be stored in global memory.
-\\
-  On the other hand,   upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\hat{s}$ in (\ref{unconstrained estimation})  requires a large amount of R operations and are read only.
-(for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\hat{s}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\hat{s}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section (\ref{programming model}), the constant memory is cached so that it is much faster than global memory.
- \begin{table}[htb]  
- \caption{Amount of R/W Operations and Storage Requirement of Different Data Set}
- \centering
-\begin{tabular}{|p{3cm}|p{3cm}|l|p{3cm}|l|l|l|}
-\hline
-data & $\mathbf{R}$ & $\hat{s}$ & $\mathit{s_{pontential matrix}}$ & $\mathit{s_{index}}$ & $\mathit{E_{u}}$ & $\mathit{s_{kernel}}$ \\
-\hline
-R/W operations/thread & $(\frac{3}{2}(N_{t})^{2}-\frac{N_{t}}{2}+\rho-\rho^{2})$ & $(\frac{2(N_{t})^{2}+2N_{t}-\rho^{2}-\rho}{2})$ & $\rho$ & $N_{t}$ &$N_{t} $ & $N_{t}$ \\
-\hline
-Storage/bytes  & $4(N_{t}+1)N_{t}$ & $8N_{t}$ & $8M^{\rho}N_{t}$ & $N_{t}M^{\rho}$ & $4N_{t}M^{\rho}$ & $8N_{t}$\\
-\hline  \label{amount of R/W operation} 
-\end{tabular} 
-\end{table} 
-\subsubsection{Memory Accesss Pattern}
-  When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.\\
-  Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W data by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible, for GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Figure \ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{potential matrix}}$ as an example to illustrate how we coalesce the the global memory,
-we store $\mathit{s_{potential matrix}}$ in one pitch of linear global memory, with each row store one $N_{t}=16$ complex symbol vector solution candidate of $\hat{s}_{FCSD}$ in (\ref{formula 5}), totally there are $M^{\rho}=4096$ rows, this matrix is stored in column major.
-As mentioned before we operate one path in one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256 bytes$, counts for two times of DRAM access.
-\begin{figure}[htb]
-\centering
-\includegraphics[scale=0.63]{coalescing_global_memory.eps}
-\caption{Global Memory Access Pattern of $\mathit{s_{potential matrix}}$}
-\label{coalesce global memory}
-\end{figure}
- Another available resource for memory bandwidth increase is to make use of share memory, for all the transient variables that used for accumulator in (\ref{path searching}) and (\ref{Eu metric}), because of the small capacity consumption and large amount of R/W operations.
-\subsubsection{Data Transfer Minimization}   
-The data transfer between the host side and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $y$ in (\ref{formula 1}) as well as the index list $\mathit{s_{index}}$ at FE stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
-\subsection{Going to Larger MIMO System}
-  Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, from \ref{path number}, the path number that need to be searched is $16^{5}=1048576$, as mentioned in section (\ref{programming model}), the maximum number of threads that can be execute in kernel function of GeForce GTX 760 is 12288, therefore we need to consider serial the one kernel into a certain times of loop, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
-Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the kernel function for 86 times and get the final solution.
-\section{Simulation Results}
-\subsection{Environment}
-\subsubsection{Device}
-\emph{Graphic Processing Units}: GeForce GTX 760, GPU clock rate: 1.08 GHz , memory clock rate: 3 GHz , number of SM: 6, maximum number of threads per stream multiprocessor: 2048, total amount of global memory: 2 GB, total amount of share memory per block: 49 KB, total amount of constant memory: 66 KB.
-\\
-\emph{Central Processing Units-Modigliani}: Intel Core i5-4th generation, 4 cores 3.20 GHz CPU clock rate, 8 GB RAM\\
-\emph{Central Processing Units-Monet} : Intel Core i7-3rd generation, 12 cores 3.20 GHz CPU clock rate, 32 GB RAM\\
-\subsection{Software}
-CUDA Driver Version / Runtime Version      6.5 / 6.0\\
-Nsight Eclipse Version 6.5
-\subsection{Performance and Evaluation}
-\begin{table}[htb]
-\caption{Speedup Performance of different MIMO Array size}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{ Array size} & \multicolumn{3}{|c|}{Time/s} & \multicolumn{2}{|c|}{Speedup}\\
-\cline{2-6}
-&GTX 760 & modigliani & monet & GTX/modigliani  & GTX/monet \\
-\hline
-$8\time 8$& 0.46& 0.09&0.08 & 0.20& 0.17\\
-\hline
-$16\time 16$&1.56 &3.2&3.57& 2.05& 2.29\\
-\hline
-$20\time 20$&31 & 74& 81& 2.39& 2.61\\
-\hline
-$25\time 25$& 38& 112& 122& 2.94& 3.21\\
-\hline
-$32\time 32$& 611&2836&3033&4.64& 4.96 \\
-\hline
-\label{speedup}
-\end{tabular}
-\end{table}
-  \quad We test 5 array sizes and make comparison between GTX 760 and two kinds of CPU, all the operation times we test is based on 100 channel realizations, the transmitted data is generated randomly and modulated by $16$ QAM modulation scheme,  as we can see in \ref{speedup}, for small size array, like $8\times 8$, GPU has no advantage over CPU, for small array size, the number of path that need to be searched is relatively small, the CPU has already had a good performance, there is a short time for GPU to "warm up", for data transferring, launch kernel function and host device synchronization, further more, for small number of threads, the memory R/W latency is not well hided.
-When the array size grows large, a large parallelism is achieved so that the GPU begin to display its data processing power, and with the array size increasing, this speedup tends to be much more considerable.
-\section{Conclusion}
-In this paper, we present the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional platform, we have reached up to nearly 5 times acceleration of FCSD and this speedup grows higher with the increasing array size.
-In addition, the GPU and CPU can work independently, the data processing power of GPU computing is an extra bonus of the traditional simulation platform.
-This shows the potential of GPU computing for the simulation and consumptive computational work of large MIMO area.
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgement
-%\section*{Acknowledgment}
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-% that's all folks
 \end{spacing}

### 2015-04-17 Lattice Reduction/Report April 2015/Report_draft.tex

@@
 \end{equation}
-Proof: see Appendix B
+Proof: see Appendix B.
+
 Based on (\ref{formula11})(\ref{formula12})(\ref{formula14}), The logarithmic expectation of $\phi_{om}$ can be written as:
@@
 \begin{equation}
-\phi_{om}=\prod_{i=1}^{N_{t}}\frac{\beta_{i}}{\alpha_{i}+\beta_{i}},
+\phi_{om}=\prod_{i=1}^{N_{t}}\frac{\beta_{i}}{\beta_{i}+\alpha_{i}},
 \label{formula21}
@@
 \end{equation}
-Furthermore,from \cite{nagar2011expectations}, we have
+Furthermore, from \cite{nagar2011expectations}, we have
 
@@
 \end{eqnarray}
-if $\mathbf{\Sigma}=\mathbf{I}$, \ref{Appendequa4} can be written as 
+if $\mathbf{\Sigma}=\mathbf{I}$, (\ref{Appendequa4}) can be written as 
 \begin{equation}
@@
 \begin{equation}
-E[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\frac{d}{dn}\int_{\mathbf{A}=\mathbf{A}^{H}>0}det(\mathbf{A})^{n-m}etr(-\mathbf{A})d\mathbf{A},
+E[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\frac{d}{dn}\int_{\mathbf{A}=\mathbf{A}^{H}>0}etr(-\mathbf{A})det(\mathbf{A})^{n-m}d\mathbf{A},
 \label{Appendequa6}
@@
 Based on (\ref{Appendequa2}), we have 
-\begin{eqnarray}
-\tilde{\Gamma}^{'}_{m}(n)=\pi^{\frac{m(m-1)}{2}}\prod_{i=1}^{m}\Gamma^{'}(\beta-i+1),
-\end{eqnarray}
+\begin{equation}
+\tilde{\Gamma}^{'}_{m}(n)=\pi^{\frac{m(m-1)}{2}}\sum_{i=1}^{m}[\Gamma^{'}(n-i+1)\prod_{j=1,j\neq i }^{m}\Gamma(n-j+1)],
+\end{equation}
 Thus we have 
 \begin{equation}
-E[\ln(det(\mathbf{A}))]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}=\prod_{i=1}^{m}\psi(n-i+1),
+E[\ln(det(\mathbf{A}))]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}=\sum_{i=1}^{m}\psi(n-i+1),
 \label{Appendequa8}
@@
 \begin{equation}
-f_{y_{i}}((y)=|\frac{dy_{i}}{dx_{i}}|^{-1}f_{x_{i}}(g^{-1}(x_{i}))=\frac{1}{\mathbb{B}(k_{1}^{i},k_{2}^{i})}e^{-k_{1}^{i}y_{i}}(1-e^{-y_{i}})^{k_{1}^{i}-1}.
+f_{y_{i}}(\rho)=|\frac{dy_{i}}{dx_{i}}|^{-1}f_{x_{i}}(g^{-1}(\rho))=\frac{1}{\mathbb{B}(k_{1}^{i},k_{2}^{i})}e^{-k_{1}^{i}\rho}(1-e^{-\rho})^{k_{1}^{i}-1}.
 \label{Appendequal14}
@@
 \begin{equation}
-f_{y_{i}}(y)=\sum_{j^{i}=0}^{k_{2}^{i}-1}c(k_{1}^{i},k_{2}^{i}, j^{i})(k_{1}^{i}+j^{i})exp(-(k_{1}^{i}+j^{i})y_{i}).
+f_{y_{i}}(\rho)=\sum_{j^{i}=0}^{k_{2}^{i}-1}c(k_{1}^{i},k_{2}^{i}, j^{i})(k_{1}^{i}+j^{i})exp(-(k_{1}^{i}+j^{i})\rho),
 \label{Appendequal15}
 \end{equation} 
+where $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
 Based on the lemma 1 of \cite{bhargava1981distribution}, if $a_{1}, a_{2}, \cdots a_{n}$ are independent exponentially distributed random variables, with pdf given by
@@
 \end{equation} 
-then $a=\sum_{i=1}^{n}a_{i}$ can be written as
+then pdf of $a=\sum_{i=1}^{n}a_{i}$ can be written as
 \begin{equation}
-f(a|\mathbf{t})=\prod_{i=1}^{n}\sum_{i=1}^{n}[exp(-t_{i}a)\prod_{j=1\\ j\neq i}^{j=n}t_{j}-t_{i}],
+f(a|\mathbf{t})=\prod_{i=1}^{n}t_{i}\sum_{i=1}^{n}[exp(-t_{i}a)/\prod_{j=1\\ j\neq i}^{j=n}(t_{j}-t_{i})],
 \label{Appendequal17}
@@
 \begin{equation}
-f_{y}(m)=\sum_{\mathbf{j}}(\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i}, j^{i}))f(m|\mathbf{k_{1}}+\mathbf{j}),
+f_{y}(m)=\sum_{\mathbf{j}}\{[\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i}, j^{i})]f(m|\mathbf{k_{1}}+\mathbf{j})\},
 \label{Appendequal18}
 \end{equation}
-where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{n}}$, the range of $j^{i}$ is defined by $j^{i}\in [0, k_{2}^{i}]$, $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
-$f(m|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})m)/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$, $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1}, k_{1}^{2}+j^{2} \cdots k_{1}^{n}+j^{n}]$.
+where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{n}}$, the range of $j^{i}$ is defined by $j^{i}\in [0, k_{2}^{i}]$, $f(m|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})m)/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$, $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1}, k_{1}^{2}+j^{2} \cdots k_{1}^{n}+j^{n}]$.
 we define $U=exp(-y)=\prod_{i=1}^{n}x_{i}$, using Jacobian transformation, the pdf of $U$ is given by
 \begin{equation}
-f_{U}(u)=|\frac{du}{dy}|^{-1}f_{y}(-\ln(u))=\frac{1}{u}\sum_{\mathbf{j}}f(-\ln(u)|\mathbf{k_{1}}+\mathbf{j}).
+f_{U}(u)=|\frac{du}{dy}|^{-1}f_{y}(-\ln(u))=\frac{1}{u}\sum_{\mathbf{j}}\{[\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i},j^{i})]f(-\ln(u)|\mathbf{k_{1}}+\mathbf{j})\}.
 \label{Appendequal19}

### 2015-05-13 Lattice Reduction/Report April 2015/Report revised May 12 2015/Report_draft.tex
Final version of report in May 2015

--- 2015-04-17 Lattice Reduction/Report April 2015/Report_draft.tex
@@
 \section{Introduction}
-Detection algorithm is one of the key components of Multiple-Input Multiple-Output (MIMO) systems.
+Decoder is one of the key components of Multiple-Input Multiple-Output (MIMO) systems.
 Designing of high performance and low complexity detector has become a bottleneck of Large MIMO systems.
-Recently, academia has found a property of large MIMO channel called channel hardening phenomenon \cite{hochwald2004multiple}\cite{tse2005fundamentals}\cite{marvcenko1967distribution}\cite{tulino2004random}, which states the phenomenon that with the number of receiving or transmitting antennas increasing, the variances of channel mutual information decrease.
+Recently, an interesting property of large MIMO channel called channel hardening phenomenon has been found \cite{hochwald2004multiple}\cite{tse2005fundamentals}\cite{marvcenko1967distribution}\cite{tulino2004random}, which states the phenomenon that with the number of receiving or transmitting antennas increasing, the variances of channel mutual information decrease.
 Simply saying, the channel "hardens".
-An useful aspect of channel hardening phenomenon is the off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$ matrix becomes more and more ignorable comparing to diagonal elements when the number of receiving antennas or transmitting antennas becomes large.
+An useful aspect of channel hardening phenomenon is that off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$ matrix becomes more and more ignorable comparing to diagonal elements when the number of receiving antennas or transmitting antennas becomes large.
 
  Channel hardening phenomenon provides an opportunity for designing computationally economical detection algorithms.
-For example, linear detectors (LDs) such as zero forcing (ZF) and minimum mean square error (MMSE) detectors need to calculate the inverse of $\mathbf{H}^{H}\mathbf{H}$ matrix.
-This process can be accelerated by approximate matrix inversion using series expansion techniques and deterministic approximations in large dimensions\cite{wu2013approximate}.
+For example, linear detectors (LDs) such as zero forcing (ZF) and minimum mean square error (MMSE) detectors need to do costly matrix operations such as multiplication and inverse.
+With channel hardening phenomenon, this process can be accelerated by approximate matrix inversion using series expansion techniques and deterministic approximations in large dimensions\cite{wu2013approximate}.
 Channel hardening phenomenon can also provide computational advances to machine learning based detectors, e.g.
@@
 The rest of the report is organized as follows, section \ref{system model} introduces system model.
-Section \ref{preliminary} provides some preliminaries of the definition of orthogonality measurement.
+Section \ref{preliminary} provides some preliminaries.
 Section \ref{log expectation of om} discusses the derivation of logarithmic expectation of orthogonality measurement.
@@
 The possible transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian components of zero mean and unit variance.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian components with unit variance.
 Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
@@
 where $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$ denotes Wishart matrix, $\mathbf{h}_{i}$ denotes the $i$ th column of $\mathbf{H}$, $det(\cdot)$ denotes determinant operation, $||\cdot||^{2}$ denotes 2-norm operation.
-In (\ref{formula1}), $||\mathbf{h}_{i}||^{2}=\sum_{i=1}^{N_{t}}|\mathbf{H}_{ij}|^{2}$, $\mathbf{H}_{ij}$ denotes the component of $\mathbf{H}$ at $i$ th row and $j$ th column.
-$\mathbf{H}_{ij}\sim Rayleigh(1/\sqrt{2})$, therefore $||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},1)$\cite{papoulis1996stochastic}.
-$Gamma(k,\theta)$ denotes Gamma distribution, with $k$ degrees of freedom.
+In (\ref{formula1}), $||\mathbf{h}_{i}||^{2}=\sum_{j=1}^{N_{r}}|\mathbf{H}_{ji}|^{2}$, $\mathbf{H}_{ji}$ denotes the component of $\mathbf{H}$ at $j$ th row and $i$ th column.
+$|\mathbf{H}_{ji}|\sim Rayleigh(1/\sqrt{2})$, therefore $||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},1)$\cite{papoulis1996stochastic}.
+$Gamma(k,\theta)$ denotes Gamma distribution, with $k$ degrees of freedom and scale $\theta$.
 Furthermore, we have:
@@
 \end{equation}
-All the components in $\mathbf{R}$ are independently distributed and $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma((N_{r}-i+1),1)$ \cite{nagar2011expectations}.
+All the components in $\mathbf{R}$ are independently distributed and $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma(N_{r}-i+1,1)$ \cite{nagar2011expectations}.
 Because $|r_{ji}|\sim Rayleigh(1/\sqrt{2})$, $\sum_{j<i}|r_{ji}|^{2}\sim Gamma(i-1, 1)$.
-Defining $\alpha_{i}=\sum_{j<i}|r_{ji}|^{2}$ and $\beta_{i}=|r_{ii}|^{2}$, $\alpha_{i}$ and $\beta_{i}$ are mutually independent, therefore (\ref{formula9}) can be rewritten to
+Defining $\alpha_{i}=\sum_{j<i}|r_{ji}|^{2}$ and $\beta_{i}=|r_{ii}|^{2}$, $\alpha_{i}$ and $\beta_{i}$ are mutually independent, therefore (\ref{formula9}) can be rewritten as
 \begin{equation}
@@
 \section{Computer Simulations}\label{computer simulation}
- Computer simulations are made for different sizes of V-BLAST MIMO systems, with $5\leq N_{r} \leq 100, 5 \leq N_{t} \leq N_{r}$, the empirical estimation of logarithmic expectation of $\phi_{om}$, $E[\ln(\phi_{om})]_{em}$, is calculated by taking average over $1e4$ channel realizations for each size of MIMO systems, as shown in Fig.
-\ref{figure1}, the Theoretical logarithmic expectation of $\phi_{om}$ $E[\ln(\phi_{om})]_{t}$ in (\ref{formula25}) is plotted in Fig.
-\ref{figure2}.
+ Computer simulations are made for different sizes of V-BLAST MIMO systems, with $5\leq N_{r} \leq 100, 5 \leq N_{t} \leq N_{r}$, the empirical estimation of logarithmic expectation of $\phi_{om}$, $E[\ln(\phi_{om})]_{em}$, is calculated by taking average over $1e4$ channel realizations for each size of MIMO systems, as shown in Fig.\ref{figure1}, the Theoretical logarithmic expectation of $\phi_{om}$ $E[\ln(\phi_{om})]_{t}$ in (\ref{formula25}) is plotted in Fig.\ref{figure2}.
 Average deviation between $E[\ln(\phi_{om})]_{em}$ and $E[\ln(\phi_{om})]_{t}$ is also calculated, $V_{em-t}= 7.3043e-04$.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
+\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
+\label{figure1}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
+\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
+\label{figure2}
+\end{figure}
 
@@
 
-Fig.
-\ref{figure3} demonstrates the relation between the number of users ($N_{t}$) and $E[\ln(\phi_{om})]_{t}$ under cases of different numbers of antennas at base station ($N_{r}$).
-From Fig.
-\ref{figure3}, we can see, on the one hand, with $N_{r}$ fixed, $E[\ln(\phi_{om})]$ decreases while $N_{t}$ increases, however the gradient of each curve becomes more and more gentle.
+Fig.\ref{figure3} demonstrates the relation between the number of users ($N_{t}$) and $E[\ln(\phi_{om})]_{t}$ under cases of different numbers of antennas at base station ($N_{r}$).
+From Fig.\ref{figure3}, we can see, on the one hand, with $N_{r}$ fixed, $E[\ln(\phi_{om})]$ decreases while $N_{t}$ increases, however the gradient of each curve becomes more and more gentle.
 On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
-\begin{figure}[htb]
-\centering
-\centering\includegraphics[width=0.7\textwidth, height=5cm]{LogE_om_em.eps}
-\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
-\label{figure1}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth, height=5cm]{LogE_om_t.eps}
-\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
-\label{figure2}
-\end{figure}
 
@@
 
-The p.d.f function of $\mathbf{A}$ can be written as\cite{nagar2011expectations}:
+The pdf of $\mathbf{A}$ can be written as\cite{nagar2011expectations}:
 \begin{equation}
-f(A)=\{\tilde{\Gamma}_{m}(n)det(\mathbf{\Sigma})^{n} \}^{-1}det(A)^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A}),
+f(\mathbf{A})=\{\tilde{\Gamma}_{m}(n)det(\mathbf{\Sigma})^{n} \}^{-1}det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A}),
 \label{Appendequa1}
@@
 \begin{equation}
-E[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A})d\mathbf{A}.
+E[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}etr(-\mathbf{A})d\mathbf{A}.
 \label{Appendequa5}
@@
 \begin{equation}
-E[\ln(det(\mathbf{A}))]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}=\sum_{i=1}^{m}\psi(n-i+1),
+E[\ln(det(\mathbf{A}))]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}=\sum_{i=1}^{m}\frac{\Gamma^{'}(n-i+1)}{\Gamma(n-i+1)}=\sum_{i=1}^{m}\psi(n-i+1),
 \label{Appendequa8}
@@
 \begin{equation}
-f_{y_{i}}(\rho)=|\frac{dy_{i}}{dx_{i}}|^{-1}f_{x_{i}}(g^{-1}(\rho))=\frac{1}{\mathbb{B}(k_{1}^{i},k_{2}^{i})}e^{-k_{1}^{i}\rho}(1-e^{-\rho})^{k_{1}^{i}-1}.
+f_{y_{i}}(\rho)=|\frac{dy_{i}}{dx_{i}}|^{-1}f_{x_{i}}(g^{-1}(\rho))=\frac{1}{\mathbb{B}(k_{1}^{i},k_{2}^{i})}e^{-k_{1}^{i}\rho}(1-e^{-\rho})^{k_{2}^{i}-1}.
 \label{Appendequal14}
@@
 \end{equation}
-where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{n}}$, the range of $j^{i}$ is defined by $j^{i}\in [0, k_{2}^{i}]$, $f(m|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})m)/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$, $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1}, k_{1}^{2}+j^{2} \cdots k_{1}^{n}+j^{n}]$.
+where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{n}}$, the range of $j^{i}$ is defined by $j^{i}\in [0, k_{2}^{i}]$, $f(m|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp(-(k_{1}^{i}+j^{i})m)/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$, $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1}, k_{1}^{2}+j^{2} \cdots k_{1}^{n}+j^{n}]$.
 we define $U=exp(-y)=\prod_{i=1}^{n}x_{i}$, using Jacobian transformation, the pdf of $U$ is given by

### 2015-05-13 Lattice Reduction/Report April 2015/Report revised May 12 2015/Report_draft.tex
The final version 2nd revise

@@
 Simply saying, the channel "hardens".
-An useful aspect of channel hardening phenomenon is that off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$ matrix becomes more and more ignorable comparing to diagonal elements when the number of receiving antennas or transmitting antennas becomes large.
+An useful aspect of channel hardening phenomenon is that off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$ matrix become more and more negligible comparing to diagonal elements when the number of receiving antennas or transmitting antennas becomes large.
 
  Channel hardening phenomenon provides an opportunity for designing computationally economical detection algorithms.
-For example, linear detectors (LDs) such as zero forcing (ZF) and minimum mean square error (MMSE) detectors need to do costly matrix operations such as multiplication and inverse.
+For example, linear detectors (LDs) such as zero forcing (ZF) and minimum mean square error (MMSE) detectors need to do costly matrix operations such as matrix multiplication and inverse.
 With channel hardening phenomenon, this process can be accelerated by approximate matrix inversion using series expansion techniques and deterministic approximations in large dimensions\cite{wu2013approximate}.

### 2015-08-06 Report April 2014/draft.tex
Reorganized Report Record

--- 2014-10-27 parallel acceleration of FCSD based on cuda/draft.tex
@@
 \documentclass[12pt,a4paper,final]{article}
-%\documentclass[conference]{IEEEtrans}
 % Add the compsoc option for Computer Society conferences.
@@
 \usepackage{setspace} 
-\usepackage{multirow}
+\usepackage{diagbox}
 
@@
 %Montreal, Quebec}}
-\author{Tianpei Chen, Harry Leib\\
- Department of Electrical and Computer Engineering\\
- McGill University\\
- Montreal, Quebec}
+\author{Tianpei Chen\\
+ Department of Electrical and Computer Engineering\\}
 
@@
 % in the abstract
-\begin{abstract}
-The large MIMO system which is a scaling up of conventional MIMO systems with several hundreds of antennas at the base station serving several tens of terminals at the same time,  which is thought to be a big idea for the next generation wireless communication system.
-However the detection of the large MIMO system acquires a long time to get optimum or sub-optimum solutions, In order to accelerate the real-time decoder for large MIMO system, in this paper we present General Purpose Graphic Processing Units (GPGPU) implementation of Fixed Complexity Sphere Decoder (FCSD) for the large scale MIMO system based on the dominant propriety framework of GPGPU-Computed Unified Device Architecture (CUDA).
-The simulation shows a up to nearly $5$ times acceleration for $32\times 32$ array of whole application CPU version, furthermore, the proposed CUDA-FCSD algorithm shows a increasing speedup performance for a increasing array size.
-\end{abstract}
+%\begin{abstract}
+
+%\end{abstract}
 
@@
 
-\section{Introduction}
- The common challenge that all the researchers, engineers and industrial companies are now facing in wireless communication area is the sharp contrast between the increasing demand of the mobile network speed for the transmission of rich media content and better QoS (quality of service) and the limited bandwidth of the radio frequency spectrum and a complex space time varying wireless environment, moreover in foreseeable future this demand will continue grow.
-Multiple Input Multiple Output (MIMO) has become a very promising technology that can help to solve this problem, the core idea of MIMO is to use multiple antennas both at the transmitting end and receiving end, the spatial domain sampled signal can be combined to provide parallel data pipes so that it can provide array gain, spatial diversity gain, spatial multiplexing gain, and interference reduction\cite{oestges2010mimo}.
-LTE standard support up to 8 antennas at the base station\cite{dahlman20103g}, The large scale MIMO (also named massive MIMO) is a system with hundreds of low-power low-price antennas collocated at the base station and serving several tens of terminals at the same time\cite{rusek2013scaling}, originated from multiuser MIMO (MU-MIMO)\cite{larsson2013massive}.
-Large scale MIMO will inherit and enhance all the advantages of conventional MIMO (array gain, spatial diversity gain, spatial multiplexing gain and interference reduction), as well as reduction of latency, improvement of the whole system robustness.
- As a classical list based decoder for MIMO system, Sphere decoder (SD) can reach the optimum diversity gain as maximum likelihood (ML) detection with a dramatic complexity reduction\cite{viterbo1999universal}\cite{hassibi2005sphere}, however, there are two major problems of this decoder is the varied complexity with signal to noise ratio and sequential nature, which is contradictory with the requirement of a constant data processing throughput and parallel implementation for practical system.
-Fixed Complexity Sphere Decoder (FCSD), overcomes this two disadvantage of the SD by searching the solution along the fixed number independent multiple paths\cite{barbero2008fixing}.
-GPGPU (General purpose Graphic processing Units Computing) has become a big idea in the industry and research of a variety of areas that needs massive data analysis and computation such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435} and finance\cite{grauer2013accelerating}.
-Comparing to CPU, The GPU has been designed as computational intensive, with most of the hardware resource be allocated for data processing and parallel computation rather than caching and flow control.
-In recent years GPU has reached huge advantages in data processing speed over CPU\cite{nvidia2008programming}.
-CUDA (Computed unified Device Architecture) is a programming model for GPGPU that proposed by Nvidia which has becoming the dominant proprietary framework for GPGPU programming, it is based on popular programming languages(C, C++, java, python, Fortran, Direct Compute) so that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
-The core essence of the CUDA is the Single Instruction Multiple Threads (SIMT) programming model, enables GPU can accelerate a lot of applications with the large dataset by implementing parallel data processing of complex computations.
-CUDA has become a parallel computing platform for wide community of different application developers in different areas.
-\section{MIMO System Model}\label{system}
+\section{System Model}\label{system}
 % no \IEEEPARstart
@@
 %\hfill December 27, 2012
-We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive antennas and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, in the flat fading channel the corresponding discrete time model is given:
+Consider a MIMO system with $N_r$ receive antennas and $N_t$ transmit antennas, where $N_r$ is large, for simplification, we assume $N_r\to\infty$, the corresponding discrete time model is given:
 \begin{equation}
-y=\mathbf{H}s+n   \label{formula 1}
+y=\mathbf{H}s+n
 \end{equation}
-$s\in \mathbb{C}^{N_{t}\times 1}$ is the transmit symbol vector, the symbol in $s$ are mutually independent and taken from the signal constellation $\mathbb{O}$ (BPSK, QPSK, M-QAM), $M$ is the signal constellation size, all the transmit symbol vectors forms a $N_{t}$-dimensional signal constellation $\mathbb{O}^{N_{t}}$.
-$\varepsilon[ss^{H}]=I_{N_t}E_{s}$, $E_{s}$ denotes the symbol average energy where $\varepsilon$ denotes the mean operation.
-$y\in \mathbb{C}^{N_{r}\times 1}$ is the receive symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean elements of unit variance, $n\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) samples with zero mean elements of variance $\varepsilon[nn^{H}]=I_{N_{r}}N_{0}$, $N_{0}$ denotes the average noise energy, $\frac{E_{s}}{N_{0}}$ denotes the signal to noise ratio (SNR).
-\\
-  Assume we have the perfect channel state information (CSI)  $\quad \mathbf{H}$, receive symbol vector $y$, and we had already known the SNR, the task of decoder for MIMO system is to estimate $s$ in \ref{formula 1} based on CSI and received signal.
+$s\in \mathbb{C}^{N_{t}\times 1}$ is the transmit symbol vector, $y\in \mathbb{C}^{N_{r}\times 1}$ is the receive symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ is the channel propagation matrix with independent identity distributed(i.i.d) Circularly Symmetric Complex Gaussian(CSCG) zero mean elements of unit variance (Rayleigh fading), $n\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) with zero mean elements of variance $\sigma^{2}$, $\varepsilon(ss^{H})=E_{s}\mathbf{I}_{Nt}$, $E_s$ denotes the average symbol energy, $\varepsilon$ denotes the expectation operation and $M$ denotes the constellation size.
 
@@
 %\end{table}
-
-\section{CUDA GPU Architecture and  Programming Model} \label{programming model}
-  CUDA programming model is the C programming extension, with special defined syntax and structure, CUDA divide the CPU and GPU as host and device, the serial code executes on the host (CPU) side and parallel data processing is performed on the device (GPU) side, which is defined as heterogeneous programming model.
-The code executes on the device side is defined as $\mathit{kernel}$ function, which is a single instruction invoked at host side but with a massive parallel data processing threads execution on the device (SIMT), This programming architecture is askin to Single Instruction Multiple Data (SIMD), however unlike the SIMD vectoring machines, SIMT can branching the behavior of each threads so that reach thread-level parallelism, thread is the basic programming unit of CUDA, a block of cooperative threads form a thread block, in one block all the threads can share a memory called shared memory that all the threads in the block have the access to this pitch of memory, the GPU use massive number of threads to hide the long latency of global memory instead of using large cache as CPU, Another function of the thread block is all the thread execute in one block can synchronize their action.
-The warp is the basic schedule unit with a constant number of threads  (for current version of CUDA device, the warp size is 32), when one warp are waiting for data loading the other warps just begin to execute.
-In a word CPU cores are designed to minimize latency for each thread at a time , whereas GPUs are designed to handle a large number of concurrent, lightweight threads in order to maximize throughput.
-Blocks are grouped into a one-dimensional, two-dimensional, or three-dimensional grid, similarly, one thread block can also be organized into one-dimentional, two-dimensional or three-dimensional.
-The organization of the block and grid shape and dimension is determined by the concrete application, Figure \ref{figure1} shows the 3 dimensional thread hierarchy of CUDA.
-\begin{figure}[htb]
-\centering
-\includegraphics[scale=0.5]{CUDA_programming_hierachy.eps}
-\caption{CUDA 3D thread hierachy\\ $5\times 5\times 5$ grid and each block contains $5\times 5\times 5$ threads\\}
-\label{figure1}
-\end{figure}
-In Figure \ref{figure2} we use the GPU-GeForce GTX 760 as an example to show the microarchitecture of  GPU.
-The GPU works as a coprocessor system, consists of Stream Multiprocessors (SM), GeForce GTX 760 has 6 SM performs the multiply-add arithmetic operation and furthermore, each SM has the special functional units(SFU) that can perform more complex arithmetic operation such as trigonometric functions and reciprocal square root.
-the shared memory is also called on-chip memory which is located at SM that has low latency and limited capacity.
-Global memory, which is off-chip located memory of GPU with long latency and large capacity, another two types of the memory is called texture memory and constant memory, which are located off-chip , but cached, therefore the loading speed of the data located at these two type of memory space will be much faster than the that from global memory, for constant memory, it is read only and the memory latency is approximately as small as the registers.
-The variables invoked in kernel functions can be stored in either of the these 4 types of memories.
-Registers are allocated dynamically to threads.\\
-   Since the resource limitation of SM the total number of threads that we can define in one block is limited, on current CUDA supported GPUs, one block can contains up to 1024 threads, in addition all the blocks are executed on SMs, thus the total number of threads we can make use of is $T_{total}=Num_{SM}\times Num_{threads/SM}$, GeForce GTX 760 allows 2048 threads in one SM, thus the total number of threads that can work in parallel is $2048\times 6=12288$, although in concrete application, the programmer can allocate more than 12288 threads for a kernel, but the threads will work in serial, which will influence the performance of program.
-\begin{figure}[htb]
-\centering
-\includegraphics[scale=0.5]{High_view_of_CUDA_GPU_microarchitecture.eps}
-\caption{High View of CUDA CPU Microarchitecture}
-\label{figure2}
-\end{figure}   
+\section{Diversity Maximization Antenna Selection Criterion}\label{channel partition}
+First we consider a general case to illustrate how the diversity maximization antenna selection scheme works,
+$N_{t}-N$ denotes the number of selected antennas and $\mathbf{H_{j}}\in \mathbb{C}^{N_{r}\times (N_{t}-N)}$ denotes the associated propagation matrix, $j\in {\displaystyle\biggl[1,{N_{t}\choose N}\biggr]}$, $s_{d}\in \mathbb{C}^{(Nt-N)\times 1}$ denotes the the transmit symbol vector, $y_{d}\in \mathbb{C}^{Nr\times 1}$ denotes the received symbol vector, $n\in \mathbb{C}^{Nr\times 1}$ denotes the Additive White Gaussian Noise (AWGN) with zero mean and variance $\sigma^{2}$ hence
+\begin{equation}
+y_{d}=\mathbf{H}_{j}s_{d}+n
+\end{equation}
+matrix $\mathbf{G}_{j}\in \mathbb{C}^{(Nt-N)\times Nr}$ denote the linear equalizer(ZF/MMSE), the linear estimates after equalization $\hat{s_{d}}$ is expressed by:
+\begin{equation}
+\hat{s_{d}}=\mathbf{G}_{j}y_{d}=\mathbf{G}_{j}\mathbf{H}_{j}s_{d}+\mathbf{G}_{j}n\label{equation0}
+\end{equation}
+From (\ref{equation0}) we can see, the equalizer colors the noise, the off-diagonal elements of $\mathbf{G}_{j}\mathbf{H}_{j}$ contributes to spatial inter symbol interference, vector $\mathbf{G}_{j}n$, contributes to additional noise, from (\ref{equation0}) we have:
+\begin{equation}
+[\hat{s_{d}}]_{m}=(gh)_{m}s_{d}+g_{m}n=g_{m}h_{m}[s_{d}]_{m}+\sum_{f\neq m}g_{m}h_{f}[s_{d}]_{f}+g_{m}n\label{equation01}
+\end{equation}
+where $[\hat{s_{d}}]_{m}$ denotes the $m$th element of $\hat{s_{d}}$, $(gh)_{m}$ denotes the $m$th row of $\mathbf{G}\mathbf{H}_{j}$, $g_{m}$ denotes the $m$th row of $\mathbf{G}_{j}$ and $h_{m}$ denotes the $m$th column of $\mathbf{H}_{j}$, The post processing SINR of $m$th sub datastream and $j$th selected antenna subset is defined as\cite{3}:
+\begin{equation}
+\rho^{j}_{m}=\frac{E_{s}|g_{m}h_{m}|^{2}}{\sigma^{2}\parallel g_{m}\parallel^{2}+E_{s}\sum_{j\neq m}|g_{m}h_{j}|^{2}}
+\end{equation}
+$E_{s}$ and $\sigma$ are defined in section \ref{system}, $\sigma^{2}||g_{m}||^{2}$ is the energy of noise after equalization, which can be derived as follow:
+\begin{equation}
+\varepsilon[|g_{m}n|^{2}]= \varepsilon[(g_{m}n)(g_{m}n)^{H}]=\varepsilon[g_{m}nn^{H}g_{m}^{H}]=g_{m}\varepsilon[nn^{H}]g_{m}^{H}=g_{m}\sigma^{2}Ig_{m}^{H}
+=\sigma^{2}\parallel g_{m} \parallel^{2}
+\end{equation}
+as to $(gh)_{m}$, we have:
+\begin{equation}
+\varepsilon[(gh)_{m}s_{d}s_{d}^{H}(gh)_{m}^{H}]=(gh)_{m}\varepsilon[s_{d}s_{d}^{H}](gh)_{m}^{H}=(gh)_{m}E_{s}I(gh)_{m}^{H} =E_{s}||(gh)_{m}||^{2}\label{equation03}
+\end{equation}
+In (\ref{equation03}), $E_{s}||(gh)_{m}||^{2}=E_{s}|g_{m}h_{m}|^{2}+E_{s}\sum_{j\neq m}|g_{m}h_{j}|^{2}$, $E_{s}|g_{m}h_{m}|^{2}$ is the post processing energy of detected symbol, $E_{s}\sum_{j\neq m}|g_{m}h_{j}|^{2}$ is the energy of spatial inter symbol interference.
+\\
+Considering zero forcing algorithm first, the spatial equalizer $(\mathbf{G}_{j})_{ZF}=(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}\mathbf{H}_{j}^{H}$, therefore from (\ref{equation0}), $\mathbf{G}_{j}\mathbf{H}_{j}=\mathbf{I}_{N_t-N}$ and
+\begin{equation}
+(\rho_{ZF}^{j})_{m}=\frac{E_{s}}{\sigma^{2}\parallel g_{m} \parallel^{2}}\label{equation05}
+\end{equation}
+Let $\omega_{m}$ denote the $m$th row of $(\mathbf{H_{j}^{H}H_{j}})^{-1}$, we have
+\begin{equation}
+\parallel g_{m} \parallel^{2}=g_{m}g_{m}^{H}=\omega_{m}\mathbf{H}_{j}^{H}\mathbf{H}_{j}\omega_{m}^{H}\label{equation04}
+\end{equation}
+In (\ref{equation04}) we have $(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}\mathbf{H}_{j}^{H}\mathbf{H}_{j}=\mathbf{I}_{N_t-N}$, hence $\omega_{m}\mathbf{H_{j}}^{H}\mathbf{H_{j}}=e_{m}$, where $e_{m}$ deontes the row vector with $m$th element equals to 1, the others are all 0.
+Therefore (\ref{equation04}) can be written as:
+\begin{equation}
+\parallel g_{m} \parallel^{2}=((\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}_{mm})^{H}
+\end{equation}
+$((\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}_{mm})^{H}$ denotes the $m$th diagonal element of $((\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1})^{H}$.
+Because $\mathbf{H}_{j}^{H}\mathbf{H}_{j}$ is a Hermitian matrix, thus $((\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1})^{H}=(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}$\cite{7} and (\ref{equation05}) can be written as:
+\begin{equation}
+(\rho_{ZF}^{j})_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{mm}^{-1}}\label{equation02}
+\end{equation}\\
+Consider minimum mean square error (MMSE) detection, where $\mathbf{G}=\mathbf{G}_{MMSE}=(\mathbf{H}_{j}^{H}\mathbf{H}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}\mathbf{H}_{j}^{H}$, from \cite{5} \cite{6}, we have the expression of the post processing SINR of MMSE:
+\begin{equation}
+(\rho_{MMSE}^{j})_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}_{j}^{H}\mathbf{H}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}_{mm}}-1\label{equation3}
+\end{equation}
+where $(\mathbf{H}_{j}^{H}\mathbf{H}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}_{mm}$ denotes the $m$th diagonal element of $(\mathbf{H}_{j}^{H}\mathbf{H}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$.
+The criterion of the diversity maximization selection scheme is to choose the antenna subset which can maximize the worst post-processing SINR of the sub-datastream.
+The column elements of $\mathbf{H}_{j}$ are mutually independent Gaussian random variables, under favorable propagation condition, when $N_{r}\to \infty$ and the 2 norm of the column will become much larger than the inner product of two different columns.
+Hence, the columns of $\mathbf{H}_{j}$ become asymptotically orthogonal, a phenomenon that can be expressed as
+\begin{equation}
+\lim_{N_{r}\to \infty}\frac{(\mathbf{H}_{j}^{H}\mathbf{H}_{j})}{N_{r}}=\mathbf{I}_{N_t-N}
+\end{equation}
+ Where $\mathbf{I}_{N_t-N}$ denotes an $(N_{t}-N)\times (N_{t}-N)$ identity matrix.
+Based on this property, for any $m$, $(\rho_{MMSE}^{j})_{m}$ and $(\rho_{ZF}^{j})_{m}$ in (\ref{equation02})(\ref{equation3}) are all the same, meaning that we can select arbitrarily the $N_{t}-N$ antenna subset.
 % Note that IEEE does not put floats in the very first column - or typically
@@
 % command of the stfloats package.
-\section{GPU Based Acceleration of FCSD}
-In this section we present the parallel implementation of fixed complexity sphere decoder by GPU, first from (\ref{formula 1}), the maximum likelihood (ML) solution is given by:
+\section{Complexity Analysis of sel-MMSE and sel-MMSE-OSIC algorithm}\label{complexity}
+\subsection{sel-MMSE}\label{sel-MMSE}
+Define the cost of complex multiplication as 6 flops and complex addition as 2 flops, the sel-MMSE algorithm can be divided into 4 steps\cite{2}:\\
+\textbf{1}. Antenna selection\\
+Based on diversity maximization antenna selection criterion, divide the detection task into two parts:
 \begin{equation}
-s_{ML}=arg\min_{s\in \mathbb{O}^{N_{t}}}||y-\mathbf{H}s||^{2} \label{formula 2}
+y=\mathbf{H}_{1}s_{1}+\mathbf{H}_{2}s_{2}+n\label{equation 4}
 \end{equation}
-we consider the array $N_{t}=N_{r}$, performing QR decomposition to channel propagation matrix
+Hence there are $N_{u}=$ $N_{t}\choose N$ possible antenna subsets, $\mathbf{H}_{1}\in \mathbb{C}^{N_{r}\times N}$ and $\mathbf{H_{2}}\in C^{N_{r}\times (N_{t}-N)}$.\\
+\textbf{2}. As to $s_{1}\in \mathbb{C}^{N\times 1}$, we choose every possible symbol vector $s_{1}$ in the lattice and calculate:
 \begin{equation}
- \mathbf{H}=\mathbf{Q}\mathbf{R}  \label{QR}
+y^{k}=y-\mathbf{H}_{1}s_{1}^{k}   \label{equation41}
 \end{equation}
-where $\mathbf{Q}\in \mathbf{C}^{N_{t}\times N_{t}}$ is the unitary matrix, $\mathbf{R}\in \mathbf{C}^{N_{t}\times N_{t}}$, is the upper triangular matrix, the basing on \cite{matrix theory}, the (\ref{formula 2}) can be changed to
+$s_{1}^{k}$ denotes the $k$th possible $N\times 1$ symbol vector that is chosen in channel partition stage.
+For ML detection:
+\begin{equation}
+x^{ML}=arg\min_{s}\parallel y-\mathbf{H}s \parallel^{2}\label{equation 5}
+\end{equation}
+based on (\ref{equation 4}), (\ref{equation 5}) can be changed to
+\begin{equation}
+arg\min_{s_{1},s_{2}}\parallel y-\mathbf{H}_{1}s_{1}-\mathbf{H}_{2}s_{2} \parallel
+\end{equation} 
+At this stage sel-MMSE uses brute-force search, take every possible $s_{1}^{k}\in \mathbb{C}^{N\times 1}$ vector according to signal constellation into consideration, therefore there are $M^N$ possible $s_{1}^{k}$ \\
+\textbf{3}.
+For every $s_{1}^{k}$ calculate $y_{k}=y-\mathbf{H}_{1}s_{1}^{k}$.
+There are $M^{N}$ possible $s_{1}^{k}$ as well as $y^{k}$.
+Using linear detection or OSIC to estimate $s_{2}^{k}$, the estimation is expressed as $\hat{s_{2}}^{k}$, then mapping $\hat{s_{2}}^{k}$ to the constellation to the nearest points, we use $s_{2}^{k}$ to represent it, every $s_{1}^{k}$ corresponds to one $s_{2}^{k}$, hence there are $M^{N}$ posssible $s_{2}^{k}$.\\
+\textbf{4}. Find the solution $[s_{1}^{k},s_{2}^{k}]$ among $M^{N}$ candidates that has the minimum total Euclidean distance.\\
+\begin{equation}
+\hat{s}=arg\min_{k=1,2,\ldots,M^{N}}\parallel y^{k}-\mathbf{H}_{2}s_{2}^{k} \parallel^{2}\label{equation6}
+\end{equation}
+According to section \ref{channel partition}, based on diversity maximization antenna selection criterion and channel hardening phenomenon we can choose an arbitrary antenna subset, and hence the cost of antenna selection is zero.
+The second step calculating $y^{k}=y-\mathbf{H}_{1}s_{1}^{k}$, including an matrix multiplication and vector substruction,
+\begin{equation}
+N_{r}N \label{cost11}
+\end{equation}
+complex multiplications and
+\begin{equation}
+ N_{r}N  \label{cost21}
+\end{equation}
+ complex substitution are required. Then calculate the MMSE estimation $\hat{s}_{2}^{k}$:
+\begin{equation}
+\hat{s}_{2}^{k}=[\mathbf{H}_{2}^{H}\mathbf{H}_{2}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H}_{2}^{H}y^{k}\label{equation7}
+\end{equation}
+$\mathbf{H}_{2}\in \mathbb{C}^{N_{r}\times (N_{t}-N)}$, the calculation of weight matrix $\mathbf{G}_{MMSE}=[\mathbf{H}_{2}^{H}\mathbf{H}_{2}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H}_{2}^{H}$, because of the channel hardening phenomenon mentioned in section \ref{channel partition}, $\mathbf{G}_{MMSE}=[\mathbf{H}_{2}^{H}\mathbf{H}_{2}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H}_{2}^{H}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}\mathbf{I}\mathbf{H}_{2}^{H}$, hence the calculation of $\mathbf{G}_{MMSE}$ is real-complex multiplication, which cost 2 flops, 1/3 of complex multiplication, hence get $\mathbf{G}_{MMSE}$ requires:
+\begin{equation}
+\frac{(N_{t}-N)N_{r}}{3}    \label{cost31}
+\end{equation}\\
+complex multiplication.\\
+In the whole process $\mathbf{G}_{MMSE}$ only need to be calculated one time. Calculation of $\hat{s}_{2}^{k}=\mathbf{G}_{MMSE}y_{k}$ is the complex matrix multiplication which requires:
+\begin{equation}
+ (N_{t}-N)N_{r} \label{cost12}
+\end{equation}
+ complex multiplications and 
+ \begin{equation}
+ (N_{t}-N)(N_{r}-1) \label{cost22}
+ \end{equation}
+complex additions.
+Finally the calculation of MED in (\ref{equation6}) requires matrix multiplication, vector substruction which cost $ N_{r}(N_{t}-N)$ complex multiplications and $ N_{r}(N_{t}-N)$ complex additions and the calculation of 2-norm, which includes the calculation of absolute value and real number addition, calculation of absolute value cost 3 flops, which is $1/2$ of the cost of complex multiplication, real number addition cost 1 flop which is $1/2$ of the cost of complex addition.
+Hence the calculation of 2-norm costs $\frac{N_{r}}{2}$ complex multiplications and $\frac{N_{r}-1}{2}$ complex additions.
+Totally, the calculation of MED costs:
+ \begin{equation}
+  N_{r}(N_{t}-N)+\frac{N_{r}}{2}\label{cost13}
+\end{equation}  
+ complex multiplications and
+ \begin{equation}
+   N_{r}(N_{t}-N)+\frac{N_{r}-1}{2}\label{cost23}
+ \end{equation}
+complex additions are required.
+All the above are the cost of single candidate  $[s_{1}^{k},s_{2}^{k}]$, Totally as mentioned before there are $M^N$ possible solution candidates $[s_{1}^{k},s_{2}^{k}]$, therefore the sel-MMSE requires overall adding (\ref{cost11})(\ref{cost31})(\ref{cost12})(\ref{cost13}), please notice (\ref{cost31}) only need to be calculated one time in the whole process.
+\begin{equation}
+M^{N}(N_rN+(N_{t}-N)N_r+N_r(N_t-N)+\frac{N_r}{2})+\frac{(N_{t}-N)N_{r}}{3}=M^{N}(2N_{r}N_{t}-N_{r}N+\frac{N_r}{2})+\frac{(N_{t}-N)N_r}{3}\label{equation8}
+\end{equation}
+complex multiplications and adding (\ref{cost21})(\ref{cost22})(\ref{cost23})
+\begin{equation}
+M^{N}(N_rN+(N_t-N)(N_r-1)+N_r(N_t-N)+\frac{N_r-1}{2})=M^{N}(2N_{r}N_{t}-N_{r}N-N_{t}+N+\frac{N_{r}-1}{2})\label{equation9}
+\end{equation}
+complex additions, Based on (\ref{equation8})(\ref{equation9}) and with 6 flops for complex multiplication and 2 flops for complex addition, we have the total cost of sel-MMSE algorithm as
 \begin{eqnarray}
 \nonumber
-s_{ML}&=&arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}y-\mathbf{Q}^{H}\mathbf{H}s||^{2}\\
-&=& arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{Q}^{H}y-\mathbf{R}s||^{2} \label{formula 3}
+f_{sel-MMSE}(N) &=& 6[M^{N}(2N_{r}N_{t}-N_{r}N+\frac{N_r}{2})+\frac{(N_{t}-N)N_r}{3}]\\  
+&+&2M^{N}(2N_{r}N_{t}-N_{r}N-N_{t}+N+\frac{N_{r}-1}{2})\\
+\nonumber 
+&=&M^{N}(16N_{r}N_{t}-8N_{r}N+4N_{r}-2N_{t}+2N-1)+2(N_{t}-N)N_{r}\quad flops  \label{equation10}
 \end{eqnarray}
-Consider the unconstrained estimation of $s$, $\hat{s}=\mathbf{G}y$, $\mathbf{G}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}$ denotes the zero forcing equalizer, basing on \ref{QR}, we have  
+According to \cite{2}, the complexity of sel-MMSE algorithm without making use of channel hardening phenomenon is 
+\begin{eqnarray}
+\nonumber
+f_{sel-MMSE_{O}}(N)&=&  N_{u}[4(N_t-N)^3+(N_t-N)^2(4N_r+1)+(N_t-N)(4N_r-6)+6]+N_r(N_t-N)\\
+&&(8N_t-8N-2)+M^{N}(16N_{r}N_{t}-8N_{r}N+4N_{r}-1-2N_{t}+2N)\quad flops \label{equation52}
+\end{eqnarray}
+where $N_{u}={\displaystyle{N_{t}\choose N}}$.
+Table \ref{table_sel-MMSE} shows the complexity comparison between $f_{sel-MMSE}$and$f_{sel-MMSE_{O}}$, at channel partition stage they all use diversity maximization scheme in \cite{2} to determine $N$.
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\diagbox{$M$}{$\frac{f_{sel-MMSE}}{f_{sel-MMSE_{O}}}$}{ $N_{r}\times N_{t}$}&$10\times 10$&$32\times 32$&$64\times 64$&$128\times 128$\\\hline
+
+BPSK&0.0249&1.3746e-05&2.3406e-09&1.5672e-14\\\hline
+
+QPSK&0.1683&4.3817e-04&5.9893e-07&3.2095e-11\\\hline
+
+16QAM&0.9282&0.3098&0.0378&1.3460e-04\\\hline
+
+64QAM&0.9988&0.9978&0.9996&0.9982\\
+\hline
+\end{tabular}
+\caption{complexity comparison between $f_{sel-MMSE}$ and $f_{sel-MMSE_{O}}$}
+\label{table_sel-MMSE}
+\end{table} 
+From table \ref{table_sel-MMSE} we can see, as the size of array increases, the complexity abbreviation gain increases, as the size of signal constellation increases, the complexity abbreviation gain decreases.
+\subsection{sel-MMSE-OSIC}
+First we use a general case to illustrate how MMSE-OSIC works. Consider a MIMO system as mentioned in section \ref{system}:
 \begin{equation}
-\hat{s}=\mathbf{G}y=(\mathbf{R}^{H}\mathbf{R})^{-1}\mathbf{R}^{H}\mathbf{Q}^{H}y=\mathbf{R}^{-1}\mathbf{Q}^{H}y 
-\label{unconstrained estimation}
+y=\mathbf{H}s+n\label{equation07}
 \end{equation}
-Therefore $\mathbf{Q}^{H}y=\mathbf{R}\hat{s}$, the \ref{formula 3} can be changed to
+With $\mathbf{G}_{MMSE}=(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}\mathbf{H}^{H}$, after equalization using $\mathbf{G}_{MMSE}$,  (\ref{equation07}) can be changed to 
 \begin{equation}
-s_{ML}=arg\min_{s\in \mathbb{O}^{N_{t}}}||\mathbf{R}(\hat{s}-s)||^{2} \label{formula 4}
+\hat{s}=\mathbf{G}_{MMSE}y=\mathbf{G}_{MMSE}Hs+\mathbf{G}_{MMSE}n\label{equation08}
 \end{equation}
-the Fixed Complexity Sphere Decoder works as a constant number of multiple path tree searching.
-\begin{figure}[tb]
+where $\hat{s}$ denote the unconstrained estimate of $s$. From (\ref{equation08}) we can express $m$th estimation of sub-datastream $\hat{s}_{m}$:
+\begin{equation}
+\hat{s}_{m}={g_{m}}y\label{equation09}
+\end{equation}
+where $g_{m}$ denote the $m$th row of $\mathbf{G}_{MMSE}$, unlike MMSE, the MMSE-OSIC algorithm detects the $s_{m}$ symbol by symbol.
+The detection order at every iteration is based on the following principle: $\hat{s_{m}}$ is detected based on their post-processing SINR at each iteration, where $\hat{s}_{m}$ with the highest SNR will be detected.
+According to (\ref{equation3}), the post processing SINR is associated to the diagonal elements of $(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$.
+The smaller is the $m$th diagonal element of $(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$, the higher is the post-processing SINR of $\hat{s}_{m}$.
+Because there are $N_{t}$ symbols in vector $s$, hence MMSE-OSIC algorithm will detect $s_{m}$ for $N_{t}$ times, in the $i$th ($i\in [0,N_{t}-1]$) iteration, it majorly has 3 steps:\\
+\textbf{1}.Ordering the channel based on the principle mentioned above, choose the sub-datastream with highest SNR(smallest diagonal element of $((\mathbf{H}_{j}^{i})^{H}\mathbf{H}_{j}^{i}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$ to detect, $\mathbf{H}_{j}^{i}\in \mathbb{C}^{Nr\times (Nt-N-i)}$ denotes the $i$th step sub-matrix in MMSE-OSIC iteration from the $j$th propagation matrix after channel partition as mentioned in section \ref{channel partition}, $\mathbf{H}_{j}^{0}=\mathbf{H}_{j}$\\
+\textbf{2}.Find the unconstrained estimate
+\begin{equation}
+\hat{s}_{i+1}=g_{i+1}y_{i}\label{equation012}
+\end{equation}
+and slice $\widehat{s_{i+1}}$ to $\bar{s}_{i+1}$ corresponds to signal constellation.\\
+\textbf{3}.Cancel the information correlated to  $\bar{s_{i}}$ from received vector $y_{i}$, $h_{m}\quad m\in [1,N_{t}]$ denotes the $m$th column of $\mathbf{H}_{j}^{i}$, $s_{2m}$ denotes the $m$th symbol of $s_{2}$.
+We have
+\begin{equation}
+y_{k}=\sum_{m=1,2,\ldots Nt-N}h_{m}s_{2m}+n
+\end{equation}
+Therefore the cancellation step is removing $\bar{s}_{i+1}$ and corresponding channel column $h_{i+1}$
+\begin{equation}
+y_{i+1}=y_{i}-h_{i+1}\bar{s}_{i+1}\label{equation091}
+\end{equation} 
+Then update propagation matrix by removing the column $h_{i+1}$ from $\mathbf{H}_{j}^{i}$.\\
+Consider now the computational complexity of sel-MMSE-OSIC.
+The difference between sel-MMSE-OSIC and sel-MMSE is in the linear detection step to detect $s_{2}$ in $y=\mathbf{H}_{1}s_{1}+\mathbf{H}_{2}s_{2}+n$, so that their computation cost except this step are all the same.
+Firstly finding $y^{k}$ in (\ref{equation41}) requires $N_{r}N$ complex multiplications and $N_{r}N$ complex additions.
+In MMSE-OSIC detection of $s_{2}^{k}$, when $N_{r}\to \infty$, because of channel hardening phenomenon, at $i$th iteration($i\in [0,\quad N_{t}-N-1]$) in step 1, the diagonal elements of $(\mathbf{H}^{i}_{j})^{H}\mathbf{H}^{i}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$ are all the same.
+Therefore the post-processing SINR of $\hat{s_{m}}$ are all the same, detection order can be arbitrary, the step 1 in MMSE-OSIC can be ignored.
+in the second step, based on (\ref{equation09}) and channel hardening phenomenon, $\mathbf{G}_{MMSE}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}(\mathbf{H}^{i}_{j})^{H}$, $\upsilon_{m}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}\theta_{m}^{H}$, where $\theta_{m}^{H}$ denotes the $m$th row of $(\mathbf{H}^{i}_{j})^{H}$, hence finding the the weight vector requires a real-complex vector multiplication, with cost of $\frac{N_{r}}{3}$ complex multiplications, totally $N_{t}-N$ weight vectors need to be calculated, therefore $(N_{t}-N)\frac{N_{r}}{3}$ complex multiplications are needed, furthermore based on (\ref{equation012}) getting the detection statistic $\hat{s}_{i}$ requires $N_{r}$ complex multiplications and $N_{r}-1$ complex additions, then the interference cancellation step in (\ref{equation091}) requires $N_{r}$ complex multiplications and $N_{r}$ complex additions.
+Since the MMSE-OSIC algorithm performs $N_{t}-N$ iteration, the cost of getting $\hat{s}_{2}$ is:
+\begin{equation}
+M^{N}(2N_{r}(N_{t}-N))+(N_{t}-N)\frac{N_{r}}{3}\label{cost14}
+\end{equation} 
+complex multiplications and
+\begin{equation}
+M^{N}(2N_{r}-1)(N_{t}-N)\label{cost24}
+\end{equation}
+complex additions.\\
+Basing on (\ref{equation091}), after $N_{t}-N$ iterations $y^{k}-\mathbf{H}_{2}s_{2}^{k}$ has already been calculated, therefore finding MED in (\ref{equation6}) just requires additional 
+\begin{equation}
+N_{r}/2     \label{cost41}
+\end{equation}
+complex multiplications and 
+\begin{equation}
+(N_{r}-1)/2  \label{cost42}
+\end{equation}
+complex additions, the total cost:\\
+Adding (\ref{cost11})(\ref{cost14})(\ref{cost41})
+\begin{equation}
+M^{N}(N_{r}N+2N_{r}(N_{t}-N)+\frac{N_{r}}{2})+(N_{t}-N)\frac{N_{r}}{3}\label{equation010}
+\end{equation}
+complex multiplications and adding (\ref{cost21})(\ref{cost24})(\ref{cost42})
+\begin{equation}
+M^{N}(N_{r}N+(2N_{r}-1)(N_{t}-N)+\frac{N_{r}-1}{2})\label{equation011}
+\end{equation}
+complex addtions.
+The computation cost in flops, based on (\ref{equation010})(\ref{equation011}) is
+\begin{eqnarray}
+f_{sel-MMSE-OSIC}(N) &=& 6[M^{N}(2N_{r}N_{t}-N_{r}N+\frac{N_r}{2})+\frac{(N_{t}-N)N_r}{3}]\\  
+&+&2M^{N}(2N_{r}N_{t}-N_{r}N-N_{t}+N+\frac{N_{r}-1}{2})\\
+\nonumber 
+&=&M^{N}(16N_{r}N_{t}-8N_{r}N+4N_{r}-2N_{t}+2N-1)+2(N_{t}-N)N_{r}\quad flops\label{flop2}
+\end{eqnarray}
+From (\ref{equation10})(\ref{flop2}), $f_{sel-MMSE-OSIC}(N)=f_{sel-MMSE}(N)$.\\
+According to \cite{2}, the complexity of sel-MMSE-OSIC algorithm without making use of channel hardening phenomenon is 
+\begin{eqnarray}
+\nonumber
+f_{sel-MMSE-OSIC_{O}}(N)&=& N_u[4(N_{t}-N)^{3}+(N_{t}-N)^{2}(4N_{r}+1)+(4N_{r}-6)(N_{t}-N)+6]\\
+\nonumber
+&+&4/3(N_{t}-N)^{3}+(N_{t}-N)^{2}(4N_{r}+3)+(N_{t}-N)(2N_{r}-13/3)\\
+\nonumber
+&+&M^{N}(16N_{r}N_{t}-8N_{r}N+4N_{r}-2N_{t}+2N-1)\quad flops\\
+\end{eqnarray}
+Table \ref{table_sel-MMSE-OSIC} shows the complexity comparison between $f_{sel-MMSE}$and$f_{sel-MMSE_{O}}$, at channel partition stage they all use diversity maximization scheme in \cite{2} to determine $N$.
+\begin{table}[t]
 \centering
-\includegraphics[scale=0.5]{FCSD_tree_searching.eps}
-\caption{Tree searching of QPSK FCSD for 8x8 MIMO system}
-\label{figure4}
-\end{figure}
-As shown in Figure \ref{figure4}, just like SD the FCSD also performs depth first searching, at the first $\rho$ level the FCSD search all the possible signal symbols $\widetilde{s}_{N_{t}} \widetilde{s}_{N_{t}-1}\dots \widetilde{s}_{N_{t}-\rho+1}$ in constellation $\mathbb{O}^{N_{t}}$, which is called Full Expansion(FE) level, the remain $N_{t}-\rho$ levels of symbols, the FCSD performs decision feed back equalization (DFE), from (\ref{formula 4}) the solution of FCSD can be given:
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\diagbox{$M$}{$\frac{f_{sel-MMSE-OSIC}}{f_{sel-MMSE-OSIC_{O}}}$}{ $N_{r}\times N_{t}$}&$10\times 10$&$32\times 32$&$64\times 64$&$128\times 128$\\\hline
+
+BPSK&0.0250&1.3746e-05&2.3406e-09&1.5672e-14\\\hline
+
+QPSK&0.1687&4.3817e-04&5.9893e-07&3.2095e-11\\\hline
+
+16QAM&0.9284&0.3098&0.0378&1.3460e-04\\\hline
+
+64QAM&0.9988&0.9978&0.9996&0.9982\\
+\hline
+\end{tabular}
+\caption{complexity comparison between $f_{sel-MMSE-OSIC}$ and $f_{sel-MMSE-OSIC_{O}}$}
+\label{table_sel-MMSE-OSIC}
+\end{table} \\
+From table \ref{table_sel-MMSE-OSIC} we can see, as the size of array increases the complexity abbreviation gain increases, as the size of signal constellation increases, the complexity abbreviation gain decreases.
+\section{Minimization of the Complexity}\label{minimization}
+Consider $N_{r}\leq 2\quad N_{t}\leq 2\quad M\leq 2$. 
+\subsection{sel-MMSE}
+Proposition 1: $f_{sel-MMSE}(N)$ increases when $N$ increases, in $[1,N_{t}-1]$\\
+Proof: According to section(\ref{complexity}), the computational cost of sel-MMSE algorithm is:
 \begin{equation}
-\hat{s}_{FCSD}=arg\min_{s\in \mathbb{O}^{N_{t}}}\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s_{j})|^{2}  \label{formula 5}
+f_{sel-MMSE}(N)=M^{N}(16N_{r}N_{t}-8N_{r}N+4N_{r}-2N_{t}+2N-1)+2(N_{t}-N)N_{r}\quad flops
 \end{equation}
-$i\in [1,2\dots N_{t}]$, $r_{ij}$ denotes the element at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$, this process is called Single Expansion (FE).
-thus the FCSD solution $s_{FCSD}=[s_{1},s_{2}\dots s_{N_{t}}]$ can be expressed as:
+In this section a discussion of the relation between $N$ and $f(N)$ is presented. Firstly we assume $N$ is a real number, take the derivative of $f_{sel-MMSE}(N)$,
+\begin{equation}
+\frac{\partial f_{sel-MMSE}(N)}{\partial N}=M^{N}[(16N_{r}N_{t}+4N_{r}-2N_{t}-1)\ln{M}+(2-8N_{r})(N\ln{M}+1)]-2N_{r}\label{equation11}
+\end{equation}
+according to (\ref{equation11}), obviously when $N\geq 0\quad$, $\frac{\partial f_{sel-MMSE}(N)}{\partial N}$ increases with $N$ increasing, consider $N=0$, we have:
+\begin{eqnarray}
+\nonumber
+\frac{\partial f_{sel-MMSE}(0)}{\partial N}&=&\ln{M}(16N_{r}N_{t}+4N_{r}-2N_{t}-1)+2-10N_{r}\\
+\nonumber
+&=&\ln{M}[4(N_{t}+1)N_{r}+2(N_{r}-1)N_{t}]+10N_{r}(N_{t}\ln{M}-1)+2-\ln{M}  \label{equation51}
+\end{eqnarray}
+because $N_{r}\geq 2$ $N_{t}\geq 2$ $M\geq 2$, therefore $\ln{M}[4(N_{t}-1)N_{r}+2(N_{r}-1)N_{t}]>0$, $\ln{M}\geq 0.6931$, $N_{t}\ln{M}\geq 1.3863$, hence $10N_{r}(N_{t}\ln{M}-1)+2>9.7259\quad$, if $M<1.6746\times 10^{4}$, $10N_{r}(N_{t}\ln{M}-1)+2-\ln{M}>0$, for the signal constellation size we consider, we can conclude that $10N_{r}(N_{t}\ln{M}-1)+2-\ln{M}>0$ holds, therefore $\frac{\partial f_{sel-MMSE}(0)}{\partial N}>0$.\\
+In conclusion when $N\geq 0$, $\frac{\partial f_{sel-MMSE}(N)}{\partial N}>0$, proposition 1 is proved.
+\subsection{sel-MMSE-OSIC}
+Proposition 2: $f_{sel-MMSE-OSIC}(N)$ increases when $N$ increases, when $N\in [1, N_{t}-1]$\\
+Proof: From section (\ref{complexity}), the complexity expressions of sel-MMSE and sel-MMSE-OSIC are the same, therefore, proposition 2 holds.
+
+\section{Trade off between Complexity and diversity}
+Sel-MMSE and sel-MMSE-OSIC can achieve optimal diversity gain $N_{r}$ asymptotically \cite{6} \cite{9} with $SNR\to \infty$ in a $N_{r}\times N_{t}$ spatial multiplexing system\cite{2}, however the most of practical communication systems are working under a moderate SNR, further more the optimal diversity gain of massive MIMO system is extensively large which is unnecessary, on the other hand, achieving the asymptotically optimal diversity gain will lead to extremely high complexity, therefore we consider sacrifice redundant diversity gain and abbreviate complexity.\\
+let $P_{e}$ denotes the average probability of detection error of sel-MMSE and sel-MMSE-OSIC, $P_{e}^{ML}$ denotes the average probability of detection error of Maximum-Likelihood detection, $(P_{e})_{2}$ denotes the average probability of detection error of $s_{2}^{k}$ after channel partition, $P_{e}$ is bounded by\cite{2}:
+\begin{equation}
+\max[(P_{e})_{2},P_{e}^{ML}]\leq P_{e} \leq P_{e}^{ML}+(P_{e})_{2}\label{equation16}
+\end{equation}
+The diversity gain of sel-MMSE and its OSIC counterpart are expressed by $d_{MMSE}$ and $d_{MMSE-OSIC}$ diversity maximization selection, they can be expressed as\cite{2}
+\begin{equation}
+d_{MMSE}=(N+1)(N_{r}-N_{t}+N+1)  \label{conjecture1}
+\end{equation}
+\begin{equation}
+d_{MMSE-OSIC}=(N+1)(N_{r}-N_{t}+N+1)\label{conjecture2}
+\end{equation}
+(\ref{conjecture1}) is proven in \cite{9}, in \cite{2}, $d_{MMSE-OSIC}\geq (N+1)(N_{r}-N_{t}+N+1)$ is proven however strictly proven of (\ref{conjecture2}) is still lacking.
+therefore we take (\ref{conjecture2}) as a conjecture here.
+\begin{equation}
+\lim_{SNR\rightarrow \infty}\frac{\log{P_{e}^{ML}}}{\log{SNR}}=-N_{r}
+\end{equation}   
+\begin{equation}
+\lim_{SNR\rightarrow \infty}\frac{\log{(P_{e})_{2}}}{\log{SNR}}=-d
+\end{equation}
+let $(P_{e})_{2}^{LD}$ denote the average probability of detection error of $s_{2}^{k}$ using linear detection.
+If $d\geq N_{r}$, sel-MMSE can achieve optimal performance asymptotically $\lim_{SNR\rightarrow \infty}P_{e}=P_{e}^{ML}$.
+If $d<N_{r}$, $\lim_{SNR\rightarrow \infty}\frac{\log{P_{e}}}{\log{SNR}}=d$\cite{2}.
+ $0\leq x\leq N_{r}$ denote the minimum required diversity.\\
+Define
+\begin{equation}
+g(N)=d-x=(N+1)(N_{r}-N_{t}+N+1)-x\label{equation17}\quad 1\leq N\leq N_{t}-1
+\end{equation}
+Based on the results in section \ref{minimization}, we seek minimum $N$ ($N_{min}$) satisfying $g(N)\geq 0$. We see that $g(N)$ is a quadratic function of $N$ with the two zero points:
+\begin{equation}
+N_{1}=\sqrt{x+1/4(N_{r}-N_{t})^2}-1/2(N_{r}-N_{t})-1\label{equation18}
+\end{equation}
+ \begin{equation}
+N_{2}=-\sqrt{x+1/4(N_{r}-N_{t})^2}-1/2(N_{r}-N_{t})-1\label{equation19}
+\end{equation} 
+Assume $N_{r}\geq 2$ $N_{t}\geq 2$
+
+Consider the following conditions:\\
+\textbf{1}. $N_{1}>0\quad N_{2}>0$\\
+It is obvious that $N_{1}>N_{2}$, thus when $N_{2}>0$ this condition is satisfied.
+\begin{eqnarray}
+\nonumber
+N_{2}>0 &\rightarrow & -\sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}-\frac{1}{2}(N_{r}-N_{t})-1>0\\
+&\rightarrow & \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}<\frac{1}{2}(N_{t}-N_{r})-1 \label{condition1}
+\end{eqnarray}
+(\ref{condition1}) holds when the following 3 conditions are satisfied:
 \begin{displaymath}
-s_{FCSD}^{i}=\left\lbrace\begin{array}{c}
-\in \mathbb{O}^{\rho}      \quad i=N_{t},N_{t}-1,\dots N_{t}-\rho+1\\
-\mathbb{Q}[\hat{s}_{i}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}}-s_{FCSD}^{i})] \quad i=N_{t}-\rho,N_{t}-\rho-1,\dots 2,1 \\
+\left\{\begin{array}{ll}
+\frac{1}{2}(N_{t}-N_{r})-1>0&\rightarrow N_{t}>N_{r}+2\\
+0<x< N_{r}-N_{t}+1&\rightarrow N_{t}<N_{r}+1\\
 \end{array}\right.
 \end{displaymath}
-$\mathbb{Q}[]$ denotes the signal constellation based quantization. At the post processing stage, FCSD takes the symbol vector candidate with the minimum Euclidean metric $E_{metric}$:
-\begin{equation}
-E_{metric}=||\mathbf{R}(\hat{s}-\widetilde{s})||^{2}
-\end{equation} 
-The $\widetilde{s}$ denotes the symbol vector candidate, the total number of candidates is: 
-\begin{equation}
-M^{\rho}     \label{path number}
-\end{equation} 
-\subsection{CUDA-FCSD Pre-Prossing}
-As shown in figure.4, each path of the FCSD searching has a serial execution nature, in order to avoid error propagation of decoder, FCSD ordering was applied to the propagation channel based on post processing signal to noise ratio\cite{Vblas}, which can be expressed as:
-\begin{equation}
-\varphi_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}}  \label{ppsnr}
-\end{equation}
-$\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inversion of $HHH$ matrix $\mathbf{H}^{H}\mathbf{H}$, thus when the SNR is determined, the post processing SNR is only determined by $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$, for the FE stage the robustness of detector performance is not influenced by the post processing SNR thus at FE stage the "weakest" data stream is detected first, that is, the data stream with the smaller $\varphi$ is detected earlier.
-At SE stage, because of the single searching path of the symbol, the performance is tightly related to the post processing SNR, therefore at SE stage the data streams with the larger post processing SNR is detected earlier in order to avoiding the error propagation, in conclusion the FCSD ordering works iteratively  and obeys the following rule:
-At the $j$th step ($j=1,2\dots N_{t}-1$), $s_{p}$ denotes the symbol to be detected, where 
-\begin{displaymath}
-p=\left\lbrace \begin{array}{c}
-arg \max_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad FE stage\\
-arg \min_{k}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{kk}^{-1}\quad SE stage \\  \label{the ordering}
-\end{array}\right.  
-\end{displaymath}  
-$\mathbf{H}_{j}\in \mathbb{C}^{N_{r}\times (N_{t}-j+1)}$ denotes the renewed channel matrix, at the $j$th iteration with the column corresponding to previous detected data streams removed from $\mathbf{H}_{j-1}$.
-the unconstrained estimation $\hat{s}$ in \ref{unconstrained estimation}  in is given by:
-\begin{equation}
- \hat{s}=(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y \label{shat}
-\end{equation}
-
-Although the FCSD pre-processing has a serial nature and can not be vectorized, the computational consumptive operations \ref{the ordering} \ref{shat} can be implement by the CUDA Basic Linear Algebra Subprograms(cuBLAS), the matrix inverse(Gaussian Jordan Elimination) and cholesky factorization(Row Major Factorization) are also implemented by GPU, as shown in Table \ref{table 1}.
-\begin{table}[htb]
-\caption{Parallel Computation Operation of FCSD Pre-processing}
-\centering
-\begin{tabular}{|c|p{3cm}|p{3cm}|p{3cm}|p{3cm}|}
-\hline
-Operations & complex matrix-matrix multiplication & complex matrix-vector multiplication & matrix inverse & cholesky factorization \\
-\hline
-GPU subroutine & $\mathit{cublasCgemm}$  & $\mathit{cublasCgemv}$ & $\mathit{GJE}$ & $\mathit{chol}$\\
-\hline
-Formula   &  $\mathbf{H}^{H}\mathbf{H}$ & $(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y$ & $\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1} $ & $\mathbf{H}^{H}\mathbf{H}=\mathbf{R}^{H}\mathbf{R}$ 
-\\
-\hline
-  \label{table 1}
-\end{tabular}
-\end{table}
-
-Figure \ref{block diagram} shows the block diagram of the CUDA-FCSD implementation, as mention in section \ref{programming model}, our implementation is based on heterogeneous programming principle, the flow control and logical operations are reside at the host side, the compute intensive works is implemented at device side.
-\begin{figure}[htb]
-\centering
-\includegraphics[scale=0.8]{CUDA_FCSD_block_diagram.eps}
-\caption{Block Diagram of CUDA-FCSD Implementation}
-\label{block diagram}
-\end{figure}
-\subsection{Parallel Acceleration of Blocked-Paths Searching}
-  We consider $16\times 16$ MIMO system, the modulation scheme is $16$QAM, the path we need to search is $\mathbb{O}[M^{\rho}]=16^{3}=4096$, $\rho=\lceil \sqrt[2]{N_{t}}-1\rceil$, as mentioned in section \ref{programming model} the maximum number of threads that can be used in GPU is limited by the number of SM and maximum number of threads per SM, as to GeForce GTX 760.
-we have $12288$ threads totally.
-For each path, decision feedback path searching has a serial nature, therefore we match path to one thread, in order to have largest amount of threads that can be paralleled, we use one dimension blocks for widest expansion and blocked all the paths into several one dimension blocks, for largest SM occupation we define 4 blocks for path searching kernel and each block has 1024 threads.
-At each path, we perform the following data operation:\\
-1. \emph{Decision Feedback Equalization}\\
+The first and last conditions are contradictory thus $N_{1}>0\quad N_{2}>0$ does not exit.\\
+\textbf{2}. $N_{1}>0\quad N_{2}<0$\\
 \begin{eqnarray}
 \nonumber
-{s}_{i}^{k}\in \mathbb{O}^{\rho}      \quad if\quad i&=&N_{t},N_{t}-1,\dots N_{t}-\rho+1\quad FE\\
+N_{1}>0&\rightarrow & \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}-\frac{1}{2}(N_{r}-N_{t})-1>0\\
 \nonumber
-{s}_{i}^{k}=\hat{s}_{i}^{k}+\sum_{j=i+1}^{N_{t}}\frac{r_{ij}}{r_{ii}}(\hat{s_{j}^{k}}-s_{j}^{k})\quad if\quad i &=& N_{t}-\rho,N_{t}-\rho-1,\dots 2,1\quad SE\\  \label{path searching}
+&\rightarrow &x>N_{r}-N_{t}+1\\ \label{condition2}
 \end{eqnarray}
-$s_{j}^{k}$ denotes the $j$th symbol of the $k$th symbol vector candidate.\\
-2. \emph{Euclidean Metric Calculation}\\
+\begin{eqnarray}
+\nonumber
+N_{2}<0&\rightarrow & -\sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}-\frac{1}{2}(N_{r}-N_{t})-1<0\\
+\nonumber
+&\rightarrow &x>N_{r}-N_{t}+1\\ \label{condition3}
+\end{eqnarray}
+based on (\ref{condition2})(\ref{condition3}), when $x>N_{r}-N_{t}+1$, $N_{min}=\lceil N_{1}+1\rceil= \lceil \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}-\frac{1}{2}(N_{r}-N_{t})\rceil$, where $\lceil n\rceil$ denote the largest integer smaller than $n$.\\
+\textbf{3}. $N_{1}\leq 0\quad N_{2}\leq 0$\\
+\begin{eqnarray}
+\nonumber
+N_{1}\leq 0&\rightarrow & \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}\leq \frac{1}{2}(N_{r}-N_{t})+1\\
+\nonumber
+&\rightarrow &x\leq N_{r}-N_{t}+1\\ \label{condition4}
+\end{eqnarray}
+\begin{eqnarray}
+\nonumber
+N_{2}\leq 0&\rightarrow & \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}\geq \frac{1}{2}(N_{t}-N_{r})-1\\
+\nonumber
+&\rightarrow &x\geq N_{r}-N_{t}+1\\ \label{condition5}
+\end{eqnarray}
+Therefore based on (\ref{condition4})(\ref{condition5}), if and only if $N_{1}=N_{2}=0\quad x=N_{r}-N_{t}+1$, this condition holds, $N_{min}=1$.\\
+\textbf{Conclusion}\\
+\begin{displaymath}
+N_{min}=\left\{\begin{array}{ll}
+\lceil \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^2}-\frac{1}{2}(N_{r}-N_{t}) \rceil & x>N_{r}-N_{t}+1\\
+1 & x= N_{r}-N_{t}+1\\
+\end{array}\right.
+\end{displaymath}\\
+\section{Future Work}
+if the channel hardening phenomenon is applied directly to sel-MMSE and sel-MMSE-OSIC algorithm.
+The performance lost are extremely severe, Figure.\ref{figure1} presents the simulated BER performance of sel-MMSE and sel-MMSE-OSIC algorithms with channel hardening phenomenon directly applied, we consider uncoded system with 16QAM modulation, $N_{t}=N_{r}=40$, the transmitted bit sequence is randomly generated and  mutually independent, the elements of propagation matrix $H$ is i.i.d Circularly Symmetric Complex Gaussian(CSCG) random variable with zero means and unit variance, magnitude Rayleigh fading.
+the minimum diversity requirement $x$ is 8, for each SNR point there is a minimum $10^{5}$ symbols transmitted and $500$ symbol errors are collected.
+As Figure.\ref{figure1} shows, there is no diversity gain for sel-MMSE and sel-MMSE-OSIC algorithms with channel hardening phenomenon, however the performance tends to be better when the ratio $\frac{N_{r}}{N_{t}}$ is large that is several tens.\\
+\begin{figure}[hb]
+\centering
+\includegraphics[scale=0.8]{hardening.eps}
+\caption{BER performance of sel-MMSE and sel-MMSE-OSIC with channel hardening phenomenon}
+\label{figure1}
+\end{figure} \\
+Consider MMSE algorithm:
  \begin{equation}
-E_{u}^{k}=\sum_{i=1}^{i=N_{t}}\sum_{j=i}^{j=N_{t}}r_{ij}(\hat{s_{j}}-s_{j})\label{Eu metric}
+ \hat{s}=\mathbf{G}y=\mathbf{G}\mathbf{H}s+\mathbf{G}n    \label{future1}
  \end{equation}
-$E_{u}^{k}$ denotes the $k$th Euclidean metric of the corresponding symbol vector candidate $\widetilde{s}^{k}$. Then we take the symbol vector $s^{\theta}$ as the solution, where 
+the definitions of $\mathbf{H}$ $y$ $s$ $n$ $\hat{s}$ are similar to the definitions in section \ref{system}.
+$G=(\mathbf{H}^{H}\mathbf{H}+SNR^{-1})^{-1}\mathbf{H}^{H}$ is the weight matrix, define $\mathbf{C}=(\mathbf{H}^{H}\mathbf{H}+SNR^{-1})^{-1}$.
+From (\ref{future1}) we have:
  \begin{equation}
-\theta=arg\min_{m}(E_{u}^{m})\quad m=1,2\dots M^{\rho} \label{Eu candidate}
+\hat{s}_{k}=c_{kk}\mathbf{H}^{H}\mathbf{H}s+c_{kk}\mathbf{H}^{H}n+\sum_{j\neq k}c_{kj}\mathbf{H}^{H}\mathbf{H}s+\sum_{j\neq k}c_{kj}\mathbf{H}^{H}n \label{future2}
 \end{equation}
-
-\subsubsection{Data Preparation}
-There are three major factors that will influence the configuration of the data set configuration in memory space.\\
-1. Amount of Reading$\&$Writing operation per thread.\\
-2. Program scope of the data.\\
-3. Storage Requirement of data.\\
-The memory reading$\&$writing (R/W) strategy of GPU is the crutial factor that influence the application performance because the GPU is data processing intensive and only has small cache for special memory space(constant, texture), another consideration is the validation life circle of data, local memory which is invoked in kernel function is valid in one thread, share memory is valid in one block, constant, texture and global memory are valid both at host side and device side.
-On the other hand different from global memory (2047 MBytes in GeForce GTX 760), the constant and share memory are all capacity limited (only $65536$ bytes totally and $49152$ bytes per block in GeForce GTX 760), so that for our application the configuration of memory is determined by the capacity requirement of the data.
-Here in table \ref{amount of R/W operation} we present the amount of R/W operations and the storage that needed for critical data variables in FCSD path searching.
-The amount of the R/W operation is calculated based on the (\ref{path searching}) and ((ref{Eu metric}), for complex value ($\mathbf{R}$,$\hat{s}$, $\mathit{s_{pontential matrix}}$,$\mathit{s_{kernel}}$ ) is stored use $\mathit{float2}$ which counts 8 bytes, floating point data set $E_{u}$ is stored in $\mathit{float}$, which counts for 4 bytes, $\mathit{s_{index}}$ is the integer list which is stored use $\mathit{int}$, which counts 1 byte.
-\\
- At host side we set 4 vector data set that are stored linearly in global memory which has program scope for both host side and device side, $\mathit{s_{potential matrix}}$ is used to store the $M^{\rho}\times N_{t}$ complex matrix that each row stores one symbol vector candidate and whose valid scope is through the whole kernel function.
-$\mathit{s_{index}}$, which is used to store the index of all the possible sub symbol vectors for  FE stage using full factorial method, requires a $\rho\times M^{\rho}$  integer matrix space.
-$\mathit{E_{u}}$ is a $M^{\rho}$ floating point vector that is used to store the Euclidean metric of all the symbol vector candidates, obviously the valid scope of it is for the whole kernel function.
-$\mathit{s_{kernel}}$ is a complex vector used to store the FCSD solution which length is $N_{t}$ and has to be transferred to host side, thus it is also needed to be stored in global memory.
-\\
-  On the other hand,   upper triangular matrix $\mathbf{R}$ in (\ref{formula 4})  and unconstrained estimation $\hat{s}$ in (\ref{unconstrained estimation})  requires a large amount of R operations and are read only.
-(for the $16\times 16$ $16QAM$ MIMO system the R/W of $\mathbf{R}$  and $\hat{s}$ are about  $370$ and $266$ per thread), these two data set need small size of storage(for the $16\times 16$ $16QAM$ MIMO system $1088$ bytes for $\mathbf{R}$ and $128$ bytes for $\hat{s}$  ) we make use of the read only constant memory to store the data which are capacity limited and do not need write operation in path searching , as we mentioned in section (\ref{programming model}), the constant memory is cached so that it is much faster than global memory.
- \begin{table}[htb]  
- \caption{Amount of R/W Operations and Storage Requirement of Different Data Set}
- \centering
-\begin{tabular}{|p{3cm}|p{3cm}|l|p{3cm}|l|l|l|}
-\hline
-data & $\mathbf{R}$ & $\hat{s}$ & $\mathit{s_{pontential matrix}}$ & $\mathit{s_{index}}$ & $\mathit{E_{u}}$ & $\mathit{s_{kernel}}$ \\
-\hline
-R/W operations/thread & $(\frac{3}{2}(N_{t})^{2}-\frac{N_{t}}{2}+\rho-\rho^{2})$ & $(\frac{2(N_{t})^{2}+2N_{t}-\rho^{2}-\rho}{2})$ & $\rho$ & $N_{t}$ &$N_{t} $ & $N_{t}$ \\
-\hline
-Storage/bytes  & $4(N_{t}+1)N_{t}$ & $8N_{t}$ & $8M^{\rho}N_{t}$ & $N_{t}M^{\rho}$ & $4N_{t}M^{\rho}$ & $8N_{t}$\\
-\hline  \label{amount of R/W operation} 
-\end{tabular} 
-\end{table} 
-\subsubsection{Memory Accesss Pattern}
-  When considering large MIMO array, the large amount of R/W operations determine that the memory bandwidth is the major bottleneck of the performance,  although the theoretical bandwidth of off-chip memory is extremely high (in GeForce GTX 760 the bandwidth of off-chip memory is around $192 GB/s$), however the effect memory bandwidth can only be achieved by proper R/W strategy.\\
-  Global memory is implemented by dynamic random access memory (DRAM) whose R/W is extremely slow process, modern DRAM R/W data by access a pitch of consecutive memory location, as mentioned in section (\ref{programming model}), the warp is the basic schedule unit of device, with one instruction recall one warp of threads that execute at the same time, the most favorable global memory access pattern is to keep one warp of threads that access consecutive memory as much as possible, for GeForce GTX 760, the DRAM will access a consecutive memory address that has 128 bytes length, In Figure \ref{coalesce global memory} we take the global access pattern of the $\mathit{s_{potential matrix}}$ as an example to illustrate how we coalesce the the global memory,
-we store $\mathit{s_{potential matrix}}$ in one pitch of linear global memory, with each row store one $N_{t}=16$ complex symbol vector solution candidate of $\hat{s}_{FCSD}$ in (\ref{formula 5}), totally there are $M^{\rho}=4096$ rows, this matrix is stored in column major.
-As mentioned before we operate one path in one thread, thus the address two consecutive symbol operated in one thread is $4096$, however for consecutive threads the address they reach is continues as shown in Figure \ref{coalesce global memory}, each 32 threads in one warp can make R/W operation to a pitch of continues memory, which is $32\times 8=256 bytes$, counts for two times of DRAM access.
-\begin{figure}[htb]
-\centering
-\includegraphics[scale=0.63]{coalescing_global_memory.eps}
-\caption{Global Memory Access Pattern of $\mathit{s_{potential matrix}}$}
-\label{coalesce global memory}
-\end{figure}
- Another available resource for memory bandwidth increase is to make use of share memory, for all the transient variables that used for accumulator in (\ref{path searching}) and (\ref{Eu metric}), because of the small capacity consumption and large amount of R/W operations.
-\subsubsection{Data Transfer Minimization}   
-The data transfer between the host side and the device side is much more slower than the inner device data transferring, therefore, in our application we minimize the data transferring times, we make data transfer only once for propagation channel matrix $\mathbf{H}$, received symbol vector $y$ in (\ref{formula 1}) as well as the index list $\mathit{s_{index}}$ at FE stage, we integrate the post processing (\ref{Eu metric}) into path searching kernel function to avoid the transferring of $E_{u}$ in (\ref{Eu metric}).
-\subsection{Going to Larger MIMO System}
-  Consider the uplink $32\times 32$ MIMO system with $16$QAM modulation scheme, from \ref{path number}, the path number that need to be searched is $16^{5}=1048576$, as mentioned in section (\ref{programming model}), the maximum number of threads that can be execute in kernel function of GeForce GTX 760 is 12288, therefore we need to consider serial the one kernel into a certain times of loop, in order to avoid device synchronization latency, we synchronize and return the control to host side in order to reduce the synchronization expense.
-Under this condition we use 12 linear blocks and each block has 1024 threads, we execute the kernel function for 86 times and get the final solution.
-\section{Simulation Results}
-\subsection{Environment}
-\subsubsection{Device}
-\emph{Graphic Processing Units}: GeForce GTX 760, GPU clock rate: 1.08 GHz , memory clock rate: 3 GHz , number of SM: 6, maximum number of threads per stream multiprocessor: 2048, total amount of global memory: 2 GB, total amount of share memory per block: 49 KB, total amount of constant memory: 66 KB.
-\\
-\emph{Central Processing Units-Modigliani}: Intel Core i5-4th generation, 4 cores 3.20 GHz CPU clock rate, 8 GB RAM\\
-\emph{Central Processing Units-Monet} : Intel Core i7-3rd generation, 12 cores 3.20 GHz CPU clock rate, 32 GB RAM\\
-\subsection{Software}
-CUDA Driver Version / Runtime Version      6.5 / 6.0\\
-Nsight Eclipse Version 6.5
-\subsection{Performance and Evaluation}
-\begin{table}[htb]
-\caption{Speedup Performance of different MIMO Array size}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{ Array size} & \multicolumn{3}{|c|}{Time/s} & \multicolumn{2}{|c|}{Speedup}\\
-\cline{2-6}
-&GTX 760 & modigliani & monet & GTX/modigliani  & GTX/monet \\
-\hline
-$8\time 8$& 0.46& 0.09&0.08 & 0.20& 0.17\\
-\hline
-$16\time 16$&1.56 &3.2&3.57& 2.05& 2.29\\
-\hline
-$20\time 20$&31 & 74& 81& 2.39& 2.61\\
-\hline
-$25\time 25$& 38& 112& 122& 2.94& 3.21\\
-\hline
-$32\time 32$& 611&2836&3033&4.64& 4.96 \\
-\hline
-\label{speedup}
-\end{tabular}
-\end{table}
-  \quad We test 5 array sizes and make comparison between GTX 760 and two kinds of CPU, all the operation times we test is based on 100 channel realizations, the transmitted data is generated randomly and modulated by $16$ QAM modulation scheme,  as we can see in \ref{speedup}, for small size array, like $8\times 8$, GPU has no advantage over CPU, for small array size, the number of path that need to be searched is relatively small, the CPU has already had a good performance, there is a short time for GPU to "warm up", for data transferring, launch kernel function and host device synchronization, further more, for small number of threads, the memory R/W latency is not well hided.
-When the array size grows large, a large parallelism is achieved so that the GPU begin to display its data processing power, and with the array size increasing, this speedup tends to be much more considerable.
-\section{Conclusion}
-In this paper, we present the GPU implementation of fixed complexity sphere decoder for a large MIMO system, which is a time consuming task for traditional platform, we have reached up to nearly 5 times acceleration of FCSD and this speedup grows higher with the increasing array size.
-In addition, the GPU and CPU can work independently, the data processing power of GPU computing is an extra bonus of the traditional simulation platform.
-This shows the potential of GPU computing for the simulation and consumptive computational work of large MIMO area.
+$k\in [1,N_{t}]$, $\hat{s}_{k}$ is the $k$th element of $\hat{s}$, $c_{kj}$ is the element of $\mathbf{C}$ at $k$th row and $j$th column.
+with channel hardening phenomenon (\ref{future2}) is changed to:
+\begin{equation}
+\hat{s}_{k}^{hardening}=\frac{1}{N_{r}+SNR^{-1}}\mathbf{H}^{H}\mathbf{H}s+\frac{1}{N_{r}+SNR^{-1}}\mathbf{H}^{H}n\label{future3}
+\end{equation}
+$\hat{s}_{k}^{hardening}$ is the MMSE estimation with channel hardening phenomenon applied.
+comparing (\ref{future2}) and (\ref{future3}), the off diagonal elements of $\mathbf{C}$ is ignored in (\ref{future3}), with the fixed $N_{r}$ if $N_{t}$ increases, the number of off diagonal elements of $\mathbf{C}$ increases and performance get worse, so it is not reasonable to ignore them.
+This explain the result in Figure.\ref{figure1}, this kind of inter user interference(IUI) causes performance lost.
+Therefore, the next step is to find a strategy to eliminate this IUI without increasing too much complexity.
 % conference papers do not normally have an appendix

### 2015-08-06 Report April 2014/draft_tradeoff_original.tex
Reorganized Report Record

--- 2015-08-06 Report April 2014/draft.tex
@@
 \usepackage{setspace}
-\usepackage{diagbox}
 
@@
 % Do not put math or special symbols in the title.
-\title{Report}
+\title{Parallel Acceleration of Fixed Complexity Sphere Decoder for Large MIMO Uplink System Based on CUDA}
 
@@
 
+\section{Introduction}
+
 \section{System Model}\label{system}
@@
 \end{equation}
-$s\in \mathbb{C}^{N_{t}\times 1}$ is the transmit symbol vector, $y\in \mathbb{C}^{N_{r}\times 1}$ is the receive symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ is the channel propagation matrix with independent identity distributed(i.i.d) Circularly Symmetric Complex Gaussian(CSCG) zero mean elements of unit variance (Rayleigh fading), $n\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) with zero mean elements of variance $\sigma^{2}$, $\varepsilon(ss^{H})=E_{s}\mathbf{I}_{Nt}$, $E_s$ denotes the average symbol energy, $\varepsilon$ denotes the expectation operation and $M$ denotes the constellation size.
+$s\in \mathbb{C}^{N_{t}\times 1}$ is the transmit symbol vector, $y\in \mathbb{C}^{N_{r}\times 1}$ is the receive symbol vector, $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ is the channel propagation matrix with independent identity distributed(i.i.d) circularly symmetric complex Gaussian zero mean elements of unit variance (Rayleigh fading), $n\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) with zero mean elements of variance $\sigma^{2}$, $E(ss^{H})=E_{s}\mathbf{I}_{Nt}$, $E_s$ denotes the average symbol energy, $E$ denotes the expectation operation and $M$ denotes the constellation size.
 
@@
 \begin{equation}
-y_{d}=\mathbf{H}_{j}s_{d}+n
+y_{d}=\mathbf{H_{j}}s_{d}+n
 \end{equation}
@@
 \begin{equation}
-\hat{s_{d}}=\mathbf{G}_{j}y_{d}=\mathbf{G}_{j}\mathbf{H}_{j}s_{d}+\mathbf{G}_{j}n\label{equation0}
+\hat{s_{d}}=\mathbf{G}_{j}y_{d}=\mathbf{G_{j}H_{j}}s_{d}+\mathbf{G}_{j}n\label{equation0}
 \end{equation}
@@
 \begin{equation}
-[\hat{s_{d}}]_{m}=(gh)_{m}s_{d}+g_{m}n=g_{m}h_{m}[s_{d}]_{m}+\sum_{f\neq m}g_{m}h_{f}[s_{d}]_{f}+g_{m}n\label{equation01}
+[\hat{s_{d}}]_{m}=(\mathbf{G}_{j}\mathbf{H_{j}})_{m}s_{d}+g_{m}n\label{equation01}
 \end{equation}
-where $[\hat{s_{d}}]_{m}$ denotes the $m$th element of $\hat{s_{d}}$, $(gh)_{m}$ denotes the $m$th row of $\mathbf{G}\mathbf{H}_{j}$, $g_{m}$ denotes the $m$th row of $\mathbf{G}_{j}$ and $h_{m}$ denotes the $m$th column of $\mathbf{H}_{j}$, The post processing SINR of $m$th sub datastream and $j$th selected antenna subset is defined as\cite{3}:
+where $[\hat{s_{d}}]_{m}$ denotes the $m$th element of $\hat{s_{d}}$, $(\mathbf{G}_{j}\mathbf{H_{j}})_{m}$ denotes the $m$th row of $\mathbf{GH_{j}}$, $g_{m}$ denotes the $m$th row of $\mathbf{G}_{j}$ and $h_{m}$ denotes the $m$th column of $\mathbf{H_{j}}$, The post processing SNR of $m$th sub datastream and $j$th selected antenna subset is defined as\cite{3}:
 \begin{equation}
@@
 \begin{equation}
-\varepsilon[|g_{m}n|^{2}]= \varepsilon[(g_{m}n)(g_{m}n)^{H}]=\varepsilon[g_{m}nn^{H}g_{m}^{H}]=g_{m}\varepsilon[nn^{H}]g_{m}^{H}=g_{m}\sigma^{2}Ig_{m}^{H}
+E[|g_{m}n|^{2}]= E[(g_{m}n)(g_{m}n)^{H}]=E[g_{m}nn^{H}g_{m}^{H}]=g_{m}E[nn^{H}]g_{m}^{H}=g_{m}\sigma^{2}Ig_{m}^{H}
 =\sigma^{2}\parallel g_{m} \parallel^{2}
 \end{equation}
-as to $(gh)_{m}$, we have:
+as to $(\mathbf{G}_{j}\mathbf{H_{j}})_{m}$, we have:
 \begin{equation}
-\varepsilon[(gh)_{m}s_{d}s_{d}^{H}(gh)_{m}^{H}]=(gh)_{m}\varepsilon[s_{d}s_{d}^{H}](gh)_{m}^{H}=(gh)_{m}E_{s}I(gh)_{m}^{H} =E_{s}||(gh)_{m}||^{2}\label{equation03}
+E((\mathbf{G}_{j}\mathbf{H_{j}})_{m}s_{d}s_{d}^{H}(\mathbf{G}_{j}\mathbf{H}_{j})_{m}^{H})=(\mathbf{G}_{j}\mathbf{H}_{j})_{m}E[s_{d}s_{d}^{H}](\mathbf{G}_{j}\mathbf{H}_{j})_{m}^{H}=(\mathbf{G}_{j}\mathbf{H}_{j})_{m}E_{s}I(\mathbf{G}_{j}\mathbf{H}_{j})_{m}^{H} =E_{s}||(\mathbf{G}_{j}\mathbf{H}_{j})_{m}||^{2}\label{equation03}
 \end{equation}
-In (\ref{equation03}), $E_{s}||(gh)_{m}||^{2}=E_{s}|g_{m}h_{m}|^{2}+E_{s}\sum_{j\neq m}|g_{m}h_{j}|^{2}$, $E_{s}|g_{m}h_{m}|^{2}$ is the post processing energy of detected symbol, $E_{s}\sum_{j\neq m}|g_{m}h_{j}|^{2}$ is the energy of spatial inter symbol interference.
+In (\ref{equation03}),$E_{s}||(\mathbf{G}_{j}\mathbf{H}_{j})_{m}||^{2}=E_{s}|g_{m}h_{m}|^{2}+E_{s}\sum_{j\neq m}|g_{m}h_{j}|^{2}$, $E_{s}|g_{m}h_{m}|^{2}$ is the post processing energy of detected symbol, $E_{s}\sum_{j\neq m}|g_{m}h_{j}|^{2}$ is the energy of spatial inter symbol interference.
 \\
-Considering zero forcing algorithm first, the spatial equalizer $(\mathbf{G}_{j})_{ZF}=(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}\mathbf{H}_{j}^{H}$, therefore from (\ref{equation0}), $\mathbf{G}_{j}\mathbf{H}_{j}=\mathbf{I}_{N_t-N}$ and
+Considering zero forcing algorithm first, the spatial equalizer $\mathbf{G_{j}}_{ZF}=(\mathbf{H_{j}}^{H}\mathbf{H_{j}})^{-1}\mathbf{H_{j}}^{H}$, therefore from (\ref{equation0}) $\mathbf{G}_{j}\mathbf{H}_{j}=\mathbf{I}_{N_t-N}$ and
 \begin{equation}
@@
 \end{equation}
-Let $\omega_{m}$ denote the $m$th row of $(\mathbf{H_{j}^{H}H_{j}})^{-1}$, we have
+Let $(\mathbf{H_{j}^{H}H_{j}})^{-1}_{m}$ denote the $m$th row of $(\mathbf{H_{j}^{H}H_{j}})^{-1}$, we have
 \begin{equation}
-\parallel g_{m} \parallel^{2}=g_{m}g_{m}^{H}=\omega_{m}\mathbf{H}_{j}^{H}\mathbf{H}_{j}\omega_{m}^{H}\label{equation04}
+\parallel g_{m} \parallel^{2}=g_{m}g_{m}^{H}=(\mathbf{H_{j}^{H}H_{j}})^{-1}_{m}\mathbf{H_{j}}^{H}\mathbf{H_{j}}((\mathbf{H_{j}^{H}H_{j}})^{-1}
+_{m})^{H}\label{equation04}
 \end{equation}
-In (\ref{equation04}) we have $(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}\mathbf{H}_{j}^{H}\mathbf{H}_{j}=\mathbf{I}_{N_t-N}$, hence $\omega_{m}\mathbf{H_{j}}^{H}\mathbf{H_{j}}=e_{m}$, where $e_{m}$ deontes the row vector with $m$th element equals to 1, the others are all 0.
+In (\ref{equation04}) we use $(\mathbf{H_{j}^{H}H_{j}})^{-1}\mathbf{H_{j}}^{H}\mathbf{H_{j}}=\mathbf{I}_{N_t-N}$ hence $(\mathbf{H_{j}^{H}H_{j}})^{-1}_{m}\mathbf{H_{j}}^{H}\mathbf{H_{j}}=e_{m}$, where $e_{m}$ deontes the row vector with $m$th element equals to 1, the others are all 0.
 Therefore (\ref{equation04}) can be written as:
 \begin{equation}
-\parallel g_{m} \parallel^{2}=((\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}_{mm})^{H}
+\parallel g_{m} \parallel^{2}=((\mathbf{H_{j}}^{H}\mathbf{H_{j}})^{-1}_{mm})^{H}
 \end{equation}
-$((\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}_{mm})^{H}$ denotes the $m$th diagonal element of $((\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1})^{H}$.
-Because $\mathbf{H}_{j}^{H}\mathbf{H}_{j}$ is a Hermitian matrix, thus $((\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1})^{H}=(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1}$\cite{7} and (\ref{equation05}) can be written as:
+$((\mathbf{H_{j}}^{H}\mathbf{H_{j}})^{-1}_{mm})^{H}$ denotes the $m$th diagonal element of $((\mathbf{H_{j}}^{H}\mathbf{H_{j}})^{-1})^{H}$.
+Because $\mathbf{H_{j}^{H}}\mathbf{H_{j}}$ is a Hermitian matrix, thus $((\mathbf{H_{j}}^{H}\mathbf{H_{j}})^{-1})^{H}=(\mathbf{H_{j}}^{H}\mathbf{H_{j}})^{-1}$\cite{7} and (\ref{equation05}) can be written as:
 \begin{equation}
-(\rho_{ZF}^{j})_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}_{j}^{H}\mathbf{H}_{j})_{mm}^{-1}}\label{equation02}
+(\rho_{ZF}^{j})_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H_{j}}^{H}\mathbf{H_{j}})_{mm}^{-1}}\label{equation02}
 \end{equation}\\
-Consider minimum mean square error (MMSE) detection, where $\mathbf{G}=\mathbf{G}_{MMSE}=(\mathbf{H}_{j}^{H}\mathbf{H}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}\mathbf{H}_{j}^{H}$, from \cite{5} \cite{6}, we have the expression of the post processing SINR of MMSE:
+Consider minimum mean square error (MMSE) detection, where $\mathbf{G}=\mathbf{G_{MMSE}}=(\mathbf{H_{j}}^{H}\mathbf{H_{j}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}\mathbf{H_{j}}^{H}$, from \cite{5} \cite{6}, we have the expression of the post processing SNR of MMSE:
 \begin{equation}
-(\rho_{MMSE}^{j})_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H}_{j}^{H}\mathbf{H}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}_{mm}}-1\label{equation3}
+(\rho_{MMSE}^{j})_{m}=\frac{E_{s}}{\sigma^{2}(\mathbf{H_{j}}^{H}\mathbf{H_{j}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}_{mm}}-1\label{equation3}
 \end{equation}
-where $(\mathbf{H}_{j}^{H}\mathbf{H}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}_{mm}$ denotes the $m$th diagonal element of $(\mathbf{H}_{j}^{H}\mathbf{H}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$.
-The criterion of the diversity maximization selection scheme is to choose the antenna subset which can maximize the worst post-processing SINR of the sub-datastream.
-The column elements of $\mathbf{H}_{j}$ are mutually independent Gaussian random variables, under favorable propagation condition, when $N_{r}\to \infty$ and the 2 norm of the column will become much larger than the inner product of two different columns.
-Hence, the columns of $\mathbf{H}_{j}$ become asymptotically orthogonal, a phenomenon that can be expressed as
+where $(\mathbf{H_{j}}^{H}\mathbf{H_{j}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}_{mm}$ denotes the $m$th diagonal element of $(\mathbf{H_{j}}^{H}\mathbf{H_{j}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$.
+The criterion of the diversity maximization selection scheme is to choose the antenna subset which can maximize the worst post-processing SNR of the sub-datastream.
+The column elements of $\mathbf{H_{j}}$ are mutually independent Gaussian random variables under favorable propagation condition.
+When $N_{r}\to \infty$ and the 2 norm of the column will become much larger than the inner product of two different columns, hence, the columns of $\mathbf{H_{j}}$ become asymptotically orthogonal, a phenomenon that can be expressed as
 \begin{equation}
-\lim_{N_{r}\to \infty}\frac{(\mathbf{H}_{j}^{H}\mathbf{H}_{j})}{N_{r}}=\mathbf{I}_{N_t-N}
+\lim_{N_{r}\to \infty}\frac{(\mathbf{H_{j}}^{H}\mathbf{H_{j})}}{N_{r}}=\mathbf{I}_{N_t-N}
 \end{equation}
  Where $\mathbf{I}_{N_t-N}$ denotes an $(N_{t}-N)\times (N_{t}-N)$ identity matrix.
-Based on this property, for any $m$, $(\rho_{MMSE}^{j})_{m}$ and $(\rho_{ZF}^{j})_{m}$ in (\ref{equation02})(\ref{equation3}) are all the same, meaning that we can select arbitrarily the $N_{t}-N$ antenna subset.
+Based on this property, for any $m$, $(\rho_{MMSE}^{j})_{m}$ and $(\rho_{ZF}^{j})_{m}$ in (\ref{equation02})(\ref{equation3}) are all the same, means that we can select arbitrarily the $N_{t}-N$ antenna subset.
 % Note that IEEE does not put floats in the very first column - or typically
@@
 \begin{equation}
-y=\mathbf{H}_{1}s_{1}+\mathbf{H}_{2}s_{2}+n\label{equation 4}
+y=\mathbf{H_{1}}s_{1}+\mathbf{H_{2}}s_{2}+n\label{equation 4}
 \end{equation}
-Hence there are $N_{u}=$ $N_{t}\choose N$ possible antenna subsets, $\mathbf{H}_{1}\in \mathbb{C}^{N_{r}\times N}$ and $\mathbf{H_{2}}\in C^{N_{r}\times (N_{t}-N)}$.\\
+Hence there are $N_{u}=$ $N_{t}\choose N$ possible antenna subsets,$\mathbf{H_{1}}\in \mathbb{C}^{N_{r}\times N}$ and $\mathbf{H_{2}}\in C^{N_{r}\times (N_{t}-N)}$,\\
 \textbf{2}. As to $s_{1}\in \mathbb{C}^{N\times 1}$, we choose every possible symbol vector $s_{1}$ in the lattice and calculate:
 \begin{equation}
-y^{k}=y-\mathbf{H}_{1}s_{1}^{k}   \label{equation41}
+y^{k}=y-\mathbf{H_{1}}s_{1}^{k}   \label{equation41}
 \end{equation}
-$s_{1}^{k}$ denotes the $k$th possible $N\times 1$ symbol vector that is chosen in channel partition stage.
-For ML detection:
+$s_{1}^{k}$ denotes the $k$th possible $N\times 1$ symbol vector that chosen in channel partition stage.
+for ML detection:
 \begin{equation}
@@
 \begin{equation}
-arg\min_{s_{1},s_{2}}\parallel y-\mathbf{H}_{1}s_{1}-\mathbf{H}_{2}s_{2} \parallel
+arg\min_{s}\parallel y-\mathbf{H_{1}}s_{1}-\mathbf{H_{2}}s_{2} \parallel
 \end{equation} 
@@
 \textbf{3}.
-For every $s_{1}^{k}$ calculate $y_{k}=y-\mathbf{H}_{1}s_{1}^{k}$.
-There are $M^{N}$ possible $s_{1}^{k}$ as well as $y^{k}$.
-Using linear detection or OSIC to estimate $s_{2}^{k}$, the estimation is expressed as $\hat{s_{2}}^{k}$, then mapping $\hat{s_{2}}^{k}$ to the constellation to the nearest points, we use $s_{2}^{k}$ to represent it, every $s_{1}^{k}$ corresponds to one $s_{2}^{k}$, hence there are $M^{N}$ posssible $s_{2}^{k}$.\\
+For every $s_{1}^{k}$ calculate $y_{k}=y-\mathbf{H_{1}}s_{1}^{k}$, There are $M^{N}$ possible $s_{1}^{k}$ as well as $y_{k}$, Using linear detection or OSIC to estimate $s_{2}^{k}$, the estimation is expressed as $\hat{s_{2}}^{k}$, then mapping $\hat{s_{2}}^{k}$ to the constellation to the nearest points, we use $s_{2}^{k}$ to represent it, every $s_{1}^{k}$ corresponds to one $s_{2}^{k}$, hence there are $M^{N}$ posssible $s_{2}^{k}$.\\
 \textbf{4}. Find the solution $[s_{1}^{k},s_{2}^{k}]$ among $M^{N}$ candidates that has the minimum total Euclidean distance.\\
 \begin{equation}
-\hat{s}=arg\min_{k=1,2,\ldots,M^{N}}\parallel y^{k}-\mathbf{H}_{2}s_{2}^{k} \parallel^{2}\label{equation6}
+\hat{s}=arg\min_{k=1,2,\ldots,N_{u}}\parallel y_{k}-\mathbf{H_{2}}s_{2}^{k} \parallel^{2}\label{equation6}
 \end{equation}
-According to section \ref{channel partition}, based on diversity maximization antenna selection criterion and channel hardening phenomenon we can choose an arbitrary antenna subset, and hence the cost of antenna selection is zero.
-The second step calculating $y^{k}=y-\mathbf{H}_{1}s_{1}^{k}$, including an matrix multiplication and vector substruction,
+According to section \ref{channel partition}, based on diversity maximization antenna selection criterion we can choose an arbitrary antenna subset, and hence the cost of antenna selection is zero. 
+The second step calculating $y_{k}=y-\mathbf{H_{1}}s_{1}^{k}$, including an matrix multiplication and vector substruction,
 \begin{equation}
@@
 \end{equation}
- complex substitution are required. Then calculate the MMSE estimation $\hat{s}_{2}^{k}$:
+ complex additions and substitution are required. Then calculate the MMSE estimation $\hat{s}_{2}^{k}$:
 \begin{equation}
-\hat{s}_{2}^{k}=[\mathbf{H}_{2}^{H}\mathbf{H}_{2}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H}_{2}^{H}y^{k}\label{equation7}
+\hat{s}_{2}^{k}=[\mathbf{H_{2}}^{H}\mathbf{H_{2}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H_{2}}^{H}y_{k}\label{equation7}
 \end{equation}
-$\mathbf{H}_{2}\in \mathbb{C}^{N_{r}\times (N_{t}-N)}$, the calculation of weight matrix $\mathbf{G}_{MMSE}=[\mathbf{H}_{2}^{H}\mathbf{H}_{2}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H}_{2}^{H}$, because of the channel hardening phenomenon mentioned in section \ref{channel partition}, $\mathbf{G}_{MMSE}=[\mathbf{H}_{2}^{H}\mathbf{H}_{2}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H}_{2}^{H}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}\mathbf{I}\mathbf{H}_{2}^{H}$, hence the calculation of $\mathbf{G}_{MMSE}$ is real-complex multiplication, which cost 2 flops, 1/3 of complex multiplication, hence get $\mathbf{G}_{MMSE}$ requires:
+$\mathbf{H_{2}}\in \mathbb{C}^{N_{r}\times (N_{t}-N)}$, the calculation of weight matrix $\mathbf{G_{MMSE}}=[\mathbf{H_{2}}^{H}\mathbf{H_{2}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H_{2}}^{H}$, because of the channel hardening phenomenon mentioned in section \ref{channel partition}, $\mathbf{G_{MMSE}}=[\mathbf{H_{2}}^{H}\mathbf{H_{2}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I}]^{-1}\mathbf{H_{2}}^{H}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}\mathbf{I}\mathbf{H_{2}}^{H}$, hence the calculation of $\mathbf{G_{MMSE}}$ is real-complex multiplication, which cost 2 flops, 1/3 of complex multiplication, hence get $\mathbf{G_{MMSE}}$ requires:
 \begin{equation}
 \frac{(N_{t}-N)N_{r}}{3}    \label{cost31}
-\end{equation}\\
-complex multiplication.\\
-In the whole process $\mathbf{G}_{MMSE}$ only need to be calculated one time. Calculation of $\hat{s}_{2}^{k}=\mathbf{G}_{MMSE}y_{k}$ is the complex matrix multiplication which requires:
+\end{equation}
+In the whole process (\ref{equation31}) only need to be calculated one time. Calculation of $\hat{s}_{2}^{k}=\mathbf{G_{MMSE}}y_{k}$ is the complex matrix multiplication which requires:
 \begin{equation}
@@
 \begin{equation}
-M^{N}(N_rN+(N_{t}-N)N_r+N_r(N_t-N)+\frac{N_r}{2})+\frac{(N_{t}-N)N_{r}}{3}=M^{N}(2N_{r}N_{t}-N_{r}N+\frac{N_r}{2})+\frac{(N_{t}-N)N_r}{3}\label{equation8}
+M^{N}(N_rN+(Nt_-N)N_r+N_r(N_t-N)+\frac{N_r}{2})+\frac{(N_{t}-N)N_{r}}{3}=M^{N}(2N_{r}N_{t}-N_{r}N+\frac{N_r}{2})+\frac{(N_{t}-N)N_r}{3}\label{equation8}
 \end{equation}
@@
 \nonumber
-f_{sel-MMSE}(N) &=& 6[M^{N}(2N_{r}N_{t}-N_{r}N+\frac{N_r}{2})+\frac{(N_{t}-N)N_r}{3}]\\  
+f_{sel-MMSE}(N) &=& 6(M^{N}(2N_{r}N_{t}-N_{r}N+\frac{N_r}{2})+\frac{(N_{t}-N)N_r}{3})\\  
 &+&2M^{N}(2N_{r}N_{t}-N_{r}N-N_{t}+N+\frac{N_{r}-1}{2})\\
@@
 \end{eqnarray}
-where $N_{u}={\displaystyle{N_{t}\choose N}}$.
-Table \ref{table_sel-MMSE} shows the complexity comparison between $f_{sel-MMSE}$and$f_{sel-MMSE_{O}}$, at channel partition stage they all use diversity maximization scheme in \cite{2} to determine $N$.
-\begin{table}[t]
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\diagbox{$M$}{$\frac{f_{sel-MMSE}}{f_{sel-MMSE_{O}}}$}{ $N_{r}\times N_{t}$}&$10\times 10$&$32\times 32$&$64\times 64$&$128\times 128$\\\hline
-
-BPSK&0.0249&1.3746e-05&2.3406e-09&1.5672e-14\\\hline
-
-QPSK&0.1683&4.3817e-04&5.9893e-07&3.2095e-11\\\hline
-
-16QAM&0.9282&0.3098&0.0378&1.3460e-04\\\hline
-
-64QAM&0.9988&0.9978&0.9996&0.9982\\
-\hline
-\end{tabular}
-\caption{complexity comparison between $f_{sel-MMSE}$ and $f_{sel-MMSE_{O}}$}
-\label{table_sel-MMSE}
-\end{table} 
-From table \ref{table_sel-MMSE} we can see, as the size of array increases, the complexity abbreviation gain increases, as the size of signal constellation increases, the complexity abbreviation gain decreases.
 \subsection{sel-MMSE-OSIC}
-First we use a general case to illustrate how MMSE-OSIC works. Consider a MIMO system as mentioned in section \ref{system}:
+First we use a general case to illustrate how MMSE-OSIC works, first consider a MIMO system as mentioned in section \ref{system}:
 \begin{equation}
@@
 \end{equation}
-With $\mathbf{G}_{MMSE}=(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}\mathbf{H}^{H}$, after equalization using $\mathbf{G}_{MMSE}$,  (\ref{equation07}) can be changed to 
+With $\mathbf{G}_{MMSE}=(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}\mathbf{H}^{H}$, after equalization using $\mathbf{G}_{MMSE}$ (\ref{equation07}) can be changed to 
 \begin{equation}
-\hat{s}=\mathbf{G}_{MMSE}y=\mathbf{G}_{MMSE}Hs+\mathbf{G}_{MMSE}n\label{equation08}
+\hat{s}=\mathbf{G_{MMSE}}y=\mathbf{G_{MMSE}H}s+\mathbf{G_{MMSE}}n\label{equation08}
 \end{equation}
-where $\hat{s}$ denote the unconstrained estimate of $s$. From (\ref{equation08}) we can express $m$th estimation of sub-datastream $\hat{s}_{m}$:
+where $\hat{s}$ denotes the unconstrained estimation of $s$. From (\ref{equation08}) we can express $m$th estimation of sub-datastream $\hat{s}_{m}$:
 \begin{equation}
-\hat{s}_{m}={g_{m}}y\label{equation09}
+\hat{s}_{m}={g^{T}_{m}}y\label{equation09}
 \end{equation}
-where $g_{m}$ denote the $m$th row of $\mathbf{G}_{MMSE}$, unlike MMSE, the MMSE-OSIC algorithm detects the $s_{m}$ symbol by symbol.
-The detection order at every iteration is based on the following principle: $\hat{s_{m}}$ is detected based on their post-processing SINR at each iteration, where $\hat{s}_{m}$ with the highest SNR will be detected.
-According to (\ref{equation3}), the post processing SINR is associated to the diagonal elements of $(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$.
-The smaller is the $m$th diagonal element of $(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$, the higher is the post-processing SINR of $\hat{s}_{m}$.
-Because there are $N_{t}$ symbols in vector $s$, hence MMSE-OSIC algorithm will detect $s_{m}$ for $N_{t}$ times, in the $i$th ($i\in [0,N_{t}-1]$) iteration, it majorly has 3 steps:\\
-\textbf{1}.Ordering the channel based on the principle mentioned above, choose the sub-datastream with highest SNR(smallest diagonal element of $((\mathbf{H}_{j}^{i})^{H}\mathbf{H}_{j}^{i}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$ to detect, $\mathbf{H}_{j}^{i}\in \mathbb{C}^{Nr\times (Nt-N-i)}$ denotes the $i$th step sub-matrix in MMSE-OSIC iteration from the $j$th propagation matrix after channel partition as mentioned in section \ref{channel partition}, $\mathbf{H}_{j}^{0}=\mathbf{H}_{j}$\\
-\textbf{2}.Find the unconstrained estimate
+where $g_{m}$ denotes the $m$th row of $\mathbf{G_{MMSE}}$, unlike MMSE, MMSE-OSIC algorithm detects the $s_{m}$ symbol by symbol.
+The detection order at every iteration is based on the following principle: $\hat{s_{m}}$ is detected based on their post-processing SNR at each iteration, $\hat{s}_{m}$ with the highest SNR will be detected , according to (\ref{equation3}), this element is associated to the diagonal elements of $(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$.
+The smaller is the $m$th diagonal element of $(\mathbf{H}^{H}\mathbf{H}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$, the higher is the post-processing SNR of $\hat{s}_{m}$.
+because there are $N_{t}$ symbols in vector $s_{m}$, hence MMSE-OSIC algorithm will detect $s_{m}$ for $N_{t}$ times, in the $i$th ($i\in [0,N_{t}-1]$) iteration, it majorly has 3 steps:\\
+\textbf{1}.Ordering the channel based on the principle mentioned above, choose the sub-datastream with highest SNR(smallest diagonal element of $(\mathbf{H_{j}^{i}}^{H}\mathbf{H_{j}^{i}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$ to detect, $H_{j}^{i}\in \mathbb{C}^{Nr\times Nt-N-i}$ denotes the $i$th step sub-matrix in MMSE-OSIC iteration from the $j$th propagation matrix after channel partition as mentioned in section \ref{channel partition}, $\mathbf{H_{j}^{0}}=\mathbf{H_{j}}$\\
+\textbf{2}.Find the unconstrained estimation
 \begin{equation}
-\hat{s}_{i+1}=g_{i+1}y_{i}\label{equation012}
+\hat{s}_{i+1}=g_{i+1}^{T}y_{i}\label{equation012}
 \end{equation}
-and slice $\widehat{s_{i+1}}$ to $\bar{s}_{i+1}$ corresponds to signal constellation.\\
-\textbf{3}.Cancel the information correlated to  $\bar{s_{i}}$ from received vector $y_{i}$, $h_{m}\quad m\in [1,N_{t}]$ denotes the $m$th column of $\mathbf{H}_{j}^{i}$, $s_{2m}$ denotes the $m$th symbol of $s_{2}$.
-We have
+and slice $\widehat{s_{i+1}}$ to $\bar{s}_{i+1}$ corresponding to symbol constellation.\\
+\textbf{3}.Cancel the information correlated to  $\bar{s_{i}}$ from received vector $y_{i}$, $h_{m} m\in [1,N_{t}-N]$ denotes the $m$th column of $\mathbf{H_{j}^{i}}$.
+Hence from (\ref{equation07}), we have
 \begin{equation}
-y_{k}=\sum_{m=1,2,\ldots Nt-N}h_{m}s_{2m}+n
+y_{k}=\sum_{m=1,2,\ldots Nt-N}h_{m}s_{2}^{m}+n
 \end{equation}
@@
 \end{equation} 
-Then update propagation matrix by removing the column $h_{i+1}$ from $\mathbf{H}_{j}^{i}$.\\
+Then update propagation matrix by removing the column $h_{i+1}$ from $\mathbf{H_{j}^{i}}$.\\
 Consider now the computational complexity of sel-MMSE-OSIC.
-The difference between sel-MMSE-OSIC and sel-MMSE is in the linear detection step to detect $s_{2}$ in $y=\mathbf{H}_{1}s_{1}+\mathbf{H}_{2}s_{2}+n$, so that their computation cost except this step are all the same.
+The difference between sel-MMSE-OSIC and sel-MMSE is in the linear detection step to detect $s_{2}$ in $y=\mathbf{H_{1}}s_{1}+\mathbf{H_{2}}s_{2}+n$, so that their computation cost except this step are all the same.
 Firstly finding $y^{k}$ in (\ref{equation41}) requires $N_{r}N$ complex multiplications and $N_{r}N$ complex additions.
-In MMSE-OSIC detection of $s_{2}^{k}$, when $N_{r}\to \infty$, because of channel hardening phenomenon, at $i$th iteration($i\in [0,\quad N_{t}-N-1]$) in step 1, the diagonal elements of $(\mathbf{H}^{i}_{j})^{H}\mathbf{H}^{i}_{j}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$ are all the same.
-Therefore the post-processing SINR of $\hat{s_{m}}$ are all the same, detection order can be arbitrary, the step 1 in MMSE-OSIC can be ignored.
-in the second step, based on (\ref{equation09}) and channel hardening phenomenon, $\mathbf{G}_{MMSE}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}(\mathbf{H}^{i}_{j})^{H}$, $\upsilon_{m}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}\theta_{m}^{H}$, where $\theta_{m}^{H}$ denotes the $m$th row of $(\mathbf{H}^{i}_{j})^{H}$, hence finding the the weight vector requires a real-complex vector multiplication, with cost of $\frac{N_{r}}{3}$ complex multiplications, totally $N_{t}-N$ weight vectors need to be calculated, therefore $(N_{t}-N)\frac{N_{r}}{3}$ complex multiplications are needed, furthermore based on (\ref{equation012}) getting the detection statistic $\hat{s}_{i}$ requires $N_{r}$ complex multiplications and $N_{r}-1$ complex additions, then the interference cancellation step in (\ref{equation091}) requires $N_{r}$ complex multiplications and $N_{r}$ complex additions.
+In MMSE-OSIC detection of $s_{2}^{k}$, when $N_{r}\to \infty$, because of channel hardening phenomenon, at $i$th iteration($i\in [0,\quad N_{t}-N-1]$) in step 1, the diagonal elements of $(\mathbf{H^{i}_{j}}^{H}\mathbf{H^{i}_{j}}+\frac{\sigma^{2}}{E_{s}}\mathbf{I})^{-1}$ are all the same.
+Therefore the post-processing SNR of $\hat{s_{k}}$ are all the same, detection order can be arbitrary, the step 1 in MMSE-OSIC can be ignored.
+in the second step, based on (\ref{equation09}) and channel hardening phenomenon, $G_{MMSE}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}\mathbf{H^{i}_{j}}^{H}$, $g_{m}=\frac{1}{N_{r}+\frac{\sigma^{2}}{E_{s}}}\mathbf{(H^{i}_{j})_{m}}^{H}$, where $\mathbf{(H^{i}_{j})_{m}}^{H}$ denotes the $m$th row of $\mathbf{H^{i}_{j}}^{H}$, hence finding the the weight vector requires a real-complex vector multiplication, with cost of $\frac{N_{r}}{3}$ complex multiplications, totally $N_{t}-N$ weight vectors need to be calculated, therefore $(N_{t}-N)\frac{N_{r}}{3}$ complex multiplications are needed, furthermore based on (\ref{equation012}) getting the detection statistic $\hat{s}_{i}$ requires $N_{r}$ complex multiplications and $N_{r}-1$ complex additions, then the interference cancellation step in (\ref{equation091}) requires $N_{r}$ complex multiplications and $N_{r}$ complex additions.
 Since the MMSE-OSIC algorithm performs $N_{t}-N$ iteration, the cost of getting $\hat{s}_{2}$ is:
@@
 \begin{equation}
-M^{N}(2N_{r}-1)(N_{t}-N)\label{cost24}
+M_{N}(2N_{r}-1)(N_{t}-N)\label{cost24}
 \end{equation}
 complex additions.\\
-Basing on (\ref{equation091}), after $N_{t}-N$ iterations $y^{k}-\mathbf{H}_{2}s_{2}^{k}$ has already been calculated, therefore finding MED in (\ref{equation6}) just requires additional 
+Finding MED in (\ref{equation6}) requires additional 
 \begin{equation}
@@
 \begin{eqnarray}
-f_{sel-MMSE-OSIC}(N) &=& 6[M^{N}(2N_{r}N_{t}-N_{r}N+\frac{N_r}{2})+\frac{(N_{t}-N)N_r}{3}]\\  
-&+&2M^{N}(2N_{r}N_{t}-N_{r}N-N_{t}+N+\frac{N_{r}-1}{2})\\
+f_{sel-MMSE-OSIC}(N) &=& 6M^{N}(N_{r}N+2N_{r}(N_{t}-N)+\frac{N_{r}}{2})+(N_{t}-N)\frac{N_{r}}{3}\\
 \nonumber
-&=&M^{N}(16N_{r}N_{t}-8N_{r}N+4N_{r}-2N_{t}+2N-1)+2(N_{t}-N)N_{r}\quad flops\label{flop2}
+&+&2M^{N}((N_{r}N+2N_{r}-1)(N_{t}-N)+\frac{N_{r}-1}{2})\\
+\nonumber
+&=&M^{N}(16N_{r}N_{t}-8N_{r}N-2N_{t}+2N+4N_{r}-1)+2N_{r}(N_{t}-N)\quad flops\label{flop2}
 \end{eqnarray}
-From (\ref{equation10})(\ref{flop2}), $f_{sel-MMSE-OSIC}(N)=f_{sel-MMSE}(N)$.\\
 According to \cite{2}, the complexity of sel-MMSE-OSIC algorithm without making use of channel hardening phenomenon is 
@@
 \end{eqnarray}
-Table \ref{table_sel-MMSE-OSIC} shows the complexity comparison between $f_{sel-MMSE}$and$f_{sel-MMSE_{O}}$, at channel partition stage they all use diversity maximization scheme in \cite{2} to determine $N$.
-\begin{table}[t]
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\diagbox{$M$}{$\frac{f_{sel-MMSE-OSIC}}{f_{sel-MMSE-OSIC_{O}}}$}{ $N_{r}\times N_{t}$}&$10\times 10$&$32\times 32$&$64\times 64$&$128\times 128$\\\hline
-
-BPSK&0.0250&1.3746e-05&2.3406e-09&1.5672e-14\\\hline
-
-QPSK&0.1687&4.3817e-04&5.9893e-07&3.2095e-11\\\hline
-
-16QAM&0.9284&0.3098&0.0378&1.3460e-04\\\hline
-
-64QAM&0.9988&0.9978&0.9996&0.9982\\
-\hline
-\end{tabular}
-\caption{complexity comparison between $f_{sel-MMSE-OSIC}$ and $f_{sel-MMSE-OSIC_{O}}$}
-\label{table_sel-MMSE-OSIC}
-\end{table} \\
-From table \ref{table_sel-MMSE-OSIC} we can see, as the size of array increases the complexity abbreviation gain increases, as the size of signal constellation increases, the complexity abbreviation gain decreases.
 \section{Minimization of the Complexity}\label{minimization}
@@
 \subsection{sel-MMSE}
-Proposition 1: $f_{sel-MMSE}(N)$ increases when $N$ increases, in $[1,N_{t}-1]$\\
+Proposition 1: $f_{sel-MMSE}(N)$ increases when $N$ increases, in $[1,Nt-1]$\\
 Proof: According to section(\ref{complexity}), the computational cost of sel-MMSE algorithm is:
@@
 \end{equation}
-according to (\ref{equation11}), obviously when $N\geq 0\quad$, $\frac{\partial f_{sel-MMSE}(N)}{\partial N}$ increases with $N$ increasing, consider $N=0$, we have:
+according to (\ref{equation11}), obviously when $N\geq 0\quad$  $\frac{\partial f_{sel-MMSE}(N)}{\partial N}$ increases with $N$ increasing, consider $N=0$, we have:
 \begin{eqnarray}
@@
 \nonumber
-&=&\ln{M}[4(N_{t}+1)N_{r}+2(N_{r}-1)N_{t}]+10N_{r}(N_{t}\ln{M}-1)+2-\ln{M}  \label{equation51}
+&=&\ln{M}[4(N_{t}-1)N_{r}+2(N_{r}-1)N_{t}]+10N_{r}(N_{t}\ln{M}-1)+2-\ln{M}  \label{equation51}
 \end{eqnarray}
-because $N_{r}\geq 2$ $N_{t}\geq 2$ $M\geq 2$, therefore $\ln{M}[4(N_{t}-1)N_{r}+2(N_{r}-1)N_{t}]>0$, $\ln{M}\geq 0.6931$, $N_{t}\ln{M}\geq 1.3863$, hence $10N_{r}(N_{t}\ln{M}-1)+2>9.7259\quad$, if $M<1.6746\times 10^{4}$, $10N_{r}(N_{t}\ln{M}-1)+2-\ln{M}>0$, for the signal constellation size we consider, we can conclude that $10N_{r}(N_{t}\ln{M}-1)+2-\ln{M}>0$ holds, therefore $\frac{\partial f_{sel-MMSE}(0)}{\partial N}>0$.\\
-In conclusion when $N\geq 0$, $\frac{\partial f_{sel-MMSE}(N)}{\partial N}>0$, proposition 1 is proved.
+because $N_{r}\geq 2$ $N_{t}\geq 2$ $M\geq 2$, therefore $\ln{M}[4(N_{t}-1)N_{r}+2(N_{r}-1)N_{t}]>0$, $\ln{M}\geq 0.6931$, $N_{t}\ln{M}\geq 1.3863$, hence $10N_{r}(N_{t}\ln{M}-1)>0\quad$ $(2-\ln{M})>0$, therefore $\frac{\partial f_{sel-MMSE}(0)}{\partial N}>0$ In conclusion when $N\geq 0$, $\frac{\partial f_{sel-MMSE}(N)}{\partial N}>0$, proposition 1 is proved.
 \subsection{sel-MMSE-OSIC}
 Proposition 2: $f_{sel-MMSE-OSIC}(N)$ increases when $N$ increases, when $N\in [1, N_{t}-1]$\\
-Proof: From section (\ref{complexity}), the complexity expressions of sel-MMSE and sel-MMSE-OSIC are the same, therefore, proposition 2 holds.
+Proof: From section (\ref{complexity}), the complexity of sel-MMSE and sel-MMSE-OSIC is the same, therefore, proposition 2 holds.
 
@@
 \end{equation}
-let $(P_{e})_{2}^{LD}$ denote the average probability of detection error of $s_{2}^{k}$ using linear detection.
-If $d\geq N_{r}$, sel-MMSE can achieve optimal performance asymptotically $\lim_{SNR\rightarrow \infty}P_{e}=P_{e}^{ML}$.
+let $(P_{e})_{2}^{LD}$ denote the average probability of detection error of $s_{2}^{k}$ using linear detection method.
+if $d\geq N_{r}$, sel-MMSE can achieve optimal performance asymptotically $\lim_{SNR\rightarrow \infty}P_{e}=P_{e}^{ML}$.
 If $d<N_{r}$, $\lim_{SNR\rightarrow \infty}\frac{\log{P_{e}}}{\log{SNR}}=d$\cite{2}.
- $0\leq x\leq N_{r}$ denote the minimum required diversity.\\
+ $0\leq x\leq N_{r}$ denote the minimum required diversity.
  Define
@@
 \end{equation}
-Based on the results in section \ref{minimization}, we seek minimum $N$ ($N_{min}$) satisfying $g(N)\geq 0$. We see that $g(N)$ is a quadratic function of $N$ with the two zero points:
+Based on the results in section (\ref{minimization}), we seek minimum $N$ ($N_{min}$) satisfying $g(N)\geq 0$. We see that $g(N)$ is a quadratic function of $N$ with the two zero points:
 \begin{equation}
@@
 Consider the following conditions:\\
-\textbf{1}. $N_{1}>0\quad N_{2}>0$\\
-It is obvious that $N_{1}>N_{2}$, thus when $N_{2}>0$ this condition is satisfied.
-\begin{eqnarray}
-\nonumber
-N_{2}>0 &\rightarrow & -\sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}-\frac{1}{2}(N_{r}-N_{t})-1>0\\
-&\rightarrow & \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}<\frac{1}{2}(N_{t}-N_{r})-1 \label{condition1}
-\end{eqnarray}
-(\ref{condition1}) holds when the following 3 conditions are satisfied:
-\begin{displaymath}
-\left\{\begin{array}{ll}
-\frac{1}{2}(N_{t}-N_{r})-1>0&\rightarrow N_{t}>N_{r}+2\\
-0<x< N_{r}-N_{t}+1&\rightarrow N_{t}<N_{r}+1\\
-\end{array}\right.
-\end{displaymath}
-The first and last conditions are contradictory thus $N_{1}>0\quad N_{2}>0$ does not exit.\\
-\textbf{2}. $N_{1}>0\quad N_{2}<0$\\
-\begin{eqnarray}
-\nonumber
-N_{1}>0&\rightarrow & \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}-\frac{1}{2}(N_{r}-N_{t})-1>0\\
-\nonumber
-&\rightarrow &x>N_{r}-N_{t}+1\\ \label{condition2}
-\end{eqnarray}
-\begin{eqnarray}
-\nonumber
-N_{2}<0&\rightarrow & -\sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}-\frac{1}{2}(N_{r}-N_{t})-1<0\\
-\nonumber
-&\rightarrow &x>N_{r}-N_{t}+1\\ \label{condition3}
-\end{eqnarray}
-based on (\ref{condition2})(\ref{condition3}), when $x>N_{r}-N_{t}+1$, $N_{min}=\lceil N_{1}+1\rceil= \lceil \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}-\frac{1}{2}(N_{r}-N_{t})\rceil$, where $\lceil n\rceil$ denote the largest integer smaller than $n$.\\
-\textbf{3}. $N_{1}\leq 0\quad N_{2}\leq 0$\\
-\begin{eqnarray}
-\nonumber
-N_{1}\leq 0&\rightarrow & \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}\leq \frac{1}{2}(N_{r}-N_{t})+1\\
-\nonumber
-&\rightarrow &x\leq N_{r}-N_{t}+1\\ \label{condition4}
-\end{eqnarray}
-\begin{eqnarray}
-\nonumber
-N_{2}\leq 0&\rightarrow & \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^{2}}\geq \frac{1}{2}(N_{t}-N_{r})-1\\
-\nonumber
-&\rightarrow &x\geq N_{r}-N_{t}+1\\ \label{condition5}
-\end{eqnarray}
-Therefore based on (\ref{condition4})(\ref{condition5}), if and only if $N_{1}=N_{2}=0\quad x=N_{r}-N_{t}+1$, this condition holds, $N_{min}=1$.\\
+\textbf{1}. $N_{r}\geq 2N_{t}-3$, the asymptotically optimal performance and minimum complexity can be reached at the same time, $N_{min}=1\leftrightarrow d\geq N_{r}$\cite{2}\\
+\textbf{2}.
+$N_{t}\leq N_r\leq 2N_{t}-4$, because $N_{r}\geq N_{t}$, according to (\ref{equation18}) $N_{2}<0$, considering $N_{1}$, when $x$ is viewed as a variable of $N_{1}$, in (\ref{equation18}), when $1/2(N_{r}-N_{t})+1>0\Rightarrow N_{r}\geq N_{t}-2$, zero point $x$ of $N_{1}(x)$ exists, zero point is $x=N_{r}-N_{t}+1$, $N_{1}$ increases when $x$ increases, because $N_{r}\geq N_{t}$, it is obvious zero point exits\\
+if $x>N_{r}-N_{t}+1\rightarrow N_{1}>0$, therefore 
+\begin{equation}
+N_{min}=\lfloor N_{1}+1 \rfloor = \lfloor \sqrt{x+1/4(N_{r}-N_{t})^2}-1/2(N_{r}-N_{t}) \rfloor\label{equation013}
+\end{equation}
+$\lfloor m \rfloor$ denotes the largest integer smaller than $m$, $N_{min}\leq N_{t}-1$, based on (\ref{euqation013}) $x<N_{r}N_{t}$.\\
+if $x\leq N_{r}-N_{t}+1\rightarrow N_{1}\leq 0$, therefore $N_{min}=1$.\\
+\textbf{3}. $N_{r}<N_{t}$\\
+consider $x$ as an variable of $N_{2}(x)$, the zero point $x_{zero}=N_{r}-N_{t}+1$ exists when $-1/2(N_{r}-N_{t})-1>0\Rightarrow N_{r}\leq N_{t}-2$, $x$ and$N_{2}$ are negatively correlated.\\
+if $N_{r}\leq N_{t}-2$, then zero point of $N_{2}(x)$ exists, $N_{r}-N_{t}+1<0$, because $x>0$, therefore $x>N_{r}-N_{t}+1$,
+$N_{2}<0$, because $N_{r}\leq N_{t}-2 \Rightarrow 1/2(N_{r}-N_{t})+1<0$, based on (\ref{equation18}) $N_{1}=\sqrt{x+1/4(N_{r}-N_{t})^2}-(1/2(N_{r}-N_{t})+1)>0$, so $N_{min}=\lfloor N_{1}+1 \rfloor = \lfloor \sqrt{x+1/4(N_{r}-N_{t})^2}-1/2(N_{r}-N_{t}) \rfloor$, because $N_{min}\leq N_{t}-1$, according to (\ref{equation013}) $x<N_{r}N_{t}$.\\
+if $N_{r}=N_{t}-1$, $-1/2(N_{r}-N_{t})-1$ in (\ref{equation19}) equals to $-\frac{1}{2}$, thus $N_{2}<0$, $N_{r}\geq N_{t}-2$, thus zero point of $N_{1}(x)$ exists, $x>0=N_{r}-N_{t}+1$, based on above discussion $N_{1}>0$, $N_{min}=\lfloor N_{1}+1 \rfloor = \lfloor \sqrt{x+1/4(N_{r}-N_{t})^2}-1/2(N_{r}-N_{t}) \rfloor$.\\
 \textbf{Conclusion}\\
+1. $N_{r}\geq 2N_{t}-3$, $d_{total}=N_{r}$ $N_{min}=1$\\
+2. $N_{t}\leq N_r\leq 2N_{t}-4$, $d_{total}=x$
 \begin{displaymath}
 N_{min}=\left\{\begin{array}{ll}
-\lceil \sqrt{x+\frac{1}{4}(N_{r}-N_{t})^2}-\frac{1}{2}(N_{r}-N_{t}) \rceil & x>N_{r}-N_{t}+1\\
-1 & x= N_{r}-N_{t}+1\\
+\lfloor \sqrt{x+1/4(N_{r}-N_{t})^2}-1/2(N_{r}-N_{t}) \rfloor & x>N_{r}-N_{t}+1\\
+1 & x\leq N_{r}-N_{t}+1\\
 \end{array}\right.
 \end{displaymath}\\
-\section{Future Work}
-if the channel hardening phenomenon is applied directly to sel-MMSE and sel-MMSE-OSIC algorithm.
-The performance lost are extremely severe, Figure.\ref{figure1} presents the simulated BER performance of sel-MMSE and sel-MMSE-OSIC algorithms with channel hardening phenomenon directly applied, we consider uncoded system with 16QAM modulation, $N_{t}=N_{r}=40$, the transmitted bit sequence is randomly generated and  mutually independent, the elements of propagation matrix $H$ is i.i.d Circularly Symmetric Complex Gaussian(CSCG) random variable with zero means and unit variance, magnitude Rayleigh fading.
-the minimum diversity requirement $x$ is 8, for each SNR point there is a minimum $10^{5}$ symbols transmitted and $500$ symbol errors are collected.
-As Figure.\ref{figure1} shows, there is no diversity gain for sel-MMSE and sel-MMSE-OSIC algorithms with channel hardening phenomenon, however the performance tends to be better when the ratio $\frac{N_{r}}{N_{t}}$ is large that is several tens.\\
-\begin{figure}[hb]
-\centering
-\includegraphics[scale=0.8]{hardening.eps}
-\caption{BER performance of sel-MMSE and sel-MMSE-OSIC with channel hardening phenomenon}
-\label{figure1}
-\end{figure} \\
-Consider MMSE algorithm:
- \begin{equation}
- \hat{s}=\mathbf{G}y=\mathbf{G}\mathbf{H}s+\mathbf{G}n    \label{future1}
- \end{equation}
-the definitions of $\mathbf{H}$ $y$ $s$ $n$ $\hat{s}$ are similar to the definitions in section \ref{system}.
-$G=(\mathbf{H}^{H}\mathbf{H}+SNR^{-1})^{-1}\mathbf{H}^{H}$ is the weight matrix, define $\mathbf{C}=(\mathbf{H}^{H}\mathbf{H}+SNR^{-1})^{-1}$.
-From (\ref{future1}) we have:
- \begin{equation}
-\hat{s}_{k}=c_{kk}\mathbf{H}^{H}\mathbf{H}s+c_{kk}\mathbf{H}^{H}n+\sum_{j\neq k}c_{kj}\mathbf{H}^{H}\mathbf{H}s+\sum_{j\neq k}c_{kj}\mathbf{H}^{H}n \label{future2}
-\end{equation}
-$k\in [1,N_{t}]$, $\hat{s}_{k}$ is the $k$th element of $\hat{s}$, $c_{kj}$ is the element of $\mathbf{C}$ at $k$th row and $j$th column.
-with channel hardening phenomenon (\ref{future2}) is changed to:
-\begin{equation}
-\hat{s}_{k}^{hardening}=\frac{1}{N_{r}+SNR^{-1}}\mathbf{H}^{H}\mathbf{H}s+\frac{1}{N_{r}+SNR^{-1}}\mathbf{H}^{H}n\label{future3}
-\end{equation}
-$\hat{s}_{k}^{hardening}$ is the MMSE estimation with channel hardening phenomenon applied.
-comparing (\ref{future2}) and (\ref{future3}), the off diagonal elements of $\mathbf{C}$ is ignored in (\ref{future3}), with the fixed $N_{r}$ if $N_{t}$ increases, the number of off diagonal elements of $\mathbf{C}$ increases and performance get worse, so it is not reasonable to ignore them.
-This explain the result in Figure.\ref{figure1}, this kind of inter user interference(IUI) causes performance lost.
-Therefore, the next step is to find a strategy to eliminate this IUI without increasing too much complexity.
+3. $N_{r}\leq N_{t}$, $d_{total}=x$, $N_{min}=\lfloor \sqrt{x+1/4(N_{r}-N_{t})^2}-1/2(N_{r}-N_{t}) \rfloor$
+
 % conference papers do not normally have an appendix

### 2015-08-06 Report Aug 5 2015/Report_Aug_2015.tex
Reorganized Report Record

--- 2015-05-13 Lattice Reduction/Report April 2015/Report revised May 12 2015/Report_draft.tex
@@
 \end{equation}  
-\section{Logarithmic Expectation of Orthogonality Measurement}\label{log expectation of om}
+\section{Dual Channel Complex Kernel Support Vector Regression for Large MIMO system}\label{dual channel CSVR}
 
@@
 Consider $\mathbf{H}=[\mathbf{h}_{1}^{'},\mathbf{h}_{2}^{'},\cdots \mathbf{h}_{N_{r}}^{'}]^{'}$, where $\mathbf{h}_{i}$ denotes the $i$ th row of $\mathbf{H}$, because each component of $\mathbf{H}$ is mutually independent and subject to circularly symmetric complex Gaussian distribution, i.e.
-$h_{i}\sim \mathbb{C}N(\mathbf{0},\mathbf{I}_{N_{t}})$.
+$\mathbf{h}_{i}\sim \mathbb{C}N(\mathbf{0},\mathbf{I}_{N_{t}})$.
 Therefore, $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}\sim \mathbb{C}W(N_{r}, \mathbf{I}_{N_{t}})$, $\mathbb{C}W(n,\mathbf{\Sigma})$ denotes complex Wishart distribution with $n$ degrees of freedom and covariance matrix $\mathbf{\Sigma}$.
@@
 \end{equation}
-where $\tilde{\Gamma}_{m}(n)$ denotes the multivariate Gamma function. Proof: see Appendix A.
+where $\tilde{\Gamma}_{m}(n)$ denotes the multivariate Gamma function and $\psi(n)$ denotes Digamma function. Proof: see Appendix A.
 
@@
 \end{eqnarray}
-\section{Probability Density Function of Orthogonality Measurement}\label{pdf of om}
+\section{Work Set Selection}\label{WSS}
+\subsection{Single Direction Solver}
+\subsection{Double Direction Solver}
+\subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}
 Recall (\ref{formula9})
@@
 \begin{equation}
-f_{\phi_{om}}(x)=\frac{1}{x}\sum_{\mathbf{j}}(\prod_{i=1}^{N_{t}}c(k_{1}^{i}k,k_{2}^{i},j^{i}))f(\ln(x)|\mathbf{k_{1}}+\mathbf{j}), 
+f_{\phi_{om}}(x)=\frac{1}{x}\sum_{\mathbf{j}}(\prod_{i=1}^{N_{t}}c(k_{1}^{i}k,k_{2}^{i},j^{i}))f(-\ln(x)|\mathbf{k_{1}}+\mathbf{j}), 
 \label{formula23}
@@
 where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{N_{t}}}$, the range of $j^{i}\in [0, k_{2}^{i}-1]$, $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
-$f(\ln(x)|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})\ln(x))/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$.
+$f(-\ln(x)|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})\ln(x))/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$.
 $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1},\cdots k_{1}^{N_{t}-1}+j^{N_{t}-1},k_{1}^{N_{t}}+j^{N_{t}}]$.
@@
 
-\section{Computer Simulations}\label{computer simulation}
+\section{Initialization}\label{Initialization}
  Computer simulations are made for different sizes of V-BLAST MIMO systems, with $5\leq N_{r} \leq 100, 5 \leq N_{t} \leq N_{r}$, the empirical estimation of logarithmic expectation of $\phi_{om}$, $E[\ln(\phi_{om})]_{em}$, is calculated by taking average over $1e4$ channel realizations for each size of MIMO systems, as shown in Fig.\ref{figure1}, the Theoretical logarithmic expectation of $\phi_{om}$ $E[\ln(\phi_{om})]_{t}$ in (\ref{formula25}) is plotted in Fig.\ref{figure2}.
@@
 On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
+\section{Stopping Criteria}
+\section{Hyperparameter Setting}
+\section{Computer Simulations}
 

### 2015-08-06 Report Sept 2013/report.tex
Reorganized Report Record

%\documentclass[12pt,a4paper,final]{article}
\documentclass[conference]{IEEEtran}
\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{psfrag}
\usepackage{color}
\usepackage{epsfig}
%\usepackage{appendix}
\usepackage{caption}
\usepackage{cite}
\usepackage{ifpdf}
\usepackage[cmex10]{amsmath}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{stfloats}
\usepackage{url}
\usepackage{fixltx2e}
%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
%\usepackage[tight,footnotesize]{subfigure}
%\usepackage{eqparbox}
%\usepackage{mdwmath}
%\usepackage{mdwtab}

\title{Report for 2013 Fall}
\author{Tianpei Chen\\
\small Department of Electrical and Computer Engineering\\
\small McGill University\\
\small Montreal, Quebec}
%\author{\IEEEauthorblockN{Tianpei Chen}
%\IEEEauthorblockA{Department of Electrical and\\Computer Engineering\\
%McGill University\\
%Montreal, Quebec}}
\small \date{}

\begin{document}
\maketitle
\begin{abstract}
Multiple Input Multiple Output(MIMO) technology offers a cost effective opportunity to make high data rate wireless communication reality, is maturing and is being incorporated into emerging wireless broadband standards like IEEE 802.11n, long-term evolution (LTE)\cite{1}. Massive MIMO, which use several hundreds of antennas at the base station, will bring a lot of breakthrough in high data rate, link reliability, radiate energy efficiency etc\cite{7}. it has become a goldmine of research problems in recent 4 years, this report presents a overview of the conventional MIMO systems and Massive MIMO systems.\newline
\textbf{keywords: }\emph{conventional MIMO, Massive MIMO, data rate, link reliability, energy efficiency}\newpage
\end{abstract}
\section{Background}
The development of the wireless communication render the increasing demand for the quality of service(QoS), data rate and network capacity, On the other hand, the designer of the wireless systems are always facing the challenges like the complicated time-frequency varying environment, limited radio frequency spectrum resources, the demand for the transmission of the rich media content, Multiple-Input Multiple-Output(MIMO) systems have emerged as a most promising technology in these measures.\newline
The core idea of MIMO is to use multiple antennas both at the transmitting end and receiving end, the spatial domain sampled signal can be combined to provide parallel data pipes so that can improve array gain, diversity gain, spatial multiplexing gain, and interference reduction.\newline
MIMO technology has been implemented or considered in some applications, for example MIMO-OFDM has been incorporated in IEEE 802.11n standard for wireless local area networks(WLANs)\cite{2}. MIMO technology was also considered in the home audio/visual devices\cite{3}.\newline
\section{Introduction}
High data rate demands of wireless systems will continue to grow for the foreseeable future. Since current technologies are not capable of supporting these demands, new and more efficient antenna configurations need to be devised. One of the most viable solutions is the deployment of Large-scale multiple antenna (LSMA) wireless systems. LSMA wireless systems with hundreds of low-power antennas, that may be colocated at a base station (BS) site, spread out on the face of a building, or distributed geographically, provide a plethora of advantages over conventional multiple-input multiple-output (MIMO) and cooperative networks. In particular, these large-scale systems offer higher data rates, increased link reliability, and potential power savings, since the transmitted RF energy can be more sharply focused in space, while many random impairments (e.g., thermal noise and intercell interference) can be averaged out. We note that these gains can be achieved by coherent, but simple, processing
(e.g. linear reception techniques in an uplink scenario). LSMA also entails a revolution in hardware. Expensive ultra-linear forty-Watt amplifiers are replaced by many cheap low-power
devices whose combined action, only, has to meet stipulated tolerances. Likewise it is expected that lower resolution A/D and D/A converters can be used. Equally importantly, the
analysis of large-scale systems can be carried out using tools from random matrix theory, which has attracted considerable research interest. For all these reasons, the area of LSMA
systems has recently emerged at the forefront of wireless communication research.\newline
The rest part of the report will be organized as follows, Section 3 presents a brief overview of the advantages that conventional MIMO can provide and some basic detection technologies of conventional MIMO. Section 4 introduce the potentials and challenges of Massive MIMO, then comes a conclusion.
\section{Conventional MIMO}
\subsection{Array Gain and Diversity Gain}
Because of the multipath and path loss$\&$shadowing, which also been defined as small scale fading and large scale fading, the diversity techniques are employed to combat these effects, principle of this technology is to transmit the multiple versions of the same signal to receiver, because each version is affected by the independent fading, so the probability of all the versions are in a fade at the same time can be greatly reduced. In the other word, the diversity techniques help to improve the link reliability. Two criterions are defined to evaluate the effect of diversity techniques, the one is signal-noise ratio(SNR) and the other is error rate, the former is array gain and the latter is diversity gain.\newline   
The average receive SNR can be improved due to the coherent combination effect of the processing at the transmitter and the receiver, Transmit/receive array gain requires channel knowledge in the transmitter and receiver, respectively, and depends on the number of transmit and receive antennas. Channel knowledge in the receiver is typically available whereas channel state information in the transmitter is in general more difficult to maintain.\newline
the arriving signals are combined by the receiver to combat the fade effect, increasing the error rate slope as a function of SNR, it is possible to extract spatial diversity gain using appropriate transmit signal design, the corresponding techniques is called space-time coding\cite{4}.\newline
\subsection{Multiplexing Gain}
MIMO channels offer a linear $\min(n,m)$ increase in capacity for no additional power or bandwidth expenditure, $n$ and $m$ is the number of transmit antenna and receive antenna. This gain, referred to as spatial multiplexing gain, is
realized by transmitting independent data signals from the individual antennas. Under conducive channel conditions, such as rich scattering, the receiver can separate the different streams, yielding a linear increase in capacity.\newline
\subsection{Interference Reduction}
Cochannel interference arises due to frequency reuse in wireless channels. When multiple antennas are used, the differentiation between the spatial signatures of the desired
signal and cochannel signals can be exploited to reduce interference. Interference reduction requires knowledge of the desired signal's channel. Exact knowledge of the interferer's channel may not be necessary. Interference reduction(or avoidance) can also be implemented at the transmitter, where the goal is to minimize the interference energy sent toward the cochannel users while delivering the signal to the desired user. Interference reduction allows aggressive frequency reuse and thereby increases multicell capacity\cite{9}.
\subsection{Detection Technology For Conventional MIMO}
The detection of MIMO system is to restitute the transmitted symbol vector from the observed receiving symbol vector which is the linear superposition of the transmitted symbols, in fact is to find a least square solution of a linear equations system, the relation function between the transmitting and receiving signal symbols can be expressed as:
\begin{equation}
y=Gx+e\label{equation:1}
\end{equation}
G is the $m\times n$ propagation matrix, $e$ is the additive noise, we assume e subject to zero mean gaussian distribution, $x$ is the $n$ transmitting signal symbol vector and $y$ is the m receiving signal symbol vector, we want to get $x$ with known $G$ and $y$, in maximum likelihood(ML) method the problem can be expressed as:
\begin{equation}
\min_{s\in s^m}=\|y-Gx\|^2\label{equation:2}
\end{equation}
now the basic methods of detection include: Zero forcing(ZF), Zero forcing decision feedback(ZFDF), Sphere decoding(SD), Fixed complexity sphere decoding(FCSD), Semidefinite relaxation detector(SDR), Lattice reduction aided method and Soft decision\cite{10}\cite{5}.\newline
\section{Massive MIMO}
Massive MIMO (also known as ''Large-Scale Antenna System'', ''Very Large MIM'', ''Hyper MIM'', ''Full-Dimension MIM'' an''ARGO'')  we think of a system that use several hundreds of antennas at the base station serving several tens of terminals using the same time-frequency resources, it use a large excess of  service antennas and time division duplex operation(TDD) which are the clear break of Massive MIMO from the conventional MIMO systems, in addition, the Massive MIMO can reap all the advantages of the conventional MIMO system\cite{11}\cite{6}.
There are many opportunities that can be brought by Massive MIMO, improvement of data rate, quality of service, spectrum efficiency\cite{6}, radiate energy efficiency\cite{6}, increasing degree of freedom, the fault of individual antenna will not greatly influence the performance of the system, vanishes of thermal noise and small scale fading\cite{6} and easier strategy to acquire channel state information(CSI) based on channel reciprocity.\newline
The challenges also exist, brand new channel characterization for the Massive MIMO systems to reflect the behavior of the real world radio propagation, which is different from the conventional MIMO systems. mutual coupling(magnetic interaction) given  that the space of aperture is limited and special array structure[1], channel reciprocity will not be valid if the coherent time is very short, what is the best way to implement the reciprocity calibration, how to reduce the cost both in time-frequency resources and hardware. pilot contamination can not vanish as the number of the base station antenna become unlimited, because of beamforming. 
The detection of MIMO system is to restitute the transmitted symbols from the observed receiving symbols which is the linear superposition of the transmitted symbols, in fact is to find a least square solution of a linear equations system.
\subsection{Channel Model}
we assume that the receiver has the perfect knowledge of channel matrix, the mutual information of the simplest narrowband memoryless channel has the following mathematical description:
\begin{equation}
C=I(y;x)=log_2det(I_m +\frac{\rho}{n}GG^H ) \label{equation:3}
\end{equation}
$m$ is the number of the receiving antennas, $n$ is the number of the transmitting antennas,Im is the $m\times m$ identical matrix, the scalar p is a measure of the SNR of the link: it is proportional to the transmitted power divided by the noise-variance, $G$ is the $m\times n$ propagation matrix, the superscript $H$ denote the conjugate transpose, $y$ is the received signal symbol vector and x is the transmitted signal vector. The actual capacity of the
channel results if the inputs are optimized according to the water-filling principle. In the case that $GG^H$ equals a scaled identity matrix, C is in fact the capacity or achievable rate
the relation between y and x can be represent as:
\begin{equation}
y=\sqrt{\rho}Gx+e  \label{equation:4}
\end{equation}
$e$ is the additive receiver noise subject to i.i.d zero mean gausssian distribution, we normalized the total transmit power to unity:$E\{\Vert x^2\Vert\}$ 
we can express the achievable rate in terms of the singular value of the propagation matrix $G$:
\begin{equation}
G=UD_sV^H \label{equation:5}
\end{equation}
$D_s$ is the diagonal matrix, $U$ and $V$ is the unitary matrix, the diagonal elements $\{v_1,v_2,v_3\newline\cdots v_{min(n,m)}\}$ are the singular values of the propagation matrix, (\ref{equation:3}) can be expressed by singular values:
\begin{equation}
C=\sum_{l=1}^{\min(m,n)}log_2(1+\frac{\rho v_l^2}{n})
\end{equation} 
the bound of the achievable rate in (\ref{equation:3}) can be expressed as:
\begin{equation}
log_2(1+\frac{\rho Tr(GG^H)}{n})\leq C\leq\min(n,m)log_2(1+\frac{\rho Tr(GG^H)}{n\min(n,m)})\label{equation:6}
\end{equation}
$Tr(GG^H)$ is the trace of the propagation matrix G and $Tr(GG^H)=\sum_{l=1}^{\min(m,n)}v_l^2$ for simplicity, we assume that the magnitude of the propagation matrix elements is 1, so $Tr(GG^H)\approx mn$, (\ref{equation:6}) is simplified as follows
\begin{equation}
log_2(1+\frac{\rho}{m})\leq C\leq\min(n,m)log_2(1+\frac{\rho\max(n,m)}{n}) \label{equation:7}
\end{equation}\newline
\subsection{Data Rate}
It can be easily deduced that the larger scale of the array will result in aggressive spatial multiplexing gain, the singular value of the tall propagation matrix $\{v_1,v_2,v_3\cdots v_{min(n,m)}\}$ tends to be large and stable under the favorable propagation condition, which will be further explained in section ''small scale fading vanish'' it is possible to get more parallel data pipes. more over under the the condition that the SNR of the receiving signal is very low e.g terminals locate at the edge of the cell, the achievable rate of (\ref{equation:6}) becomes:
\begin{equation}
C_{\rho\to 0}\approx\frac{\rho Tr(GG^H)}{nln2}=\frac{\rho m}{ln2} \label{equation:8}
\end{equation}
from the perspective of achievable rate, multiple transmit antennas are of no value.
with the number of transmit antennas grows large, the (\ref{equation:6}) becomes:
\begin{equation}
C_{n\gg m}\approx log_2det(I_m+\rho I_m)=mlog_2(1+\rho)\label{equation:9}
\end{equation}
with the number of receive antennas grows large, the (\ref{equation:6}) becomes:
\begin{equation}
C_{m\gg n}=log_2det(I_n+\frac{\rho G^HG}{n})\approx nlog_2(1+\frac{\rho m}{n})
\end{equation}\label{equation:10}
the large number of the antennas will help to reserve the multiplexing gain under the extreme conditions that the SNR is low.
\subsection{Radiate Energy Efficiency}
The large scale antenna array has the potential to focus the radiate energy into a small regions or we can say the location of the intended terminal,The underlying physics is coherent superposition of wavefronts. By appropriately shaping the signals sent out by the antennas, the base station can make sure that all wave fronts collectively emitted by all antennas add up constructively at the locations of the intended terminals, but destructively (randomly) at every where else.\newline
\subsection{Small Scale Fading Vanishes}
In the massive MIMO scheme, we have the propagation matrix G that has a very tall structure, at the same time, under the favorable propagation condition\cite{8}(the propagation elements subject to independent and identical Rayleigh distribution), with the combination of these two conditions, recall the achievable rate in (\ref{equation:3}) the propagation matrix G has the row vector that is enough independent from each other and the as the length of the row vector increase the 2-norm of the row vectors increase much more faster than the inner product of the different row vectors, which is called asymptotically orthogonal. With this conclusion, in theory the small scale fading can be eliminated, more details are provided in\cite{7}.
\subsection{Pilot Contamination}
Pilot contamination can not vanish as the number of the base station antenna become unlimited, because of beamforming. One cell overhear the pilot from the terminals in the other cell. As consequence, base station will transmit the partially beamformed data vector to the terminals in the other cells and at the same time the terminals in this cell will also receive the component of the composite vector.
\subsection{Mutual Coupling}
Antenna array is never ideal(nonisotropic and polarized) as we often assume,  In large scale MIMO Increasing the number of antenna elements implies that the antenna separation decreases. Which indicate the mutual coupling(magnetic interaction), this effect will greatly determined by the structure of the antenna array(ULA, 2D, 3D), how to solve the issue of increasing coupling effect when the structure of array is 2 dimensions or 3 dimensions. 
\subsection{Channel reciprocity}
Because of the large scale of array, the traditional pilot training method of the down link will not be valid the time slots that need to be allocated for estimation will surpass the coherence time of channel. Massive MIMO must make use of TDD and matrix reciprocity to get the DL channel information.
\section{Conclusion}
This report provide a brief review of conventional MIMO system and Massive MIMO system, as to conventional MIMO system, the basic two major advantages it can provide are the diversity gain and multiplexing gain, the former one can improve the reliability of the channel, the latter one can increase the data rate of the channel. What is more, MIMO systems consider interference reduction which allows spectrum reuse for cochannel and increase multicell capacity. the basic concept and techniques are also presented.\newline
very large scale MIMO is widely recognized as a key enabling technology for future beyond 4G cellular system. the second part focus on the potentials and challenges of Massive MIMO system, comparing to conventional MIMO system, very large scale MIMO can provide huge advantages at high data rate, radiate energy efficiency, quality of service, degree of freedom and small scale fading vanish. The challenges also exit ahead the realization of Massive MIMO system such as pilot contamination, mutual coupling of antennas and channel reciprocity. The detection of Massive MIMO system is different from that of conventional MIMO system, the further exploration will launch soon.
\newpage
\bibliographystyle{IEEEtran}
\bibliography{citation}

\end{document}

### 2015-08-06 Report revised May 12 2015/Report April 2015/Report_draft.tex
Reorganized Report Record

--- 2015-04-17 Lattice Reduction/Report April 2015/Report_draft.tex
@@
 \section{Introduction}
-Detection algorithm is one of the key components of Multiple-Input Multiple-Output (MIMO) systems.
+Decoder is one of the key components of Multiple-Input Multiple-Output (MIMO) systems.
 Designing of high performance and low complexity detector has become a bottleneck of Large MIMO systems.
@@
 \centering
-\includegraphics[scale=0.6]{NtE.eps}
+\includegraphics[scale=0.6]{NtE1.eps}
 \caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
@@
 \centering
-\centering\includegraphics[width=0.7\textwidth, height=5cm]{LogE_om_em.eps}
+\includegraphics[width=0.7\textwidth, height=5cm]{LogE_om_em1.eps}
 \caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
@@
 \centering
-\includegraphics[width=0.7\textwidth, height=5cm]{LogE_om_t.eps}
+\includegraphics[width=0.7\textwidth, height=5cm]{LogE_om_t1.eps}
 \caption{Theoretical $E[\ln(\phi_{om})]_{t}$}

### 2015-08-06 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/SVR_DETECTOR.cpp

@@ -1,17 +1,0 @@
-//============================================================================
-// Name        : SVR_DETECTOR
-// Author      : Tianpei Chen
-// Version     :
-// Copyright   : Your copyright notice
-// Description : The original version of support vector regression for large MIMO uplink
-//detection
-//============================================================================
-
-#include"common.h"
-
-
-void SVR_DETECTOR(){
-return;
-}
-
-

### 2015-08-06 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/SVR_MIMO_communication_line.cpp

@@ -95,7 +95,7 @@ int main(void) {
 	long int iteration;                       //iteration time
 	long int bitError=0;               //bit error symbol error
 	double BitErrorRate, SymbolErrorRate, sigmas, sigman; //bit error rate, symbol error rate, standard deviation of signal and noise
-	float *SNR;      //this is the SNR per bit in dB
+	float *SNR;      //this is the SNR per bit
 	int M = Constellationsize;                               //modulation scheme
 	int count, count1, count2, count3, count4;   //used for loops
 	const int Nt = MATRIX_SIZE; // Nt is the number of transmit antennas. Must be a positive integer.

### 2015-08-06 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/TakeStep.h

@@ -1,0 +1,84 @@
+/*
+ * TakeStep.h
+ *
+ *  Created on: Aug 5, 2015
+ *      Author: tianpei.chen@mail.mcgill.ca
+ */
+
+#ifndef TAKESTEP_H_
+#define TAKESTEP_H_
+#include"common.h"
+void TakeStep(gsl_vector *l_m,
+		gsl_vector_complex *phi,
+		gsl_matrix *K,
+		int label, // determine which part we are updating(real or imaginary)
+		int i,
+		int j
+		){
+	double l_m_temp, phi_temp;
+	double sigmai=0,sigmai_hat=0, sigmaj=0, sigmaj_hat=0;
+	gsl_complex phi_temp_complex;
+	int count;
+	if(i<Nr){
+		l_m_temp=gsl_vector_get(l_m, i)+(gsl_vector_complex_get(phi,i).dat[label]-epsilon)
+				/(gsl_matrix_get(K,i,i));
+		if(l_m_temp<0){
+			l_m_temp=0;
+		}else if(l_m_temp>C){
+			l_m_temp=C;
+		}
+		sigmai=gsl_vector_get(l_m,i)-l_m_temp;
+		gsl_vector_set(l_m,i, l_m_temp);
+	}else{
+		l_m_temp=gsl_vector_get(l_m, i)-(gsl_vector_complex_get(phi,i).dat[label]+epsilon)
+					/(gsl_matrix_get(K,i,i));
+		if(l_m_temp<0){
+			l_m_temp=0;
+		}else if(l_m_temp>C){
+			l_m_temp=C;
+		}
+		sigmai_hat=gsl_vector_get(l_m,i)-l_m_temp;
+		gsl_vector_set(l_m,i, l_m_temp);
+	}
+	if(j<Nr){
+		l_m_temp=gsl_vector_get(l_m, j)+(gsl_vector_complex_get(phi,j).dat[label]-epsilon)
+				/(gsl_matrix_get(K,j,j));
+		if(l_m_temp<0){
+			l_m_temp=0;
+		}else if(l_m_temp>C){
+			l_m_temp=C;
+		}
+		sigmaj=gsl_vector_get(l_m,j)-l_m_temp;
+		gsl_vector_set(l_m, j,l_m_temp);
+	}else{
+		l_m_temp=gsl_vector_get(l_m, j)-(gsl_vector_complex_get(phi,j).dat[label]-epsilon)
+				/(gsl_matrix_get(K, j,j));
[…]

### 2015-08-06 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/WSS2_1Dsolver.h

@@ -1,0 +1,73 @@
+/*
+ * WSS2_1Dsolver.h
+ *
+ *  Created on: Aug 4, 2015
+ *      Author: tianpei.chen@mail.mcgill.ca
+ *      This is 2D selection subroutine based on maximum 2 1D direction
+ *      subroutine, choose the two Lagrange multipliers with maximum 1D gain
+ *      to perform 2D solver.
+ *      INPUT: alpha(beta), alpha_hat(beta_hat), label1, label2, phi, R_Kernel
+ *      OUTPUT: First, Second
+ */
+#include "common.h"
+#ifndef WSS2_1DSOLVER_H_
+#define WSS2_1DSOLVER_H_
+void 	WSS2_1Dsolver(gsl_vector *l_m,  //Lagrange Multiplier vector
+        gsl_vector_complex *phi,  //update parameter
+        gsl_matrix *R_Kernel,    //real kernel matrix
+        int F_i,  //index of first maximum Lagrange multiplier
+        int S_i //index of second maximum Lagrange multiplier
+){
+double best_g, g;
+double sigma, sigma_hat;
+double temp_l_m, temp_l_m_hat;
+int count;
+double phi_p[2*Nr];
+for(count=0;count<2*Nr;count++){  //take real and imaginary part of phi
+	if(count<Nr){
+  phi_p[count]=gsl_vector_complex_get(phi,count).dat[0];
+	}else{
+		phi_p[count]=gsl_vector_complex_get(phi,count-Nr).dat[1];
+	}
+}
+best_g=-1;
+F_i=S_i=-1;
+for(count=0;count<2*Nr;count++){
+	if(count<Nr){
+		temp_l_m=gsl_vector_get(l_m, count)+(phi_p[count]-epsilon)/
+				(gsl_matrix_get(R_Kernel, count,count));
+		if(temp_l_m<0){
+			temp_l_m=0;
+		}else if (temp_l_m>C){
+			temp_l_m=C;
+		}
+		sigma=temp_l_m-gsl_vector_get(l_m,count);
+		sigma_hat=0;
+	}else{
+		temp_l_m_hat=gsl_vector_get(l_m, count)-(phi_p[count]+epsilon)/
+				(gsl_matrix_get(R_Kernel, count,count));
+		if(temp_l_m<0){
+			temp_l_m_hat=0;
[…]

### 2015-08-06 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/takestep.h

@@ -1,0 +1,21 @@
+/*
+ * takestep.h
+ *
+ *  Created on: Jul 16, 2015
+ *      Author: tianpei.chen@mail.mcgill.ca
+ */
+
+#ifndef TAKESTEP_H_
+#define TAKESTEP_H_
+#include"common.h"
+int takestep(gsl_complex alpha,
+		int index,
+		gsl_vector_complex *Error,
+		gsl_vector_complex *eta){
+	return 0;
+}
+
+
+
+
+#endif /* TAKESTEP_H_ */

### 2015-08-07 Report Aug 5 2015/Report Aug 2015.tex
backup

--- 2015-08-06 Report Aug 5 2015/Report_Aug_2015.tex
@@
-%% bare_conf.tex
-%% V1.4
-%% 2012/12/27
+%% bare_jrnl.tex
+%% V1.4a
+%% 2014/09/17
 %% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
+%% see http://www.michaelshell.org/
 %% for current contact information.
@@
 %% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8 or later) with an IEEE conference paper.
+%% (requires IEEEtran.cls version 1.8a or later) with an IEEE
+%% journal paper.
 %%
@@
 %% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex,
-%%                    bare_jrnl_transmag.tex
+%%                    bare_conf.tex, bare_jrnl.tex, bare_conf_compsoc.tex,
+%%                    bare_jrnl_compsoc.tex, bare_jrnl_transmag.tex
 %%*************************************************************************
@@
 % *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
+% *** with production work. IEEE's font choices and paper sizes can       ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
 % The testflow support page is at:
@@
 
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-\documentclass[12pt,letter,final]{article}
-% Add the compsoc option for Computer Society conferences.
+%\documentclass[journal]{IEEEtran}
+\documentclass[12pt, draftclsnofoot, onecolumn]{IEEEtran}
 %
@@
 % manually specify the path to it like:
+% \documentclass[journal]{../sty/IEEEtran}
+
 \usepackage[latin1]{inputenc}
@@
 \usepackage{epsfig}
-\usepackage{appendix}
+%\usepackage{appendix}
 \usepackage{caption}
@@
 % cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
 % The latest version can be obtained at:
@@
 %
-%\ifCLASSINFOpdf
+\ifCLASSINFOpdf
   % \usepackage[pdftex]{graphicx}
@@
   % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-%\else
+\else
   % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
@@
   % \DeclareGraphicsExtensions{.eps}
-%\fi
+\fi
 % graphicx was written by David Carlisle and Sebastian Rahtz. It is
@@
 %
-%\usepackage{fixltx2e}
+\usepackage{fixltx2e}
 % fixltx2e, the successor to the earlier fix2col.sty, was written by
@@
 
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
+% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
 % *** PDF, URL AND HYPERLINK PACKAGES ***
 %
-%\usepackage{url}
+\usepackage{url}
 % url.sty was written by Donald Arseneau. It provides better support for
@@
 % correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
+\hyphenation{op-tical net-works semi-conduc-tor}
+
+\begin{document}
 
@@
 % paper title
-% can use linebreaks \\ within to get better formatting as desired
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
 % Do not put math or special symbols in the title.
@@
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-%\author{\IEEEauthorblockN{Tianpei Chen}
-%\IEEEauthorblockA{ID: 25504946\\Department of Electrical and\\Computer Engineering\\
-%McGill University\\
-%Montreal, Quebec}}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
 \author{Tianpei Chen\\
 Department of Electrical and Computer Engineering\\
- McGill University}
+McGill University\\
+\today}
 
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
+%\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
+%        John~Doe,~\IEEEmembership{Fellow,~OSA,}
+%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
+%\thanks{M. Shell is with the Department
+%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
+%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
+%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
+%\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
 
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
 % 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+%\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
+%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2014 IEEE}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark.
 
@@
 %\IEEEspecialpapernotice{(Invited Paper)}
-\begin{document}
+
 % make the title area
+\maketitle
+
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
+%\begin{abstract}
+%The abstract goes here.
+%\end{abstract}
+
+% Note that keywords are not normally used for peerreview papers.
+%\begin{IEEEkeywords}
+%IEEEtran, journal, \LaTeX, paper, template.
+%\end{IEEEkeywords}
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
 \begin{spacing}{2.5}
-\maketitle
+
 \section{Introduction}
-Decoder is one of the key components of Multiple-Input Multiple-Output (MIMO) systems.
-Designing of high performance and low complexity detector has become a bottleneck of Large MIMO systems.
-Recently, an interesting property of large MIMO channel called channel hardening phenomenon has been found \cite{hochwald2004multiple}\cite{tse2005fundamentals}\cite{marvcenko1967distribution}\cite{tulino2004random}, which states the phenomenon that with the number of receiving or transmitting antennas increasing, the variances of channel mutual information decrease.
-Simply saying, the channel "hardens".
-An useful aspect of channel hardening phenomenon is that off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$ matrix become more and more negligible comparing to diagonal elements when the number of receiving antennas or transmitting antennas becomes large.
+% The very first letter is a 2 line initial drop letter followed
+% by the rest of the first word in caps.
+% 
+% form to use if the first word consists of a single letter:
+% \IEEEPARstart{A}{demo} file is ....
+% 
+% form to use if you need the single drop letter followed by
+% normal text (unknown if ever used by IEEE):
+% \IEEEPARstart{A}{}demo file is ....
+% 
+% Some journals put the first two words in caps:
+% \IEEEPARstart{T}{his demo} file is ....
+% 
+% Here we have the typical use of a "T" for an initial drop letter
+% and "HIS" in caps to complete the first word.
+%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
+%for IEEE journal papers produced under \LaTeX\ using
+%IEEEtran.cls version 1.8a and later.
+% You must have at least 2 lines in the paragraph with the drop letter
+% (should never be an issue)
+%I wish you the best of success.
 
- Channel hardening phenomenon provides an opportunity for designing computationally economical detection algorithms.
-For example, linear detectors (LDs) such as zero forcing (ZF) and minimum mean square error (MMSE) detectors need to do costly matrix operations such as matrix multiplication and inverse.
-With channel hardening phenomenon, this process can be accelerated by approximate matrix inversion using series expansion techniques and deterministic approximations in large dimensions\cite{wu2013approximate}.
-Channel hardening phenomenon can also provide computational advances to machine learning based detectors, e.g.
-probability data association (PDA)\cite{fricke1900impact}\cite{pham2004generalized} and message passing detectors\cite{som2011low}\cite{goldberger2011mimo}\cite{lakshmi2013channel} and Monte-Carlo Markov Chain (MCMC) MIMO detectors\cite{farhang2006markov}\cite{datta2012novel}.
-This type of algorithms work well in large sparse systems.
+%\hfill mds
 
-In this report, we propose some useful insights of the orthogonal properties of channel.
-We define orthogonality measurement (om), which is a well round metric that considers both diagonal and off diagonal elements of $\mathbf{H}^{H}\mathbf{H}$.
+%\hfill September 17, 2014
+Decoder is one of the key components of Multiple-Input Multiple-Output (MIMO) systems. Designing of high performance and low complexity detector has become a bottleneck of Large MIMO systems.
 
-The rest of the report is organized as follows, section \ref{system model} introduces system model.
-Section \ref{preliminary} provides some preliminaries.
-Section \ref{log expectation of om} discusses the derivation of logarithmic expectation of orthogonality measurement.
-In section \ref{pdf of om} we obtain probability density function of orthogonality measurement.
-Some computer simulation results are presented in section \ref{computer simulation}.
+Firmly grounded in framework of statistical learning theory, Support Vector Machine (SVM) is proposed in 1960s [ref vapnik], and of immense research and industry interest since 1990s.
+SVM is a powerful tool for supervised learning tasks such as classification, regression and prediction.
+Moreover, the kernel trick [ref learning with kernels SVM regularization] makes it possible to map data samples into higher dimensional feature space.
+Therefore SVM can deal with non-linear learning tasks.
+This makes SVM become a promising tool for complex real-world problems.
+Based on the similar principle, $\epsilon$-Support Vector Regression (epsilon-SVR) [vapnik 1995, smola 2003], is developed.
 
+Like SVM, epsilon-SVR first change primal objective function into dual optimization task, then solving the dual quadratic optimization problem.
+Typically this kind of problem can be solved by numerical quadratic optimization (QP) methods, however, they are computational costly.
+Decomposition methods, denotes a set of algorithms that divide the optimization variables (Lagrange multipliers) into two sets W and N, W is the work set and N contains the rest optimization variables.
+In each iteration, only work set is updated for optimization while the other variables are fixed.
+Sequential Minimal Optimization (SMO) [ref A fast algorithm sequential minimal optimization] is an extreme case of decomposition methods which chooses dual Lagrange multiplier to optimize in each iteration.
+In each iteration, decomposition method can find an analytic optimal solution for work set, which makes the solver works much more faster than numerical QP algorithms.
+Decomposition methods can be employed to epsilon SVR by the similar manner.
+
+  Bouloulis et employ Wirtinger’s calculus into Reproducing Kernel Hilbert Space (RKHS) so that expands real-SVM to pure complex SVM by exploiting complex kernel [ref complex support vector machine].
+Based on this work, we construct a prototype of a complexity \$ performance controllable detector for large MIMO based on dual channel complex SVR.
+The detector can be divided into two parallel real SVR optimization problem which can be solved independently.
+Moreover, only real part of kernel matrix is needed in both channel.
+This means a large amount of computation can be reduced.
+
+  Steinwart et[ref SVM without offset] shows with a proper designed work set selection strategy, the approach that choosing double Lagrange multipliers can be much more faster than choosing single Lagrange multiplier without performance loss.
+
+Based on the discrete time MIMO channel model, In our regression model, this CSVR-detector is constructed without offset, The offset in SVR imposes an additional linear quality constraint, which makes it necessary for decomposition methods such as Sequential Minimal Optimization to update more than one Lagrange multipliers in each iteration.
+
+Therefore, for each real SVR without offset, in principle, only one offset is needed to be updated in each iteration, In our prototype, we propose a sequential single Lagrange multiplier search strategy that find two Lagrange multiplier sequentially, which can approximate the optimal dual Lagrange multiplier searching strategy.
+The former one only requires O(n) searches in one iteration, while the optimal dual Lagrange multiplier strategy requires O(n2) searches per iteration.
+%\subsection{Subsection Heading Here}
+%Subsection text here.
+
+% needed in second column of first page if using \IEEEpubid
+%\IEEEpubidadjcol
+
+%\subsubsection{Subsubsection Heading Here}
+%Subsubsection text here.
 \section{System Model}\label{system model}
@@
 \end{equation}
-where $\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
+where $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
 4-QAM, 16-QAM, 64-QAM) of size $M$.
 The possible transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian components with unit variance.
-Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian zero mean components with unit variance.
+Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
 
@@
 \end{equation}  
+\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
+Suppose we are given training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{l},y_{l}))$, $l$ denotes the number of training samples, $\mathbf{x}\in \mathbb{R}^{v}$ denotes input data vector, $v$ is the number of features in $\mathbf{x}$.
+$y$ denotes output.
+The regression model (either linear or non-linear regression) is given by
+\begin{equation}
+y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i\in 1\cdots l 
+\label{equation1}
+\end{equation} 
+where $\mathbf{w}$ denotes regression coefficient vector, $\Phi(x)$ denotes the mapping of $\mathbf{x}$ to higher dimensional feature space. \ref{equation1}.
+\begin{figure}
+\centering
+%\includegraphics[scale=•]{•}
+\caption{}
+\label{epsilon-SVR}
+\end{figure}
+Here we give the primal optimization problem directly
+%\begin{eqnarray}
+%\nonumber
+ %\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{j=1}^{l}(\xi_{i}+\hat{\xi}_{i}})\\
+%s.t. \l{
+
+%\end{eqnarray}\label{primal optimization problem}
+In \ref{primal optimization problem}, $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model.
+$\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function.
+$\xi$ and $\hat{\xi}$ denote slack variable to cope with noise of input data set.
+$C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
+From the rationale of risk function, let $f(\mathbf{x})$ denotes regression function, $R(\mathbf{x},f(\mathbf{x}))$ denotes the risk function.
+\begin{equation}
+R(\mathbf{x},f(\mathbf{x}))
+\label{risk function1}
+\end{equation}
+ The optimization problem can be expressed as
+\begin{equation}
+minimize \lambda||f||^{2}+R(\mathbf{x},f(\mathbf{x}))
+\label{risk function2}
+\end{equation}
+
 \section{Dual Channel Complex Kernel Support Vector Regression for Large MIMO system}\label{dual channel CSVR}
@@
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
-\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
-\label{figure1}
-\end{figure}
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
+%\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
+%\label{figure1}
+%\end{figure}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
-\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
-\label{figure2}
-\end{figure}
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
+%\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
+%\label{figure2}
+%\end{figure}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[scale=0.6]{NtE.eps}
-\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
-\label{figure3}
-\end{figure}
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[scale=0.6]{NtE.eps}
+%\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
+%\label{figure3}
+%\end{figure}
 
@@
 
-\begin{appendices}
-\section{Appendix A}
+% An example of a floating figure using the graphicx package.
+% Note that \label must occur AFTER (or within) \caption.
+% For figures, \caption should occur after the \includegraphics.
+% Note that IEEEtran v1.7 and later has special internal code that
+% is designed to preserve the operation of \label within \caption
+% even when the captionsoff option is in effect. However, because
+% of issues like this, it may be the safest practice to put all your
+% \label just after \caption rather than within \caption{}.
+%
+% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+% option should be used if it is desired that the figures are to be
+% displayed while in draft mode.
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=2.5in]{myfigure}
+% where an .eps filename suffix will be assumed under latex, 
+% and a .pdf suffix will be assumed for pdflatex; or what has been declared
+% via \DeclareGraphicsExtensions.
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure}
+
+% Note that IEEE typically puts floats only at the top, even when this
+% results in a large percentage of a column being occupied by floats.
+
+% An example of a double column floating figure using two subfigures.
+% (The subfig.sty package must be loaded for this to work.)
+% The subfigure \label commands are set within each subfloat command,
+% and the \label for the overall figure must come after \caption.
+% \hfil is used as a separator to get equal spacing.
+% Watch out that the combined width of all the subfigures on a 
+% line do not exceed the text width or a line break will occur.
+%
+%\begin{figure*}[!t]
+%\centering
+%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
+%\label{fig_first_case}}
+%\hfil
+%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
+%\label{fig_second_case}}
+%\caption{Simulation results for the network.}
+%\label{fig_sim}
+%\end{figure*}
+%
+% Note that often IEEE papers with subfigures do not employ subfigure
+% captions (using the optional argument to \subfloat[]), but instead will
+% reference/describe all of them (a), (b), etc., within the main caption.
+% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
+% labels, the optional argument to \subfloat must be present. If a
+% subcaption is not desired, just leave its contents blank,
+% e.g., \subfloat[].
+
+% An example of a floating table. Note that, for IEEE style tables, the
+% \caption command should come BEFORE the table and, given that table
+% captions serve much like titles, are usually capitalized except for words
+% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
+% and up, which are usually not capitalized unless they are the first or
+% last word of the caption. Table text will default to \footnotesize as
+% IEEE normally uses this smaller font for tables.
+% The \label must come after \caption as always.
+%
+%\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+%\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+%\caption{An Example of a Table}
+%\label{table_example}
+%\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+%\begin{tabular}{|c||c|}
+%\hline
+%One & Two\\
+%\hline
+%Three & Four\\
+%\hline
+%\end{tabular}
+%\end{table}
+
+% Note that the IEEE does not put floats in the very first column
+% - or typically anywhere on the first page for that matter. Also,
+% in-text middle ("here") positioning is typically not used, but it
+% is allowed and encouraged for Computer Society conferences (but
+% not Computer Society journals). Most IEEE journals/conferences use
+% top floats exclusively. 
+% Note that, LaTeX2e, unlike IEEE journals/conferences, places
+% footnotes above bottom floats. This can be corrected via the
+% \fnbelowfloat command of the stfloats package.
+
+\section{Conclusion}
+The conclusion goes here.
+
+% if have a single appendix:
+%\appendix[Proof of the Zonklar Equations]
+% or
+%\appendix  % for no appendix heading
+% do not use \section anymore after \appendix, only \section*
+% is possibly needed
+
+% use appendices with more than one appendix
+% then use \section to start each appendix
+% you must declare a \section before using any
+% \subsection or using \label (\appendices by itself
+% starts a section numbered zero.)
+%
+
+\appendices
+\section{Proof of the First Zonklar Equation}
+Appendix one text goes here.
+
+% you can choose not to have a title for an appendix
+% if you want by leaving the argument blank
+\section{}
+Appendix two text goes here.
+\section{}
 Let $\mathbf{A}\in \mathbb{C}^{m\times m}$, $A\sim \mathbb{C}W(n, \mathbf{\Sigma})$, $\mathbb{C}W(n, \mathbf{\Sigma})$ denotes complex Wishart distribution with $n$ degrees of freedom and covariance matrix $\mathbf{\Sigma}$.
@@
 where $\psi$ denotes Digamma function.
-\section{Appendix B}
+\section{}
 If $x\sim Gamma(n, \theta)$, with shape parameter $k$ and scale parameter $\theta$, $x>0$, $\Gamma(k)$ denotes Gamma function, the density function of Gamma distribution is
@@
 where $\psi(k)$ denotes Digamma function.
-\section{Appendix C}
+\section{}
 $x_{1}, x_{2}, \cdots x_{N_{t}}$ are independent beta variables, the probability density function (pdf) can be written as: 
@@
 
-\end{appendices}
+% use section* for acknowledgment
+%\section*{Acknowledgment}
 
+%The authors would like to thank...
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+%\begin{thebibliography}{1}
+
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+%\end{thebibliography}
+
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+%\begin{IEEEbiography}{Michael Shell}
+%Biography text here.
+%\end{IEEEbiography}
+
+% if you will not have a photo at all:
+%\begin{IEEEbiographynophoto}{John Doe}
+%Biography text here.
+%\end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+%\begin{IEEEbiographynophoto}{Jane Doe}
+%Biography text here.
+%\end{IEEEbiographynophoto}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
 \end{spacing}

### 2015-08-10 Report Aug 5 2015/Report Aug 2015.tex
backup

@@
 Here we give the primal optimization problem directly
-%\begin{eqnarray}
-%\nonumber
- %\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{j=1}^{l}(\xi_{i}+\hat{\xi}_{i}})\\
-%s.t. \l{
-
-%\end{eqnarray}\label{primal optimization problem}
+\begin{eqnarray}
+\nonumber
+\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
+s.t. \left\{\begin{array}{ll}
+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
+\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
+\epsilon, \xi,\hat{\xi} &\geq 0\\
+\end{array}\right.
+\label{primal optimization problem}
+\end{eqnarray}
 In \ref{primal optimization problem}, $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model.
 $\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function.
-$\xi$ and $\hat{\xi}$ denote slack variable to cope with noise of input data set.
+$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes cost function, the simplest cost function is $R(x)=x$, risk function is determined by the statistical distribution of noise \cite{A tutorial of Support Vector Regression}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
 $C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
-From the rationale of risk function, let $f(\mathbf{x})$ denotes regression function, $R(\mathbf{x},f(\mathbf{x}))$ denotes the risk function.
-\begin{equation}
-R(\mathbf{x},f(\mathbf{x}))
+
+From the rationale of risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
+Assume the data samples are i.i.d.
+Based on Maximum Likelihood (ML) principle we want to
+\begin{eqnarray}
+maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=\prod_{i=1}^{l}P(\xi_{i})\\
+&=\prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),
 \label{risk function1}
-\end{equation}
- The optimization problem can be expressed as
-\begin{equation}
-minimize \lambda||f||^{2}+R(\mathbf{x},f(\mathbf{x}))
+\end{eqnarray}
+Take the logarithm of (\ref{risk function1}), we have
+\begin{eqnarray}
+maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))),
 \label{risk function2}
-\end{equation}
+\end{eqnarray}
+Therefore the $i$th risk function of $(\mathbf{x_{i}}, y_{i})$ can be written as 
+\begin{eqnarray}
+c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i}))=-log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))).
+\label{risk function3}
+\end{eqnarray}
+In $\epsilon$-SVR, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{risk function3}).
+\begin{eqnarray}
+|x|_{\epsilon}=\left\{\begin{array}{ll}
+0   &if\quad |x|<\epsilon\\
+|x|-\epsilon  &otherwise\\
+\end{array}\right.
+\label{Vepsilon}
+\end{eqnarray}
+Thus the cost function in $\epsilon$-SVR can be written as 
+\begin{equation}
+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
+\label{cost function}
+\end{equation}
+where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the cost function with regularization term can written as
+\begin{equation}
+minimize\quad \lambda||w||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),
+\label{total cost function}
+\end{equation} 
+where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
+\begin{equation}
+minimize \quad \frac{1}{2}||w||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
+\label{final cost function}
+\end{equation}
+where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
+\begin{eqnarray}
+\nonumber
+\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
+s.t. \left\{\begin{array}{ll}
+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
+\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
+\epsilon, \xi,\hat{\xi} &\geq 0\\
+\end{array}\right.
+\end{eqnarray}
+where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered, we arrive to at a convex minimization problem \cite{smola and skpkof 1998a tutorial of SVR}.
+
+Build dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier, we have dual optimization problem
+\begin{eqnarray}
+\nonumber
+\min_{\mathbf{w}, \xi, \hat{\xi}} \max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\theta=
+\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
+-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
+\nonumber
+s.t. \left\{\begin{array}{cc}
+\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
+\xi, \hat{\xi}\geq  0\\
+\end{array}\right. 
+\label{lagrange duality1}
+\end{eqnarray}
+where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, \ref{lagrange duality1} is equivalent to
+\begin{eqnarray}
+\nonumber
+\max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\min_{\mathbf{w}, \xi, \hat{\xi}} \Theta=
+\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
+-\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
+\nonumber
+s.t. \left\{\begin{array}{cc}
+\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
+\xi, \hat{\xi}\geq  0\\
+\end{array}\right. 
+\label{lagrange duality2}
+\end{eqnarray}
+Take the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$, and find the minimum.
+\begin{equation}
+\frac{\partial \theta}{\partial \mathbf{w}}=w-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})
+\label{partial1}
+\end{equation}
+\begin{equation}
+\frac{\partial \theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0
+\label{partial2}
+\end{equation}
+\begin{equation}
+\frac{\partial \theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0
+\label{partial3}
+\end{equation}
+\begin{equation}
+\frac{\partial \theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0
+\label{partial4}
+\end{equation} 
+Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}), yields the final dual optimization objective function.
 

### 2015-08-10 Report Aug 5 2015/Report Aug 2015.tex
backup

@@
 
-Build dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier, we have dual optimization problem
+we construct dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier, we have dual optimization problem
 \begin{eqnarray}
@@
 \frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
+\nonumber
 -\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
-\nonumber
 s.t. \left\{\begin{array}{cc}
@@
 \end{eqnarray}
-where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, \ref{lagrange duality1} is equivalent to
+where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, (\ref{lagrange duality1}) is equivalent to
 \begin{eqnarray}
@@
 \frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
+\nonumber
 -\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\ 
-\nonumber
 s.t. \left\{\begin{array}{cc}
@@
 \xi, \hat{\xi}\geq  0\\
-\end{array}\right. 
-\label{lagrange duality2}
+\end{array}\right.\label{lagrange duality2}
 \end{eqnarray}
 Take the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$, and find the minimum.
+
 \begin{equation}
@@
 \end{equation}
+
 \begin{equation}
@@
 \end{equation} 
-Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}), yields the final dual optimization objective function.
+Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}), yields the final dual optimization objective function, for sake of brevity, we make $C_{i}$ uniform to all data samples ：
+\begin{eqnarray}
+\nonumber
+maximize\quad\Theta &=&\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
+\nonumber
+&+&(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
++\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
+&-&\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
+\nonumber
+s.t.\left\{\begin{array}{l}
+\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
+0<\alpha<C\tilde{R}(\alpha)\\
+0<\hat{\alpha}<C\tilde{R}(\hat{\alpha})\\
+\end{array}\right.
+\label{dual objective function1}
+\end{eqnarray}
+(\ref{dual objective function1}) can be simplified to 
+\begin{eqnarray}
+\nonumber
+maximize\quad \Theta &=&-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
+\nonumber
+&+&C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
+&=&-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
+\label{dual optimization function2}
+\end{eqnarray}
+where $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{l}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{l}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{l}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{l}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0,  $\tilde{R}(\xi)=R(\xi)-\xi R^{'}(\xi)\in \mathbb{R}^{l}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes data kernel matrix.
+We define the following $2l$ vectors
+$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2l}$, 
+\begin{eqnarray}
+\mathbf{v}_{i}=\left\{\begin{array}{ll}
+1\quad i=1,\ldots, l\\
+-1\quad i=l+1,\ldots, 2l\\ 
+\end{array}\right.
+\end{eqnarray}
+(\ref{dual optimization function2}) can be reformulate as 
+\begin{equation}
+maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{array}{ll}
+\mathbf{K}\quad -\mathbf{K}\\
+-\mathbf{K}\quad \mathbf{K}\\
+\end{array}\right]\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
+\label{vectorize dual optimization function}
+\end{equation}
 

### 2015-08-12 Report Aug 5 2015/Report Aug 2015.tex
backup
document backup

@@
 
-\begin{spacing}{2.5}
+%\begin{spacing}{2.5}
 
@@
 
-Therefore, for each real SVR without offset, in principle, only one offset is needed to be updated in each iteration, In our prototype, we propose a sequential single Lagrange multiplier search strategy that find two Lagrange multiplier sequentially, which can approximate the optimal dual Lagrange multiplier searching strategy.
-The former one only requires O(n) searches in one iteration, while the optimal dual Lagrange multiplier strategy requires O(n2) searches per iteration.
+Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our prototype, we propose a sequential single Lagrange multiplier search strategy that find two Lagrange multiplier sequentially, which can approximate the optimal dual Lagrange multiplier searching strategy.
+The former one only requires $O(n)$ searches in one iteration, while the optimal dual Lagrange multiplier strategy requires $O(n^{2})$ searches per iteration.
 %\subsection{Subsection Heading Here}
@@
 \section{System Model}\label{system model}
-We consider a complex uncoded spatial multiplexing MIMO system with $N_r$ receive and $N_t$ transmit antennas, $N_{r}\geq N_{t}$, over a flat fading channel.
+  Consider a large MIMO uplink multiplexing system with $N_{t}$ users, each user has one transmit antenna.
+The number of receive antennas at Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
+Typically large MIMO systems have hundreds of antennas at BS serving several tens of terminals, as shown in Fig {\ref{large MIMO uplink model}}.
+  \begin{figure}
+  \centering
+  \def\svgwidth{\columnwidth}
+  %\includegraphics[scale=•]{•}
+  \input{largeMIMOuplink.pdf_tex}
+  \caption{Large MIMO uplink system }
+  \label{large MIMO uplink model}
+  \end{figure}
+
+  Uncoded binary information sequences, which are modulated to complex symbols, are transmitted by users over a flat fading channel.
 Using a discrete time model, $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector written as:
 \begin{equation}
-\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{formula 1}
+\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{discrete time MIMO system}
 \end{equation}
@@
 where $\mathbf{w}$ denotes regression coefficient vector, $\Phi(x)$ denotes the mapping of $\mathbf{x}$ to higher dimensional feature space. \ref{equation1}.
+
 \begin{figure}
 \centering
-%\includegraphics[scale=•]{•}
+\def\svgwidth{\columnwidth}
+\input{epsilon-SVR.pdf_tex}
 \caption{}
@@
 \end{figure}
+
 Here we give the primal optimization problem directly
+\begin{eqnarray}
+\nonumber
+\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
+s.t. \left\{\begin{array}{ll}
+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
+\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
+\epsilon, \xi,\hat{\xi} &\geq 0
+\end{array}\right.
+\label{primal optimization problem}
+\end{eqnarray}
+In \ref{primal optimization problem}, $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model.
+$\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function.
+$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes cost function, the simplest cost function is $R(x)=x$, risk function is determined by the statistical distribution of noise \cite{A tutorial of Support Vector Regression}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
+$C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
+
+From the rationale of risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
+Assume the data samples are i.i.d.
+Based on Maximum Likelihood (ML) principle we want to
+\begin{eqnarray}
+\nonumber
+maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=\prod_{i=1}^{l}P(\xi_{i})\\
+&=\prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),
+\label{risk function1}
+\end{eqnarray}
+Take the logarithm of (\ref{risk function1}), we have
+\begin{eqnarray}
+maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))),
+\label{risk function2}
+\end{eqnarray}
+Therefore the $i$th risk function of $(\mathbf{x_{i}}, y_{i})$ can be written as 
+\begin{eqnarray}
+c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i}))=-log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))).
+\label{risk function3}
+\end{eqnarray}
+In $\epsilon$-SVR, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{risk function3}).
+\begin{eqnarray}
+|x|_{\epsilon}=\left\{\begin{array}{ll}
+0   &if\quad |x|<\epsilon\\
+|x|-\epsilon  &otherwise\\
+\end{array}\right.
+\label{Vepsilon}
+\end{eqnarray}
+Thus the cost function in $\epsilon$-SVR can be written as 
+\begin{equation}
+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
+\label{cost function}
+\end{equation}
+where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the cost function with regularization term can written as
+\begin{equation}
+minimize\quad \lambda||w||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),
+\label{total cost function}
+\end{equation} 
+where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
+\begin{equation}
+minimize \quad \frac{1}{2}||w||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
+\label{final cost function}
+\end{equation}
+where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
 \begin{eqnarray}
@@
 \end{array}\right.
-\label{primal optimization problem}
-\end{eqnarray}
-In \ref{primal optimization problem}, $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model.
-$\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function.
-$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes cost function, the simplest cost function is $R(x)=x$, risk function is determined by the statistical distribution of noise \cite{A tutorial of Support Vector Regression}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
-$C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
-
-From the rationale of risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
-Assume the data samples are i.i.d.
-Based on Maximum Likelihood (ML) principle we want to
-\begin{eqnarray}
-maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=\prod_{i=1}^{l}P(\xi_{i})\\
-&=\prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),
-\label{risk function1}
-\end{eqnarray}
-Take the logarithm of (\ref{risk function1}), we have
-\begin{eqnarray}
-maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))),
-\label{risk function2}
-\end{eqnarray}
-Therefore the $i$th risk function of $(\mathbf{x_{i}}, y_{i})$ can be written as 
-\begin{eqnarray}
-c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i}))=-log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))).
-\label{risk function3}
-\end{eqnarray}
-In $\epsilon$-SVR, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{risk function3}).
-\begin{eqnarray}
-|x|_{\epsilon}=\left\{\begin{array}{ll}
-0   &if\quad |x|<\epsilon\\
-|x|-\epsilon  &otherwise\\
-\end{array}\right.
-\label{Vepsilon}
-\end{eqnarray}
-Thus the cost function in $\epsilon$-SVR can be written as 
-\begin{equation}
-\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
-\label{cost function}
-\end{equation}
-where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the cost function with regularization term can written as
-\begin{equation}
-minimize\quad \lambda||w||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),
-\label{total cost function}
-\end{equation} 
-where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
-\begin{equation}
-minimize \quad \frac{1}{2}||w||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
-\label{final cost function}
-\end{equation}
-where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
-\begin{eqnarray}
-\nonumber
-\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-s.t. \left\{\begin{array}{ll}
-y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
-\epsilon, \xi,\hat{\xi} &\geq 0\\
-\end{array}\right.
 \end{eqnarray}
@@
 
-\section{Dual Channel Complex Kernel Support Vector Regression for Large MIMO system}\label{dual channel CSVR}
+\section{Dual Channel Real Kernel Complex Support Vector Regression for Large MIMO system}\label{dual channel CSVR}
+ Based on discrete time model of large MIMO uplink system in (\ref{discrete time MIMO system}), in our  regression model, the training data sample at detector is $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of channel propagation matrix $\mathbf{H}$, this yields a regression task without offset $b$:
+ \begin{eqnarray}
+ y_{i}=f_{true}(\mathbf{h}_{i})+n,\\
+ \label{regression part1a}
+ f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\mathbf{s},\\
+ \label{regression part1b}
+ \end{eqnarray}
+ where $f_{true}()$ denotes the true regression function, $n$ denotes additive noise.
+In this regression problem, receive symbol $y$ is the output data, $\mathbf{h}$ is input data sample, transmitted symbol vector $s$ is regression coefficients.
+Because the large MIMO system we consider here is complex, we employ complex support vector regression (CSVR).
+As shown in section (\ref{Introduce epsilon SVR}), in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to real cost functions which are defined in complex domain.
+The recent mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS)[\cite{wirtinger's calculus}] is employed to solve this problem.
+First we generalize our regression model by complex Hilbert space,
+Let $<>_{H}$ denotes inner product operation in real Hilbert space. $<,>_{\mathbb{H}}$ denotes inner products operation in complex Hilbert space, which has the following properties 
+\newtheorem{Lemma}{Lemma}
+\newtheorem{Property}{Property}
+\begin{Property}
+\label{Property1}
+\end{Property}
+\begin{Lemma}
+$\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{H}>_{\mathbb{H}}$
+\end{Lemma}
+
+\begin{proof}
+
+Assume $\mathbf{a}$, $\mathbf{b}$ are real vectors,$\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{v}$, $\mathbf{x}$, $\mathbf{y}$ are complex vectors,$\mathbf{x}$, $\mathbf{x}$ $\in \mathbb{C}^{v}$, according to the properties of complex Hilbert space, is can be easily proved
+\begin{equation}
+\mathbf{a}^{T}\mathbf{b} \in <\mathbf{a}, \mathbf{b}>_{H}
+\end{equation}
+\end{proof}
 
@@
 % that's all folks
-\end{spacing}
+%\end{spacing}
 \bibliographystyle{IEEEtran}

### 2015-08-18 Report Aug 5 2015/Report Aug 2015.tex
Backup

@@
 The task of the MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
-\section{Preliminaries}\label{preliminary}
-Orthogonality deficiency measures the how orthogonal a matrix is \cite{ma2008performance}, which is defined by
-\begin{equation}
-\phi_{od}=1-\frac{det(\mathbf{W})}{\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||^{2}},
-\label{formula1}
-\end{equation}
-where $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$ denotes Wishart matrix, $\mathbf{h}_{i}$ denotes the $i$ th column of $\mathbf{H}$, $det(\cdot)$ denotes determinant operation, $||\cdot||^{2}$ denotes 2-norm operation.
-In (\ref{formula1}), $||\mathbf{h}_{i}||^{2}=\sum_{j=1}^{N_{r}}|\mathbf{H}_{ji}|^{2}$, $\mathbf{H}_{ji}$ denotes the component of $\mathbf{H}$ at $j$ th row and $i$ th column.
-$|\mathbf{H}_{ji}|\sim Rayleigh(1/\sqrt{2})$, therefore $||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},1)$\cite{papoulis1996stochastic}.
-$Gamma(k,\theta)$ denotes Gamma distribution, with $k$ degrees of freedom and scale $\theta$.
-Furthermore, we have:
-\begin{equation}
-2||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},2)\sim\chi^{2}_{2N_{r}},
-\label{formula2}
-\end{equation} 
-$\chi^{2}_{k}$ denotes chi-square distribution with $k$ degrees of freedom. For the sake of simplicity, (\ref{formula1}) can be changed to:
-\begin{equation}
-\phi_{om}=\frac{det(\mathbf{W})}{\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||^{2}}=\frac{2^{N_{t}}det(\mathbf{W})}{\prod_{i=1}^{N_{t}}2||\mathbf{h}_{i}||^{2}}.
-\label{formula3}
-\end{equation}
-Taking logarithmic operation to $\phi_{om}$ we have 
-\begin{equation}
-\ln(\phi_{om})=N_{t}\ln(2)+\ln(det(\mathbf{W}))-\sum_{i=1}^{N_{t}}\ln(2||\mathbf{h}_{i}||^{2}),
-\label{formula4}
-\end{equation}
-$\phi_{om}$ in (\ref{formula3}) is defined as Orthogonality Measure.
-Based on Hadamard's inequality ($\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||\geq det(\mathbf{H})$).
-$\phi_{om}\in [0,1]$.
-If $\phi_{om}$ is more closer to 1, $\mathbf{H}$ is closer to orthogonal matrix.
-
-Because $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$, do QR factorization to $\mathbf{H}$ 
-\begin{equation}
-\mathbf{H}=\mathbf{Q}\mathbf{R},
-\label{formula5} 
- \end{equation}
-where $\mathbf{Q}\in\mathbb{C}^{N_{r}\times N_{t}}$ is a unitary matrix and $\mathbf{R}\in\mathbb{C}^{N_{t}\times N_{t}}$ is the upper triangular matrix.
-Using (\ref{formula5}), we have $\mathbf{W}=\mathbf{R}^{H}\mathbf{R}$.
-$r_{ii}$ denotes the $i$ th diagonal component of $\mathbf{R}$, thus $det(\mathbf{W})$ can be rewritten as:
-\begin{equation}
-det(\mathbf{W})=det(\mathbf{R}^{H}\mathbf{R})=det(\mathbf{R}^{H})det(\mathbf{R})\\=\prod_{i=1}^{N_{t}}r_{ii}^{H}\prod_{i=1}^{N_{t}}r_{ii}=\prod_{i=1}^{N_{t}}|r_{ii}|^{2}.
-\label{formula6}
-\end{equation}  
-Notice that $\mathbf{R}$ can be viewed as the Cholesky factorization of $\mathbf{W}$. Therefore, we have
-\begin{equation}
- ||\mathbf{h}_{i}||^{2}=\mathbf{W}_{ii}=\sum^{i-1}_{j=1}|r_{ji}|^{2}+|r_{ii}|^{2},
-\label{formula7}
- \end{equation}
- where $\mathbf{W}_{ii}$ denotes the $i$ th diagonal element of $\mathbf{W}$.
- Thus based on (\ref{formula6}) and (\ref{formula7}), (\ref{formula3}) can be rewritten as:
-\begin{equation}
-\phi_{om}=\prod_{i=1}^{N_{t}}\frac{|r_{ii}|^{2}}{|r_{ii}|^{2}+\sum^{i-1}_{j=1}|r_{ji}|^{2}}.
-\label{formula9}
-\end{equation}  
+
 \section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
@@
 
-From the rationale of risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
+From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
 Assume the data samples are i.i.d.
@@
 \nonumber
-maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=\prod_{i=1}^{l}P(\xi_{i})\\
-&=\prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),
+maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=maximize\quad \prod_{i=1}^{l}P(\xi_{i})\\
+&=maximize\quad \prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),
 \label{risk function1}
@@
 \end{eqnarray}
+Thus the equivalent formula of (12) can be written as 
+\begin{equation}
+minimize\quad  \sum_{i=1}^{l}c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i})),
+\label{Total risk function}
+\end{equation} 
 In $\epsilon$-SVR, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{risk function3}).
@@
 \end{equation}
-where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the cost function with regularization term can written as
+where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as
 \begin{equation}
@@
 \end{eqnarray}
-where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, (\ref{lagrange duality1}) is equivalent to
+where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, the dual problem of (\ref{lagrange duality1}) can be formulated as
 \begin{eqnarray}
@@
 \end{eqnarray}
+Karush–Kuhn–Tucker (KKT) condition is satisfied or not \cite{} determines whether a non linear optimization problem find its optimal solution, the complementary KKT solution of (\ref{lagrange duality2}) is
+\begin{IEEEeqnarray}[\relax]{l}
+\left\{\begin{array}{ll}
+\eta_{i}\xi_{i}=0\\
+\hat{\eta}_{i}\hat{\xi}_{i}=0\\
+\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))=0\\
+\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))=0\\
+\end{array}\right.
+\label{complementary KKT condition}
+\end{IEEEeqnarray}
+
 Take the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$, and find the minimum.
@@
 +\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
+\nonumber
 &-&\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
-\nonumber
-s.t.\left\{\begin{array}{l}
+&s.t.&\left\{\begin{array}{l}
 \sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
-0<\alpha<C\tilde{R}(\alpha)\\
-0<\hat{\alpha}<C\tilde{R}(\hat{\alpha})\\
+0<\alpha<C\tilde{R}^{'}(\alpha)\\
+0<\hat{\alpha}<C\tilde{R}^{'}(\hat{\alpha})\\
 \end{array}\right.
@@
 (\ref{dual optimization function2}) can be reformulate as 
-\begin{equation}
-maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{array}{ll}
-\mathbf{K}\quad -\mathbf{K}\\
--\mathbf{K}\quad \mathbf{K}\\
-\end{array}\right]\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
+\newcommand{\mysmallarraydecl}{\renewcommand{%
+\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
+\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
+\renewcommand{\baselinestretch}{1.1}%
+\settowidth{\normalbaselineskip}{\scriptsize
+\hspace{\baselinestretch\baselineskip}}%
+\setlength{\baselineskip}{\normalbaselineskip}%
+\setlength{\jot}{0.25\normalbaselineskip}%
+\setlength{\arraycolsep}{2pt}}
+\begin{equation}
+maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\mathbf{K}& -\mathbf{K}\\
+-\mathbf{K}& \mathbf{K}
+\end{IEEEeqnarraybox*}\right]
+\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
 \label{vectorize dual optimization function}
@@
 In this regression problem, receive symbol $y$ is the output data, $\mathbf{h}$ is input data sample, transmitted symbol vector $s$ is regression coefficients.
-Because the large MIMO system we consider here is complex, we employ complex support vector regression (CSVR).
-As shown in section (\ref{Introduce epsilon SVR}), in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to real cost functions which are defined in complex domain.
-The recent mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS)[\cite{wirtinger's calculus}] is employed to solve this problem.
-First we generalize our regression model by complex Hilbert space,
-Let $<>_{H}$ denotes inner product operation in real Hilbert space. $<,>_{\mathbb{H}}$ denotes inner products operation in complex Hilbert space, which has the following properties 
+Because the large MIMO system we consider here is complex, we employ complex support vector regression (CSVR) without offset term $b$.
+As shown in section \ref{Introduce epsilon SVR}, in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to real cost functions which are defined in complex domain.
+The recent mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS)[\cite{wirtinger's calculus}][\cite {reproducing Kernel Hilbert Space}] is employed to solve this problem.
+First we generalize our regression model by complex RKHS,
+Let $<,>_{H}$ denotes inner product operation in real RKHS.
+$<,>_{\mathbb{H}}$ denotes inner products operation in complex RKHS.
+Assume $\mathbf{x}$, $\mathbf{y}$, $\mathbf{z}$, $j$, $k$ $\in \mathbb{C}$, complex Hilbert space has the following properties
 \newtheorem{Lemma}{Lemma}
@@
 \begin{Property}
-\label{Property1}
+ $<\mathbf{x},\mathbf{y}>_{\mathbb{H}}=<\overline{\mathbf{y},\mathbf{x}}>_{\mathbb{H}}$
+\label{CHSProperty1}
 \end{Property}
+
+\begin{Property}
+$<j\mathbf{x}+k\mathbf{y},\mathbf{z}>_{\mathbb{H}}=j<\mathbf{x},\mathbf{z}>_{\mathbb{H}}+k<\mathbf{y},\mathbf{z}>_{\mathbb{H}}$
+\label{CHSProperty2}
+\end{Property}
+
+\begin{Property}
+$<\mathbf{z}, j\mathbf{x}+k\mathbf{y}>=\bar{j}<\mathbf{z},\mathbf{x}>_{\mathbb{H}}+\bar{k}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}}$
+\label{CHSProperty3}
+\end{Property}
+
 \begin{Lemma}
-$\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{H}>_{\mathbb{H}}$
+$\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{*}>_{\mathbb{H}}$
 \end{Lemma}
@@
 \begin{proof}
-
-Assume $\mathbf{a}$, $\mathbf{b}$ are real vectors,$\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{v}$, $\mathbf{x}$, $\mathbf{y}$ are complex vectors,$\mathbf{x}$, $\mathbf{x}$ $\in \mathbb{C}^{v}$, according to the properties of complex Hilbert space, is can be easily proved
-\begin{equation}
-\mathbf{a}^{T}\mathbf{b} \in <\mathbf{a}, \mathbf{b}>_{H}
-\end{equation}
+Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{v}$, it can be easily proved  
+\begin{equation}
+\mathbf{a}^{T}\mathbf{b} \in <\mathbf{a}, \mathbf{b}>_{H},
+\label{CHSequation1}
+\end{equation}
+ From Property \ref{CHSProperty1} and Property \ref{CHSProperty3}, it is obvious 
+\begin{equation}
+<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\mathbf{g}^{r},\mathbf{h}^{r}>_{H}+<\mathbf{g}^{i},\mathbf{h}^{i}>_{H}+i(<\mathbf{g}^{i},\mathbf{h}^{r}>_{H}-<\mathbf{g}^{r},\mathbf{h}^{i}>_{H})
+\label{CHSProperty4}
+\end{equation}
+where $\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{v}$, and $\mathbf{g}=\mathbf{g}^{r}+i\mathbf{g}^{i}$, $\mathbf{h}=\mathbf{h}^{r}+i\mathbf{h}^{i}$. Therefore, 
+\begin{eqnarray}
+\nonumber
+<\mathbf{h}, \mathbf{s}^{*}>_{\mathbb{H}}&=&<\mathbf{h}^{r},  (\mathbf{s}^{*})^{r}>_{H}+<\mathbf{h}^{i},  (\mathbf{s}^{*})^{i}>_{H}+i(<\mathbf{h}^{i},  (\mathbf{s}^{*})^{r}>_{H}-<\mathbf{h}^{r},  (\mathbf{s}^{*})^{i}>_{H})\\
+&=&<\mathbf{h}^{r}, \mathbf{s}^{r}>_{H}-<\mathbf{h}^{i}, \mathbf{s}^{i}>_{H}+i(<\mathbf{h}^{i}, \mathbf{s}^{r}>_{H}+<\mathbf{h}^{r}, \mathbf{s}^{i}>_{H}),
+\label{CHSequation2}
+\end{eqnarray}
+
+\begin{equation}
+\mathbf{h}\mathbf{s}=\mathbf{h}^{r}\mathbf{s}^{r}-\mathbf{h}^{i}\mathbf{s}^{i}+i(\mathbf{h}^{i}\mathbf{s}^{r}+\mathbf{h}^{r}\mathbf{s}^{i}),
+\label{CHSequation3}
+\end{equation}
+Because of (\ref{CHSequation1}), (\ref{CHSequation2}) and (\ref{CHSequation3}), $\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{*}>_{\mathbb{H}}$
 \end{proof}
-
-Taking expectation of (\ref{formula4}), we have 
-\begin{equation}
-\mathbb{E}[\ln(\phi_{om})]=N_{t}\ln(2)+\mathbb{E}[\ln(det(\mathbf{W}))]-\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(2||\mathbf{h}_{i}||^{2})].
-\label{formula11}
-\end{equation}
-Consider $\mathbf{H}=[\mathbf{h}_{1}^{'},\mathbf{h}_{2}^{'},\cdots \mathbf{h}_{N_{r}}^{'}]^{'}$, where $\mathbf{h}_{i}$ denotes the $i$ th row of $\mathbf{H}$, because each component of $\mathbf{H}$ is mutually independent and subject to circularly symmetric complex Gaussian distribution, i.e.
-$\mathbf{h}_{i}\sim \mathbb{C}N(\mathbf{0},\mathbf{I}_{N_{t}})$.
-Therefore, $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}\sim \mathbb{C}W(N_{r}, \mathbf{I}_{N_{t}})$, $\mathbb{C}W(n,\mathbf{\Sigma})$ denotes complex Wishart distribution with $n$ degrees of freedom and covariance matrix $\mathbf{\Sigma}$.
-The logarithmic expectation of $\mathbf{W}$ can be rewritten as
-\begin{equation}
-\mathbb{E}[\ln(det(\mathbf{W}))]=\frac{\tilde{\Gamma}^{'}_{N_{t}}(N_{r})}{\tilde{\Gamma}_{N_{t}}(N_{r})}=\sum_{i=1}^{N_{t}}\psi(N_{r}-i+1),
-\label{formula12}
-\end{equation}
-where $\tilde{\Gamma}_{m}(n)$ denotes the multivariate Gamma function and $\psi(n)$ denotes Digamma function. Proof: see Appendix A.
-
-Because the logarithmic expectation of a Gamma distribution variable $\mathbb{g}\sim Gamma(n,\theta)$ can be written as:
-\begin{equation}
-\mathbb{E}[\ln(\mathbb{g})]=\psi(n)+\ln(\theta),
-\end{equation}
-where $\psi(n)$ denotes Digamma function. Thus according to (\ref{formula2}), we have:
-\begin{equation}
-\mathbb{E}[\ln(2||\mathbf{h}_{i}||^{2})]=\psi(N_{r})+\ln(2).
-\label{formula14}
-\end{equation}
-Proof: see Appendix B.
-
-Based on (\ref{formula11})(\ref{formula12})(\ref{formula14}), The logarithmic expectation of $\phi_{om}$ can be written as:
-\begin{eqnarray}
-\nonumber
-\mathbb{E}[\ln(\phi_{om})]&=&N_{t}\ln(2)+\sum_{i=1}^{N_{t}}\psi(N_{r}-i+1)-N_{t}\psi(N_{r})-N_{t}\ln(2)\\
-&=& \sum_{i=1}^{N_{t}}\psi(N_{r}-i+1)-N_{t}\psi(N_{r})
-\label{formula15}
-\end{eqnarray}
-\section{Work Set Selection}\label{WSS}
+represent $\mathbf{s}^{*}$ by $\mathbf{w}$, The general regularized risk function of large MIMO detection in complex RKHS can be formulated:
+\begin{eqnarray}
+\nonumber
+minimize \quad \frac{1}{2}||w||_{\mathbb{H}}^{2}+C\sum_{k=1}^{N_{r}}[(R(\xi^{r}_{k})+R(\hat{\xi}^{r}_{k})+R(\xi^{i}_{k})+R(\hat{\xi}^{i}_{k}))]\\
+s.t. \left\{\begin{array}{ll}
+Re(y_{k}-<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})\leq \epsilon+\xi^{r}_{k}\\
+Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}-y_{k})\leq \epsilon+\hat{\xi}^{r}_{k}\\
+Im(y_{k}-<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})\leq \epsilon+\xi^{i}_{k}\\
+Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}-y_{k})\leq \epsilon+\hat{\xi}^{i}_{k}\\
+\xi^{r}, \hat{\xi}^{r},\xi^{i},\hat{\xi}^{i}\geq 0\\
+\end{array}\right.
+\label{complex objective function1}
+\end{eqnarray}
+where $Re()$ and $Im()$ denote real part and imaginary part of a complex variable, restrictions are set to real and imaginary part of regression function separately.
+Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denotes the kernel function, $\mathbf{K}=\mathbf{K}^{r}+i\mathbf{K}^{i}$, $\mathbf{K}^{r}$ and $\mathbf{K}^{i}$ denote matrix of corresponding real part and imaginary part.
+Similar to the Lagrange duality rational in (\ref{lagrange duality2}), Lagrange duality is formulated for (\ref{complex objective function1})
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{(\alpha, \hat{\alpha}, \beta, \hat{\beta}, \eta, \hat{\eta}, \tau, \hat{\tau})} \min_{(\mathbf{w}, \xi^{r}, \hat{\xi}^{r}, \hat{\xi}^{i}, \hat{\xi}^{i})} \theta =
+\frac{1}{2}||w||_{\mathbb{H}}^{2}+C\sum_{k=1}^{N_{r}}[(R(\xi^{r}_{k})+R(\hat{\xi}^{r}_{k})+R(\xi^{i}_{k})+R(\hat{\xi}^{i}_{k}))]- \sum_{k=1}^{N_{r}}(\eta_{i}\xi^{r}_{k}+\hat{\eta}_{k}\hat{\xi}^{r}_{k}\\
+\nonumber
++\tau_{k}\xi^{i}_{k}+\hat{\tau}_{k}\hat{\xi}^{i}_{k})-\sum_{k=1}^{N_{r}}\alpha_{k}(\epsilon+\xi^{r}_{k}-Re(y_{k})+Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))
+-\sum_{k=1}^{N_{r}}\hat{\alpha}_{k}(\epsilon+\hat{\xi}^{r}_{k}+Re(y_{k})-Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))\\
+\nonumber
+-\sum_{k=1}^{N_{r}}\beta_{k}(\epsilon+\xi^{i}_{k}-Im(y_{k})+Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))-\sum_{k=1}^{N_{r}}\hat{\beta}_{k}(\epsilon+\hat{\xi}^{i}_{k}+Im(y_{k})-Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))\\
+s.t. \left\{\begin{array}{ll}
+\eta, \hat{\eta}, \tau, \hat{\tau} \alpha, \hat{\alpha}, \beta, \hat{\beta}\geq 0\\
+\xi^{r}, \hat{\xi}^{r}, \xi^{i}, \hat{\xi}^{i} \geq  0
+\end{array}\right. 
+\label{complex lagrange duality1}
+\end{IEEEeqnarray}
+with Wirtinger's calculus applied to RKHS described in \cite{wirtinger's calculus to RKHS}, The partial derivatives of $\Theta$ respect to $\mathbf{w}$, which is define at complex domain, as well as the real variables $\xi^{r}$, $\hat{\xi}^{r}$, $\xi^{i}$ and $\hat{\xi}^{i}$ can be deduced
+\begin{IEEEeqnarray}[\relax]{l}
+\left\{\begin{array}{ll}
+\frac{\partial \Theta}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{k=1}^{N_{r}}\alpha_{k}\mathbf{h}_{k}+\frac{1}{2}\sum_{k=1}^{N_{r}}\hat{\alpha}_{k}\mathbf{h}_{k}+\frac{i}{2}(\sum_{k=1}^{N_{r}}\beta_{k}\mathbf{h}_{k}-\sum_{k=1}^{N_{r}}\hat{\beta}_{k}\mathbf{h}_{k})=0\\
+\Rightarrow \mathbf{w}=\sum_{k=1}^{N_{r}}(\alpha_{k}-\hat{\alpha}_{k})\mathbf{h}_{k}-i\sum_{k=1}^{N_{r}}(\beta_{k}-\hat{\beta}_{k})\mathbf{h}_{k}\\
+\frac{\partial \Theta}{\partial \xi^{r}_{k}}=CR^{'}(\xi^{r}_{k})-\eta_{k}-\alpha_{k}=0\Rightarrow \eta_{k}=CR^{'}(\xi^{r}_{k})-\alpha_{k}\\
+\frac{\partial \Theta}{\partial \hat{\xi}^{r}_{k}}=CR^{'}(\hat{\xi}^{r}_{k})-\hat{\eta}_{k}-\hat{\alpha}_{k}=0\Rightarrow \hat{\eta}_{k}=CR^{'}(\hat{\xi}^{r}_{k})-\hat{\alpha}_{k}\\
+\frac{\partial \Theta}{\partial \xi^{i}_{k}}=CR^{'}(\xi^{i}_{k})-\tau_{k}-\beta_{k}=0\Rightarrow \tau_{k}=CR^{'}(\xi^{i}_{k})-\beta_{k}\\
+\frac{\partial \Theta}{\partial \hat{\xi}^{i}_{k}}=CR^{'}(\hat{\xi}^{i}_{k})-\hat{\eta}_{k}-\hat{\beta}_{k}=0\Rightarrow \hat{\eta}_{k}=CR^{'}(\hat{\xi}^{i}_{k})-\hat{\beta}_{k}\\
+
+\end{array}\right.
+\label{complex lagrange duality2}
+\end{IEEEeqnarray}
+Based on (\ref{complex lagrange duality2}), we have 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}\\
+\nonumber
+=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
+=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}+i(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}),
+\label{complex duality regression function}
+\end{IEEEeqnarray}
+
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
++i(\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}-\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}\mathbf{h}^{H}_{i})
+\label{complex duality regularization1}
+\end{IEEEeqnarray}
+Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$, if we have $r_{i}$ and $r_{j}$ $\in \mathbb{R}$, 
+\begin{equation}
+\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij}=-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ji}=-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij},
+\end{equation}
+Therefore
+\begin{equation}
+\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij}=0,
+\label{conjugate1}
+\end{equation}
+Based on (\ref{conjugate1}), (\ref{complex duality regularization1}) can be changed to
+\begin{equation}
+||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{K}^{r}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{K}^{r}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta-\hat{\beta}_{i})\mathbf{K}^{i}_{ij}.
+\label{complex duality regularization2}
+\end{equation}
+Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), the final form of Lagrange duality can be obtained
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize\quad \Theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
+\nonumber
+-\sum_{i}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta+\hat{\beta}_{i})\epsilon+[\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})]\\
+\nonumber
++C\sum_{i}^{N_{r}}(\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i}))\\ 
+\left\{\begin{array}{ll}
+0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
+0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
+\xi^{r}(\hat{\xi}^{r})\geq 0\\
+\xi^{i}(\hat{\xi}^{i})\geq 0\\
+\end{array}\right.
+\label{final complex lagrange duality}
+\end{IEEEeqnarray}
+which can be divided into 2 independent regression task,
+
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize \quad \Theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
+\nonumber
++\tilde{R}(\hat{\xi}^{r}_{i}))\\
+\left\{\begin{array}{ll}
+0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
+\xi^{r}(\hat{\xi}^{r})\geq 0\\
+\end{array}\right.
+\label{complex duality real part}
+\end{IEEEeqnarray}
+
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize \quad \Theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
+\nonumber
++\tilde{R}(\hat{\xi}^{i}_{i}))\\
+\left\{\begin{array}{ll}
+0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
+\xi^{i}(\hat{\xi}^{i})\geq 0\\
+\end{array}\right.
+\label{complex duality imaginary part}
+\end{IEEEeqnarray}
+
+The alternate form can be written as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize \quad \Theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})-\tilde{R}(\hat{\xi}^{r})))\\
+\left\{\begin{array}{ll}
+0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
+\xi^{r}(\hat{\xi}^{r})\geq 0\\
+\end{array}\right.
+\label{complex duality real part vectorizes}
+\end{IEEEeqnarray}
+
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})-\tilde{R}(\hat{\xi}^{i})))\\
+\left\{\begin{array}{ll}
+0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
+\xi^{i}(\hat{\xi}^{i})\geq 0\\
+\end{array}\right.
+\label{complex duality imaginary part vectorized}
+\end{IEEEeqnarray}
+where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components.
+\section{Work Set Selection and Solver}\label{WSS}
+(\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.
+Decomposition method is a set of efficient algorithms that can help to conquer this difficulty.
+Decomposition method works iteratively, the basic idea of decomposition method is to choose a subset of variable pairs $S$ (named work set) to optimize in each iteration step while keep the rest variable pairs $N$ fixed.
+Sequential Minimal Optimization (SMO) \cite{SMO} is an extreme case of decomposition method, the work set size is 2, an analytic quadratic programming (QP) step instead of numerical QP step can be taken in each iteration.
+
+Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) are symmetric, in this section we discuss real part only.
+By dividing the variables into work set $S$ and fixed set $N$, (\ref{complex duality real part vectorizes}) can be changed to:
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}+2(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}(\alpha-\hat{\alpha})_{S}]
++Re(\mathbf{y})_{S}^{T}(\alpha-\hat{\alpha})_{S}-\\
+\nonumber
+\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{S})
+-\frac{1}{2}(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NN}^{r}(\alpha-\hat{\alpha})_{N}+Re(\mathbf{y})_{N}^{T}(\alpha-\hat{\alpha})_{N}-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{N})\\+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})-\tilde{R}(\hat{\xi}^{r}))),
+\label{real part decomposition}
+\end{IEEEeqnarray}
+Where $\mathbf{K}^{r}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\mathbf{K}^{r}_{SS}& -\mathbf{K}^{r}_{SN}\\
+-\mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
+\end{IEEEeqnarraybox*}\right]$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$
+and  $\alpha_{S}\in \mathbb{R}^{N_{r}}$ denotes the vector with the components that do not belong to $S$ zeroed. Therefore the sub-optimization problem is formulated as 
+\begin{equation}
+maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]-[(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
++Re(\mathbf{y})_{S}^{T}](\alpha-\hat{\alpha})_{S}-\epsilon[\mathbf{e}_{S}^{T}(\alpha+\hat{\alpha})_{S}],
+\label{subset optimization}
+\end{equation}
+In decomposition method, a proper work set selection strategy is required so that acceptable speed and performance can be guaranteed.
+One approach is to choose dual variable pairs that violate KKT conditions, so that after each iteration, the objective function can be increased according to Osuna's theorem\cite{inproved training algorithms for support vector machines}, Heuristic methods are used in [\cite{SMO}] in order to accelerate process, in work set selection process, the algorithm first searches among the non-bound variables (that is $0<\alpha<C\tilde{R}(\xi)$), which are more likely to violate KKT condition, then searching the whole dual variable set, the second dual variable that can maximize optimization step of the first coordinate is chosen, approximate step size is used as evaluator for sake of reducing computational cost.
+Lin propose another work set selection strategy based on an alternative form of KKT condition.
+
+Another class of approaches is to choose the dual variables whose update can provide the maximum improvements to objective function \cite{}, \cite{}, \cite{}(Training without offset). That is 
+\begin{equation}
+maximize\quad \bigtriangledown \Theta_{S}=\Theta((\alpha+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta(\alpha, \hat{\alpha}),
+\label{maximum gain work set selection}
+\end{equation} 
+where $\delta_{S}=\alpha_{S}^{new}-\alpha_{S}$
+In our regression model, the offset is omitted, therefore different from SMO algorithm, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration.
+However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{Training without offset}.
+Here we propose sequential 1-D work set selection, which can approximate the effect of optimal 2-D work set selection.
+There is only $O(n)$ searching times required for the former one while the later one need $O(n^{2})$ searching times.
 \subsection{Single Direction Solver}
+ We will first introduce 1-D work set selection strategy in which the dual variable pair that maximizes the gain of objective function is chosen.
+Recall the decomposition method in (\ref{maximum gain work set selection}), let $\alpha_{1}$ denotes the dual variable that is chosen to be updated.
+The sub optimization  problem is formulated as
+ \begin{IEEEeqnarray}[\relax]{l}
+ \nonumber
+ maximize\quad \Theta_{1}^{r}=-\frac{1}{2}((\alpha_{1}-\hat{\alpha}_{1})^{new})^{2}\mathbf{K}_{11}^{r}-(\alpha_{1}-\hat{\alpha}_{1})^{new}\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}(\alpha_{j}-\hat{\alpha}_{j})^{new}
++Re(y_{1})(\alpha_{1}-\hat{\alpha}_{1})^{new}\\
+-\epsilon(\alpha_{1}+\hat{\alpha}_{1})^{new},
+ \label{optimization function 1-D}
+ \end{IEEEeqnarray}
+take the partial derivative of $\Theta_{1}^{r}$ respect to $\alpha_{1}$ and $\hat{\alpha}_{1}$, we have 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\frac{\partial \Theta_{1}^{r}}{\partial \alpha_{1}}=-(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}_{11}^{r}-\sum_{j=2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})^{new}\mathbf{K}_{1j}^{r}+Re(y_{1})-\epsilon=0\\
+\Rightarrow \alpha_{1}^{new}=\alpha_{1}+\frac{\Phi_{1}^{r}-\epsilon}{\mathbf{K}_{11}^{r}},
+\label{partial optimization function 1-D alpha}
+\end{IEEEeqnarray}
+
+ \begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\frac{\partial \Theta_{1}^{r}}{\partial \hat{\alpha}_{1}}=(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}_{11}^{r}+\sum_{j=2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})^{new}\mathbf{K}_{1j}^{r}-Re(y_{1})-\epsilon=0\\
+\Rightarrow \hat{\alpha}_{1}^{new}=\hat{\alpha}_{1}-\frac{\Phi_{1}^{r}+\epsilon}{\mathbf{K}_{11}^{r}}\\
+\label{partial optimization function 1-D alpha hat}
+\end{IEEEeqnarray} 
+where we define $\Phi_{i}^{r}=Re(y_{i})-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}_{ij}^{r}$, similarly, as to dual variable  $\beta$ and $\hat{\beta}$, we define $\Phi_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}_{ij}^{r}$.
+Recall complementary KKT condition
+\begin{IEEEeqnarray}[\relax]{l}
+\left\{\begin{array}{ll}
+(C\tilde{R}(\xi^{r})-\alpha)\xi^{r}=0\\
+(C\tilde{R}(\hat{\xi}^{r})-\hat{\alpha})\hat{\xi}^{r}=0\\
+\alpha(\epsilon+\xi^{r}-Re(y)+<\mathbf{h},\mathbf{w}>_{\mathbb{H}})=0\\
+\hat{\alpha}(\epsilon+\hat{\xi}^{r}+Re(y)-<\mathbf{h},\mathbf{w}>_{\mathbb{H}})=0\\
+\end{array}\right.
+\label{complementary KKT condition}
+\end{IEEEeqnarray}
+it can be easily observed that $\alpha\hat{\alpha}=0$, because $0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(C\tilde{R}(\hat{\xi}^{r}))$,  $\xi^{r}$ and $\hat{\xi}^{r}$ satisfy $\xi^{r}\hat{\xi}^{r}$.
+The update of $\alpha_{1}$ or $\hat{\alpha}_{1}$ is completed by clipping
+\begin{IEEEeqnarray}[\relax]{l}
+\alpha^{new\quad clipped}=[\alpha^{new}]_{0}^{C\tilde{R}(\xi^{r})}\\
+\hat{\alpha}^{new\quad clipped}=[\hat{\alpha}^{new}]_{0}^{C\tilde{R}(\hat{\xi}^{r})}\\
+\label{clipped new dual variable}
+\end{IEEEeqnarray}
+where $[ ]_{a}^{b}$ denotes to function 
+\begin{IEEEeqnarray}[\relax]{l}
+[x]_{a}^{b}=\left\{\begin{array}{ll}
+a \quad if\quad  x\leq a\\
+x \quad if\quad a<x<b\\
+b \quad if\quad x\geq b\\
+\end{array}\right.
+\label{clipping function}
+\end{IEEEeqnarray}
+Based on (\ref{partial optimization function 1-D alpha}), (\ref{partial optimization function 1-D alpha hat}) and (\ref{clipped new dual variable}), The gain of objective function respect to $i$th dual variable pair is
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \Theta_{i}^{r}=\Theta^{r}((\alpha+\delta_{i}\mathbf{e}_{i}), (\hat{\alpha}+\hat{\delta}_{i}\mathbf{e}_{i}))-\Theta^{r}(\alpha, \hat{\alpha})\\
+\nonumber
+=-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})^{2}\mathbf{K}_{ii}^{r}-(\delta_{i}-\hat{\delta}_{i})\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}_{ij}^{r}+Re(y_{i})(\delta_{i}-\hat{\delta}_{i})-\epsilon(\delta_{i}+\hat{\delta}_{i})\\
+=(\delta_{i}-\hat{\delta}_{i})[-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})\mathbf{K}_{ii}^{r}+\Phi_{i}^{r}-\epsilon\frac{\delta_{i}+\hat{\delta}_{i}}{\delta_{i}-\hat{\delta}_{i}}],
+\label{gain of objective function}
+\end{IEEEeqnarray}
+where $\delta_{1}=\alpha^{new\quad clipped}_{1}-\alpha_{1}$, $\hat{\delta}_{1}=\hat{\alpha}^{new\quad clipped}_{1}-\hat{\alpha}_{1}$, in 1-D searching procedure, the dual variable pair which has the maximum gain of objective function is chosen as $1$ in (\ref{optimization function 1-D}), that is
+\begin{equation}
+1=arg_{(i=1,\ldots, N_{r})}\max \bigtriangledown \Theta_{i}^{r},
+\label{1-D direction}
+\end{equation}
 \subsection{Double Direction Solver}
+
 \subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}
@@
 %\end{spacing}
+\newpage
 \bibliographystyle{IEEEtran}

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/Initialization.h

@@ -1,43 +1,0 @@
-/*
- * Initialization.h
- *
- *  Created on: Aug 3, 2015
- *      Author: tianpei.chen@mail.mcgill.ca
- *      Initialization of SVR
- *      INPUT: alpha, alpha_hat, beta, beta_hat, preceived, method
- *      OUTPUT: phi, S_C_real, S_C_imag
- */
-#include "common.h"
-#ifndef INITIALIZATION_H_
-#define INITIALIZATION_H_
-int Initialization(gsl_vector *alpha,//Lagrange multiplier
-		gsl_vector *alpha_hat,//Lagrange multiplier
-		gsl_vector *beta,//Lagrange multiplier
-		gsl_vector *beta_hat,//Lagrange multiplier
-		gsl_vector_complex *preceived,//received symbol vector(output of trainning data set)
-		gsl_vector_complex *phi, // update parameter
-		double S_C_real, //real stopping parameter
-		double S_C_imag,  //imaginary stopping parameter
-		int method //label which start strategy is used
-		){
-//	int method=0; //label of method
-    int count1,count2;
-    gsl_complex temp;
-    GSL_SET_COMPLEX(&temp, 0, 0);
-//cold start (L0-W0)
-for(count1=0;count1<Nr,count1++){
-temp=gsl_vector_complex_get(preceived, count1);
-gsl_vector_complex_set(phi, count1, temp);
-S_C_real=0;
-S_C_imag=0;  //need to consider what is stopping criteria of this SVR
-}
-
-method=1;
-
-	return method;
-}
-
-
-
-
-#endif /* INITIALIZATION_H_ */

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/SVR_DETECTOR.h

@@ -1,139 +1,0 @@
-/*
- * SVR_DETECTOR.h
- *
- *  Created on: Jul 15, 2015
- *      Author: tianpei.chen@mail.mcgill.ca
- */
-
-#ifndef SVR_DETECTOR_H_
-#define SVR_DETECTOR_H_
-#include "common.h"
-/*
- *  Parameters configuration
- */
-//#define  C  1e-3;      //Penalize weight for noise
-//#define epsilon 1e-3; //Training precision
-typedef struct{
-	gsl_complex data;
-	int index;
-
-}Nalpha_Node;
-/*
- * inner function
- */
-int TestData(gsl_complex alpha, int index, gsl_vector_complex *Error, gsl_vector_complex *eta);
-int takestep(gsl_complex alpha, int index, gsl_vector_complex *Error, gsl_vector_complex *eta);
-Nalpha_Node checkNonbound(gsl_vector_complex *alpha);
-
-
-void SVR_DETECTOR(const gsl_vector_complex *preceived, const gsl_matrix_complex *pH, float SNRb, gsl_vector_complex *psymout, int start_M, int selection_M){
-//gsl_vector  *eta=gsl_vector_calloc(Nt); //the diagonal components of Wishart matrix
-//gsl_vector_complex *Error=gsl_vector_complex_calloc(Nr);  //the error e=y-hx
-int count1, count2, count3; //counters
-double S_pilot=0; //stoping criteria parameter
-gsl_vector *alpha=gsl_vector_calloc(2*Nr);
-//gsl_vector *alpha_hat=gsl_vector_calloc(Nr);
-gsl_vector *beta=gsl_vector_calloc(2*Nr);
-//gsl_vector *beta_hat=gsl_vector_calloc(Nr);  // Lagrange multipliers
-gsl_matrix_complex *K_complex=gsl_matrix_complex_calloc(Nr,Nr);
-gsl_blas_zherk(CblasUpper,CblasNoTrans, 1, pH,0, K_complex);  //calculate complex kernel matrix
-gsl_matrix *K=gsl_matrix_calloc(Nr,Nr);   //kernel matrix
-for(count1=0;count1<Nr;count1++){
-	for(count2=0;count2<=count1;count2++){
-		gsl_matrix_set(K,count1,count2,gsl_matrix_complex_get(K_complex,count1,count2).dat[0]);
-	}
-}   //get the real kernel
[…]

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/SVR_MIMO_communication_line.cpp

@@ -1,429 +1,0 @@
-//============================================================================
-// Name        : SVR_MIMO_communication_line.cpp
-// Author      : Tianpei Chen
-// Version     :
-// Copyright   : Your copyright notice
-// Description : This is the main routine for large MIMO communication line,
-// including random data generator, gray encoder, modulator, channel generator, noise generator
-// detector, symbol error and binary error accumulator, SER and BER calculator.
-//============================================================================
-#include <stdio.h>
-#include <stdlib.h>
-#include<string.h>
-#include <math.h>
-#include <gsl/gsl_rng.h>
-#include <time.h>
-#include <gsl/gsl_vector.h>
-#include <gsl/gsl_vector_ulong.h>
-#include <gsl/gsl_vector_int.h>
-#include <gsl/gsl_vector_complex.h>
-#include <gsl/gsl_complex.h>
-#include <gsl/gsl_complex_math.h>
-/*#include <gsl/gsl_matrix.h>*/
-#include <gsl/gsl_matrix_complex_float.h>
-#include <gsl/gsl_randist.h>
-/*#include <gsl/gsl_cblas.h>*/
-#include <gsl/gsl_blas.h>
-#include <gsl/gsl_linalg.h>
-#include <gsl/gsl_combination.h>
-#include <gsl/gsl_eigen.h>
-#include<gsl/gsl_math.h>
-#include<gsl/gsl_sort.h>
-#include<gsl/gsl_sort_vector.h>
-//#include<cuda_runtime.h>
-#include<assert.h>
-#include<time.h>
-#include"channel_generator.h"
-#include"grayencoder.h"
-#include"symbolconstellation.h"
-//   cudaMemset(Eu_mini,0,sizeof(float));
-#include"modulator.h"
-#include"noise_generator.h"
-//#include"chol.cuh"
-#include"data_generator.h"
-#include"demodulator.h"
-#include"binaryerrors.h"
-#include"FCSD_detection_CPU.h"
-//#include"complex.h"
-//#include"chol.cuh"
-//#include"cu_complex_operation.cuh"
-//#include "helper_functions.h"
-//#include"chol_common.h"
-#include<time.h>
-//#include<cublas_v2.h>
-//#include<cuComplex.h>
-//#include<cuda_runtime.h>
[…]

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/WSS2_1Dsolver.h

@@ -1,73 +1,0 @@
-/*
- * WSS2_1Dsolver.h
- *
- *  Created on: Aug 4, 2015
- *      Author: tianpei.chen@mail.mcgill.ca
- *      This is 2D selection subroutine based on maximum 2 1D direction
- *      subroutine, choose the two Lagrange multipliers with maximum 1D gain
- *      to perform 2D solver.
- *      INPUT: alpha(beta), alpha_hat(beta_hat), label1, label2, phi, R_Kernel
- *      OUTPUT: First, Second
- */
-#include "common.h"
-#ifndef WSS2_1DSOLVER_H_
-#define WSS2_1DSOLVER_H_
-void 	WSS2_1Dsolver(gsl_vector *l_m,  //Lagrange Multiplier vector
-        gsl_vector_complex *phi,  //update parameter
-        gsl_matrix *R_Kernel,    //real kernel matrix
-        int F_i,  //index of first maximum Lagrange multiplier
-        int S_i //index of second maximum Lagrange multiplier
-){
-double best_g, g;
-double sigma, sigma_hat;
-double temp_l_m, temp_l_m_hat;
-int count;
-double phi_p[2*Nr];
-for(count=0;count<2*Nr;count++){  //take real and imaginary part of phi
-	if(count<Nr){
-  phi_p[count]=gsl_vector_complex_get(phi,count).dat[0];
-	}else{
-		phi_p[count]=gsl_vector_complex_get(phi,count-Nr).dat[1];
-	}
-}
-best_g=-1;
-F_i=S_i=-1;
-for(count=0;count<2*Nr;count++){
-	if(count<Nr){
-		temp_l_m=gsl_vector_get(l_m, count)+(phi_p[count]-epsilon)/
-				(gsl_matrix_get(R_Kernel, count,count));
-		if(temp_l_m<0){
-			temp_l_m=0;
-		}else if (temp_l_m>C){
-			temp_l_m=C;
-		}
-		sigma=temp_l_m-gsl_vector_get(l_m,count);
-		sigma_hat=0;
-	}else{
-		temp_l_m_hat=gsl_vector_get(l_m, count)-(phi_p[count]+epsilon)/
-				(gsl_matrix_get(R_Kernel, count,count));
-		if(temp_l_m<0){
-			temp_l_m_hat=0;
[…]

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/binaryerrors.h

@@ -1,21 +1,0 @@
-unsigned long binaryerrors (unsigned long input, unsigned long output, unsigned long Q)
-{
-	unsigned long count=0UL, errors=0UL, temp=0UL, temp2=0UL;
-
-	int M=0;
-	M = (int) log2(static_cast<double>(Q));
-
-	temp = input^output;
-	errors = 0L;
-	for (count=0; count<M; count++)
-	  {
-		temp2 = temp%2;
-		temp = temp/2;
-		if (temp2 != 0)
-		 	errors = errors+1;
-
-	  } 
-	//printf ("\n input = %ld, \t output = %ld, \t errors = %ld", input, output, errors);
-
-	return errors;
-}

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/channel_generator.h

@@ -1,21 +1,0 @@
-void channel_generator (gsl_matrix_complex *pH, gsl_rng *pr)
-{
-	int Nt, Nr, count1=0, count2=0;
-	Nr=pH->size1;
-	Nt=pH->size2;
-	
-	gsl_complex z;
-	GSL_SET_COMPLEX (&z, 0.0, 0.0);
-
-	for (count1=0 ; count1<Nr ; count1++)
-	    {
-		for (count2=0; count2<Nt; count2++)
-		    { 
-			GSL_SET_COMPLEX (&z, gsl_ran_gaussian (pr, 1.0/sqrt(2.0)), gsl_ran_gaussian (pr, 1.0/sqrt(2.0)));
-			gsl_matrix_complex_set (pH, count1, count2, z);
-			//printf("z = %g \n", gsl_ran_gaussian (pr, 1.0));
-		     }
-	    }
-	return;
-		   
-}

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/checkNonbound.h

@@ -1,21 +1,0 @@
-/*
- * checkNonbound.h
- *
- *  Created on: Jul 16, 2015
- *      Author: tianpei.chen@mail.mcgill.ca
- */
-
-#ifndef CHECKNONBOUND_H_
-#define CHECKNONBOUND_H_
-#include "common.h"
-Nalpha_Node checkNonbound(gsl_vector_complex *alpha){
-//check the non bound alpha and store them in Nalpha
-Nalpha_Node *Nalpha=(Nalpha_Node*)malloc(Constellationsize);
-//  gsl_vector_complex *Nalpha=gsl_vector_complex_calloc(Constellationsize);
-  return Nalpha;
-}
-
-
-
-
-#endif /* CHECKNONBOUND_H_ */

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/constrcandidates.h

@@ -1,204 +1,0 @@
-void constrcandidates (gsl_complex sbabai, double bound, double d, int M, gsl_matrix *prings, gsl_matrix_int *pringsindexes, gsl_vector_int *pringsize, gsl_vector *pringradius, int numberofrings, gsl_vector_complex *psymbolconstellation, int maxcandidates, double alpha, gsl_complex rll, int *pfoundcandidates, gsl_vector_complex *pcandidates, gsl_vector_ulong *poutputcandidates, gsl_vector *pdistances, int *ptotalcandidates)
-{
-	int Q, count=0, ringsize=0, count2=0, numberofcandidates=0, temp=0, ii=0;
-	Q = psymbolconstellation -> size;
-
-	double Rc=0.0, Rest=0.0, Rcsq=0.0, Restsq=0.0, thetac=0.0, thetaest=0.0, Rllsq=0.0, alphasq=0.0, weight=0.0, bias=0.0, temp2=0.0, etha=0.0, Rmax=0.0, Rmaxsq=0.0;
-	Rest = gsl_complex_abs (sbabai);
-	Restsq = pow(Rest, 2.0);
-
-	thetaest = gsl_complex_arg (sbabai);
-
-	Rllsq = gsl_complex_abs2(rll);
-
-	alphasq = pow (alpha, 2.0);
-	Rmax = gsl_vector_get (pringradius, numberofrings-1);
-	Rmaxsq = pow (Rmax, 2.0);
-	//printf("Rmaxsq = %g \n", Rmaxsq);
-
-	//printf ("bound = %g \n", bound);
-	//printf ("sbabai = %g + (%g)i \n ", GSL_REAL(sbabai), GSL_IMAG(sbabai));
-
-	gsl_vector_complex *pcurrentcandidates;
-	pcurrentcandidates = gsl_vector_complex_calloc (Q);
-
-	gsl_vector_ulong *pcurrentoutputs;
-	pcurrentoutputs = gsl_vector_ulong_calloc (Q);
-	
-	gsl_vector *pclosest;
-	pclosest = gsl_vector_calloc (Q);
-	
-
-	gsl_complex z, candidate;
-		GSL_SET_COMPLEX (&z, 0.0, 0.0);
-		GSL_SET_COMPLEX (&candidate, 0.0, 0.0);
-	//z = gsl_vector_complex_get (psymbolconstellation, 0);
[…]

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/data_generator.h

@@ -1,13 +1,0 @@
-
-void data_generator(gsl_vector_ulong *pdata, gsl_rng *pr, unsigned long Q)
-{
-	int Nt;
-	Nt = pdata -> size;	
-	int count = 0;
-	for (count=0; count<Nt ; count++)
-	  {
-		gsl_vector_ulong_set(pdata, count, gsl_rng_uniform_int (pr,Q));	
-		/*printf ("\n data(%d)= %d \n", count, gsl_vector_ulong_get (pdata, count));*/	
-	  }
-	return;
-}

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/fullfactorial.h

@@ -1,68 +1,0 @@
-/* *
- * Copyright 1993-2012 NVIDIA Corporation.  All rights reserved.
- *
- * Please refer to the NVIDIA end user license agreement (EULA) associated
- * with this source code for terms and conditions that govern your use of
- * this software. Any use, reproduction, disclosure, or distribution of
- * this software and related documentation outside the terms of the EULA
- * is strictly prohibited.
- */
-/*
- * this fuction implement the full factorial design
- * 29/08/2014
- * Tianpei Chen
- */
-#include "common.h"
-#include<stdlib.h>
-#include <stdio.h>
-#include<string.h>
-#include<math.h>
-void fullfact(
-		int rho,  //the number of elements that use full expansion
-		int M,    //constellation size
-		int *s_sub_index    //the indexes of the full expansion matrix  (pow(M,rho))
-		)
-{
-	int ssize,ncycles,columns,nreps;
-	int count1,count2,count3,count4;
-	int *settings2,*settings1;
-	settings2=(int*)calloc(1,int(pow(M,rho))*sizeof(int));
-	ssize=int(pow(M,rho));
-	ncycles=ssize;
-	for(count1=0;count1<rho;count1++)
-	{
-//		memset(settings2,0,int(pow(M,rho))*sizeof(int));
-
-		nreps=int(ssize/ncycles);
-		ncycles=ncycles/M;
-		settings1=(int*)calloc(1,M*nreps*sizeof(int));
-		for(count2=0;count2<M;count2++)
-		{
-			for(count3=0;count3<nreps;count3++)
-			{
-				settings1[count2*nreps+count3]=count2;
-			}
-		}
-
-
-	for(count2=0;count2<ncycles;count2++)
-	{
-		for(count3=0;count3<M*nreps;count3++)
-		{
-			settings2[count2*M*nreps+count3]=settings1[count3];
-		}
-	}
-	for(count4=0;count4<pow(M,rho);count4++)
-	{
-	s_sub_index[IDC2D(count1,count4,int(pow(M,rho)))]=settings2[count4];
-	}
-
-    free(settings1);
-	}
-//	memset(settings2,0,int(pow(M,rho))*sizeof(int));
-	free(settings2);
-//	free(settings1);
-
-
-
-}

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/grayencoder.h

@@ -1,67 +1,0 @@
-void grayencoder (gsl_vector_ulong *pgraydata, gsl_vector_ulong *pgrayindexes, unsigned long Q)
-{
-	unsigned long count=0UL, value=0UL, count2=0UL, temp=0UL;
-
-	int M=0;
-	M = (int) ceil(sqrt(Q));
-
-	gsl_vector_ulong *ppamdata, *pQAMdata, *peqvdata;
-	ppamdata = gsl_vector_ulong_calloc (M);
-	pQAMdata = gsl_vector_ulong_calloc (Q);
-	peqvdata = gsl_vector_ulong_calloc (Q);
-if(Q==4)
-{
- for (count=0;count<Q;count++)
- {
-	 switch (count) {
-	 case 0:
-	 gsl_vector_ulong_set(pQAMdata,count,0); break;
-	 gsl_vector_ulong_set(peqvdata,0,count); break;
-	 case 1:
-		 gsl_vector_ulong_set(pQAMdata,count,1); break;
-		 gsl_vector_ulong_set(peqvdata,1,count); break;
-	 case 2:
-		 gsl_vector_ulong_set(pQAMdata,count,3); break;
-		 gsl_vector_ulong_set(peqvdata,3,count); break;
-	 case 3:
-		 gsl_vector_ulong_set(pQAMdata,count,2); break;
-		 gsl_vector_ulong_set(peqvdata,2,count); break;
-	 }
- }
-}
-else
-{
-	for (count=0; count<M; count++)
-	  {
-		value=count;
-		count2 = count;
-		count2 = count2 >> 1;
-		value = value^count2;
-		
-		gsl_vector_ulong_set (ppamdata, count, value);
-
-	  }
-
-	//vectorviewerint("ppamdata", ppamdata);
-	
-	for (count=0; count<Q; count++)
-	  {
-		value = M*gsl_vector_ulong_get(ppamdata, count/M) + gsl_vector_ulong_get (ppamdata, count%M);
-		gsl_vector_ulong_set (pQAMdata, count, value);
-		gsl_vector_ulong_set (peqvdata, value, count);   //the pdata is actually the index
-		//according to the gray code we can find its indexs according to the indexes we can find the gray code
-
-	  }
-}
-
-	//vectorviewerint ("pQAMdata", pQAMdata);
-	//vectorviewerint ("peqvdata", peqvdata);
[…]

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/please_delete.h

@@ -1,105 +1,0 @@
-/*
- * please_delete.h
- *
- *  Created on: Sep 29, 2014
- *      Author: tianpei.chen@mail.mcgill.ca
- */
-
-#ifndef PLEASE_DELETE_H_
-#define PLEASE_DELETE_H_
-
-//elements update
-__global__ void linearMge( cuComplex *matrix, int index, int lda) {
-//int ty = threadIdx.x;
-//int x = blockIdx.x;
-//int count1,count2;
-//int y = ty + x* blockDim.x;
-//cuComplex zero;
-//zero.x=0;
-//zero.y=0;
-////extern __shared__ cuComplex matrix[];
-////if(y==0){
-////for(count1=0; count1<2*column; count1++){
-////	for(count2=0; count2<column; count2++){
-////      matrix[IDC2D(count1,count2,lda)]=H[IDC2D(count1,count2,lda)];
-////	}
-////}
-////}
-////__shared__ cuComplex multColumn[ LINEAR_BLOCK_SIZE ];
-////__shared__ cuComplex matrixPivotValue;
-////__shared__ cuComplex matrixRow[ LINEAR_BLOCK_SIZE ];
-////__shared__ cuComplex resultPivotValue;
-////__shared__ cuComplex resultRow[ LINEAR_BLOCK_SIZE];
-////cuComplex newMatrixValue;
-//extern __shared__ cuComplex newResultValue[];
-////if(y==0){
-//// Each block loads the value of the pivot Row to be substracted
-//if(x!=index){
-//if ( ty == 0 ){
-////matrixPivotValue = matrix[ IDC2D( x, index, lda )];
-//
-//	newResultValue[x]=matrix[ IDC2D( index, x, lda )];
-//	matrix[ IDC2D( index, x, lda )]=zero;
-//
-//}
-////multColumn[ ty ] = matrix[ IDC2D( y, index, lda )];
-////matrixRow[ ty ] = matrix[ IDC2D( y, x, lda )];
-////resultRow[ ty ] = result[ IDC2D( y, x, lda )];
-//__syncthreads();
-//if ( ty<2*column-index-1 ) {
-//matrix[IDC2D(ty+index+1,x,lda)] = complex_sub(matrix[IDC2D(ty+index+1,x,lda)],complex_mulcom(matrix[IDC2D(ty+index+1,index,lda)],newResultValue[x]));
[…]

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line  original version/src/reordering.h

@@ -1,16 +1,0 @@
-/*
- * reordering.h
- *
- *  Created on: Sep 22, 2014
- *      Author: tianpei.chen@mail.mcgill.ca
- */
-#include<cuda_runtime.h>
-#include<cuda.h>
-#include<cuComplex.h>
-#ifndef REORDERING_H_
-#define REORDERING_H_
-
-
-
-
-#endif /* REORDERING_H_ */

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/Initialization.h

@@ -13,9 +13,15 @@
 int Initialization(gsl_vector *alpha,//Lagrange multiplier
 		gsl_vector *beta,//Lagrange multiplier
 		const gsl_vector_complex *preceived,//received symbol vector(output of trainning data set)
-		gsl_vector_complex *phi, // update parameter
-		double S_C_real, //real stopping parameter
-		double S_C_imag,  //imaginary stopping parameter
+		gsl_matrix *K_r, //real kernel matrix
+		gsl_matrix *K_i, //imaginary kernel matrix
+		gsl_vector_complex *phi, // intermediate parameter
+		gsl_vector_complex *eta, //intermediate parameter
+		double L_real, //L real stopping parameter
+		double L_imag,  //L imaginary stopping parameter
+		double S_real, //S real stopping parameter
+		double S_imag, //S imaginary stopping parameter
+		double S_total, //global stopping parameter
 		int method //label which start strategy is used
 		){
 //	int method=0; //label of method
@@ -24,12 +30,52 @@ int Initialization(gsl_vector *alpha,//Lagrange multiplier
     GSL_SET_COMPLEX(&temp, 0, 0);
 //cold start (L0-W0)
 if(method==1){
+//	gsl_vector *alpha_temp=gsl_vector_calloc(Nr);
+//	gsl_vector *beta_temp=gsl_vector_calloc(Nr);
+//	gsl_vector *alpha_temp_sum=gsl_vector_calloc(Nr);
+//	gsl_vector *beta_temp_sum=gsl_vector_calloc(Nr);
+//	double tempa=0;
+//	double tempb=0;
+//	double tempsa=0;
+//	double tempsb=0;
+//	for(count1=0;count1<Nr;count1++){
+//		tempa=gsl_vector_get(alpha,count1)-gsl_vector_get(alpha, count1+Nr);
+//		tempa=gsl_vector_get(alpha,count1)+gsl_vector_get(alpha, count1+Nr);
+//		tempb=gsl_vector_get(beta,count1)-gsl_vector_get(beta, count1+Nr);
+//		tempb=gsl_vector_get(beta,count1)+gsl_vector_get(beta, count1+Nr);
+//		gsl_vector_set(alpha_temp, count1, tempa);
+//		gsl_vector_set(beta_temp, count1, tempb);
[…]

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/SVR_MIMO_communication_line.cpp

@@ -64,7 +64,6 @@
 #define GFLOPS "GFLOPS.txt"          //the file to store the Giga flops operated per second
 #define miniteration 1e5               //the minimum number of channel realizations
 #define minSymbolError 300          //the minimum number of symbol error
-#define epsilon 1e-5               //the accuracy
 #define SNRnum 7                     //the point number of signal to noise ratio per bit
 void data_generator(gsl_vector_ulong *pdata, gsl_rng *pr, unsigned long Q);
 void grayencoder(gsl_vector_ulong *pgraydata, gsl_vector_ulong *pgrayindexes,

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/common.h

@@ -27,7 +27,7 @@
 #define IDC2D(i,j,row)    (i)*row+j
 #define Constellationsize 4
 #define  C  1e-3;      //Penalize weight for noise
-#define epsilon 1e-3; //Training precision
+#define epsilon 1e-5; //Training precision
 #define tol 1e-4   //the tolerance for KKT condition
 //void FCSD_detection(
 //		cuComplex *sigRec,   //received signal vector

### 2015-08-18 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/takestep.h

@@ -3,19 +3,56 @@
  *
  *  Created on: Jul 16, 2015
  *      Author: tianpei.chen@mail.mcgill.ca
+ *      this subroutine update 2 Lagrange variable pair sequentially
  */
 
 #ifndef TAKESTEP_H_
 #define TAKESTEP_H_
 #include"common.h"
-int takestep(gsl_complex alpha,
-		int index,
-		gsl_vector_complex *Error,
-		gsl_vector_complex *eta){
+int TakeStep(gsl_vector *l_m,
+		int index1,
+		int index2, //coordinates that are chosen
+		gsl_vector_complex *preceive, //receive symbol vector
+		gsl_vector_complex *Phi, // phi complex vector
+		gsl_vector_complex *eta, //eta complex vector
+		gsl_matrix *K_r,// real kernel matrix
+		gsl_matrix *K_i, //imaginary kernel matrix
+//		double eta_sub, //mutual part
+		double L_sub,  //update L function
+		double S_sub,  //update S function
+		int label //0 real part 1 imaginary part
+		){
+	int count1,count2;  //counter
+	double sigma1, sigma1_hat, sigma2, sigma2_hat;//step of dual variable
+	double Phi_temp=0;
+	double eta_temp=0;
+//update alpha or beta vector
+
+//update Phi sub function
+//update eta sub function
+	for(count1=0;count1<Nr;count1++){
+	Phi_temp-=(sigma1-sigma1_hat)*gsl_matrix_get(K_r, count1,index1 );
+	Phi_temp-=(sigma2-sigma2_hat)*gsl_matrix_get(K_r, count1, index2);
+	gsl_vector_complex_get(Phi, count1).dat[label]=Phi_temp;
+    eta_temp+=pow(-1, label+1)*(sigma1-sigma1_hat)*gsl_matrix_get(K_r, count1, index1);
+    eta_temp+=pow(-1, label+1)*(sigma2-sigma2_hat)*gsl_matrix_get(K_r, count1, index2);
+    gsl_vector_complex_get(eta, count1).dat[label]=eta_temp;
+	}
+	//update S sub function
+	for(count2=0;count2<Nr;count2++){
+
+	}
+	//update L sub function
+	L_sub=(sigma1-sigma1_hat)*((sigma1-sigma1_hat)*gsl_matrix_get(K_r, index1, index1)
[…]

### 2015-08-25 Report Aug 5 2015/Report Aug 2015.tex
Backup

@@
 where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components.
+Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), only the real part of kernel matrix is required for each channel.
+In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping condition.
+Therefore, in large MIMO scenario, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.
 \section{Work Set Selection and Solver}\label{WSS}
 (\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.
+
 Decomposition method is a set of efficient algorithms that can help to conquer this difficulty.
@@
 Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) are symmetric, in this section we discuss real part only.
-By dividing the variables into work set $S$ and fixed set $N$, (\ref{complex duality real part vectorizes}) can be changed to:
+By dividing the variables into work set $S$ and fixed set $N$, we have $(\alpha, \hat{\alpha})=((\alpha_{N}, \hat{\alpha}_{N})\mathbf{e}_{N}+(\alpha_{S}+\hat{\alpha}_{S})\mathbf{e}_{S})$, where $\mathbf{e}_{K}$ denotes the modified vector of $\mathbf{e}$ with the components in set $K$ zeroed, for sake of brevity， we replace $\alpha_{K}\mathbf{e}_{K}$ by $\alpha_{K}$.
+Thus (\ref{complex duality real part vectorizes}) can be changed to:
 \begin{IEEEeqnarray}[\relax]{l}
@@
 Where $\mathbf{K}^{r}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\mathbf{K}^{r}_{SS}& -\mathbf{K}^{r}_{SN}\\
--\mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
+\mathbf{K}^{r}_{SS}& \mathbf{K}^{r}_{SN}\\
+\mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
 \end{IEEEeqnarraybox*}\right]$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$
@@
 \begin{equation}
-maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]-[(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
-+Re(\mathbf{y})_{S}^{T}](\alpha-\hat{\alpha})_{S}-\epsilon[\mathbf{e}_{S}^{T}(\alpha+\hat{\alpha})_{S}],
+maximize\quad \Theta_{S}^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]+[Re(\mathbf{y})_{S}^{T}-(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
+](\alpha-\hat{\alpha})_{S}-\epsilon[\mathbf{e}_{S}^{T}(\alpha+\hat{\alpha})_{S}],
 \label{subset optimization}
@@
 \end{equation} 
-where $\delta_{S}=\alpha_{S}^{new}-\alpha_{S}$
-In our regression model, the offset is omitted, therefore different from SMO algorithm, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration.
+where $\delta_{S}=\alpha_{S}^{new}-\alpha_{S}$, the gain in (\ref{maximum gain work set selection}) can be written as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}[(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+2(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}]+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}](\delta-\hat{\delta})_{S}\\
+-\epsilon(\delta+\hat{\delta})_{S}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S}](\delta-\hat{\delta})_{S}-\epsilon(\delta+\hat{\delta})_{S}
+\label{gain work set selection1}
+\end{IEEEeqnarray} 
+In (\ref{gain work set selection1}), we use 
+\begin{IEEEeqnarray}[\relax]{l}
+(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}+(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}=[(\alpha-\hat{\alpha})^{T}_{S}, (\alpha-\hat{\alpha})^{T}_{N}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\mathbf{K}^{r}_{SS}\\
+\mathbf{K}^{r}_{NS}
+\end{IEEEeqnarraybox*}\right]=(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S},
+\label{modification of gain work set selection}
+\end{IEEEeqnarray}
+where $\mathbf{K}^{r}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns  that belong to work set $S$.
+Then we define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Phi^{r}=Re(\mathbf{y})-\mathbf{K}^{r}(\alpha-\hat{\alpha})$ and $\Phi^{i}=Im(\mathbf{y})-\mathbf{K}^{r}(\beta-\hat{\beta})$
+Thus (\ref{gain work set selection1}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon(\delta+\hat{\delta})_{S}
+\label{gain work set selection2}
+\end{IEEEeqnarray} 
+In our regression model, the offset is omitted, therefore different from SMO type algorithms, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration.
 However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{Training without offset}.
@@
  \nonumber
- maximize\quad \Theta_{1}^{r}=-\frac{1}{2}((\alpha_{1}-\hat{\alpha}_{1})^{new})^{2}\mathbf{K}_{11}^{r}-(\alpha_{1}-\hat{\alpha}_{1})^{new}\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}(\alpha_{j}-\hat{\alpha}_{j})^{new}
+ maximize\quad \Theta_{1}^{r}=-\frac{1}{2}((\alpha_{1}-\hat{\alpha}_{1})^{new})^{2}\mathbf{K}_{11}^{r}-(\alpha_{1}-\hat{\alpha}_{1})^{new}\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}(\alpha_{j}-\hat{\alpha}_{j})
 +Re(y_{1})(\alpha_{1}-\hat{\alpha}_{1})^{new}\\
@@
 \Rightarrow \hat{\alpha}_{1}^{new}=\hat{\alpha}_{1}-\frac{\Phi_{1}^{r}+\epsilon}{\mathbf{K}_{11}^{r}}\\
+\nonumber
 \label{partial optimization function 1-D alpha hat}
@@
 \hat{\alpha}^{new\quad clipped}=[\hat{\alpha}^{new}]_{0}^{C\tilde{R}(\hat{\xi}^{r})}\\
+\nonumber
 \label{clipped new dual variable}
 \end{IEEEeqnarray}
+
 where $[ ]_{a}^{b}$ denotes to function 
@@
 \end{IEEEeqnarray}
-Based on (\ref{partial optimization function 1-D alpha}), (\ref{partial optimization function 1-D alpha hat}) and (\ref{clipped new dual variable}), The gain of objective function respect to $i$th dual variable pair is
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \Theta_{i}^{r}=\Theta^{r}((\alpha+\delta_{i}\mathbf{e}_{i}), (\hat{\alpha}+\hat{\delta}_{i}\mathbf{e}_{i}))-\Theta^{r}(\alpha, \hat{\alpha})\\
-\nonumber
-=-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})^{2}\mathbf{K}_{ii}^{r}-(\delta_{i}-\hat{\delta}_{i})\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}_{ij}^{r}+Re(y_{i})(\delta_{i}-\hat{\delta}_{i})-\epsilon(\delta_{i}+\hat{\delta}_{i})\\
+Based on (\ref{gain work set selection2}), The gain of objective function respect to $i$th dual variable pair is 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \Theta_{i}^{r}=\Theta^{r}((\alpha_{i}+\delta_{i}\mathbf{e}_{i}), (\hat{\alpha}_{i}+\hat{\delta}_{i}\mathbf{e}_{i}))-\Theta^{r}(\alpha, \hat{\alpha})\\
+\nonumber
+=-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})^{2}\mathbf{K}_{ii}^{r}+\Phi^{r}_{1}(\delta_{i}-\hat{\delta}_{i})-\epsilon(\delta_{i}+\hat{\delta}_{i})\\
 =(\delta_{i}-\hat{\delta}_{i})[-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})\mathbf{K}_{ii}^{r}+\Phi_{i}^{r}-\epsilon\frac{\delta_{i}+\hat{\delta}_{i}}{\delta_{i}-\hat{\delta}_{i}}],
-\label{gain of objective function}
+\label{gain of 1-D objective function}
 \end{IEEEeqnarray}
@@
 \subsection{Double Direction Solver}
-
+Although omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however recent work in machine learning field shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained\cite{training SVM without offset}.
+The 2-D solver uses the same principle as 1-D solver, the work set size is 2, recall (\ref{subset optimization}), let $(\alpha_{1}, \hat{\alpha}_{1})$, $(\alpha_{2}, \hat{\alpha}_{2})$ denote the two dual variable pairs that are chosen for optimization, that is $(\alpha_{s}, \hat{\alpha}_{s})=((\alpha_{1}\mathbf{e}_{1}+\alpha_{2}\mathbf{e}_{2}), (\hat{\alpha}_{1}\mathbf{e}_{1}+\hat{\alpha}_{2}\mathbf{e}_{2}))$.
+Thus we have, based on (\ref{subset optimization}), the sub objective function can be written as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize\quad \Theta^{r}_{1,2}=-\frac{1}{2}[(\alpha_{1}-\hat{\alpha}_{1})^{2}\mathbf{K}^{r}_{11}+(\alpha_{2}-\hat{\alpha}_{2})^{2}\mathbf{K}^{r}_{22}+2(\alpha_{1}-\hat{\alpha}_{1})(\alpha_{2}-\hat{\alpha}_{2})\mathbf{K}^{r}_{12}]-\\
+\nonumber
+(\alpha_{1}-\hat{\alpha}_{1})\sum_{j\neq 1, 2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{1j}-(\alpha_{2}-\hat{\alpha}_{2})\sum_{j\neq 1, 2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{2j}+Re(y_{1})(\alpha_{1}-\hat{\alpha}_{1})+Re(y_{2})(\alpha_{2}-\hat{\alpha}_{2})\\
+-\epsilon(\alpha_{1}+\hat{\alpha}_{1}+\alpha_{2}+\hat{\alpha}_{2}), 
+\label{2-D solver}
+\end{IEEEeqnarray}
+Based on (\ref{2-D solver}), the partial derivative of $\Theta^{r}_{1,2}$ with respect to $\alpha_{1}$ is 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\frac{\partial \Theta^{r}_{1,2}}{\partial \alpha_{1}}=-(\alpha_{1}-\hat{\alpha}_{1})\mathbf{K}^{r}_{11}-(\alpha_{2}-\hat{\alpha}_{2})\mathbf{K}^{r}_{12}-\sum_{j\neq 1, 2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{1j}+Re(y_{1})-\epsilon=\\
+\nonumber
+-(\alpha_{1}-\hat{\alpha}_{1})\mathbf{K}^{r}_{11}+Re(y_{1})-\sum_{j\neq 1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{1j}-\epsilon\\
+\Rightarrow \alpha^{new}_{1}=\alpha_{1}+\frac{(\Phi^{r}_{1}-\epsilon)}{\mathbf{K}^{r}_{11}},
+\label{partial derivative sample1}
+\end{IEEEeqnarray}
+Similarly we can derive the update formulas of $\hat{\alpha}_{1}$,$\alpha_{2}$ and $\hat{\alpha}_{2}$
+\begin{equation}
+\hat{\alpha}^{new}_{1}=\hat{\alpha}_{1}-\frac{(\Phi^{r}_{1}+\epsilon)}{\mathbf{K}^{r}_{11}},
+\label{partial derivative sample2}
+\end{equation}
+
+\begin{equation}
+\alpha^{new}_{2}=\alpha_{2}+\frac{(\Phi^{r}_{2}-\epsilon)}{\mathbf{K}^{r}_{22}},
+\label{partial derivative sample3}
+\end{equation}
+
+\begin{equation}
+\hat{\alpha}^{new}_{2}=\hat{\alpha}_{2}-\frac{(\Phi^{r}_{2}+\epsilon)}{\mathbf{K}^{r}_{22}},
+\label{partial derivative sample4}
+\end{equation}
+It is obviously the dual variables in 2-D solver have the same update rule as that of 1-D solver.
+Based on (\ref{gain work set selection2}), assume the $i$th and $j$th dual variable pair are chosen, the gain of 2-D solver objective function can be written as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \Theta^{r}_{ij}=-\frac{1}{2}[(\delta_{i}-\hat{\delta}_{i})^{2}\mathbf{K}^{r}_{ii}+(\delta_{j}-\hat{\delta}_{j})^{2}\mathbf{K}^{r}_{jj}+2(\delta_{i}-\hat{\delta}_{i})(\delta_{j}-\hat{\delta}_{j})\mathbf{K}^{r}_{ij}]+\Phi^{r}_{i}(\delta_{i}-\hat{\delta}_{i})+\Phi^{r}_{j}(\delta_{j}-\hat{\delta}_{j})\\
+-\epsilon(\delta_{i}+\hat{\delta}_{i}+\delta_{j}+\hat{\delta}_{j}),
+\label{gain of 2-D objective function1}
+\end{IEEEeqnarray}
+recall the gain of objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
+ \begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \Theta^{r}_{ij}=\bigtriangledown \Theta^{r}_{i}+\bigtriangledown \Theta^{r}_{j}-(\delta_{i}-\hat{\delta}_{i})(\delta_{j}-\hat{\delta}_{j})\mathbf{K}^{r}_{ij},
+\label{gain of 2-D objective function1}
+\end{IEEEeqnarray}
 \subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}
@@
 On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
-\section{Stopping Criteria}
+\section{Stopping Criteria}\label{stopping criteria}
 \section{Hyperparameter Setting}

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/SVR_DETECTOR.c

@@ -1,0 +1,305 @@
+/*
+ * SVR_DETECTOR.h
+ *
+ *  Created on: Jul 15, 2015
+ *      Author: tianpei.chen@mail.mcgill.ca
+ */
+
+#ifndef SVR_DETECTOR_CPP_
+#define SVR_DETECTOR_CPP_
+#include "public.h"
+#include"Initialization.h"
+#include"WSS2_1Dsolver.h"
+#include"TakeStep.h"
+#include"Stopping_Criteria.h"
+typedef struct{
+	gsl_complex data;
+	int index;
+
+}Nalpha_Node;
+
+void  Initialization(gsl_vector *alpha,//Lagrange multiplier
+		gsl_vector *beta,//Lagrange multiplier
+		const gsl_vector_complex *preceived,//received symbol vector(output of trainning data set)
+		gsl_matrix *K_r, //real kernel matrix
+		gsl_matrix *K_i, //imaginary kernel matrix
+		gsl_vector_complex *phi, // intermediate parameter
+		gsl_vector_complex *eta, //intermediate parameter
+		double L, //L sub function
+		double S,  //S sub function
+		double G_pilot, //global stopping parameter
+		int method //label which start strategy is used
+		);
+void 	WSS2_1Dsolver(gsl_vector *l_m,  //Lagrange Multiplier vector
+        gsl_vector_complex *phi,  //update parameter
+        gsl_matrix *R_Kernel,    //real kernel matrix
+        int F_i,  //index of first maximum Lagrange multiplier
+        int S_i, //index of second maximum Lagrange multiplier
+		int model //determine this routine is for real part (0) or imaginary part (1)
+);
+void TakeStep(gsl_vector *l_m,
+		int index1, //coordinates that are chosen
+		int index2, //coordinates that are chosen
+		gsl_vector_complex *preceive, //receive symbol vector
+		gsl_vector_complex *Phi, // phi complex vector
+		gsl_vector_complex *eta, //eta complex vector
+		gsl_matrix *K_r,// real kernel matrix
[…]

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/SVR_DETECTOR.cpp

@@ -1,0 +1,305 @@
+/*
+ * SVR_DETECTOR.h
+ *
+ *  Created on: Jul 15, 2015
+ *      Author: tianpei.chen@mail.mcgill.ca
+ */
+
+#ifndef SVR_DETECTOR_CPP_
+#define SVR_DETECTOR_CPP_
+#include "public.h"
+#include"Initialization.h"
+#include"WSS2_1Dsolver.h"
+#include"TakeStep.h"
+#include"Stopping_Criteria.h"
+typedef struct{
+	gsl_complex data;
+	int index;
+
+}Nalpha_Node;
+
+void  Initialization(gsl_vector *alpha,//Lagrange multiplier
+		gsl_vector *beta,//Lagrange multiplier
+		const gsl_vector_complex *preceived,//received symbol vector(output of trainning data set)
+		gsl_matrix *K_r, //real kernel matrix
+		gsl_matrix *K_i, //imaginary kernel matrix
+		gsl_vector_complex *phi, // intermediate parameter
+		gsl_vector_complex *eta, //intermediate parameter
+		double L, //L sub function
+		double S,  //S sub function
+		double G_pilot, //global stopping parameter
+		int method //label which start strategy is used
+		);
+void 	WSS2_1Dsolver(gsl_vector *l_m,  //Lagrange Multiplier vector
+        gsl_vector_complex *phi,  //update parameter
+        gsl_matrix *R_Kernel,    //real kernel matrix
+        int F_i,  //index of first maximum Lagrange multiplier
+        int S_i, //index of second maximum Lagrange multiplier
+		int model //determine this routine is for real part (0) or imaginary part (1)
+);
+void TakeStep(gsl_vector *l_m,
+		int index1, //coordinates that are chosen
+		int index2, //coordinates that are chosen
+		gsl_vector_complex *preceive, //receive symbol vector
+		gsl_vector_complex *Phi, // phi complex vector
+		gsl_vector_complex *eta, //eta complex vector
+		gsl_matrix *K_r,// real kernel matrix
[…]

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/SVR_DETECTOR.h

@@ -1,161 +1,21 @@
 /*
  * SVR_DETECTOR.h
  *
- *  Created on: Jul 15, 2015
- *      Author: tianpei.chen@mail.mcgill.ca
+ *  Created on: Aug 21, 2015
+ *      Author: Preston Chen
  */
-
+#include"public.h"
 #ifndef SVR_DETECTOR_H_
 #define SVR_DETECTOR_H_
-#include "common.h"
-/*
- *  Parameters configuration
- */
-//#define  C  1e-3;      //Penalize weight for noise
-//#define epsilon 1e-3; //Training precision
-typedef struct{
-	gsl_complex data;
-	int index;
 
-}Nalpha_Node;
-/*
- * inner function
- */
-//int TestData(gsl_complex alpha, int index, gsl_vector_complex *Error, gsl_vector_complex *eta);
-//int takestep(gsl_complex alpha, int index, gsl_vector_complex *Error, gsl_vector_complex *eta);
-//Nalpha_Node checkNonbound(gsl_vector_complex *alpha);
 
-int Initialization(gsl_vector *alpha,//Lagrange multiplier
-		gsl_vector *beta,//Lagrange multiplier
-		const gsl_vector_complex *preceived,//received symbol vector(output of trainning data set)
-		gsl_vector_complex *phi, // update parameter
-		double S_C_real, //real stopping parameter
-		double S_C_imag,  //imaginary stopping parameter
-		int method //label which start strategy is used
+void SVR_DETECTOR( gsl_vector_complex *preceived,  //received symbol vector
+	 gsl_matrix_complex *pH, //channel propagation matrix
+		float SNRb, // bit signal to noise ratio
+		gsl_vector_complex *psymout, //detected transmitted symbol vector
+		int start_M,  //initialization method
+		int selection_M //work set selection strategy
 		);
-void 	WSS2_1Dsolver(gsl_vector *l_m,  //Lagrange Multiplier vector
-        gsl_vector_complex *phi,  //update parameter
-        gsl_matrix *R_Kernel,    //real kernel matrix
-        int F_i,  //index of first maximum Lagrange multiplier
-        int S_i, //index of second maximum Lagrange multiplier
[…]

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/TestData.h

@@ -7,7 +7,7 @@
 
 #ifndef TESTDATA_H_
 #define TESTDATA_H_
-#include"common.h"
+#include "public.h"
 int TestData(gsl_complex alpha,
 		int index,
 		gsl_vector_complex *Error,

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/WSS2_1Dsolver.h

@@ -9,7 +9,7 @@
  *      INPUT: alpha(beta), alpha_hat(beta_hat), label1, label2, phi, R_Kernel
  *      OUTPUT: First, Second
  */
-#include "common.h"
+#include "public.h"
 #ifndef WSS2_1DSOLVER_H_
 #define WSS2_1DSOLVER_H_
 void 	WSS2_1Dsolver(gsl_vector *l_m,  //Lagrange Multiplier vector
@@ -47,7 +47,7 @@ for(count=0;count<2*Nr;count++){
 		sigma=temp_l_m-gsl_vector_get(l_m,count);
 		sigma_hat=0;
 	}else{
-		temp_l_m_hat=gsl_vector_get(l_m, count)-double((gsl_vector_complex_get(phi,count).dat[model]+epsilon))/double((gsl_matrix_get(R_Kernel, count,count)));
+		temp_l_m_hat=gsl_vector_get(l_m, count)-(double)((gsl_vector_complex_get(phi,count).dat[model]+epsilon))/(double)((gsl_matrix_get(R_Kernel, count,count)));
 		if(temp_l_m_hat<0){
 			temp_l_m_hat=0;
 		}else if (temp_l_m_hat>C){
@@ -57,7 +57,7 @@ for(count=0;count<2*Nr;count++){
 		sigma_hat=temp_l_m_hat-gsl_vector_get(l_m,count);
 	}
 
-	g=abs((sigma-sigma_hat)*(-0.5*(sigma-sigma_hat)*gsl_matrix_get(R_Kernel(count,count))+gsl_vector_complex_get(phi, count).dat[model]-epsilon*(sigma+sigma_hat)/(sigma-sigma_hat)));
+	g=fabs((sigma-sigma_hat)*(-0.5*(sigma-sigma_hat)*gsl_matrix_get(R_Kernel, count,count)+gsl_vector_complex_get(phi, count).dat[model]-epsilon*(sigma+sigma_hat)/(sigma-sigma_hat)));
 	if(g>best_g){
 		best_g=g;
 		S_i=F_i;

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/channel_generator.h

@@ -1,8 +1,9 @@
+#include "public.h"
 void channel_generator (gsl_matrix_complex *pH, gsl_rng *pr)
 {
-	int Nt, Nr, count1=0, count2=0;
-	Nr=pH->size1;
-	Nt=pH->size2;
+	int  count1=0, count2=0;
+//	Nr1=pH->size1;
+//	Nt1=pH->size2;
 	
 	gsl_complex z;
 	GSL_SET_COMPLEX (&z, 0.0, 0.0);

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/data_generator.h

@@ -1,8 +1,8 @@
-
+#include "public.h"
 void data_generator(gsl_vector_ulong *pdata, gsl_rng *pr, unsigned long Q)
 {
-	int Nt;
-	Nt = pdata -> size;	
+//	int Nt_gener;
+//	Nt_gener = pdata -> size;
 	int count = 0;
 	for (count=0; count<Nt ; count++)
 	  {

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/grayencoder.h

@@ -1,12 +1,13 @@
+#include"public.h"
 void grayencoder (gsl_vector_ulong *pgraydata, gsl_vector_ulong *pgrayindexes, unsigned long Q)
 {
 	unsigned long count=0UL, value=0UL, count2=0UL, temp=0UL;
 
-	int M=0;
-	M = (int) ceil(sqrt(Q));
+	int S=0;
+	S = (int) ceil(sqrt(Q));
 
 	gsl_vector_ulong *ppamdata, *pQAMdata, *peqvdata;
-	ppamdata = gsl_vector_ulong_calloc (M);
+	ppamdata = gsl_vector_ulong_calloc (S);
 	pQAMdata = gsl_vector_ulong_calloc (Q);
 	peqvdata = gsl_vector_ulong_calloc (Q);
 if(Q==4)
@@ -31,7 +32,7 @@ if(Q==4)
 }
 else
 {
-	for (count=0; count<M; count++)
+	for (count=0; count<S; count++)
 	  {
 		value=count;
 		count2 = count;
@@ -46,7 +47,7 @@ else
 	
 	for (count=0; count<Q; count++)
 	  {
-		value = M*gsl_vector_ulong_get(ppamdata, count/M) + gsl_vector_ulong_get (ppamdata, count%M);
+		value = S*gsl_vector_ulong_get(ppamdata, count/S) + gsl_vector_ulong_get (ppamdata, count%S);
 		gsl_vector_ulong_set (pQAMdata, count, value);
 		gsl_vector_ulong_set (peqvdata, value, count);   //the pdata is actually the index
 		//according to the gray code we can find its indexs according to the indexes we can find the gray code

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/modulator.h

@@ -1,10 +1,11 @@
-
+#include "public.h"
 void modulator (gsl_vector_ulong *pdata, gsl_vector_complex *ptransmitted, gsl_vector_complex *psymbolconstellation)
 {
-	int Nt, count=0;
-	Nt = pdata->size;
+	int Nt_modu;
+	int count=0;
+	Nt_modu = pdata->size;
 	
-	for (count=0 ; count < Nt ; count++)
+	for (count=0 ; count < Nt_modu ; count++)
 		gsl_vector_complex_set (ptransmitted, count, gsl_vector_complex_get (psymbolconstellation, gsl_vector_ulong_get (pdata, count)));
 	
 

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/noise_generator.h

@@ -1,12 +1,14 @@
+#include "public.h"
 void noise_generator (gsl_vector_complex *pnoise, gsl_rng *pr, double sigman)
 {
-	int Nr, count=0;
-	Nr=pnoise->size;
+	int Nr_ngener;
+	int count=0;
+	Nr_ngener=pnoise->size;
 	
 	gsl_complex z;
 	GSL_SET_COMPLEX (&z, 0.0, 0.0);
 
-	for (count=0 ; count<Nr ; count++)
+	for (count=0 ; count<Nr_ngener ; count++)
 	    {
 			GSL_SET_COMPLEX (&z, gsl_ran_gaussian (pr, sigman), gsl_ran_gaussian (pr, sigman));
 			gsl_vector_complex_set (pnoise, count, z);

### 2015-08-25 SVR for large MIMO/SVR_MIMO_communication_line_original_version/src/symbolconstellation.h

@@ -6,31 +6,33 @@
 // Description : Generate symbol constellation according to the index of the random generated data
 // (pdata)
 //============================================================================
-#include"common.h"
-void symbolconstellation(gsl_vector_complex *psymbolconstellation, int Nt) {
-	int Q, count1, count = 0;
+#include "public.h"
+void symbolconstellation(gsl_vector_complex *psymbolconstellation, int Nt_conste) {
+	int Q;
+	int count1=0;
+	int count = 0;
 	Q = psymbolconstellation->size;
 	gsl_complex z;
-	int M = 0;
-	M = (int) ceil(sqrt(Q)); /*the square QAM of dimension Q is equivalent to 2 PAM of dimension M */
+	int S = 0;
+	S = (int) ceil(sqrt(Q)); /*the square QAM of dimension Q is equivalent to 2 PAM of dimension S */
 	/* The average energy of the square QAM is given by: Es=2/3*d^2*(Q-1)
 	 where dmin=2d
 	 Hence we get d=sqrt(3*Es/(2*(Q-1)))
-	 We set Es=1/Nt so the total transmitted power is normalized*/
+	 We set Es=1/Nt_conste so the total transmitted power is normalized*/
 
 	double d = 0.0;
 	if (Q == 2)   //BPSK
 			{
-		d = sqrt(double(1 / double(Nt)));
+		d = sqrt((double)((double)(1) / (double)(Nt_conste)));
 	}
 	else {
-		d = sqrt(3 / (2 * (float) (Nt * (Q - 1))));
+		d = sqrt(3 / (2 * (float) (Nt_conste * (Q - 1))));
 	}
 	gsl_vector *psymbolconstellationreal;
-	psymbolconstellationreal = gsl_vector_calloc(M);
-		for (count = 0; count < M; count++) /*generates an M-PAM constellation*/
+	psymbolconstellationreal = gsl_vector_calloc(S);
+		for (count = 0; count < S; count++) /*generates an S-PAM constellation*/
 			gsl_vector_set(psymbolconstellationreal, count,
-					d * (2 * count - M + 1));
+					d * (2 * count - S + 1));
 
 		for (count = 0; count < Q; count++) {
 			gsl_complex z;
@@ -39,8 +41,8 @@ void symbolconstellation(gsl_vector_complex *psymbolconstellation, int Nt) {
 						gsl_vector_get(psymbolconstellationreal, count), 0);
 			} else {
 				GSL_SET_COMPLEX(&z,
[…]

### 2015-08-25 SVR for large MIMO/test/src/test.c

@@ -1,0 +1,22 @@
+/*
+ ============================================================================
+ Name        : test.c
+ Author      : Tianpei Chen
+ Version     :
+ Copyright   : Your copyright notice
+ Description : Hello World in C, Ansi-style
+ ============================================================================
+ */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include<gsl/gsl_vector.h>
+int main(void) {
+	gsl_vector *v=gsl_vector_calloc(8);
+	int count;
+	for(count=0; count<8;count++){
+		gsl_vector_set(v,count,count);
+	}
+	puts("!!!Hello World!!!"); /* prints !!!Hello World!!! */
+	return EXIT_SUCCESS;
+}

### 2015-08-25 FCSD-CUDA project/The final draft of CUDA paper/conf_draft/GPU Acceleration for Fixed Complexity Sphere Decoder in Large MIMO Uplink Systems.tex
update SVR package

--- 2015-02-04 FCSD-CUDA project/The final draft of CUDA paper/conf_draft/conference draft.tex
@@
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}
-\documentclass[letterpaper, 10pt, conference,twoside]{ieeeconf}
+\documentclass[letterpaper, 10pt, conference, twoside]{ieeeconf}
 %\documentclass[12pt,a4paper,final]{article}
@@
 \author{Tianpei Chen and Harry Leib\\
-Department of Electrical and Computer Engineering, McGill University, Montreal, Quebec\\
+Department of Electrical and Computer Engineering,\\
+ McGill University\\ Montreal, Quebec, Canada\\
 tianpei.chen@mail.mcgill.ca harry.leib@mcgill.ca}
@@
 \maketitle
-\thispagestyle{fancy} % IEEE模板在\maketitle后会自动声明\thispagestyle{plain}，  
+%\thispagestyle{fancy} % IEEE模板在\maketitle后会自动声明\thispagestyle{plain}，  
                       % 导致第一页什么都没有。所以得把plain更改为fancy
 %\fancyhead{\thepage} % 奇数页右侧，偶数页左侧显示页码 
-\lhead{} % 页眉左，需要东西的话就在{}内添加  
-\chead{} % 页眉中  
-\rhead{} % 页眉右  
-\lfoot{} % 页眉左  
-\cfoot{} % 页眉中  
-\rfoot{} %页眉右，\thepage 表示当前页码  
-\renewcommand{\headrulewidth}{0pt} %改为0pt即可去掉页眉下面的横线  
-\renewcommand{\footrulewidth}{0pt} %改为0pt即可去掉页脚上面的横线  
-\pagestyle{fancy}  
-\fancyhead[RO,LE]{\thepage}  
+%\lhead{} % 页眉左，需要东西的话就在{}内添加  
+%\chead{} % 页眉中  
+%\rhead{} % 页眉右  
+%\lfoot{} % 页眉左  
+%\cfoot{} % 页眉中  
+%\rfoot{} %页眉右，\thepage 表示当前页码  
+%\renewcommand{\headrulewidth}{0pt} %改为0pt即可去掉页眉下面的横线  
+%\renewcommand{\footrulewidth}{0pt} %改为0pt即可去掉页脚上面的横线  
+%\pagestyle{fancy}  
+%\fancyhead[RO,LE]{\thepage}  
 %\rhead{\thepage}
@@
 In order to improve simulation efficiency of decoders in large MIMO systems, we propose to use General Purpose Graphic Processing Units (GPGPU).
-This paper considers the implementation of a Fixed Complexity Sphere Decoder (FCSD) for large scale MIMO systems using the framework of GPGPU-Computed Unified Device Architecture (CUDA).
-Significant speedups were formed for large MIMO systems and constellation sizes over conventional CPU implementation while providing the same Bit Error Rate (BER) performance, hence the proposed algorithm provides great potential for GPGPU to accelerate the simulation of large MIMO systems.
+This paper considers the implementation of a Fixed Complexity Sphere Decoder (FCSD) for large scale MIMO uplink systems using the framework of GPGPU-Computed Unified Device Architecture (CUDA).
+Using GPGPU, significant speedups were found for large MIMO systems and constellation sizes, over conventional CPU implementation, while providing the same Bit Error Rate (BER) performance.
+Hence the proposed approach shows great potential of GPGPU to accelerate computer simulations of large MIMO systems.
 
-\textbf{ Keywords: Large MIMO, fixed complexity sphere decoder (FCSD), general purpose graphic processing units (GPGPU), computed unified device architecture (CUDA)}
+\textbf{ \textit{ Keywords: Large MIMO, fixed complexity sphere decoder (FCSD), general purpose graphic processing units (GPGPU), computed unified device architecture (CUDA)}}
 \end{abstract}
@@
 \section{Introduction}
-A present challenge in the wireless communication area is to bridge the sharp contrast between the increasing demand of mobile network speed for the transmission of rich media content with better QoS (Quality of Service), and the shortage of radio frequency spectrum.
+A present challenge in the wireless communication area is to bridge the sharp gulf between the increasing demand of mobile network speed for the transmission of rich media content with better QoS (Quality of Service), and the shortage of radio frequency spectrum.
 Multiple Input Multiple Output (MIMO) technology is of immense research interest since it can help solving this problem owing to several advantages it offers.
@@
 GPU computing has been applied to different research fields such as computer vision\cite{fung2008using}, computer games\cite{blewitt2013applicability}, signal processing\cite{van2011accelerating}\cite{6671435}, and finance\cite{grauer2013accelerating}.
-The Computed unified Device Architecture (CUDA)\cite{cook2013cuda}\cite{nvidia2008programming} is a programming model for GPGPU that was proposed by NIVIDIA and has become the dominant framework for GPGPU programming.
-It is based on popular programming languages (C, C++, Java, Python, Fortran, Direct Compute), such that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
-CUDA employs the Single Instruction Multiple Threads (SIMT) programming model, enables a GPU to implement parallel data processing, and has become a parallel computing platform for different applications.
+The Computed Unified Device Architecture (CUDA)\cite{cook2013cuda}\cite{nvidia2008programming} is a parallel computing platform and programming model for GPGPU that was proposed by NIVIDIA and has become the dominant framework for GPGPU programming.
+It is based on popular programming languages (e.g.
+C, C++, Java, Python, Fortran, Direct Compute), such that the application developers in different areas do not need to learn a new programming language or get to know the hardware details.
+CUDA employs the Single-instruction, Multiple-threads (SIMT) architecture that enables a GPU to implement parallel data processing, and has become a parallel computing platform for different applications.
 
- \cite{hongyuan2010fixed} presents an interesting implementation of Fixed Complexity Sphere Decoder (FCSD) based on GPU, however only parallel implementation of multiple decoders is considered rather than exploiting the attribute of parallelism of the algorithm itself.
-In this paper, a GPU based implementation of single FCSD is proposed, which is referred to as CUDA-FCSD.
-A heterogeneous programming solution for FCSD preprocessing and integrated blocked parallel path searching and decision making are presented.
+ An interesting implementation of a Fixed Complexity Sphere Decoder (FCSD) based on GPU is presented in \cite{hongyuan2010fixed}.
+However, in this scheme only parallel implementation of multiple decoders is considered rather than exploiting the attribute of parallelism of the decoding algorithm itself.
+In our paper, a GPU based implementation of a single FCSD is proposed, which is referred to as CUDA-FCSD.
+A heterogeneous programming solution for FCSD preprocessing, integrated blocked parallel path searching and decision making are presented.
 Using this implementation the speedup as well as Bit Error Rate (BER) performance of different sizes of MIMO systems and signal constellations are analyzed.
-The proposed CUDA-FCSD implementation demonstrates a great potential for large MIMO systems.
+The proposed CUDA-FCSD implementation demonstrates a great speedup potential for large MIMO systems.
 
-The rest of the paper is organized as follows.
-Section \ref{programming model} briefly introduces CUDA, the GPU architecture and the programming model.
+The rest of this paper is organized as follows.
+Section \ref{programming model} briefly introduces CUDA and GPU architecture.
 In section \ref{GPUFCSD}, we present details of the implementation of CUDA-FCSD.
@@
 \section{CUDA Programming Model and GPU Architecture} \label{programming model} 
-\subsection{Single Instruction Multiple Thread Model}
-The CUDA programming model is a C programming extension with special defined syntax and structure.
+\subsection{Single-instruction, Multiple-thread Architecture}
+The CUDA programming model is a C programming extension with special defined syntax and principle.
 The serial code is executed on the host (CPU) side, and massive parallel data processing is performed on the device (GPU) side.
@@
 A thread is the basic programming unit of CUDA.
-A block of cooperative threads form a thread block, where they can synchronize their behavior and communicate.
+A set of cooperative threads form a thread block, where they can synchronize their behavior and communicate.
 Fig.
@@
 The threads can be organized into one-dimensional, two-dimensional or three-dimensional blocks.
-Similarly, blocks can also be grouped into a one-dimensional, two-dimensional, or three-dimensional grid.
+Similarly, blocks can also be grouped into a one-dimensional, two-dimensional, or three-dimensional grids.
 }
@@
 When one warp is waiting for data loading, the other warps begin to execute.
-Such an approach is called a Single Instruction Multiple Thread (SIMT) model, whereby the behavior of each thread can be branched to achieve thread level parallelism.
+Such an approach is called a Single-instruction, Multiple-thread (SIMT) architecture, whereby the behavior of each thread can be branched to achieve thread level parallelism.
 The GPU uses a massive number of threads to hide the long latency of a global memory, instead of using a large cache as CPU.
@@
 The GPU works as a coprocessor system, consisting of Stream Multiprocessors (SMs), which perform multiply-add arithmetic operations.
-Furthermore, each SM has the special functional units (SFU) that can perform more complex operations such as trigonometric functions and reciprocal square root.
-There are five types of memories: registers, shared memory, global memory, constant memory and texture memory.
-Registers are allocated dynamically and privately to threads, and provide most rapid access speeds.
+Furthermore, each SM has the special functional units (SFU) that can perform more complex operations such as trigonometric functions and square root.
+In a GPU, there are five types of memories: registers, shared memory, global memory, constant memory and texture memory.
+Registers are allocated dynamically and privately to threads, and provide most rapid access.
 The shared memory, also called on-chip memory, is located on the SMs and can be shared among the threads in one block.
 Shared memory has low latency and limited capacity.
-Global memory, which is off-chip has large latency and large capacity.
-The other two types of memories, constant memory and texture memory, are located off-chip, but cached.
-Therefore the access speed of these two type of memory space is much faster than that of global memory.
-The variables invoked by \textit{kernel} functions can be stored in either of the these five types of memories.
+Global memory, which is off-chip, has large latency and large capacity.
+The other two types of memories, constant memory and texture memory, are also located off-chip, however they are cached.
+Therefore the access speed of these two types of memory are much faster than that of global memory.
+The variables invoked by \textit{kernel} functions can be stored in either of the these five types of memory.
 
-Because of the resource limitation of SM, the total number of threads that can be defined in one block is limited.
+Because of the resource limitation of SMs, the total number of threads that can be defined in one block is limited.
 On current CUDA supported GPUs, one block contains up to 1024 threads.
@@
 where $\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from a signal constellation $\mathbb{O}$ (4-QAM, 16-QAM, 64-QAM) of size $M$.
-All the possible transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, with $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identity distributed (i.i.d) circularly symmetric complex Gaussian components of zero mean and unit variance.
+The possible transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian components of zero mean and unit variance.
 Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
 
-Assume the receiver has the perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known by receiver, as well as the SNR.
+Assume the receiver has perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known, as well as the SNR.
 The task of the MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
@@
 \end{equation}
-where $\mathbf{Q}\in \mathbb{C}^{N_{t}\times N_{t}}$ is a unitary matrix and $\mathbf{R}\in \mathbb{C}^{N_{t}\times N_{t}}$, is an upper triangular matrix \cite{golub2012matrix}, we can write (\ref{formula 2}) as:
+where $\mathbf{Q}\in \mathbb{C}^{N_{t}\times N_{t}}$ is a unitary matrix and $\mathbf{R}\in \mathbb{C}^{N_{t}\times N_{t}}$ is an upper triangular matrix \cite{golub2012matrix}, we can write (\ref{formula 2}) as:
 \begin{eqnarray}
@@
 Similarly to SD the FCSD also performs depth first searching.
-At the first $\rho$ node levels\footnote{when $N_{r}=N_{t}$ the FCSD can achieve the same diversity as the MLD if $\rho\geq \sqrt{N_{t}}-1$ \cite{barbero2008fixing}} the FCSD searches all the possible signal symbols in constellation $\mathbb{O}^{N_{t}}$, a process called the Full Expansion (FE) stage.
+At the first $\rho$ node levels\footnote{when $N_{r}=N_{t}$ the FCSD can achieve the same diversity as the MLD if $\rho\geq \sqrt{N_{t}}-1$ \cite{barbero2008fixing}} the FCSD searches all the possible signal symbols in constellation $\mathbb{O}$, a process called the Full Expansion (FE) stage.
 Let $\mathbf{s}^{F}$ denote FCSD symbol vector candidates.
@@
 \ref{figure4}, there are $\rho=2$ FE node levels and each node level has $M=4$ branches.
-According to (\ref{formula 4}), we have:
+According to (\ref{formula 4}), The decision feedback is:
 \begin{equation}
-s^{F}_{i}=arg\min_{s\in \mathbb{O}^{N_{t}}}\{\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s^{F}_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s^{F}_{j})|^{2}\},  \label{formula 5}
+s^{D}_{i}=arg\min_{s^{D}_{i}\in \mathbb{O}}\{\sum_{i=1}^{N_{t}}|r_{ii}(\hat{s}_{i}-s^{D}_{i})+\sum_{j=i+1}^{N_{t}}r_{ij}(\hat{s}_{j}-s^{D}_{j})|^{2}\},  \label{formula 5}
 \end{equation} 
-$i\in [1,2\dots N_{t}]$, where $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$.
-Based on (\ref{formula 5}) at the remaining $N_{t}-\rho$ levels of symbols, the FCSD employs decision feedback, and therefore there are only one branch expansion for each symbol node at this stage.
+$i\in [1,2\dots N_{t}]$, where $r_{ij}$ denotes the component at the $i$th row and $j$th column of the upper triangular matrix $\mathbf{R}$, $s^{D}_{i}$ denotes the $i$ th symbol solution of decision feedback.
+Based on (\ref{formula 5}) at the remaining $N_{t}-\rho$ levels of symbols, the FCSD employs decision feedback, therefore there are only one branch expansion for each symbol node at this stage.
 This stage is called Single Expansion (SE).
@@
 \begin{equation}
-E_{metric}=||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{s}^{F})||^{2},
+E_{metric}=||\mathbf{R}(\mathbf{\hat{s}}-\mathbf{s}^{F})||^{2}.
 \end{equation} 
-where $\mathbf{s}^{F}$ denotes the symbol vector candidate. The symbol vector candidate with minimum $E_{metric}$ is chosen as the solution. The total number of candidates is $M^{\rho}$.  
+The symbol vector candidate with minimum $E_{metric}$ is chosen as the solution. The total number of candidates is $M^{\rho}$.  
 \begin{figure}[htb]
@@
 \end{equation}
-where $\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$th data stream, and $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inverse of $\mathbf{H}^{H}\mathbf{H}$.
+where $\varphi_{m}$ denotes the post processing signal to noise ratio of the $m$ th data stream, and $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$ denotes the diagonal elements of the inverse of $\mathbf{H}^{H}\mathbf{H}$.
 The post processing SNR depends only on $(\mathbf{H}^{H}\mathbf{H})_{mm}^{-1}$.
@@
 
-As mentioned in section \ref{programming model}, our implementation is based on the heterogeneous programming principle, employing a mix of CPU and GPU technology.
+As mentioned in section \ref{programming model}, our implementation is based on the heterogeneous programming principle, employing a mix of CPU and GPU technologies.
 The flow control and logical operations reside at the host side, while the compute intensive work is implemented at the device side.
-Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational intensive operations can be performed by the CUDA Basic Linear Algebra Subprograms (cuBLAS)\cite{nvidia2013basic} and corresponding GPU program implementations, as shown in Table \ref{table1}.
+Although the FCSD preprocessing has a serial nature and can not be vectorized, the computational intensive operations can be performed by the CUDA Basic Linear Algebra Subprograms (cuBLAS)\cite{nvidia2013basic} and the corresponding GPU program implementations, as shown in Table \ref{table1}.
 \begin{table*}[htb]
@@
 \hline
-Formula   &  $\mathbf{H}^{H}\mathbf{H}$ & $(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}y$ & $(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1} $ & $\mathbf{H}^{H}\mathbf{H}=\mathbf{R}^{H}\mathbf{R}$ 
-\\
+\multirow{2}{*}{Formula}   &  \multirow{2}{*}{$\mathbf{H}^{H}\mathbf{H}$} & \multirow{2}{*}{$(\mathbf{H}^{H}\mathbf{H})^{-1}\mathbf{H}^{H}\mathbf{y}$} & \multirow{2}{*}{$(\mathbf{H}_{j}^{H}\mathbf{H}_{j})^{-1} $} & \multirow{2}{*}{$\mathbf{H}^{H}\mathbf{H}=\mathbf{R}^{H}\mathbf{R}$} \\[10pt]
+
 \hline
@@
 \subsection{Parallel Acceleration of Paths Searching}
-Since the decision feedback searching paths have a serial nature, we match one path to one thread.
+Since the decision feedback searching paths has a serial nature, we match one path to one thread.
 In order to have the largest number of threads that can be parallelized, we use one dimensional blocks for widest expansion, and organize all the paths into several such blocks.
@@
 \centering
-\includegraphics[width=0.5\textwidth, height=5.1cm]{CUDA_FCSD_block_diagram.eps}
+\includegraphics[width=0.5\textwidth, height=5.5cm]{CUDA_FCSD_block_diagram.eps}
 \caption{Block Diagram of CUDA-FCSD Implementation}
@@
 \subsubsection{Data Preparation}\label{data preparation}
-There are three major factors that influence the configuration of the data sets in memory space.
+There are three major factors that influence the configuration of the data sets in memories.
 \begin{itemize}
@@
 Furthermore different memory types have different program scopes.
-Local memory, which is invoked in \textit{kernel} functions is valid only in one thread.
+Local memory (registers), which is invoked in \textit{kernel} functions, is valid only in one thread.
 Shared memory is valid in one block.
-Constant, texture and global memories are valid both at host side and device side.
-On the other hand different from global memory, the constant and share memory are all capacity limited.
+Constant and global memories are valid both at host side and device side.
+On the other hand, different from global memory, the constant and share memories are all capacity limited.
 Thus the memory occupancy is an important factor that needs to be considered.
@@
 The $M^{\rho}\times N_{t}$ complex matrix $\mathit{s_{pm}}$ that stores in each row one symbol vector candidate and its program scope should be during the whole \textit{kernel} execution.
-The matrix $\mathit{s_{index}}$ is used to store the index of all the possible sub-symbol vectors for  FE stage using the full factorial method and requires a $\rho\times M^{\rho}$  integer matrix space.
+The matrix $\mathit{s_{index}}$ is used to store the index of all the possible sub-symbol vectors for the FE stage using the full factorial method and requires a $\rho\times M^{\rho}$  integer matrix space.
 The $M^{\rho}$ dimensional floating point vector is used to store the Euclidean distance of all the symbol vector candidates.
@@
 Global memory access is implemented by a dynamic random access memory (DRAM) whose R/W is an extremely slow process.
-In a modern DRAM the R/W operations are performed by accessing a piece of consecutive memory location.
+In a modern DRAM the R/W operations are performed by accessing a piece of consecutive memory location during one cycle.
 As mentioned in section \ref{programming model}, the warp is the basic schedule unit of a device, and memory space is accessed warp by warp.
@@
 In Fig.
-\ref{coalesce global memory} we present the global access pattern of $\mathit{s_{pm}}$ as an example to illustrate global memory access pattern.
+\ref{coalesce global memory} we present the global access pattern of $\mathit{s_{pm}}$ as an example.
 \begin{figure}[htb]
@@
 
-The complex matrix $\mathit{s_{pm}}$ is stored in one piece of linear global memory, where each row represents one $N_{t}$ complex symbols solution candidates of $\mathbf{\hat{s}}^{F}$ in (\ref{formula 5}).
-There are $M^{\rho}$ rows, and this matrix is stored in column major (first column in the first piece of memory space and the second in the second piece of memory space etc.).
+The complex matrix $\mathit{s_{pm}}$ is stored in one piece of linear global memory, where each row represents one $N_{t}$ complex symbols solution candidates of $\mathbf{s}^{F}$.
+There are $M^{\rho}$ rows, and this matrix is stored in column major form (first column of the matrix stored in the first piece of memory space and the second in the second piece of memory space etc.).
 As mentioned before, one path searching is performed by one thread, and therefore the address distance between two consecutive symbols in one thread is $M^{\rho}$.
@@
 \ref{coalesce global memory}.
-Every 32 threads in one warp can confirm R/W operations to a piece of memory that is consecutive, and reduce DRAM access as much as possible resulting in a better memory bandwidth.
+Every 32 threads in one warp can consolidate R/W operations to a piece of memory that is consecutive, and reduce DRAM access as much as possible, resulting in a better memory bandwidth.
 
@@
 One solution to these problems is to employ partial parallelism.
-The detection task is divided into several \textit{kernel} executions, where for each, only one potential symbol vector solution, as well as its corresponding Euclidean distance are preserved.
+The detection task is divided into several \textit{kernel} executions, where for each only one potential symbol vector solution, as well as its corresponding Euclidean distance, are preserved.
 This allows the global memory space to be reused to avoid exceeding its limit.
@@
 \subsection{Performance Evaluation}
+
 \begin{table*}[htb]
@@
 \end{tabular}
+\quad\\[25pt]
 \label{speedup1}
@@
 \end{tabular}
+\quad\\[25pt]
 \label{speedup2}
 \end{table*}
+
 \begin{table*}[htb]
 \centering
+%\setlength{\belowcaptionskip}{5cm}
 \caption{Speedup Performance of Different MIMO Systems using 64 QAM}
@@
 \end{table*}
-Monte-Carlo simulations were conducted for MIMO systems of different sizes and signal constellation.
+Monte-Carlo simulations were conducted for MIMO systems of different sizes and signal constellations.
 In this work the speedup is defined as $\vartheta_{GPU}/\vartheta_{CPU}$, where $\vartheta_{GPU}$ and $\vartheta_{CPU}$ denotes the number of symbols detected on GPU and CPU per second.
-Comparison is made between the GeForce GTX 760 and two types of CPUs, with speedup performance presented in Tables \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
+Comparison is made between the GeForce GTX 760 and two types of CPUs, with speedup performances presented in Tables \ref{speedup1}, \ref{speedup2} and \ref{speedup3}.
 All the operation times correspond to $1000$ channel realizations.
@@
 From Table \ref{speedup1}, we see that for small MIMO systems of $8\times 8$, $16\times 16$, and $32\times 32$ with $4$QAM, the speed performance of GPU implementation is worse than that of CPU.
-The number of paths of these MIMO configurations that need to be searched is relatively small\footnote{$8\times 8$ MIMO system with $4$QAM has $16$ paths, $16\times 16$ MIMO system with $4$QAM has $64$ paths and $32\times 32$ MIMO system with $4$QAM has $1024$ paths}.
-The CPUs are designed for serial code execution with special hardware (branch prediction units, multiple caches, etc.) that provide extremely good performance, while the GPUs can achieve good performance only when they are utilized in a massive parallel manner.
-Furthermore there is a short time for GPU to "warm up", for host-device data transmission, \textit{kernel} function  launching and host device synchronization.
+This is because the number of paths of these MIMO configurations that need to be searched is relatively small ($8\times 8$ MIMO system with $4$QAM has $16$ paths, $16\times 16$ MIMO system with $4$QAM has $64$ paths and $32\times 32$ MIMO system with $4$QAM has $1024$ paths).
+Furthermore the CPUs are designed for serial code execution with special hardware (branch prediction units, multiple caches, etc.) that provide extremely good performance, while the GPUs can achieve good performance only when they are utilized in a massive parallel manner.
+Moreover there is a short time for GPU to "warm up", for host-device data transmission, \textit{kernel} function  launching and host device synchronization.
 When comes to larger MIMO systems of $48\times 48$, $64\times 64$, $72\times 72$, a large parallelism is achieved allowing the GPU to begin displaying its data processing power.
@@
 In Tables \ref{speedup2} and \ref{speedup3}, $16$QAM and $64$QAM are considered.
-We see that speedups larger than 1 can be achieved with GPU implementation also with smaller MIMO systems.
+We see that speedups larger than 1 can be achieved with GPU implementation also for smaller MIMO systems.
 For a $16\times 16$ system with $16$QAM modulation, GTX 760 provides a $1.18$ speedup over Modigliani and $1.57$ speedup over Monet.
 For a $16\times 16$ system with $64$QAM, GTX 760 provides a $4.41$ speedup over Modigliani and $5.73$ speedup over Monet.
-The nature of FCSD is such that for lager signal constellations, massive parallelism can be reached also for small MIMO systems that are not extremely large.
+This is because the nature of FCSD is such that for lager signal constellations, massive parallelism can be reached also for small MIMO systems that are not extremely large.
 
-It can be observed from Tables \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, that the GPU implementation shows its speed advantage over CPU implementation for increasing size of MIMO systems and signal constellations, indicating that GPUs provide advantages for large MIMO system with large signal constellations.
+It can be observed from Tables \ref{speedup1}, \ref{speedup2} and \ref{speedup3}, that the GPU implementation has an increasing speed advantage over CPU implementation when the size of MIMO systems and signal constellations increase, indicating that GPUs provide advantages for large MIMO system with large signal constellations.
 
@@
 \ref{BER curve} we present Monte Carlo simulation results for bit error rate (BER) performance, using the GPU implementation of different MIMO system configurations and constellation sizes.
-We consider uncoded complex MIMO systems with $M$ QAM, where each antenna transmits different streams of binary data generated randomly and independently.
+We consider uncoded complex MIMO systems with $M$QAM, where each antenna transmits different streams of binary data which are generated randomly and independently.
 The results have been obtained by using $10^{5}$ channel realizations with at least $500$ symbol errors accumulated.
-The simulation results show that FCSD-CUDA provides the same BER performance as its CPU version, due to the space limitation we do not present the results of CPU implementation, \cite{barbero2008fixing} provides some of the referable results.
+The simulation results show that our CUDA-FCSD provides the same BER performance as its CPU counterpart.
+Due to space limitation we do not present the results of the CPU implementation.
+The interested reader can consult \cite{barbero2008fixing} for more details.
 \begin{figure}[htb]
 \centering
-\includegraphics*[width=0.5\textwidth, height=10cm]{BER_curves.eps}
+\includegraphics*[width=0.5\textwidth, height=9.5cm]{BER_curves.eps}
 \caption{BER performance for MIMO systems with various modulation schemes using the GPU implementation}
@@
 \section{Conclusions}\label{conclusion}
-This paper presents a GPU implementation of the fixed complexity sphere decoder (FCSD) for large MIMO systems.
-In order to exploit the computational capability of GPU in the simulation of large MIMO systems, the utilization of a heterogeneous programming model, accounting for resource limitations and memory configuration must be considered.
-The simulation results show that significant accelerations of the GPU implementation of FCSD can be reached for large MIMO systems and signal constellation sizes over CPU implementation, while maintaining the same BER performance.
-Since the GPU and CPU can work independently, the data processing power of GPU computing is an additional advantages provided by the traditional simulation platforms.
+This paper presents a GPU implementation of a single fixed complexity sphere decoder (FCSD) for large MIMO  uplink systems.
+In order to exploit the computational capability of GPU in the simulation of large MIMO systems, the utilization of a heterogeneous programming method, accounting for resource limitations and memory configurations, must be considered.
+The simulation results show that significant accelerations of the GPU implementation of FCSD over CPU implementation can be\newline\newline\newline\newline\newline obtained for large MIMO systems and signal constellation sizes, while maintaining the same BER performance.
 This shows the potential of GPU computing to reduce the time associated with intensive simulations of large MIMO systems.
+Since the GPU and CPU can work independently, the data processing power of GPU computing is an additional advantage provided by the traditional simulation platforms.
 

### 2015-08-25 Lattice Reduction/CC_practice/src/CC_practice.c

@@ -1,0 +1,72 @@
+/*
+ ============================================================================
+ Name        : CC_practice.c
+ Author      : Tianpei Chen
+ Version     :
+ Copyright   : Your copyright notice
+ Description : Hello World in C, Ansi-style
+ ============================================================================
+ */
+#include <stdio.h>
+#include <math.h>
+#include <stdlib.h>
+#include <string.h>
+//#include <>
+int fix(float a){
+	int answer;
+	answer=(int)(a<0? (a+0.5): (a-0.5));
+	return answer;
+
+}
+
+
+void reverse1(char str[]){
+printf("the original string is %s\n", str);
+int count; //counter
+size_t length;
+length=strlen(str);
+char charTemp;
+int end=(int)((length-1)/2);
+printf("%d\n",end);
+for(count=0;count<=end;count++){
+	charTemp=str[count];
+	int first=count;
+	int last=(length-1)-count;
+	charTemp=str[first];
+	str[first]=str[last];
+	str[last]=charTemp;
+}
+printf("the reverse string is %s\n", str);
+}
+
+void reverse2(char *str){
+	printf("the original string is %s\n", str);
+	char *end, *strtmp, temp;
+	end=str;
+	strtmp=str;    //used to store the string pointer
+	while(*end){ //find the end of the string
+		++end;
+	}
+	--end;  //go back for one bit  because the last bit is NULL
+	/*swap the string elements*/
+	while(end>strtmp){
+		temp=*strtmp;
+		*strtmp++=*end;
+		*end--=temp;
+	}
+	// the pointer string is still point to the begining of the string
+	printf("the reverse string is %s\n", str);
+}
+
+
+
+int main(){
+	int fix(float a);
+	void reverse1(char str[]);
+	void reverse2(char *str);
+	char str1[8]="tianpei";
+	char *str2=str1;
+	reverse1(str1);
+	reverse2(str2);
+	return 0;
+}

### 2015-08-25 Lattice Reduction/LogExpectationOM.m

@@ -1,0 +1,16 @@
+%This programme visualize the logarithmic expectation of orthogonality
+%measure
+%Preston Chen
+%Feb/24/2015
+E=zeros(40,20);
+
+for Nt=1:5:100
+    for Nr=Nt:5:200
+        E((Nr-1)/5+1,(Nt-1)/5+1)=Nt*log(2)/log(exp(1))-Nt*psi(Nr);
+        for i=1:Nt
+        E((Nr-1)/5+1,(Nt-1)/5+1)=E((Nr-1)/5+1,(Nt-1)/5+1)+psi((Nr+1-i)/2);
+        end
+    end
+end
+figure (1)
+mesh(1:5:100,1:5:200,E),xlabel('Nt'),ylabel('Nr'),zlabel('Orthogonality Measurement');

### 2015-08-25 Lattice Reduction/src/common.h

@@ -1,0 +1,111 @@
+/*
+ * common.h
+ *
+ *  Created on: Sep 12, 2014
+ *      Author: tianpei.chen@mail.mcgill.ca
+ */
+
+#ifndef COMMON_H_
+#define COMMON_H_
+#include <gsl/gsl_vector.h>
+#include<gsl/gsl_matrix.h>
+#include<gsl/gsl_vector_complex.h>
+#include <gsl/gsl_vector_ulong.h>
+//#include<cuComplex.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include<string.h>
+#include <math.h>
+#include <gsl/gsl_rng.h>
+#include <time.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+#define MATRIX_SIZE_Nt 16
+#define MATRIX_SIZE_Nr 16
+#define IDC2D(i,j,row)    (i)*row+j
+#define Constellationsize 4
+void D_SLB_LR_MMSE(
+		gsl_vector_complex *preceived,
+		gsl_matrix_complex *pH,
+		double *SNR,
+		int Nr,
+		int Nt,
+		int M,
+		gsl_vector_complex *psymbolconstellation,
+		gsl_vector_complex *symOut
+		);
+//void FCSD_detection(
+//		cuComplex *sigRec,   //received signal vector
+//		cuComplex *pH,        //propagation matrix
+//		int Nt,             //number of transmit antennas
+//		int Nr,              //number of receive antennas
+//		int M,               //modulation scheme
+//		cuComplex *psymbolconstellation, //the symbol constellation
+//		float SNR,          //signal to noise ratio
+//		cuComplex *symOut,    //output symbol vector
+//		float *durationKernel
+//		);
+//void FCSD_decoding(
+//		cuComplex *d_R,  //upper triangular matrix after cholesky factorization store in device side
+////		cuComplex *s_sub, //the sub brute force rho vector matrix
+//		cuComplex *s_hat,  //unconstrained estimation of transmitted symbol vector s
+//		cuComplex *s_kernel,  //quantization of estimation ,decoding results
+////		cuComplex *Eu,  //Euclidean distance
+//		int Nt,    //the number of transmit antennas
+//		int Nr,    //the number of receive antennas
+//		int M,    //modulation scheme
+//		int *list,   //the permutation list
+//		cuComplex *psymbolconstellation //the symbol constellation
+//		);
[…]

### 2015-08-25 Lattice Reduction/src/communication_line.cpp

@@ -1,0 +1,450 @@
+/**
+ * Copyright 1993-2012 NVIDIA Corporation.  All rights reserved.
+ *
+ * Please refer to the NVIDIA end user license agreement (EULA) associated
+ * with this source code for terms and conditions that govern your use of
+ * this software. Any use, reproduction, disclosure, or distribution of
+ * this software and related documentation outside the terms of the EULA
+ * is strictly prohibited.
+ */
+/**
+ *This is the communication line performing the fixed complexity sphere decoding algorithm
+ * * This function implement a complete communication line including: data generation, modulation,
+ * channel generation, detection, decoding, print the result, speed and bit error rate
+ * Tianpei chen
+ * Email:tianpei.chen@mail.mcgill.ca
+ * 2014.08.19
+ * pdata: the transmitted gray data in decimal
+ * pgraycode: find the indexes of symbol according to graycode
+ * pgrayindex: find the graycode according to the indexes of the symbol
+ * pgraydata: find the indexes according to the pdata
+ * ptransmitted: find the complex symbol corresponding to he pgraydata
+ */
+#include <stdio.h>
+#include <stdlib.h>
+#include<string.h>
+#include <math.h>
+#include <gsl/gsl_rng.h>
+#include <time.h>
+#include <gsl/gsl_vector.h>
+#include <gsl/gsl_vector_ulong.h>
+#include <gsl/gsl_vector_int.h>
+#include <gsl/gsl_vector_complex.h>
+#include <gsl/gsl_complex.h>
+#include <gsl/gsl_complex_math.h>
+/*#include <gsl/gsl_matrix.h>*/
+#include <gsl/gsl_matrix_complex_float.h>
+#include <gsl/gsl_randist.h>
+/*#include <gsl/gsl_cblas.h>*/
+#include <gsl/gsl_blas.h>
+#include <gsl/gsl_linalg.h>
+#include <gsl/gsl_combination.h>
+#include <gsl/gsl_eigen.h>
+#include<gsl/gsl_math.h>
+#include<gsl/gsl_sort.h>
+#include<gsl/gsl_sort_vector.h>
+//#include<cuda_runtime.h>
+#include<assert.h>
+#include<time.h>
+#include"channel_generator.h"
[…]

### 2015-08-26 Report Aug 5 2015/Report Aug 2015.tex
Backup Aug 26 2015

@@
 \nonumber
-\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
+minimize \quad f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
 s.t. \left\{\begin{array}{ll}
@@
 \end{array}\right.
+\label{primal objective function}
 \end{eqnarray}
@@
 
-we construct dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier, we have dual optimization problem
+construct Lagrangian dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier,  dual optimization problem
 \begin{eqnarray}
 \nonumber
-\min_{\mathbf{w}, \xi, \hat{\xi}} \max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\theta=
+\min_{\alpha, \hat{\alpha}, \eta, \hat{\eta}, \mathbf{w}, \xi, \hat{\xi}}\Theta=
 \frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
@@
 \end{eqnarray}
-where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers, the solution of dual optimization problem is saddle point, from \cite{saddle point}, the dual problem of (\ref{lagrange duality1}) can be formulated as
-\begin{eqnarray}
-\nonumber
-\max_{\alpha, \hat{\alpha}, \eta, \hat{\eta}}\min_{\mathbf{w}, \xi, \hat{\xi}} \Theta=
-\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
-\nonumber
--\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\ 
-s.t. \left\{\begin{array}{cc}
-\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
-\xi, \hat{\xi}\geq  0\\
-\end{array}\right.\label{lagrange duality2}
-\end{eqnarray}
-Karush–Kuhn–Tucker (KKT) condition is satisfied or not \cite{} determines whether a non linear optimization problem find its optimal solution, the complementary KKT solution of (\ref{lagrange duality2}) is
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-\eta_{i}\xi_{i}=0\\
-\hat{\eta}_{i}\hat{\xi}_{i}=0\\
-\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))=0\\
-\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))=0\\
-\end{array}\right.
-\label{complementary KKT condition}
-\end{IEEEeqnarray}
-
-Take the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$, and find the minimum.
+where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers.
+
+According to Lagrangian Theorem \cite{Introduction to SVM}, the necessary condition to find the minimum of (\ref{primal objective function}) is the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$ equal to $0$,
 
@@
 \begin{equation}
-\frac{\partial \theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0
+\frac{\partial \Theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0
 \label{partial2}
@@
 \begin{equation}
-\frac{\partial \theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0
+\frac{\partial \Theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0
 \label{partial3}
@@
 \begin{equation}
-\frac{\partial \theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0
+\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0
 \label{partial4}
 \end{equation} 
-Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}), yields the final dual optimization objective function, for sake of brevity, we make $C_{i}$ uniform to all data samples ：
+Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}) and for sake of brevity, we make $C_{i}$ uniform to all data samples, we have the dual form ：
 \begin{eqnarray}
 \nonumber
-maximize\quad\Theta &=&\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
+\theta &=&\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
 \nonumber
@@
 \end{eqnarray}
-(\ref{dual objective function1}) can be simplified to 
+Thus $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, according to general Lagrange function\cite{introduction to SVM}, Lagrange duality with feasible solution always less or equal to original objective function, because inequality constraints is introduced.
+Therefore we have $\theta\leq \Theta \leq f(\mathbf{w})$, based on the lemma 5.16 of Lagrange theorem\cite{introduction of SVM}, the upper bound of $\theta$ is given by the minimal of $f(\mathbf{w})$, equality holds only when the optimal of $f(\mathbf{w})$ is obtained (property 5.19).
+Therefore the Lagrangian duality form can be written as 
 \begin{eqnarray}
@@
 \bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}[(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+2(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}]+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}](\delta-\hat{\delta})_{S}\\
--\epsilon(\delta+\hat{\delta})_{S}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S}](\delta-\hat{\delta})_{S}-\epsilon(\delta+\hat{\delta})_{S}
+-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S}](\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}
 \label{gain work set selection1}
@@
 \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon(\delta+\hat{\delta})_{S}
+\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}
 \label{gain work set selection2}
@@
  \begin{IEEEeqnarray}[\relax]{l}
-\nonumber
 \bigtriangledown \Theta^{r}_{ij}=\bigtriangledown \Theta^{r}_{i}+\bigtriangledown \Theta^{r}_{j}-(\delta_{i}-\hat{\delta}_{i})(\delta_{j}-\hat{\delta}_{j})\mathbf{K}^{r}_{ij},
@@
 \end{IEEEeqnarray}
+where $\bigtriangledown \Theta^{r}_{i}$, $\bigtriangledown \Theta^{r}_{j}$ denote gains of 1-D solver with $i$th and $j$th dual variable pairs are chosen. 
 \subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}
+From (\ref{gain of 2-D objective function1}), it is obviously that the gain of 2-D solver is a summation of the gain of 2 independent 1-D solver and a correlation term $(\delta_{i}+\hat{\delta}_{i})(\delta_{j}+\hat{\delta}_{j})\mathbf{K}^{r}_{ij}$.
+
+Obviously optimal 2-D coordinate combination ($i, j$) can be determined by comparing the gains of all the possibilities exhaustively, which requires $O(n^{2})$ times of searching.
+Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D solution by 1-D search approach, we will prove in large MIMO scenario, when $N_{t}$ is sufficient large, with channel hardening become effective, this approximation is very efficient.
+Here we propose two kinds of 1-D approximate searching strategy:\\
+1. 1-D searching without damping:\\
+do 1 time 1-D searching and calculate all the 1-D gain based on (\ref{gain of 1-D objective function}), then choose the coordinate pairs with first and second largest 1-D gain as the candidate.\\
+2. 1-D searching with damping:\\
+do 2 times 1-D searching, in the first round find dual variable pair $i$ that can maximize 1-D gain, then in the second round, find $j$th dual variable pair with the value of $i$th coordinate updated.
+
+From (\ref{gain of 2-D objective function1}), it can be easily interpreted the efficient of 1-D approximation approach is majorly determined by the approximation ratio $\frac{(\delta_{i}+\hat{\delta}_{i})(\delta_{j}+\hat{\delta}_{j})\mathbf{K}^{r}_{ij}}{\bigtriangledown \Theta^{r}_{i}+\bigtriangledown \Theta^{r}_{j}}$, hence we provide theoretical analyse from the view of channel hardening phenomenon, and give the upper bound of approximation ratio.
+Prior the theoretical analyse, we first investigate some mathematical properties of channel hardening.
+
 Recall (\ref{formula9})
@@
 \section{Stopping Criteria}\label{stopping criteria}
+As we have explained in section \ref{Introduce epsilon SVR}, the upper bound of Lagrangian dual objective function is determined by primal objective function further more the Lagrangian dual objective function equals to original objective function only when the optimal is found.
+Therefore, the gap between primal problem and dual problem is used to evaluate how is close is the current solution to global minimum.
+In our scenario, feasibility gap is employed as stopping criteria because of low computational cost and reliable performance.
+
+Based on the dual objective function in (\ref{final complex lagrange duality}) and the primal objective function in (\ref{complex objective function1}), based on the proposition of Lagrangian theorem
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+ -\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})+Im(\mathbf{y}^{T})(\beta-\hat{\beta})-\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})\\
++C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi_{i}^{r})+\tilde{R}(\hat{\xi}_{i}^{r})+\tilde{R}(\xi_{i}^{i})+\tilde{R}(\hat{\xi}_{i}^{i})] \leq \frac{1}{2}||\mathbf{W}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})]
+\label{duality gap1}
+\end{IEEEeqnarray}
+ where $\mathbf{W}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}$. The duality gap can be obtained by 
+ \begin{IEEEeqnarray}[\relax]{l}
+ \nonumber
+ G(\alpha, \hat{\alpha}, \beta, \hat{\beta})=\frac{1}{2}||\mathbf{W}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})]-\{-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})\\
+\nonumber 
+ -\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})+Im(\mathbf{y}^{T})(\beta-\hat{\beta})-\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi_{i}^{r})+\tilde{R}(\hat{\xi}_{i}^{r})\\
+ \nonumber
+ +\tilde{R}(\xi_{i}^{i})+\tilde{R}(\hat{\xi}_{i}^{i})]\}=(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha}) +(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})-Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})-Im(\mathbf{y}^{T})(\beta-\hat{\beta})+\\
+ \epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{i}(\beta-\hat{\beta})+C\sum_{i=1}^{N_{r}}[\xi_{i}^{r}R^{'}(\xi_{i}^{r})+\hat{\xi}_{i}^{r}R^{'}(\hat{\xi}_{i}^{r})+\xi_{i}^{i}R^{'}(\xi_{i}^{i})+\hat{\xi}_{i}^{i}R^{'}(\hat{\xi}_{i}^{i})]
+ \label{duality gap2}
+ \end{IEEEeqnarray}
+Because the noise is white Gaussian, therefore the optimal risk function is 
+$R(\xi)=\frac{1}{2}\xi^{2}$, $\xi$ is the slack variable, hence 
+\begin{equation}
+\xi R^{'}(\xi)=\xi^{2},
+\label{risk functional1}
+\end{equation} 
+\begin{equation}
+\xi_{i}^{r}(\hat{\xi}^{r})=\max(0, |Re(y_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon),
+\label{risk functional2}
+\end{equation}
+Because $\xi^{r}\hat{\xi}^{r}=0$ (estimation can only exceed $\epsilon$ tube in one direction), therefore there is only one of $\xi$ and $\hat{\xi}$ need to be considered, notice $Re(y_{i})-Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi_{i}^{r}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}$ and $Im(y_{i})-Im(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi_{i}^{i}-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}$ hence the last term in (\ref{duality gap2}) can be rewritten as
+\begin{equation}
+C\sum_{i=1}^{N_{r}}((|\Phi_{i}^{r}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon}+(|\Phi_{i}^{i}-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon})
+\label{risk functional3}
+\end{equation}
+where $()_{\epsilon}$ denotes $\epsilon$ insensitive function.
+duality gap in (\ref{duality gap2}) can be divided into two part
+\begin{equation}
+G(\alpha, \hat{\alpha}, \beta, \hat{\beta})=L(\alpha, \hat{\alpha}, \beta, \hat{\beta})+S(\alpha, \hat{\alpha}, \beta, \hat{\beta}),
+\label{divide duality gap}
+\end{equation}
+where 
+\begin{equation}
+L(\alpha, \hat{\alpha}, \beta, \hat{\beta})=(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha}) +(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})-Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})-Im(\mathbf{y}^{T})(\beta-\hat{\beta})+\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})，
+\label{L sub function}
+\end{equation}
+
+\begin{equation}
+S(\alpha, \hat{\alpha}, \beta, \hat{\beta})=C\sum_{i=1}^{N_{r}}((|\Phi_{i}^{r}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon}+(|\Phi_{i}^{i}-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon})-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{i}(\beta-\hat{\beta})
+\label{S sub function}
+\end{equation}
 \section{Hyperparameter Setting}
+
 \section{Computer Simulations}

### 2015-09-04 Report Aug 5 2015/Report Aug 2015.tex
write a simple real SVR on matlab
modified matlab code for real SVR
modification of matlab and C code

@@
 \input{epsilon-SVR.pdf_tex}
-\caption{}
+\caption{$\epsilon$-Support Vector Regression and Risk Functional}
 \label{epsilon-SVR}
@@
 \nonumber
-maximize \quad \Theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})-\tilde{R}(\hat{\xi}^{r})))\\
+maximize \quad \Theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r})))\\
 \left\{\begin{array}{ll}
@@
 \nonumber
-maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})-\tilde{R}(\hat{\xi}^{i})))\\
+maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})+\tilde{R}(\hat{\xi}^{i})))\\
 \left\{\begin{array}{ll}
@@
 \epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{S})
--\frac{1}{2}(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NN}^{r}(\alpha-\hat{\alpha})_{N}+Re(\mathbf{y})_{N}^{T}(\alpha-\hat{\alpha})_{N}-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{N})\\+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})-\tilde{R}(\hat{\xi}^{r}))),
+-\frac{1}{2}(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NN}^{r}(\alpha-\hat{\alpha})_{N}+Re(\mathbf{y})_{N}^{T}(\alpha-\hat{\alpha})_{N}-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{N})\\+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r}))),
 \label{real part decomposition}
@@
 \mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
-\end{IEEEeqnarraybox*}\right]$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$
-and  $\alpha_{S}\in \mathbb{R}^{N_{r}}$ denotes the vector with the components that do not belong to $S$ zeroed. Therefore the sub-optimization problem is formulated as 
+\end{IEEEeqnarraybox*}\right]$ is a permutation of $\mathbf{K}^{r}$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$ 
+and  $\alpha_{S}\in \mathbb{R}^{N_{r}}$ denotes the vector with the components that do not belong to $S$ zeroed.
+In each iteration, in (\ref{real part decomposition}), $\alpha_{N}$ is fixed and only the sub problem that correlated to $\alpha_{S}$ is solved i.e
 \begin{equation}
@@
 \begin{equation}
-maximize\quad \bigtriangledown \Theta_{S}=\Theta((\alpha+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta(\alpha, \hat{\alpha}),
+maximize\quad \bigtriangledown \Theta_{S}=\Theta_{S}((\alpha_{S}+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}_{s}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta_{S}(\alpha_{S}, \hat{\alpha}_{S}),
 \label{maximum gain work set selection}
@@
 \end{IEEEeqnarray} 
-In our regression model, the offset is omitted, therefore different from SMO type algorithms, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration.
+The offset term is omitted in Large MIMO system, therefore different from SMO type algorithms, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration.
 However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{Training without offset}.
-Here we propose sequential 1-D work set selection, which can approximate the effect of optimal 2-D work set selection.
-There is only $O(n)$ searching times required for the former one while the later one need $O(n^{2})$ searching times.
+Here we propose sequential 1-D work set selection strategy, which can approximate the performance of optimal 2-D work set selection, while only $O(n)$ searching times required for the former one instead of $O(n^{2})$ searching times.
 \subsection{Single Direction Solver}

### 2015-09-04 SVR for large MIMO/real SVR matlab/real_SVR_WSSS1D_2Dsolver.m

@@ -24,15 +24,16 @@ lamida=zeros(Nr,1);
 Phi=y; %intermediate variable
 G=[]; %duality gap
 G(1)=0;
+Theta(1)=0;
 for count=1:Nr
 
     if(abs(Phi(count))>epsilon)
-    G(1)=G(1)+(abs(Phi(count))-epsilon)^2;
+    Theta(1)=Theta(1)+(abs(Phi(count))-epsilon)^2;
     end
 end
-G(1)=G(1)*C;
-G(1)=1;
-Theta(1)=0;
+Theta(1)=-0.5*Theta(1)*C;
+G(1)=-2*Theta(1);
+G(1)=G(1)/abs(G(1)+Theta(1));
 %% update lamida
 
 iteration=1;
@@ -45,6 +46,18 @@ NoiseTerm=0;
 for count=1:Nr
     lamida_tmp1=lamida(count)+(Phi(count)-epsilon*(-1))/K(count,count);
     lamida_tmp2=lamida(count)+(Phi(count)-epsilon*(1))/K(count,count);
+        %clipping
+    if(lamida_tmp1<-C)
+        lamida_tmp1=-C;
+    elseif(lamida_tmp1>C)
+        lamida_tmp1=C;
+    end
+        %clipping
+    if(lamida_tmp2<-C)
+        lamida_tmp2=-C;
+    elseif(lamida_tmp2>C)
+        lamida_tmp2=C;
+    end
     delta1=(lamida_tmp1-lamida(count))*((-1/2)*(lamida_tmp1-lamida(count))*K(count,count)+Phi(count))-epsilon*(abs(lamida_tmp1)-abs(lamida(count)));
     delta2=(lamida_tmp2-lamida(count))*((-1/2)*(lamida_tmp2-lamida(count))*K(count,count)+Phi(count))-epsilon*(abs(lamida_tmp2)-abs(lamida(count)));
     if(delta1>delta2)
@@ -55,12 +68,7 @@ for count=1:Nr
         delta(count)=delta2;
         lamida_tmp=lamida_tmp2;
     end
-    %clipping
-    if(lamida_tmp<-C)
-        lamida_tmp=-C;
-    elseif(lamida_tmp>C)
-        lamida_tmp=C;
-    end
+
     sigma_tmp(count)=lamida_tmp-lamida(count);
 end
 %bubble sorting
@@ -96,7 +104,7 @@ end
     
 
 
-%% update lamida, Phi, Theta and duality gap
[…]

### 2015-09-07 Report Aug 5 2015/Report Aug 2015.tex
modified C code and report

@@
 \documentclass[12pt, draftclsnofoot, onecolumn]{IEEEtran}
-%
+%\documentclass[12pt,paper,final]{article}
+%
+%\documentclass[12pt, onecolummn]{report}
 % If IEEEtran.cls has not been installed into the LaTeX system files,
@@
 \usepackage[cmex10]{amsmath}
-\usepackage{algorithmic}
+\usepackage{algorithm}
 \usepackage{array}
@@
 \usepackage{subfigure}
+\usepackage{algpseudocode}
 
@@
 %
-\usepackage{algorithmic}
+%\usepackage{algorithmic}
 % algorithmic.sty was written by Peter Williams and Rogerio Brito.
@@
 \begin{document}
-
+%\begin{spacing}{8}
 %
@@
 
-%\begin{spacing}{2.5}
-
 \section{Introduction}
@@
 %\hfill September 17, 2014
-Decoder is one of the key components of Multiple-Input Multiple-Output (MIMO) systems. Designing of high performance and low complexity detector has become a bottleneck of Large MIMO systems.
+  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) and the limited radio frequency spectrum over a complex space-time varying environment.
+As the most promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years and become mature, which is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} long-term evolution (LTE)\cite{3GLTE}.
+The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve bandwidth efficiency) and diversity gain (better reliability of communication link) is obtained by employing spatial domain.
+Large MIMO (also called Massive MIMO) is an upgrade version of conventional MIMO system, it equips   unprecedentedly hundreds of low power low price antennas at base station (BS), serving several tens of terminals simultaneously, It can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness\cite{rusek2013scaling}\cite{larsson2014massive}.
+
+  The price paid for large MIMO system is the increasing complexities for signal processing at both transmitting and receiving end.
+Uplink Detector is one of the key components in large MIMO system.
+With orders magnitude more antennas equipped at BS, benefit and challenge coexist in designing of detection algorithms for large MIMO uplink, on the one hand, large number of receive antennas provide potential of large diversity gain, on the other hand, complexity of the algorithm becomes extremely crucial to make system practical.
+
+The optimal maximum likelihood detector (MLD) for MIMO system requires the complexity increase exponentially with number of transmitted antennas with a factor of the size of size of constellation, which is prohibitive in practical implementations.
+Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes lattice structure of MIMO system. 
+Its variant fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} make it possible to achieve near optimal performance with a fixed complexity under different signal to noise ratio (SNR).
+However, all the algorithms that based on lattice structure have the same shortage - their complexities increases exponentially with a factor of the size of symbol constellation.
+Therefore, they are prohibitive when it comes to a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.
+
+Suboptimal linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, which have good performance for low loading factor in massive MIMO system (that is the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
+In the last several years, a set of detection algorithms are proposed with complexities that is comparable with LD-OSIC and suboptimal performance can be achieved.
+The local search algorithm, such as likelihood ascend searching (LAS)\cite{vardhan2008low}\cite{li2010multiple}, an theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was presented\cite{sunfamily}.
+Layered Tabu search algorithm presented in\cite{srinidhi2011layered} is superior to the LAS algorithms because it can move away to new searching area to avoid local minimal.
+Message passing detectors based on belief propagation (BF) and Gaussian Approximation (GA) \cite{goldberger2011mimo}\cite{som2011low}\cite{narasimhan2014channel}\cite{som2010improved}.
+Markov Chain Monte Carlo algorithm\cite{datta2013novel}  and Lattice Reduction aided detectors\cite{zhou2013element}.
 
@@
 \section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
+\subsection{Regression Model}
 Suppose we are given training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{l},y_{l}))$, $l$ denotes the number of training samples, $\mathbf{x}\in \mathbb{R}^{v}$ denotes input data vector, $v$ is the number of features in $\mathbf{x}$.
@@
 $\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function.
-$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes cost function, the simplest cost function is $R(x)=x$, risk function is determined by the statistical distribution of noise \cite{A tutorial of Support Vector Regression}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
+$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes risk function, the simplest risk function is $R(x)=x$, risk function is determined by the statistical distribution of noise \cite{A tutorial of Support Vector Regression}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
 $C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
-
+\subsection{Risk Functional}
 From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
@@
 where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered, we arrive to at a convex minimization problem \cite{smola and skpkof 1998a tutorial of SVR}. 
-
-construct Lagrangian dual form of (\ref{primal optimization problem}) by introducing Lagrange multiplier,  dual optimization problem
+\subsection{Lagrange Duality}
+According to Lagrange Theorem, the optimization problem (\ref{primal objective function}) can be transferred to dual form by combining original objective function with linear combination of equality and inequality constraints, the combination coefficient is called Lagrange multiplier.
+Thus we have Lagrange function.
 \begin{eqnarray}
 \nonumber
-\min_{\alpha, \hat{\alpha}, \eta, \hat{\eta}, \mathbf{w}, \xi, \hat{\xi}}\Theta=
+\Theta(\mathbf{w}, b, \xi, \hat{\xi}, \alpha, \hat{\alpha}, \eta, \hat{\eta})=
 \frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
@@
 
-According to Lagrangian Theorem \cite{Introduction to SVM}, the necessary condition to find the minimum of (\ref{primal objective function}) is the partial derivative of $\Theta$ with respect to $\mathbf{w}$, $\xi$, $\hat{\xi}$ and $b$ equal to $0$,
-
-\begin{equation}
-\frac{\partial \theta}{\partial \mathbf{w}}=w-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})
-\label{partial1}
-\end{equation}
-
-\begin{equation}
-\frac{\partial \Theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0
-\label{partial2}
-\end{equation}
-
-\begin{equation}
-\frac{\partial \Theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0
-\label{partial3}
-\end{equation}
-
-\begin{equation}
-\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0
+The sufficient and necessary condition that $f(\mathbf{w}^{*})$ is the global minimum of (\ref{primal objective function}) is called Karush Kuhn Tucker conditions, which can be written as 
+\begin{IEEEeqnarray}[\relax]{l}
+\frac{\partial \Theta}{\partial \mathbf{w}}=w-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\\\label{partial1}
+\frac{\partial \Theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0\\\label{partial2}
+\frac{\partial \Theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\\\label{parial3}
+\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\
 \label{partial4}
-\end{equation} 
+\left\{\begin{array}{cc}
+\alpha, \hat{\alpha}\geq 0\\
+\alpha(y-\mathbf{w}^{T}\Phi(\mathbf{x})-b-\epsilon-\xi)=0\\
+\hat{\alpha}(\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi})=0
+\end{array}\right. \label{KKT complimentary}
+\end{IEEEeqnarray}
+
+The conditions in (\ref{KKT complimentary}) is called KKT complimentary condition.
 Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}) and for sake of brevity, we make $C_{i}$ uniform to all data samples, we have the dual form ：
-\begin{eqnarray}
-\nonumber
-\theta &=&\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
-\nonumber
-&+&(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\theta(\alpha, \hat{\alpha}) =\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
+\nonumber
++(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
 +\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
 \nonumber
-&-&\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
-&s.t.&\left\{\begin{array}{l}
+-\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
+s.t.\left\{\begin{array}{l}
 \sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
@@
 \label{dual objective function1}
-\end{eqnarray}
-Thus $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, according to general Lagrange function\cite{introduction to SVM}, Lagrange duality with feasible solution always less or equal to original objective function, because inequality constraints is introduced.
-Therefore we have $\theta\leq \Theta \leq f(\mathbf{w})$, based on the lemma 5.16 of Lagrange theorem\cite{introduction of SVM}, the upper bound of $\theta$ is given by the minimal of $f(\mathbf{w})$, equality holds only when the optimal of $f(\mathbf{w})$ is obtained (property 5.19).
-Therefore the Lagrangian duality form can be written as 
-\begin{eqnarray}
-\nonumber
-maximize\quad \Theta &=&-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
-\nonumber
-&+&C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
-&=&-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
+\end{IEEEeqnarray}
+Obviously $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, Because 
+\begin{equation}
+\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
+\end{equation} 
+where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
+\begin{IEEEeqnarray}[\relax]{l}
+g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
+\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
+l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
+\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
+\end{IEEEeqnarray}
+Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$.
+when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied.
+hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds.
+Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.
+
+In conclusion, the dual objective function can be written as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize\quad \Theta =-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
+\nonumber
++C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
+=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
 \label{dual optimization function2}
-\end{eqnarray}
+\end{IEEEeqnarray}
 where $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{l}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{l}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{l}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{l}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0,  $\tilde{R}(\xi)=R(\xi)-\xi R^{'}(\xi)\in \mathbb{R}^{l}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes data kernel matrix.
@@
 $\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2l}$, 
-\begin{eqnarray}
+\begin{IEEEeqnarray}[\relax]{l}
 \mathbf{v}_{i}=\left\{\begin{array}{ll}
@@
 \end{array}\right.
-\end{eqnarray}
-(\ref{dual optimization function2}) can be reformulate as 
+\end{IEEEeqnarray}
+(\ref{dual optimization function2}) can also be reformulate as 
 \newcommand{\mysmallarraydecl}{\renewcommand{%
@@
 \nonumber
--(\alpha_{1}-\hat{\alpha}_{1})\mathbf{K}^{r}_{11}+Re(y_{1})-\sum_{j\neq 1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{1j}-\epsilon\\
+-(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}^{r}_{11}+Re(y_{1})-\sum_{j\neq 1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{1j}-\epsilon=-(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}^{r}_{11}+\Phi_{1}+(\alpha_{1}-\hat{\alpha}_{1})\mathbf{K}^{r}_{11}-\epsilon\\
 \Rightarrow \alpha^{new}_{1}=\alpha_{1}+\frac{(\Phi^{r}_{1}-\epsilon)}{\mathbf{K}^{r}_{11}},
@@
 where $\bigtriangledown \Theta^{r}_{i}$, $\bigtriangledown \Theta^{r}_{j}$ denote gains of 1-D solver with $i$th and $j$th dual variable pairs are chosen. 
-\subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}
+\subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
 From (\ref{gain of 2-D objective function1}), it is obviously that the gain of 2-D solver is a summation of the gain of 2 independent 1-D solver and a correlation term $(\delta_{i}+\hat{\delta}_{i})(\delta_{j}+\hat{\delta}_{j})\mathbf{K}^{r}_{ij}$.
@@
 
-Recall (\ref{formula9})
-\begin{equation}
-\phi_{om}=\prod_{i=1}^{N_{t}}\frac{|r_{ii}|^{2}}{|r_{ii}|^{2}+\sum_{j<i}|r_{ji}|^{2}}.
-\end{equation}
-All the components in $\mathbf{R}$ are independently distributed and $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma(N_{r}-i+1,1)$ \cite{nagar2011expectations}.
-Because $|r_{ji}|\sim Rayleigh(1/\sqrt{2})$, $\sum_{j<i}|r_{ji}|^{2}\sim Gamma(i-1, 1)$.
-Defining $\alpha_{i}=\sum_{j<i}|r_{ji}|^{2}$ and $\beta_{i}=|r_{ii}|^{2}$, $\alpha_{i}$ and $\beta_{i}$ are mutually independent, therefore (\ref{formula9}) can be rewritten as
-\begin{equation}
-\phi_{om}=\prod_{i=1}^{N_{t}}\frac{\beta_{i}}{\beta_{i}+\alpha_{i}},
-\label{formula21}
-\end{equation}
-From \cite{gupta2004handbook}, if $X\sim Gamma(k_{1},\theta)$ and $Y\sim Gamma(k_{2},\theta)$, then $\frac{X}{X+Y}\sim B(k_{1},k_{2})$, where $B$ denotes Beta distribution.
-Therefore $\frac{\beta_{i}}{\beta_{i}+\alpha_{i}}\sim B(k^{i}_{1}, k^{i}_{2})$, where $k^{i}_{1}=N_{r}-i+1$, $k^{i}_{2}=i-1$.
-we define $\eta_{i}=\frac{\beta_{i}}{\beta_{i}+\alpha_{i}}$, it is obvious that $\eta_{i}$ are independently distributed.
-Based on (\ref{formula21}), we have
-\begin{equation}
-\phi_{om}=\prod_{i=1}^{N_{t}}\eta_{i}.
-\label{formula22}
-\end{equation}
-Therefore the density function of $\phi_{om}$ can be defined as
-\begin{equation}
-f_{\phi_{om}}(x)=\frac{1}{x}\sum_{\mathbf{j}}(\prod_{i=1}^{N_{t}}c(k_{1}^{i}k,k_{2}^{i},j^{i}))f(-\ln(x)|\mathbf{k_{1}}+\mathbf{j}), 
-\label{formula23}
-\end{equation}
-where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{N_{t}}}$, the range of $j^{i}\in [0, k_{2}^{i}-1]$, $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
-$f(-\ln(x)|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp((k_{1}^{i}+j^{i})\ln(x))/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$.
-$\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1},\cdots k_{1}^{N_{t}-1}+j^{N_{t}-1},k_{1}^{N_{t}}+j^{N_{t}}]$.
-Proof: see Appendix C.
-
-Consider logarithmic expectation of $\phi_{om}$, we have
-\begin{equation}
-E[\ln(\phi_{om})]=\sum_{i=1}^{N_{t}}E[\ln(\eta_{i})],
-\label{formula24}
-\end{equation}
-where $E[\ln(\eta_{i})]=\psi(k^{i}_{1})-\psi(k^{i}_{1}+k^{i}_{2})$, thus we have 
-\begin{equation}
-E[\ln(\phi_{om})]=\sum_{i=1}^{N_{t}}\psi(N_{r}-i+1)-N_{t}\psi(N_{r}).
-\label{formula25}
-\end{equation}
-we can find (\ref{formula25}) is consistent with (\ref{formula15}).
+ Based on the complimentary KKT conditions, we have $\alpha\hat{\alpha}=0$, therefore we transform (\ref{subset optimization}) and (\ref{gain work set selection2}) by substituting $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, hence we have
+\begin{equation}
+maximize\quad \Theta_{S}^{r}=-\frac{1}{2}\lambda_{S}^{T}\mathbf{K}_{SS}^{r}\lambda_{S}+(Re(\mathbf{y})_{S}^{T}-\lambda_{N}^{T}\mathbf{K}_{NS}^{r}
+)\lambda_{S}-\epsilon(\mathbf{e}_{S}^{T}|\lambda_{s}|),
+\label{simplified subset optimization}
+\end{equation}
+
+\begin{IEEEeqnarray}[\relax]{l}
+\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}\tau^{T}_{S}\mathbf{K}^{r}_{SS}\tau_{S}+(\Phi^{r}_{S})^{T}\tau_{S}-\epsilon\mathbf{e}^{T}_{S}(|\lambda|^{new}-|\lambda|)_{S},
+\label{simplified gain work set selection}
+\end{IEEEeqnarray}
+where $\tau=\lambda^{new}-\lambda$. 
+Therefore we can simplify the work set selection procedure by update variables $\lambda$ rather than dual variable pairs
+For single direction solver, (\ref{optimization function 1-D}) can be transformed as 
+\begin{IEEEeqnarray}[\relax]{l}
+ maximize\quad \Theta_{1}^{r}=-\frac{1}{2}(\lambda_{1}^{new})^{2}\mathbf{K}_{11}^{r}-(\lambda_{1})^{new}\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}\lambda_{j}
++Re(y_{1})\lambda_{1}^{new}-\epsilon|\lambda_{1}|^{new},
+ \label{simplified optimization function 1-D}
+ \end{IEEEeqnarray}
+Thus for 1-D solver the gradient of (\ref{simplified optimization function 1-D}) with respect to $\lambda$ can be written as
+\begin{equation}
+\lambda_{1}^{new}=\lambda_{1}+\frac{\Phi_{1}-sgn(\lambda_{1}^{new})\epsilon}{\mathbf{K}^{r}_{11}},
+\label{gradient lambda}
+\end{equation}
+where $\frac{\partial |\lambda^{new}_{1}|}{\partial \lambda_{1}^{new}}=sgn(\lambda_{1}^{new})$
+the similar principle can be also applied to double direction solver.
+Because in the update process the $sgn(\lambda^{new})$ is unknown to old parameter values , therefore, we need to consider both the case $sgn(\lambda^{new})=-1 $ or $1$ and choose the one with the larger objective function gain $\bigtriangledown \Theta^{r}_{S}$.
+Here we give the pseudo code for sequential approximate optimal double direction solver.
+
+\begin{algorithm}
+\begin{algorithmic}
+\Procedure{CSVD}{$\mathbf{y}$,$\mathbf{H}$}
+\State Step 1. Initialization
+\For{$i=1:N_{r}$}\Comment{initialize $\lambda^{r}$, $\lambda^{i}$, $\Phi^{r}$, $\Phi^{i}$, $\Psi^{r}$, $\Psi^{i}$ and duality gap $G$}
+\State $\lambda_{i}^{r}=0, \lambda_{i}^{i}=0$
+\State $\Phi_{i}^{r}=Re(y_{i}), \Phi_{i}^{i}=Im(y_{i})$
+\State $\Psi_{i}^{r}=0, \Psi_{i}^{i}=0$
+\EndFor 
+\State  Step 2. if $G>tol$, go to step 3, else go to Step 6
+\State Step 3.
+\State Sequential 2-D solver with or without damping \Comment{find two dual variables to be updated} 
+\State Step 4.
+\State  $G$
+\State Step 5.
+\State $\tilde{x}=(\lambda^{r}+i\lambda^{i})\mathbf{H}$ \Comment{reconstruct $\mathbf{x}$}
+\State $\mathbf{x}=\mathbb{Q}(\tilde{x})$\Comment{$\mathbb{Q}(\cdot)$ denotes quantization operation based on symbol constellation}
+\State go back to Step 2
+\State Step 6. \textbf{Return} $\mathbf{x}$
+
+\EndProcedure
+\end{algorithmic}
+\label{CSVD algorithm}
+\caption{Dual Channel Complex Support Vector Detection Algorithm }
+\end{algorithm}
+
+\begin{algorithm}
+\begin{algorithmic}
+\Procedure{Sequential 2-D solver without Damping}{$1st$, $2nd$} 
+\For{$i=1:N_{r}$}
+\State update $\lambda^{r}_{i}(\lambda_{i}^{i})$ by single direction solver
+\State calculate $\bigtriangledown \theta^{r}_{i}(\bigtriangledown \theta_{i}^{i})$\Comment{ calculate the gain of sub objective function}
+\EndFor
+\State choose the dual variable with first and the second largest gain of sub objective function, denoted as 1st and 2nd
+\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to 1st and 2nd
+\State \textbf{Return} 1st, 2nd
+\EndProcedure
+\end{algorithmic}
+\caption{Sequential 2-D Solver without Damping}
+\label{1D2D Nodamping}
+\end{algorithm}
+
+ \begin{algorithm}
+\begin{algorithmic}
+\Procedure{Sequential 2-D solver with Damping}{$1s_{1}t$,$1st_{2}$}
+\For{$i=1:N_{r}$}\Comment{First round searching}
+\State update $\lambda_{i}^{r}(\lambda_{i}^{i})$ by single direction solver
+\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{calculate the gain of objective function}
+\EndFor
+\State choose the dual variable with the largest gain of objective function as $1st_{1}$
+\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to $1st_{1}$
+\For{$i=1:N_{r}$} \Comment{Second round searching}
+\State update $\lambda_{i}^{r}(\lambda_{i}^{i})$ by single direction solver
+\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{calculate the gain of objective function}
+\EndFor
+\State choose the dual variable with the largest gain of objective function as $1st_{2}$
+\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to $1st_{2}$
+\State \textbf{Return} $1st_{1}$ and $1st_{2}$
+\EndProcedure
+\end{algorithmic}
+\caption{Sequential 2-D Solver with Damping}
+\label{1D2D damping}
+\end{algorithm}
 
@@
 \appendices
-\section{Proof of the First Zonklar Equation}
+%\section{Proof of the First Zonklar Equation}
 Appendix one text goes here.
@@
 %\end{spacing}
+
 \newpage

### 2015-09-08 Report Aug 5 2015/Report Aug 2015.tex

@@
 \begin{document}
-%\begin{spacing}{8}
+\begin{spacing}{2}
+%\doublespacing
 %
@@
 $C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
-\subsection{Risk Functional}
+\subsection{Risk Functional}\label{risk functional}
 From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
@@
 \begin{equation}
-minimize\quad \lambda||w||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),
+minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),
 \label{total cost function}
@@
 \begin{equation}
-minimize \quad \frac{1}{2}||w||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
+minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
 \label{final cost function}
@@
 where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered, we arrive to at a convex minimization problem \cite{smola and skpkof 1998a tutorial of SVR}. 
-\subsection{Lagrange Duality}
+\subsection{Lagrange Duality}\label{section lagrange duality}
 According to Lagrange Theorem, the optimization problem (\ref{primal objective function}) can be transferred to dual form by combining original objective function with linear combination of equality and inequality constraints, the combination coefficient is called Lagrange multiplier.
@@
 
-The sufficient and necessary condition that $f(\mathbf{w}^{*})$ is the global minimum of (\ref{primal objective function}) is called Karush Kuhn Tucker conditions, which can be written as 
-\begin{IEEEeqnarray}[\relax]{l}
-\frac{\partial \Theta}{\partial \mathbf{w}}=w-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\\\label{partial1}
+The sufficient and necessary condition that $f(\mathbf{w}^{*})$ is the global minimum of (\ref{primal objective function}) is called Karush-Kuhn-Tucker (KKT) conditions, which can be written as 
+\begin{IEEEeqnarray}[\relax]{l}
+\frac{\partial \Theta}{\partial \mathbf{w}}=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\\label{partial1}
 \frac{\partial \Theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0\\\label{partial2}
 \frac{\partial \Theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\\\label{parial3}
-\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\
-\label{partial4}
+\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\label{partial4}
+\nonumber
+\end{IEEEeqnarray}
+\begin{IEEEeqnarray}[\relax]{l}
 \left\{\begin{array}{cc}
@@
 \hat{\alpha}(\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi})=0
-\end{array}\right. \label{KKT complimentary}
+\end{array}\right. 
+\label{KKT complimentary}
 \end{IEEEeqnarray}
@@
 The conditions in (\ref{KKT complimentary}) is called KKT complimentary condition.
-Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality2}) and for sake of brevity, we make $C_{i}$ uniform to all data samples, we have the dual form ：
+Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}) and for sake of brevity, we make $C_{i}$ uniform to all data samples, we have the dual form of objective function ：
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-Obviously $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, Because 
+Obviously $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, notice now (\ref{partial1})-(\ref{partial4})are satisfied, therefore, KKT complimentary condition (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
+Because
 \begin{equation}
@@
 \hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
+\nonumber
 \end{IEEEeqnarray}
@@
 \nonumber
-maximize\quad \Theta =-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
+maximize\quad \theta =-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
 \nonumber
@@
 \begin{equation}
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{K}^{r}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{K}^{r}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta-\hat{\beta}_{i})\mathbf{K}^{i}_{ij}.
+||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{K}^{r}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{K}^{r}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}.
 \label{complex duality regularization2}
@@
 \nonumber
-maximize\quad \Theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
+maximize\quad \theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
 \nonumber
@@
 \section{Stopping Criteria}\label{stopping criteria}
-As we have explained in section \ref{Introduce epsilon SVR}, the upper bound of Lagrangian dual objective function is determined by primal objective function further more the Lagrangian dual objective function equals to original objective function only when the optimal is found.
-Therefore, the gap between primal problem and dual problem is used to evaluate how is close is the current solution to global minimum.
-In our scenario, feasibility gap is employed as stopping criteria because of low computational cost and reliable performance.
-
-  Based on the dual objective function in (\ref{final complex lagrange duality}) and the primal objective function in (\ref{complex objective function1}), based on the proposition of Lagrangian theorem
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
- -\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})+Im(\mathbf{y}^{T})(\beta-\hat{\beta})-\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})\\
-+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi_{i}^{r})+\tilde{R}(\hat{\xi}_{i}^{r})+\tilde{R}(\xi_{i}^{i})+\tilde{R}(\hat{\xi}_{i}^{i})] \leq \frac{1}{2}||\mathbf{W}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})]
-\label{duality gap1}
-\end{IEEEeqnarray}
- where $\mathbf{W}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}$. The duality gap can be obtained by 
- \begin{IEEEeqnarray}[\relax]{l}
- \nonumber
- G(\alpha, \hat{\alpha}, \beta, \hat{\beta})=\frac{1}{2}||\mathbf{W}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})]-\{-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})\\
-\nonumber 
- -\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})+Im(\mathbf{y}^{T})(\beta-\hat{\beta})-\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi_{i}^{r})+\tilde{R}(\hat{\xi}_{i}^{r})\\
- \nonumber
- +\tilde{R}(\xi_{i}^{i})+\tilde{R}(\hat{\xi}_{i}^{i})]\}=(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha}) +(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})-Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})-Im(\mathbf{y}^{T})(\beta-\hat{\beta})+\\
- \epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{i}(\beta-\hat{\beta})+C\sum_{i=1}^{N_{r}}[\xi_{i}^{r}R^{'}(\xi_{i}^{r})+\hat{\xi}_{i}^{r}R^{'}(\hat{\xi}_{i}^{r})+\xi_{i}^{i}R^{'}(\xi_{i}^{i})+\hat{\xi}_{i}^{i}R^{'}(\hat{\xi}_{i}^{i})]
- \label{duality gap2}
- \end{IEEEeqnarray}
-Because the noise is white Gaussian, therefore the optimal risk function is 
-$R(\xi)=\frac{1}{2}\xi^{2}$, $\xi$ is the slack variable, hence 
-\begin{equation}
-\xi R^{'}(\xi)=\xi^{2},
-\label{risk functional1}
-\end{equation} 
-\begin{equation}
-\xi_{i}^{r}(\hat{\xi}^{r})=\max(0, |Re(y_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon),
-\label{risk functional2}
-\end{equation}
-Because $\xi^{r}\hat{\xi}^{r}=0$ (estimation can only exceed $\epsilon$ tube in one direction), therefore there is only one of $\xi$ and $\hat{\xi}$ need to be considered, notice $Re(y_{i})-Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi_{i}^{r}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}$ and $Im(y_{i})-Im(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi_{i}^{i}-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}$ hence the last term in (\ref{duality gap2}) can be rewritten as
-\begin{equation}
-C\sum_{i=1}^{N_{r}}((|\Phi_{i}^{r}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon}+(|\Phi_{i}^{i}-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon})
-\label{risk functional3}
-\end{equation}
-where $()_{\epsilon}$ denotes $\epsilon$ insensitive function.
-duality gap in (\ref{duality gap2}) can be divided into two part
-\begin{equation}
-G(\alpha, \hat{\alpha}, \beta, \hat{\beta})=L(\alpha, \hat{\alpha}, \beta, \hat{\beta})+S(\alpha, \hat{\alpha}, \beta, \hat{\beta}),
-\label{divide duality gap}
-\end{equation}
-where 
-\begin{equation}
-L(\alpha, \hat{\alpha}, \beta, \hat{\beta})=(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha}) +(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})-Re(\mathbf{y}^{T})(\alpha-\hat{\alpha})-Im(\mathbf{y}^{T})(\beta-\hat{\beta})+\epsilon\mathbf{e}^{T}(\alpha+\hat{\alpha}+\beta+\hat{\beta})，
-\label{L sub function}
-\end{equation}
-
-\begin{equation}
-S(\alpha, \hat{\alpha}, \beta, \hat{\beta})=C\sum_{i=1}^{N_{r}}((|\Phi_{i}^{r}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon}+(|\Phi_{i}^{i}-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}|)^{2}_{\epsilon})-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{i}(\beta-\hat{\beta})
-\label{S sub function}
-\end{equation}
+As we have explained in section \ref{section lagrange duality}, the upper bound of Lagrangian dual objective function is determined by primal objective function, further more the optimal of primal and dual objective function is found if and only if the equality holds, that is
+\begin{equation}
+\theta(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)
+\label{duality equal}
+\end{equation}
+\begin{equation}
+\frac{1}{2}||\mathbf{w}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
+\label{simple primal}
+\end{equation}
+(\ref{final complex lagrange duality}) can be rewritten as follow by substituting $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\theta(\lambda^{r}, \lambda^{i})=-\frac{1}{2}<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>-\frac{1}{2}<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>+<Re(\mathbf{y})^{T}, \lambda^{r}>+<Im(\mathbf{y})^{T}, \lambda^{i}>\\
+-\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
+\label{simple dual function}
+\end{IEEEeqnarray}
+Similarly, (\ref{complex duality regularization1}) can be formulated as 
+\begin{IEEEeqnarray}[\relax]{l}
+||\mathbf{W}||^{2}_{\mathbb{H}}=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>,
+\label{simple regularization}
+\end{IEEEeqnarray}
+hence, duality gap can be formulated as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+G(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)-\theta(\lambda^{r},\lambda^{i})=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-<Re(\mathbf{y})^{T}, \lambda^{r}>-<Im(\mathbf{y})^{T}, \lambda^{i}>\\
+-\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.
+\label{simple duality gap}
+\end{IEEEeqnarray}
+As we explained in section \ref{risk functional}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
+\begin{equation}
+R(\xi)=\frac{1}{2}\xi^{2},
+\label{risk function1}
+\end{equation} 
+hence 
+\begin{equation}
+\tilde{R}(\xi)=R(\xi)-\xi R{'}(\xi)=-\frac{1}{2}\xi^{2},
+\label{risk function2}
+\end{equation}
+In $\epsilon$-SVR, the objective to employ slack variables $\xi$ is to deal with the outliers that outside $\epsilon$ tube to compensate the influence from noise.
+Therefore 
+\begin{IEEEeqnarray}[\relax]{l}
+\xi^{r}_{i}=Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})-\epsilon\\
+\hat{\xi}^{r}_{i}=Re(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})-Re(\mathbf{y}_{i})-\epsilon
+\label{outlier1}
+\end{IEEEeqnarray}
+Because $\xi^{r}\hat{\xi}^{r}=0$ (estimation can only exceed $\epsilon$ tube in one direction), therefore there is only one of $\xi$ and $\hat{\xi}$ need to be considered, thus 
+\begin{IEEEeqnarray}[\relax]{l}
+\xi^{r}_{i}(\hat{\xi}^{r}_{i})=\max(0, |Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon)\\
+\xi^{i}_{i}(\hat{\xi}^{i}_{i})=\max(0, |Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon)\\
+\xi\hat{\xi}=0,
+\label{outlier2}
+\end{IEEEeqnarray} 
+Therefore the risk function can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}(|Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|)^{2}_{\epsilon}\\
+\label{simple risk function1}
+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}(|Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|)^{2}_{\epsilon}
+\label{simple risk function2}
+\end{IEEEeqnarray}
+where $()_{\epsilon}$ denotes $\epsilon$ insensitive function as we mention in section \ref{risk functional}. Based on (\ref{complex duality regression function}), we have 
+\begin{IEEEeqnarray}[\relax]{l}
+Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}^{r}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}^{i}_{ij}\\
+Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}^{r}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}^{i}_{ij}
+\label{intermediate function1}
+\end{IEEEeqnarray}
+we define two intermediate variables $\Phi$ and $\Psi$
+\begin{IEEEeqnarray}[\relax]{l}
+\Phi^{r}=Re(\mathbf{y})-\mathbf{K}^{r}
+\lambda^{r};
+\Phi^{i}=Im(\mathbf{y})-\mathbf{K}^{r}\lambda^{i}\\
+\Psi^{r}=\mathbf{K}^{i}\lambda^{i};
+\Psi^{i}=-\mathbf{K}^{i}\lambda^{r}\\
+\nonumber
+\label{intermediate function2}
+\end{IEEEeqnarray} 
+Therefore based on (\ref{simple risk function1})-(\ref{intermediate function2}), duality gap in (\ref{simple duality gap}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+G(\lambda^{r}, \lambda^{i})=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-<Re(\mathbf{y})^{T}, \lambda^{r}>-<Im(\mathbf{y})^{T}, \lambda^{i}>\\
+-\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.
+\label{simple duality gap final}
+\end{IEEEeqnarray}
+The duality gap between primal problem and dual problem is used to evaluate how close a solution is to global minimum.
+In our scenario, duality gap is employed as stopping criteria because of low computational cost and reliable performance comparing to monitor KKT complementary condition.
+
 \section{Hyperparameter Setting}
@@
 \bibliography{citation}	
+\end{spacing}												
 \end{document}

### 2015-09-09 Report Aug 5 2015/Report Aug 2015.tex

@@
 %\usepackage{appendix}
-\usepackage{caption}
+%\usepackage{caption}
 \usepackage{cite}
@@
 Message passing detectors based on belief propagation (BF) and Gaussian Approximation (GA) \cite{goldberger2011mimo}\cite{som2011low}\cite{narasimhan2014channel}\cite{som2010improved}.
-Markov Chain Monte Carlo algorithm\cite{datta2013novel}  and Lattice Reduction aided detectors\cite{zhou2013element}.
-
-Firmly grounded in framework of statistical learning theory, Support Vector Machine (SVM) is proposed in 1960s [ref vapnik], and of immense research and industry interest since 1990s.
-SVM is a powerful tool for supervised learning tasks such as classification, regression and prediction.
-Moreover, the kernel trick [ref learning with kernels SVM regularization] makes it possible to map data samples into higher dimensional feature space.
-Therefore SVM can deal with non-linear learning tasks.
-This makes SVM become a promising tool for complex real-world problems.
-Based on the similar principle, $\epsilon$-Support Vector Regression (epsilon-SVR) [vapnik 1995, smola 2003], is developed.
-
-Like SVM, epsilon-SVR first change primal objective function into dual optimization task, then solving the dual quadratic optimization problem.
-Typically this kind of problem can be solved by numerical quadratic optimization (QP) methods, however, they are computational costly.
-Decomposition methods, denotes a set of algorithms that divide the optimization variables (Lagrange multipliers) into two sets W and N, W is the work set and N contains the rest optimization variables.
-In each iteration, only work set is updated for optimization while the other variables are fixed.
-Sequential Minimal Optimization (SMO) [ref A fast algorithm sequential minimal optimization] is an extreme case of decomposition methods which chooses dual Lagrange multiplier to optimize in each iteration.
-In each iteration, decomposition method can find an analytic optimal solution for work set, which makes the solver works much more faster than numerical QP algorithms.
-Decomposition methods can be employed to epsilon SVR by the similar manner.
-
-  Bouloulis et employ Wirtinger’s calculus into Reproducing Kernel Hilbert Space (RKHS) so that expands real-SVM to pure complex SVM by exploiting complex kernel [ref complex support vector machine].
-Based on this work, we construct a prototype of a complexity \$ performance controllable detector for large MIMO based on dual channel complex SVR.
-The detector can be divided into two parallel real SVR optimization problem which can be solved independently.
+Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}  and Lattice Reduction (LR) aided detectors\cite{zhou2013element}.
+
+Firmly grounded in framework of statistical learning theory, Support Vector Machine (SVM) has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction.
+SVM method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can give good generalization performance to unseen data\cite{scholkopf2002learning}.
+
+Research and industry interest of SVM boosted since 1990s, promoted by related works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}
+Moreover, the kernel based methods\cite{scholkopf2002learning} carries out nonlinear learning task by mapping input data sets into high dimensional feature space, then replacing inner product of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
+This rational is supported mathematically by Reproducing Kernel Hilbert Space (RKHS).
+Based on the same regularized risk function principle, ϵ-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.
+
+Like SVM, $\epsilon$-SVR solving original optimization problem by transforming it into Lagrange dual optimization problem, which can be solved by Quadratic Programming (QP), Sequential Minimal Optimization (SMO) algorithm was proposed as a fast algorithm to solve this QP problem by decompose the it into sub QP problems and solve them analytically\cite{platt1999fast}, therefore, the computational intensive numerical method can be avoided.
+A more general method is decomposition solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets W and N, W is the work set and N contains the remaining optimization variables.
+In each iteration, only the optimization variables in work set is optimized while keeping other variables fixed.
+SMO algorithm is an extreme case of decomposition solver.
+An important issue of decomposition solver is the choice of work set, one strategy is to choose Karush–Kuhn–Tucker (KKT) condition violators, and final converge can be guaranteed\cite{osuna1997improved}.
+SMO algorithm restricts the size of work set to 2, because of linear constraint in dual problem that inducted by offset.
+In\cite{steinwart2011training}, a method to train SVM without offset was proposed, with the comparable performance to the SVM with offset.
+The authors work demonstrates that with the combination of two single optimization variable work set selection strategies which requires searching time $O(n)$ and update a work set size of two in each iteration, this method can achieve a iteration time as few as that searching over all pairs of optimization variables which requires $O(n^{2})$ searching times.
+
+Until now, although the mathematical foundation of kernel based methods is RKHS which is defined in complex domain, the most of practitioners are dealing with real data set.
+In communication and signal processing area, the channel gains, signals, waveforms etc.
+are all represented in complex form.
+Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can process the complex data set purely in complex domain.
+The simulation of channel realization and equalization in\cite{bouboulis2013complex} demonstrate a better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernel.
+Based on this work, we construct a prototype of a complexity-performance controllable detector for large MIMO based on dual channel complex SVR.
+The detector can work in two parallel real SVR pipeline which can be solved independently.
 Moreover, only real part of kernel matrix is needed in both channel.
 This means a large amount of computation can be reduced.
-
-  Steinwart et[ref SVM without offset] shows with a proper designed work set selection strategy, the approach that choosing double Lagrange multipliers can be much more faster than choosing single Lagrange multiplier without performance loss.
-
-Based on the discrete time MIMO channel model, In our regression model, this CSVR-detector is constructed without offset, The offset in SVR imposes an additional linear quality constraint, which makes it necessary for decomposition methods such as Sequential Minimal Optimization to update more than one Lagrange multipliers in each iteration.
-
-Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our prototype, we propose a sequential single Lagrange multiplier search strategy that find two Lagrange multiplier sequentially, which can approximate the optimal dual Lagrange multiplier searching strategy.
-The former one only requires $O(n)$ searches in one iteration, while the optimal dual Lagrange multiplier strategy requires $O(n^{2})$ searches per iteration.
+Based on the discrete time MIMO channel model, In our regression model, this CSVR-detector
+is constructed without offset, Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our prototype, we propose a sequential single optimization variable searching strategy that find two optimization variable sequentially, which can approximate the optimal double optimization variables searching strategy.
+
 %\subsection{Subsection Heading Here}
@@
 Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), only the real part of kernel matrix is required for each channel.
-In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping condition.
-Therefore, in large MIMO scenario, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.
+In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping criteria.
+Therefore, in large MIMO uplink system, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.
 \section{Work Set Selection and Solver}\label{WSS}
@@
 
-where $[ ]_{a}^{b}$ denotes to function 
+where $[ ]_{a}^{b}$ denotes clipping function 
 \begin{IEEEeqnarray}[\relax]{l}

### 2015-09-11 Report Aug 5 2015/Report Aug 2015.tex
modified report

@@
 SMO algorithm is an extreme case of decomposition solver.
-An important issue of decomposition solver is the choice of work set, one strategy is to choose Karush–Kuhn–Tucker (KKT) condition violators, and final converge can be guaranteed\cite{osuna1997improved}.
+An important issue of decomposition solver is the choice of work set, one strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, and final converge can be guaranteed\cite{osuna1997improved}.
 SMO algorithm restricts the size of work set to 2, because of linear constraint in dual problem that inducted by offset.
@@
 %Subsubsection text here.
-\section{System Model}\label{system model}
-  Consider a large MIMO uplink multiplexing system with $N_{t}$ users, each user has one transmit antenna.
-The number of receive antennas at Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
-Typically large MIMO systems have hundreds of antennas at BS serving several tens of terminals, as shown in Fig {\ref{large MIMO uplink model}}.
-  \begin{figure}
-  \centering
-  \def\svgwidth{\columnwidth}
-  %\includegraphics[scale=•]{•}
-  \input{largeMIMOuplink.pdf_tex}
-  \caption{Large MIMO uplink system }
-  \label{large MIMO uplink model}
-  \end{figure}
-
-  Uncoded binary information sequences, which are modulated to complex symbols, are transmitted by users over a flat fading channel.
-Using a discrete time model, $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector written as:
-\begin{equation}
-\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{discrete time MIMO system}
-\end{equation}
-where $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
-4-QAM, 16-QAM, 64-QAM) of size $M$.
-The possible transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian zero mean components with unit variance.
-Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
-
-  Assume the receiver has perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known, as well as the SNR.
-The task of the MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
 
@@
 $\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function.
-$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes risk function, the simplest risk function is $R(x)=x$, risk function is determined by the statistical distribution of noise \cite{A tutorial of Support Vector Regression}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
+$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes risk function, the simplest risk function is $R(x)=x$, risk function is determined by the statistical distribution of noise\cite{smola2004tutorial}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
 $C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
@@
 \end{eqnarray}
-where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered, we arrive to at a convex minimization problem \cite{smola and skpkof 1998a tutorial of SVR}. 
+where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered. 
 \subsection{Lagrange Duality}\label{section lagrange duality}
@@
 
-The sufficient and necessary condition that $f(\mathbf{w}^{*})$ is the global minimum of (\ref{primal objective function}) is called Karush-Kuhn-Tucker (KKT) conditions, which can be written as 
+The sufficient and necessary condition that $f(\mathbf{w}^{*})$ is the global minimum of (\ref{primal objective function}) is called Karush-Kuhn-Tucker (KKT) conditions, which can be written as\cite{cristianini2000introduction}
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \alpha(y-\mathbf{w}^{T}\Phi(\mathbf{x})-b-\epsilon-\xi)=0\\
-\hat{\alpha}(\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi})=0
+\hat{\alpha}(\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi})=0\\
+y-\mathbf{w}^{T}\Phi(\mathbf{x})-b-\epsilon-\xi\leq 0\\
+\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi}\leq 0
 \end{array}\right. 
@@
 \end{IEEEeqnarray}
-Obviously $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, notice now (\ref{partial1})-(\ref{partial4})are satisfied, therefore, KKT complimentary condition (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
+Obviously $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, notice by transforming $\Theta(\mathbf{w}, \alpha, \hat{\alpha},\eta, \hat{\eta})$, (\ref{partial1})-(\ref{partial4}) are satisfied, therefore, KKT complimentary condition (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
 Because
@@
 
-\section{Dual Channel Real Kernel Complex Support Vector Regression for Large MIMO system}\label{dual channel CSVR}
+\section{System Model}\label{system model}
+  Consider a complex large MIMO uplink multiplexing system with $N_{t}$ users, each user has one transmit antenna.
+The number of receive antennas at Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
+Typically large MIMO systems have hundreds of antennas at BS serving several tens of terminals, as shown in Fig {\ref{large MIMO uplink model}}.
+  \begin{figure}[htb]
+  \centering
+  \def\svgwidth{\columnwidth}
+  %\includegraphics[scale=•]{•}
+  \input{largeMIMOuplink.pdf_tex}
+  \caption{Large MIMO uplink system }
+  \label{large MIMO uplink model}
+  \end{figure}
+
+  Uncoded bit sequences, which are modulated to complex symbols, are transmitted by users over a flat fading channel. The discrete time model is:
+\begin{equation}
+\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{discrete time MIMO system}
+\end{equation}
+where $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
+4-QAM, 16-QAM, 64-QAM) of size $M$.
+The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian zero mean components with unit variance.
+Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
+
+  Assume the receiver has perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known, as well as the SNR.
+The task of the MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
+
+\section{Dual Channel Complex Support Vector Regression for Large MIMO system}\label{dual channel CSVR}
  Based on discrete time model of large MIMO uplink system in (\ref{discrete time MIMO system}), in our  regression model, the training data sample at detector is $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of channel propagation matrix $\mathbf{H}$, this yields a regression task without offset $b$:
@@
  \end{eqnarray}
- where $f_{true}()$ denotes the true regression function, $n$ denotes additive noise.
+ where $f_{true}()$ denotes the underlying true function, $n$ denotes additive noise.
 In this regression problem, receive symbol $y$ is the output data, $\mathbf{h}$ is input data sample, transmitted symbol vector $s$ is regression coefficients.
 Because the large MIMO system we consider here is complex, we employ complex support vector regression (CSVR) without offset term $b$.
-As shown in section \ref{Introduce epsilon SVR}, in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to real cost functions which are defined in complex domain.
-The recent mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS)[\cite{wirtinger's calculus}][\cite {reproducing Kernel Hilbert Space}] is employed to solve this problem.
+As shown in section \ref{Introduce epsilon SVR}, in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to risk functions which are defined in complex domain.
+Recently mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) is employed to solve this problem\cite{bouboulis2011extension}.
 First we generalize our regression model by complex RKHS,
@@
 \end{equation}
-Because of (\ref{CHSequation1}), (\ref{CHSequation2}) and (\ref{CHSequation3}), $\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{*}>_{\mathbb{H}}$
+Because of (\ref{CHSequation1}), (\ref{CHSequation2}) and (\ref{CHSequation3}), $\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{*}>_{\mathbb{H}}$.
 \end{proof}
@@
 Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denotes the kernel function, $\mathbf{K}=\mathbf{K}^{r}+i\mathbf{K}^{i}$, $\mathbf{K}^{r}$ and $\mathbf{K}^{i}$ denote matrix of corresponding real part and imaginary part.
-Similar to the Lagrange duality rational in (\ref{lagrange duality2}), Lagrange duality is formulated for (\ref{complex objective function1})
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{(\alpha, \hat{\alpha}, \beta, \hat{\beta}, \eta, \hat{\eta}, \tau, \hat{\tau})} \min_{(\mathbf{w}, \xi^{r}, \hat{\xi}^{r}, \hat{\xi}^{i}, \hat{\xi}^{i})} \theta =
-\frac{1}{2}||w||_{\mathbb{H}}^{2}+C\sum_{k=1}^{N_{r}}[(R(\xi^{r}_{k})+R(\hat{\xi}^{r}_{k})+R(\xi^{i}_{k})+R(\hat{\xi}^{i}_{k}))]- \sum_{k=1}^{N_{r}}(\eta_{i}\xi^{r}_{k}+\hat{\eta}_{k}\hat{\xi}^{r}_{k}\\
-\nonumber
-+\tau_{k}\xi^{i}_{k}+\hat{\tau}_{k}\hat{\xi}^{i}_{k})-\sum_{k=1}^{N_{r}}\alpha_{k}(\epsilon+\xi^{r}_{k}-Re(y_{k})+Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))
+Similar to the Lagrange duality rational in section \ref{section lagrange duality}, Lagrange function is formulated for (\ref{complex objective function1})
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\theta =
+\frac{1}{2}||w||_{\mathbb{H}}^{2}+C\sum_{k=1}^{N_{r}}[(R(\xi^{r}_{k})+R(\hat{\xi}^{r}_{k})+R(\xi^{i}_{k})+R(\hat{\xi}^{i}_{k}))]- \sum_{k=1}^{N_{r}}(\eta_{i}\xi^{r}_{k}+\hat{\eta}_{k}\hat{\xi}^{r}_{k}+\tau_{k}\xi^{i}_{k}+\hat{\tau}_{k}\hat{\xi}^{i}_{k})\\
+\nonumber
+-\sum_{k=1}^{N_{r}}\alpha_{k}(\epsilon+\xi^{r}_{k}-Re(y_{k})+Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))
 -\sum_{k=1}^{N_{r}}\hat{\alpha}_{k}(\epsilon+\hat{\xi}^{r}_{k}+Re(y_{k})-Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))\\
@@
 \end{IEEEeqnarray}
-with Wirtinger's calculus applied to RKHS described in \cite{wirtinger's calculus to RKHS}, The partial derivatives of $\Theta$ respect to $\mathbf{w}$, which is define at complex domain, as well as the real variables $\xi^{r}$, $\hat{\xi}^{r}$, $\xi^{i}$ and $\hat{\xi}^{i}$ can be deduced
+with Wirtinger's calculus applied to RKHS described in \cite{bouboulis2011extension}, The partial derivatives of $\theta$ respect to $\mathbf{w}$, which is define at complex domain, as well as the real variables $\xi^{r}$, $\hat{\xi}^{r}$, $\xi^{i}$ and $\hat{\xi}^{i}$ can be deduced
 \begin{IEEEeqnarray}[\relax]{l}
@@
 Decomposition method works iteratively, the basic idea of decomposition method is to choose a subset of variable pairs $S$ (named work set) to optimize in each iteration step while keep the rest variable pairs $N$ fixed.
-Sequential Minimal Optimization (SMO) \cite{SMO} is an extreme case of decomposition method, the work set size is 2, an analytic quadratic programming (QP) step instead of numerical QP step can be taken in each iteration.
+Sequential Minimal Optimization (SMO) is an extreme case of decomposition method, the work set size is 2, an analytic quadratic programming (QP) step instead of numerical QP step can be taken in each iteration.
 
@@
 maximize\quad \Theta_{S}^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]+[Re(\mathbf{y})_{S}^{T}-(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
-](\alpha-\hat{\alpha})_{S}-\epsilon[\mathbf{e}_{S}^{T}(\alpha+\hat{\alpha})_{S}],
+](\alpha-\hat{\alpha})_{S}-\epsilon<\mathbf{e}_{S}^{T}, (\alpha+\hat{\alpha})_{S}>,
 \label{subset optimization}
 \end{equation}
-In decomposition method, a proper work set selection strategy is required so that acceptable speed and performance can be guaranteed.
-One approach is to choose dual variable pairs that violate KKT conditions, so that after each iteration, the objective function can be increased according to Osuna's theorem\cite{inproved training algorithms for support vector machines}, Heuristic methods are used in [\cite{SMO}] in order to accelerate process, in work set selection process, the algorithm first searches among the non-bound variables (that is $0<\alpha<C\tilde{R}(\xi)$), which are more likely to violate KKT condition, then searching the whole dual variable set, the second dual variable that can maximize optimization step of the first coordinate is chosen, approximate step size is used as evaluator for sake of reducing computational cost.
+In decomposition method, a proper work set selection strategy is required so that speed and performance requirement can be guaranteed.
+One approach is to choose dual variable pairs that violate KKT conditions, so that after each iteration, the objective function can be increased according to Osuna's theorem\cite{osuna1997improved}, Heuristic methods are used in in order to accelerate process, in work set selection process, the algorithm first searches among the non-bound variables (that is $0<\alpha<C\tilde{R}(\xi)$), which are more likely to violate KKT condition, then searching the whole dual variable set, the second dual variable that can maximize optimization step of the first coordinate is chosen, approximate step size is used as evaluator for sake of reducing computational cost.
 Lin propose another work set selection strategy based on an alternative form of KKT condition.
 
-Another class of approaches is to choose the dual variables whose update can provide the maximum improvements to objective function \cite{}, \cite{}, \cite{}(Training without offset). That is 
+Another class of approaches is to choose the dual variables whose update can provide the maximum improvements to objective function. That is 
 \begin{equation}
@@
 \subsection{Single Direction Solver}
- We will first introduce 1-D work set selection strategy in which the dual variable pair that maximizes the gain of objective function is chosen.
-Recall the decomposition method in (\ref{maximum gain work set selection}), let $\alpha_{1}$ denotes the dual variable that is chosen to be updated.
-The sub optimization  problem is formulated as
- \begin{IEEEeqnarray}[\relax]{l}
- \nonumber
- maximize\quad \Theta_{1}^{r}=-\frac{1}{2}((\alpha_{1}-\hat{\alpha}_{1})^{new})^{2}\mathbf{K}_{11}^{r}-(\alpha_{1}-\hat{\alpha}_{1})^{new}\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}(\alpha_{j}-\hat{\alpha}_{j})
-+Re(y_{1})(\alpha_{1}-\hat{\alpha}_{1})^{new}\\
--\epsilon(\alpha_{1}+\hat{\alpha}_{1})^{new},
- \label{optimization function 1-D}
- \end{IEEEeqnarray}
-take the partial derivative of $\Theta_{1}^{r}$ respect to $\alpha_{1}$ and $\hat{\alpha}_{1}$, we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\frac{\partial \Theta_{1}^{r}}{\partial \alpha_{1}}=-(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}_{11}^{r}-\sum_{j=2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})^{new}\mathbf{K}_{1j}^{r}+Re(y_{1})-\epsilon=0\\
-\Rightarrow \alpha_{1}^{new}=\alpha_{1}+\frac{\Phi_{1}^{r}-\epsilon}{\mathbf{K}_{11}^{r}},
-\label{partial optimization function 1-D alpha}
-\end{IEEEeqnarray}
-
- \begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\frac{\partial \Theta_{1}^{r}}{\partial \hat{\alpha}_{1}}=(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}_{11}^{r}+\sum_{j=2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})^{new}\mathbf{K}_{1j}^{r}-Re(y_{1})-\epsilon=0\\
-\Rightarrow \hat{\alpha}_{1}^{new}=\hat{\alpha}_{1}-\frac{\Phi_{1}^{r}+\epsilon}{\mathbf{K}_{11}^{r}}\\
-\nonumber
-\label{partial optimization function 1-D alpha hat}
-\end{IEEEeqnarray} 
-where we define $\Phi_{i}^{r}=Re(y_{i})-\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}_{ij}^{r}$, similarly, as to dual variable  $\beta$ and $\hat{\beta}$, we define $\Phi_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}_{ij}^{r}$.
-Recall complementary KKT condition
+Recall KKT complementary condition
 \begin{IEEEeqnarray}[\relax]{l}
@@
 (C\tilde{R}(\hat{\xi}^{r})-\hat{\alpha})\hat{\xi}^{r}=0\\
-\alpha(\epsilon+\xi^{r}-Re(y)+<\mathbf{h},\mathbf{w}>_{\mathbb{H}})=0\\
-\hat{\alpha}(\epsilon+\hat{\xi}^{r}+Re(y)-<\mathbf{h},\mathbf{w}>_{\mathbb{H}})=0\\
+\alpha(Re(y)-<\mathbf{h},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi^{r})=0\\
+\hat{\alpha}(<\mathbf{h},\mathbf{w}>_{\mathbb{H}}-Re(y)-\epsilon-\hat{\xi}^{r})=0\\
 \end{array}\right.
@@
 \end{IEEEeqnarray}
-it can be easily observed that $\alpha\hat{\alpha}=0$, because $0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(C\tilde{R}(\hat{\xi}^{r}))$,  $\xi^{r}$ and $\hat{\xi}^{r}$ satisfy $\xi^{r}\hat{\xi}^{r}$.
+it can be easily observed that $\alpha\hat{\alpha}=0$, because $0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(C\tilde{R}(\hat{\xi}^{r}))$,  $\xi^{r}$ and $\hat{\xi}^{r}$ satisfy $\xi^{r}\hat{\xi}^{r}=0$.
+Hence we can substitute $\lambda=\alpha-\hat{\alpha}$ and $|\lambda|=\alpha+\hat{\alpha}$, therefore the update unit is single optimization variable $\lambda$, rather than pair $\alpha$ and $\hat{\alpha}$.
+ We will first introduce 1-D work set selection strategy in which one optimization variable that maximizes the gain of objective function is updated in one iteration.
+Reformulate by $\lambda$ and $\sigma=\lambda^{new}-\lambda$ sub optimization objective function(\ref{subset optimization}) and its gain (\ref{gain work set selection2})
+  \begin{equation}
+maximize\quad \theta_{S}^{r}=-\frac{1}{2}[\lambda_{S}^{T}\mathbf{K}_{SS}^{r}\lambda_{S}]+[Re(\mathbf{y})_{S}^{T}-\lambda_{N}^{T}\mathbf{K}_{NS}^{r}
+]\lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\lambda_{S}|>,
+\label{subset optimization lambda}
+\end{equation}
+
+\begin{IEEEeqnarray}[\relax]{l}
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\sigma^{T}_{S}\mathbf{K}^{r}_{SS}\sigma_{S}+(\Phi^{r}_{S})^{T}\sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\lambda^{new}_{S}|-|\lambda_{S}|>,
+\label{gain work set selection lambda}
+\end{IEEEeqnarray} 
+For 1-D solver, the sub optimization objective function can be written as
+\begin{IEEEeqnarray}[\relax]{l}
+ maximize\quad \theta_{1}^{r}=-\frac{1}{2}(\lambda_{1}^{new})^{2}\mathbf{K}_{11}^{r}
++[Re(y_{1})-\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}\lambda_{j}]\lambda_{1}^{new}-\epsilon(|\lambda^{new}_{1}|),
+ \label{optimization function 1-D}
+ \end{IEEEeqnarray}
+take the partial derivative of $\theta_{1}^{r}$ respect to $\lambda^{new}_{1}$, where we define $\Phi_{i}^{r}=Re(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}_{ij}^{r}$, similarly, as to dual variable $\lambda^{i}$ , we define $\Phi_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}_{ij}^{r}$.
+Here for sake of brevity, we use $\lambda$.
+Hence we have
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\frac{\partial \theta_{1}^{r}}{\partial \lambda^{new}_{1}}=-\lambda_{1}^{new}\mathbf{K}_{11}^{r}+Re(y_{1})-\sum_{j=2}^{N_{r}}\lambda_{j}^{new}\mathbf{K}_{1j}^{r}-\epsilon(sgn(\lambda^{new}_{1}))=\\
+\nonumber
+-\lambda_{1}^{new}\mathbf{K}_{11}^{r}+\Phi^{r}_{1}+\lambda_{1}\mathbf{K}^{r}_{11}-\epsilon(sgn(\lambda^{new}_{1}))\\
+\Rightarrow \lambda_{1}^{new}=\lambda_{1}+\frac{\Phi_{1}^{r}-\epsilon(sgn(\lambda^{new}_{1}))}{\mathbf{K}_{11}^{r}},
+\label{partial optimization function 1-D lambda}
+\end{IEEEeqnarray}
+
  The update of $\alpha_{1}$ or $\hat{\alpha}_{1}$ is completed by clipping
 \begin{IEEEeqnarray}[\relax]{l}
-\alpha^{new\quad clipped}=[\alpha^{new}]_{0}^{C\tilde{R}(\xi^{r})}\\
-\hat{\alpha}^{new\quad clipped}=[\hat{\alpha}^{new}]_{0}^{C\tilde{R}(\hat{\xi}^{r})}\\
-\nonumber
+\lambda^{new\quad clipped}_{1}=[\lambda^{new}_{1}]^{CR^{'}(\xi)}_{-CR^{'}(\xi)}
 \label{clipped new dual variable}
@@
 \end{IEEEeqnarray}
-Based on (\ref{gain work set selection2}), The gain of objective function respect to $i$th dual variable pair is 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \Theta_{i}^{r}=\Theta^{r}((\alpha_{i}+\delta_{i}\mathbf{e}_{i}), (\hat{\alpha}_{i}+\hat{\delta}_{i}\mathbf{e}_{i}))-\Theta^{r}(\alpha, \hat{\alpha})\\
-\nonumber
-=-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})^{2}\mathbf{K}_{ii}^{r}+\Phi^{r}_{1}(\delta_{i}-\hat{\delta}_{i})-\epsilon(\delta_{i}+\hat{\delta}_{i})\\
-=(\delta_{i}-\hat{\delta}_{i})[-\frac{1}{2}(\delta_{i}-\hat{\delta}_{i})\mathbf{K}_{ii}^{r}+\Phi_{i}^{r}-\epsilon\frac{\delta_{i}+\hat{\delta}_{i}}{\delta_{i}-\hat{\delta}_{i}}],
+Define $\sigma=\lambda^{new\quad clipped}-\lambda$, based on (\ref{gain work set selection lambda}), The gain of objective function respect to $i$th optimization variable is 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta_{i}^{r}=\theta^{r}(\lambda_{1}+\sigma_{1})-\theta^{r}(\lambda_{1})\\
+\nonumber
+=-\frac{1}{2}\sigma_{i}^{2}\mathbf{K}_{ii}^{r}+\Phi^{r}_{i}\sigma_{i}-\epsilon(|\lambda^{new\quad cipped}_{i}|-|\lambda_{i}|)\\
+=\sigma_{i}[-\frac{1}{2}\sigma_{i}\mathbf{K}_{ii}^{r}+\Phi_{i}^{r}]-\epsilon(|\lambda^{new\quad clipped}_{i}|-|\lambda_{i}|),
 \label{gain of 1-D objective function}
 \end{IEEEeqnarray}
-where $\delta_{1}=\alpha^{new\quad clipped}_{1}-\alpha_{1}$, $\hat{\delta}_{1}=\hat{\alpha}^{new\quad clipped}_{1}-\hat{\alpha}_{1}$, in 1-D searching procedure, the dual variable pair which has the maximum gain of objective function is chosen as $1$ in (\ref{optimization function 1-D}), that is
+In 1-D searching procedure, the optimization variable which has the maximum gain of sub optimization objective function is updated as $1$ in (\ref{optimization function 1-D}), that is 
 \begin{equation}
@@
 \subsection{Double Direction Solver}
-Although omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however recent work in machine learning field shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained\cite{training SVM without offset}.
-The 2-D solver uses the same principle as 1-D solver, the work set size is 2, recall (\ref{subset optimization}), let $(\alpha_{1}, \hat{\alpha}_{1})$, $(\alpha_{2}, \hat{\alpha}_{2})$ denote the two dual variable pairs that are chosen for optimization, that is $(\alpha_{s}, \hat{\alpha}_{s})=((\alpha_{1}\mathbf{e}_{1}+\alpha_{2}\mathbf{e}_{2}), (\hat{\alpha}_{1}\mathbf{e}_{1}+\hat{\alpha}_{2}\mathbf{e}_{2}))$.
-Thus we have, based on (\ref{subset optimization}), the sub objective function can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-maximize\quad \Theta^{r}_{1,2}=-\frac{1}{2}[(\alpha_{1}-\hat{\alpha}_{1})^{2}\mathbf{K}^{r}_{11}+(\alpha_{2}-\hat{\alpha}_{2})^{2}\mathbf{K}^{r}_{22}+2(\alpha_{1}-\hat{\alpha}_{1})(\alpha_{2}-\hat{\alpha}_{2})\mathbf{K}^{r}_{12}]-\\
-\nonumber
-(\alpha_{1}-\hat{\alpha}_{1})\sum_{j\neq 1, 2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{1j}-(\alpha_{2}-\hat{\alpha}_{2})\sum_{j\neq 1, 2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{2j}+Re(y_{1})(\alpha_{1}-\hat{\alpha}_{1})+Re(y_{2})(\alpha_{2}-\hat{\alpha}_{2})\\
--\epsilon(\alpha_{1}+\hat{\alpha}_{1}+\alpha_{2}+\hat{\alpha}_{2}), 
+Although omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however recent work in machine learning field shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained.
+The 2-D solver uses the same principle as 1-D solver, the work set size is 2, that is $\lambda_{S}=\lambda_{1}\mathbf{e}_{1}+\lambda_{2}\mathbf{e}_{2}$.
+Based on (\ref{gain work set selection lambda}), the sub objective function can be written as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+maximize\quad \theta^{r}_{1,2}=-\frac{1}{2}[(\lambda^{new}_{1})^{2}\mathbf{K}^{r}_{11}+(\lambda^{new}_{2})^{2}\mathbf{K}^{r}_{22}+2\lambda^{new}_{1}\lambda^{new}_{2}\mathbf{K}^{r}_{12}]-\\
+\nonumber
+\lambda^{new}_{1}\sum_{j\neq 1, 2}^{N_{r}}\lambda_{j}\mathbf{K}^{r}_{1j}-\lambda^{new}_{2}\sum_{j\neq 1, 2}^{N_{r}}\lambda_{j}\mathbf{K}^{r}_{2j}+Re(y_{1})\lambda^{new}_{1}+Re(y_{2})\lambda^{2}_{2}\\
+-\epsilon(|\lambda^{new}_{1}|+|\lambda_{2}^{new}|), 
 \label{2-D solver}
 \end{IEEEeqnarray}
-Based on (\ref{2-D solver}), the partial derivative of $\Theta^{r}_{1,2}$ with respect to $\alpha_{1}$ is 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\frac{\partial \Theta^{r}_{1,2}}{\partial \alpha_{1}}=-(\alpha_{1}-\hat{\alpha}_{1})\mathbf{K}^{r}_{11}-(\alpha_{2}-\hat{\alpha}_{2})\mathbf{K}^{r}_{12}-\sum_{j\neq 1, 2}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{1j}+Re(y_{1})-\epsilon=\\
-\nonumber
--(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}^{r}_{11}+Re(y_{1})-\sum_{j\neq 1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{1j}-\epsilon=-(\alpha_{1}-\hat{\alpha}_{1})^{new}\mathbf{K}^{r}_{11}+\Phi_{1}+(\alpha_{1}-\hat{\alpha}_{1})\mathbf{K}^{r}_{11}-\epsilon\\
-\Rightarrow \alpha^{new}_{1}=\alpha_{1}+\frac{(\Phi^{r}_{1}-\epsilon)}{\mathbf{K}^{r}_{11}},
+Based on (\ref{2-D solver}), the partial derivatives of $\theta^{r}_{1,2}$ with respect to $\lambda^{new}_{1}$ and $\lambda_{2}^{new}$ are 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\label{lambda1 partial}
+\frac{\partial \theta^{r}_{1,2}}{\partial \lambda^{new}_{1}}=-\lambda^{new}_{1}\mathbf{K}^{r}_{11}-\lambda^{new}_{2}\mathbf{K}^{r}_{12}-\sum_{j\neq 1, 2}^{N_{r}}\lambda_{j}\mathbf{K}^{r}_{1j}+Re(y_{1})-\epsilon sgn(\lambda^{new}_{1})=\\
+-\lambda_{1}^{new}\mathbf{K}^{r}_{11}-\lambda^{new}_{2}\mathbf{K}^{r}_{12}+\Phi^{r}_{1}+\lambda_{1}\mathbf{K}^{r}_{11}+\lambda_{2}\mathbf{K}^{r}_{12}-\epsilon sgn(\lambda^{new}_{1})=0\\
+\nonumber
+\label{lambda2 partial}
+\frac{\partial \theta^{r}_{1,2}}{\partial \lambda^{new}_{2}}=-\lambda^{new}_{2}\mathbf{K}^{r}_{22}-\lambda^{new}_{1}\mathbf{K}^{r}_{12}-\sum_{j\neq 1, 2}^{N_{r}}\lambda_{j}\mathbf{K}^{r}_{2j}+Re(y_{2})-\epsilon sgn(\lambda^{new}_{2})=\\
+-\lambda_{2}^{new}\mathbf{K}^{r}_{22}-\lambda^{new}_{1}\mathbf{K}^{r}_{12}+\Phi^{r}_{2}+\lambda_{1}\mathbf{K}^{r}_{12}+\lambda_{2}\mathbf{K}^{r}_{22}-\epsilon sgn(\lambda^{new}_{2})=0\\
+\nonumber
 \label{partial derivative sample1}
 \end{IEEEeqnarray}
-Similarly we can derive the update formulas of $\hat{\alpha}_{1}$,$\alpha_{2}$ and $\hat{\alpha}_{2}$
-\begin{equation}
-\hat{\alpha}^{new}_{1}=\hat{\alpha}_{1}-\frac{(\Phi^{r}_{1}+\epsilon)}{\mathbf{K}^{r}_{11}},
-\label{partial derivative sample2}
-\end{equation}
-
-\begin{equation}
-\alpha^{new}_{2}=\alpha_{2}+\frac{(\Phi^{r}_{2}-\epsilon)}{\mathbf{K}^{r}_{22}},
-\label{partial derivative sample3}
-\end{equation}
-
-\begin{equation}
-\hat{\alpha}^{new}_{2}=\hat{\alpha}_{2}-\frac{(\Phi^{r}_{2}+\epsilon)}{\mathbf{K}^{r}_{22}},
-\label{partial derivative sample4}
-\end{equation}
+where $\frac{\partial |x|}{\partial x}=sgn(x)$ denotes the sign of $x$. Based on (\ref{lambda1 partial}) and (\ref{lambda2 partial}) we have 
+\begin{IEEEeqnarray}[\relax]{l}
+\label{post partial lambda1}
+(\lambda^{new}_{1}-\lambda_{1})\mathbf{K}^{r}_{11}=\Phi^{r}_{1}-\epsilon sgn(\lambda^{new}_{1})-(\lambda^{new}_{2}-\lambda_{2})\mathbf{K}^{r}_{12}\\
+\label{post partial lambda2}
+(\lambda^{new}_{2}-\lambda_{2})\mathbf{K}^{r}_{22}=\Phi^{r}_{2}-\epsilon sgn(\lambda^{new}_{2})-(\lambda^{new}_{1}-\lambda_{1})\mathbf{K}^{r}_{12}\\
+\nonumber
+\end{IEEEeqnarray}
+hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formula of $\lambda^{new}_{1}$ and $\lambda^{new}_{2}$ are
+\begin{equation}
+\lambda^{new}_{1}=\lambda_{1}+\frac{\Phi^{r}_{1}\mathbf{K}^{r}_{22}-\Phi^{r}_{2}\mathbf{K}^{r}_{12}-\epsilon[sgn(\lambda^{new}_{1})\mathbf{K}^{r}_{22}-sgn(\lambda^{new}_{2})\mathbf{K}^{r}_{12}]}{\mathbf{K}^{r}_{11}\mathbf{K}^{r}_{22}-(\mathbf{K}^{r}_{12})^{2}}
+\label{update lambda1}
+\end{equation}
+
+\begin{equation}
+\lambda^{new}_{2}=\lambda_{2}+\frac{\Phi^{r}_{2}\mathbf{K}^{r}_{11}-\Phi^{r}_{1}\mathbf{K}^{r}_{12}-\epsilon[sgn(\lambda^{new}_{2})\mathbf{K}^{r}_{11}-sgn(\lambda^{new}_{1})\mathbf{K}^{r}_{12}]}{\mathbf{K}^{r}_{11}\mathbf{K}^{r}_{22}-(\mathbf{K}^{r}_{12})^{2}}
+\label{update lambda2}
+\end{equation} 
+Then the updated optimization variables are clipped by constraint 
+\begin{IEEEeqnarray}[\relax]{l}
+\lambda^{new\quad clipped}=[\lambda^{new}]^{CR^{'}(\xi)}_{-CR^{'}(\xi)},
+\label{cipped optimization variable}
+\end{IEEEeqnarray}
 It is obviously the dual variables in 2-D solver have the same update rule as that of 1-D solver.
@@
 \nonumber
-\bigtriangledown \Theta^{r}_{ij}=-\frac{1}{2}[(\delta_{i}-\hat{\delta}_{i})^{2}\mathbf{K}^{r}_{ii}+(\delta_{j}-\hat{\delta}_{j})^{2}\mathbf{K}^{r}_{jj}+2(\delta_{i}-\hat{\delta}_{i})(\delta_{j}-\hat{\delta}_{j})\mathbf{K}^{r}_{ij}]+\Phi^{r}_{i}(\delta_{i}-\hat{\delta}_{i})+\Phi^{r}_{j}(\delta_{j}-\hat{\delta}_{j})\\
--\epsilon(\delta_{i}+\hat{\delta}_{i}+\delta_{j}+\hat{\delta}_{j}),
+\bigtriangledown \theta^{r}_{ij}=-\frac{1}{2}[\sigma_{i}^{2}\mathbf{K}^{r}_{ii}+\sigma_{j}^{2}\mathbf{K}^{r}_{jj}+2\sigma_{i}\sigma_{j}\mathbf{K}^{r}_{ij}]+\Phi^{r}_{i}\sigma_{i}+\Phi^{r}_{j}\sigma_{j}\\
+-\epsilon(|\lambda^{new\quad clipped}_{i}|-|\lambda_{i}|+|\lambda^{new\quad clipped}_{j}|-|\lambda_{j}|),
 \label{gain of 2-D objective function1}
@@
  \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \Theta^{r}_{ij}=\bigtriangledown \Theta^{r}_{i}+\bigtriangledown \Theta^{r}_{j}-(\delta_{i}-\hat{\delta}_{i})(\delta_{j}-\hat{\delta}_{j})\mathbf{K}^{r}_{ij},
+\bigtriangledown \theta^{r}_{ij}=\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}-\sigma_{i}\sigma_{j}\mathbf{K}^{r}_{ij},
 \label{gain of 2-D objective function1}
@@
 \subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
-From (\ref{gain of 2-D objective function1}), it is obviously that the gain of 2-D solver is a summation of the gain of 2 independent 1-D solver and a correlation term $(\delta_{i}+\hat{\delta}_{i})(\delta_{j}+\hat{\delta}_{j})\mathbf{K}^{r}_{ij}$.
+From (\ref{gain of 2-D objective function1}), it is obviously that the gain of 2-D solver is a summation of the gain of 2 independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\mathbf{K}^{r}_{ij}$.
 
@@
 1. 1-D searching without damping:\\
-do 1 time 1-D searching and calculate all the 1-D gain based on (\ref{gain of 1-D objective function}), then choose the coordinate pairs with first and second largest 1-D gain as the candidate.\\
+do one time 1-D searching and calculate all the 1-D gain based on (\ref{gain of 1-D objective function}), then choose the coordinate with first and second largest 1-D gain as the candidates, then update the two candidates by 2-D solver as shown in (\ref{update lambda1}) and (\ref{update lambda2})\\
 2. 1-D searching with damping:\\
-do 2 times 1-D searching, in the first round find dual variable pair $i$ that can maximize 1-D gain, then in the second round, find $j$th dual variable pair with the value of $i$th coordinate updated.
-
-From (\ref{gain of 2-D objective function1}), it can be easily interpreted the efficient of 1-D approximation approach is majorly determined by the approximation ratio $\frac{(\delta_{i}+\hat{\delta}_{i})(\delta_{j}+\hat{\delta}_{j})\mathbf{K}^{r}_{ij}}{\bigtriangledown \Theta^{r}_{i}+\bigtriangledown \Theta^{r}_{j}}$, hence we provide theoretical analyse from the view of channel hardening phenomenon, and give the upper bound of approximation ratio.
-Prior the theoretical analyse, we first investigate some mathematical properties of channel hardening.
-
- Based on the complimentary KKT conditions, we have $\alpha\hat{\alpha}=0$, therefore we transform (\ref{subset optimization}) and (\ref{gain work set selection2}) by substituting $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, hence we have
-\begin{equation}
-maximize\quad \Theta_{S}^{r}=-\frac{1}{2}\lambda_{S}^{T}\mathbf{K}_{SS}^{r}\lambda_{S}+(Re(\mathbf{y})_{S}^{T}-\lambda_{N}^{T}\mathbf{K}_{NS}^{r}
-)\lambda_{S}-\epsilon(\mathbf{e}_{S}^{T}|\lambda_{s}|),
-\label{simplified subset optimization}
-\end{equation}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}\tau^{T}_{S}\mathbf{K}^{r}_{SS}\tau_{S}+(\Phi^{r}_{S})^{T}\tau_{S}-\epsilon\mathbf{e}^{T}_{S}(|\lambda|^{new}-|\lambda|)_{S},
-\label{simplified gain work set selection}
-\end{IEEEeqnarray}
-where $\tau=\lambda^{new}-\lambda$. 
-Therefore we can simplify the work set selection procedure by update variables $\lambda$ rather than dual variable pairs
-For single direction solver, (\ref{optimization function 1-D}) can be transformed as 
-\begin{IEEEeqnarray}[\relax]{l}
- maximize\quad \Theta_{1}^{r}=-\frac{1}{2}(\lambda_{1}^{new})^{2}\mathbf{K}_{11}^{r}-(\lambda_{1})^{new}\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}\lambda_{j}
-+Re(y_{1})\lambda_{1}^{new}-\epsilon|\lambda_{1}|^{new},
- \label{simplified optimization function 1-D}
- \end{IEEEeqnarray}
-Thus for 1-D solver the gradient of (\ref{simplified optimization function 1-D}) with respect to $\lambda$ can be written as
+do two times 1-D searchings, in the first round find optimization variable $i$ that can maximize 1-D gain, then in the second round, find $j$th optimization variable with the value of $i$th coordinate updated.
+
+From (\ref{gain of 2-D objective function1}), it can be easily interpreted the efficient of 1-D approximation approach is majorly determined by the approximation ratio $\frac{\sigma_{i}\sigma_{j}\mathbf{K}^{r}_{ij}}{\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}}$, hence we provide theoretical analyse from the view of channel hardening phenomenon.
+Prior the theoretical analyse, we first investigate some mathematical properties of channel hardening (to be completed).
+
+For 1-D solver the gradient of (\ref{partial optimization function 1-D lambda}) with respect to $\lambda$ can be written as
 \begin{equation}
@@
 \end{equation}
-where $\frac{\partial |\lambda^{new}_{1}|}{\partial \lambda_{1}^{new}}=sgn(\lambda_{1}^{new})$
-the similar principle can be also applied to double direction solver.
-Because in the update process the $sgn(\lambda^{new})$ is unknown to old parameter values , therefore, we need to consider both the case $sgn(\lambda^{new})=-1 $ or $1$ and choose the one with the larger objective function gain $\bigtriangledown \Theta^{r}_{S}$.
-Here we give the pseudo code for sequential approximate optimal double direction solver.
-
-\begin{algorithm}
+In the update process the $sgn(\lambda^{new})$ is unknown at current step, therefore, we need to consider both the case $sgn(\lambda^{new})=-1 $ or $1$ and choose the one with the larger objective function gain $\bigtriangledown \theta^{r}_{S}$.
+
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
+%\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
+%\label{figure1}
+%\end{figure}
+
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
+%\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
+%\label{figure2}
+%\end{figure}
+
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[scale=0.6]{NtE.eps}
+%\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
+%\label{figure3}
+%\end{figure}
+
+\section{Stopping Criteria}\label{stopping criteria}
+As we have explained in section \ref{section lagrange duality}, the upper bound of Lagrangian dual objective function is determined by primal objective function, further more the optimal of primal and dual objective function is found if and only if the equality holds, that is
+\begin{equation}
+\theta(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)
+\label{duality equal}
+\end{equation}
+\begin{equation}
+\frac{1}{2}||\mathbf{w}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
+\label{simple primal}
+\end{equation}
+(\ref{final complex lagrange duality}) can be rewritten as follow by substituting $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\theta(\lambda^{r}, \lambda^{i})=-\frac{1}{2}<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>-\frac{1}{2}<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>+<Re(\mathbf{y})^{T}, \lambda^{r}>+<Im(\mathbf{y})^{T}, \lambda^{i}>\\
+-\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
+\label{simple dual function}
+\end{IEEEeqnarray}
+Similarly, (\ref{complex duality regularization1}) can be formulated as 
+\begin{IEEEeqnarray}[\relax]{l}
+||\mathbf{W}||^{2}_{\mathbb{H}}=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>,
+\label{simple regularization}
+\end{IEEEeqnarray}
+hence, duality gap can be formulated as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+G(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)-\theta(\lambda^{r},\lambda^{i})=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-<Re(\mathbf{y})^{T}, \lambda^{r}>-<Im(\mathbf{y})^{T}, \lambda^{i}>\\
+-\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.
+\label{simple duality gap}
+\end{IEEEeqnarray}
+As we explained in section \ref{risk functional}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
+\begin{equation}
+R(\xi)=\frac{1}{2}\xi^{2},
+\label{risk function1}
+\end{equation} 
+hence 
+\begin{equation}
+\tilde{R}(\xi)=R(\xi)-\xi R{'}(\xi)=-\frac{1}{2}\xi^{2},
+\label{risk function2}
+\end{equation}
+In $\epsilon$-SVR, the objective to employ slack variables $\xi$ is to deal with the outliers that outside $\epsilon$ tube to compensate the influence from noise.
+Therefore 
+\begin{IEEEeqnarray}[\relax]{l}
+\xi^{r}_{i}=Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})-\epsilon\\
+\hat{\xi}^{r}_{i}=Re(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})-Re(\mathbf{y}_{i})-\epsilon
+\label{outlier1}
+\end{IEEEeqnarray}
+Because $\xi^{r}\hat{\xi}^{r}=0$ (estimation can only exceed $\epsilon$ tube in one direction), therefore there is only one of $\xi$ and $\hat{\xi}$ need to be considered, thus 
+\begin{IEEEeqnarray}[\relax]{l}
+\xi^{r}_{i}(\hat{\xi}^{r}_{i})=\max(0, |Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon)\\
+\xi^{i}_{i}(\hat{\xi}^{i}_{i})=\max(0, |Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon)\\
+\xi\hat{\xi}=0,
+\label{outlier2}
+\end{IEEEeqnarray} 
+Therefore the risk function can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}(|Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|)^{2}_{\epsilon}\\
+\label{simple risk function1}
+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}(|Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|)^{2}_{\epsilon}
+\label{simple risk function2}
+\end{IEEEeqnarray}
+where $()_{\epsilon}$ denotes $\epsilon$ insensitive function as we mention in section \ref{risk functional}. Based on (\ref{complex duality regression function}), we have 
+\begin{IEEEeqnarray}[\relax]{l}
+Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}^{r}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}^{i}_{ij}\\
+Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}^{r}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}^{i}_{ij}
+\label{intermediate function1}
+\end{IEEEeqnarray}
+we define two intermediate variables $\Phi$ and $\Psi$
+\begin{IEEEeqnarray}[\relax]{l}
+\label{intermedia function 2a}
+\Phi^{r}=Re(\mathbf{y})-\mathbf{K}^{r}
+\lambda^{r};
+\Phi^{i}=Im(\mathbf{y})-\mathbf{K}^{r}\lambda^{i}\\
+\Psi^{r}=\mathbf{K}^{i}\lambda^{i};
+\Psi^{i}=-\mathbf{K}^{i}\lambda^{r}\\\label{intermediate function 2b}
+\nonumber
+\end{IEEEeqnarray} 
+Therefore based on (\ref{simple risk function1})-(\ref{intermediate function2}), duality gap in (\ref{simple duality gap}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+G(\lambda^{r}, \lambda^{i})=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-<Re(\mathbf{y})^{T}, \lambda^{r}>-<Im(\mathbf{y})^{T}, \lambda^{i}>\\
++\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.
+\label{simple duality gap final}
+\end{IEEEeqnarray}
+Based on objective function in (\ref{simple dual function}), (\ref{simple duality gap final}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+G=(\lambda_{r}, \lambda_{i})=<Re(\mathbf{y})^{T}, \lambda^{r}>+<Im(\mathbf{y})^{T}, \lambda^{i}>-\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>-2\theta(\lambda_{i}, \lambda_{j})\\
+-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.\label{simple duality gap ratio1}
+\end{IEEEeqnarray}
+The duality gap between primal problem and dual problem is used to evaluate how close a solution is to global minimum. In our scenario, duality gap is employed as stopping criteria.
+Therefore to make stopping criteria more effective to monitor if algorithm convergent, we monitor the ratio by a value of tolerance (usually this tolerance is set to $10^{-3}$).
+\begin{equation}
+\frac{G}{G+\theta}
+\label{simple duality gap ratio2}
+\end{equation}
+\subsection{Update $\Phi$, $\Psi$ and $G$}
+Here we give the pseudo code to update $\Phi$, $\Psi$ and $G$.
+
+Based on the definition of $\Phi$ and $\Psi$ in (\ref{intermedia function 2a}) and (\ref{intermediate function 2b}), we have the following procedure to update $\Phi$ and $\Psi$ in real channel and imaginary channel, assume the optimization coordinate updated in each channel are $1$ and $2$.\\
+\begin{algorithm}[htb]
+\begin{algorithmic}
+\Procedure{\textbf{1}. Update $\Phi^{r}$ and $\Psi^{i}$ in real channel}{}
+\For{$i=1:N_{r}$}
+\State $\Phi_{i}^{r}=\Phi_{i}^{r}-\sigma_{1}^{r}\mathbf{K}^{r}_{i1}-\sigma_{2}^{r}\mathbf{K}_{i2}^{r}$
+\State $\Psi_{i}^{i}=\Psi_{i}^{i}-\sigma_{1}^{r}\mathbf{K}^{i}_{i1}-\sigma_{2}^{r}\mathbf{K}^{i}_{i2}$
+\EndFor
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\begin{algorithm}[htb]
+\begin{algorithmic}
+\Procedure{\textbf{2}. Update $\Phi^{i}$ and $\Psi^{r}$ in imaginary channel}{}
+\For{$i=1:N_{r}$}
+\State $\Phi_{i}^{i}=\Phi_{i}^{i}-\sigma_{1}^{i}\mathbf{K}^{r}_{i1}-\sigma_{2}^{i}\mathbf{K}_{i2}^{r}$
+\State $\Psi_{i}^{r}=\Psi_{i}^{r}+\sigma_{1}^{i}\mathbf{K}^{i}_{i1}+\sigma_{2}^{i}\mathbf{K}^{i}_{i2}$
+\EndFor
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
+Then the risk function term in (\ref{simple duality gap final}) is updated as following
+\begin{algorithm}[htb]
+\begin{algorithmic}
+\Procedure{\textbf{3}. Update risk function in real channel}{$\chi^{r}$}
+\State $\chi^{r}=0$  \Comment{initial risk term}
+\For{$i=1:N_{r}$}
+\If{$|\Phi^{r}_{i}+\Psi^{r}_{i}|>\epsilon$}
+\State $\chi^{r}+=(|\Phi^{r}_{i}+\Psi^{r}_{i}|-\epsilon)^{2}$
+\EndIf
+\EndFor
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[htb]
+\begin{algorithmic}
+\Procedure{\textbf{4}. Update risk function in imaginary channel}{$\chi^{i}$}
+\State $\chi^{i}=0$  \Comment{initial risk term}
+\For{$i=1:N_{r}$}
+\If{$|\Phi^{i}_{i}+\Psi^{i}_{i}|>\epsilon$}
+\State $\chi^{i}+=(|\Phi^{i}_{i}+\Psi^{i}_{i}|-\epsilon)^{2}$
+\EndIf
+\EndFor
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+The pseudo code to update duality gap $G$ based on (\ref{simple duality gap final}) is shown as follow (assume the coordinate updated in real channel is $i$ and $j$, in imaginary channel is $m$ and $f$.
+\begin{algorithm}[htb]
+\begin{algorithmic}
+\Procedure{\textbf{5}. Update $G$}{ratio of $G$}
+\State $G+=Re(\mathbf{y}_{1})\sigma^{r}_{i}+Re(\mathbf{y}_{2})\sigma^{r}_{j}$
+\State $G+=Im(\mathbf{y}_{1})\sigma^{i}_{m}+Re(\mathbf{y}_{2})\sigma^{i}_{f}$
+\State $G-=\epsilon(|\lambda^{r}_{i}+\sigma^{r}_{i}|-|\lambda^{r}_{i}|+|\lambda^{r}_{j}+\sigma^{r}_{j}|-|\lambda^{r}_{j}|)$
+\State $G-=\epsilon(|\lambda^{i}_{m}+\sigma^{i}_{m}|-|\lambda^{i}_{m}|+|\lambda^{i}_{f}+\sigma^{i}_{f}|-|\lambda^{i}_{f}|)$
+\State $G-=2(\bigtriangledown \theta(\sigma^{r}_{i},\sigma^{r}_{j},\sigma^{i}_{m},\sigma^{i}_{f}))$
+\State $G-=$
+\EndProcedure
+\label{update G Phi and Psi}
+\end{algorithmic}
+\end{algorithm}
+
+Here we give the pseudo code for sequential 1-D searching 2-D solver
+
+\begin{algorithm}[htb]
 \begin{algorithmic}
@@
 \State Step 3.
-\State Sequential 2-D solver with or without damping \Comment{find two dual variables to be updated} 
+\State Sequentia 1-D searching 2-D solver with or without damping \Comment{find two optimization variables to be updated} 
 \State Step 4.
-\State  $G$
+\State \textbf{Procedure 1} update $G$, $\Phi$ and $\Psi$
 \State Step 5.
@@
 
-\begin{algorithm}
+\begin{algorithm}[htb]
 \begin{algorithmic}
-\Procedure{Sequential 2-D solver without Damping}{$1st$, $2nd$} 
+\Procedure{\textbf{2}. Sequential 2-D solver without Damping}{$1st$, $2nd$} 
 \For{$i=1:N_{r}$}
@@
 \end{algorithmic}
-\caption{Sequential 2-D Solver without Damping}
+%\caption{Sequential 2-D Solver without Damping}
 \label{1D2D Nodamping}
@@
 \begin{algorithmic}
-\Procedure{Sequential 2-D solver with Damping}{$1s_{1}t$,$1st_{2}$}
+\Procedure{\textbf{3}. Sequential 2-D solver with Damping}{$1s_{1}t$,$1st_{2}$}
 \For{$i=1:N_{r}$}\Comment{First round searching}
@@
 \end{algorithmic}
-\caption{Sequential 2-D Solver with Damping}
+%\caption{Sequential 2-D Solver with Damping}
 \label{1D2D damping}
@@
 
-\section{Initialization}\label{Initialization}
- Computer simulations are made for different sizes of V-BLAST MIMO systems, with $5\leq N_{r} \leq 100, 5 \leq N_{t} \leq N_{r}$, the empirical estimation of logarithmic expectation of $\phi_{om}$, $E[\ln(\phi_{om})]_{em}$, is calculated by taking average over $1e4$ channel realizations for each size of MIMO systems, as shown in Fig.\ref{figure1}, the Theoretical logarithmic expectation of $\phi_{om}$ $E[\ln(\phi_{om})]_{t}$ in (\ref{formula25}) is plotted in Fig.\ref{figure2}.
-Average deviation between $E[\ln(\phi_{om})]_{em}$ and $E[\ln(\phi_{om})]_{t}$ is also calculated, $V_{em-t}= 7.3043e-04$.
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
-%\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
-%\label{figure1}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
-%\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
-%\label{figure2}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[scale=0.6]{NtE.eps}
-%\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
-%\label{figure3}
-%\end{figure}
-
-Fig.\ref{figure3} demonstrates the relation between the number of users ($N_{t}$) and $E[\ln(\phi_{om})]_{t}$ under cases of different numbers of antennas at base station ($N_{r}$).
-From Fig.\ref{figure3}, we can see, on the one hand, with $N_{r}$ fixed, $E[\ln(\phi_{om})]$ decreases while $N_{t}$ increases, however the gradient of each curve becomes more and more gentle.
-On the other hand, when $N_{r}$ becomes larger $E[\ln(\phi_{om})]$ becomes more insensitive to variation of $N_{t}$.
-\section{Stopping Criteria}\label{stopping criteria}
-As we have explained in section \ref{section lagrange duality}, the upper bound of Lagrangian dual objective function is determined by primal objective function, further more the optimal of primal and dual objective function is found if and only if the equality holds, that is
-\begin{equation}
-\theta(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)
-\label{duality equal}
-\end{equation}
-\begin{equation}
-\frac{1}{2}||\mathbf{w}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal}
-\end{equation}
-(\ref{final complex lagrange duality}) can be rewritten as follow by substituting $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\lambda^{r}, \lambda^{i})=-\frac{1}{2}<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>-\frac{1}{2}<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>+<Re(\mathbf{y})^{T}, \lambda^{r}>+<Im(\mathbf{y})^{T}, \lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
-\label{simple dual function}
-\end{IEEEeqnarray}
-Similarly, (\ref{complex duality regularization1}) can be formulated as 
-\begin{IEEEeqnarray}[\relax]{l}
-||\mathbf{W}||^{2}_{\mathbb{H}}=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>,
-\label{simple regularization}
-\end{IEEEeqnarray}
-hence, duality gap can be formulated as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)-\theta(\lambda^{r},\lambda^{i})=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-<Re(\mathbf{y})^{T}, \lambda^{r}>-<Im(\mathbf{y})^{T}, \lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.
-\label{simple duality gap}
-\end{IEEEeqnarray}
-As we explained in section \ref{risk functional}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
-\begin{equation}
-R(\xi)=\frac{1}{2}\xi^{2},
-\label{risk function1}
-\end{equation} 
-hence 
-\begin{equation}
-\tilde{R}(\xi)=R(\xi)-\xi R{'}(\xi)=-\frac{1}{2}\xi^{2},
-\label{risk function2}
-\end{equation}
-In $\epsilon$-SVR, the objective to employ slack variables $\xi$ is to deal with the outliers that outside $\epsilon$ tube to compensate the influence from noise.
-Therefore 
-\begin{IEEEeqnarray}[\relax]{l}
-\xi^{r}_{i}=Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})-\epsilon\\
-\hat{\xi}^{r}_{i}=Re(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})-Re(\mathbf{y}_{i})-\epsilon
-\label{outlier1}
-\end{IEEEeqnarray}
-Because $\xi^{r}\hat{\xi}^{r}=0$ (estimation can only exceed $\epsilon$ tube in one direction), therefore there is only one of $\xi$ and $\hat{\xi}$ need to be considered, thus 
-\begin{IEEEeqnarray}[\relax]{l}
-\xi^{r}_{i}(\hat{\xi}^{r}_{i})=\max(0, |Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon)\\
-\xi^{i}_{i}(\hat{\xi}^{i}_{i})=\max(0, |Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon)\\
-\xi\hat{\xi}=0,
-\label{outlier2}
-\end{IEEEeqnarray} 
-Therefore the risk function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}(|Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|)^{2}_{\epsilon}\\
-\label{simple risk function1}
-R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}(|Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|)^{2}_{\epsilon}
-\label{simple risk function2}
-\end{IEEEeqnarray}
-where $()_{\epsilon}$ denotes $\epsilon$ insensitive function as we mention in section \ref{risk functional}. Based on (\ref{complex duality regression function}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}^{r}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}^{i}_{ij}\\
-Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}^{r}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}^{i}_{ij}
-\label{intermediate function1}
-\end{IEEEeqnarray}
-we define two intermediate variables $\Phi$ and $\Psi$
-\begin{IEEEeqnarray}[\relax]{l}
-\Phi^{r}=Re(\mathbf{y})-\mathbf{K}^{r}
-\lambda^{r};
-\Phi^{i}=Im(\mathbf{y})-\mathbf{K}^{r}\lambda^{i}\\
-\Psi^{r}=\mathbf{K}^{i}\lambda^{i};
-\Psi^{i}=-\mathbf{K}^{i}\lambda^{r}\\
-\nonumber
-\label{intermediate function2}
-\end{IEEEeqnarray} 
-Therefore based on (\ref{simple risk function1})-(\ref{intermediate function2}), duality gap in (\ref{simple duality gap}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\lambda^{r}, \lambda^{i})=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-<Re(\mathbf{y})^{T}, \lambda^{r}>-<Im(\mathbf{y})^{T}, \lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.
-\label{simple duality gap final}
-\end{IEEEeqnarray}
-The duality gap between primal problem and dual problem is used to evaluate how close a solution is to global minimum.
-In our scenario, duality gap is employed as stopping criteria because of low computational cost and reliable performance comparing to monitor KKT complementary condition.
-
 \section{Hyperparameter Setting}
@@
 \section{Computer Simulations}
-
+Computer simulation is launched to test the detection and run time performance of proposed dual channel complex support vector detection algorithm.
+For sake of brevity, the real case is tested first, all the experiments are made by C, compiled by gcc version 4.8.3 on 64 bit Fedora (release 19) Linux system.
+The experiment platform is a desktop computer with I5-4th generation CPU with quad processing cores, 3.2 GHz clock rate, 8 GB RAM.
+
+For sake of brevity, we consider a real uncoded spatial multiplex large MIMO system to simulate one channel of the proposed dual channel complex support vector detection algorithm.
+with $N_{r}$ received antennas and $N_{t}$ transmitted antennas.
+The propagation channel matrix is constructed by channel gain components that are identically independent distributed (i.i.d) Gaussian random variables with zero mean and unit variance.
+transmitted symbols are mutually independent modulated by $M$ PAM with normalized average energy $\frac{1}{N_{t}}$, transmitted over flat fading channel, the sample of noise is AWGN with zero mean and variance $\frac{1}{10^{SNR/10}}$, where $SNR$ denotes the signal to noise ratio.
+We make experiment to low loading factor system $100\times 40$ and full loading factor $100\times 100$, Fig \ref{SER performance} shows the symbol error rate (SER) performance.  
+\begin{figure}
+\centering
+\def\svgwidth{\columnwidth}
+\input{BER_curve_real_system.pdf_tex}
+\caption{SER performance of $100\times 100 $ and $100\times 40$ MIMO system}
+\label{SER performance}
+\end{figure}
 % An example of a floating figure using the graphicx package.
@@
 % \fnbelowfloat command of the stfloats package.
+\section{Complexity Analysis}
 
@@
 Appendix two text goes here.
-\section{}
-Let $\mathbf{A}\in \mathbb{C}^{m\times m}$, $A\sim \mathbb{C}W(n, \mathbf{\Sigma})$, $\mathbb{C}W(n, \mathbf{\Sigma})$ denotes complex Wishart distribution with $n$ degrees of freedom and covariance matrix $\mathbf{\Sigma}$.
-It is obvious $\mathbf{A}$ is Hermition positive definite matrix, $\mathbf{A}=\mathbf{A}^{H}>0$.
-
-The pdf of $\mathbf{A}$ can be written as\cite{nagar2011expectations}:
-\begin{equation}
-f(\mathbf{A})=\{\tilde{\Gamma}_{m}(n)det(\mathbf{\Sigma})^{n} \}^{-1}det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A}),
-\label{Appendequa1}
-\end{equation}
-where $\tilde{\Gamma}_{m}(\beta)$ denotes multivariate complex Gamma function defined by:
-\begin{equation}
-\tilde{\Gamma}_{m}(\beta)=\pi^{\frac{m(m-1)}{2}}\prod_{i=1}^{m}\Gamma(\beta-i+1)\quad Re(\beta)>m-1.
-\label{Appendequa2}
-\end{equation}
-Furthermore, from \cite{nagar2011expectations}, we have
-
-\begin{equation}
-\tilde{\Gamma}_{m}(\beta)=\int_{\mathbf{X}=\mathbf{X}^{H}>0}etr(-\mathbf{X})det(\mathbf{X})^{\beta-m}d
-\mathbf{X} \quad Re(\beta)>m-1.
-\label{Appendequa3}
-\end{equation}
-We derive logarithmic expectation of $det(\mathbf{A})$
-\begin{eqnarray}
-\nonumber
-E[\ln(det(\mathbf{A}))]&=&\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))f(\mathbf{A})d\mathbf{A}\\
-\nonumber
-&=&\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))\{\tilde{\Gamma}_{m}(n)det(\mathbf{\Sigma})^{n} \}^{-1}det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A})d\mathbf{A}\\
-&=&\frac{det(\mathbf{\Sigma})^{-n}}{\tilde{\Gamma}_{m}(n)}\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A})d\mathbf{A},
-\label{Appendequa4}
-\end{eqnarray}
-if $\mathbf{\Sigma}=\mathbf{I}$, (\ref{Appendequa4}) can be written as 
-\begin{equation}
-E[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}etr(-\mathbf{A})d\mathbf{A}.
-\label{Appendequa5}
-\end{equation}
-Because $\frac{d}{dn}[det(\mathbf{A})]^{n-m}=\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}$, (\ref{Appendequa5}) can be rewritten as
-\begin{equation}
-E[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\frac{d}{dn}\int_{\mathbf{A}=\mathbf{A}^{H}>0}etr(-\mathbf{A})det(\mathbf{A})^{n-m}d\mathbf{A},
-\label{Appendequa6}
-\end{equation}
-using (\ref{Appendequa3}), (\ref{Appendequa6}) can be rewritten as 
-\begin{equation}
-E[\ln(\mathbf{A})]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}.
-\label{Appendequa7}
-\end{equation}
-Based on (\ref{Appendequa2}), we have 
-\begin{equation}
-\tilde{\Gamma}^{'}_{m}(n)=\pi^{\frac{m(m-1)}{2}}\sum_{i=1}^{m}[\Gamma^{'}(n-i+1)\prod_{j=1,j\neq i }^{m}\Gamma(n-j+1)],
-\end{equation}
-Thus we have 
-\begin{equation}
-E[\ln(det(\mathbf{A}))]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}=\sum_{i=1}^{m}\frac{\Gamma^{'}(n-i+1)}{\Gamma(n-i+1)}=\sum_{i=1}^{m}\psi(n-i+1),
-\label{Appendequa8}
-\end{equation}
-where $\psi$ denotes Digamma function.
-\section{}
-If $x\sim Gamma(n, \theta)$, with shape parameter $k$ and scale parameter $\theta$, $x>0$, $\Gamma(k)$ denotes Gamma function, the density function of Gamma distribution is
-\begin{equation}
-f(x,k,\theta)=\frac{x^{k-1}e^{-x/\theta}}{\Gamma(k)\theta^{k}}.
-\label{Appendequa9}
-\end{equation}
-Thus we have 
-\begin{equation}
-E[\ln(x)]=\frac{1}{\Gamma(k)}\int_{0}^{\infty}\ln(x)x^{k-1}e^{-x/\theta}\theta^{-k}dx,
-\label{Appendequa10}
-\end{equation}
-define $z=x/\theta$ and since $\Gamma(k)=\int_{0}^{\infty}x^{k-1}e^{-x}dx$, (\ref{Appendequa10}) can be rewritten as
-\begin{equation}
-E[\ln(x)]=\ln(\theta)+\frac{1}{\Gamma(k)}\int_{0}^{\infty}\ln(z)z^{k-1}e^{-z}dz.
-\label{Appendequa11}
-\end{equation}
-Because $\frac{d(z^{k-1})}{dk}=\ln(z)z^{k-1}$, (\ref{Appendequa11}) can be rewritten as
-\begin{eqnarray}
-\nonumber
-E[\ln(z)]&=&\ln(\theta)+\frac{1}{\Gamma(k)}\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz\\
-\nonumber
-&=&\ln(\theta)+\frac{\Gamma^{'}(k)}{\Gamma(k)}\\
-\nonumber
-&=&\ln(\theta)+\psi(k),
-\label{Appendequa12}
-\end{eqnarray}
-where $\psi(k)$ denotes Digamma function.
-\section{}
-$x_{1}, x_{2}, \cdots x_{N_{t}}$ are independent beta variables, the probability density function (pdf) can be written as: 
-\begin{equation}
-f(x_{i})=\frac{1}{\mathbb{B}(k_{1}^{i}, k_{2}^{i})}x_{i}^{k_{1}^{i}-1}(1-x_{i})^{k_{2}^{i}-1},
-\label{Appendequal13}
-\end{equation}
-define $y_{i}=-\ln(x_{i})=g(x_{i})$, Based on Jacobian transformation, we have 
-\begin{equation}
-f_{y_{i}}(\rho)=|\frac{dy_{i}}{dx_{i}}|^{-1}f_{x_{i}}(g^{-1}(\rho))=\frac{1}{\mathbb{B}(k_{1}^{i},k_{2}^{i})}e^{-k_{1}^{i}\rho}(1-e^{-\rho})^{k_{2}^{i}-1}.
-\label{Appendequal14}
-\end{equation}
-where (\ref{Appendequal14}) can be alternatively expressed as \cite{bhargava1981distribution}
-\begin{equation}
-f_{y_{i}}(\rho)=\sum_{j^{i}=0}^{k_{2}^{i}-1}c(k_{1}^{i},k_{2}^{i}, j^{i})(k_{1}^{i}+j^{i})exp(-(k_{1}^{i}+j^{i})\rho),
-\label{Appendequal15}
-\end{equation} 
-where $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
-Based on the lemma 1 of \cite{bhargava1981distribution}, if $a_{1}, a_{2}, \cdots a_{n}$ are independent exponentially distributed random variables, with pdf given by
-\begin{equation}
-t_{i}exp(-t_{i}a_{i})，
-\label{Appendequal16}
-\end{equation} 
-then pdf of $a=\sum_{i=1}^{n}a_{i}$ can be written as
-\begin{equation}
-f(a|\mathbf{t})=\prod_{i=1}^{n}t_{i}\sum_{i=1}^{n}[exp(-t_{i}a)/\prod_{j=1\\ j\neq i}^{j=n}(t_{j}-t_{i})],
-\label{Appendequal17}
-\end{equation}
-where $t=[t_{1}, t_{2}, \cdots t_{n}]$.
-The pdf of $y_{i}$ can be viewed as the weighting summation of exponential distribution functions, define $y=\sum_{i=1}^{n}y_{i}$, based on (\ref{Appendequal17}), the pdf of $y$ is given by
-\begin{equation}
-f_{y}(m)=\sum_{\mathbf{j}}\{[\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i}, j^{i})]f(m|\mathbf{k_{1}}+\mathbf{j})\},
-\label{Appendequal18}
-\end{equation}
-where $\sum_{\mathbf{j}}=\sum_{j^{1}}\sum_{j^{2}}\cdots \sum_{j^{n}}$, the range of $j^{i}$ is defined by $j^{i}\in [0, k_{2}^{i}]$, $f(m|\mathbf{k_{1}}+\mathbf{j})=(\prod_{i=1}^{N_{t}}(k_{1}^{i}+j^{i}))\sum_{i=1}^{N_{t}}[exp(-(k_{1}^{i}+j^{i})m)/\prod_{j=1\\ j\neq i}^{N_{t}}(k_{1}^{j}+j^{j}-k_{1}^{i}-j^{i})]$, $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j^{1}, k_{1}^{2}+j^{2} \cdots k_{1}^{n}+j^{n}]$.
-we define $U=exp(-y)=\prod_{i=1}^{n}x_{i}$, using Jacobian transformation, the pdf of $U$ is given by
-\begin{equation}
-f_{U}(u)=|\frac{du}{dy}|^{-1}f_{y}(-\ln(u))=\frac{1}{u}\sum_{\mathbf{j}}\{[\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i},j^{i})]f(-\ln(u)|\mathbf{k_{1}}+\mathbf{j})\}.
-\label{Appendequal19}
-\end{equation}
 

### 2015-09-11 Report Aug 5 2015/SNR_BER_new.m

@@ -1,0 +1,53 @@
+%this is for ploting the figure of SNR-BER curve
+%the output of this code generate a eps file 
+% sim8_4_0_18=[0.22589062154, 0.15894874930, 0.08640749753, 0.03090812452, 0.00636250013, 0.00079124997, 0.00005481876,0.00000279009,0.00000014225951464822, 0.00000000451437990952];
+% sim8_16_0_18=[0.25537124276, 0.22414547205, 0.19270686805, 0.15720969439, 0.10538093746, 0.04198125005, 0.00701593747, 0.00052656251,0.00004961727, 0.00000235999];
+% sim8_64_0_22=[0.30989542603, 0.28304228187, 0.25555500388, 0.22751520574, 0.19991666079, 0.16876062751, 0.12789249420, 0.07114583254, 0.02219000086, 0.00312604173, 0.00018895834,0.00000633392  ];
+% sim16_4_0_14=[0.23751124740, 0.17347000539, 0.09674874693, 0.03350968659, 0.00618375000, 0.00060968747, 0.00002066603,0.00000026777  ];
+% sim16_16_0_18=[0.25537124276, 0.22414547205, 0.19270686805, 0.15720969439, 0.10538093746, 0.04198125005, 0.00701593747, 0.00052656251,0.00002031656,0.00000020876338590830];
+% 0.25537124276 0.22414547205 0.19270686805 0.15720969439, 0.075001, 0.019427, 0.002040, 0.000093,
+% sim32_4_0_14=[0.24545359612, 0.18672686815, 0.11097452790, 0.04044124857, 0.00811937544, 0.00093781250,0.00005755865,0.00000097851];
+% sim48_4_0_14=[0.25442603230, 0.19931979477, 0.12637500465, 0.05224249884, 0.01231614593, 0.00185479166, 0.00016166667,0.00000549426];
+% sim_100_40_old=[0.26819999999999999396, 0.19164999999999998703, 0.11859999999999999709,...
+%     0.06090000000000000274, 0.02457499999999999962, 0.00645000000000000000 ,0.00121277617675312195,0.00005600000000000000,0.00000121703063996339...
+%     0.00000000607241023727 ]; %the old one with one coordinate updated
[…]

### 2015-09-21 Report Aug 5 2015/Report Aug 2015.tex
Report modification

@@
 \usepackage{algpseudocode}
-
+\usepackage{multirow}
+\usepackage{calc}
 % Some very useful LaTeX packages include:
@@
 % Do not put math or special symbols in the title.
-\title{Report}
+\title{Report: Complex Support Vector Detector for Large MIMO System}
 
@@
 The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve bandwidth efficiency) and diversity gain (better reliability of communication link) is obtained by employing spatial domain.
-Large MIMO (also called Massive MIMO) is an upgrade version of conventional MIMO system, it equips   unprecedentedly hundreds of low power low price antennas at base station (BS), serving several tens of terminals simultaneously, It can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness\cite{rusek2013scaling}\cite{larsson2014massive}.
+Large MIMO (also called Massive MIMO) is an upgrade version of conventional MIMO system, it equips unprecedented hundreds of low power low price antennas at base station (BS), serving several tens of terminals simultaneously, It can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness\cite{rusek2013scaling}\cite{larsson2014massive}.
 
@@
 Uplink Detector is one of the key components in large MIMO system.
-With orders magnitude more antennas equipped at BS, benefit and challenge coexist in designing of detection algorithms for large MIMO uplink, on the one hand, large number of receive antennas provide potential of large diversity gain, on the other hand, complexity of the algorithm becomes extremely crucial to make system practical.
+With orders magnitude more antennas equipped at BS, benefits and challenges coexist in designing of detection algorithms for large MIMO uplink, on the one hand, large number of receive antennas provide potential of large diversity gain, on the other hand, complexity of the algorithm becomes extremely crucial to make system practical.
 
@@
 
-Suboptimal linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, which have good performance for low loading factor in massive MIMO system (that is the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
+Suboptimal linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
 In the last several years, a set of detection algorithms are proposed with complexities that is comparable with LD-OSIC and suboptimal performance can be achieved.
@@
 
-Research and industry interest of SVM boosted since 1990s, promoted by related works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}
+Research and industry interest of SVM boosted since 1990s, promoted by related works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
 Moreover, the kernel based methods\cite{scholkopf2002learning} carries out nonlinear learning task by mapping input data sets into high dimensional feature space, then replacing inner product of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
-This rational is supported mathematically by Reproducing Kernel Hilbert Space (RKHS).
-Based on the same regularized risk function principle, ϵ-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.
+This rationale is supported mathematically by Reproducing Kernel Hilbert Space (RKHS).
+Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.
 
@@
 Until now, although the mathematical foundation of kernel based methods is RKHS which is defined in complex domain, the most of practitioners are dealing with real data set.
-In communication and signal processing area, the channel gains, signals, waveforms etc.
+However in communication and signal processing area, the channel gains, signals, waveforms etc.
 are all represented in complex form.
@@
 \end{equation} 
-where $\mathbf{w}$ denotes regression coefficient vector, $\Phi(x)$ denotes the mapping of $\mathbf{x}$ to higher dimensional feature space. \ref{equation1}.
+where $\mathbf{w}$ denotes regression coefficient vector, $\Phi(x)$ denotes the mapping of $\mathbf{\mathbf{x}}$ to higher dimensional feature space.
 
@@
 \nonumber
-\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
+\min_{\mathbf{w}} \frac{1}{2}||\mathbf{w}||^{2}+C\sum_{j=1}^{l}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
 s.t. \left\{\begin{array}{ll}
@@
 $\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function.
-$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes risk function, the simplest risk function is $R(x)=x$, risk function is determined by the statistical distribution of noise\cite{smola2004tutorial}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
-$C\sum_{i=1}^{l}(\xi_{i}+\hat{\xi}_{i})$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
+$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes risk function, the simplest risk function is $R(u)=u$, risk function is determined by the statistical distribution of noise\cite{smola2004tutorial}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
+$C\sum_{i=1}^{l}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
 \subsection{Risk Functional}\label{risk functional}
-From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $f_{estimate}(\mathbf{x})$, $c(\mathbf{x},y,f_{estimate}(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
+From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $c(\mathbf{x},y,f(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
 Assume the data samples are i.i.d.
@@
 \nonumber
-maximize\quad \prod_{i=1}^{l}P(y_{i}|f_{estimation}(\mathbf{x}_{i}))&=maximize\quad \prod_{i=1}^{l}P(\xi_{i})\\
-&=maximize\quad \prod_{i=1}^{l}P(y_{i}-f(\mathbf{x}_{i})),
+\max_{f()}\quad \prod_{i=1}^{l}P(y_{i}|f_{true}(\mathbf{x}_{i}))&=\max\quad \prod_{i=1}^{l}P(\xi_{i})\\
+&=\max\quad \prod_{i=1}^{l}P(y_{i}-f_{true}(\mathbf{x}_{i})),
 \label{risk function1}
@@
 \begin{eqnarray}
-maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))),
+maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f(\mathbf{x}_{i}))),
 \label{risk function2}
@@
 \begin{eqnarray}
-c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i}))=-log(P(y_{i}-f_{estimation}(\mathbf{x}_{i}))).
+c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-log(P(y_{i}-f(\mathbf{x}_{i}))).
 \label{risk function3}
@@
 \begin{equation}
-minimize\quad  \sum_{i=1}^{l}c(\mathbf{x}_{i}, y_{i}, f_{estimation}(\mathbf{x}_{i})),
+minimize\quad  \sum_{i=1}^{l}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
 \label{Total risk function}
@@
 \begin{eqnarray}
-|x|_{\epsilon}=\left\{\begin{array}{ll}
-0   &if\quad |x|<\epsilon\\
-|x|-\epsilon  &otherwise\\
+|u|_{\epsilon}=\left\{\begin{array}{ll}
+0   &if\quad |u|<\epsilon\\
+|u|-\epsilon  &otherwise\\
 \end{array}\right.
@@
 \begin{equation}
-\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
+\tilde{c}(\mathbf{x}, y, f(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
 \label{cost function}
@@
 \begin{equation}
-minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f_{estimation}(\mathbf{x})),
+minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f}(\mathbf{x})),
 \label{total cost function}
@@
 \begin{equation}
-minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f_{estimation}(\mathbf{x}_{i})|_{\epsilon}))),
+minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
 \label{final cost function}
@@
 
-\section{Dual Channel Complex Support Vector Regression for Large MIMO system}\label{dual channel CSVR}
+\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
  Based on discrete time model of large MIMO uplink system in (\ref{discrete time MIMO system}), in our  regression model, the training data sample at detector is $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of channel propagation matrix $\mathbf{H}$, this yields a regression task without offset $b$:
@@
 \nonumber
-maximize \quad \Theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
+maximize \quad \theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
 \nonumber
@@
 \nonumber
-maximize \quad \Theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
+maximize \quad \theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
 \nonumber
@@
 \nonumber
-maximize \quad \Theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r})))\\
+maximize \quad \theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r})))\\
 \left\{\begin{array}{ll}
@@
 \nonumber
-maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})+\tilde{R}(\hat{\xi}^{i})))\\
+maximize \quad \theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})+\tilde{R}(\hat{\xi}^{i})))\\
 \left\{\begin{array}{ll}
@@
 Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) are symmetric, in this section we discuss real part only.
-By dividing the variables into work set $S$ and fixed set $N$, we have $(\alpha, \hat{\alpha})=((\alpha_{N}, \hat{\alpha}_{N})\mathbf{e}_{N}+(\alpha_{S}+\hat{\alpha}_{S})\mathbf{e}_{S})$, where $\mathbf{e}_{K}$ denotes the modified vector of $\mathbf{e}$ with the components in set $K$ zeroed, for sake of brevity， we replace $\alpha_{K}\mathbf{e}_{K}$ by $\alpha_{K}$.
+By dividing the variables into work set $S$ and fixed set $N$, we can divide vector $\alpha$ into two sub vectors, $[\alpha_{S}, \alpha_{N}]$.
 Thus (\ref{complex duality real part vectorizes}) can be changed to:
@@
 \nonumber
-maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}+2(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}(\alpha-\hat{\alpha})_{S}]
+maximize\quad \theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}+2(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}(\alpha-\hat{\alpha})_{S}]
 +Re(\mathbf{y})_{S}^{T}(\alpha-\hat{\alpha})_{S}-\\
@@
 \end{IEEEeqnarraybox*}\right]$ is a permutation of $\mathbf{K}^{r}$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$ 
-and  $\alpha_{S}\in \mathbb{R}^{N_{r}}$ denotes the vector with the components that do not belong to $S$ zeroed.
+and  $\alpha_{S}\in \mathbb{R}^{|S|}$ denotes the vector constitute of all the $\alpha_{i}\in S$.
 In each iteration, in (\ref{real part decomposition}), $\alpha_{N}$ is fixed and only the sub problem that correlated to $\alpha_{S}$ is solved i.e
 \begin{equation}
-maximize\quad \Theta_{S}^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]+[Re(\mathbf{y})_{S}^{T}-(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
-](\alpha-\hat{\alpha})_{S}-\epsilon<\mathbf{e}_{S}^{T}, (\alpha+\hat{\alpha})_{S}>,
+maximize\quad \theta_{S}^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]+[Re(\mathbf{y})_{S}^{T}-(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
+](\alpha-\hat{\alpha})_{S}-\epsilon<\mathbf{e}_{S}^{T}, (\alpha+\hat{\alpha})>,
 \label{subset optimization}
@@
 \begin{equation}
-maximize\quad \bigtriangledown \Theta_{S}=\Theta_{S}((\alpha_{S}+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}_{s}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta_{S}(\alpha_{S}, \hat{\alpha}_{S}),
+maximize\quad \bigtriangledown \theta_{S}=\theta_{S}((\alpha+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}+\hat{\delta}_{S}\mathbf{e}_{S}))-\theta_{S}(\alpha, \hat{\alpha}),
 \label{maximum gain work set selection}
@@
 \nonumber
-\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}[(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+2(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}]+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}](\delta-\hat{\delta})_{S}\\
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+2(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}]+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}](\delta-\hat{\delta})_{S}\\
 -\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S}](\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}
@@
 \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \Theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}
 \label{gain work set selection2}
@@
 The offset term is omitted in Large MIMO system, therefore different from SMO type algorithms, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration.
-However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{Training without offset}.
+However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{steinwart2011training}.
 Here we propose sequential 1-D work set selection strategy, which can approximate the performance of optimal 2-D work set selection, while only $O(n)$ searching times required for the former one instead of $O(n^{2})$ searching times.
-\subsection{Single Direction Solver}
+\subsection{Single Direction Solver}\label{single direction solver}
 Recall KKT complementary condition
@@
 \nonumber
-\frac{\partial \theta_{1}^{r}}{\partial \lambda^{new}_{1}}=-\lambda_{1}^{new}\mathbf{K}_{11}^{r}+Re(y_{1})-\sum_{j=2}^{N_{r}}\lambda_{j}^{new}\mathbf{K}_{1j}^{r}-\epsilon(sgn(\lambda^{new}_{1}))=\\
+\frac{\partial \theta_{1}^{r}}{\partial \lambda^{new}_{1}}=-\lambda_{1}^{new}\mathbf{K}_{11}^{r}+Re(y_{1})-\sum_{j=2}^{N_{r}}\lambda_{j}\mathbf{K}_{1j}^{r}-\epsilon(sgn(\lambda^{new}_{1}))=\\
 \nonumber
@@
 \end{equation}
-\subsection{Double Direction Solver}
+\subsection{Double Direction Solver}\label{double direction solver}
 Although omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however recent work in machine learning field shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained.
@@
 Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D solution by 1-D search approach, we will prove in large MIMO scenario, when $N_{t}$ is sufficient large, with channel hardening become effective, this approximation is very efficient.
-Here we propose two kinds of 1-D approximate searching strategy:\\
-1. 1-D searching without damping:\\
-do one time 1-D searching and calculate all the 1-D gain based on (\ref{gain of 1-D objective function}), then choose the coordinate with first and second largest 1-D gain as the candidates, then update the two candidates by 2-D solver as shown in (\ref{update lambda1}) and (\ref{update lambda2})\\
-2. 1-D searching with damping:\\
-do two times 1-D searchings, in the first round find optimization variable $i$ that can maximize 1-D gain, then in the second round, find $j$th optimization variable with the value of $i$th coordinate updated.
+Here we propose two kinds of 1-D approximate searching strategy:
+\subsubsection{ 1-D searching without damping}
+do one round 1-D searching and calculate all the 1-D gain based on (\ref{gain of 1-D objective function}), then choose the coordinates with first and second largest 1-D gain as the candidates, then update the two candidates by 2-D solver as shown in (\ref{update lambda1}) and (\ref{update lambda2})
+\subsubsection{ 1-D searching with damping}
+do two rounds 1-D searchings, in the first round find optimization variable $i$ that can maximize 1-D gain, then in the second round, find $j$th optimization variable with the value of $i$th coordinate updated.
 
@@
 \Phi^{i}=Im(\mathbf{y})-\mathbf{K}^{r}\lambda^{i}\\
+\label{intermediate function 2b}
 \Psi^{r}=\mathbf{K}^{i}\lambda^{i};
-\Psi^{i}=-\mathbf{K}^{i}\lambda^{r}\\\label{intermediate function 2b}
-\nonumber
-\end{IEEEeqnarray} 
-Therefore based on (\ref{simple risk function1})-(\ref{intermediate function2}), duality gap in (\ref{simple duality gap}) can be rewritten as 
+\Psi^{i}=-\mathbf{K}^{i}\lambda^{r}\\
+\nonumber
+\end{IEEEeqnarray} 
+Therefore based on (\ref{simple risk function1})-(\ref{intermediate function 2b}), duality gap in (\ref{simple duality gap}) can be rewritten as 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \subsection{Update $\Phi$, $\Psi$ and $G$}
-Here we give the pseudo code to update $\Phi$, $\Psi$ and $G$.
+In each iteration $\Phi$, $\Psi$ and $G$ are updated partially based on 2 updated optimization variables. Here we give the pseudo code to update $\Phi$, $\Psi$ and $G$.
 
@@
 \end{algorithm}
-The pseudo code to update duality gap $G$ based on (\ref{simple duality gap final}) is shown as follow (assume the coordinate updated in real channel is $i$ and $j$, in imaginary channel is $m$ and $f$.
+The pseudo code to update duality gap $G$ based on (\ref{simple duality gap final}) is shown as follow assume the coordinate updated in real channel is $i$ and $j$, in imaginary channel is $m$ and $f$.
 \begin{algorithm}[htb]
 \begin{algorithmic}
-\Procedure{\textbf{5}. Update $G$}{ratio of $G$}
+\Procedure{\textbf{5}. Update $G$}{}
 \State $G+=Re(\mathbf{y}_{1})\sigma^{r}_{i}+Re(\mathbf{y}_{2})\sigma^{r}_{j}$
@@
 \State $G-=\epsilon(|\lambda^{i}_{m}+\sigma^{i}_{m}|-|\lambda^{i}_{m}|+|\lambda^{i}_{f}+\sigma^{i}_{f}|-|\lambda^{i}_{f}|)$
-\State $G-=2(\bigtriangledown \theta(\sigma^{r}_{i},\sigma^{r}_{j},\sigma^{i}_{m},\sigma^{i}_{f}))$
-\State $G-=$
+\State $G-=2(\bigtriangledown \theta_{i,j,m,f}(\sigma^{r}_{i},\sigma^{r}_{j},\sigma^{i}_{m},\sigma^{i}_{f}))$\Comment{Update sub objective function based on (\ref{gain of 2-D objective function1})}
+\State $G+=C(\chi^{r}+\chi^{i})^{new}-(\chi^{r}+\chi^{i})$ \Comment{Update risk function term based on \textbf{Procedure 3} and \textbf{Procedure 4}}
+\State $G-=\sigma^{r}_{i}\sigma^{i}_{m}\mathbf{K}^{i}_{im}+\sigma^{r}_{i}\sigma^{i}_{f}\mathbf{K}^{i}_{if}+\sigma^{r}_{j}\sigma^{i}_{m}\mathbf{K}^{i}_{jm}+\sigma^{r}_{j}\sigma^{i}_{f}\mathbf{K}^{i}_{jf}+\sigma^{i}_{m}\sum_{k=1}^{N_{r}}\lambda_{k}^{r}\mathbf{K}^{i}_{km}+\sigma^{i}_{f}\sum_{k=1}^{N_{r}}\lambda_{k}^{r}\mathbf{K}^{i}_{kf}-\sigma^{r}_{i}\sum_{k=1}^{N_{r}}\lambda_{k}^{i}\mathbf{K}^{i}_{ki}-\sigma^{r}_{j}\sum_{k=1}^{N_{r}}\lambda_{k}^{i}\mathbf{K}^{i}_{kj}$ \Comment{Update $<\lambda^{r},\mathbf{K}^{i}\lambda^{i}>$}
 \EndProcedure
@@
 
-Here we give the pseudo code for sequential 1-D searching 2-D solver
-
+Pseudo code for sequential single searching 2-D solver is shown as following 
 \begin{algorithm}[htb]
 \begin{algorithmic}
-\Procedure{CSVD}{$\mathbf{y}$,$\mathbf{H}$}
-\State Step 1. Initialization
-\For{$i=1:N_{r}$}\Comment{initialize $\lambda^{r}$, $\lambda^{i}$, $\Phi^{r}$, $\Phi^{i}$, $\Psi^{r}$, $\Psi^{i}$ and duality gap $G$}
-\State $\lambda_{i}^{r}=0, \lambda_{i}^{i}=0$
-\State $\Phi_{i}^{r}=Re(y_{i}), \Phi_{i}^{i}=Im(y_{i})$
-\State $\Psi_{i}^{r}=0, \Psi_{i}^{i}=0$
-\EndFor 
-\State  Step 2. if $G>tol$, go to step 3, else go to Step 6
-\State Step 3.
-\State Sequentia 1-D searching 2-D solver with or without damping \Comment{find two optimization variables to be updated} 
-\State Step 4.
-\State \textbf{Procedure 1} update $G$, $\Phi$ and $\Psi$
-\State Step 5.
-\State $\tilde{x}=(\lambda^{r}+i\lambda^{i})\mathbf{H}$ \Comment{reconstruct $\mathbf{x}$}
-\State $\mathbf{x}=\mathbb{Q}(\tilde{x})$\Comment{$\mathbb{Q}(\cdot)$ denotes quantization operation based on symbol constellation}
-\State go back to Step 2
-\State Step 6. \textbf{Return} $\mathbf{x}$
-
-\EndProcedure
-\end{algorithmic}
-\label{CSVD algorithm}
-\caption{Dual Channel Complex Support Vector Detection Algorithm }
-\end{algorithm}
-
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{2}. Sequential 2-D solver without Damping}{$1st$, $2nd$} 
+\Procedure{\textbf{6}. Sequential single searching 2-D solver without Damping}{} 
+\State Step 1. Search for two optimization variables based on single direction solver
 \For{$i=1:N_{r}$}
-\State update $\lambda^{r}_{i}(\lambda_{i}^{i})$ by single direction solver
-\State calculate $\bigtriangledown \theta^{r}_{i}(\bigtriangledown \theta_{i}^{i})$\Comment{ calculate the gain of sub objective function}
+\State calculate $\bigtriangledown \theta^{r}_{i}(\bigtriangledown \theta_{i}^{i})$\Comment{Based on single direction solver \ref{single direction solver}}
 \EndFor
 \State choose the dual variable with first and the second largest gain of sub objective function, denoted as 1st and 2nd
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to 1st and 2nd
-\State \textbf{Return} 1st, 2nd
+\State Step 2. Update 1st and 2nd optimization variables based on double direction solver 
+\State update $\lambda^{r}_{1st}(\lambda^{i}_{1st})$ and $\lambda^{r}_{2nd}(\lambda^{i}_{2nd})$\Comment{Based on double direction solver \ref{double direction solver}}
+\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
 \EndProcedure
@@
 \begin{algorithmic}
-\Procedure{\textbf{3}. Sequential 2-D solver with Damping}{$1s_{1}t$,$1st_{2}$}
+\Procedure{\textbf{7}. Sequential single searching 2-D solver with Damping}{}
+\State Step 1. Search for two optimization variables based on single direction solver
 \For{$i=1:N_{r}$}\Comment{First round searching}
-\State update $\lambda_{i}^{r}(\lambda_{i}^{i})$ by single direction solver
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{calculate the gain of objective function}
+\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
 \EndFor
-\State choose the dual variable with the largest gain of objective function as $1st_{1}$
+\State choose the optimization variable with the largest gain of objective function as $1st_{1}$
 \State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to $1st_{1}$
 \For{$i=1:N_{r}$} \Comment{Second round searching}
-\State update $\lambda_{i}^{r}(\lambda_{i}^{i})$ by single direction solver
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{calculate the gain of objective function}
+\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
 \EndFor
-\State choose the dual variable with the largest gain of objective function as $1st_{2}$
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to $1st_{2}$
-\State \textbf{Return} $1st_{1}$ and $1st_{2}$
+\State choose the optimization variable with the largest gain of objective function as $1st_{2}$
+\State Step 2. Update $1st_{1}$ and $1st_{2}$ optimization variables based on double direction solver 
+\State update $\lambda^{r}_{1st_{1}}(\lambda^{i}_{1st_{1}})$ and $\lambda^{r}_{1st_{2}}(\lambda^{i}_{1st_{2}})$\Comment{Based on double direction solver \ref{double direction solver}}
+\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
+
 \EndProcedure
@@
 
-\section{Hyperparameter Setting}
-
+The following is the pseudo code of complex support vector detector (CSVD) is shown in Appendix \ref{Pseudo code of CSVD}
+
+%\section{Hyperparameter Setting}
+\newpage
 \section{Computer Simulations}
@@
 transmitted symbols are mutually independent modulated by $M$ PAM with normalized average energy $\frac{1}{N_{t}}$, transmitted over flat fading channel, the sample of noise is AWGN with zero mean and variance $\frac{1}{10^{SNR/10}}$, where $SNR$ denotes the signal to noise ratio.
-We make experiment to low loading factor system $100\times 40$ and full loading factor $100\times 100$, Fig \ref{SER performance} shows the symbol error rate (SER) performance.  
-\begin{figure}
+We make experiment to low loading factor system $100\times 40$ and full loading factor $100\times 100$, with at least $1e^{5}$ channel realizations and at least $500$ symbol errors accumulated.
+Fig.\ref{SER performance} shows the symbol error rate (SER) performance, Table.\ref{iteration time} shows the average iteration time of real SVD for different SNR.
+\begin{figure}[htb]
 \centering
+%\def\svgscale{0.5}
 \def\svgwidth{\columnwidth}
@@
 \end{figure}
+\begin{table}[htb]
+\renewcommand{\arraystretch}{1.3}
+\caption{Average Iteration Time of Real Support Vector Detector}
+\label{iteration time}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\multirow{2}{*} {\bfseries Array Size} & \multicolumn{9}{|c|}{\bfseries SNR}\\
+\cline{2-10}
+ &6& 8 &10& 12& 14& 16& 18& 20& 22\\
+\hline
+$100\times 40$&682 &681 &681 &681& 680 &679 &678&677 & 680\\
+\hline
+$100\times 100$&1925 &1916& 1903& 1885& 1862& 1827& 1782&1723&1654 \\
+\hline
+\end{tabular}
+\end{table}
 % An example of a floating figure using the graphicx package.
@@
 % \fnbelowfloat command of the stfloats package.
-\section{Complexity Analysis}
-
-\section{Conclusion}
-The conclusion goes here.
+%\section{Complexity Analysis}
+
+%\section{Conclusion}
+%The conclusion goes here.
 
@@
 %\section{Proof of the First Zonklar Equation}
-Appendix one text goes here.
+%Appendix one text goes here.
 
@@
 % if you want by leaving the argument blank
-\section{}
-Appendix two text goes here.
+\section{Pseudo Code of CSVD}\label{Pseudo code of CSVD}
+\begin{algorithm}[htb]
+\begin{algorithmic}
+\Procedure{CSVD}{$\mathbf{y}$,$\mathbf{H}$}
+\State Step 1. Initialization
+\State $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ \Comment{kernel matrix}
+\State $\chi^{r}=0$, $\chi^{i}=0$ \Comment{risk function}
+\For{$i=1:N_{r}$}\Comment{initialize $\lambda^{r}$, $\lambda^{i}$, $\Phi^{r}$, $\Phi^{i}$, $\Psi^{r}$, $\Psi^{i}$ and duality gap $G$}
+\State $\lambda_{i}^{r}=0, \lambda_{i}^{i}=0$
+\State $\Phi_{i}^{r}=Re(y_{i}), \Phi_{i}^{i}=Im(y_{i})$
+\State $\Psi_{i}^{r}=0, \Psi_{i}^{i}=0$
+\If{$|\Phi^{r}_{i}|>\epsilon$}
+\State $\chi^{r}+=(|\Phi^{r}_{i}|-\epsilon)^{2}$
+\EndIf
+\If{$|\Phi^{i}_{i}|>\epsilon$}
+\State $\chi^{i}+=(|\Phi_{i}^{i}|-\epsilon)^{2}$
+\EndIf
+\EndFor 
+\State $G=C(\chi^{r}+\chi^{i})$ \Comment{initialize duality gap}
+\State $\theta=-0.5G$ \Comment{initialize objective function}
+\State  Step 2. if $G>tol$, go to step 3, else go to Step 5
+\State Step 3.
+\State Sequentia single searching 2-D solver with or without damping \Comment{find two optimization variables to be updated} 
+\State Step 4. \textbf{Procedure 5} update $G$
+\State Step 5.
+\State $\tilde{x}=(\lambda^{r}+i\lambda^{i})^{T}\mathbf{H}$ \Comment{reconstruct $\mathbf{x}$}
+\State $\mathbf{x}=\mathbb{Q}(\tilde{x})$\Comment{$\mathbb{Q}(\cdot)$ denotes quantization operation based on symbol constellation}
+\State go back to Step 2
+\State Step 6. \textbf{Return} $\mathbf{x}$
+
+\EndProcedure
+\end{algorithmic}
+\label{CSVD algorithm}
+\caption{Dual Channel Complex Support Vector Detection Algorithm }
+\end{algorithm}
+%Appendix two text goes here.
 

### 2015-09-21 SVR for large MIMO/real SVR matlab/MMSE.m

@@ -1,0 +1,50 @@
+function [  symOut,   MSE] = MMSE(pH,  y, SNRd, symbolContellation, Nr, Nt, M )
+%MMSE algorithm
+%Output: symOut, and mean square error
+G=zeros(Nt,Nr);
+symOut=zeros(Nt,1);
+I=ones(Nt,Nt);
+G=(inv(pH'*pH+SNRd^(-1)*I))*pH';
+symOut=G*y;
+%% rounding 
+d=sqrt(3/(Nt*(M^2-1))); %the distance of constellation
+for count=1:Nt
+if(M==4)
+    if(symOut(count)<=-2*d)
+         symOut(count)=-3*d;
+%           symOut_MMSE(count)=-3*d;
+    elseif(symOut(count)>-2*d&&symOut(count)<=0)
+         symOut(count)=-1*d;
+%          symOut_MMSE(count)=-1*d;
+    elseif(symOut(count)>0&&symOut(count)<=2*d)
+         symOut(count)=d;
+%          symOut_MMSE(count)=d;
+    elseif(symOut(count)>=2*d)
+         symOut(count)=3*d;
+%           symOut_MMSE(count)=3*d;
+    end
+elseif (M==8)
+        if(symOut(count)<=-6*d)
+        symOut(count)=-7*d;
+    elseif(symOut(count)>-6*d&&symOut(count)<=-4*d)
+        symOut(count)=-5*d;
+    elseif(symOut(count)>-4*d&&symOut(count)<=-2*d)
+        symOut(count)=-3*d;
+    elseif(symOut(count)>-2*d&&symOut(count)<=0)
+        symOut(count)=-1*d;
+    elseif(symOut(count)>0&&symOut(count)<=2*d)
+        symOut(count)=1*d;
+    elseif(symOut(count)>2*d&&symOut(count)<=4*d)
+        symOut(count)=3*d;
+    elseif(symOut(count)>4*d&&symOut(count)<=6*d)
+        symOut(count)=5*d;
+     elseif(symOut(count)>=6*d)
+         symOut(count)=7*d;
+        end
+    
+end
+end
+MSE=norm(y-pH*symOut);
+
+end
+

### 2015-09-21 SVR for large MIMO/real SVR matlab/real_SVR_WSSS1D_2Dsolver.m

@@ -25,15 +25,15 @@ Phi=y; %intermediate variable
 G=[]; %duality gap
 G(1)=0;
 Theta(1)=0;
-for count=1:Nr
-
-    if(abs(Phi(count))>epsilon)
-    Theta(1)=Theta(1)+(abs(Phi(count))-epsilon)^2;
-    end
-end
+ for count=1:Nr 
+     if(abs(Phi(count))>epsilon)
+     Theta(1)=Theta(1)+(abs(Phi(count))-epsilon)^2;
+     end
+ end
 Theta(1)=-0.5*Theta(1)*C;
 G(1)=-2*Theta(1);
-G(1)=G(1)/abs(G(1)+Theta(1));
+
+% G(1)=G(1)/abs(G(1)+Theta(1));
 %% update lamida
 
 iteration=1;
@@ -42,34 +42,43 @@ while(G(iteration)>tol)
 delta=zeros(Nr,1);
 sigma_tmp=zeros(Nr, 1);
 NoiseTerm=0;
+sgn=zeros(Nr,1);
+K_tmp=0;
  %% approximate 2-D work set selection (without damping-bubble sorting)
 for count=1:Nr
-    lamida_tmp1=lamida(count)+(Phi(count)-epsilon*(-1))/K(count,count);
-    lamida_tmp2=lamida(count)+(Phi(count)-epsilon*(1))/K(count,count);
+%      k=(K(count,count)+1/C);
+%        lamida_tmp1=lamida(count)*(K(count,count)/k)+(Phi(count)-epsilon*(-1))/k;
+%       lamida_tmp2=lamida(count)*(K(count,count)/k)+(Phi(count)-epsilon*(1))/k;
+  lamida_tmp1=lamida(count)+(Phi(count)-epsilon*(-1))/(K(count,count));
+  lamida_tmp2=lamida(count)+(Phi(count)-epsilon*(1))/(K(count,count));
         %clipping
-    if(lamida_tmp1<-C)
-        lamida_tmp1=-C;
-    elseif(lamida_tmp1>C)
-        lamida_tmp1=C;
-    end
+%     if(lamida_tmp1<-C)
+%         lamida_tmp1=-C;
+%     elseif(lamida_tmp1>C)
+%         lamida_tmp1=C;
+%     end
         %clipping
-    if(lamida_tmp2<-C)
-        lamida_tmp2=-C;
-    elseif(lamida_tmp2>C)
[…]

### 2015-09-29 Report Aug 5 2015/Report Aug 2015.tex
Reservation point

@@
 
-The optimal maximum likelihood detector (MLD) for MIMO system requires the complexity increase exponentially with number of transmitted antennas with a factor of the size of size of constellation, which is prohibitive in practical implementations.
+The optimal maximum likelihood detector (MLD) for MIMO system requires the complexity increase exponentially with number of transmitted antennas with a factor of the size of constellation, which is prohibitive in practical implementations.
 Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes lattice structure of MIMO system. 
@@
 
-Suboptimal linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
+Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
 In the last several years, a set of detection algorithms are proposed with complexities that is comparable with LD-OSIC and suboptimal performance can be achieved.
@@
 \begin{equation}
-minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f}(\mathbf{x})),
+minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f(\mathbf{x})),
 \label{total cost function}

### 2015-09-29 SVR for large MIMO/real SVR matlab/SISO_realchannel.m

@@ -7,7 +7,7 @@ symbolReal=zeros(M,1);
 for i=1:M
     symbolReal(i)=-(M-1)*d+(i-1)*2*d;
 end
-SNR=[6,8,10];
+SNR=[9];
 SNRd=10.^(SNR./10);
 NoiseVariance=zeros(1, length(SNR));
 NoiseVariance=1./SNRd;
@@ -15,22 +15,62 @@ symErrorRate=zeros(1,length(SNR));
 for count=1:length(SNR)
     channelRealization=0;
     symError=0;
-    while(channelRealization<1e3||symError<200)
+    while(channelRealization<1e3||symError<10)
 data=randi(M,1,1);
-CG=normrnd(0, 1, 1,1);   %channel gain 
+% CG=normrnd(0, 1, 1,1);   %channel gain 
 s=symbolReal(data);
-n=normrnd(0, sqrt(NoiseVariance(count)),1,1);
- r=CG*s+n;
+n=normrnd(0, sqrt(NoiseVariance(count)/2),1,1);
+ r=s+n;
 % r=s+n;
 % r=CG^(-1)*r;
 %% ML detection
-metric=zeros(1,M);
-for count1=1:M
-    metric(count1)=norm(r-CG*symbolReal(count1));
+% metric=zeros(1,M);
+% for count1=1:M
+%     metric(count1)=norm(r-CG*symbolReal(count1));
+% end
+% [value, index]=min(metric);
+% symOut=symbolReal(index);
+%% Slicing 
+if(M==2)
+    if(r<=0)
+        symOut=-d;
+    else
+        symOut=d;
+    end
+elseif(M==4)
+    if(r<=-2*d)
+         symOut=-3*d;
+%           symOut_MMSE(count)=-3*d;
+    elseif(r>-2*d&&r<=0)
+         symOut=-1*d;
+%          symOut_MMSE(count)=-1*d;
+    elseif(r>0&&r<=2*d)
+         symOut=d;
+%          symOut_MMSE(count)=d;
+    elseif(r>=2*d)
+         symOut=3*d;
+%           symOut_MMSE(count)=3*d;
+    end
+elseif (M==8)
+        if(r<=-6*d)
+        symOut=-7*d;
+    elseif(r>-6*d&&r<=-4*d)
+        symOut=-5*d;
+    elseif(r>-4*d&&r<=-2*d)
+        symOut=-3*d;
+    elseif(r>-2*d&&r<=0)
[…]

### 2015-10-02 Report Aug 5 2015/Report Aug 2015.tex
Report Aug 5 revised
Introduction

@@
 % correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+%\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 %\hfill September 17, 2014
-  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) and the limited radio frequency spectrum over a complex space-time varying environment.
-As the most promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years and become mature, which is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} long-term evolution (LTE)\cite{3GLTE}.
-The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve bandwidth efficiency) and diversity gain (better reliability of communication link) is obtained by employing spatial domain.
-Large MIMO (also called Massive MIMO) is an upgrade version of conventional MIMO system, it equips unprecedented hundreds of low power low price antennas at base station (BS), serving several tens of terminals simultaneously, It can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness\cite{rusek2013scaling}\cite{larsson2014massive}.
-
-  The price paid for large MIMO system is the increasing complexities for signal processing at both transmitting and receiving end.
-Uplink Detector is one of the key components in large MIMO system.
-With orders magnitude more antennas equipped at BS, benefits and challenges coexist in designing of detection algorithms for large MIMO uplink, on the one hand, large number of receive antennas provide potential of large diversity gain, on the other hand, complexity of the algorithm becomes extremely crucial to make system practical.
-
-The optimal maximum likelihood detector (MLD) for MIMO system requires the complexity increase exponentially with number of transmitted antennas with a factor of the size of constellation, which is prohibitive in practical implementations.
-Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes lattice structure of MIMO system. 
-Its variant fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} make it possible to achieve near optimal performance with a fixed complexity under different signal to noise ratio (SNR).
-However, all the algorithms that based on lattice structure have the same shortage - their complexities increases exponentially with a factor of the size of symbol constellation.
-Therefore, they are prohibitive when it comes to a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.
-
-Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
-In the last several years, a set of detection algorithms are proposed with complexities that is comparable with LD-OSIC and suboptimal performance can be achieved.
-The local search algorithm, such as likelihood ascend searching (LAS)\cite{vardhan2008low}\cite{li2010multiple}, an theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was presented\cite{sunfamily}.
-Layered Tabu search algorithm presented in\cite{srinidhi2011layered} is superior to the LAS algorithms because it can move away to new searching area to avoid local minimal.
-Message passing detectors based on belief propagation (BF) and Gaussian Approximation (GA) \cite{goldberger2011mimo}\cite{som2011low}\cite{narasimhan2014channel}\cite{som2010improved}.
-Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}  and Lattice Reduction (LR) aided detectors\cite{zhou2013element}.
-
-Firmly grounded in framework of statistical learning theory, Support Vector Machine (SVM) has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction.
-SVM method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can give good generalization performance to unseen data\cite{scholkopf2002learning}.
-
-Research and industry interest of SVM boosted since 1990s, promoted by related works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
-Moreover, the kernel based methods\cite{scholkopf2002learning} carries out nonlinear learning task by mapping input data sets into high dimensional feature space, then replacing inner product of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
-This rationale is supported mathematically by Reproducing Kernel Hilbert Space (RKHS).
+  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment.
+The most promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} long-term evolution (LTE)\cite{3GLTE}.
+The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve bandwidth efficiency) and diversity gain (better reliability of communication link) is obtained by exploiting the spatial domain.
+Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously.
+This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness both to unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
+
+  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving end.
+The uplink Detector is one of the key components in large MIMO systems.
+With orders magnitude more antennas at the BS, benefits and challenges coexist in designing of detection algorithms for the uplink communication of large MIMO systems.
+On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexity of the algorithm becomes crucial to make the system practical.
+
+Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams.
+However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with number of transmitted antennas, which is prohibitive for practical applications.
+
+As alternatives to MLD, linear detectors (LD) such as zero-forcing (ZF) and minimum mean square error (MMSE) with optimized ordering sequential interference cancellation (ZF-OSIC, MMSE-OSIC) are exploited in V-BLAST architecture\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast},  however the performance of ZF-OSIC and MMMSE-OSIC are inferior comparing to MLD.
+
+Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes the lattice structure of MIMO systems, which can achieve optimal performance with relatively much lower complexity comparing to MLD.
+However, SD has two major shortages that make it problematic to be integrated into a practical systems.
+The first shortage is SD has various complexities under different signal to noise ratios (SNR), while a constant processing data rate is required for hardware.
+The second shortage is SD's complexity still has a lower bound for complexity that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
+The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different value of SNR.
+The FCSD inherits the principle of list based searching algorithms, which first generate a list of candidate symbol vectors and then the best candidate is chosen as the solution.
+The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC(sel-MMSE-OSIC)\cite{radji2009interference}.
+However, all these list based searching algorithms have the same shortage - their complexities increase exponentially with the number of transmit antennas and the order of modulation scheme\cite{radji2009interference}.
+Therefore, such algorithms are prohibitive when it comes to a large number of antennas or a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.
+
+%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
+Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance.
+such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
+Tabu search based algorithms which have superior performance compared to LAS detectors because local minima can be avoided (e.g.
+Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g.
+Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g.
+Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) and Lattice Reduction (LR) aided algorithms\cite{zhou2013element}.
+
+Firmly grounded in framework of statistical learning theory, the Support Vector Machine (SVM) technique has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction.
+the SVM method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can provide good generalization performance\cite{scholkopf2002learning}.
+
+Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
+Moreover, the kernel based methods\cite{scholkopf2002learning} solve nonlinear learning tasks by mapping input data sets into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
+This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS).
 Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.
 
-Like SVM, $\epsilon$-SVR solving original optimization problem by transforming it into Lagrange dual optimization problem, which can be solved by Quadratic Programming (QP), Sequential Minimal Optimization (SMO) algorithm was proposed as a fast algorithm to solve this QP problem by decompose the it into sub QP problems and solve them analytically\cite{platt1999fast}, therefore, the computational intensive numerical method can be avoided.
+Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual optimization problem, which can be solved by Quadratic Programming (QP).
+Sequential Minimal Optimization (SMO) algorithm was proposed as a fast algorithm to solve this QP problem by decomposing the it into sub QP problems and solving them analytically\cite{platt1999fast}.
+Therefore, the computational intensive numerical method can be avoided.
 A more general method is decomposition solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets W and N, W is the work set and N contains the remaining optimization variables.
-In each iteration, only the optimization variables in work set is optimized while keeping other variables fixed.
-SMO algorithm is an extreme case of decomposition solver.
-An important issue of decomposition solver is the choice of work set, one strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, and final converge can be guaranteed\cite{osuna1997improved}.
-SMO algorithm restricts the size of work set to 2, because of linear constraint in dual problem that inducted by offset.
+In each iteration, only the optimization variables in the work set is optimized while keeping other variables fixed.
+The SMO algorithm is an extreme case of decomposition solver.
+An important issue of decomposition solver is the choice of the work set.
+One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring final converge\cite{osuna1997improved}.
+Because of the linear constraint inducted by offset, the SMO algorithm restricts the size of the work set to 2.
 In\cite{steinwart2011training}, a method to train SVM without offset was proposed, with the comparable performance to the SVM with offset.
-The authors work demonstrates that with the combination of two single optimization variable work set selection strategies which requires searching time $O(n)$ and update a work set size of two in each iteration, this method can achieve a iteration time as few as that searching over all pairs of optimization variables which requires $O(n^{2})$ searching times.
-
-Until now, although the mathematical foundation of kernel based methods is RKHS which is defined in complex domain, the most of practitioners are dealing with real data set.
-However in communication and signal processing area, the channel gains, signals, waveforms etc.
+A set of sequential single variable work set selection strategies, which require $O(n)$ searching time are proposed.
+The optimal double variable work set selection strategy, which performs exhaustively searching, however, requires $O(n^{2})$ searching time.
+The authors demonstrate that with the combination of two proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.
+
+The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets.
+In communication and signal processing area, the channel gains, signals, waveforms etc.
 are all represented in complex form.
-Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can process the complex data set purely in complex domain.
-The simulation of channel realization and equalization in\cite{bouboulis2013complex} demonstrate a better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernel.
-Based on this work, we construct a prototype of a complexity-performance controllable detector for large MIMO based on dual channel complex SVR.
-The detector can work in two parallel real SVR pipeline which can be solved independently.
-Moreover, only real part of kernel matrix is needed in both channel.
+Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain.
+The results in\cite{bouboulis2013complex} demonstrate better performances as well as reduced complexity comparing to simply split learning task into two real case by real kernel.
+Based on this work, we derive of a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR).
+The detector can work in two parallel real SVR channels which can be solved independently.
+Moreover, only the real part of kernel matrix is needed in both channels.
 This means a large amount of computation can be reduced.
-Based on the discrete time MIMO channel model, In our regression model, this CSVR-detector
-is constructed without offset, Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our prototype, we propose a sequential single optimization variable searching strategy that find two optimization variable sequentially, which can approximate the optimal double optimization variables searching strategy.
+Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
+is constructed without offset, Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed.
+By this strategy, two variables can be updated at each iteration, with much smaller searching time.
 

### 2015-10-02 SVR for large MIMO/real SVR matlab/communication_line.m

@@ -9,6 +9,10 @@ N=4;
 M=4; %modulation sheme
 d=sqrt(3/(Nt*(M^2-1)));
 symbolReal=zeros(M,1);
+epsilon=2*(1e-1);
+C=1;
+tol=1e-2;
+tau=0.2;
 for i=1:M
     symbolReal(i)=-(M-1)*d+(i-1)*2*d;
 end
@@ -27,15 +31,91 @@ K=zeros(Nr, Nr); %kernel matrix
 Phi=zeros(Nr); %intermediate variables
 iteration=0; %iteration time of SVR algorithm
 symError=0;
-SymErrorRate=zeros(length(SNR),1);
+SymErrorRate1=zeros(length(SNR),1);
+SymErrorRate2=zeros(length(SNR),1);
 symOut_candidate=zeros(M^(N),Nt-N);
+%% document settings
+fid1=fopen('D_SVR.txt','a');
+fid2=fopen('D_MMSE.txt','a');
+fid3=fopen('D_original.txt','a');
+
+fprintf(fid1, 'This document stores the information for SVR\n');
+fprintf(fid1, '%d X %d MIMO system\n',Nr,Nt);
+fprintf(fid1, '%d PAM modulation scheme\n', M);
+fprintf(fid1, 'SNR are\n');
+fprintf(fid1, '   ');
+for i=1:length(SNR)
+    fprintf(fid1, '%d  ', SNR(i));
+end
+fprintf(fid1, '\n\n');
+fprintf(fid1, '   ');
+for i=1:length(SNR)
+    fprintf(fid1, '%f  ', SNRd(i));
+end
+fprintf(fid1, '\n\n');
+fprintf(fid1, 'SER AMMSE\n');
+fprintf(fid1, 'hyperparameters\n');
+fprintf(fid1, 'epsilon is %0.10f\n',epsilon);
+fprintf(fid1,'C is %f\n', C);
+fprintf(fid1, 'tolerance is %0.8f\n', tol);
+fclose(fid1);
+
+
+fprintf(fid2, 'This document stores the information for MMSE\n');
+fprintf(fid2, '%d X %d MIMO system\n',Nr,Nt);
+fprintf(fid2, '%d PAM modulation scheme\n', M);
+fprintf(fid2, 'SNR are\n');
+fprintf(fid2, '   ');
+for i=1:length(SNR)
+    fprintf(fid2, '%d  ', SNR(i));
+end
[…]

### 2015-10-02 SVR for large MIMO/real_SVR_C/src/MMSE_detec.h

@@ -1,0 +1,113 @@
+/*
+ * MMSE_detec.h
+ *
+ *  Created on: Sep 2, 2015
+ *      Author: Preston Chen
+ */
+
+#ifndef MMSE_DETEC_H_
+#define MMSE_DETEC_H_
+
+#include"Public.h"
+void MMSE_detec(
+		gsl_matrix *pH,
+		gsl_vector *symReceived,
+		double SNRd,
+		gsl_vector *symConstellation,
+		gsl_vector *symOut,
+		double *MSE
+		){
+	//MMSE equalization
+	gsl_matrix *G=gsl_matrix_calloc(Nt,Nt);
+	gsl_permutation *p=gsl_permutation_calloc(Nt);
+	gsl_matrix *LU=gsl_matrix_calloc(Nt,Nt);
+    gsl_vector *y_tmp=gsl_vector_calloc(Nr);
+    gsl_vector *symOut_tmp=gsl_vector_calloc(Nr);
+	gsl_matrix *inverse=gsl_matrix_calloc(Nt,Nt);
+	gsl_matrix *E=gsl_matrix_calloc(Nt, Nr);
+    int *signum=(int*)malloc(sizeof(int));
+	int count,count1,count2;
+    gsl_matrix_set_identity(G);
+	gsl_blas_dgemm(CblasTrans, CblasNoTrans, 1, pH, pH, (double)1/(SNRd), G);
+	gsl_matrix_memcpy(LU, G);
+	gsl_linalg_LU_decomp(LU, p, signum);
+	gsl_linalg_LU_invert(LU, p, inverse);
+#ifdef DEBUG
+	gsl_matrix *I=gsl_matrix_calloc(Nt,Nt);
+	gsl_blas_dgemm(CblasNoTrans, CblasNoTrans, 1, inverse, G, 0,I);
+	printf("the identity matrix is\n");
+	for(count1=0;count1<Nt;count1++){
+		for(count2=0;count2<Nt;count2++){
+			printf("%f ", gsl_matrix_get(I,count1,count2));
+		}
+		printf("\n");
+	}
+	gsl_matrix_free(I);
+#endif
+
+	gsl_blas_dgemm(CblasNoTrans, CblasTrans, 1, inverse, pH, 0, E);
+	gsl_blas_dgemv(CblasNoTrans, 1, E, symReceived, 0, symOut);
+#ifdef DEBUG
+	printf("the unrounded output symbols are\n");
+	for(count=0;count<Nt;count++){
[…]

### 2015-10-06 Report Aug 5 2015/Report Aug 2015.tex
Report Aug 5 Revised
revised lagrange duality and system model parts

@@
 \subsection{Regression Model}
-Suppose we are given training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{l},y_{l}))$, $l$ denotes the number of training samples, $\mathbf{x}\in \mathbb{R}^{v}$ denotes input data vector, $v$ is the number of features in $\mathbf{x}$.
-$y$ denotes output.
-The regression model (either linear or non-linear regression) is given by
-\begin{equation}
-y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i\in 1\cdots l 
+Suppose we are given training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
+$y_{i}$ denotes output.
+Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Lambda}$, $\Lambda \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$).
+The regression model (either linear or non-linear) is given by
+\begin{equation}
+y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1\cdots L 
 \label{equation1}
 \end{equation}
-where $\mathbf{w}$ denotes regression coefficient vector, $\Phi(x)$ denotes the mapping of $\mathbf{\mathbf{x}}$ to higher dimensional feature space.
 
@@
 
-Here we give the primal optimization problem directly
-\begin{eqnarray}
-\nonumber
-\min_{\mathbf{w}} \frac{1}{2}||\mathbf{w}||^{2}+C\sum_{j=1}^{l}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
+We present the primal optimization problem directly
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\min_{\mathbf{w}} f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
 s.t. \left\{\begin{array}{ll}
-y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
-\epsilon, \xi,\hat{\xi} &\geq 0
+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
+\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
+\epsilon_{i}, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
 \end{array}\right.
 \label{primal optimization problem}
-\end{eqnarray}
-In \ref{primal optimization problem}, $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model.
-$\epsilon$ denotes the precision, if the error between estimation and real output is less than $\epsilon$, As shown in Fig \ref{epsilon-SVR}, only those data points outside the shadow part, which is called $\epsilon$ tube, contribute to cost function.
-$\xi$ and $\hat{\xi}$ denote slack variables that cope with noise of input data set, $R(x)$ denotes risk function, the simplest risk function is $R(u)=u$, risk function is determined by the statistical distribution of noise\cite{smola2004tutorial}, for example if the noise subject to Gaussian distribution, the optimal cost function is $R(x)=\frac{1}{2}x^{2}$.
-$C\sum_{i=1}^{l}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ controls the trade off between regularization term and noise penalty term.
-\subsection{Risk Functional}\label{risk functional}
-From the rationale of regularized risk function, let $f_{true}(\mathbf{x})$ denotes true regression function and $c(\mathbf{x},y,f(\mathbf{x}))$ denotes the risk function, the regression model can be written as $y=f_{true}(\mathbf{x})+\xi$, $\xi$ denotes additive noise.
-Assume the data samples are i.i.d.
-Based on Maximum Likelihood (ML) principle we want to
-\begin{eqnarray}
-\nonumber
-\max_{f()}\quad \prod_{i=1}^{l}P(y_{i}|f_{true}(\mathbf{x}_{i}))&=\max\quad \prod_{i=1}^{l}P(\xi_{i})\\
-&=\max\quad \prod_{i=1}^{l}P(y_{i}-f_{true}(\mathbf{x}_{i})),
-\label{risk function1}
-\end{eqnarray}
-Take the logarithm of (\ref{risk function1}), we have
-\begin{eqnarray}
-maximize\quad \sum_{i=1}^{l}log(P(y_{i}-f(\mathbf{x}_{i}))),
-\label{risk function2}
-\end{eqnarray}
-Therefore the $i$th risk function of $(\mathbf{x_{i}}, y_{i})$ can be written as 
-\begin{eqnarray}
+\end{IEEEeqnarray}
+In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the area between two dash line is called $\epsilon$ tube.
+Only those data samples located outside $\epsilon$ tube contribute to cost.
+Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with noise of input data samples, $R(u)$ denotes risk function, the simplest risk function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}.
+For example if the noise is Gaussian noise, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$.
+The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.
+
+\subsection{Cost Function}\label{cost function}
+The optimal cost function in (\ref{primal optimization problem}) can be derived based on maximum likelihood (ML) principle.
+Assume the data samples $\mathbf{x}_{i}$ in data set are iid, Let $f_{true}(\mathbf{x}_{i}), i=1,2,\cdots L$ denotes true regression function.
+the underlying assumption is $y_{i}=f_{true}(\mathbf{x}_{i})+\xi_{i}, i=1,2,\cdots, L$, $\xi_{i}$ denotes additive noise of the $i$th data sample, with probability density function (pdf) $Pr(\cdot)$.
+Let $P(\cdot)$ denotes the pdf of $y_{i}$.
+Based on ML principle we want to
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{f}\quad \prod_{i=1}^{L}P(y_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}P(f(\mathbf{x}_{i})+\xi_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}Pr(\xi_{i})=\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))\\
+\label{cost function1}
+\end{IEEEeqnarray}
+Take the logarithm of $\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))$, we have
+\begin{IEEEeqnarray}[\relax]{l}
+\sum_{i=1}^{L}log(Pr(y_{i}-f(\mathbf{x}_{i}))),
+\label{cost function2}
+\end{IEEEeqnarray}
+maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}log(Pr(y_{i}-f(\mathbf{x}_{i})))$
+Let $c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))$ denotes the $i$th cost function, which is defined as  
+\begin{IEEEeqnarray}[\relax]{l}
 c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-log(P(y_{i}-f(\mathbf{x}_{i}))).
-\label{risk function3}
-\end{eqnarray}
-Thus the equivalent formula of (12) can be written as 
-\begin{equation}
-minimize\quad  \sum_{i=1}^{l}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
+\label{cost function3}
+\end{IEEEeqnarray}
+Thus (\ref{cost function1}) can be rewritten as 
+\begin{equation}
+\min_{f}\quad  \sum_{i=1}^{L}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
 \label{Total risk function}
 \end{equation} 
-In $\epsilon$-SVR, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{risk function3}).
-\begin{eqnarray}
+In $\epsilon$-SVR, in order to provide more flexibility to precision control, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{cost function3}).
+\begin{IEEEeqnarray}[\relax]{l}
 |u|_{\epsilon}=\left\{\begin{array}{ll}
@@
 \label{Vepsilon}
-\end{eqnarray}
-Thus the cost function in $\epsilon$-SVR can be written as 
-\begin{equation}
-\tilde{c}(\mathbf{x}, y, f(\mathbf{x}))=\frac{1}{l}\sum_{i=1}^{l}m_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
-\label{cost function}
-\end{equation}
-where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as
-\begin{equation}
-minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f(\mathbf{x})),
-\label{total cost function}
-\end{equation} 
-where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
-\begin{equation}
-minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
+\end{IEEEeqnarray}
+Thus the final form of cost function in $\epsilon$-SVR can be written as 
+\begin{equation}
+\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),
 \label{final cost function}
 \end{equation}
-where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
-\begin{eqnarray}
-\nonumber
-minimize \quad f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-s.t. \left\{\begin{array}{ll}
-y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
-\epsilon, \xi,\hat{\xi} &\geq 0\\
-\end{array}\right.
-\label{primal objective function}
-\end{eqnarray}
-where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered. 
+Consider the cost function term in (\ref{primal optimization problem}),
+\begin{equation}
+\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))
+\end{equation}  
+the cost function term is determined according to noise distribution.  
+%where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as
+%\begin{equation}
+%minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f(\mathbf{x})),
+%\label{total cost function}
+%\end{equation} 
+%where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
+%\begin{equation}
+%minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
+%\label{final cost function}
+%\end{equation}
+%where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
+%\begin{eqnarray}
+%\nonumber
+%minimize \quad f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
+%s.t. \left\{\begin{array}{ll}
+%y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
+%\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
+%\epsilon, \xi,\hat{\xi} &\geq 0\\
+%\end{array}\right.
+%\label{primal objective function}
+%\end{eqnarray}
+%where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered. 
 \subsection{Lagrange Duality}\label{section lagrange duality}
-According to Lagrange Theorem, the optimization problem (\ref{primal objective function}) can be transferred to dual form by combining original objective function with linear combination of equality and inequality constraints, the combination coefficient is called Lagrange multiplier.
-Thus we have Lagrange function.
-\begin{eqnarray}
-\nonumber
-\Theta(\mathbf{w}, b, \xi, \hat{\xi}, \alpha, \hat{\alpha}, \eta, \hat{\eta})=
-\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{l}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
-\nonumber
--\sum_{i=1}^{l}\alpha_{i}(\epsilon+\xi_{i}-y_{i}+\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))-\sum_{i=1}^{l}\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i}))\\
+According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier.
+The Lagrange function is given by.
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+L(\mathbf{w}, b, \xi_{i}, \hat{\xi}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})=
+\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{L}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
+\nonumber
++\sum_{i=1}^{L}\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\sum_{i=1}^{L}\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})\\
 s.t. \left\{\begin{array}{cc}
-\eta, \hat{\eta}, \alpha, \hat{\alpha}\geq 0\\
-\xi, \hat{\xi}\geq  0\\
+\eta_{i}, \hat{\eta}_{i}, \alpha_{i}, \hat{\alpha}_{i}\geq 0, i=1,2,\cdots L\\
+\xi_{i}, \hat{\xi}_{i}\geq  0, i=1,2,\cdots L\\
 \end{array}\right.
 \label{lagrange duality1}
-\end{eqnarray}
-where $\eta$,$\hat{\eta}$, $\alpha$, $\hat{\alpha}$ are Lagrange multipliers.
-
-The sufficient and necessary condition that $f(\mathbf{w}^{*})$ is the global minimum of (\ref{primal objective function}) is called Karush-Kuhn-Tucker (KKT) conditions, which can be written as\cite{cristianini2000introduction}
-\begin{IEEEeqnarray}[\relax]{l}
-\frac{\partial \Theta}{\partial \mathbf{w}}=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\\label{partial1}
-\frac{\partial \Theta}{\partial \xi}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0\\\label{partial2}
-\frac{\partial \Theta}{\partial \hat{\xi}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\\\label{parial3}
-\frac{\partial \Theta}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\label{partial4}
-\nonumber
-\end{IEEEeqnarray}
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha, \hat{\alpha}\geq 0\\
-\alpha(y-\mathbf{w}^{T}\Phi(\mathbf{x})-b-\epsilon-\xi)=0\\
-\hat{\alpha}(\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi})=0\\
-y-\mathbf{w}^{T}\Phi(\mathbf{x})-b-\epsilon-\xi\leq 0\\
-\mathbf{w}^{T}\Phi(\mathbf{x})+b-y-\epsilon-\hat{\xi}\leq 0
-\end{array}\right. 
-\label{KKT complimentary}
-\end{IEEEeqnarray}
-
-The conditions in (\ref{KKT complimentary}) is called KKT complimentary condition.
-Then substitute (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}) and for sake of brevity, we make $C_{i}$ uniform to all data samples, we have the dual form of objective function ：
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha, \hat{\alpha}) =\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{l}[(R(\xi_{i})-\xi_{i}R^{'}(\xi_{i}))\\
-\nonumber
-+(R(\hat{\xi}_{i})-\hat{\xi}_{i}R^{'}(\hat{\xi}_{i}))]
-+\sum_{i=1}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
-\nonumber
--\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i}),\\
+\end{IEEEeqnarray}
+where $\eta_{i}$, $\hat{\eta}_{i}$, $\alpha_{i}$, $\hat{\alpha}_{i}$ are Lagrange multipliers.
+
+The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
+Here we briefly introduce how the dual objective problem is derived from KKT conditions.
+
+Assume a constraint optimization problem is given by 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\min_{\mathbf{w}} \quad f(\mathbf{w})\\
+s.t. \quad c_{i}(\mathbf{w})\leq 0, i=1,2,\ldots L,
+\label{constraint optimization problem}
+\end{IEEEeqnarray}
+its Lagrange function is given by 
+\begin{equation}
+L(\mathbf{w}, a_{i})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),
+\label{orginal Lagrange}
+\end{equation}
+where $a_{i}$ denote Lagrange multipliers.
+ Based on Theorem 6.21 in \cite{scholkopf2002learning}, For a variable set $[\bar{\mathbf{w}}, \bar{a}_{i}]$, $\bar{\mathbf{w}}$ is the solution to (\ref{constraint optimization problem}) only when the following inequalities are satisfied
+ \begin{equation}
+ L(\mathbf{x}, \bar{a}_{i})\geq L(\bar{\mathbf{x}}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, a_{i})
+ \label{KKT inequalities}
+ \end{equation}
+This inequalities yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
+\begin{IEEEeqnarray}[\relax]{l}
+\label{original KKT condition1}
+\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, a_{i})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\
+\label{original KKT condition2}
+\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{a}_{i})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\
+\label{original KKT condition3}
+\bar{a}_{i}c_{i}(\bar{\mathbf{w}})=0, i=1,2,\ldots L
+\end{IEEEeqnarray}
+In order to satisfy the first inequality in (\ref{KKT inequalities}), (\ref{original KKT condition1}) has to hold,
+applying (\ref{original KKT condition1}) to (\ref{lagrange duality1}), which are  
+\begin{IEEEeqnarray}[\relax]{l}
+\label{partial1}
+\frac{\partial L}{\partial \mathbf{w}}=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\
+\label{partial2}
+\frac{\partial L}{\partial \xi_{i}}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\
+\label{parial3}
+\frac{\partial L}{\partial \hat{\xi}_{i}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\
+\label{partial4}
+\frac{\partial L}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\
+\end{IEEEeqnarray}
+Then by substituting (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}), (\ref{lagrange duality1}) can be rewritten as :
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\theta(\alpha_{i}, \hat{\alpha}_{i})=\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[R(\xi_{i})+R(\hat{\xi}_{i})]-\sum_{i=1}^{L}[(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}\\
+\nonumber
++(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}(y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\\
+\sum_{i=1}^{L}\hat{\alpha}_{i}(\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})
+\label{lagrange duality1 inter}
+\end{IEEEeqnarray}
+notice in (\ref{partial4}), $\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha}_{i})=0$, define $\tilde{R}(u)=R(u)-uR^{'}(u)$, (\ref{lagrange duality1 inter}) can be further simplified to
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i})]\\
+\nonumber
++\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
 s.t.\left\{\begin{array}{l}
@@
 \end{IEEEeqnarray}
-Obviously $\theta(\alpha,\hat{\alpha})\leq \Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})$, notice by transforming $\Theta(\mathbf{w}, \alpha, \hat{\alpha},\eta, \hat{\eta})$, (\ref{partial1})-(\ref{partial4}) are satisfied, therefore, KKT complimentary condition (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
-Because
-\begin{equation}
-\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
-\end{equation} 
-where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
-\begin{IEEEeqnarray}[\relax]{l}
-g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
-\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
-l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
-\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
-\nonumber
-\end{IEEEeqnarray}
-Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$.
-when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied.
-hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds.
-Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.
-
-In conclusion, the dual objective function can be written as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-maximize\quad \theta =-\frac{1}{2}\sum_{i=1}^{l}\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+\sum_{i=i}^{l}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
-\nonumber
-+C\sum_{i=1}^{l}[\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi_{i}})]\\
-=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon)^{T}\mathbf{a}+(-\mathbf{y}-\epsilon)^{T}\mathbf{\hat{a}}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
+In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold.
+Satisfying the condition (\ref{original KKT condition2}) is equivalent to find the maximum of $L(\bar{\mathbf{w}}, a_{i})$, notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\bar{\mathbf{w}}, a_{i})$ in (\ref{KKT inequalities}), thus yield the dual optimization problem which is given by
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{\alpha_{i}, \hat{\alpha}_{i}}\quad \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i}))\\
++\sum_{i=i}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
 \label{dual optimization function2}
 \end{IEEEeqnarray}
-where $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{l}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{l}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{l}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{l}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0,  $\tilde{R}(\xi)=R(\xi)-\xi R^{'}(\xi)\in \mathbb{R}^{l}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes data kernel matrix.
-We define the following $2l$ vectors
-$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2l}$, 
-\begin{IEEEeqnarray}[\relax]{l}
-\mathbf{v}_{i}=\left\{\begin{array}{ll}
+Define $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{L}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{L}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{L}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{L}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0, $\mathbf{R}_{\xi}=[\tilde{R}(\xi_{1}), \tilde{R}(\xi_{2}), \ldots, \tilde{R}(\xi_{L})]^{T}$, $\mathbf{R}_{\hat{\xi}}=[\tilde{R}(\hat{\xi}_{1}), \tilde{R}(\hat{\xi}_{2}), \ldots, \tilde{R}(\hat{\xi}_{L})]^{T}$, $[\mathbf{K}]_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes a component of data kernel matrix at $i$th row and $j$th column.
+An alternative vector form of (\ref{dual optimization function2}) can be written as
+\begin{equation}
+\max_{\mathbf{a}, \hat{\mathbf{a}}}\theta(\mathbf{a},\hat{\mathbf{a}})=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon \mathbf{e})^{T}\mathbf{a}+(-\mathbf{y}-\epsilon\mathbf{e})^{T}\mathbf{\hat{a}}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
+\label{dual objective alternative}
+\end{equation} 
+We define the following $2L$ vectors 
+$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2L}$, 
+\begin{IEEEeqnarray}[\relax]{l}
+[\mathbf{v}]_{i}=\left\{\begin{array}{ll}
 1\quad i=1,\ldots, l\\
@@
 \end{IEEEeqnarray}
-(\ref{dual optimization function2}) can also be reformulate as 
+(\ref{dual objective alternative}) can also be reformulate as 
 \newcommand{\mysmallarraydecl}{\renewcommand{%
@@
 \begin{equation}
-maximize\quad \Theta=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\max_{\mathbf{a}^{*}}\quad \theta(\mathbf{a}^{*})=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
 \mathbf{K}& -\mathbf{K}\\
@@
 \end{IEEEeqnarraybox*}\right]
-\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+\mathbf{e}^{T}C(\tilde{R}(\xi)+\tilde{R}(\hat{\xi})),
+\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
 \label{vectorize dual optimization function}
@@
 
+Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can monitor how close the solution is to the global optimum.
+Thus it can be used as a stopping criterion.
+In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by
+\begin{IEEEeqnarray}[\relax]{l}
+\left\{\begin{array}{cc}
+\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
+\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L
+\end{array}\right. 
+\label{KKT complimentary}
+\end{IEEEeqnarray}
+
+%The conditions in (\ref{KKT complimentary}) are called KKT complimentary condition. 
+%Obviously by taking partial derivations of (\ref{lagrange duality1}) with respect to $\mathbf{w}$, $\xi_{i}$, $\hat{\xi}_{i}$ and $b$, $\theta(\alpha_{i},\hat{\alpha}_{i})\leq \Theta(\mathbf{w},\alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})$, notice in $\theta(\alpha_{i}, \hat{\alpha}_{i})$ KKT conditions in (\ref{partial1}) to (\ref{partial4}) are satisfied.
+Therefore, KKT complimentary conditions (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
+Because
+%\begin{equation}
+%\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
+%\end{equation} 
+%where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
+%\begin{IEEEeqnarray}[\relax]{l}
+%g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
+%\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
+%l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
+%\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
+%\nonumber
+%\end{IEEEeqnarray}
+%Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$.
+when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied.
+hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds.
+Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.
+
+%In conclusion, the dual objective function can be written as
+
 \section{System Model}\label{system model}
-  Consider a complex large MIMO uplink multiplexing system with $N_{t}$ users, each user has one transmit antenna.
-The number of receive antennas at Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
-Typically large MIMO systems have hundreds of antennas at BS serving several tens of terminals, as shown in Fig {\ref{large MIMO uplink model}}.
+  Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna.
+The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
+Typically large MIMO systems have hundreds of antennas at the BS, as shown in Fig {\ref{large MIMO uplink model}}.
   \begin{figure}[htb]
@@
 
-  Uncoded bit sequences, which are modulated to complex symbols, are transmitted by users over a flat fading channel. The discrete time model is:
+Bit sequences, which are modulated to complex symbols, are transmitted by the users over a flat fading channel. The discrete time model of the system is given by:
 \begin{equation}
@@
 where $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
-4-QAM, 16-QAM, 64-QAM) of size $M$.
-The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, and $\mathbb{E}[\cdot]$ denotes the expectation operation.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix with independent identically distributed (i.i.d) circularly symmetric complex Gaussian zero mean components with unit variance.
+BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
+The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian random variable with zero mean and unit variance.
 Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
 
-  Assume the receiver has perfect channel state information (CSI), meaning that $ \mathbf{H}$ is known, as well as the SNR.
-The task of the MIMO decoder is to recover $\mathbf{s}$ based on $\mathbf{y}$ and $\mathbf{H}$.
+The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
 

### 2015-10-11 Report Aug 5 2015/Report Aug 2015.tex
report  revised until P28

@@
 The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
-Here we briefly introduce how the dual objective problem is derived from KKT conditions.
+Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.
 
@@
  \begin{equation}
- L(\mathbf{x}, \bar{a}_{i})\geq L(\bar{\mathbf{x}}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, a_{i})
+ L(\mathbf{w}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, a_{i})
  \label{KKT inequalities}
@@
 \label{partial4}
-\frac{\partial L}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\
+\frac{\partial L}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber
 \end{IEEEeqnarray}
@@
 In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold.
-Satisfying the condition (\ref{original KKT condition2}) is equivalent to find the maximum of $L(\bar{\mathbf{w}}, a_{i})$, notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\bar{\mathbf{w}}, a_{i})$ in (\ref{KKT inequalities}), thus yield the dual optimization problem which is given by
+Condition (\ref{original KKT condition2}) is satisfied when the maximum of $L(\bar{\mathbf{w}}, a_{i})$ is found, notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\bar{\mathbf{w}}, a_{i})$ in (\ref{KKT inequalities}), thus yielding the dual optimization problem, which is given by
 \begin{IEEEeqnarray}[\relax]{l}
@@
 
-Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can monitor how close the solution is to the global optimum.
+Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor how close the solution is to the global optimum.
 Thus it can be used as a stopping criterion.
@@
 
-\section{System Model}\label{system model}
+\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
+\subsection{System Model}\label{system model}
   Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna.
@@
 The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
-
-\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
- Based on discrete time model of large MIMO uplink system in (\ref{discrete time MIMO system}), in our  regression model, the training data sample at detector is $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of channel propagation matrix $\mathbf{H}$, this yields a regression task without offset $b$:
- \begin{eqnarray}
- y_{i}=f_{true}(\mathbf{h}_{i})+n,\\
+\subsection{Complex Regression Model}
+ Based on the discrete time model of the large MIMO uplink system of (\ref{discrete time MIMO system}), our regression model is set such that the training data samples at the detector are $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of matrix $\mathbf{H}$.
+This yields a regression task without offset $b$ in (\ref{equation1}) :
+ \begin{IEEEeqnarray}[\relax]{l}
+ y_{i}=f_{true}(\mathbf{h}_{i})+n_{i}, i=1,2\ldots L\\
  \label{regression part1a}
- f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\mathbf{s},\\
+ f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\cdot\mathbf{s}, i=1,2,\ldots, L\\
  \label{regression part1b}
- \end{eqnarray}
- where $f_{true}()$ denotes the underlying true function, $n$ denotes additive noise.
-In this regression problem, receive symbol $y$ is the output data, $\mathbf{h}$ is input data sample, transmitted symbol vector $s$ is regression coefficients.
-Because the large MIMO system we consider here is complex, we employ complex support vector regression (CSVR) without offset term $b$.
-As shown in section \ref{Introduce epsilon SVR}, in order to derive Lagrange duality optimization formula, partial derivatives of objective function with respect to $\mathbf{w}$ and $\xi$ are needed to be calculated, in CSVR, that means take partial derivatives to risk functions which are defined in complex domain.
-Recently mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) is employed to solve this problem\cite{bouboulis2011extension}.
+ \end{IEEEeqnarray}
+ where $f_{true}()$ denotes the underlying true regression function, $n_{i}$ denotes discrete sample of additive noise.
+In this regression problem, received symbols $y_{i}$ are the output data, $\mathbf{h}_{i}$ are the input data samples, transmitted symbol vector $\mathbf{s}$ contains the regression coefficients.
+We employ complex support vector regression (CSVR) without offset term $b$, in order to deal with the complex large MIMO systems.
+As shown in section \ref{Introduce epsilon SVR}, As shown in (\ref{original KKT condition1}) the first KKT condition is satisfied by finding the saddle point $\bar{\mathbf{w}}$ by taking paritial derivatives of $L(\mathbf{w},a_{i})$ with respect to $\mathbf{w}$.
+Mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) are employed to calculate partial derivatives of Lagrangian function of CSVR in complex manner\cite{bouboulis2011extension}.
 First we generalize our regression model by complex RKHS,
-Let $<,>_{H}$ denotes inner product operation in real RKHS.
-$<,>_{\mathbb{H}}$ denotes inner products operation in complex RKHS.
-Assume $\mathbf{x}$, $\mathbf{y}$, $\mathbf{z}$, $j$, $k$ $\in \mathbb{C}$, complex Hilbert space has the following properties
+Define a real RKHS $\mathcal{H}$, $<,>_{\mathcal{H}}$ denotes the corresponding inner product in $\mathcal{H}$.
+define complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $<,>_{\mathbb{H}}$ denotes the corresponding inner products in $\mathbb{H}$.
+Assume $\mathbf{x}$, $\mathbf{y}$, $\mathbf{z}$, $\mu$, $\chi$ $\in \mathbb{C}$, complex Hilbert space has the following properties
 \newtheorem{Lemma}{Lemma}
@@
 \begin{Property}
- $<\mathbf{x},\mathbf{y}>_{\mathbb{H}}=<\overline{\mathbf{y},\mathbf{x}}>_{\mathbb{H}}$
+ $<\mathbf{x},\mathbf{y}>_{\mathbb{H}}=(<{\mathbf{y},\mathbf{x}}>_{\mathbb{H}})^{*}$
 \label{CHSProperty1}
@@
 \begin{Property}
-$<j\mathbf{x}+k\mathbf{y},\mathbf{z}>_{\mathbb{H}}=j<\mathbf{x},\mathbf{z}>_{\mathbb{H}}+k<\mathbf{y},\mathbf{z}>_{\mathbb{H}}$
+$<\mu\mathbf{x}+\chi\mathbf{y},\mathbf{z}>_{\mathbb{H}}=\mu<\mathbf{x},\mathbf{z}>_{\mathbb{H}}+\chi<\mathbf{y},\mathbf{z}>_{\mathbb{H}}$
 \label{CHSProperty2}
@@
 \begin{Property}
-$<\mathbf{z}, j\mathbf{x}+k\mathbf{y}>=\bar{j}<\mathbf{z},\mathbf{x}>_{\mathbb{H}}+\bar{k}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}}$
+$<\mathbf{z}, \mu\mathbf{x}+\chi\mathbf{y}>_{\mathbb{H}}=\mu^{*}<\mathbf{z},\mathbf{x}>_{\mathbb{H}}+\chi^{*}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}}$
 \label{CHSProperty3}
@@
 \begin{Lemma}
-$\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{*}>_{\mathbb{H}}$
+Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{V}$, define a real RKHS $\mathcal{H}$ that satisfy $<\mathbf{a}, \mathbf{b}>_{\mathcal{H}}=\mathbf{a}^{T}\mathbf{b}$.
+For the corresponding complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$,
+$<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$
 \end{Lemma}
@@
 \begin{proof} 
-Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{v}$, it can be easily proved  
-\begin{equation}
-\mathbf{a}^{T}\mathbf{b} \in <\mathbf{a}, \mathbf{b}>_{H},
-\label{CHSequation1}
-\end{equation}
- From Property \ref{CHSProperty1} and Property \ref{CHSProperty3}, it is obvious 
-\begin{equation}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\mathbf{g}^{r},\mathbf{h}^{r}>_{H}+<\mathbf{g}^{i},\mathbf{h}^{i}>_{H}+i(<\mathbf{g}^{i},\mathbf{h}^{r}>_{H}-<\mathbf{g}^{r},\mathbf{h}^{i}>_{H})
-\label{CHSProperty4}
-\end{equation}
-where $\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{v}$, and $\mathbf{g}=\mathbf{g}^{r}+i\mathbf{g}^{i}$, $\mathbf{h}=\mathbf{h}^{r}+i\mathbf{h}^{i}$. Therefore, 
-\begin{eqnarray}
-\nonumber
-<\mathbf{h}, \mathbf{s}^{*}>_{\mathbb{H}}&=&<\mathbf{h}^{r},  (\mathbf{s}^{*})^{r}>_{H}+<\mathbf{h}^{i},  (\mathbf{s}^{*})^{i}>_{H}+i(<\mathbf{h}^{i},  (\mathbf{s}^{*})^{r}>_{H}-<\mathbf{h}^{r},  (\mathbf{s}^{*})^{i}>_{H})\\
-&=&<\mathbf{h}^{r}, \mathbf{s}^{r}>_{H}-<\mathbf{h}^{i}, \mathbf{s}^{i}>_{H}+i(<\mathbf{h}^{i}, \mathbf{s}^{r}>_{H}+<\mathbf{h}^{r}, \mathbf{s}^{i}>_{H}),
+$\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{V}$, and $\mathbf{g}=\Re{(\mathbf{g})}+\imath\Im{(\mathbf{g})}$, $\mathbf{h}=\Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}$.
+From Property \ref{CHSProperty1} and Property \ref{CHSProperty3},
+\begin{IEEEeqnarray}[\relax]{l}
+<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(g)}+\imath\Im{(g)}, \Re{(h)}+\imath\Im{(h)}>_{\mathbb{H}}
+\label{CHSProperty4 inter1}
+\end{IEEEeqnarray}
+According to Property \ref{CHSProperty2}, (\ref{CHSProperty4 inter1}) can be rewritten as 
+\begin{equation}
+<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath <\Im{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}},
+\label{CHSProperty4 inter2}
+\end{equation}
+According to Property \ref{CHSProperty3}
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-\imath <\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathbb{H}}+\imath (<\Im{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-
+\imath <\Im{(\mathbf{g})}, \\ \nonumber  \Im{(\mathbf{h})}>_{\mathbb{H}})
+=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}-<\Re{(\mathbf{g})},\\ \Im{(\mathbf{h})}>_{\mathbb{H}}]
+\label{CHSProperty4 inter2}
+\end{IEEEeqnarray}
+Because $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathbb{H}}=<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}=\mathbf{f}^{T}_{1}\cdot \mathbf{f}_{2}$ if $\mathbf{f}_{1}, \mathbf{f}_{2}\in \mathcal{H}$, thus (\ref{CHSProperty4 inter2}) can be rewritten as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathcal{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}-<\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathcal{H}}]=\\
+\Re{(\mathbf{g})}^{T}\cdot \Re{(\mathbf{h})}+\Im{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}+\imath [\Im{(\mathbf{g})}^{T}\cdot  \Re{(\mathbf{h})}-\Re{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}]=\mathbf{g}\cdot \mathbf{h}^{*}
 \label{CHSequation2}
-\end{eqnarray}
-
-\begin{equation}
-\mathbf{h}\mathbf{s}=\mathbf{h}^{r}\mathbf{s}^{r}-\mathbf{h}^{i}\mathbf{s}^{i}+i(\mathbf{h}^{i}\mathbf{s}^{r}+\mathbf{h}^{r}\mathbf{s}^{i}),
-\label{CHSequation3}
-\end{equation}
-Because of (\ref{CHSequation1}), (\ref{CHSequation2}) and (\ref{CHSequation3}), $\mathbf{h}_{i}\mathbf{s}\in <\mathbf{h}_{i},\mathbf{s}^{*}>_{\mathbb{H}}$.
+\end{IEEEeqnarray}
+
+Therefore $<\mathbf{m},\mathbf{l}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$.
 \end{proof}
-represent $\mathbf{s}^{*}$ by $\mathbf{w}$, The general regularized risk function of large MIMO detection in complex RKHS can be formulated:
-\begin{eqnarray}
-\nonumber
-minimize \quad \frac{1}{2}||w||_{\mathbb{H}}^{2}+C\sum_{k=1}^{N_{r}}[(R(\xi^{r}_{k})+R(\hat{\xi}^{r}_{k})+R(\xi^{i}_{k})+R(\hat{\xi}^{i}_{k}))]\\
+Therefore we have $<\mathbf{h}_{i}, \mathbf{s}^{*}>_{\mathbb{H}}=\mathbf{h}_{i}\cdot \mathbf{s}$, 
+For sake of simplicity we define $\mathbf{s}^{*}=\mathbf{w}$.
+Based on the same principle in the real case presented in (\ref{Introduce epsilon SVR}), the general regularized risk function of large MIMO detection in complex RKHS $\mathbb{H}$ defined by $<\mathbf{m}, \mathbf{l}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}$ can be formulated as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\min_{\mathbf{w}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i}} \quad \frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]\\
 s.t. \left\{\begin{array}{ll}
-Re(y_{k}-<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})\leq \epsilon+\xi^{r}_{k}\\
-Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}-y_{k})\leq \epsilon+\hat{\xi}^{r}_{k}\\
-Im(y_{k}-<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})\leq \epsilon+\xi^{i}_{k}\\
-Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}-y_{k})\leq \epsilon+\hat{\xi}^{i}_{k}\\
-\xi^{r}, \hat{\xi}^{r},\xi^{i},\hat{\xi}^{i}\geq 0\\
+\Re{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{r}_{i}, i=1,2,\ldots, N_{r}\\
+\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{r}_{i}, i=1,2,\ldots, N_{r}\\
+\Im{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{i}_{i}, i=1,2,\ldots, N_{r}\\
+\Im{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{i}_{i}, i=1,2,\ldots, N_{r}\\
+\xi^{r}_{i}, \hat{\xi}^{r}_{i},\xi^{i}_{i},\hat{\xi}^{i}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
 \end{array}\right.
 \label{complex objective function1}
-\end{eqnarray}
-where $Re()$ and $Im()$ denote real part and imaginary part of a complex variable, restrictions are set to real and imaginary part of regression function separately.
-Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denotes the kernel function, $\mathbf{K}=\mathbf{K}^{r}+i\mathbf{K}^{i}$, $\mathbf{K}^{r}$ and $\mathbf{K}^{i}$ denote matrix of corresponding real part and imaginary part.
-Similar to the Lagrange duality rational in section \ref{section lagrange duality}, Lagrange function is formulated for (\ref{complex objective function1})
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta =
-\frac{1}{2}||w||_{\mathbb{H}}^{2}+C\sum_{k=1}^{N_{r}}[(R(\xi^{r}_{k})+R(\hat{\xi}^{r}_{k})+R(\xi^{i}_{k})+R(\hat{\xi}^{i}_{k}))]- \sum_{k=1}^{N_{r}}(\eta_{i}\xi^{r}_{k}+\hat{\eta}_{k}\hat{\xi}^{r}_{k}+\tau_{k}\xi^{i}_{k}+\hat{\tau}_{k}\hat{\xi}^{i}_{k})\\
-\nonumber
--\sum_{k=1}^{N_{r}}\alpha_{k}(\epsilon+\xi^{r}_{k}-Re(y_{k})+Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))
--\sum_{k=1}^{N_{r}}\hat{\alpha}_{k}(\epsilon+\hat{\xi}^{r}_{k}+Re(y_{k})-Re(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))\\
-\nonumber
--\sum_{k=1}^{N_{r}}\beta_{k}(\epsilon+\xi^{i}_{k}-Im(y_{k})+Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))-\sum_{k=1}^{N_{r}}\hat{\beta}_{k}(\epsilon+\hat{\xi}^{i}_{k}+Im(y_{k})-Im(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}}))\\
+\end{IEEEeqnarray}
+ Where $\Re{(\cdot)}$ and $\Im{(\cdot)}$ denote real and imaginary part of a complex variable and inequality restrictions are set to real and imaginary part of the regression function separately.
+Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denote the kernel function, $\mathbf{K}=\Re{(\mathbf{K})}+\imath\Im{(\mathbf{K})}$, where $\Re{(\mathbf{K})}$ and $\Im{(\mathbf{K})}$ denote matrices of corresponding real and imaginary parts.
+Similar to the Lagrange duality rational in section \ref{section lagrange duality}, the Lagrange function associated with (\ref{complex objective function1}) is
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+L=
+\frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]- \sum_{i=1}^{N_{r}}(\eta_{i}\xi^{r}_{i}+\hat{\eta}_{i}\hat{\xi}^{r}_{i}+\tau_{i}\xi^{i}_{i}\\\nonumber +\hat{\tau}_{i}\hat{\xi}^{i}_{i})
++\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{r}_{i})
++\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}(\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})\\
+\nonumber
++\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}(\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\Im{(y_{i})}-\epsilon-\hat{\xi}^{i}_{i})\\
 s.t. \left\{\begin{array}{ll}
-\eta, \hat{\eta}, \tau, \hat{\tau} \alpha, \hat{\alpha}, \beta, \hat{\beta}\geq 0\\
-\xi^{r}, \hat{\xi}^{r}, \xi^{i}, \hat{\xi}^{i} \geq  0
+\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
+\xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i} \geq  0, i=1,2,\ldots, N_{r}
 \end{array}\right. 
@@
 \end{IEEEeqnarray}
-with Wirtinger's calculus applied to RKHS described in \cite{bouboulis2011extension}, The partial derivatives of $\theta$ respect to $\mathbf{w}$, which is define at complex domain, as well as the real variables $\xi^{r}$, $\hat{\xi}^{r}$, $\xi^{i}$ and $\hat{\xi}^{i}$ can be deduced
+where $\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}$ are Lagrange multipliers.
+In order to calculate the partial derivations of $L$ with respect to $\mathbf{w}$ which is defined in complex domain, the Wirtinger's calculus is exploited\cite{bouboulis2011extension} , Therefore we have
 \begin{IEEEeqnarray}[\relax]{l}
 \left\{\begin{array}{ll}
-\frac{\partial \Theta}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{k=1}^{N_{r}}\alpha_{k}\mathbf{h}_{k}+\frac{1}{2}\sum_{k=1}^{N_{r}}\hat{\alpha}_{k}\mathbf{h}_{k}+\frac{i}{2}(\sum_{k=1}^{N_{r}}\beta_{k}\mathbf{h}_{k}-\sum_{k=1}^{N_{r}}\hat{\beta}_{k}\mathbf{h}_{k})=0\\
-\Rightarrow \mathbf{w}=\sum_{k=1}^{N_{r}}(\alpha_{k}-\hat{\alpha}_{k})\mathbf{h}_{k}-i\sum_{k=1}^{N_{r}}(\beta_{k}-\hat{\beta}_{k})\mathbf{h}_{k}\\
-\frac{\partial \Theta}{\partial \xi^{r}_{k}}=CR^{'}(\xi^{r}_{k})-\eta_{k}-\alpha_{k}=0\Rightarrow \eta_{k}=CR^{'}(\xi^{r}_{k})-\alpha_{k}\\
-\frac{\partial \Theta}{\partial \hat{\xi}^{r}_{k}}=CR^{'}(\hat{\xi}^{r}_{k})-\hat{\eta}_{k}-\hat{\alpha}_{k}=0\Rightarrow \hat{\eta}_{k}=CR^{'}(\hat{\xi}^{r}_{k})-\hat{\alpha}_{k}\\
-\frac{\partial \Theta}{\partial \xi^{i}_{k}}=CR^{'}(\xi^{i}_{k})-\tau_{k}-\beta_{k}=0\Rightarrow \tau_{k}=CR^{'}(\xi^{i}_{k})-\beta_{k}\\
-\frac{\partial \Theta}{\partial \hat{\xi}^{i}_{k}}=CR^{'}(\hat{\xi}^{i}_{k})-\hat{\eta}_{k}-\hat{\beta}_{k}=0\Rightarrow \hat{\eta}_{k}=CR^{'}(\hat{\xi}^{i}_{k})-\hat{\beta}_{k}\\
+\frac{\partial L}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{i=1}^{N_{r}}\alpha_{i}\mathbf{h}_{i}+\frac{1}{2}\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\mathbf{h}_{i}+\frac{\imath}{2}(\sum_{i=1}^{N_{r}}\beta_{i}\mathbf{h}_{i}-\sum_{i=1}^{N_{r}}\hat{\beta}_{i}\mathbf{h}_{i})=0\\
+\Rightarrow \mathbf{w}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-\imath\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\\
+\frac{\partial L}{\partial \xi^{r}_{i}}=CR^{'}(\xi^{r}_{i})-\eta_{i}-\alpha_{i}=0\Rightarrow \eta_{i}=CR^{'}(\xi^{r}_{i})-\alpha_{i}\\
+\frac{\partial L}{\partial \hat{\xi}^{r}_{i}}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\Rightarrow \hat{\eta}_{i}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\alpha}_{i}\\
+\frac{\partial L}{\partial \xi^{i}_{i}}=CR^{'}(\xi^{i}_{i})-\tau_{i}-\beta_{i}=0\Rightarrow \tau_{i}=CR^{'}(\xi^{i}_{i})-\beta_{i}\\
+\frac{\partial L}{\partial \hat{\xi}^{i}_{i}}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\tau}_{i}-\hat{\beta}_{i}=0\Rightarrow \hat{\tau}_{i}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\beta}_{i}\\
 
@@
 \nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}+i(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{i}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}),
+=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\\nonumber
+=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\\ \sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}),
 \label{complex duality regression function}
@@
 \end{IEEEeqnarray}
-Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$, if we have $r_{i}$ and $r_{j}$ $\in \mathbb{R}$, 
-\begin{equation}
-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij}=-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ji}=-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij},
+Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$. If we have $r_{i}$, $r_{j}$ $\in \mathbb{R}$, then 
+\begin{equation}
+\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ji}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij},
 \end{equation}
@@
 \begin{equation}
-\sum_{i,j}^{l}r_{i}r_{j}\mathbf{K}^{i}_{ij}=0,
+\sum_{i,j}^{l}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=0,
 \label{conjugate1}
@@
 \begin{equation}
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{K}^{r}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{K}^{r}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{i}_{ij}.
+||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}.
 \label{complex duality regularization2}
@@
 \nonumber
-maximize\quad \theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
+L=\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}]+\\
+\nonumber
+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})]- \sum_{i=1}^{N_{r}}((CR^{'}(\xi^{r}_{i})-\alpha_{i})\xi^{r}_{i}+(CR^{'}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}^{r}_{i}+(CR^{'}-\beta_{i})\xi^{i}_{i}\\\nonumber +(CR^{'}(\hat{\xi}_{i})-\hat{\beta}_{i})\hat{\xi}^{i}_{i})+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\epsilon-\xi^{r}_{i})
++\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\\ \nonumber
+((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})
++\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\\ \nonumber
+\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\Im{(y_{i})}-\\
+\epsilon-\hat{\xi}^{i}_{i})
+\label{complex lagrange duality inter1}
+\end{IEEEeqnarray}
+
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\theta=-\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}]+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})-\xi_{i}^{r}R^{'}(\xi^{r}_{i})\\\nonumber
++R(\hat{\xi}^{r}_{i})-\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})-\xi_{i}R^{'}(\xi_{i}^{i})+R(\hat{\xi}^{i}_{i})-\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]+\sum_{i=1}^{N_{r}}[\Re{(y_{i})}(\alpha_{i}-\hat{\alpha}_{i})+\Im{(y_{i})}(\beta_{i}-\hat{\beta}_{i})]-\\
+\epsilon\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta_{i}+\hat{\beta}_{i})
+\label{complex lagrange duality inter2}
+\end{IEEEeqnarray}
+define $\tilde{R}(u)=R(u)-uR^{'}(u)$. Similar to (\ref{dual optimization function2}), The dual optimization problem of complex MIMO system is 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{\alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}}\quad \theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
 \nonumber
@@
 \left\{\begin{array}{ll}
-0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
-0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
-\xi^{r}(\hat{\xi}^{r})\geq 0\\
-\xi^{i}(\hat{\xi}^{i})\geq 0\\
+0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
+0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
+\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
+\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
 \end{array}\right.
@@
 \end{IEEEeqnarray}
-which can be divided into 2 independent regression task,
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-maximize \quad \theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
+Notice in (\ref{final complex lagrange duality}), there is no correlation term between $\alpha_{i}, \hat{\alpha}_{i}$ and $\beta_{i}, \hat{\beta}_{i}$, therefore, (\ref{final complex lagrange duality}) can be divided into two independent regression tasks,
+
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{\alpha_{i}, \hat{\alpha}_{i}} \quad \theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
 \nonumber
@@
 \left\{\begin{array}{ll}
-0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
-\xi^{r}(\hat{\xi}^{r})\geq 0\\
+0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
+\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
 \end{array}\right.
@@
 \nonumber
-maximize \quad \theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
+\max_{\beta_{i}, \hat{\beta}_{i}} \quad \theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
 \nonumber
@@
 \left\{\begin{array}{ll}
-0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
-\xi^{i}(\hat{\xi}^{i})\geq 0\\
+0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
+\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
 \end{array}\right.
@@
 \end{IEEEeqnarray}
-
+Let $\mathbf{a}=[\alpha_{1}, \alpha_{2},\ldots, \alpha_{N_{r}}]^{T}$, $\mathbf{\hat{a}}=[\hat{\alpha}_{1}, \hat{\alpha}_{2},\ldots, \hat{\alpha}_{N_{r}}]^{T}$, $\mathbf{b}=[\beta_{1}, \beta_{2},\ldots, \beta_{N_{r}}]^{T}$,$\mathbf{\hat{b}}=[\hat{\beta}_{1}, \hat{\beta}_{2},\ldots, \hat{\beta}_{N_{r}}]^{T}$, $\Re{(\mathbf{y})}=[\Re{(y_{1})}, \Re{(y_{2})},\ldots, \Re{(y_{N_{r}})}]^{T}$, $\Im{(\mathbf{y})}=[\Im{(y_{1})}, \Im{(y_{2})}, \ldots, \Im{(y_{N_{r}})}]^{T}$, $\mathbf{R}^{r}=[\tilde{R}(\xi^{r}_{1})+\tilde{R}(\hat{\xi}^{r}_{1}), \tilde{R}(\xi^{r}_{2})+\tilde{R}(\hat{\xi}^{r}_{2}), \ldots, \tilde{R}(\xi^{r}_{N_{r}})+\tilde{R}(\hat{\xi}^{r}_{N_{r}})]^{T}$, $\mathbf{R}^{i}=[\tilde{R}(\xi^{i}_{1})+\tilde{R}(\hat{\xi}^{i}_{1}), \tilde{R}(\xi^{i}_{2})+\tilde{R}(\hat{\xi}^{i}_{2}), \ldots, \tilde{R}(\xi^{i}_{N_{r}})+\tilde{R}(\hat{\xi}^{i}_{N_{r}})]^{T}$, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$.
 The alternate form can be written as
@@
 \nonumber
-maximize \quad \theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r})))\\
+\max_{\mathbf{a},\mathbf{\hat{a}}} \quad \theta^{r}=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\Re{(\mathbf{K})}(\mathbf{a}-\mathbf{\hat{a}})+\Re{(\mathbf{y})}^{T}(\mathbf{a}-\mathbf{\hat{a}})-\epsilon(\mathbf{e}^{T}(a+\mathbf{\hat{a}}))+C(\mathbf{e}^{T}\mathbf{R}^{r})\\
 \left\{\begin{array}{ll}
-0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
-\xi^{r}(\hat{\xi}^{r})\geq 0\\
+0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
+\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
 \end{array}\right.
@@
 \nonumber
-maximize \quad \theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})+\tilde{R}(\hat{\xi}^{i})))\\
+\max_{\mathbf{b}, \mathbf{\hat{b}}} \quad \theta^{i}=-\frac{1}{2}(\mathbf{b}-\mathbf{\hat{b}})^{T}\Re{(\mathbf{K})}(\mathbf{b}-\mathbf{\hat{b}})+\Im{(\mathbf{y})}^{T}(\mathbf{b}-\mathbf{\hat{b}})-\epsilon(\mathbf{e}^{T}(\mathbf{b}+\mathbf{\hat{b}}))+C(\mathbf{e}^{T}\mathbf{R}^{i})\\
 \left\{\begin{array}{ll}
-0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
-\xi^{i}(\hat{\xi}^{i})\geq 0\\
+0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, N_{r}\\
+\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, N_{r}\\
 \end{array}\right.
@@
 \end{IEEEeqnarray}
-where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components.
-Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), only the real part of kernel matrix is required for each channel.
-In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping criteria.
-Therefore, in large MIMO uplink system, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.
+
+Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), where only the real part of the kernel matrix is required for each channel.
+This can provide computational advantages for solving the dual optimization problems.
 \section{Work Set Selection and Solver}\label{WSS}
-(\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.
-
-Decomposition method is a set of efficient algorithms that can help to conquer this difficulty.
-Decomposition method works iteratively, the basic idea of decomposition method is to choose a subset of variable pairs $S$ (named work set) to optimize in each iteration step while keep the rest variable pairs $N$ fixed.
-Sequential Minimal Optimization (SMO) is an extreme case of decomposition method, the work set size is 2, an analytic quadratic programming (QP) step instead of numerical QP step can be taken in each iteration.
-
-Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) are symmetric, in this section we discuss real part only.
-By dividing the variables into work set $S$ and fixed set $N$, we can divide vector $\alpha$ into two sub vectors, $[\alpha_{S}, \alpha_{N}]$.
-Thus (\ref{complex duality real part vectorizes}) can be changed to:
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-maximize\quad \theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}+2(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}(\alpha-\hat{\alpha})_{S}]
-+Re(\mathbf{y})_{S}^{T}(\alpha-\hat{\alpha})_{S}-\\
-\nonumber
-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{S})
--\frac{1}{2}(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NN}^{r}(\alpha-\hat{\alpha})_{N}+Re(\mathbf{y})_{N}^{T}(\alpha-\hat{\alpha})_{N}-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{N})\\+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r}))),
+In (\ref{final complex lagrange duality}) we have a quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with a large data set.
+
+Decomposition methods are a set of efficient algorithms that can help to ease this difficulty.
+Decomposition methods work iteratively, and based on choosing a subset of variables $S$ (named work set) to optimize in each iteration step, while keeping the rest variables $N$ fixed.
+Sequential Minimal Optimization (SMO) is an extreme case of decomposition method, where the work set size is 2, and an analytic quadratic programming (QP) step instead of numerical QP step can be performed in each iteration.
+
+Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) have the same structure, in this section we discuss the real part only.
+By dividing the variables into work set $S$ and fixed set $N$, we can divide vector $\mathbf{a}$ into two sub vectors $[\mathbf{a}_{S}, \mathbf{a}_{N}]$.
+thereafter $\mathbf{a}_{S}$ denotes a vector that consists of the components of $\mathbf{a}$ that belongs to set $S$, the same modifications are applied to $\mathbf{\hat{a}}$ and $\mathbf{y}$.
+Thus (\ref{complex duality real part vectorizes}) can be rewritten as:
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}, \mathbf{a}_{N}, \hat{\mathbf{a}}_{N}} \theta= -\frac{1}{2}[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
+\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
+\end{IEEEeqnarraybox*}\right]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
+\end{IEEEeqnarraybox*}\right]+[\Re{(\mathbf{y}_{S})}^{T}, \Re{(\mathbf{y}_{N})}^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
+\end{IEEEeqnarraybox*}\right]-\\\nonumber\epsilon[\mathbf{e}^{T}_{S}, \mathbf{e}^{T}_{N}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S})\\
+(\mathbf{a}_{N}+\hat{\mathbf{a}}_{N})
+\end{IEEEeqnarraybox*}\right]+C(\mathbf{e}^{T}, \mathbf{R}^{r})
+\\
+\left\{\begin{array}{ll}
+0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
+\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
+\end{array}\right.
+\label{real part decomposition inter1}
+\end{IEEEeqnarray}
+
+Where $\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
+\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
+\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{\mathbf{a}, \mathbf{\hat{a}}}\quad \theta^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})+2(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]
++\Re{(\mathbf{y}_{S}^{T})}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\
+\nonumber
+\epsilon(\mathbf{e}^{T}(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S}))
+-\frac{1}{2}(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NN}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})+\Re{(\mathbf{y}_{N}^{T})}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{N}+\mathbf{\hat{a}}_{N}))\\\nonumber+C(\mathbf{e}^{T}(\mathbf{R}^{r}),
+\\
+\left\{\begin{array}{ll}
+0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
+\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
+\end{array}\right.
 \label{real part decomposition}
 \end{IEEEeqnarray}
-Where $\mathbf{K}^{r}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\mathbf{K}^{r}_{SS}& \mathbf{K}^{r}_{SN}\\
-\mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
-\end{IEEEeqnarraybox*}\right]$ is a permutation of $\mathbf{K}^{r}$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$ 
-and  $\alpha_{S}\in \mathbb{R}^{|S|}$ denotes the vector constitute of all the $\alpha_{i}\in S$.
-In each iteration, in (\ref{real part decomposition}), $\alpha_{N}$ is fixed and only the sub problem that correlated to $\alpha_{S}$ is solved i.e
-\begin{equation}
-maximize\quad \theta_{S}^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]+[Re(\mathbf{y})_{S}^{T}-(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
-](\alpha-\hat{\alpha})_{S}-\epsilon<\mathbf{e}_{S}^{T}, (\alpha+\hat{\alpha})>,
+In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is solved i.e 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{\mathbf{a}_{S}, \mathbf{\hat{a}}_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]+[Re(\mathbf{y}_{S}^{T})-(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\mathbf{K}_{NS}^{r}
+](\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\\nonumber\epsilon<\mathbf{e}^{T}, (\mathbf{a}_{S}+\mathbf{\hat{a}}_{S})>,
+\\
+\left\{\begin{array}{ll}
+0\leq [\mathbf{a}_{S}]_{i}([\hat{\mathbf{a}}_{S}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i\in S\\
+\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i\in S\\
+\end{array}\right.
 \label{subset optimization}
-\end{equation}
-In decomposition method, a proper work set selection strategy is required so that speed and performance requirement can be guaranteed.
-One approach is to choose dual variable pairs that violate KKT conditions, so that after each iteration, the objective function can be increased according to Osuna's theorem\cite{osuna1997improved}, Heuristic methods are used in in order to accelerate process, in work set selection process, the algorithm first searches among the non-bound variables (that is $0<\alpha<C\tilde{R}(\xi)$), which are more likely to violate KKT condition, then searching the whole dual variable set, the second dual variable that can maximize optimization step of the first coordinate is chosen, approximate step size is used as evaluator for sake of reducing computational cost.
-Lin propose another work set selection strategy based on an alternative form of KKT condition.
-
-Another class of approaches is to choose the dual variables whose update can provide the maximum improvements to objective function. That is 
-\begin{equation}
-maximize\quad \bigtriangledown \theta_{S}=\theta_{S}((\alpha+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}+\hat{\delta}_{S}\mathbf{e}_{S}))-\theta_{S}(\alpha, \hat{\alpha}),
+\end{IEEEeqnarray}
+A proper work set selection strategy is required so that speed and performance requirement can be guaranteed.
+One idea is to perform update to dual variables that violate the complementary KKT conditions, which, based on (\ref{original KKT condition3}) in \ref{section lagrange duality}, can be formulated as
+\begin{IEEEeqnarray}[\relax]{l}
+\left\{\begin{array}{ll}
+(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
+(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
+\alpha(\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})=0, i=1,2,\ldots, L\\
+\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})})=0, i=1,2,\ldots, L\\
+\end{array}\right.
+\label{complementary KKT condition1}
+\end{IEEEeqnarray}
+According to Osuna's theorem\cite{osuna1997improved}, the final convergence can be guaranteed.
+In SMO algorithm, heuristic methods are used to find a work set of size two in order to accelerate the decomposition process\cite{platt1999fast}.
+The heuristic method first searches among the non-bound variables (that is $0<\alpha_{i}<C\tilde{R}(\xi^{r}_{i})$ and $0<\hat{\alpha}_{i}<C\tilde{R}(\hat{\xi}_{i})$), which are more likely to violate the complementary KKT conditions, Then searching the whole dual variable set.
+The second dual variable that can maximize optimization step size is chosen.
+An approximate step size is used as evaluator for sake of reducing computational cost.
+
+Another idea for work set selection is to choose the dual variables whose update can provide the maximum improvements to dual objective function. That is
+\begin{equation}
+\bigtriangledown \theta^{r}_{S}=\theta^{r}_{S}((\mathbf{a}_{S}+\Delta_{S}), (\hat{\mathbf{a}}_{S}+\hat{\Delta}_{S}))-\theta^{r}_{S}(\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}),
 \label{maximum gain work set selection}
 \end{equation} 
-where $\delta_{S}=\alpha_{S}^{new}-\alpha_{S}$, the gain in (\ref{maximum gain work set selection}) can be written as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+2(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}]+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}](\delta-\hat{\delta})_{S}\\
--\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+[Re(\mathbf{y})^{T}_{S}-(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S}](\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}
+where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\mathbf{a}_{S}$ is the update of $\mathbf{a}^{new}_{S}$.
+$\bigtriangledown \theta_{S}^{r}$ in (\ref{maximum gain work set selection}),  based on (\ref{subset optimization}), can be written as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathfrak{n}_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta})_{S}]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})\\
+-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}](\Delta_{S}-\hat{\Delta}_{S})\\
+-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S}),
 \label{gain work set selection1}
 \end{IEEEeqnarray} 
-In (\ref{gain work set selection1}), we use 
-\begin{IEEEeqnarray}[\relax]{l}
-(\alpha-\hat{\alpha})^{T}_{S}\mathbf{K}^{r}_{SS}+(\alpha-\hat{\alpha})^{T}_{N}\mathbf{K}^{r}_{NS}=[(\alpha-\hat{\alpha})^{T}_{S}, (\alpha-\hat{\alpha})^{T}_{N}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\mathbf{K}^{r}_{SS}\\
-\mathbf{K}^{r}_{NS}
-\end{IEEEeqnarraybox*}\right]=(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}_{S},
+Notice in (\ref{gain work set selection1}), we use 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}=[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\Re{(\mathbf{K})}_{SS}\\
+\Re{(\mathbf{K})}_{NS}
+\end{IEEEeqnarraybox*}\right]=\\
+(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S},
 \label{modification of gain work set selection}
 \end{IEEEeqnarray}
-where $\mathbf{K}^{r}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns  that belong to work set $S$.
-Then we define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Phi^{r}=Re(\mathbf{y})-\mathbf{K}^{r}(\alpha-\hat{\alpha})$ and $\Phi^{i}=Im(\mathbf{y})-\mathbf{K}^{r}(\beta-\hat{\beta})$
+where $\Re{(\mathbf{K})}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns corresponding to the work set $S$.
+Then we define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Re{(\Phi)}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Im{(\Phi)}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$
 Thus (\ref{gain work set selection1}) can be rewritten as 
 \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\delta-\hat{\delta})^{T}_{S}\mathbf{K}^{r}_{SS}(\delta-\hat{\delta})_{S}+(\Phi^{r}_{S})^{T}(\delta-\hat{\delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\delta+\hat{\delta})_{S}
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta})^{T}_{S}\Re{(\mathbf{K})}_{SS}(\Delta-\hat{\Delta})_{S}+(\Re{(\Phi)}_{S})^{T}(\Delta-\hat{\Delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\Delta+\hat{\Delta})_{S}
 \label{gain work set selection2}
 \end{IEEEeqnarray} 
-The offset term is omitted in Large MIMO system, therefore different from SMO type algorithms, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration.
-However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{steinwart2011training}.
-Here we propose sequential 1-D work set selection strategy, which can approximate the performance of optimal 2-D work set selection, while only $O(n)$ searching times required for the former one instead of $O(n^{2})$ searching times.
+Because the offset term is omitted in Large MIMO regression model, therefore different from SMO type algorithms, there is no linear equation constraint, which is inducted by offset $b$, as shown in (\ref{partial4}).
+Therefore it is possible to update only one variable pair in each iteration.
+However, more efficient work set selection strategies based on maximum dual objective gain selection without considering offset term, is proposed in \cite{steinwart2011training}.
+A work set of size two is updated in each iteration.
+The computational cost is reduced while maintaining the comparable performance with that with offset.
+In CSVR large MIMO detector, the work set selection strategy in \cite{steinwart2011training} is exploited.
+Basically, in each iteration this strategy uses sequential single variable searchings, whose searching time is $O(n)$, where $n$ is the number of data set, to determine a work set of size two.
+On the one hand, this strategy can find a work set of size two, whose update approximately maximize the gain in the dual objective function.
+On the other hand, the brute-force searching for the work size of two, whose update can maximize the gain in the dual objective function, requires $O(n^{2})$ searching time.
+The former strategy requires as few iterations as the latter one, since in each iteration, the latter strategy is more expensive, the former one can enjoy significantly faster running speed.
 \subsection{Single Direction Solver}\label{single direction solver}
-Recall KKT complementary condition
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-(C\tilde{R}(\xi^{r})-\alpha)\xi^{r}=0\\
-(C\tilde{R}(\hat{\xi}^{r})-\hat{\alpha})\hat{\xi}^{r}=0\\
-\alpha(Re(y)-<\mathbf{h},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi^{r})=0\\
-\hat{\alpha}(<\mathbf{h},\mathbf{w}>_{\mathbb{H}}-Re(y)-\epsilon-\hat{\xi}^{r})=0\\
-\end{array}\right.
-\label{complementary KKT condition}
-\end{IEEEeqnarray}
-it can be easily observed that $\alpha\hat{\alpha}=0$, because $0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(C\tilde{R}(\hat{\xi}^{r}))$,  $\xi^{r}$ and $\hat{\xi}^{r}$ satisfy $\xi^{r}\hat{\xi}^{r}=0$.
-Hence we can substitute $\lambda=\alpha-\hat{\alpha}$ and $|\lambda|=\alpha+\hat{\alpha}$, therefore the update unit is single optimization variable $\lambda$, rather than pair $\alpha$ and $\hat{\alpha}$.
- We will first introduce 1-D work set selection strategy in which one optimization variable that maximizes the gain of objective function is updated in one iteration.
-Reformulate by $\lambda$ and $\sigma=\lambda^{new}-\lambda$ sub optimization objective function(\ref{subset optimization}) and its gain (\ref{gain work set selection2})
-  \begin{equation}
-maximize\quad \theta_{S}^{r}=-\frac{1}{2}[\lambda_{S}^{T}\mathbf{K}_{SS}^{r}\lambda_{S}]+[Re(\mathbf{y})_{S}^{T}-\lambda_{N}^{T}\mathbf{K}_{NS}^{r}
-]\lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\lambda_{S}|>,
+Recall the KKT complementary conditions 
+\begin{IEEEeqnarray}[\relax]{l}
+\label{KKT complementary1}
+(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
+\label{KKT complementary2}
+(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
+\label{KKT complementary3}
+\alpha(\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})=0, i=1,2,\ldots, L\\
+\label{KKT complementary4}
+\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})})=0, i=1,2,\ldots, L\\\nonumber
+\label{complementary KKT condition2}
+\end{IEEEeqnarray}
+notice that in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}$ and  $\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})}$ can be non zero, therefore in order to satisfy the equalities, at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$, because $0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(C\tilde{R}(\hat{\xi}_{i}^{r}))$ and $\alpha_{i}\hat{\alpha}_{i}=0$, there is at least one of $C\tilde{R}(\xi_{i}^{r})-\alpha_{i}$ and $C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i}$ in (\ref{KKT complementary1}) and (\ref{KKT complementary2}) is non zero, in order to satisfy the equalities, there is at least one of $\xi_{i}$ and $\hat{\xi}_{i}$ need to be zero, that is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
+Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.
+
+  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of dual objective function is chosen as the work set in each iteration.
+Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]$.
+Substitute $\mathbf{a}, \hat{\mathbf{a}}$ with $\Lambda$ and using $\Sigma$.
+Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2})
+  \begin{equation}
+\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y})}_{S}^{T}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
+]\Lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\Lambda_{S}|>,
 \label{subset optimization lambda}
@@
 \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\sigma^{T}_{S}\mathbf{K}^{r}_{SS}\sigma_{S}+(\Phi^{r}_{S})^{T}\sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\lambda^{new}_{S}|-|\lambda_{S}|>,
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
 \label{gain work set selection lambda}
 \end{IEEEeqnarray} 
-For 1-D solver, the sub optimization objective function can be written as
-\begin{IEEEeqnarray}[\relax]{l}
- maximize\quad \theta_{1}^{r}=-\frac{1}{2}(\lambda_{1}^{new})^{2}\mathbf{K}_{11}^{r}
-+[Re(y_{1})-\sum_{j=2}^{N_{r}}\mathbf{K}_{1j}^{r}\lambda_{j}]\lambda_{1}^{new}-\epsilon(|\lambda^{new}_{1}|),
+In 1-D solver, $|S|=1$, the sub dual objective function corresponding to $\lambda_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
+\begin{IEEEeqnarray}[\relax]{l}
+ \max_{\lambda_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\lambda_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
++[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\lambda_{m}^{new}-\epsilon(|\lambda^{new}_{m}|),
  \label{optimization function 1-D}
  \end{IEEEeqnarray}
-take the partial derivative of $\theta_{1}^{r}$ respect to $\lambda^{new}_{1}$, where we define $\Phi_{i}^{r}=Re(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}_{ij}^{r}$, similarly, as to dual variable $\lambda^{i}$ , we define $\Phi_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}_{ij}^{r}$.
-Here for sake of brevity, we use $\lambda$.
-Hence we have
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\frac{\partial \theta_{1}^{r}}{\partial \lambda^{new}_{1}}=-\lambda_{1}^{new}\mathbf{K}_{11}^{r}+Re(y_{1})-\sum_{j=2}^{N_{r}}\lambda_{j}\mathbf{K}_{1j}^{r}-\epsilon(sgn(\lambda^{new}_{1}))=\\
-\nonumber
--\lambda_{1}^{new}\mathbf{K}_{11}^{r}+\Phi^{r}_{1}+\lambda_{1}\mathbf{K}^{r}_{11}-\epsilon(sgn(\lambda^{new}_{1}))\\
-\Rightarrow \lambda_{1}^{new}=\lambda_{1}+\frac{\Phi_{1}^{r}-\epsilon(sgn(\lambda^{new}_{1}))}{\mathbf{K}_{11}^{r}},
+ Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Re{(\Phi)}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$, $\Re{(\Phi)}_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$.
+Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
+Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))=\\
+\nonumber
+-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
+\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Re{(\Phi)}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
 \label{partial optimization function 1-D lambda}
@@
 \begin{IEEEeqnarray}[\relax]{l}
-\lambda^{new\quad clipped}_{1}=[\lambda^{new}_{1}]^{CR^{'}(\xi)}_{-CR^{'}(\xi)}
+\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
 \label{clipped new dual variable}
@@
 \end{IEEEeqnarray}
-Define $\sigma=\lambda^{new\quad clipped}-\lambda$, based on (\ref{gain work set selection lambda}), The gain of objective function respect to $i$th optimization variable is 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{i}^{r}=\theta^{r}(\lambda_{1}+\sigma_{1})-\theta^{r}(\lambda_{1})\\
-\nonumber
-=-\frac{1}{2}\sigma_{i}^{2}\mathbf{K}_{ii}^{r}+\Phi^{r}_{i}\sigma_{i}-\epsilon(|\lambda^{new\quad cipped}_{i}|-|\lambda_{i}|)\\
-=\sigma_{i}[-\frac{1}{2}\sigma_{i}\mathbf{K}_{ii}^{r}+\Phi_{i}^{r}]-\epsilon(|\lambda^{new\quad clipped}_{i}|-|\lambda_{i}|),
+based on (\ref{gain work set selection lambda}), The maximum gain of objective function respect to the $m$th optimization variable $\lambda_{m}$ is 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta_{m}^{r}=\theta_{m}^{r}(\lambda_{m}+\sigma_{m})-\theta_{m}^{r}(\lambda_{m})\\
+\nonumber
+=-\frac{1}{2}\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}\sigma_{m}-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)\\
+=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|),
 \label{gain of 1-D objective function}
 \end{IEEEeqnarray}
-In 1-D searching procedure, the optimization variable which has the maximum gain of sub optimization objective function is updated as $1$ in (\ref{optimization function 1-D}), that is 
-\begin{equation}
-1=arg_{(i=1,\ldots, N_{r})}\max \bigtriangledown \Theta_{i}^{r},
+In 1-D searching procedure, the optimization variable whose update has the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, that is 
+\begin{equation}
+k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r},
 \label{1-D direction}
@@
 \subsection{Double Direction Solver}\label{double direction solver}
-Although omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however recent work in machine learning field shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained.
-The 2-D solver uses the same principle as 1-D solver, the work set size is 2, that is $\lambda_{S}=\lambda_{1}\mathbf{e}_{1}+\lambda_{2}\mathbf{e}_{2}$.
-Based on (\ref{gain work set selection lambda}), the sub objective function can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-maximize\quad \theta^{r}_{1,2}=-\frac{1}{2}[(\lambda^{new}_{1})^{2}\mathbf{K}^{r}_{11}+(\lambda^{new}_{2})^{2}\mathbf{K}^{r}_{22}+2\lambda^{new}_{1}\lambda^{new}_{2}\mathbf{K}^{r}_{12}]-\\
-\nonumber
-\lambda^{new}_{1}\sum_{j\neq 1, 2}^{N_{r}}\lambda_{j}\mathbf{K}^{r}_{1j}-\lambda^{new}_{2}\sum_{j\neq 1, 2}^{N_{r}}\lambda_{j}\mathbf{K}^{r}_{2j}+Re(y_{1})\lambda^{new}_{1}+Re(y_{2})\lambda^{2}_{2}\\
--\epsilon(|\lambda^{new}_{1}|+|\lambda_{2}^{new}|), 
+Although the omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however, recent work in machine learning field shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained\cite{steinwart2011training}.
+The optimal 2-D solver uses the same principle as 1-D solver, $|S|=2$, assume the work set consists of the $m$th and $n$th optimization variables, that are $\Lambda_{S}=[\lambda_{m}, \lambda_{n}]$.
+Based on (\ref{gain work set selection lambda}), the sub dual objective function can be written as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{\lambda_{m}, 
+\lambda_{n}}\quad \theta^{r}_{m,n}=-\frac{1}{2}[(\tilde{\lambda}^{new}_{m})^{2}\Re{(\mathbf{K})}_{mm}+(\tilde{\lambda}^{new}_{n})^{2}\Re{(\mathbf{K})}_{nn}+2\tilde{\lambda}^{new}_{m}\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}]-\\
+\nonumber
+\tilde{\lambda}^{new}_{m}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\tilde{\lambda}^{new}_{n}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{m})}\tilde{\lambda}^{new}_{1}+\Re{(\mathbf{y}_{n})}\tilde{\lambda}^{2}_{n}\\
+-\epsilon(|\lambda^{new}_{m}|+|\tilde{\lambda}_{n}^{new}|), 
 \label{2-D solver}
 \end{IEEEeqnarray}
-Based on (\ref{2-D solver}), the partial derivatives of $\theta^{r}_{1,2}$ with respect to $\lambda^{new}_{1}$ and $\lambda_{2}^{new}$ are 
+Based on (\ref{2-D solver}), the partial derivatives of $\theta^{r}_{m,n}$ with respect to $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}_{n}^{new}$ are 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \label{lambda1 partial}
-\frac{\partial \theta^{r}_{1,2}}{\partial \lambda^{new}_{1}}=-\lambda^{new}_{1}\mathbf{K}^{r}_{11}-\lambda^{new}_{2}\mathbf{K}^{r}_{12}-\sum_{j\neq 1, 2}^{N_{r}}\lambda_{j}\mathbf{K}^{r}_{1j}+Re(y_{1})-\epsilon sgn(\lambda^{new}_{1})=\\
--\lambda_{1}^{new}\mathbf{K}^{r}_{11}-\lambda^{new}_{2}\mathbf{K}^{r}_{12}+\Phi^{r}_{1}+\lambda_{1}\mathbf{K}^{r}_{11}+\lambda_{2}\mathbf{K}^{r}_{12}-\epsilon sgn(\lambda^{new}_{1})=0\\
+\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}+\Re{(\mathbf{y}_{m})}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=\\
+-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}+\Re{(\Phi)}_{m}+\lambda_{m}\Re{\mathbf{K}}_{mm}+\lambda_{n}\Re{(\mathbf{K})}_{mn}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=0\\
 \nonumber
 \label{lambda2 partial}
-\frac{\partial \theta^{r}_{1,2}}{\partial \lambda^{new}_{2}}=-\lambda^{new}_{2}\mathbf{K}^{r}_{22}-\lambda^{new}_{1}\mathbf{K}^{r}_{12}-\sum_{j\neq 1, 2}^{N_{r}}\lambda_{j}\mathbf{K}^{r}_{2j}+Re(y_{2})-\epsilon sgn(\lambda^{new}_{2})=\\
--\lambda_{2}^{new}\mathbf{K}^{r}_{22}-\lambda^{new}_{1}\mathbf{K}^{r}_{12}+\Phi^{r}_{2}+\lambda_{1}\mathbf{K}^{r}_{12}+\lambda_{2}\mathbf{K}^{r}_{22}-\epsilon sgn(\lambda^{new}_{2})=0\\
+\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{n}}=-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{n})}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=\\
+-\tilde{\lambda}_{n}^{new}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}+\Re{(\Phi)}_{n}+\lambda_{m}\Re{(\mathbf{K})}_{mn}+\lambda_{n}\Re{(\mathbf{K})}_{nn}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=0\\
 \nonumber
@@
 \label{post partial lambda1}
-(\lambda^{new}_{1}-\lambda_{1})\mathbf{K}^{r}_{11}=\Phi^{r}_{1}-\epsilon sgn(\lambda^{new}_{1})-(\lambda^{new}_{2}-\lambda_{2})\mathbf{K}^{r}_{12}\\
+(\tilde{\lambda}^{new}_{m}-\lambda_{n})\Re{(\mathbf{K})}_{mm}=\Re{(\Phi)}_{m}-\epsilon sgn(\tilde{\lambda}^{new}_{m})-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{mn}\\
 \label{post partial lambda2}
-(\lambda^{new}_{2}-\lambda_{2})\mathbf{K}^{r}_{22}=\Phi^{r}_{2}-\epsilon sgn(\lambda^{new}_{2})-(\lambda^{new}_{1}-\lambda_{1})\mathbf{K}^{r}_{12}\\
-\nonumber
-\end{IEEEeqnarray}
-hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formula of $\lambda^{new}_{1}$ and $\lambda^{new}_{2}$ are
-\begin{equation}
-\lambda^{new}_{1}=\lambda_{1}+\frac{\Phi^{r}_{1}\mathbf{K}^{r}_{22}-\Phi^{r}_{2}\mathbf{K}^{r}_{12}-\epsilon[sgn(\lambda^{new}_{1})\mathbf{K}^{r}_{22}-sgn(\lambda^{new}_{2})\mathbf{K}^{r}_{12}]}{\mathbf{K}^{r}_{11}\mathbf{K}^{r}_{22}-(\mathbf{K}^{r}_{12})^{2}}
+(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{nn}=\Re{(\Phi)}_{n}-\epsilon sgn(\tilde{\lambda}^{new}_{n})-(\tilde{\lambda}^{new}_{m}-\lambda_{m})\Re{(\mathbf{K})}_{mn}\\
+\nonumber
+\end{IEEEeqnarray}
+hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formula of $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}^{new}_{n}$ are
+\begin{equation}
+\tilde{\lambda}^{new}_{m}=\lambda_{m}+\frac{\Re{(\Phi)}_{m}\Re{(\mathbf{K})}_{nn}-\Re{(\Phi)}_{n}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{nn}-sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
 \label{update lambda1}
@@
 \begin{equation}
-\lambda^{new}_{2}=\lambda_{2}+\frac{\Phi^{r}_{2}\mathbf{K}^{r}_{11}-\Phi^{r}_{1}\mathbf{K}^{r}_{12}-\epsilon[sgn(\lambda^{new}_{2})\mathbf{K}^{r}_{11}-sgn(\lambda^{new}_{1})\mathbf{K}^{r}_{12}]}{\mathbf{K}^{r}_{11}\mathbf{K}^{r}_{22}-(\mathbf{K}^{r}_{12})^{2}}
+\tilde{\lambda}^{new}_{n}=\lambda_{n}+\frac{\Re{(\Phi)}_{n}\Re{(\mathbf{K})}_{mm}-\Re{(\Phi)}_{m}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mm}-sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
 \label{update lambda2}
@@
 \begin{IEEEeqnarray}[\relax]{l}
-\lambda^{new\quad clipped}=[\lambda^{new}]^{CR^{'}(\xi)}_{-CR^{'}(\xi)},
+\nonumber
+\lambda_{i}^{new}=[\tilde{\lambda}_{i}^{new}]^{CR^{'}(\xi_{i})}_{-CR^{'}(\xi_{i})},\\
+i=m,n
 \label{cipped optimization variable}
 \end{IEEEeqnarray}
-It is obviously the dual variables in 2-D solver have the same update rule as that of 1-D solver.
-Based on (\ref{gain work set selection2}), assume the $i$th and $j$th dual variable pair are chosen, the gain of 2-D solver objective function can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{ij}=-\frac{1}{2}[\sigma_{i}^{2}\mathbf{K}^{r}_{ii}+\sigma_{j}^{2}\mathbf{K}^{r}_{jj}+2\sigma_{i}\sigma_{j}\mathbf{K}^{r}_{ij}]+\Phi^{r}_{i}\sigma_{i}+\Phi^{r}_{j}\sigma_{j}\\
--\epsilon(|\lambda^{new\quad clipped}_{i}|-|\lambda_{i}|+|\lambda^{new\quad clipped}_{j}|-|\lambda_{j}|),
+Based on (\ref{gain work set selection2}),  the gain of 2-D solver objective function can be written as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta^{r}_{mn}=-\frac{1}{2}[\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\sigma_{n}^{2}\Re{(\mathbf{K})}_{nn}+2\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn}]+\Re{(\Phi)}_{m}\sigma_{m}+\Re{(\Phi)}_{n}\sigma_{n}\\
+-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|+|\lambda^{new}_{n}|-|\lambda_{n}|),
 \label{gain of 2-D objective function1}
 \end{IEEEeqnarray}
-recall the gain of objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
+assume the $i$th and $j$th optimization variables are chosen, the optimization variables in 2-D solver have the same update rule as that of 1-D solver, that is 
+\begin{equation}
+[i,j]=\arg\max_{m,n=1,2,\ldots, N_{r}}\bigtriangledown \theta_{m,n}^{r}.
+\label{dual optimization variables}
+\end{equation}
+Recall the gain of objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
  \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-where $\bigtriangledown \Theta^{r}_{i}$, $\bigtriangledown \Theta^{r}_{j}$ denote gains of 1-D solver with $i$th and $j$th dual variable pairs are chosen. 
+where $\bigtriangledown \theta^{r}_{i}$, $\bigtriangledown \theta^{r}_{j}$ denote gains of 1-D solver with $m$th and $n$th dual variable pairs are chosen. 
 \subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}

### 2015-10-11 SVR for large MIMO/real SVR matlab/MMSE.m

@@ -2,9 +2,8 @@ function [  symOut,   MSE] = MMSE(pH,  y, SNRd, symbolContellation, Nr, Nt, M )
 %MMSE algorithm
 %Output: symOut, and mean square error
 G=zeros(Nt,Nr);
-symOut=zeros(Nt,1);
-I=eye(Nt,Nt);
-G=(inv(pH'*pH+SNRd^(-1)*I))*pH';
+I=eye(Nt);
+G=(I/(pH'*pH+SNRd^(-1)*I))*pH';
 symOut=G*y;
 MSE=norm(y-pH*symOut);
 %% rounding 

### 2015-10-11 SVR for large MIMO/real SVR matlab/Partial_MIC_recursive.m

@@ -1,0 +1,141 @@
+function [ symOut ] = Partial_MIC_recursive( y, H, symOut_total, list, H1, symOut_prev, SNRd, M, pav, stage, maxStage, symConstell, tol)
+%UNTITLED8 Summary of this function goes here
+%   Detailed explanation goes here
+%Multistage Interference Cancellation (MIC) recursive algorithm
+%   Detailed explanation goes here
+
+Nt=length(H(1,:)); %number of receive antennas
+% Nt=length(H(:,1));  %number of transmit antennas
+I=eye(Nt);
+%% IC
+if(stage~=1)
+y=y-H1*symOut_prev;
+end
+%% MMSE
+symOut_tmp=(I/(H'*H+SNRd^(-1)*I))*H'*y;
+[symOut_tmp1]=Rectangular_QAM_slicer(symOut_tmp,M, pav);
+%% check reliability
+[W]=weightCal(symOut_tmp, symOut_tmp1, tol, pav, M);
+%% update H and symOut_total
+count1=1;
+symOut_un=zeros(length(symOut_total),1);
+H_tmp=[];
+list_tmp=[];
+symOut_current=[];
+H1=[];
+for count=1:Nt
+    if(W(count)==1)
+        H1=[H1,H(:,count)];
+%         H(:,count)=[];
+        symOut_total(list(count))=symOut_tmp1(count);
+        symOut_current=[symOut_current; symOut_tmp1(count)];
+%         list(count)=[];
+        count1=count1+1;
+    else
+    symOut_un(list(count))=symOut_tmp1(count);
+    H_tmp=[H_tmp,H(:,count)];
+    list_tmp=[list_tmp, list(count)];
+    end
+end
+
+% maxStage=4;
+%% First stage estimation by MMSE
+% if(Nstage==0)
+% symOut_current=zeros(Nt,1);
+% if(stage==1)
+% INV=(I/(H'*H+SNRd^(-1)*I));
+% G=INV*H';
+% symOut_current=G*y;
+% [symOut_current]=Rectangular_QAM_slicer(symOut_current, M, pav);
+% symOut_prev=symOut_current;
+% end
+
+
+if(stage==maxStage)
+    if(~isempty(list))
+        for count=1:length(list)
+    symOut_total(list(count))=symOut_un(list(count));
+        end
+    end
+    symOut=symOut_total;
+    return
[…]

### 2015-10-11 SVR for large MIMO/real SVR matlab/commynicationLinePIC.m

@@ -1,0 +1,140 @@
+close all
+clear all
+tic
+% cd('/home/tchen44/Documents/spheredecodingtest/4X4')
+%% Signal Modulation and MIMO Channel modeling %% 
+M =4;         %size of constellation
+Nt=32;         %number of transmit antennas
+Nr=32;         %number of receive antennas
+x=6;            %diversity gain that required
+SNR=[18];       %signal to noise ratio per bit in dB
+SNRd=10.^(SNR.*0.1);   %SNR in dicimal
+noiseV=1./SNRd;   %noise variance of AWGN 
+BER=zeros(length(SNR),1);         %bit error rate
+% numFlop=zeros(length(SNR),1);    %complexity of the algorithm
+SER1=zeros(length(SNR),1);  %symbol error rate of MIC
+SER2=zeros(length(SNR),1); %symbol error rate of MMSE-OSIC
+% symNum=1e3;   %the number of symbol
+% symMap=[11 10 14 15 9 8 12 13 1 0 4 5 3 2 6 7];    %symbol map
+pav=1/Nt;  %average symbol power
+[symConstell]=symbolConstellation( M, pav );
+% dataInMatrix = reshape(dataIn, [], 2); % Reshape data into binary 4-tuples
+% dataSymbolsIn = bi2de(dataInMatrix);                 % Convert to integers
+% dataMod = qammod(dataSymbolsIn, M);
+% channelInput = reshape(dataMod, [4, length(dataMod)/4])';    %split data stream into 4 channel
+% hMod = comm.RectangularQAMModulator('BitInput', true, ...
+%         'ModulationOrder', M, 'NormalizationMethod', 'Average power',...
+%  'SymbolMapping','Custom','CustomSymbolMapping',symMap);   %generate a QAM modulation object 
+%     hDmod=comm.RectangularQAMDemodulator('BitOutput',true,...
+%         'ModulationOrder',M,'NormalizationMethod','Average power',...
+%     'SymbolMapping','Custom','CustomSymbolMapping',symMap); %generate a QAM demodulation object
+
+%      channelInput = reshape(dataMod, [],Nt);    %split data stream into 4 channel
[…]

### 2015-10-12 Report Aug 5 2015/Report Aug 2015.tex
Report revised stopping cirteria

@@
 
+In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
+Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}$ are defined as  
+\begin{IEEEeqnarray}[\relax]{l}
+\label{definition of slack variable1}
+\xi_{i}=\max(0, \mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
+\label{definition of slack variable2}
+\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon)
+\end{IEEEeqnarray} 
+Because the distance of the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
+That is $\xi_{i}\hat{\xi}_{i}=0$.
 \subsection{Cost Function}\label{cost function}
@@
 \end{IEEEeqnarray}
+Based on the definitions of slack variables in (\ref{definition of slack variable1}) an (\ref{definition of slack variable2}), only when there is a outlier exists, $\xi_{i}$ or $\hat{\xi}_{i}$ can be non zero, that is
+\begin{equation}
+\xi_{i}(\hat{\xi}_{i})=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
+\label{definition of slack variable3}
+\end{equation} 
+because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig.
+\ref{epsilon-SVR}.
+Therefore at most one of $(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})$  and $(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})$ can be zero.
+In order to satisfy the KKT complementary conditions in (\ref{KKT complimentary}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
 
@@
 (C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
-\alpha(\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})=0, i=1,2,\ldots, L\\
-\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})})=0, i=1,2,\ldots, L\\
+\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, L\\
+\hat{\alpha}_{i}(-\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, L\\
 \end{array}\right.
@@
 
-Another idea for work set selection is to choose the dual variables whose update can provide the maximum improvements to dual objective function. That is
+Another idea for work set selection is to choose the dual variables whose update can provide the maximum improvement to dual objective function. The improvement of the sub dual objective function is
 \begin{equation}
@@
 \end{equation} 
-where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\mathbf{a}_{S}$ is the update of $\mathbf{a}^{new}_{S}$.
+where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\hat{\Delta}_{S}=\hat{\mathbf{a}}_{S}^{new}-\hat{\mathbf{a}}_{S}$, $\mathbf{a}^{new}_{S}$ and $\hat{\mathbf{a}}^{new}_{S}$ are the updates of $\mathbf{a}_{S}$ and $\hat{\mathbf{a}}_{S}$.
 $\bigtriangledown \theta_{S}^{r}$ in (\ref{maximum gain work set selection}),  based on (\ref{subset optimization}), can be written as
@@
 \nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathfrak{n}_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta})_{S}]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})\\
--\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}](\Delta_{S}-\hat{\Delta}_{S})\\
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\\\nonumber\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+\{\Re{(\mathbf{y}^{T}_{S})}-[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\\
+\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}]\}(\Delta_{S}-\hat{\Delta}_{S})
 -\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S}),
@@
 \end{IEEEeqnarray} 
-Notice in (\ref{gain work set selection1}), we use 
+where we have 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 where $\Re{(\mathbf{K})}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns corresponding to the work set $S$.
-Then we define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Re{(\Phi)}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Im{(\Phi)}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$
-Thus (\ref{gain work set selection1}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta})^{T}_{S}\Re{(\mathbf{K})}_{SS}(\Delta-\hat{\Delta})_{S}+(\Re{(\Phi)}_{S})^{T}(\Delta-\hat{\Delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\Delta+\hat{\Delta})_{S}
+Therefore, (\ref{gain work set selection1}) can be rewritten as
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}]
+(\Delta_{S}-\hat{\Delta}_{S})
+-\epsilon\mathbf{e}^{T}_{S}\\
+(\Delta_{S}+\hat{\Delta}_{S}),
+\label{gain of work set selection1 inter}
+\end{IEEEeqnarray}
+define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Re{(\Phi)}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Im{(\Phi)}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$, let $\Phi_{S}$ denote the vector that consists of the components in $\Phi$ that corresponding to $S$.
+Thus (\ref{gain of work set selection1 inter}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta})^{T}_{S}\Re{(\mathbf{K})}_{SS}(\Delta-\hat{\Delta})_{S}+(\Re{(\Phi)}_{S})^{T}(\Delta-\hat{\Delta})_{S}-\epsilon\mathbf{e}^{T}_{S}\\
+(\Delta+\hat{\Delta})_{S}
 \label{gain work set selection2}
@@
 \label{KKT complementary1}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
+(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
 \label{KKT complementary2}
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
+(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
 \label{KKT complementary3}
-\alpha(\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})=0, i=1,2,\ldots, L\\
+\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
 \label{KKT complementary4}
-\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})})=0, i=1,2,\ldots, L\\\nonumber
+\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, N_{r}
 \label{complementary KKT condition2}
 \end{IEEEeqnarray}
-notice that in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}$ and  $\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})}$ can be non zero, therefore in order to satisfy the equalities, at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$, because $0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(C\tilde{R}(\hat{\xi}_{i}^{r}))$ and $\alpha_{i}\hat{\alpha}_{i}=0$, there is at least one of $C\tilde{R}(\xi_{i}^{r})-\alpha_{i}$ and $C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i}$ in (\ref{KKT complementary1}) and (\ref{KKT complementary2}) is non zero, in order to satisfy the equalities, there is at least one of $\xi_{i}$ and $\hat{\xi}_{i}$ need to be zero, that is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
-Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.
+Recall the discussions of slack variables by (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}) in section \ref{section lagrange duality}.
+we have $\xi^{r}_{i}\hat{\xi}^{r}_{i}=0$.
+similar to the definitions in (\ref{definition of slack variable3}), we have
+\begin{equation}
+\xi^{r}_{i}(\hat{\xi}_{i}^{r})=|\Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}|_{\epsilon},
+\label{definition of complex slack variables}
+\end{equation} 
+ therefore in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})$ and  $(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})$ can be non zero, therefore in order to satisfy equalities (\ref{KKT complementary3}) and (\ref{KKT complementary4}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
+
+ Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is changed to the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.
 
@@
 \end{IEEEeqnarray} 
-In 1-D solver, $|S|=1$, the sub dual objective function corresponding to $\lambda_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
+In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to $\lambda_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray} 
-
- The update of $\alpha_{1}$ or $\hat{\alpha}_{1}$ is completed by clipping
+ The update of $\lambda_{m}$ is completed by clipping
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-based on (\ref{gain work set selection lambda}), The maximum gain of objective function respect to the $m$th optimization variable $\lambda_{m}$ is 
+based on (\ref{gain work set selection lambda}), The maximal gain of objective function with respect to the $m$th optimization variable $\lambda_{m}$ is 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-In 1-D searching procedure, the optimization variable whose update has the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, that is 
-\begin{equation}
-k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r},
+In 1-D searching procedure, the optimization variable whose update can achieve the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, based on the this principle
+\begin{equation}
+k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r}.
 \label{1-D direction}
 \end{equation}
+Notice in (\ref{partial optimization function 1-D lambda}), $sgn(\tilde{\lambda}^{new}_{m})$ is unknown before $\lambda_{m}$ is updated, therefore two conditions $sgn(\tilde{\lambda}^{new}_{m})=1$ and $sgn(\tilde{\lambda}^{new}_{m})=-1$ are considered.
+The final decision of $sgn(\tilde{\lambda}_{m}^{new})$ is made by comparing the corresponding gains of the sub objective functions in (\ref{gain of 1-D objective function}).
 \subsection{Double Direction Solver}\label{double direction solver}
@@
 \end{equation}
-Recall the gain of objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
- \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta^{r}_{ij}=\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}-\sigma_{i}\sigma_{j}\mathbf{K}^{r}_{ij},
+ modify (\ref{gain of 2-D objective function1}), we have 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta^{r}_{mn}=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)+\sigma_{n}[-\frac{1}{2}\sigma_{n}\Re{(\mathbf{K})}_{nn}+\Re{(\Phi)}_{n}]-\epsilon(|\lambda^{new}_{n}|-|\lambda_{n}|)\\
+-\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn},
+\end{IEEEeqnarray}
+
+Similar to single direction solver, notice in (\ref{update lambda1}) and (\ref{update lambda2}), $sgn(\tilde{\lambda}^{new}_{m})$ and $sgn(\tilde{\lambda}^{new}_{n})$ are unknown before $\lambda_{m}$ and $\lambda_{n}$ are updated, therefore four conditions are considered
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=1\\
+\nonumber
+sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=-1\\
+\nonumber
+sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=1\\
+\nonumber
+sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=-1
+\label{four conditions of sign}
+\end{IEEEeqnarray} 
+The final decisions of $sgn(\tilde{\lambda}_{m}^{new})$ and $sgn(\tilde{\lambda}_{n}^{new})$ are made by comparing the corresponding possible gains of the sub objective functions in (\ref{gain of 2-D objective function1}).
+
+Recall the gain of dual objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
+ \begin{IEEEeqnarray}[\relax]{l}
+\bigtriangledown \theta^{r}_{ij}=\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}-\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij},
 \label{gain of 2-D objective function1}
@@
 where $\bigtriangledown \theta^{r}_{i}$, $\bigtriangledown \theta^{r}_{j}$ denote gains of 1-D solver with $m$th and $n$th dual variable pairs are chosen. 
-\subsection{Approximation to Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
-From (\ref{gain of 2-D objective function1}), it is obviously that the gain of 2-D solver is a summation of the gain of 2 independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\mathbf{K}^{r}_{ij}$.
-
-Obviously optimal 2-D coordinate combination ($i, j$) can be determined by comparing the gains of all the possibilities exhaustively, which requires $O(n^{2})$ times of searching.
-Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D solution by 1-D search approach, we will prove in large MIMO scenario, when $N_{t}$ is sufficient large, with channel hardening become effective, this approximation is very efficient.
+\subsection{Approximation of Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
+From (\ref{gain of 2-D objective function1}), we can observe that the gain of 2-D solver is a summation of the gain of 2 independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}$.
+
+Obviously optimal 2-D work set $[i,j]$ can be determined by brute-force searching manner, which requires $O(n^{2})$ searching times.
+Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D searching strategy by the combinations of optimal 1-D searching approach, we will prove in the large MIMO systems, when $N_{t}$ is sufficient large, this approximation is very effective.
 Here we propose two kinds of 1-D approximate searching strategy:
-\subsubsection{ 1-D searching without damping}
-do one round 1-D searching and calculate all the 1-D gain based on (\ref{gain of 1-D objective function}), then choose the coordinates with first and second largest 1-D gain as the candidates, then update the two candidates by 2-D solver as shown in (\ref{update lambda1}) and (\ref{update lambda2})
-\subsubsection{ 1-D searching with damping}
-do two rounds 1-D searchings, in the first round find optimization variable $i$ that can maximize 1-D gain, then in the second round, find $j$th optimization variable with the value of $i$th coordinate updated.
-
-From (\ref{gain of 2-D objective function1}), it can be easily interpreted the efficient of 1-D approximation approach is majorly determined by the approximation ratio $\frac{\sigma_{i}\sigma_{j}\mathbf{K}^{r}_{ij}}{\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}}$, hence we provide theoretical analyse from the view of channel hardening phenomenon.
-Prior the theoretical analyse, we first investigate some mathematical properties of channel hardening (to be completed).
-
-For 1-D solver the gradient of (\ref{partial optimization function 1-D lambda}) with respect to $\lambda$ can be written as
-\begin{equation}
-\lambda_{1}^{new}=\lambda_{1}+\frac{\Phi_{1}-sgn(\lambda_{1}^{new})\epsilon}{\mathbf{K}^{r}_{11}},
-\label{gradient lambda}
-\end{equation}
-In the update process the $sgn(\lambda^{new})$ is unknown at current step, therefore, we need to consider both the case $sgn(\lambda^{new})=-1 $ or $1$ and choose the one with the larger objective function gain $\bigtriangledown \theta^{r}_{S}$.
+\subsubsection{ One-shot 1-D Searching}
+do one round 1-D searching and calculate all the 1-D gain based on (\ref{gain of 1-D objective function}), then choose the two optimization variables indexed by $i$ and $j$, whose update can achieve the first and the second largest gain of the sub dual objective functions.
+\subsubsection{ Sequential 1-D Searching}
+do two rounds 1-D searchings, in the first round find optimization variable indexed by $i$ whose update can achieve the maximal 1-D gain of the sub dual objective functions, then update the $i$th optimization variable.
+In the second round, find $j$th optimization variable whose update can achieve the maximal 1-D gain of the sub dual objective functions.
+
+ The effectiveness of 1-D approximation strategies are majorly determined by the ratio $\frac{\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}}{\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}}$.
+Hence we provide theoretical analyses based on the view of channel hardening phenomenon.
+It can be proved that in the large MIMO systems, the correlation term is ignorable comparing to 1-D gains of the sub objective function.
+Prior to the theoretical analyse, we first investigate some mathematical properties of channel hardening (to be completed).
 
@@
 \end{IEEEeqnarray}
-As we explained in section \ref{risk functional}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
-\begin{equation}
-R(\xi)=\frac{1}{2}\xi^{2},
+As we explained in section \ref{cost function}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
+\begin{equation}
+R(u)=\frac{1}{2}u^{2},
 \label{risk function1}
@@
 \begin{equation}
-\tilde{R}(\xi)=R(\xi)-\xi R{'}(\xi)=-\frac{1}{2}\xi^{2},
+\tilde{R}(u)=R(u)-u R{'}(u)=-\frac{1}{2}u^{2},
 \label{risk function2}
 \end{equation}
-In $\epsilon$-SVR, the objective to employ slack variables $\xi$ is to deal with the outliers that outside $\epsilon$ tube to compensate the influence from noise.
-Therefore 
-\begin{IEEEeqnarray}[\relax]{l}
-\xi^{r}_{i}=Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})-\epsilon\\
-\hat{\xi}^{r}_{i}=Re(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})-Re(\mathbf{y}_{i})-\epsilon
-\label{outlier1}
-\end{IEEEeqnarray}
-Because $\xi^{r}\hat{\xi}^{r}=0$ (estimation can only exceed $\epsilon$ tube in one direction), therefore there is only one of $\xi$ and $\hat{\xi}$ need to be considered, thus 
-\begin{IEEEeqnarray}[\relax]{l}
-\xi^{r}_{i}(\hat{\xi}^{r}_{i})=\max(0, |Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon)\\
-\xi^{i}_{i}(\hat{\xi}^{i}_{i})=\max(0, |Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|-\epsilon)\\
-\xi\hat{\xi}=0,
+In $\epsilon$-SVR, the objective to exploit slack variables $\xi^{r}_{i}$ and $\hat{\xi}_{i}^{r}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
+Therefore in $\epsilon$-SVR, $\xi^{r}_{i}$ and $\hat{\xi}^{r}$ are defined as  
+\begin{IEEEeqnarray}[\relax]{l}
+\xi^{r}_{i}=\max(0, \Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\epsilon)\\
+\hat{\xi}^{r}_{i}=\max(0, \Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\Re{(\mathbf{y}_{i})}-\epsilon)
 \label{outlier2}
 \end{IEEEeqnarray} 
+Because the distance between the estimations $\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}$ and the observations $\Re{(\mathbf{y}_{i})}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi^{r}_{i}$ and $\hat{\xi}^{r}_{i}$ can be non zero.
+That is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
 Therefore the risk function can be rewritten as 
 \begin{IEEEeqnarray}[\relax]{l}
-R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}(|Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|)^{2}_{\epsilon}\\
+R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}|Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|_{\epsilon}^{2}\\
 \label{simple risk function1}
-R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}(|Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|)^{2}_{\epsilon}
+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}|Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|^{2}_{\epsilon}
 \label{simple risk function2}
 \end{IEEEeqnarray}
-where $()_{\epsilon}$ denotes $\epsilon$ insensitive function as we mention in section \ref{risk functional}. Based on (\ref{complex duality regression function}), we have 
+where $|\cdot|_{\epsilon}$ denotes $\epsilon$ insensitive function as mentioned in section \ref{cost function}. Recall (\ref{complex duality regression function}),
+\begin{IEEEeqnarray}[\relax]{l}
+<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}
+=\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}),
+\end{IEEEeqnarray}
+ we obtain 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-we define two intermediate variables $\Phi$ and $\Psi$
+Two intermediate variables $\Phi$ and $\Psi$ are defined
 \begin{IEEEeqnarray}[\relax]{l}

### 2015-10-14 Report Aug 5 2015/Report Aug 2015.tex
Report for CSVR revised

@@
   One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment.
-The most promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} long-term evolution (LTE)\cite{3GLTE}.
-The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve bandwidth efficiency) and diversity gain (better reliability of communication link) is obtained by exploiting the spatial domain.
+The promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} and long-term evolution (LTE)\cite{3GLTE}.
+The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve spectrum efficiency) and diversity gain (better reliability of communication link) are obtained by exploiting the spatial domain.
 Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously.
-This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness both to unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
-
-  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving end.
-The uplink Detector is one of the key components in large MIMO systems.
+This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
+
+  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving ends.
+The uplink detector is one of the key components in a large MIMO system.
 With orders magnitude more antennas at the BS, benefits and challenges coexist in designing of detection algorithms for the uplink communication of large MIMO systems.
-On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexity of the algorithm becomes crucial to make the system practical.
+On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexities of the algorithms become crucial to make the system practical.
 
 Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams.
-However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with number of transmitted antennas, which is prohibitive for practical applications.
+However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with the number of transmitted antennas, which is prohibitive for practical applications.
 
@@
 The first shortage is SD has various complexities under different signal to noise ratios (SNR), while a constant processing data rate is required for hardware.
-The second shortage is SD's complexity still has a lower bound for complexity that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
-The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different value of SNR.
+The second shortage is the complexity of SD still has a lower bound that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
+The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different values of SNR.
 The FCSD inherits the principle of list based searching algorithms, which first generate a list of candidate symbol vectors and then the best candidate is chosen as the solution.
-The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC(sel-MMSE-OSIC)\cite{radji2009interference}.
+The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC (sel-MMSE-OSIC)\cite{radji2009interference}.
 However, all these list based searching algorithms have the same shortage - their complexities increase exponentially with the number of transmit antennas and the order of modulation scheme\cite{radji2009interference}.
@@
 %Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
-Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance.
+Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of metaheuristic based detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance.
 such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
-Tabu search based algorithms which have superior performance compared to LAS detectors because local minima can be avoided (e.g.
+Tabu search based algorithms which have superior performances compared to LAS detectors because of the efficient local minima exit strategy (e.g.
 Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g.
 Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g.
-Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) and Lattice Reduction (LR) aided algorithms\cite{zhou2013element}.
+Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) .
+Moreover, element based Lattice Reduction (LR) aided algorithms were also proposed to  large MIMO systems.\cite{zhou2013element}.
 
@@
 Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
-Moreover, the kernel based methods\cite{scholkopf2002learning} solve nonlinear learning tasks by mapping input data sets into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
+Moreover, the kernel based methods\cite{scholkopf2002learning} were proposed which solve nonlinear learning tasks by mapping input data samples into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
 This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS).
@@
 
-Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual optimization problem, which can be solved by Quadratic Programming (QP).
-Sequential Minimal Optimization (SMO) algorithm was proposed as a fast algorithm to solve this QP problem by decomposing the it into sub QP problems and solving them analytically\cite{platt1999fast}.
-Therefore, the computational intensive numerical method can be avoided.
-A more general method is decomposition solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets W and N, W is the work set and N contains the remaining optimization variables.
-In each iteration, only the optimization variables in the work set is optimized while keeping other variables fixed.
-The SMO algorithm is an extreme case of decomposition solver.
-An important issue of decomposition solver is the choice of the work set.
-One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring final converge\cite{osuna1997improved}.
-Because of the linear constraint inducted by offset, the SMO algorithm restricts the size of the work set to 2.
-In\cite{steinwart2011training}, a method to train SVM without offset was proposed, with the comparable performance to the SVM with offset.
+Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual form, which can be solved by Quadratic Programming (QP).
+Decomposition methods were proposed to solve this QP problem by decomposing it into sub QP problems and solving them iteratively\cite{platt1999fast}.
+Therefore, the computational intensive numerical methods can be avoided.
+Decomposition is performed by sub set selection solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets S and N, S is the work set and N contains the remaining optimization variables.
+In each iteration, only the optimization variables in the work set is updated while keeping other optimization variables fixed.
+The Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} is an extreme case of the decomposition solvers.
+An important issue of the sub set selection solvers is the selection of the work set.
+One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring the final converge\cite{osuna1997improved}.
+The SMO algorithm restricts the size of the work set to two.
+A method to train SVM without offset was proposed In\cite{steinwart2011training}, with the comparable performance to the SVM with offset.
 A set of sequential single variable work set selection strategies, which require $O(n)$ searching time are proposed.
 The optimal double variable work set selection strategy, which performs exhaustively searching, however, requires $O(n^{2})$ searching time.
-The authors demonstrate that with the combination of two proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.
+The authors demonstrate that with the combination of two different proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.
 
@@
 Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain.
-The results in\cite{bouboulis2013complex} demonstrate better performances as well as reduced complexity comparing to simply split learning task into two real case by real kernel.
-Based on this work, we derive of a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR).
+The results in\cite{bouboulis2013complex} demonstrate the better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernels.
+Based on this work, we derive a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR).
 The detector can work in two parallel real SVR channels which can be solved independently.
 Moreover, only the real part of kernel matrix is needed in both channels.
-This means a large amount of computation can be reduced.
+This means a large amount of computation cost saving can be achieved.
 Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
-is constructed without offset, Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed.
+is constructed without offset, Therefore, for each real SVR without offset, 
+%in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed.
 By this strategy, two variables can be updated at each iteration, with much smaller searching time.
+Two types of combined single optimization variable selection strategy are proposed based on the work in \cite{steinwart2011training}.
+The proposed combined single optimization variable selection strategy can approximate optimal double optimization variable selection strategy.
+The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
 
@@
 \subsection{Regression Model}
-Suppose we are given training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
+Suppose we are given a training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
 $y_{i}$ denotes output.
-Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Lambda}$, $\Lambda \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$).
+Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Omega}$, $\Omega \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$, $\Omega=V$).
 The regression model (either linear or non-linear) is given by
 \begin{equation}
-y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1\cdots L 
+y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1,2,\ldots, L
 \label{equation1}
@@
 \end{IEEEeqnarray}
-In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the area between two dash line is called $\epsilon$ tube.
-Only those data samples located outside $\epsilon$ tube contribute to cost.
-Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with noise of input data samples, $R(u)$ denotes risk function, the simplest risk function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}.
-For example if the noise is Gaussian noise, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$.
+In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the solid line represents the estimation of the input-output relation, the area between two dash lines ($\epsilon$-bound) is called $\epsilon$-tube.
+Only those data samples located outside $\epsilon$-tube contribute to the estimation error.
+Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with additive noise of observations, $R(u)$ denotes the cost function.
+The simplest cost function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}.
+For example if the noise is Gaussian distributed, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$.
 The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.
@@
 In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
-Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}$ are defined as  
+Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
 \begin{IEEEeqnarray}[\relax]{l}
 \label{definition of slack variable1}
-\xi_{i}=\max(0, \mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
+\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
 \label{definition of slack variable2}
-\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon)
-\end{IEEEeqnarray} 
-Because the distance of the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
+\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon).
+\end{IEEEeqnarray} 
+Because the distance between the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
 That is $\xi_{i}\hat{\xi}_{i}=0$.
@@
 \begin{IEEEeqnarray}[\relax]{l}
-\sum_{i=1}^{L}log(Pr(y_{i}-f(\mathbf{x}_{i}))),
+\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
 \label{cost function2}
 \end{IEEEeqnarray}
-maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}log(Pr(y_{i}-f(\mathbf{x}_{i})))$
+maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i})))$, therefore (\ref{cost function1}) is equivalent to 
+\begin{equation}
+\min_{f}-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
+\label{cost function3}
+\end{equation}
 Let $c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))$ denotes the $i$th cost function, which is defined as  
 \begin{IEEEeqnarray}[\relax]{l}
-c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-log(P(y_{i}-f(\mathbf{x}_{i}))).
+c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-\log(P(y_{i}-f(\mathbf{x}_{i}))).
 \label{cost function3}
 \end{IEEEeqnarray}
-Thus (\ref{cost function1}) can be rewritten as 
+Thus (\ref{cost function3}) can be rewritten as 
 \begin{equation}
@@
 \begin{equation}
-\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),
+\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),
 \label{final cost function}
@@
 \begin{equation}
-\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))
-\end{equation}  
-the cost function term is determined according to noise distribution.  
+\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))
+\end{equation}  
+the cost function term is determined according to the distribution of noise.  
 %where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as
@@
 According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier.
-The Lagrange function is given by.
+The Lagrange function is given by
 \begin{IEEEeqnarray}[\relax]{l}
@@
 
-The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
+The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the primal constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
 Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.
@@
 \begin{equation}
-L(\mathbf{w}, a_{i})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),
+L(\mathbf{w}, \mathbf{a})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),
 \label{orginal Lagrange}
 \end{equation}
-where $a_{i}$ denote Lagrange multipliers.
- Based on Theorem 6.21 in \cite{scholkopf2002learning}, For a variable set $[\bar{\mathbf{w}}, \bar{a}_{i}]$, $\bar{\mathbf{w}}$ is the solution to (\ref{constraint optimization problem}) only when the following inequalities are satisfied
- \begin{equation}
- L(\mathbf{w}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, a_{i})
+where $\mathbf{a}=[a_{1},a_{2},\ldots, a_{L}]^{T}$ denotes the vector consist of Lagrange multipliers.
+ Based on Theorem 6.21 in \cite{scholkopf2002learning}, a variable pair $[\bar{\mathbf{w}}, \bar{\mathbf{a}}]$ is the solution to (\ref{constraint optimization problem}) if and only if the following inequalities are satisfied
+ \begin{equation}
+ L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
  \label{KKT inequalities}
  \end{equation}
-This inequalities yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
+This inequalities (also called saddle point conditions) yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
 \begin{IEEEeqnarray}[\relax]{l}
 \label{original KKT condition1}
-\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, a_{i})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\
+\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, \mathbf{a})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\
 \label{original KKT condition2}
-\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{a}_{i})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\
+\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\
 \label{original KKT condition3}
@@
 \label{partial1}
-\frac{\partial L}{\partial \mathbf{w}}=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\
+\partial_{\mathbf{w}} L=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\
 \label{partial2}
-\frac{\partial L}{\partial \xi_{i}}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\
+\partial_{\xi_{i}}L=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\
 \label{parial3}
-\frac{\partial L}{\partial \hat{\xi}_{i}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\
+\partial_{\hat{\xi}_{i}}L=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\
 \label{partial4}
-\frac{\partial L}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber
+\partial_{b}L=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber
 \end{IEEEeqnarray}
@@
 \nonumber
-+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}(y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\\
-\sum_{i=1}^{L}\hat{\alpha}_{i}(\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})
++(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}[y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}]+\\
+\sum_{i=1}^{L}\hat{\alpha}_{i}[\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i}]
 \label{lagrange duality1 inter}
@@
 \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i})]\\
-\nonumber
-+\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
-s.t.\left\{\begin{array}{l}
-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
-0<\alpha<C\tilde{R}^{'}(\alpha)\\
-0<\hat{\alpha}<C\tilde{R}^{'}(\hat{\alpha})\\
-\end{array}\right.
++\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
 \label{dual objective function1}
@@
 In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold.
-Condition (\ref{original KKT condition2}) is satisfied when the maximum of $L(\bar{\mathbf{w}}, a_{i})$ is found, notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\bar{\mathbf{w}}, a_{i})$ in (\ref{KKT inequalities}), thus yielding the dual optimization problem, which is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}}\quad \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i}))\\
+A $\mathbf{w}$ that satisfies the conditions in (\ref{original KKT condition2}) is in the feasible region defined by inequality constraints as mentioned (\ref{constraint optimization problem}).
+In $\epsilon$-SVR, this condition is satisfied by making use of the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ defined in (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}).
+Define that $\tilde{\mathbf{w}}$ is in the feasible region and satisfies the conditions in (\ref{original KKT condition1}), notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\tilde{\mathbf{w}}, \mathbf{a})$, thus yielding the dual optimization problem, which is given by
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\max_{\mathbf{a}}L(\tilde{\mathbf{w}},\mathbf{a})\equiv\max_{\alpha_{i}, \hat{\alpha}_{i}}\quad \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i}))\\
 +\sum_{i=i}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
@@
 \end{IEEEeqnarray}
-Define $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{L}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{L}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{L}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{L}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0, $\mathbf{R}_{\xi}=[\tilde{R}(\xi_{1}), \tilde{R}(\xi_{2}), \ldots, \tilde{R}(\xi_{L})]^{T}$, $\mathbf{R}_{\hat{\xi}}=[\tilde{R}(\hat{\xi}_{1}), \tilde{R}(\hat{\xi}_{2}), \ldots, \tilde{R}(\hat{\xi}_{L})]^{T}$, $[\mathbf{K}]_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes a component of data kernel matrix at $i$th row and $j$th column.
+Define $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{L}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{L}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{L}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{L}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0, $\mathbf{R}_{\xi}=[\tilde{R}(\xi_{1}), \tilde{R}(\xi_{2}), \ldots, \tilde{R}(\xi_{L})]^{T}$, $\mathbf{R}_{\hat{\xi}}=[\tilde{R}(\hat{\xi}_{1}), \tilde{R}(\hat{\xi}_{2}), \ldots, \tilde{R}(\hat{\xi}_{L})]^{T}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes a component of data kernel matrix at $i$th row and $j$th column.
 An alternative vector form of (\ref{dual optimization function2}) can be written as
@@
 
-Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor how close the solution is to the global optimum.
+Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor the proximity of the current solution and the optimal solution.
 Thus it can be used as a stopping criterion.
@@
 \alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L
+\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
+(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
 \end{array}\right. 
@@
 \begin{equation}
-\xi_{i}(\hat{\xi}_{i})=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
+\xi_{i} or \hat{\xi}_{i}=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
 \label{definition of slack variable3}
 \end{equation} 
-because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig.
+because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $y_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig.
 \ref{epsilon-SVR}.
@@
 In order to satisfy the KKT complementary conditions in (\ref{KKT complimentary}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
+
+Therefore the complete KKT complementary conditions of $\epsilon$-SVR is given by
+\begin{IEEEeqnarray}[\relax]{l}
+\left\{\begin{array}{cc}
+\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
+\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
+(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
+\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots L
+\end{array}\right. 
+\label{complete KKT complimentary}
+\end{IEEEeqnarray}
 
@@
 \subsection{Complex Regression Model}
- Based on the discrete time model of the large MIMO uplink system of (\ref{discrete time MIMO system}), our regression model is set such that the training data samples at the detector are $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of matrix $\mathbf{H}$.
+ Based on the discrete time model of a large MIMO uplink system of (\ref{discrete time MIMO system}), our regression model is set such that the training data set at the detector are $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of matrix $\mathbf{H}$.
 This yields a regression task without offset $b$ in (\ref{equation1}) :
@@
  where $f_{true}()$ denotes the underlying true regression function, $n_{i}$ denotes discrete sample of additive noise.
-In this regression problem, received symbols $y_{i}$ are the output data, $\mathbf{h}_{i}$ are the input data samples, transmitted symbol vector $\mathbf{s}$ contains the regression coefficients.
-We employ complex support vector regression (CSVR) without offset term $b$, in order to deal with the complex large MIMO systems.
-As shown in section \ref{Introduce epsilon SVR}, As shown in (\ref{original KKT condition1}) the first KKT condition is satisfied by finding the saddle point $\bar{\mathbf{w}}$ by taking paritial derivatives of $L(\mathbf{w},a_{i})$ with respect to $\mathbf{w}$.
+In this regression problem, received symbols $y_{i}$ are the observations, $\mathbf{h}_{i}$ are the input data samples, transmitted symbol vector $\mathbf{s}$ contains the regression coefficients.
+We employ complex support vector regression (CSVR) without offset term $b$.
+As shown in (\ref{original KKT condition1}) the first KKT condition is satisfied by finding the saddle point $\bar{\mathbf{w}}$ by taking paritial derivatives of $L(\mathbf{w},a_{i})$ with respect to $\mathbf{w}$.
 Mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) are employed to calculate partial derivatives of Lagrangian function of CSVR in complex manner\cite{bouboulis2011extension}.
@@
 define complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $<,>_{\mathbb{H}}$ denotes the corresponding inner products in $\mathbb{H}$.
-Assume $\mathbf{x}$, $\mathbf{y}$, $\mathbf{z}$, $\mu$, $\chi$ $\in \mathbb{C}$, complex Hilbert space has the following properties
+Assume $\mathbf{x}, \mathbf{y},\mathbf{z}$ are complex vectors, $\mu$, $\chi$ $\in \mathbb{C}$, In general a complex Hilbert space $\mathbb{H}_{g}$ has the following properties
 \newtheorem{Lemma}{Lemma}
@@
 \begin{Property}
- $<\mathbf{x},\mathbf{y}>_{\mathbb{H}}=(<{\mathbf{y},\mathbf{x}}>_{\mathbb{H}})^{*}$
+ $<\mathbf{x},\mathbf{y}>_{\mathbb{H}_{g}}=(<{\mathbf{y},\mathbf{x}}>_{\mathbb{H}_{g}})^{*}$
 \label{CHSProperty1}
@@
 \begin{Property}
-$<\mu\mathbf{x}+\chi\mathbf{y},\mathbf{z}>_{\mathbb{H}}=\mu<\mathbf{x},\mathbf{z}>_{\mathbb{H}}+\chi<\mathbf{y},\mathbf{z}>_{\mathbb{H}}$
+$<\mu\mathbf{x}+\chi\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}=\mu<\mathbf{x},\mathbf{z}>_{\mathbb{H}_{g}}+\chi<\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}$
 \label{CHSProperty2}
@@
 \begin{Property}
-$<\mathbf{z}, \mu\mathbf{x}+\chi\mathbf{y}>_{\mathbb{H}}=\mu^{*}<\mathbf{z},\mathbf{x}>_{\mathbb{H}}+\chi^{*}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}}$
+$<\mathbf{z}, \mu\mathbf{x}+\chi\mathbf{y}>_{\mathbb{H}_{g}}=\mu^{*}<\mathbf{z},\mathbf{x}>_{\mathbb{H}_{g}}+\chi^{*}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}_{g}}$
 \label{CHSProperty3}
@@
 Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{V}$, define a real RKHS $\mathcal{H}$ that satisfy $<\mathbf{a}, \mathbf{b}>_{\mathcal{H}}=\mathbf{a}^{T}\mathbf{b}$.
-For the corresponding complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$,
+For the corresponding complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $\mathbf{m}, \mathbf{l}\in \mathbb{C}^{V}$,
 $<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$
@@
 \end{IEEEeqnarray}
-Because $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathbb{H}}=<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}=\mathbf{f}^{T}_{1}\cdot \mathbf{f}_{2}$ if $\mathbf{f}_{1}, \mathbf{f}_{2}\in \mathcal{H}$, thus (\ref{CHSProperty4 inter2}) can be rewritten as
+According to (\ref{CHSProperty4 inter2}), if $\mathbf{f}_{1}, \mathbf{f}_{2}\in \mathcal{H}$, we have  $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathbb{H}}=<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}$, furthermore because $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}=\mathbf{f}^{T}_{1}\mathbf{f}_{2}$, (\ref{CHSProperty4 inter2}) can be rewritten as
 \begin{IEEEeqnarray}[\relax]{l}
@@
 
-Therefore $<\mathbf{m},\mathbf{l}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$.
+Therefore $<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}$.
 \end{proof}
 Therefore we have $<\mathbf{h}_{i}, \mathbf{s}^{*}>_{\mathbb{H}}=\mathbf{h}_{i}\cdot \mathbf{s}$, 
-For sake of simplicity we define $\mathbf{s}^{*}=\mathbf{w}$.
-Based on the same principle in the real case presented in (\ref{Introduce epsilon SVR}), the general regularized risk function of large MIMO detection in complex RKHS $\mathbb{H}$ defined by $<\mathbf{m}, \mathbf{l}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}$ can be formulated as
+For sake of simplicity we define $\mathbf{w}=\mathbf{s}^{*}$.
+Based on the same principle in the real case presented in section \ref{Introduce epsilon SVR}, the primal optimization problem of large MIMO detection in complex RKHS $\mathbb{H}$ defined by $<\mathbf{m}, \mathbf{l}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}^{*}$ can be formulated as
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
- Where $\Re{(\cdot)}$ and $\Im{(\cdot)}$ denote real and imaginary part of a complex variable and inequality restrictions are set to real and imaginary part of the regression function separately.
+ Where $\Re{(\cdot)}$ and $\Im{(\cdot)}$ denote real and imaginary part of a complex variable and inequality constraints are set to real and imaginary part of the regression function separately.
 Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denote the kernel function, $\mathbf{K}=\Re{(\mathbf{K})}+\imath\Im{(\mathbf{K})}$, where $\Re{(\mathbf{K})}$ and $\Im{(\mathbf{K})}$ denote matrices of corresponding real and imaginary parts.
@@
 \end{equation}
-Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), the final form of Lagrange duality can be obtained
+Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), we have
 \begin{IEEEeqnarray}[\relax]{l}
@@
 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta=-\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}]+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})-\xi_{i}^{r}R^{'}(\xi^{r}_{i})\\\nonumber
+Then simplify (\ref{complex lagrange duality inter1}), we obtain
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+L\equiv\theta=-\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}]+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})-\xi_{i}^{r}R^{'}(\xi^{r}_{i})\\\nonumber
 +R(\hat{\xi}^{r}_{i})-\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})-\xi_{i}R^{'}(\xi_{i}^{i})+R(\hat{\xi}^{i}_{i})-\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]+\sum_{i=1}^{N_{r}}[\Re{(y_{i})}(\alpha_{i}-\hat{\alpha}_{i})+\Im{(y_{i})}(\beta_{i}-\hat{\beta}_{i})]-\\
@@
 \end{IEEEeqnarray}
-define $\tilde{R}(u)=R(u)-uR^{'}(u)$. Similar to (\ref{dual optimization function2}), The dual optimization problem of complex MIMO system is 
+define $\tilde{R}(u)=R(u)-uR^{'}(u)$. Similar to (\ref{dual optimization function2}), The dual optimization problem of a complex MIMO system is given by
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-Notice in (\ref{final complex lagrange duality}), there is no correlation term between $\alpha_{i}, \hat{\alpha}_{i}$ and $\beta_{i}, \hat{\beta}_{i}$, therefore, (\ref{final complex lagrange duality}) can be divided into two independent regression tasks,
+Notice in (\ref{final complex lagrange duality}), there is no correlation term between $\alpha_{i}, \hat{\alpha}_{i}$ and $\beta_{i}, \hat{\beta}_{i}$, therefore, (\ref{final complex lagrange duality}) can be divided into two independent regression tasks, which are given by
 
@@
 \end{IEEEeqnarray}
-
+and 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-Let $\mathbf{a}=[\alpha_{1}, \alpha_{2},\ldots, \alpha_{N_{r}}]^{T}$, $\mathbf{\hat{a}}=[\hat{\alpha}_{1}, \hat{\alpha}_{2},\ldots, \hat{\alpha}_{N_{r}}]^{T}$, $\mathbf{b}=[\beta_{1}, \beta_{2},\ldots, \beta_{N_{r}}]^{T}$,$\mathbf{\hat{b}}=[\hat{\beta}_{1}, \hat{\beta}_{2},\ldots, \hat{\beta}_{N_{r}}]^{T}$, $\Re{(\mathbf{y})}=[\Re{(y_{1})}, \Re{(y_{2})},\ldots, \Re{(y_{N_{r}})}]^{T}$, $\Im{(\mathbf{y})}=[\Im{(y_{1})}, \Im{(y_{2})}, \ldots, \Im{(y_{N_{r}})}]^{T}$, $\mathbf{R}^{r}=[\tilde{R}(\xi^{r}_{1})+\tilde{R}(\hat{\xi}^{r}_{1}), \tilde{R}(\xi^{r}_{2})+\tilde{R}(\hat{\xi}^{r}_{2}), \ldots, \tilde{R}(\xi^{r}_{N_{r}})+\tilde{R}(\hat{\xi}^{r}_{N_{r}})]^{T}$, $\mathbf{R}^{i}=[\tilde{R}(\xi^{i}_{1})+\tilde{R}(\hat{\xi}^{i}_{1}), \tilde{R}(\xi^{i}_{2})+\tilde{R}(\hat{\xi}^{i}_{2}), \ldots, \tilde{R}(\xi^{i}_{N_{r}})+\tilde{R}(\hat{\xi}^{i}_{N_{r}})]^{T}$, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$.
+Let $\mathbf{a}=[\alpha_{1}, \alpha_{2},\ldots, \alpha_{N_{r}}]^{T}$, $\mathbf{\hat{a}}=[\hat{\alpha}_{1}, \hat{\alpha}_{2},\ldots, \hat{\alpha}_{N_{r}}]^{T}$, $\mathbf{b}=[\beta_{1}, \beta_{2},\ldots, \beta_{N_{r}}]^{T}$,$\mathbf{\hat{b}}=[\hat{\beta}_{1}, \hat{\beta}_{2},\ldots, \hat{\beta}_{N_{r}}]^{T}$, $\mathbf{R}^{r}=[\tilde{R}(\xi^{r}_{1})+\tilde{R}(\hat{\xi}^{r}_{1}), \tilde{R}(\xi^{r}_{2})+\tilde{R}(\hat{\xi}^{r}_{2}), \ldots, \tilde{R}(\xi^{r}_{N_{r}})+\tilde{R}(\hat{\xi}^{r}_{N_{r}})]^{T}$, $\mathbf{R}^{i}=[\tilde{R}(\xi^{i}_{1})+\tilde{R}(\hat{\xi}^{i}_{1}), \tilde{R}(\xi^{i}_{2})+\tilde{R}(\hat{\xi}^{i}_{2}), \ldots, \tilde{R}(\xi^{i}_{N_{r}})+\tilde{R}(\hat{\xi}^{i}_{N_{r}})]^{T}$, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$.
 The alternate form can be written as
@@
 \nonumber
-\max_{\mathbf{a},\mathbf{\hat{a}}} \quad \theta^{r}=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\Re{(\mathbf{K})}(\mathbf{a}-\mathbf{\hat{a}})+\Re{(\mathbf{y})}^{T}(\mathbf{a}-\mathbf{\hat{a}})-\epsilon(\mathbf{e}^{T}(a+\mathbf{\hat{a}}))+C(\mathbf{e}^{T}\mathbf{R}^{r})\\
+\max_{\mathbf{a},\mathbf{\hat{\mathbf{a}}}} \quad \theta^{r}=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\Re{(\mathbf{K})}(\mathbf{a}-\mathbf{\hat{a}})+\Re{(\mathbf{y})}^{T}(\mathbf{a}-\mathbf{\hat{a}})-\epsilon(\mathbf{e}^{T}(\mathbf{a}+\mathbf{\hat{a}}))+C(\mathbf{e}^{T}\mathbf{R}^{r})\\
 \left\{\begin{array}{ll}
@@
 \section{Work Set Selection and Solver}\label{WSS}
-In (\ref{final complex lagrange duality}) we have a quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with a large data set.
+ As we can see, a quadratic optimization problem is formulated in (\ref{final complex lagrange duality}).
+The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with a large data set.
 
 Decomposition methods are a set of efficient algorithms that can help to ease this difficulty.
-Decomposition methods work iteratively, and based on choosing a subset of variables $S$ (named work set) to optimize in each iteration step, while keeping the rest variables $N$ fixed.
+Decomposition methods work iteratively, and are based on choosing a subset of optimization variables $S$ (named work set) to be updated in each iteration step, while keeping the rest variables $N$ fixed.
 Sequential Minimal Optimization (SMO) is an extreme case of decomposition method, where the work set size is 2, and an analytic quadratic programming (QP) step instead of numerical QP step can be performed in each iteration.
@@
 Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) have the same structure, in this section we discuss the real part only.
-By dividing the variables into work set $S$ and fixed set $N$, we can divide vector $\mathbf{a}$ into two sub vectors $[\mathbf{a}_{S}, \mathbf{a}_{N}]$.
+By dividing the variables into work set $S$ and fixed set $N$.
+Therefore, the vector $\mathbf{a}$ in (\ref{complex duality real part vectorizes}) can be divided into two sub vectors $[\mathbf{a}_{S}, \mathbf{a}_{N}]$.
 thereafter $\mathbf{a}_{S}$ denotes a vector that consists of the components of $\mathbf{a}$ that belongs to set $S$, the same modifications are applied to $\mathbf{\hat{a}}$ and $\mathbf{y}$.
@@
 \Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as
+\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of the components in $\Re(\mathbf{K})$ that belong to both of the rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\mathbf{K}$ is a Hermitian matrix, thus $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is solved i.e 
+In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is considered i.e 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 A proper work set selection strategy is required so that speed and performance requirement can be guaranteed.
-One idea is to perform update to dual variables that violate the complementary KKT conditions, which, based on (\ref{original KKT condition3}) in \ref{section lagrange duality}, can be formulated as
+One idea is to perform update to optimization variables that violate the KKT complementary conditions, which, based on (\ref{complete KKT complimentary})
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, L\\
-\hat{\alpha}_{i}(-\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, L\\
+\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, L\\
+\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots, L
 \end{array}\right.
@@
 
-Another idea for work set selection is to choose the dual variables whose update can provide the maximum improvement to dual objective function. The improvement of the sub dual objective function is
+Another idea for work set selection is to choose the optimization variables whose update can provide the maximum improvement to the sub dual objective functions.
+The improvement of the sub dual objective function is
 \begin{equation}
@@
 \end{IEEEeqnarray}
-define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Re{(\Phi)}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Im{(\Phi)}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$, let $\Phi_{S}$ denote the vector that consists of the components in $\Phi$ that corresponding to $S$.
+define intermediate variable vector $\Phi^{r}, \Phi^{i}\in \mathbb{R}^{N_{r}}$, $\Phi^{r}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Phi^{i}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$.
+Let $\Phi_{S}$ denote the vector that consists of the components in $\Phi$ that corresponding to $S$.
 Thus (\ref{gain of work set selection1 inter}) can be rewritten as 
@@
 \nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta})^{T}_{S}\Re{(\mathbf{K})}_{SS}(\Delta-\hat{\Delta})_{S}+(\Re{(\Phi)}_{S})^{T}(\Delta-\hat{\Delta})_{S}-\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta+\hat{\Delta})_{S}
+\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+(\Phi^{r}_{S})^{T}(\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}\\
+(\Delta_{S}+\hat{\Delta}_{S})
 \label{gain work set selection2}
 \end{IEEEeqnarray} 
-Because the offset term is omitted in Large MIMO regression model, therefore different from SMO type algorithms, there is no linear equation constraint, which is inducted by offset $b$, as shown in (\ref{partial4}).
-Therefore it is possible to update only one variable pair in each iteration.
-However, more efficient work set selection strategies based on maximum dual objective gain selection without considering offset term, is proposed in \cite{steinwart2011training}.
+Because the offset term is omitted in the large MIMO regression model, therefore different from SMO type algorithms, there is no linear equality constraint, which is inducted by offset $b$, as shown in (\ref{partial4}).
+Therefore the size of work set can be less than two.
+However, more efficient work set selection strategies based on maximal sub dual objective gain selection, is proposed in \cite{steinwart2011training}.
 A work set of size two is updated in each iteration.
-The computational cost is reduced while maintaining the comparable performance with that with offset.
-In CSVR large MIMO detector, the work set selection strategy in \cite{steinwart2011training} is exploited.
-Basically, in each iteration this strategy uses sequential single variable searchings, whose searching time is $O(n)$, where $n$ is the number of data set, to determine a work set of size two.
-On the one hand, this strategy can find a work set of size two, whose update approximately maximize the gain in the dual objective function.
-On the other hand, the brute-force searching for the work size of two, whose update can maximize the gain in the dual objective function, requires $O(n^{2})$ searching time.
-The former strategy requires as few iterations as the latter one, since in each iteration, the latter strategy is more expensive, the former one can enjoy significantly faster running speed.
-\subsection{Single Direction Solver}\label{single direction solver}
+The computational cost is reduced while maintaining the comparable performance with the model with offset term.
+In the CSVR large MIMO detector, the work set selection strategy in \cite{steinwart2011training} is exploited.
+Basically, in each iteration this strategy uses the combined single variable searchings, whose searching time is $O(n)$, where $n$ is the number of data samples, to determine a work set of size two.
+On the one hand, this strategy can find a work set of size two, whose update approximately maximize the gain of the dual sub objective function.
+On the other hand, the brute-force searching for the work size of two, whose update can maximize the gain of the sub dual objective function, requires $O(n^{2})$ searching time.
+The former strategy requires as few iterations as the latter one, since in each iteration, the latter strategy is more computationally expensive, the former one can enjoy significantly faster running speed.
+\subsection{Single Direction (1-D) Solver}\label{single direction solver}
 Recall the KKT complementary conditions 
@@
 \label{KKT complementary4}
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, N_{r}
-\label{complementary KKT condition2}
+\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
+\label{KKT complementary5}
+0\leq \alpha_{i}(\hat{\alpha}_{i})\leq R^{'}(\xi^{r}_{i})(R^{'}(\hat{\xi}_{i})), i=1,2,\ldots, N_{r} 
 \end{IEEEeqnarray}
@@
 \begin{equation}
-\xi^{r}_{i}(\hat{\xi}_{i}^{r})=|\Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}|_{\epsilon},
+\xi^{r}_{i} or \hat{\xi}_{i}^{r}=|\Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}|_{\epsilon},
 \label{definition of complex slack variables}
@@
 
-  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of dual objective function is chosen as the work set in each iteration.
-Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]$.
+  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of the sub dual objective function is chosen as the work set in each iteration.
+Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]^{T}$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]^{T}$.
 Substitute $\mathbf{a}, \hat{\mathbf{a}}$ with $\Lambda$ and using $\Sigma$.
-Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2})
-  \begin{equation}
-\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y})}_{S}^{T}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
+Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2}) can be rewritten as
+  \begin{equation}
+\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y}_{S}^{T})}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
 ]\Lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\Lambda_{S}|>,
@@
 \end{IEEEeqnarray} 
-In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to $\lambda_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
-\begin{IEEEeqnarray}[\relax]{l}
- \max_{\lambda_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\lambda_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
-+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\lambda_{m}^{new}-\epsilon(|\lambda^{new}_{m}|),
+In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
+\begin{IEEEeqnarray}[\relax]{l}
+ \max_{\tilde{\lambda}^{new}_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\tilde{\lambda}_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
++[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\tilde{\lambda}_{m}^{new}-\epsilon(|\tilde{\lambda}^{new}_{m}|),
  \label{optimization function 1-D}
  \end{IEEEeqnarray}
- Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Re{(\Phi)}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$, $\Re{(\Phi)}_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$.
+ where $\tilde{\lambda}^{new}_{m}$ is the update of $\lambda_{m}$.
+ Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Phi^{r}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$ in the imaginary channel, $\Phi_{i}^{i}=\Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$.
 Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
@@
 \nonumber
-\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))=\\
-\nonumber
--\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
-\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Re{(\Phi)}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
+\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))
 \label{partial optimization function 1-D lambda}
 \end{IEEEeqnarray} 
- The update of $\lambda_{m}$ is completed by clipping
+where $\Re(y_{m})-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re(\mathbf{K})_{mj}=\Re(y_{m})-\sum_{j=1}^{N_{r}}\lambda_{j}\Re(\mathbf{K}_{mj})=\Phi^{r}_{m}+\lambda_{m}\Re(\mathbf{K}_{mm})$
+and $\lambda_{m}$ denotes the $m$th optimization variable before update. Therefore (\ref{partial optimization function 1-D lambda}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\frac{\partial \theta^{r}_{m}}{\partial \tilde{\lambda}_{m}^{new}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
+\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Phi^{r}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
+\end{IEEEeqnarray}
+ The update of $\tilde{\lambda}^{new}_{m}$ is completed by clipping based on (\ref{KKT complementary5})
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-based on (\ref{gain work set selection lambda}), The maximal gain of objective function with respect to the $m$th optimization variable $\lambda_{m}$ is 
+based on (\ref{gain work set selection lambda}), The maximal gain of the sub dual objective function with respect to the $m$th optimization variable is 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \nonumber
-=-\frac{1}{2}\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}\sigma_{m}-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)\\
-=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|),
+=-\frac{1}{2}\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}\sigma_{m}-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)\\
+=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|),
 \label{gain of 1-D objective function}
@@
 Notice in (\ref{partial optimization function 1-D lambda}), $sgn(\tilde{\lambda}^{new}_{m})$ is unknown before $\lambda_{m}$ is updated, therefore two conditions $sgn(\tilde{\lambda}^{new}_{m})=1$ and $sgn(\tilde{\lambda}^{new}_{m})=-1$ are considered.
-The final decision of $sgn(\tilde{\lambda}_{m}^{new})$ is made by comparing the corresponding gains of the sub objective functions in (\ref{gain of 1-D objective function}).
-\subsection{Double Direction Solver}\label{double direction solver}
-Although the omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however, recent work in machine learning field shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained\cite{steinwart2011training}.
+The final decision of $sgn(\tilde{\lambda}_{m}^{new})$ is made by comparing the corresponding gains of the sub dual objective functions in (\ref{gain of 1-D objective function}).
+\subsection{Double Direction (2-D) Solver}\label{double direction solver}
+Although the omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however, recent work in \cite{steinwart2011training} shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained.
 The optimal 2-D solver uses the same principle as 1-D solver, $|S|=2$, assume the work set consists of the $m$th and $n$th optimization variables, that are $\Lambda_{S}=[\lambda_{m}, \lambda_{n}]$.
@@
 \frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}+\Re{(\mathbf{y}_{m})}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=\\
--\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}+\Re{(\Phi)}_{m}+\lambda_{m}\Re{\mathbf{K}}_{mm}+\lambda_{n}\Re{(\mathbf{K})}_{mn}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=0\\
+-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{m}+\lambda_{m}\Re{\mathbf{K}}_{mm}+\lambda_{n}\Re{(\mathbf{K})}_{mn}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=0\\
 \nonumber
@@
 \frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{n}}=-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{n})}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=\\
--\tilde{\lambda}_{n}^{new}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}+\Re{(\Phi)}_{n}+\lambda_{m}\Re{(\mathbf{K})}_{mn}+\lambda_{n}\Re{(\mathbf{K})}_{nn}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=0\\
+-\tilde{\lambda}_{n}^{new}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{n}+\lambda_{m}\Re{(\mathbf{K})}_{mn}+\lambda_{n}\Re{(\mathbf{K})}_{nn}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=0\\
 \nonumber
@@
 \label{post partial lambda1}
-(\tilde{\lambda}^{new}_{m}-\lambda_{n})\Re{(\mathbf{K})}_{mm}=\Re{(\Phi)}_{m}-\epsilon sgn(\tilde{\lambda}^{new}_{m})-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{mn}\\
+(\tilde{\lambda}^{new}_{m}-\lambda_{n})\Re{(\mathbf{K})}_{mm}=\Phi^{r}_{m}-\epsilon sgn(\tilde{\lambda}^{new}_{m})-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{mn}\\
 \label{post partial lambda2}
-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{nn}=\Re{(\Phi)}_{n}-\epsilon sgn(\tilde{\lambda}^{new}_{n})-(\tilde{\lambda}^{new}_{m}-\lambda_{m})\Re{(\mathbf{K})}_{mn}\\
-\nonumber
-\end{IEEEeqnarray}
-hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formula of $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}^{new}_{n}$ are
-\begin{equation}
-\tilde{\lambda}^{new}_{m}=\lambda_{m}+\frac{\Re{(\Phi)}_{m}\Re{(\mathbf{K})}_{nn}-\Re{(\Phi)}_{n}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{nn}-sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
+(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{nn}=\Phi^{r}_{n}-\epsilon sgn(\tilde{\lambda}^{new}_{n})-(\tilde{\lambda}^{new}_{m}-\lambda_{m})\Re{(\mathbf{K})}_{mn}\\
+\nonumber
+\end{IEEEeqnarray}
+hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formulas of $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}^{new}_{n}$ are given by
+\begin{equation}
+\tilde{\lambda}^{new}_{m}=\lambda_{m}+\frac{\Phi^{r}_{m}\Re{(\mathbf{K})}_{nn}-\Phi^{r}_{n}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{nn}-sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
 \label{update lambda1}
@@
 \begin{equation}
-\tilde{\lambda}^{new}_{n}=\lambda_{n}+\frac{\Re{(\Phi)}_{n}\Re{(\mathbf{K})}_{mm}-\Re{(\Phi)}_{m}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mm}-sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
+\tilde{\lambda}^{new}_{n}=\lambda_{n}+\frac{\Phi^{r}_{n}\Re{(\mathbf{K})}_{mm}-\Phi^{r}_{m}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mm}-sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
 \label{update lambda2}
 \end{equation} 
-Then the updated optimization variables are clipped by constraint 
+Then the updated optimization variables are clipped by constraint based on (\ref{KKT complementary5})
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
-Based on (\ref{gain work set selection2}),  the gain of 2-D solver objective function can be written as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=-\frac{1}{2}[\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\sigma_{n}^{2}\Re{(\mathbf{K})}_{nn}+2\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn}]+\Re{(\Phi)}_{m}\sigma_{m}+\Re{(\Phi)}_{n}\sigma_{n}\\
+Based on (\ref{gain work set selection2}),  the gain of the sub dual objective function can be written as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta^{r}_{mn}=-\frac{1}{2}[\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\sigma_{n}^{2}\Re{(\mathbf{K})}_{nn}+2\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn}]+\Phi^{r}_{m}\sigma_{m}+\Phi^{r}_{n}\sigma_{n}\\
 -\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|+|\lambda^{new}_{n}|-|\lambda_{n}|),
@@
 \end{equation}
- modify (\ref{gain of 2-D objective function1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)+\sigma_{n}[-\frac{1}{2}\sigma_{n}\Re{(\mathbf{K})}_{nn}+\Re{(\Phi)}_{n}]-\epsilon(|\lambda^{new}_{n}|-|\lambda_{n}|)\\
--\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn},
-\end{IEEEeqnarray}
 
@@
 
-Recall the gain of dual objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
+Modify (\ref{gain of 2-D objective function1}), we have 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\bigtriangledown \theta^{r}_{mn}=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)+\sigma_{n}[-\frac{1}{2}\sigma_{n}\Re{(\mathbf{K})}_{nn}+\Phi^{r}_{n}]-\epsilon(|\lambda^{new}_{n}|-|\lambda_{n}|)\\
+-\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn},
+\end{IEEEeqnarray}
+then recall the gain of the sub dual objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
  \begin{IEEEeqnarray}[\relax]{l}
 \bigtriangledown \theta^{r}_{ij}=\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}-\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij},
-\label{gain of 2-D objective function1}
-\end{IEEEeqnarray}
-where $\bigtriangledown \theta^{r}_{i}$, $\bigtriangledown \theta^{r}_{j}$ denote gains of 1-D solver with $m$th and $n$th dual variable pairs are chosen. 
+\label{gain of 2-D objective function2}
+\end{IEEEeqnarray}
+where $\bigtriangledown \theta^{r}_{i}$, $\bigtriangledown \theta^{r}_{j}$ denote gains of the sub dual objective functions of 1-D solver with $i$th and $j$th optimization variables are updated. 
 \subsection{Approximation of Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
-From (\ref{gain of 2-D objective function1}), we can observe that the gain of 2-D solver is a summation of the gain of 2 independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}$.
-
-Obviously optimal 2-D work set $[i,j]$ can be determined by brute-force searching manner, which requires $O(n^{2})$ searching times.
+From (\ref{gain of 2-D objective function1}), we can observe that the gain of the sub dual objective function of 2-D solver is a summation of the gains of the sub dual objective functions of two independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}$.
+
+The optimal 2-D work set $[i,j]$ can be determined by brute-force searching manner, which requires $O(n^{2})$ searching times.
 Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D searching strategy by the combinations of optimal 1-D searching approach, we will prove in the large MIMO systems, when $N_{t}$ is sufficient large, this approximation is very effective.
-Here we propose two kinds of 1-D approximate searching strategy:
-\subsubsection{ One-shot 1-D Searching}
-do one round 1-D searching and calculate all the 1-D gain based on (\ref{gain of 1-D objective function}), then choose the two optimization variables indexed by $i$ and $j$, whose update can achieve the first and the second largest gain of the sub dual objective functions.
-\subsubsection{ Sequential 1-D Searching}
-do two rounds 1-D searchings, in the first round find optimization variable indexed by $i$ whose update can achieve the maximal 1-D gain of the sub dual objective functions, then update the $i$th optimization variable.
+Here we propose two types of combined 1-D searching strategy:
+\subsubsection{ One-shot 1-D combined Searching}
+do one round 1-D searching and calculate all the 1-D gains based on (\ref{gain of 1-D objective function}), then choose the two optimization variables indexed by $i$ and $j$, whose update can achieve the first and the second largest gain of the sub dual objective functions.
+\subsubsection{ Sequential 1-D combined Searching}
+do two rounds 1-D searchings, in the first round find optimization variable indexed by $i$ whose update can achieve the maximal 1-D gain of the sub dual objective functions based on (\ref{gain of 1-D objective function}), then update the $i$th optimization variable.
 In the second round, find $j$th optimization variable whose update can achieve the maximal 1-D gain of the sub dual objective functions.
@@
 Hence we provide theoretical analyses based on the view of channel hardening phenomenon.
-It can be proved that in the large MIMO systems, the correlation term is ignorable comparing to 1-D gains of the sub objective function.
+It can be proved that in the large MIMO systems, the correlation term $\sigma_{i}\sigma_{j}\Re(\mathbf{K}_{ij})$is ignorable comparing to 1-D gains of the sub objective function.
 Prior to the theoretical analyse, we first investigate some mathematical properties of channel hardening (to be completed).
@@
 \section{Stopping Criteria}\label{stopping criteria}
-As we have explained in section \ref{section lagrange duality}, the upper bound of Lagrangian dual objective function is determined by primal objective function, further more the optimal of primal and dual objective function is found if and only if the equality holds, that is
-\begin{equation}
-\theta(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)
-\label{duality equal}
-\end{equation}
-\begin{equation}
-\frac{1}{2}||\mathbf{w}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
+As discussed in section\ref{section lagrange duality}, in dual objective function, the complementary KKT conditions are the measurement of the proximity of current solution to the optimal solution. 
+The feasibility gap, which is a effective stopping criteria used in SVR and SVM, can implicitly monitor whether the KKT complementary conditions are satisfied.
+The feasibility gap measures the gap between the values of primal objective function and dual objective function.
+To elaborate a little further, recall the saddle point conditions in section\ref{section lagrange duality}
+ \begin{equation}
+ L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
+ \label{saddle point conditions}
+ \end{equation}
+Where $(\bar{\mathbf{w}}, \bar{\mathbf{a}})$ are the solution to primal objective function, the KKT complementary conditions are satisfied, that is 
+\begin{equation}
+\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=0,
+\label{complementary KKT condition revisited}
+\end{equation}
+we have 
+\begin{equation}
+L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=f(\bar{\mathbf{w}})+\sum_{i=1}^{N_{r}}\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=f(\bar{\mathbf{w}})
+\end{equation} 
+Let $(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$ denote the variable pair that satisfies the first and second KKT conditions in (\ref{original KKT condition1} ) and (\ref{original KKT condition2})
+
+\begin{IEEEeqnarray}[\relax]{l}
+\label{original KKT condition revisited1}
+\partial_{\mathbf{w}}L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=\partial_{\mathbf{w}}f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{a}_{i}\partial_{\mathbf{w}}c_{i}(\tilde{\mathbf{w}})=0,\\
+\label{original KKT condition revisited2}
+c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots L
+\end{IEEEeqnarray}
+based on (\ref{original KKT condition revisited1}), we have 
+\begin{IEEEeqnarray}[\relax]{l}
+L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq f(\tilde{\mathbf{w}}),
+\end{IEEEeqnarray} 
+based on Theorem 6.27\cite{scholkopf2002learning}, the following equalities hold
+\begin{IEEEeqnarray}[\relax]{l}
+f(\tilde{\mathbf{w}})\geq f(\bar{\mathbf{w}})=L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})
+\label{inequality gap}
+\end{IEEEeqnarray}
+Therefore the feasibility gap is defined by the gap between the primal objective function $f(\tilde{\mathbf{w}})$ and the dual objective function $L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$   
+\begin{equation}
+f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\geq 0
+\label{original feasibility gap}
+\end{equation}
+If the feasibility gap is vanished, based on (\ref{inequality gap}), we have $f(\bar{\mathbf{w}})=f(\tilde{\mathbf{w}})$, thus $\tilde{\mathbf{w}}=\bar{\mathbf{w}}$, $\tilde{\mathbf{a}}=\bar{\mathbf{a}}$.
+Furthermore, because $f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})$, the vanish of feasibility gap indicates $\sum_{i=1}^{L}\tilde{\mathbf{a}}c_{i}(\tilde{\mathbf{w}})=0$.
+Because $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots, L$, we have $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})=0, i=1,2,\ldots, L$, the KKT complementary conditions are satisfied.
+
+In CSVR detector for the large MIMO systems, the primal objective function is
+\begin{equation}
+f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
+\label{simple primal inter}
+\end{equation}
+where $\tilde{\mathbf{w}}$ satisfies the KKT  conditions in (\ref{original KKT condition revisited1}) and (\ref{original KKT condition revisited2}).
+Define $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$, $\Lambda^{r}=[\lambda^{r}_{1}, \lambda^{r}_{2}, \ldots, \lambda^{r}_{L}]^{T}$ and $\Lambda^{i}=[\lambda^{i}_{1}, \lambda_{2}^{i}, \ldots, \lambda^{i}_{L}]^{T}$,
+(\ref{complex duality regularization1}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-2<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>,
+\label{simple regularization}
+\end{IEEEeqnarray}
+Therefore we obtain  
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+\\R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
 \label{simple primal}
-\end{equation}
-(\ref{final complex lagrange duality}) can be rewritten as follow by substituting $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\lambda^{r}, \lambda^{i})=-\frac{1}{2}<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>-\frac{1}{2}<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>+<Re(\mathbf{y})^{T}, \lambda^{r}>+<Im(\mathbf{y})^{T}, \lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
+\end{IEEEeqnarray}
+Based on (\ref{final complex lagrange duality}), the dual objective function can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\theta(\Lambda^{r}, \Lambda^{i})=-\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>-\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>+<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>\\
+-\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
 \label{simple dual function}
 \end{IEEEeqnarray}
-Similarly, (\ref{complex duality regularization1}) can be formulated as 
-\begin{IEEEeqnarray}[\relax]{l}
-||\mathbf{W}||^{2}_{\mathbb{H}}=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>,
-\label{simple regularization}
-\end{IEEEeqnarray}
-hence, duality gap can be formulated as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\lambda^{r}, \lambda^{i})=f(\mathbf{w},\xi)-\theta(\lambda^{r},\lambda^{i})=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-<Re(\mathbf{y})^{T}, \lambda^{r}>-<Im(\mathbf{y})^{T}, \lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.
+
+Based on (\ref{simple primal}) and (\ref{simple dual function}), the feasibility gap is obtained 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+G(\lambda^{r}, \lambda^{i})=f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})-\theta(\Lambda^{r},\Lambda^{i})=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Re{(\mathbf{y}^{T})}, \Lambda^{r}>\\\nonumber
+-<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-\\<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>.
 \label{simple duality gap}
@@
 \end{equation}
-In $\epsilon$-SVR, the objective to exploit slack variables $\xi^{r}_{i}$ and $\hat{\xi}_{i}^{r}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
+In $\epsilon$-SVR, the objective to exploit slack variables is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by the noise.
 Therefore in $\epsilon$-SVR, $\xi^{r}_{i}$ and $\hat{\xi}^{r}$ are defined as  
@@
 \end{IEEEeqnarray} 
-Because the distance between the estimations $\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}$ and the observations $\Re{(\mathbf{y}_{i})}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi^{r}_{i}$ and $\hat{\xi}^{r}_{i}$ can be non zero.
-That is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
+Because the distance between the estimations $\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}$ and the observations $\Re{(\mathbf{y}_{i})}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi^{r}_{i}$ and $\hat{\xi}^{r}_{i}$ can be non zero that is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
 Therefore the risk function can be rewritten as 
 \begin{IEEEeqnarray}[\relax]{l}
-R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}|Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|_{\epsilon}^{2}\\
 \label{simple risk function1}
-R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}|Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|^{2}_{\epsilon}
-\label{simple risk function2}
+R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}|\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|_{\epsilon}^{2}\\\label{simple risk function2}
+R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}|\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|^{2}_{\epsilon}
 \end{IEEEeqnarray}
@@
 \begin{IEEEeqnarray}[\relax]{l}
-Re(\mathbf{y}_{i})-Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}^{r}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}^{i}_{ij}\\
-Im(\mathbf{y}_{i})-Im(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\mathbf{K}^{r}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\mathbf{K}^{i}_{ij}
-\label{intermediate function1}
+\label{intermediate function1a}
+\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re(\mathbf{K})_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im(\mathbf{K})_{ij}\\
+\label{intermediate function1b}
+\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re(\mathbf{K})_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Im(\mathbf{K})_{ij}
 \end{IEEEeqnarray}
@@
 \label{intermedia function 2a}
-\Phi^{r}=Re(\mathbf{y})-\mathbf{K}^{r}
+\Phi^{r}=\Re(\mathbf{y})-\Re(\mathbf{K})
 \lambda^{r};
-\Phi^{i}=Im(\mathbf{y})-\mathbf{K}^{r}\lambda^{i}\\
+\Phi^{i}=\Im(\mathbf{y})-\Re(\mathbf{K})\lambda^{i}\\
 \label{intermediate function 2b}
-\Psi^{r}=\mathbf{K}^{i}\lambda^{i};
-\Psi^{i}=-\mathbf{K}^{i}\lambda^{r}\\
-\nonumber
-\end{IEEEeqnarray} 
-Therefore based on (\ref{simple risk function1})-(\ref{intermediate function 2b}), duality gap in (\ref{simple duality gap}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\lambda^{r}, \lambda^{i})=<(\lambda^{r})^{T}, \mathbf{K}^{r}\lambda^{r}>+<(\lambda^{i})^{T}, \mathbf{K}^{r}\lambda^{i}>-<Re(\mathbf{y})^{T}, \lambda^{r}>-<Im(\mathbf{y})^{T}, \lambda^{i}>\\
-+\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.
+\Psi^{r}=\Im(\mathbf{K})\lambda^{i};
+\Psi^{i}=-\Im(\mathbf{K})\lambda^{r}\\
+\nonumber
+\end{IEEEeqnarray} 
+therefore (\ref{intermediate function1a}) and (\ref{intermediate function1b}) can be rewritten as
+\begin{IEEEeqnarray}[\relax]{l}
+\label{intermediate function3a}
+\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi^{r}_{i}+\Psi_{i}^{r}\\\label{intermediate function3b}
+\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Phi_{i}^{i}+\Psi_{i}^{i}
+\end{IEEEeqnarray}
+Therefore based on (\ref{intermediate function3a}) and (\ref{intermediate function3b}), 
+(\ref{simple risk function1}) and (\ref{simple risk function2}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\label{intermediate function4a}
+R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})=\frac{1}{2}|\Phi^{r}_{i}+\Psi_{i}^{r}|^{2}_{\epsilon}\\
+\label{intermediate function4b}
+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})=\frac{1}{2}|\Phi^{i}_{i}+\Psi_{i}^{i}|^{2}_{\epsilon}
+\end{IEEEeqnarray}
+Thus based on (\ref{intermediate function4a}) and (\ref{intermediate function4b}), the feasibility gap in (\ref{simple duality gap}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+G(\Lambda^{r}, \Lambda^{i})=<(\Lambda^{r})^{T}, \Re(\mathbf{K})\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re(\mathbf{K})\Lambda^{i}>-<\Re(\mathbf{y})^{T}, \Lambda^{r}>-<\Im(\mathbf{y})^{T}, \Lambda^{i}>\\
++\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.
 \label{simple duality gap final}
 \end{IEEEeqnarray}
-Based on objective function in (\ref{simple dual function}), (\ref{simple duality gap final}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G=(\lambda_{r}, \lambda_{i})=<Re(\mathbf{y})^{T}, \lambda^{r}>+<Im(\mathbf{y})^{T}, \lambda^{i}>-\epsilon<\mathbf{e}^{T}, (|\lambda^{r}|+|\lambda^{i}|)>-2\theta(\lambda_{i}, \lambda_{j})\\
--2<\lambda^{r}, \mathbf{K}^{i}\lambda^{i}>.\label{simple duality gap ratio1}
-\end{IEEEeqnarray}
-The duality gap between primal problem and dual problem is used to evaluate how close a solution is to global minimum. In our scenario, duality gap is employed as stopping criteria.
-Therefore to make stopping criteria more effective to monitor if algorithm convergent, we monitor the ratio by a value of tolerance (usually this tolerance is set to $10^{-3}$).
+Based on dual objective function in (\ref{simple dual function}), (\ref{simple duality gap final}) can be rewritten as 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+G(\Lambda^{r}, \Lambda^{i})=<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im(\mathbf{y})^{T}, \Lambda^{i}>-\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>-2\theta(\Lambda_{i}, \Lambda_{j})\\
+-<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.\label{simple duality gap1}
+\end{IEEEeqnarray}
+The following ratio of the feasibility gap $G(\Lambda^{r}, \Lambda^{i})$ is used to measure the proximity of current solution to the optimal solution.
+The algorithm stops when the ratio satisfies a certain tolerance.
 \begin{equation}
 \frac{G}{G+\theta}
-\label{simple duality gap ratio2}
+\label{simple duality gap ratio1}
 \end{equation}
 \subsection{Update $\Phi$, $\Psi$ and $G$}
-In each iteration $\Phi$, $\Psi$ and $G$ are updated partially based on 2 updated optimization variables. Here we give the pseudo code to update $\Phi$, $\Psi$ and $G$.
-
-Based on the definition of $\Phi$ and $\Psi$ in (\ref{intermedia function 2a}) and (\ref{intermediate function 2b}), we have the following procedure to update $\Phi$ and $\Psi$ in real channel and imaginary channel, assume the optimization coordinate updated in each channel are $1$ and $2$.\\
+$\Phi$, $\Psi$ and $G$ are updated in each iteration along with the optimization variables updated. The pseudo code to update $\Phi$, $\Psi$ and $G$ is given.
+
+Based on the definitions of $\Phi$ and $\Psi$ in (\ref{intermedia function 2a}) and (\ref{intermediate function 2b}), we have the following procedure to update $\Phi$ and $\Psi$ in real channel and imaginary channel, assume the optimization variables updated in each channel are indexed by $1$ and $2$, let $\sigma^{r}_{i}=(\lambda^{r}_{i})^{new}-\lambda^{r}_{i}$ and $\sigma^{i}_{i}=(\lambda^{i}_{i})^{new}-\lambda^{i}_{i}$ denote the differences between the updated optimization variables and the old optimization variables.\\
 \begin{algorithm}[htb]
@@
 
-Then the risk function term in (\ref{simple duality gap final}) is updated as following
+Then the cost function term in (\ref{simple duality gap final}) are updated by \textbf{Procedure 3} and \textbf{Procedure 4}.
+The cost function terms are denoted by $\chi^{r}$ in real channel and $\chi^{i}$ in imaginary channel.
+\begin{IEEEeqnarray}[\relax]{l}
+\label{cost function update1}
+\chi^{r}=\sum_{i}^{N_{r}}|\Phi^{r}_{i}+\Psi^{r}_{i}|^{2}_{\epsilon}\\
+\label{cost function update2}
+\chi^{i}=\sum_{i}^{N_{r}}|\Phi^{i}_{i}+\Psi^{i}_{i}|^{2}_{\epsilon}
+\end{IEEEeqnarray}
 \begin{algorithm}[htb]
 \begin{algorithmic}
-\Procedure{\textbf{3}. Update risk function in real channel}{$\chi^{r}$}
+\Procedure{\textbf{3}. Update cost function in real channel}{$\chi^{r}$}
 \State $\chi^{r}=0$  \Comment{initial risk term}
@@
 \begin{algorithmic}
-\Procedure{\textbf{4}. Update risk function in imaginary channel}{$\chi^{i}$}
+\Procedure{\textbf{4}. Update cost function in imaginary channel}{$\chi^{i}$}
 \State $\chi^{i}=0$  \Comment{initial risk term}
@@
 \end{algorithm}
-The pseudo code to update duality gap $G$ based on (\ref{simple duality gap final}) is shown as follow assume the coordinate updated in real channel is $i$ and $j$, in imaginary channel is $m$ and $f$.
+The pseudo code to update duality gap $G$ based on (\ref{simple duality gap1}) is shown in \textbf{Procedure 5}.
+Assume the indexes of optimization variables updated in real channel is $i$ and $j$, the indexes of optimization variables updated in imaginary channel is $m$ and $f$.
+Define the work sets in real and imaginary channels $S^{r}=[i,j]$ and $S^{i}=[m,f]$.
+Define $(\chi^{r})^{new}$ and $(\chi^{i})^{new}$ are the updated cost function terms based on \textbf{Procedure 3} and \textbf{Procedure 4}, the update process for the term $\theta(\Lambda^{r}, \Lambda^{i})$ in (\ref{simple duality gap1}) can be written as
+\begin{equation}
+\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}})=\bigtriangledown \theta^{r}_{S^{r}}+\bigtriangledown \theta^{i}_{S^{i}}-\frac{C}{2}((\chi^{r})^{new}+(\chi^{i})^{new}-\chi^{r}-\chi^{i}),
+\label{update dual objective function}
+\end{equation}
+Where $\theta_{S}^{r}$ is the gain of the sub dual objective function as shown in (\ref{gain work set selection lambda}), 
+\begin{IEEEeqnarray}[\relax]{l}
+\bigtriangledown \theta_{S^{r}}^{r}=-\frac{1}{2}(\Sigma^{r}_{S^{r}})^{T}\Re{(\mathbf{K})}_{S^{r}S^{r}}\Sigma^{r}_{S^{r}}+(\Phi^{r}_{S^{r}})^{T}\Sigma^{r}_{S^{r}}-\epsilon<\mathbf{e}^{T}_{S^{r}},|(\Lambda^{r}_{S^{r}})^{new}|-|\Lambda^{r}_{S^{r}}|>\\
+\bigtriangledown \theta_{S^{i}}^{i}=-\frac{1}{2}(\Sigma^{i}_{S^{i}})^{T}\Re{(\mathbf{K})}_{S^{i}S^{i}}\Sigma^{i}_{S^{i}}+(\Phi^{i}_{S^{i}})^{T}\Sigma^{i}_{S^{i}}-\epsilon<\mathbf{e}^{T}_{S^{i}},|(\Lambda^{i}_{S^{i}})^{new}|-|\Lambda^{i}_{S^{i}}|>
+\end{IEEEeqnarray}
 \begin{algorithm}[htb]
@@
 \State $G-=\epsilon(|\lambda^{i}_{m}+\sigma^{i}_{m}|-|\lambda^{i}_{m}|+|\lambda^{i}_{f}+\sigma^{i}_{f}|-|\lambda^{i}_{f}|)$
-\State $G-=2(\bigtriangledown \theta_{i,j,m,f}(\sigma^{r}_{i},\sigma^{r}_{j},\sigma^{i}_{m},\sigma^{i}_{f}))$\Comment{Update sub objective function based on (\ref{gain of 2-D objective function1})}
-\State $G+=C(\chi^{r}+\chi^{i})^{new}-(\chi^{r}+\chi^{i})$ \Comment{Update risk function term based on \textbf{Procedure 3} and \textbf{Procedure 4}}
-\State $G-=\sigma^{r}_{i}\sigma^{i}_{m}\mathbf{K}^{i}_{im}+\sigma^{r}_{i}\sigma^{i}_{f}\mathbf{K}^{i}_{if}+\sigma^{r}_{j}\sigma^{i}_{m}\mathbf{K}^{i}_{jm}+\sigma^{r}_{j}\sigma^{i}_{f}\mathbf{K}^{i}_{jf}+\sigma^{i}_{m}\sum_{k=1}^{N_{r}}\lambda_{k}^{r}\mathbf{K}^{i}_{km}+\sigma^{i}_{f}\sum_{k=1}^{N_{r}}\lambda_{k}^{r}\mathbf{K}^{i}_{kf}-\sigma^{r}_{i}\sum_{k=1}^{N_{r}}\lambda_{k}^{i}\mathbf{K}^{i}_{ki}-\sigma^{r}_{j}\sum_{k=1}^{N_{r}}\lambda_{k}^{i}\mathbf{K}^{i}_{kj}$ \Comment{Update $<\lambda^{r},\mathbf{K}^{i}\lambda^{i}>$}
+\State $G-=2(\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}}))$ \Comment{Update sub objective function based on (\ref{update dual objective function})}
+
+\State $G-=(\Sigma^{r}_{S^{r}})^{T}\Im(\mathbf{K}_{S^{r}S^{i}})\Sigma^{i}_{S^{i}}+(\Sigma^{r}_{S^{r}})^{T}\Psi^{r}_{S^{r}}+(\Sigma^{i}_{S^{i}})^{T}\Psi^{i}_{S^{i}}$ \Comment{Update $<\Lambda^{r},\Im(\mathbf{K})\Lambda^{i}>$}
 \EndProcedure
@@
 
-Pseudo code for sequential single searching 2-D solver is shown as following 
+Pseudo code for two types of combined 1-D searching solver are given by \textbf{Procedure 6} and \textbf{Procedure 7}. 
 \begin{algorithm}[htb]
 \begin{algorithmic}
-\Procedure{\textbf{6}. Sequential single searching 2-D solver without Damping}{} 
+\Procedure{\textbf{6}. One-shot 1-D combined searching solver}{} 
 \State Step 1. Search for two optimization variables based on single direction solver
@@
 
- \begin{algorithm}
+ \begin{algorithm}[htb]
 \begin{algorithmic}
-\Procedure{\textbf{7}. Sequential single searching 2-D solver with Damping}{}
+\Procedure{\textbf{7}. Sequential 1-D combined searching solver}{}
 \State Step 1. Search for two optimization variables based on single direction solver
@@
 \end{algorithm} 
-
-The following is the pseudo code of complex support vector detector (CSVD) is shown in Appendix \ref{Pseudo code of CSVD}
+\newpage
+The pseudo code of complex support vector detector (CSVD) is shown in Appendix \ref{Pseudo code of CSVD}
 
 %\section{Hyperparameter Setting}
-\newpage
 \section{Computer Simulations}
-Computer simulation is launched to test the detection and run time performance of proposed dual channel complex support vector detection algorithm.
+Computer simulations are launched to test the detection and run time performance of proposed dual channel complex support vector detection algorithm.
 For sake of brevity, the real case is tested first, all the experiments are made by C, compiled by gcc version 4.8.3 on 64 bit Fedora (release 19) Linux system.
@@
 \end{figure}
+
 \begin{table}[htb]
@@
 \State Step 3.
-\State Sequentia single searching 2-D solver with or without damping \Comment{find two optimization variables to be updated} 
-\State Step 4. \textbf{Procedure 5} update $G$
+\State call combined 1-D searching solver in \textbf{Procedure 6} and \textbf{Procedure 7} \Comment{find and update two optimization variables in the real and imaginary channel} 
+\State Step 4. \textbf{Procedure 5} update $\frac{G}{G+\theta}$, go back to step 2.
 \State Step 5.
-\State $\tilde{x}=(\lambda^{r}+i\lambda^{i})^{T}\mathbf{H}$ \Comment{reconstruct $\mathbf{x}$}
+\State $\tilde{\mathbf{x}}=\mathbf{H}^{H}(\Lambda^{r}+i\Lambda^{i})$ \Comment{reconstruct $\mathbf{x}$}
 \State $\mathbf{x}=\mathbb{Q}(\tilde{x})$\Comment{$\mathbb{Q}(\cdot)$ denotes quantization operation based on symbol constellation}
-\State go back to Step 2
 \State Step 6. \textbf{Return} $\mathbf{x}$ 
-
 \EndProcedure
@@
 % by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
+%\ifCLASSOPTIONcaptionsoff
+%  \newpage
+%\fi
 

### 2015-10-20 Report Aug 5 2015/Report Aug 2015.tex
simulation matlab code

@@
 Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]^{T}$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]^{T}$.
-Substitute $\mathbf{a}, \hat{\mathbf{a}}$ with $\Lambda$ and using $\Sigma$.
+In (\ref{subset optimization}), substitute $\mathbf{a}, \hat{\mathbf{a}}$ by $\Lambda$ and in (\ref{gain work set selection2}), substitute $\Delta$ by $\Sigma$.
 Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2}) can be rewritten as
@@
 \end{IEEEeqnarray} 
-In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
+In 1-D solver, $|S|=1$, based on (\ref{subset optimization lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
 \begin{IEEEeqnarray}[\relax]{l}

### 2015-10-20 SVR for large MIMO/real SVR matlab/CSVR/MMSE_OSIC.m

@@ -1,0 +1,90 @@
+function [ symOut ] = MMSE_OSIC(y, H, SNRd, M, pav)
+%this routine implement MMSE-OSIC algorithm
+%   Detailed explanation goes here
+
+Nr=length(H);
+Nt=length(H(:,1));
+symOut=zeros(Nt,1);  %output symbol vector
+% symOut_tmp_v=zeros(Nt,1);  %
+symOut_list=1:Nt; %record the current index of the updated subvector
+% symOut_Recons=zeros(Nt,1);
+
+H_tmp=H;  %updated channel matrix
+y_tmp=y; %updated received symbol vector 
+for count=1:Nt
+    I=eye(Nt-(count-1));
+    G=(I/(H_tmp'*H_tmp+SNRd^(-1)*I));   %inverse of HHH matrix with SNR
+    [value, index]=min(diag(G));   %choice of the channel with the minimum post processing SNR
+    G=G*H_tmp';   %equalization matrix
+    symOut_tmp=G(index,:)*y_tmp;   
+    symOut_tmp=Rectangular_QAM_slicer(symOut_tmp,M,pav); %detected symbol 
+    symOut(symOut_list(index))=symOut_tmp; %upate output symbol vector
+    y_tmp=y_tmp-H_tmp(:,index)*symOut_tmp; %update received symbol vector
+    H_tmp(:,index)=[];  %update channel matrix
+    symOut_list(index)=[];   %update symbol index list
+
+end
+
+
+
+end
+
+function [X_hat] = Rectangular_QAM_slicer(X, M, pav)    %slicer
+%need to be modified
+
+% sq10=sqrt(10);
+if(M==2)
+    d=sqrt(pav);
+else
+d=sqrt(3*pav/(2*(M-1)));
+end
+
+N=length(X);
+for i=1:N
+if(M==2)
+    
+    if(real(X(i))<=0)
+        REAL=-d;
+    else
+        REAL=d;
+    end
+    X(i)=complex(REAL,0);
+elseif(M==4)
+        if(real(X(i))<=0)
+        REAL=-d;
+    else
+        REAL=d;
+        end
+        if(imag(X(i))<=0)
+        IMAG=-d;
+    else
+        IMAG=d;
+        end
+        X(i)=complex(REAL, IMAG);
+elseif(M==16)
+    
+        if(real(X(i))<=-2*d)
+        REAL=-3*d;
[…]

### 2015-10-20 SVR for large MIMO/real SVR matlab/CSVR/RSVR_MIC_ordering_descend.m

@@ -1,9 +1,10 @@
-function [ symOut ] = MIC_Recursive(y, H, symOut_prev, SNRd, M, pav, stage, maxStage,W,G, symConstell)
+function [ symOut ] = RSVR_MIC_ordering_descend(y, H, symOut_prev, SNRd, M, pav, stage, maxStage,W,G, symConstell, order)
 %Multistage Interference Cancellation (MIC) recursive algorithm
 %   Detailed explanation goes here
 % W is weight matrix with the diagonal elements represent the weight of
 % each estimation
 %is W is an identity matrix, that this is the original version MIC
+%the weakest data stream is detected firsly
 Nr=length(H(:,1)); %number of receive antennas
 Nt=length(H(1,:));  %number of transmit antennas
 I=eye(Nt);
@@ -14,8 +15,26 @@ symOut_current=zeros(Nt,1);
 if(stage==1)
 INV=(I/(H'*H+SNRd^(-1)*I));
 G=INV*H';
-symOut_current=G*y;
-[symOut_current]=Rectangular_QAM_slicer(symOut_current, M, pav);
+D=diag(INV);
+[value, order]=sort(D,'ascend');
+% H_tmp=H;
+% G_tmp=INV;
+% order=zeros(Nt,1);
+% list=1:Nt;
+% for count=1:Nt-1
+%     [value, i]=min(diag(G_tmp));
+%     order(count)=list(i);
+%     H_tmp(:,i)=[];
+%     list(i)=[];
+%     I=eye(Nt-count);
+%     G_tmp=(I/(H_tmp'*H_tmp+SNRd^(-1)*I));
+% end
+% order(Nt)=list(1);
+% symOut_current=G*y;
+% [symOut_current]=Rectangular_QAM_slicer(symOut_current, M, pav);
+H_r=[real(H), -imag(H); imag(H), real(H)];
+y_r=[real(y);imag(y)];
+[ symOut_current] = RSVR( H_r,  y_r, SNRd,  M, pav );
 symOut_prev=symOut_current;
 end
 
@@ -32,14 +51,21 @@ end
 %% weighted PIC
 % [W]=weightCal(G,SNRd, symOut_prev, symConstell);
 W=eye(Nt,Nt);
+symOut_tmp=symOut_prev;
 for i=1:Nt
[…]

### 2015-10-20 SVR for large MIMO/real SVR matlab/MIC_ordering_ascend_Recursive.m

@@ -1,9 +1,10 @@
-function [ symOut ] = MIC_Recursive(y, H, symOut_prev, SNRd, M, pav, stage, maxStage,W,G, symConstell)
+function [ symOut ] = MIC_ordering_ascend_Recursive(y, H, symOut_prev, SNRd, M, pav, stage, maxStage,W,G, symConstell, order)
 %Multistage Interference Cancellation (MIC) recursive algorithm
 %   Detailed explanation goes here
 % W is weight matrix with the diagonal elements represent the weight of
 % each estimation
 %is W is an identity matrix, that this is the original version MIC
+%the strongest data stream is detected firstly
 Nr=length(H(:,1)); %number of receive antennas
 Nt=length(H(1,:));  %number of transmit antennas
 I=eye(Nt);
@@ -14,6 +15,21 @@ symOut_current=zeros(Nt,1);
 if(stage==1)
 INV=(I/(H'*H+SNRd^(-1)*I));
 G=INV*H';
+D=diag(INV);
+[value, order]=sort(D,'ascend');
+% H_tmp=H;
+% G_tmp=INV;
+% order=zeros(Nt,1);
+% list=1:Nt;
+% for count=1:Nt-1
+%     [value, i]=max(diag(G_tmp));
+%     order(count)=list(i);
+%     H_tmp(:,i)=[];
+%     list(i)=[];
+%     I=eye(Nt-count);
+%     G_tmp=(I/(H_tmp'*H_tmp+SNRd^(-1)*I));
+% end
+% order(Nt)=list(1);
 symOut_current=G*y;
 [symOut_current]=Rectangular_QAM_slicer(symOut_current, M, pav);
 symOut_prev=symOut_current;
@@ -32,14 +48,18 @@ end
 %% weighted PIC
 % [W]=weightCal(G,SNRd, symOut_prev, symConstell);
 W=eye(Nt,Nt);
+symOut_tmp=symOut_prev;
 for i=1:Nt
-    symOut_tmp=symOut_prev;
-    symOut_tmp(i)=0;
-    y_tmp=y-H*W*symOut_tmp;
-    symOut_current(i)=((H(:,i)')/(H(:,i)'*H(:,i)+SNRd^(-1)))*y_tmp;
+    count=order(i);
+    W_t=W;
+    W_t(count,count)=0;
+    y_tmp=y-H*W_t*symOut_tmp;
[…]

### 2015-10-21 FCSD-CUDA project/parallel_acceleration_of_FCSD_based_on_cuda/conference draft.tex
revised version after acceptance 1
simulation result for MMSE MMSE-OSIC MMSE-AOMIC, MMSE-OMIC, RSVD, RSVD-OMIC

--- 2015-01-05 Parallel Acceleration of Fixed Complexity Sphere Decoder Based on GPU/conf_draft/conference draft.tex
@@
 \ref{BER curve} we present Monte Carlo simulation results for bit error rate (BER) performance, using the GPU implementation of different MIMO system configurations and constellation sizes.
-We consider uncoded complex MIMO systems with $M$QAM, where each antenna transmits different streams of binary data generated randomly and independently.
-The results have been obtained by using $100000$ channel realizations with at least $500$ symbol errors accumulated.
-The simulation results show that FCSD-CUDA provides the same BER performance as its CPU version\cite{barbero2008fixing}.
+We consider uncoded complex MIMO systems with $M$ QAM, where each antenna transmits different streams of binary data generated randomly and independently.
+The results have been obtained by using $10^{5}$ channel realizations with at least $500$ symbol errors accumulated.
+The simulation results show that FCSD-CUDA provides the same BER performance as its CPU version, due to the space limitation we do not present the results of CPU implementation, \cite{barbero2008fixing} provides some of the referable results.
 \begin{figure}[htb]
 \centering
-\includegraphics*[width=0.56\textwidth]{BER_curves.eps}
+\includegraphics*[width=0.5\textwidth, height=9.5cm]{BER_curves.eps}
 \caption{BER performance for MIMO systems with various modulation schemes using the GPU implementation}

### 2015-10-21 SVR for large MIMO/real SVR matlab/CSVR/MFB/communicationLine_MFB.m

@@ -1,0 +1,261 @@
+close all
+clear all
+% cd('F:\GitHub\Tianpei\SVR for large MIMO')
+tic
+%match filter bound
+% cd('/home/tchen44/Documents/spheredecodingtest/4X4')
+%% Signal Modulation and MIMO Channel modeling %% 
+M =4;         %size of constellation
+Nt=1;         %number of transmit antennas
+Nr=16;         %number of receive antennas
+% x=6;            %diversity gain that required
+SNR=[10:2:20];       %signal to noise ratio per bit in dB
+SNRd=10.^(SNR.*0.1);   %SNR in dicimal
+noiseV=1./SNRd;   %noise variance of AWGN 
+BER=zeros(length(SNR),1);         %bit error rate
+% numFlop=zeros(length(SNR),1);    %complexity of the algorithm
+SER1=zeros(length(SNR),1);  %symbol error rate of MIC
+% SER2=zeros(length(SNR),1); %symbol error rate of MMSE-OSIC
+% SER3=zeros(length(SNR),1); %symbol error rate of partial-MIC
+% SER4=zeros(length(SNR),1); %symbol error rate of ordered-MIC(ascend)
+% SER5=zeros(length(SNR),1); %symbol error rate of ordered-MIC(descend)
+% SER6=zeros(length(SNR),1); %symbol error rate of CSVD
+% SER7=zeros(length(SNR),1); %symbol error rate of RSVD aided ordered MIC
+pav=1;  %average symbol power
+[symConstell]=symbolConstellation( M, pav );
+
+%% generate files
+fid_t=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\MFB\data\README.txt','a');   %the file for explanations
+fprintf(fid_t, 'this is %d X %d MIMO\n', Nr, Nt);
+fprintf(fid_t, '%d QAM modulation\n', M);
+fprintf('\n');
+fprintf(fid_t, 'The detectors tested are\n');
+fprintf(fid_t, 'MFB-SER1\n');
+% fprintf(fid_t, 'RSVD-SER2\n');
+% fprintf(fid_t, 'MMSE-OSIC-SER3\n');
+% fprintf(fid_t, 'MMSE-OMIC(ascend)-SER4\n');
[…]

### 2015-10-21 SVR for large MIMO/real SVR matlab/CSVR/MMSE-AOMIC/64/16QAM/communicationLineMMSE_AOMIC_64_16.m

@@ -1,0 +1,283 @@
+close all
+clear all
+% cd('/home/tchen44/code/Tianpei/SVR for large MIMO/real SVR matlab/CSVR/MMSE-OSIC/32/4QAM')
+tic
+% cd('/home/tchen44/Documents/spheredecodingtest/4X4')
+%% Signal Modulation and MIMO Channel modeling %% 
+M =16;         %size of constellation
+Nt=64;         %number of transmit antennas
+Nr=64;         %number of receive antennas
+% x=6;            %diversity gain that required
+SNR=[10:2:28];       %signal to noise ratio per bit in dB
+SNRd=10.^(SNR.*0.1);   %SNR in dicimal
+noiseV=1./SNRd;   %noise variance of AWGN 
+BER=zeros(length(SNR),1);         %bit error rate
+% numFlop=zeros(length(SNR),1);    %complexity of the algorithm
+SER1=zeros(length(SNR),1);  %symbol error rate of MMSE-OSIC
+% SER2=zeros(length(SNR),1); %symbol error rate of MMSE-OSIC
+% SER3=zeros(length(SNR),1); %symbol error rate of partial-MIC
+% SER4=zeros(length(SNR),1); %symbol error rate of ordered-MIC(ascend)
+% SER5=zeros(length(SNR),1); %symbol error rate of ordered-MIC(descend)
+% SER6=zeros(length(SNR),1); %symbol error rate of CSVD
+% SER7=zeros(length(SNR),1); %symbol error rate of RSVD aided ordered MIC
+pav=1/Nt;  %average symbol power
+[symConstell]=symbolConstellation( M, pav );
+
+%% generate files
+fid_t=fopen('/home/tchen44/code/Tianpei/SVR for large MIMO/real SVR matlab/CSVR/MMSE-AOMIC/64/16QAM/data/README.txt','a');   %the file for explanations
+fprintf(fid_t, '\n');
+fprintf(fid_t, 'this is %d X %d MIMO\n', Nr, Nt);
+fprintf(fid_t, '%d QAM modulation\n', M);
+fprintf('\n');
+fprintf(fid_t, 'The detectors tested are\n');
+fprintf(fid_t, 'MMSE-AOMIC-SER1\n');
+% fprintf(fid_t, 'RSVD-SER2\n');
[…]

### 2015-11-09 Report Aug 5 2015/Report Aug 2015.tex
simulation result for MMSE MMSE-OSIC MMSE-AOMIC, MMSE-OMIC, RSVD, RSVD-OMIC
Thesis Introduction

@@
  \end{equation}
-This inequalities (also called saddle point conditions) yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
+These inequalities (also called saddle point conditions) holds if and only if KKT conditions holds (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}
+Therefore, KKT conditions are the necessary and sufficient conditions for optimality.
 In order to satisfy the first inequality in (\ref{KKT inequalities}), (\ref{original KKT condition1}) has to hold,

### 2015-11-09 Thesis Draft Tianpei Chen/Thesis Draft/C-CSVR.tex
Thesis Introduction

--- 2015-10-14 Report Aug 5 2015/Report Aug 2015.tex
@@
-%% bare_jrnl.tex
-%% V1.4a
-%% 2014/09/17
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8a or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
+\resetdatestamp
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_conf_compsoc.tex,
-%%                    bare_jrnl_compsoc.tex, bare_jrnl_transmag.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices and paper sizes can       ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-%\documentclass[journal]{IEEEtran}
-\documentclass[12pt, draftclsnofoot, onecolumn]{IEEEtran}
-%\documentclass[12pt,paper,final]{article}
-%
-%\documentclass[12pt, onecolummn]{report}
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
-
-\usepackage[latin1]{inputenc}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{fullpage}
-\usepackage{setspace}
-\usepackage{graphicx}
-%\usepackage[pdftex]{graphicx}
-\usepackage{psfrag}
-\usepackage{color}
-\usepackage{epsfig}
-%\usepackage{appendix}
-%\usepackage{caption}
-\usepackage{cite}
-\usepackage{ifpdf}
-\usepackage[cmex10]{amsmath}
-\usepackage{algorithm}
-\usepackage{array}
-\usepackage{stfloats}
-\usepackage{url}
-\usepackage{fixltx2e}
-\usepackage{setspace} 
-\usepackage{diagbox}
-\usepackage{subfigure}
-\usepackage{algpseudocode}
-\usepackage{multirow}
-\usepackage{calc}
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/tex-archive/info/epslatex/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-
-% *** FLOAT PACKAGES ***
-%
-\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Do not use the stfloats baselinefloat ability as IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-\begin{spacing}{2}
-%\doublespacing
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Report: Complex Support Vector Detector for Large MIMO System}
-
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-\author{Tianpei Chen\\
-Department of Electrical and Computer Engineering\\
-McGill University\\
-\today}
-
-%\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
-%        John~Doe,~\IEEEmembership{Fellow,~OSA,}
-%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-%\thanks{M. Shell is with the Department
-%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-%\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2014 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-%\begin{abstract}
-%The abstract goes here.
-%\end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-%\begin{IEEEkeywords}
-%IEEEtran, journal, \LaTeX, paper, template.
-%\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps.
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-%for IEEE journal papers produced under \LaTeX\ using
-%IEEEtran.cls version 1.8a and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-%I wish you the best of success.
-
-%\hfill mds
-
-%\hfill September 17, 2014
-  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment.
-The promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} and long-term evolution (LTE)\cite{3GLTE}.
-The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve spectrum efficiency) and diversity gain (better reliability of communication link) are obtained by exploiting the spatial domain.
-Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously.
-This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
-
-  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving ends.
-The uplink detector is one of the key components in a large MIMO system.
-With orders magnitude more antennas at the BS, benefits and challenges coexist in designing of detection algorithms for the uplink communication of large MIMO systems.
-On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexities of the algorithms become crucial to make the system practical.
-
-Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams.
-However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with the number of transmitted antennas, which is prohibitive for practical applications.
-
-As alternatives to MLD, linear detectors (LD) such as zero-forcing (ZF) and minimum mean square error (MMSE) with optimized ordering sequential interference cancellation (ZF-OSIC, MMSE-OSIC) are exploited in V-BLAST architecture\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast},  however the performance of ZF-OSIC and MMMSE-OSIC are inferior comparing to MLD.
-
-Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes the lattice structure of MIMO systems, which can achieve optimal performance with relatively much lower complexity comparing to MLD.
-However, SD has two major shortages that make it problematic to be integrated into a practical systems.
-The first shortage is SD has various complexities under different signal to noise ratios (SNR), while a constant processing data rate is required for hardware.
-The second shortage is the complexity of SD still has a lower bound that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
-The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different values of SNR.
-The FCSD inherits the principle of list based searching algorithms, which first generate a list of candidate symbol vectors and then the best candidate is chosen as the solution.
-The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC (sel-MMSE-OSIC)\cite{radji2009interference}.
-However, all these list based searching algorithms have the same shortage - their complexities increase exponentially with the number of transmit antennas and the order of modulation scheme\cite{radji2009interference}.
-Therefore, such algorithms are prohibitive when it comes to a large number of antennas or a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.
-
-%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
-Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of metaheuristic based detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance.
-such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
-Tabu search based algorithms which have superior performances compared to LAS detectors because of the efficient local minima exit strategy (e.g.
-Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g.
-Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g.
-Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) .
-Moreover, element based Lattice Reduction (LR) aided algorithms were also proposed to  large MIMO systems.\cite{zhou2013element}.
-
-Firmly grounded in framework of statistical learning theory, the Support Vector Machine (SVM) technique has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction.
-the SVM method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can provide good generalization performance\cite{scholkopf2002learning}.
-
-Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
-Moreover, the kernel based methods\cite{scholkopf2002learning} were proposed which solve nonlinear learning tasks by mapping input data samples into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
-This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS).
-Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.
-
-Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual form, which can be solved by Quadratic Programming (QP).
+\chapter{Complex Support Vector Preliminary Detector (CSVPD) for Large-Scale MIMO Uplink Systems}
 Decomposition methods were proposed to solve this QP problem by decomposing it into sub QP problems and solving them iteratively\cite{platt1999fast}.
@@
 The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
-
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
-
-\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
-\subsection{Regression Model}
-Suppose we are given a training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
-$y_{i}$ denotes output.
-Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Omega}$, $\Omega \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$, $\Omega=V$).
-The regression model (either linear or non-linear) is given by
-\begin{equation}
-y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1,2,\ldots, L
-\label{equation1}
-\end{equation}
-
-\begin{figure}
-\centering
-\def\svgwidth{\columnwidth}
-\input{epsilon-SVR.pdf_tex}
-\caption{$\epsilon$-Support Vector Regression and Risk Functional}
-\label{epsilon-SVR}
-\end{figure}
-
-We present the primal optimization problem directly
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}} f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-s.t. \left\{\begin{array}{ll}
-y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
-\epsilon_{i}, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
-\end{array}\right.
-\label{primal optimization problem}
-\end{IEEEeqnarray}
-In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the solid line represents the estimation of the input-output relation, the area between two dash lines ($\epsilon$-bound) is called $\epsilon$-tube.
-Only those data samples located outside $\epsilon$-tube contribute to the estimation error.
-Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with additive noise of observations, $R(u)$ denotes the cost function.
-The simplest cost function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}.
-For example if the noise is Gaussian distributed, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$.
-The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.
-
-In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
-Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-\label{definition of slack variable1}
-\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
-\label{definition of slack variable2}
-\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon).
-\end{IEEEeqnarray} 
-Because the distance between the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
-That is $\xi_{i}\hat{\xi}_{i}=0$.
-\subsection{Cost Function}\label{cost function}
-The optimal cost function in (\ref{primal optimization problem}) can be derived based on maximum likelihood (ML) principle.
-Assume the data samples $\mathbf{x}_{i}$ in data set are iid, Let $f_{true}(\mathbf{x}_{i}), i=1,2,\cdots L$ denotes true regression function.
-the underlying assumption is $y_{i}=f_{true}(\mathbf{x}_{i})+\xi_{i}, i=1,2,\cdots, L$, $\xi_{i}$ denotes additive noise of the $i$th data sample, with probability density function (pdf) $Pr(\cdot)$.
-Let $P(\cdot)$ denotes the pdf of $y_{i}$.
-Based on ML principle we want to
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{f}\quad \prod_{i=1}^{L}P(y_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}P(f(\mathbf{x}_{i})+\xi_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}Pr(\xi_{i})=\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))\\
-\label{cost function1}
-\end{IEEEeqnarray}
-Take the logarithm of $\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))$, we have
-\begin{IEEEeqnarray}[\relax]{l}
-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
-\label{cost function2}
-\end{IEEEeqnarray}
-maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i})))$, therefore (\ref{cost function1}) is equivalent to 
-\begin{equation}
-\min_{f}-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
-\label{cost function3}
-\end{equation}
-Let $c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))$ denotes the $i$th cost function, which is defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-\log(P(y_{i}-f(\mathbf{x}_{i}))).
-\label{cost function3}
-\end{IEEEeqnarray}
-Thus (\ref{cost function3}) can be rewritten as 
-\begin{equation}
-\min_{f}\quad  \sum_{i=1}^{L}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
-\label{Total risk function}
-\end{equation} 
-In $\epsilon$-SVR, in order to provide more flexibility to precision control, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{cost function3}).
-\begin{IEEEeqnarray}[\relax]{l}
-|u|_{\epsilon}=\left\{\begin{array}{ll}
-0   &if\quad |u|<\epsilon\\
-|u|-\epsilon  &otherwise\\
-\end{array}\right.
-\label{Vepsilon}
-\end{IEEEeqnarray}
-Thus the final form of cost function in $\epsilon$-SVR can be written as 
-\begin{equation}
-\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),
-\label{final cost function}
-\end{equation}
-Consider the cost function term in (\ref{primal optimization problem}),
-\begin{equation}
-\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))
-\end{equation}  
-the cost function term is determined according to the distribution of noise.  
-%where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as
-%\begin{equation}
-%minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f(\mathbf{x})),
-%\label{total cost function}
-%\end{equation} 
-%where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
-%\begin{equation}
-%minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
-%\label{final cost function}
-%\end{equation}
-%where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
-%\begin{eqnarray}
-%\nonumber
-%minimize \quad f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-%s.t. \left\{\begin{array}{ll}
-%y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
-%\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
-%\epsilon, \xi,\hat{\xi} &\geq 0\\
-%\end{array}\right.
-%\label{primal objective function}
-%\end{eqnarray}
-%where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered. 
-\subsection{Lagrange Duality}\label{section lagrange duality}
-According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier.
-The Lagrange function is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L(\mathbf{w}, b, \xi_{i}, \hat{\xi}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})=
-\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{L}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
-\nonumber
-+\sum_{i=1}^{L}\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\sum_{i=1}^{L}\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})\\
-s.t. \left\{\begin{array}{cc}
-\eta_{i}, \hat{\eta}_{i}, \alpha_{i}, \hat{\alpha}_{i}\geq 0, i=1,2,\cdots L\\
-\xi_{i}, \hat{\xi}_{i}\geq  0, i=1,2,\cdots L\\
-\end{array}\right.
-\label{lagrange duality1}
-\end{IEEEeqnarray}
-where $\eta_{i}$, $\hat{\eta}_{i}$, $\alpha_{i}$, $\hat{\alpha}_{i}$ are Lagrange multipliers.
-
-The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the primal constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
-Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.
-
-Assume a constraint optimization problem is given by 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}} \quad f(\mathbf{w})\\
-s.t. \quad c_{i}(\mathbf{w})\leq 0, i=1,2,\ldots L,
-\label{constraint optimization problem}
-\end{IEEEeqnarray}
-its Lagrange function is given by 
-\begin{equation}
-L(\mathbf{w}, \mathbf{a})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),
-\label{orginal Lagrange}
-\end{equation}
-where $\mathbf{a}=[a_{1},a_{2},\ldots, a_{L}]^{T}$ denotes the vector consist of Lagrange multipliers.
- Based on Theorem 6.21 in \cite{scholkopf2002learning}, a variable pair $[\bar{\mathbf{w}}, \bar{\mathbf{a}}]$ is the solution to (\ref{constraint optimization problem}) if and only if the following inequalities are satisfied
- \begin{equation}
- L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
- \label{KKT inequalities}
- \end{equation}
-This inequalities (also called saddle point conditions) yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{original KKT condition1}
-\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, \mathbf{a})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\
-\label{original KKT condition2}
-\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\
-\label{original KKT condition3}
-\bar{a}_{i}c_{i}(\bar{\mathbf{w}})=0, i=1,2,\ldots L
-\end{IEEEeqnarray}
-In order to satisfy the first inequality in (\ref{KKT inequalities}), (\ref{original KKT condition1}) has to hold,
-applying (\ref{original KKT condition1}) to (\ref{lagrange duality1}), which are  
-\begin{IEEEeqnarray}[\relax]{l}
-\label{partial1}
-\partial_{\mathbf{w}} L=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\
-\label{partial2}
-\partial_{\xi_{i}}L=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\
-\label{parial3}
-\partial_{\hat{\xi}_{i}}L=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\
-\label{partial4}
-\partial_{b}L=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber
-\end{IEEEeqnarray}
-Then by substituting (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}), (\ref{lagrange duality1}) can be rewritten as :
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha_{i}, \hat{\alpha}_{i})=\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[R(\xi_{i})+R(\hat{\xi}_{i})]-\sum_{i=1}^{L}[(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}\\
-\nonumber
-+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}[y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}]+\\
-\sum_{i=1}^{L}\hat{\alpha}_{i}[\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i}]
-\label{lagrange duality1 inter}
-\end{IEEEeqnarray}
-notice in (\ref{partial4}), $\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha}_{i})=0$, define $\tilde{R}(u)=R(u)-uR^{'}(u)$, (\ref{lagrange duality1 inter}) can be further simplified to
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i})]\\
-+\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
-\label{dual objective function1}
-\end{IEEEeqnarray}
-In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold.
-A $\mathbf{w}$ that satisfies the conditions in (\ref{original KKT condition2}) is in the feasible region defined by inequality constraints as mentioned (\ref{constraint optimization problem}).
-In $\epsilon$-SVR, this condition is satisfied by making use of the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ defined in (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}).
-Define that $\tilde{\mathbf{w}}$ is in the feasible region and satisfies the conditions in (\ref{original KKT condition1}), notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\tilde{\mathbf{w}}, \mathbf{a})$, thus yielding the dual optimization problem, which is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}}L(\tilde{\mathbf{w}},\mathbf{a})\equiv\max_{\alpha_{i}, \hat{\alpha}_{i}}\quad \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i}))\\
-+\sum_{i=i}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
-\label{dual optimization function2}
-\end{IEEEeqnarray}
-Define $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{L}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{L}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{L}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{L}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0, $\mathbf{R}_{\xi}=[\tilde{R}(\xi_{1}), \tilde{R}(\xi_{2}), \ldots, \tilde{R}(\xi_{L})]^{T}$, $\mathbf{R}_{\hat{\xi}}=[\tilde{R}(\hat{\xi}_{1}), \tilde{R}(\hat{\xi}_{2}), \ldots, \tilde{R}(\hat{\xi}_{L})]^{T}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes a component of data kernel matrix at $i$th row and $j$th column.
-An alternative vector form of (\ref{dual optimization function2}) can be written as
-\begin{equation}
-\max_{\mathbf{a}, \hat{\mathbf{a}}}\theta(\mathbf{a},\hat{\mathbf{a}})=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon \mathbf{e})^{T}\mathbf{a}+(-\mathbf{y}-\epsilon\mathbf{e})^{T}\mathbf{\hat{a}}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
-\label{dual objective alternative}
-\end{equation} 
-We define the following $2L$ vectors 
-$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2L}$, 
-\begin{IEEEeqnarray}[\relax]{l}
-[\mathbf{v}]_{i}=\left\{\begin{array}{ll}
-1\quad i=1,\ldots, l\\
--1\quad i=l+1,\ldots, 2l\\ 
-\end{array}\right.
-\end{IEEEeqnarray}
-(\ref{dual objective alternative}) can also be reformulate as 
-\newcommand{\mysmallarraydecl}{\renewcommand{%
-\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
-\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
-\renewcommand{\baselinestretch}{1.1}%
-\settowidth{\normalbaselineskip}{\scriptsize
-\hspace{\baselinestretch\baselineskip}}%
-\setlength{\baselineskip}{\normalbaselineskip}%
-\setlength{\jot}{0.25\normalbaselineskip}%
-\setlength{\arraycolsep}{2pt}}
-\begin{equation}
-\max_{\mathbf{a}^{*}}\quad \theta(\mathbf{a}^{*})=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\mathbf{K}& -\mathbf{K}\\
--\mathbf{K}& \mathbf{K}
-\end{IEEEeqnarraybox*}\right]
-\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
-\label{vectorize dual optimization function}
-\end{equation}
-
-Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor the proximity of the current solution and the optimal solution.
-Thus it can be used as a stopping criterion.
-In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
-(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
-(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
-\end{array}\right. 
-\label{KKT complimentary}
-\end{IEEEeqnarray}
-Based on the definitions of slack variables in (\ref{definition of slack variable1}) an (\ref{definition of slack variable2}), only when there is a outlier exists, $\xi_{i}$ or $\hat{\xi}_{i}$ can be non zero, that is
-\begin{equation}
-\xi_{i} or \hat{\xi}_{i}=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
-\label{definition of slack variable3}
-\end{equation} 
-because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $y_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig.
-\ref{epsilon-SVR}.
-Therefore at most one of $(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})$  and $(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})$ can be zero.
-In order to satisfy the KKT complementary conditions in (\ref{KKT complimentary}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
-
-Therefore the complete KKT complementary conditions of $\epsilon$-SVR is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
-(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
-(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
-\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots L
-\end{array}\right. 
-\label{complete KKT complimentary}
-\end{IEEEeqnarray}
-
-%The conditions in (\ref{KKT complimentary}) are called KKT complimentary condition. 
-%Obviously by taking partial derivations of (\ref{lagrange duality1}) with respect to $\mathbf{w}$, $\xi_{i}$, $\hat{\xi}_{i}$ and $b$, $\theta(\alpha_{i},\hat{\alpha}_{i})\leq \Theta(\mathbf{w},\alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})$, notice in $\theta(\alpha_{i}, \hat{\alpha}_{i})$ KKT conditions in (\ref{partial1}) to (\ref{partial4}) are satisfied.
-Therefore, KKT complimentary conditions (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
-Because
-%\begin{equation}
-%\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
-%\end{equation} 
-%where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
-%\begin{IEEEeqnarray}[\relax]{l}
-%g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
-%\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
-%l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
-%\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
-%\nonumber
-%\end{IEEEeqnarray}
-%Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$.
-when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied.
-hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds.
-Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.
-
-%In conclusion, the dual objective function can be written as
-
-\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
-\subsection{System Model}\label{system model}
-  Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna.
-The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
-Typically large MIMO systems have hundreds of antennas at the BS, as shown in Fig {\ref{large MIMO uplink model}}.
-  \begin{figure}[htb]
-  \centering
-  \def\svgwidth{\columnwidth}
-  %\includegraphics[scale=•]{•}
-  \input{largeMIMOuplink.pdf_tex}
-  \caption{Large MIMO uplink system }
-  \label{large MIMO uplink model}
-  \end{figure}
-
-Bit sequences, which are modulated to complex symbols, are transmitted by the users over a flat fading channel. The discrete time model of the system is given by:
-\begin{equation}
-\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{discrete time MIMO system}
-\end{equation}
-where $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
-BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
-The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian random variable with zero mean and unit variance.
-Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
-
-The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
-\subsection{Complex Regression Model}
- Based on the discrete time model of a large MIMO uplink system of (\ref{discrete time MIMO system}), our regression model is set such that the training data set at the detector are $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of matrix $\mathbf{H}$.
-This yields a regression task without offset $b$ in (\ref{equation1}) :
- \begin{IEEEeqnarray}[\relax]{l}
- y_{i}=f_{true}(\mathbf{h}_{i})+n_{i}, i=1,2\ldots L\\
- \label{regression part1a}
- f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\cdot\mathbf{s}, i=1,2,\ldots, L\\
- \label{regression part1b}
- \end{IEEEeqnarray}
- where $f_{true}()$ denotes the underlying true regression function, $n_{i}$ denotes discrete sample of additive noise.
-In this regression problem, received symbols $y_{i}$ are the observations, $\mathbf{h}_{i}$ are the input data samples, transmitted symbol vector $\mathbf{s}$ contains the regression coefficients.
-We employ complex support vector regression (CSVR) without offset term $b$.
-As shown in (\ref{original KKT condition1}) the first KKT condition is satisfied by finding the saddle point $\bar{\mathbf{w}}$ by taking paritial derivatives of $L(\mathbf{w},a_{i})$ with respect to $\mathbf{w}$.
-Mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) are employed to calculate partial derivatives of Lagrangian function of CSVR in complex manner\cite{bouboulis2011extension}.
-First we generalize our regression model by complex RKHS,
-Define a real RKHS $\mathcal{H}$, $<,>_{\mathcal{H}}$ denotes the corresponding inner product in $\mathcal{H}$.
-define complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $<,>_{\mathbb{H}}$ denotes the corresponding inner products in $\mathbb{H}$.
-Assume $\mathbf{x}, \mathbf{y},\mathbf{z}$ are complex vectors, $\mu$, $\chi$ $\in \mathbb{C}$, In general a complex Hilbert space $\mathbb{H}_{g}$ has the following properties
-\newtheorem{Lemma}{Lemma}
-\newtheorem{Property}{Property}
-\begin{Property}
- $<\mathbf{x},\mathbf{y}>_{\mathbb{H}_{g}}=(<{\mathbf{y},\mathbf{x}}>_{\mathbb{H}_{g}})^{*}$
-\label{CHSProperty1}
-\end{Property}
-
-\begin{Property}
-$<\mu\mathbf{x}+\chi\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}=\mu<\mathbf{x},\mathbf{z}>_{\mathbb{H}_{g}}+\chi<\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}$
-\label{CHSProperty2}
-\end{Property}
-
-\begin{Property}
-$<\mathbf{z}, \mu\mathbf{x}+\chi\mathbf{y}>_{\mathbb{H}_{g}}=\mu^{*}<\mathbf{z},\mathbf{x}>_{\mathbb{H}_{g}}+\chi^{*}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}_{g}}$
-\label{CHSProperty3}
-\end{Property}
-
-\begin{Lemma}
-Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{V}$, define a real RKHS $\mathcal{H}$ that satisfy $<\mathbf{a}, \mathbf{b}>_{\mathcal{H}}=\mathbf{a}^{T}\mathbf{b}$.
-For the corresponding complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $\mathbf{m}, \mathbf{l}\in \mathbb{C}^{V}$,
-$<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$
-\end{Lemma}
-
-\begin{proof} 
-$\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{V}$, and $\mathbf{g}=\Re{(\mathbf{g})}+\imath\Im{(\mathbf{g})}$, $\mathbf{h}=\Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}$.
-From Property \ref{CHSProperty1} and Property \ref{CHSProperty3},
-\begin{IEEEeqnarray}[\relax]{l}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(g)}+\imath\Im{(g)}, \Re{(h)}+\imath\Im{(h)}>_{\mathbb{H}}
-\label{CHSProperty4 inter1}
-\end{IEEEeqnarray}
-According to Property \ref{CHSProperty2}, (\ref{CHSProperty4 inter1}) can be rewritten as 
-\begin{equation}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath <\Im{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}},
-\label{CHSProperty4 inter2}
-\end{equation}
-According to Property \ref{CHSProperty3}
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-\imath <\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathbb{H}}+\imath (<\Im{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-
-\imath <\Im{(\mathbf{g})}, \\ \nonumber  \Im{(\mathbf{h})}>_{\mathbb{H}})
-=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}-<\Re{(\mathbf{g})},\\ \Im{(\mathbf{h})}>_{\mathbb{H}}]
-\label{CHSProperty4 inter2}
-\end{IEEEeqnarray}
-According to (\ref{CHSProperty4 inter2}), if $\mathbf{f}_{1}, \mathbf{f}_{2}\in \mathcal{H}$, we have  $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathbb{H}}=<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}$, furthermore because $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}=\mathbf{f}^{T}_{1}\mathbf{f}_{2}$, (\ref{CHSProperty4 inter2}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathcal{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}-<\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathcal{H}}]=\\
-\Re{(\mathbf{g})}^{T}\cdot \Re{(\mathbf{h})}+\Im{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}+\imath [\Im{(\mathbf{g})}^{T}\cdot  \Re{(\mathbf{h})}-\Re{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}]=\mathbf{g}\cdot \mathbf{h}^{*}
-\label{CHSequation2}
-\end{IEEEeqnarray}
-
-Therefore $<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}$.
-\end{proof}
-Therefore we have $<\mathbf{h}_{i}, \mathbf{s}^{*}>_{\mathbb{H}}=\mathbf{h}_{i}\cdot \mathbf{s}$, 
-For sake of simplicity we define $\mathbf{w}=\mathbf{s}^{*}$.
-Based on the same principle in the real case presented in section \ref{Introduce epsilon SVR}, the primal optimization problem of large MIMO detection in complex RKHS $\mathbb{H}$ defined by $<\mathbf{m}, \mathbf{l}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}^{*}$ can be formulated as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i}} \quad \frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]\\
-s.t. \left\{\begin{array}{ll}
-\Re{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{r}_{i}, i=1,2,\ldots, N_{r}\\
-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{r}_{i}, i=1,2,\ldots, N_{r}\\
-\Im{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{i}_{i}, i=1,2,\ldots, N_{r}\\
-\Im{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{i}_{i}, i=1,2,\ldots, N_{r}\\
-\xi^{r}_{i}, \hat{\xi}^{r}_{i},\xi^{i}_{i},\hat{\xi}^{i}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex objective function1}
-\end{IEEEeqnarray}
- Where $\Re{(\cdot)}$ and $\Im{(\cdot)}$ denote real and imaginary part of a complex variable and inequality constraints are set to real and imaginary part of the regression function separately.
-Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denote the kernel function, $\mathbf{K}=\Re{(\mathbf{K})}+\imath\Im{(\mathbf{K})}$, where $\Re{(\mathbf{K})}$ and $\Im{(\mathbf{K})}$ denote matrices of corresponding real and imaginary parts.
-Similar to the Lagrange duality rational in section \ref{section lagrange duality}, the Lagrange function associated with (\ref{complex objective function1}) is
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L=
-\frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]- \sum_{i=1}^{N_{r}}(\eta_{i}\xi^{r}_{i}+\hat{\eta}_{i}\hat{\xi}^{r}_{i}+\tau_{i}\xi^{i}_{i}\\\nonumber +\hat{\tau}_{i}\hat{\xi}^{i}_{i})
-+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{r}_{i})
-+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}(\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})\\
-\nonumber
-+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}(\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\Im{(y_{i})}-\epsilon-\hat{\xi}^{i}_{i})\\
-s.t. \left\{\begin{array}{ll}
-\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
-\xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i} \geq  0, i=1,2,\ldots, N_{r}
-\end{array}\right. 
-\label{complex lagrange duality1}
-\end{IEEEeqnarray}
-where $\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}$ are Lagrange multipliers.
-In order to calculate the partial derivations of $L$ with respect to $\mathbf{w}$ which is defined in complex domain, the Wirtinger's calculus is exploited\cite{bouboulis2011extension} , Therefore we have
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-\frac{\partial L}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{i=1}^{N_{r}}\alpha_{i}\mathbf{h}_{i}+\frac{1}{2}\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\mathbf{h}_{i}+\frac{\imath}{2}(\sum_{i=1}^{N_{r}}\beta_{i}\mathbf{h}_{i}-\sum_{i=1}^{N_{r}}\hat{\beta}_{i}\mathbf{h}_{i})=0\\
-\Rightarrow \mathbf{w}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-\imath\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\\
-\frac{\partial L}{\partial \xi^{r}_{i}}=CR^{'}(\xi^{r}_{i})-\eta_{i}-\alpha_{i}=0\Rightarrow \eta_{i}=CR^{'}(\xi^{r}_{i})-\alpha_{i}\\
-\frac{\partial L}{\partial \hat{\xi}^{r}_{i}}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\Rightarrow \hat{\eta}_{i}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\alpha}_{i}\\
-\frac{\partial L}{\partial \xi^{i}_{i}}=CR^{'}(\xi^{i}_{i})-\tau_{i}-\beta_{i}=0\Rightarrow \tau_{i}=CR^{'}(\xi^{i}_{i})-\beta_{i}\\
-\frac{\partial L}{\partial \hat{\xi}^{i}_{i}}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\tau}_{i}-\hat{\beta}_{i}=0\Rightarrow \hat{\tau}_{i}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\beta}_{i}\\
-
-\end{array}\right.
-\label{complex lagrange duality2}
-\end{IEEEeqnarray}
-Based on (\ref{complex lagrange duality2}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}\\
-\nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\\nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\\ \sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}),
-\label{complex duality regression function}
-\end{IEEEeqnarray}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
-+i(\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}-\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}\mathbf{h}^{H}_{i})
-\label{complex duality regularization1}
-\end{IEEEeqnarray}
-Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$. If we have $r_{i}$, $r_{j}$ $\in \mathbb{R}$, then 
-\begin{equation}
-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ji}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij},
-\end{equation}
-Therefore
-\begin{equation}
-\sum_{i,j}^{l}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=0,
-\label{conjugate1}
-\end{equation}
-Based on (\ref{conjugate1}), (\ref{complex duality regularization1}) can be changed to
-\begin{equation}
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}.
-\label{complex duality regularization2}
-\end{equation}
-Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), we have
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L=\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}]+\\
-\nonumber
-C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})]- \sum_{i=1}^{N_{r}}((CR^{'}(\xi^{r}_{i})-\alpha_{i})\xi^{r}_{i}+(CR^{'}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}^{r}_{i}+(CR^{'}-\beta_{i})\xi^{i}_{i}\\\nonumber +(CR^{'}(\hat{\xi}_{i})-\hat{\beta}_{i})\hat{\xi}^{i}_{i})+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\epsilon-\xi^{r}_{i})
-+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\\ \nonumber
-((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})
-+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\\ \nonumber
-\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\Im{(y_{i})}-\\
-\epsilon-\hat{\xi}^{i}_{i})
-\label{complex lagrange duality inter1}
-\end{IEEEeqnarray}
-
-Then simplify (\ref{complex lagrange duality inter1}), we obtain
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L\equiv\theta=-\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}]+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})-\xi_{i}^{r}R^{'}(\xi^{r}_{i})\\\nonumber
-+R(\hat{\xi}^{r}_{i})-\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})-\xi_{i}R^{'}(\xi_{i}^{i})+R(\hat{\xi}^{i}_{i})-\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]+\sum_{i=1}^{N_{r}}[\Re{(y_{i})}(\alpha_{i}-\hat{\alpha}_{i})+\Im{(y_{i})}(\beta_{i}-\hat{\beta}_{i})]-\\
-\epsilon\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta_{i}+\hat{\beta}_{i})
-\label{complex lagrange duality inter2}
-\end{IEEEeqnarray}
-define $\tilde{R}(u)=R(u)-uR^{'}(u)$. Similar to (\ref{dual optimization function2}), The dual optimization problem of a complex MIMO system is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}}\quad \theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
-\nonumber
--\sum_{i}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta+\hat{\beta}_{i})\epsilon+[\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})]\\
-\nonumber
-+C\sum_{i}^{N_{r}}(\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i}))\\ 
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{final complex lagrange duality}
-\end{IEEEeqnarray}
-Notice in (\ref{final complex lagrange duality}), there is no correlation term between $\alpha_{i}, \hat{\alpha}_{i}$ and $\beta_{i}, \hat{\beta}_{i}$, therefore, (\ref{final complex lagrange duality}) can be divided into two independent regression tasks, which are given by
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}} \quad \theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
-\nonumber
-+\tilde{R}(\hat{\xi}^{r}_{i}))\\
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{complex duality real part}
-\end{IEEEeqnarray}
-and 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\beta_{i}, \hat{\beta}_{i}} \quad \theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
-\nonumber
-+\tilde{R}(\hat{\xi}^{i}_{i}))\\
-\left\{\begin{array}{ll}
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{complex duality imaginary part}
-\end{IEEEeqnarray}
-Let $\mathbf{a}=[\alpha_{1}, \alpha_{2},\ldots, \alpha_{N_{r}}]^{T}$, $\mathbf{\hat{a}}=[\hat{\alpha}_{1}, \hat{\alpha}_{2},\ldots, \hat{\alpha}_{N_{r}}]^{T}$, $\mathbf{b}=[\beta_{1}, \beta_{2},\ldots, \beta_{N_{r}}]^{T}$,$\mathbf{\hat{b}}=[\hat{\beta}_{1}, \hat{\beta}_{2},\ldots, \hat{\beta}_{N_{r}}]^{T}$, $\mathbf{R}^{r}=[\tilde{R}(\xi^{r}_{1})+\tilde{R}(\hat{\xi}^{r}_{1}), \tilde{R}(\xi^{r}_{2})+\tilde{R}(\hat{\xi}^{r}_{2}), \ldots, \tilde{R}(\xi^{r}_{N_{r}})+\tilde{R}(\hat{\xi}^{r}_{N_{r}})]^{T}$, $\mathbf{R}^{i}=[\tilde{R}(\xi^{i}_{1})+\tilde{R}(\hat{\xi}^{i}_{1}), \tilde{R}(\xi^{i}_{2})+\tilde{R}(\hat{\xi}^{i}_{2}), \ldots, \tilde{R}(\xi^{i}_{N_{r}})+\tilde{R}(\hat{\xi}^{i}_{N_{r}})]^{T}$, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$.
-The alternate form can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a},\mathbf{\hat{\mathbf{a}}}} \quad \theta^{r}=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\Re{(\mathbf{K})}(\mathbf{a}-\mathbf{\hat{a}})+\Re{(\mathbf{y})}^{T}(\mathbf{a}-\mathbf{\hat{a}})-\epsilon(\mathbf{e}^{T}(\mathbf{a}+\mathbf{\hat{a}}))+C(\mathbf{e}^{T}\mathbf{R}^{r})\\
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex duality real part vectorizes}
-\end{IEEEeqnarray}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{b}, \mathbf{\hat{b}}} \quad \theta^{i}=-\frac{1}{2}(\mathbf{b}-\mathbf{\hat{b}})^{T}\Re{(\mathbf{K})}(\mathbf{b}-\mathbf{\hat{b}})+\Im{(\mathbf{y})}^{T}(\mathbf{b}-\mathbf{\hat{b}})-\epsilon(\mathbf{e}^{T}(\mathbf{b}+\mathbf{\hat{b}}))+C(\mathbf{e}^{T}\mathbf{R}^{i})\\
-\left\{\begin{array}{ll}
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex duality imaginary part vectorized}
-\end{IEEEeqnarray}
-
-Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), where only the real part of the kernel matrix is required for each channel.
-This can provide computational advantages for solving the dual optimization problems.
-\section{Work Set Selection and Solver}\label{WSS}
- As we can see, a quadratic optimization problem is formulated in (\ref{final complex lagrange duality}).
-The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with a large data set.
-
-Decomposition methods are a set of efficient algorithms that can help to ease this difficulty.
-Decomposition methods work iteratively, and are based on choosing a subset of optimization variables $S$ (named work set) to be updated in each iteration step, while keeping the rest variables $N$ fixed.
-Sequential Minimal Optimization (SMO) is an extreme case of decomposition method, where the work set size is 2, and an analytic quadratic programming (QP) step instead of numerical QP step can be performed in each iteration.
-
-Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) have the same structure, in this section we discuss the real part only.
-By dividing the variables into work set $S$ and fixed set $N$.
-Therefore, the vector $\mathbf{a}$ in (\ref{complex duality real part vectorizes}) can be divided into two sub vectors $[\mathbf{a}_{S}, \mathbf{a}_{N}]$.
-thereafter $\mathbf{a}_{S}$ denotes a vector that consists of the components of $\mathbf{a}$ that belongs to set $S$, the same modifications are applied to $\mathbf{\hat{a}}$ and $\mathbf{y}$.
-Thus (\ref{complex duality real part vectorizes}) can be rewritten as:
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}, \mathbf{a}_{N}, \hat{\mathbf{a}}_{N}} \theta= -\frac{1}{2}[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
-\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]+[\Re{(\mathbf{y}_{S})}^{T}, \Re{(\mathbf{y}_{N})}^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]-\\\nonumber\epsilon[\mathbf{e}^{T}_{S}, \mathbf{e}^{T}_{N}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}+\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]+C(\mathbf{e}^{T}, \mathbf{R}^{r})
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{real part decomposition inter1}
-\end{IEEEeqnarray}
-
-Where $\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
-\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of the components in $\Re(\mathbf{K})$ that belong to both of the rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\mathbf{K}$ is a Hermitian matrix, thus $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}, \mathbf{\hat{a}}}\quad \theta^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})+2(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]
-+\Re{(\mathbf{y}_{S}^{T})}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\
-\nonumber
-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S}))
--\frac{1}{2}(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NN}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})+\Re{(\mathbf{y}_{N}^{T})}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{N}+\mathbf{\hat{a}}_{N}))\\\nonumber+C(\mathbf{e}^{T}(\mathbf{R}^{r}),
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{real part decomposition}
-\end{IEEEeqnarray}
-In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is considered i.e 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}_{S}, \mathbf{\hat{a}}_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]+[Re(\mathbf{y}_{S}^{T})-(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\mathbf{K}_{NS}^{r}
-](\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\\nonumber\epsilon<\mathbf{e}^{T}, (\mathbf{a}_{S}+\mathbf{\hat{a}}_{S})>,
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}_{S}]_{i}([\hat{\mathbf{a}}_{S}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i\in S\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i\in S\\
-\end{array}\right.
-\label{subset optimization}
-\end{IEEEeqnarray}
-A proper work set selection strategy is required so that speed and performance requirement can be guaranteed.
-One idea is to perform update to optimization variables that violate the KKT complementary conditions, which, based on (\ref{complete KKT complimentary})
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
-\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, L\\
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, L\\
-\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots, L
-\end{array}\right.
-\label{complementary KKT condition1}
-\end{IEEEeqnarray}
-According to Osuna's theorem\cite{osuna1997improved}, the final convergence can be guaranteed.
-In SMO algorithm, heuristic methods are used to find a work set of size two in order to accelerate the decomposition process\cite{platt1999fast}.
-The heuristic method first searches among the non-bound variables (that is $0<\alpha_{i}<C\tilde{R}(\xi^{r}_{i})$ and $0<\hat{\alpha}_{i}<C\tilde{R}(\hat{\xi}_{i})$), which are more likely to violate the complementary KKT conditions, Then searching the whole dual variable set.
-The second dual variable that can maximize optimization step size is chosen.
-An approximate step size is used as evaluator for sake of reducing computational cost.
-
-Another idea for work set selection is to choose the optimization variables whose update can provide the maximum improvement to the sub dual objective functions.
-The improvement of the sub dual objective function is
-\begin{equation}
-\bigtriangledown \theta^{r}_{S}=\theta^{r}_{S}((\mathbf{a}_{S}+\Delta_{S}), (\hat{\mathbf{a}}_{S}+\hat{\Delta}_{S}))-\theta^{r}_{S}(\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}),
-\label{maximum gain work set selection}
-\end{equation} 
-where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\hat{\Delta}_{S}=\hat{\mathbf{a}}_{S}^{new}-\hat{\mathbf{a}}_{S}$, $\mathbf{a}^{new}_{S}$ and $\hat{\mathbf{a}}^{new}_{S}$ are the updates of $\mathbf{a}_{S}$ and $\hat{\mathbf{a}}_{S}$.
-$\bigtriangledown \theta_{S}^{r}$ in (\ref{maximum gain work set selection}),  based on (\ref{subset optimization}), can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\\\nonumber\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+\{\Re{(\mathbf{y}^{T}_{S})}-[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\\
-\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}]\}(\Delta_{S}-\hat{\Delta}_{S})
--\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S}),
-\label{gain work set selection1}
-\end{IEEEeqnarray} 
-where we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}=[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}\\
-\Re{(\mathbf{K})}_{NS}
-\end{IEEEeqnarraybox*}\right]=\\
-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S},
-\label{modification of gain work set selection}
-\end{IEEEeqnarray}
-where $\Re{(\mathbf{K})}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns corresponding to the work set $S$.
-Therefore, (\ref{gain work set selection1}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}]
-(\Delta_{S}-\hat{\Delta}_{S})
--\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta_{S}+\hat{\Delta}_{S}),
-\label{gain of work set selection1 inter}
-\end{IEEEeqnarray}
-define intermediate variable vector $\Phi^{r}, \Phi^{i}\in \mathbb{R}^{N_{r}}$, $\Phi^{r}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Phi^{i}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$.
-Let $\Phi_{S}$ denote the vector that consists of the components in $\Phi$ that corresponding to $S$.
-Thus (\ref{gain of work set selection1 inter}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+(\Phi^{r}_{S})^{T}(\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta_{S}+\hat{\Delta}_{S})
-\label{gain work set selection2}
-\end{IEEEeqnarray} 
-Because the offset term is omitted in the large MIMO regression model, therefore different from SMO type algorithms, there is no linear equality constraint, which is inducted by offset $b$, as shown in (\ref{partial4}).
-Therefore the size of work set can be less than two.
-However, more efficient work set selection strategies based on maximal sub dual objective gain selection, is proposed in \cite{steinwart2011training}.
-A work set of size two is updated in each iteration.
-The computational cost is reduced while maintaining the comparable performance with the model with offset term.
-In the CSVR large MIMO detector, the work set selection strategy in \cite{steinwart2011training} is exploited.
-Basically, in each iteration this strategy uses the combined single variable searchings, whose searching time is $O(n)$, where $n$ is the number of data samples, to determine a work set of size two.
-On the one hand, this strategy can find a work set of size two, whose update approximately maximize the gain of the dual sub objective function.
-On the other hand, the brute-force searching for the work size of two, whose update can maximize the gain of the sub dual objective function, requires $O(n^{2})$ searching time.
-The former strategy requires as few iterations as the latter one, since in each iteration, the latter strategy is more computationally expensive, the former one can enjoy significantly faster running speed.
-\subsection{Single Direction (1-D) Solver}\label{single direction solver}
-Recall the KKT complementary conditions 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{KKT complementary1}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary2}
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary3}
-\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary4}
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary5}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq R^{'}(\xi^{r}_{i})(R^{'}(\hat{\xi}_{i})), i=1,2,\ldots, N_{r} 
-\end{IEEEeqnarray}
-Recall the discussions of slack variables by (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}) in section \ref{section lagrange duality}.
-we have $\xi^{r}_{i}\hat{\xi}^{r}_{i}=0$.
-similar to the definitions in (\ref{definition of slack variable3}), we have
-\begin{equation}
-\xi^{r}_{i} or \hat{\xi}_{i}^{r}=|\Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}|_{\epsilon},
-\label{definition of complex slack variables}
-\end{equation} 
- therefore in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})$ and  $(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})$ can be non zero, therefore in order to satisfy equalities (\ref{KKT complementary3}) and (\ref{KKT complementary4}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
-
- Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is changed to the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.
-
-  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of the sub dual objective function is chosen as the work set in each iteration.
-Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]^{T}$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]^{T}$.
-Substitute $\mathbf{a}, \hat{\mathbf{a}}$ with $\Lambda$ and using $\Sigma$.
-Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2}) can be rewritten as
-  \begin{equation}
-\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y}_{S}^{T})}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
-]\Lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\Lambda_{S}|>,
-\label{subset optimization lambda}
-\end{equation}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
-\label{gain work set selection lambda}
-\end{IEEEeqnarray} 
-In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
-\begin{IEEEeqnarray}[\relax]{l}
- \max_{\tilde{\lambda}^{new}_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\tilde{\lambda}_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
-+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\tilde{\lambda}_{m}^{new}-\epsilon(|\tilde{\lambda}^{new}_{m}|),
- \label{optimization function 1-D}
- \end{IEEEeqnarray}
- where $\tilde{\lambda}^{new}_{m}$ is the update of $\lambda_{m}$.
- Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Phi^{r}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$ in the imaginary channel, $\Phi_{i}^{i}=\Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$.
-Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
-Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))
-\label{partial optimization function 1-D lambda}
-\end{IEEEeqnarray} 
-where $\Re(y_{m})-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re(\mathbf{K})_{mj}=\Re(y_{m})-\sum_{j=1}^{N_{r}}\lambda_{j}\Re(\mathbf{K}_{mj})=\Phi^{r}_{m}+\lambda_{m}\Re(\mathbf{K}_{mm})$
-and $\lambda_{m}$ denotes the $m$th optimization variable before update. Therefore (\ref{partial optimization function 1-D lambda}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\frac{\partial \theta^{r}_{m}}{\partial \tilde{\lambda}_{m}^{new}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
-\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Phi^{r}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
-\end{IEEEeqnarray}
- The update of $\tilde{\lambda}^{new}_{m}$ is completed by clipping based on (\ref{KKT complementary5})
-\begin{IEEEeqnarray}[\relax]{l}
-\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
-\label{clipped new dual variable}
-\end{IEEEeqnarray}
-
-where $[ ]_{a}^{b}$ denotes clipping function 
-\begin{IEEEeqnarray}[\relax]{l}
-[x]_{a}^{b}=\left\{\begin{array}{ll}
-a \quad if\quad  x\leq a\\
-x \quad if\quad a<x<b\\
-b \quad if\quad x\geq b\\
-\end{array}\right.
-\label{clipping function}
-\end{IEEEeqnarray}
-based on (\ref{gain work set selection lambda}), The maximal gain of the sub dual objective function with respect to the $m$th optimization variable is 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{m}^{r}=\theta_{m}^{r}(\lambda_{m}+\sigma_{m})-\theta_{m}^{r}(\lambda_{m})\\
-\nonumber
-=-\frac{1}{2}\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}\sigma_{m}-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)\\
-=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|),
-\label{gain of 1-D objective function}
-\end{IEEEeqnarray}
-In 1-D searching procedure, the optimization variable whose update can achieve the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, based on the this principle
-\begin{equation}
-k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r}.
-\label{1-D direction}
-\end{equation}
-Notice in (\ref{partial optimization function 1-D lambda}), $sgn(\tilde{\lambda}^{new}_{m})$ is unknown before $\lambda_{m}$ is updated, therefore two conditions $sgn(\tilde{\lambda}^{new}_{m})=1$ and $sgn(\tilde{\lambda}^{new}_{m})=-1$ are considered.
-The final decision of $sgn(\tilde{\lambda}_{m}^{new})$ is made by comparing the corresponding gains of the sub dual objective functions in (\ref{gain of 1-D objective function}).
-\subsection{Double Direction (2-D) Solver}\label{double direction solver}
-Although the omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however, recent work in \cite{steinwart2011training} shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained.
-The optimal 2-D solver uses the same principle as 1-D solver, $|S|=2$, assume the work set consists of the $m$th and $n$th optimization variables, that are $\Lambda_{S}=[\lambda_{m}, \lambda_{n}]$.
-Based on (\ref{gain work set selection lambda}), the sub dual objective function can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\lambda_{m}, 
-\lambda_{n}}\quad \theta^{r}_{m,n}=-\frac{1}{2}[(\tilde{\lambda}^{new}_{m})^{2}\Re{(\mathbf{K})}_{mm}+(\tilde{\lambda}^{new}_{n})^{2}\Re{(\mathbf{K})}_{nn}+2\tilde{\lambda}^{new}_{m}\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}]-\\
-\nonumber
-\tilde{\lambda}^{new}_{m}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\tilde{\lambda}^{new}_{n}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{m})}\tilde{\lambda}^{new}_{1}+\Re{(\mathbf{y}_{n})}\tilde{\lambda}^{2}_{n}\\
--\epsilon(|\lambda^{new}_{m}|+|\tilde{\lambda}_{n}^{new}|), 
-\label{2-D solver}
-\end{IEEEeqnarray}
-Based on (\ref{2-D solver}), the partial derivatives of $\theta^{r}_{m,n}$ with respect to $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}_{n}^{new}$ are 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\label{lambda1 partial}
-\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}+\Re{(\mathbf{y}_{m})}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=\\
--\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{m}+\lambda_{m}\Re{\mathbf{K}}_{mm}+\lambda_{n}\Re{(\mathbf{K})}_{mn}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=0\\
-\nonumber
-\label{lambda2 partial}
-\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{n}}=-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{n})}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=\\
--\tilde{\lambda}_{n}^{new}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{n}+\lambda_{m}\Re{(\mathbf{K})}_{mn}+\lambda_{n}\Re{(\mathbf{K})}_{nn}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=0\\
-\nonumber
-\label{partial derivative sample1}
-\end{IEEEeqnarray}
-where $\frac{\partial |x|}{\partial x}=sgn(x)$ denotes the sign of $x$. Based on (\ref{lambda1 partial}) and (\ref{lambda2 partial}) we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{post partial lambda1}
-(\tilde{\lambda}^{new}_{m}-\lambda_{n})\Re{(\mathbf{K})}_{mm}=\Phi^{r}_{m}-\epsilon sgn(\tilde{\lambda}^{new}_{m})-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{mn}\\
-\label{post partial lambda2}
-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{nn}=\Phi^{r}_{n}-\epsilon sgn(\tilde{\lambda}^{new}_{n})-(\tilde{\lambda}^{new}_{m}-\lambda_{m})\Re{(\mathbf{K})}_{mn}\\
-\nonumber
-\end{IEEEeqnarray}
-hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formulas of $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}^{new}_{n}$ are given by
-\begin{equation}
-\tilde{\lambda}^{new}_{m}=\lambda_{m}+\frac{\Phi^{r}_{m}\Re{(\mathbf{K})}_{nn}-\Phi^{r}_{n}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{nn}-sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
-\label{update lambda1}
-\end{equation}
-
-\begin{equation}
-\tilde{\lambda}^{new}_{n}=\lambda_{n}+\frac{\Phi^{r}_{n}\Re{(\mathbf{K})}_{mm}-\Phi^{r}_{m}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mm}-sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
-\label{update lambda2}
-\end{equation} 
-Then the updated optimization variables are clipped by constraint based on (\ref{KKT complementary5})
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\lambda_{i}^{new}=[\tilde{\lambda}_{i}^{new}]^{CR^{'}(\xi_{i})}_{-CR^{'}(\xi_{i})},\\
-i=m,n
-\label{cipped optimization variable}
-\end{IEEEeqnarray}
-Based on (\ref{gain work set selection2}),  the gain of the sub dual objective function can be written as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=-\frac{1}{2}[\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\sigma_{n}^{2}\Re{(\mathbf{K})}_{nn}+2\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn}]+\Phi^{r}_{m}\sigma_{m}+\Phi^{r}_{n}\sigma_{n}\\
--\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|+|\lambda^{new}_{n}|-|\lambda_{n}|),
-\label{gain of 2-D objective function1}
-\end{IEEEeqnarray}
-assume the $i$th and $j$th optimization variables are chosen, the optimization variables in 2-D solver have the same update rule as that of 1-D solver, that is 
-\begin{equation}
-[i,j]=\arg\max_{m,n=1,2,\ldots, N_{r}}\bigtriangledown \theta_{m,n}^{r}.
-\label{dual optimization variables}
-\end{equation}
-
-Similar to single direction solver, notice in (\ref{update lambda1}) and (\ref{update lambda2}), $sgn(\tilde{\lambda}^{new}_{m})$ and $sgn(\tilde{\lambda}^{new}_{n})$ are unknown before $\lambda_{m}$ and $\lambda_{n}$ are updated, therefore four conditions are considered
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=-1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=-1
-\label{four conditions of sign}
-\end{IEEEeqnarray} 
-The final decisions of $sgn(\tilde{\lambda}_{m}^{new})$ and $sgn(\tilde{\lambda}_{n}^{new})$ are made by comparing the corresponding possible gains of the sub objective functions in (\ref{gain of 2-D objective function1}).
-
-Modify (\ref{gain of 2-D objective function1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)+\sigma_{n}[-\frac{1}{2}\sigma_{n}\Re{(\mathbf{K})}_{nn}+\Phi^{r}_{n}]-\epsilon(|\lambda^{new}_{n}|-|\lambda_{n}|)\\
--\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn},
-\end{IEEEeqnarray}
-then recall the gain of the sub dual objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
- \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta^{r}_{ij}=\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}-\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij},
-\label{gain of 2-D objective function2}
-\end{IEEEeqnarray}
-where $\bigtriangledown \theta^{r}_{i}$, $\bigtriangledown \theta^{r}_{j}$ denote gains of the sub dual objective functions of 1-D solver with $i$th and $j$th optimization variables are updated. 
-\subsection{Approximation of Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
-From (\ref{gain of 2-D objective function1}), we can observe that the gain of the sub dual objective function of 2-D solver is a summation of the gains of the sub dual objective functions of two independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}$.
-
-The optimal 2-D work set $[i,j]$ can be determined by brute-force searching manner, which requires $O(n^{2})$ searching times.
-Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D searching strategy by the combinations of optimal 1-D searching approach, we will prove in the large MIMO systems, when $N_{t}$ is sufficient large, this approximation is very effective.
-Here we propose two types of combined 1-D searching strategy:
-\subsubsection{ One-shot 1-D combined Searching}
-do one round 1-D searching and calculate all the 1-D gains based on (\ref{gain of 1-D objective function}), then choose the two optimization variables indexed by $i$ and $j$, whose update can achieve the first and the second largest gain of the sub dual objective functions.
-\subsubsection{ Sequential 1-D combined Searching}
-do two rounds 1-D searchings, in the first round find optimization variable indexed by $i$ whose update can achieve the maximal 1-D gain of the sub dual objective functions based on (\ref{gain of 1-D objective function}), then update the $i$th optimization variable.
-In the second round, find $j$th optimization variable whose update can achieve the maximal 1-D gain of the sub dual objective functions.
-
- The effectiveness of 1-D approximation strategies are majorly determined by the ratio $\frac{\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}}{\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}}$.
-Hence we provide theoretical analyses based on the view of channel hardening phenomenon.
-It can be proved that in the large MIMO systems, the correlation term $\sigma_{i}\sigma_{j}\Re(\mathbf{K}_{ij})$is ignorable comparing to 1-D gains of the sub objective function.
-Prior to the theoretical analyse, we first investigate some mathematical properties of channel hardening (to be completed).
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
-%\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
-%\label{figure1}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
-%\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
-%\label{figure2}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[scale=0.6]{NtE.eps}
-%\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
-%\label{figure3}
-%\end{figure}
-
-\section{Stopping Criteria}\label{stopping criteria}
-As discussed in section\ref{section lagrange duality}, in dual objective function, the complementary KKT conditions are the measurement of the proximity of current solution to the optimal solution. 
-The feasibility gap, which is a effective stopping criteria used in SVR and SVM, can implicitly monitor whether the KKT complementary conditions are satisfied.
-The feasibility gap measures the gap between the values of primal objective function and dual objective function.
-To elaborate a little further, recall the saddle point conditions in section\ref{section lagrange duality}
- \begin{equation}
- L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
- \label{saddle point conditions}
- \end{equation}
-Where $(\bar{\mathbf{w}}, \bar{\mathbf{a}})$ are the solution to primal objective function, the KKT complementary conditions are satisfied, that is 
-\begin{equation}
-\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=0,
-\label{complementary KKT condition revisited}
-\end{equation}
-we have 
-\begin{equation}
-L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=f(\bar{\mathbf{w}})+\sum_{i=1}^{N_{r}}\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=f(\bar{\mathbf{w}})
-\end{equation} 
-Let $(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$ denote the variable pair that satisfies the first and second KKT conditions in (\ref{original KKT condition1} ) and (\ref{original KKT condition2})
-
-\begin{IEEEeqnarray}[\relax]{l}
-\label{original KKT condition revisited1}
-\partial_{\mathbf{w}}L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=\partial_{\mathbf{w}}f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{a}_{i}\partial_{\mathbf{w}}c_{i}(\tilde{\mathbf{w}})=0,\\
-\label{original KKT condition revisited2}
-c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots L
-\end{IEEEeqnarray}
-based on (\ref{original KKT condition revisited1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq f(\tilde{\mathbf{w}}),
-\end{IEEEeqnarray} 
-based on Theorem 6.27\cite{scholkopf2002learning}, the following equalities hold
-\begin{IEEEeqnarray}[\relax]{l}
-f(\tilde{\mathbf{w}})\geq f(\bar{\mathbf{w}})=L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})
-\label{inequality gap}
-\end{IEEEeqnarray}
-Therefore the feasibility gap is defined by the gap between the primal objective function $f(\tilde{\mathbf{w}})$ and the dual objective function $L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$   
-\begin{equation}
-f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\geq 0
-\label{original feasibility gap}
-\end{equation}
-If the feasibility gap is vanished, based on (\ref{inequality gap}), we have $f(\bar{\mathbf{w}})=f(\tilde{\mathbf{w}})$, thus $\tilde{\mathbf{w}}=\bar{\mathbf{w}}$, $\tilde{\mathbf{a}}=\bar{\mathbf{a}}$.
-Furthermore, because $f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})$, the vanish of feasibility gap indicates $\sum_{i=1}^{L}\tilde{\mathbf{a}}c_{i}(\tilde{\mathbf{w}})=0$.
-Because $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots, L$, we have $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})=0, i=1,2,\ldots, L$, the KKT complementary conditions are satisfied.
-
-In CSVR detector for the large MIMO systems, the primal objective function is
-\begin{equation}
-f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal inter}
-\end{equation}
-where $\tilde{\mathbf{w}}$ satisfies the KKT  conditions in (\ref{original KKT condition revisited1}) and (\ref{original KKT condition revisited2}).
-Define $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$, $\Lambda^{r}=[\lambda^{r}_{1}, \lambda^{r}_{2}, \ldots, \lambda^{r}_{L}]^{T}$ and $\Lambda^{i}=[\lambda^{i}_{1}, \lambda_{2}^{i}, \ldots, \lambda^{i}_{L}]^{T}$,
-(\ref{complex duality regularization1}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-2<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>,
-\label{simple regularization}
-\end{IEEEeqnarray}
-Therefore we obtain  
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+\\R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal}
-\end{IEEEeqnarray}
-Based on (\ref{final complex lagrange duality}), the dual objective function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\Lambda^{r}, \Lambda^{i})=-\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>-\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>+<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
-\label{simple dual function}
-\end{IEEEeqnarray}
-
-Based on (\ref{simple primal}) and (\ref{simple dual function}), the feasibility gap is obtained 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\lambda^{r}, \lambda^{i})=f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})-\theta(\Lambda^{r},\Lambda^{i})=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Re{(\mathbf{y}^{T})}, \Lambda^{r}>\\\nonumber
--<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-\\<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>.
-\label{simple duality gap}
-\end{IEEEeqnarray}
-As we explained in section \ref{cost function}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
-\begin{equation}
-R(u)=\frac{1}{2}u^{2},
-\label{risk function1}
-\end{equation} 
-hence 
-\begin{equation}
-\tilde{R}(u)=R(u)-u R{'}(u)=-\frac{1}{2}u^{2},
-\label{risk function2}
-\end{equation}
-In $\epsilon$-SVR, the objective to exploit slack variables is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by the noise.
-Therefore in $\epsilon$-SVR, $\xi^{r}_{i}$ and $\hat{\xi}^{r}$ are defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-\xi^{r}_{i}=\max(0, \Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\epsilon)\\
-\hat{\xi}^{r}_{i}=\max(0, \Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\Re{(\mathbf{y}_{i})}-\epsilon)
-\label{outlier2}
-\end{IEEEeqnarray} 
-Because the distance between the estimations $\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}$ and the observations $\Re{(\mathbf{y}_{i})}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi^{r}_{i}$ and $\hat{\xi}^{r}_{i}$ can be non zero that is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
-Therefore the risk function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{simple risk function1}
-R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}|\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|_{\epsilon}^{2}\\\label{simple risk function2}
-R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}|\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-where $|\cdot|_{\epsilon}$ denotes $\epsilon$ insensitive function as mentioned in section \ref{cost function}. Recall (\ref{complex duality regression function}),
-\begin{IEEEeqnarray}[\relax]{l}
-<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}
-=\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}),
-\end{IEEEeqnarray}
- we obtain 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function1a}
-\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re(\mathbf{K})_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im(\mathbf{K})_{ij}\\
-\label{intermediate function1b}
-\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re(\mathbf{K})_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Im(\mathbf{K})_{ij}
-\end{IEEEeqnarray}
-Two intermediate variables $\Phi$ and $\Psi$ are defined
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermedia function 2a}
-\Phi^{r}=\Re(\mathbf{y})-\Re(\mathbf{K})
-\lambda^{r};
-\Phi^{i}=\Im(\mathbf{y})-\Re(\mathbf{K})\lambda^{i}\\
-\label{intermediate function 2b}
-\Psi^{r}=\Im(\mathbf{K})\lambda^{i};
-\Psi^{i}=-\Im(\mathbf{K})\lambda^{r}\\
-\nonumber
-\end{IEEEeqnarray} 
-therefore (\ref{intermediate function1a}) and (\ref{intermediate function1b}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function3a}
-\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi^{r}_{i}+\Psi_{i}^{r}\\\label{intermediate function3b}
-\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Phi_{i}^{i}+\Psi_{i}^{i}
-\end{IEEEeqnarray}
-Therefore based on (\ref{intermediate function3a}) and (\ref{intermediate function3b}), 
-(\ref{simple risk function1}) and (\ref{simple risk function2}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function4a}
-R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})=\frac{1}{2}|\Phi^{r}_{i}+\Psi_{i}^{r}|^{2}_{\epsilon}\\
-\label{intermediate function4b}
-R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})=\frac{1}{2}|\Phi^{i}_{i}+\Psi_{i}^{i}|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-Thus based on (\ref{intermediate function4a}) and (\ref{intermediate function4b}), the feasibility gap in (\ref{simple duality gap}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\Lambda^{r}, \Lambda^{i})=<(\Lambda^{r})^{T}, \Re(\mathbf{K})\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re(\mathbf{K})\Lambda^{i}>-<\Re(\mathbf{y})^{T}, \Lambda^{r}>-<\Im(\mathbf{y})^{T}, \Lambda^{i}>\\
-+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.
-\label{simple duality gap final}
-\end{IEEEeqnarray}
-Based on dual objective function in (\ref{simple dual function}), (\ref{simple duality gap final}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\Lambda^{r}, \Lambda^{i})=<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im(\mathbf{y})^{T}, \Lambda^{i}>-\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>-2\theta(\Lambda_{i}, \Lambda_{j})\\
--<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.\label{simple duality gap1}
-\end{IEEEeqnarray}
-The following ratio of the feasibility gap $G(\Lambda^{r}, \Lambda^{i})$ is used to measure the proximity of current solution to the optimal solution.
-The algorithm stops when the ratio satisfies a certain tolerance.
-\begin{equation}
-\frac{G}{G+\theta}
-\label{simple duality gap ratio1}
-\end{equation}
-\subsection{Update $\Phi$, $\Psi$ and $G$}
-$\Phi$, $\Psi$ and $G$ are updated in each iteration along with the optimization variables updated. The pseudo code to update $\Phi$, $\Psi$ and $G$ is given.
-
-Based on the definitions of $\Phi$ and $\Psi$ in (\ref{intermedia function 2a}) and (\ref{intermediate function 2b}), we have the following procedure to update $\Phi$ and $\Psi$ in real channel and imaginary channel, assume the optimization variables updated in each channel are indexed by $1$ and $2$, let $\sigma^{r}_{i}=(\lambda^{r}_{i})^{new}-\lambda^{r}_{i}$ and $\sigma^{i}_{i}=(\lambda^{i}_{i})^{new}-\lambda^{i}_{i}$ denote the differences between the updated optimization variables and the old optimization variables.\\
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{1}. Update $\Phi^{r}$ and $\Psi^{i}$ in real channel}{}
-\For{$i=1:N_{r}$}
-\State $\Phi_{i}^{r}=\Phi_{i}^{r}-\sigma_{1}^{r}\mathbf{K}^{r}_{i1}-\sigma_{2}^{r}\mathbf{K}_{i2}^{r}$
-\State $\Psi_{i}^{i}=\Psi_{i}^{i}-\sigma_{1}^{r}\mathbf{K}^{i}_{i1}-\sigma_{2}^{r}\mathbf{K}^{i}_{i2}$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{2}. Update $\Phi^{i}$ and $\Psi^{r}$ in imaginary channel}{}
-\For{$i=1:N_{r}$}
-\State $\Phi_{i}^{i}=\Phi_{i}^{i}-\sigma_{1}^{i}\mathbf{K}^{r}_{i1}-\sigma_{2}^{i}\mathbf{K}_{i2}^{r}$
-\State $\Psi_{i}^{r}=\Psi_{i}^{r}+\sigma_{1}^{i}\mathbf{K}^{i}_{i1}+\sigma_{2}^{i}\mathbf{K}^{i}_{i2}$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-Then the cost function term in (\ref{simple duality gap final}) are updated by \textbf{Procedure 3} and \textbf{Procedure 4}.
-The cost function terms are denoted by $\chi^{r}$ in real channel and $\chi^{i}$ in imaginary channel.
-\begin{IEEEeqnarray}[\relax]{l}
-\label{cost function update1}
-\chi^{r}=\sum_{i}^{N_{r}}|\Phi^{r}_{i}+\Psi^{r}_{i}|^{2}_{\epsilon}\\
-\label{cost function update2}
-\chi^{i}=\sum_{i}^{N_{r}}|\Phi^{i}_{i}+\Psi^{i}_{i}|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{3}. Update cost function in real channel}{$\chi^{r}$}
-\State $\chi^{r}=0$  \Comment{initial risk term}
-\For{$i=1:N_{r}$}
-\If{$|\Phi^{r}_{i}+\Psi^{r}_{i}|>\epsilon$}
-\State $\chi^{r}+=(|\Phi^{r}_{i}+\Psi^{r}_{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{4}. Update cost function in imaginary channel}{$\chi^{i}$}
-\State $\chi^{i}=0$  \Comment{initial risk term}
-\For{$i=1:N_{r}$}
-\If{$|\Phi^{i}_{i}+\Psi^{i}_{i}|>\epsilon$}
-\State $\chi^{i}+=(|\Phi^{i}_{i}+\Psi^{i}_{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-The pseudo code to update duality gap $G$ based on (\ref{simple duality gap1}) is shown in \textbf{Procedure 5}.
-Assume the indexes of optimization variables updated in real channel is $i$ and $j$, the indexes of optimization variables updated in imaginary channel is $m$ and $f$.
-Define the work sets in real and imaginary channels $S^{r}=[i,j]$ and $S^{i}=[m,f]$.
-Define $(\chi^{r})^{new}$ and $(\chi^{i})^{new}$ are the updated cost function terms based on \textbf{Procedure 3} and \textbf{Procedure 4}, the update process for the term $\theta(\Lambda^{r}, \Lambda^{i})$ in (\ref{simple duality gap1}) can be written as
-\begin{equation}
-\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}})=\bigtriangledown \theta^{r}_{S^{r}}+\bigtriangledown \theta^{i}_{S^{i}}-\frac{C}{2}((\chi^{r})^{new}+(\chi^{i})^{new}-\chi^{r}-\chi^{i}),
-\label{update dual objective function}
-\end{equation}
-Where $\theta_{S}^{r}$ is the gain of the sub dual objective function as shown in (\ref{gain work set selection lambda}), 
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S^{r}}^{r}=-\frac{1}{2}(\Sigma^{r}_{S^{r}})^{T}\Re{(\mathbf{K})}_{S^{r}S^{r}}\Sigma^{r}_{S^{r}}+(\Phi^{r}_{S^{r}})^{T}\Sigma^{r}_{S^{r}}-\epsilon<\mathbf{e}^{T}_{S^{r}},|(\Lambda^{r}_{S^{r}})^{new}|-|\Lambda^{r}_{S^{r}}|>\\
-\bigtriangledown \theta_{S^{i}}^{i}=-\frac{1}{2}(\Sigma^{i}_{S^{i}})^{T}\Re{(\mathbf{K})}_{S^{i}S^{i}}\Sigma^{i}_{S^{i}}+(\Phi^{i}_{S^{i}})^{T}\Sigma^{i}_{S^{i}}-\epsilon<\mathbf{e}^{T}_{S^{i}},|(\Lambda^{i}_{S^{i}})^{new}|-|\Lambda^{i}_{S^{i}}|>
-\end{IEEEeqnarray}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{5}. Update $G$}{}
-\State $G+=Re(\mathbf{y}_{1})\sigma^{r}_{i}+Re(\mathbf{y}_{2})\sigma^{r}_{j}$
-\State $G+=Im(\mathbf{y}_{1})\sigma^{i}_{m}+Re(\mathbf{y}_{2})\sigma^{i}_{f}$
-\State $G-=\epsilon(|\lambda^{r}_{i}+\sigma^{r}_{i}|-|\lambda^{r}_{i}|+|\lambda^{r}_{j}+\sigma^{r}_{j}|-|\lambda^{r}_{j}|)$
-\State $G-=\epsilon(|\lambda^{i}_{m}+\sigma^{i}_{m}|-|\lambda^{i}_{m}|+|\lambda^{i}_{f}+\sigma^{i}_{f}|-|\lambda^{i}_{f}|)$
-\State $G-=2(\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}}))$ \Comment{Update sub objective function based on (\ref{update dual objective function})}
-
-\State $G-=(\Sigma^{r}_{S^{r}})^{T}\Im(\mathbf{K}_{S^{r}S^{i}})\Sigma^{i}_{S^{i}}+(\Sigma^{r}_{S^{r}})^{T}\Psi^{r}_{S^{r}}+(\Sigma^{i}_{S^{i}})^{T}\Psi^{i}_{S^{i}}$ \Comment{Update $<\Lambda^{r},\Im(\mathbf{K})\Lambda^{i}>$}
-\EndProcedure
-\label{update G Phi and Psi}
-\end{algorithmic}
-\end{algorithm}
-
-Pseudo code for two types of combined 1-D searching solver are given by \textbf{Procedure 6} and \textbf{Procedure 7}. 
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{6}. One-shot 1-D combined searching solver}{} 
-\State Step 1. Search for two optimization variables based on single direction solver
-\For{$i=1:N_{r}$}
-\State calculate $\bigtriangledown \theta^{r}_{i}(\bigtriangledown \theta_{i}^{i})$\Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the dual variable with first and the second largest gain of sub objective function, denoted as 1st and 2nd
-\State Step 2. Update 1st and 2nd optimization variables based on double direction solver 
-\State update $\lambda^{r}_{1st}(\lambda^{i}_{1st})$ and $\lambda^{r}_{2nd}(\lambda^{i}_{2nd})$\Comment{Based on double direction solver \ref{double direction solver}}
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
-\EndProcedure
-\end{algorithmic}
-%\caption{Sequential 2-D Solver without Damping}
-\label{1D2D Nodamping}
-\end{algorithm}
-
- \begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{7}. Sequential 1-D combined searching solver}{}
-\State Step 1. Search for two optimization variables based on single direction solver
-\For{$i=1:N_{r}$}\Comment{First round searching}
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the optimization variable with the largest gain of objective function as $1st_{1}$
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to $1st_{1}$
-\For{$i=1:N_{r}$} \Comment{Second round searching}
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the optimization variable with the largest gain of objective function as $1st_{2}$
-\State Step 2. Update $1st_{1}$ and $1st_{2}$ optimization variables based on double direction solver 
-\State update $\lambda^{r}_{1st_{1}}(\lambda^{i}_{1st_{1}})$ and $\lambda^{r}_{1st_{2}}(\lambda^{i}_{1st_{2}})$\Comment{Based on double direction solver \ref{double direction solver}}
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
-
-\EndProcedure
-\end{algorithmic}
-%\caption{Sequential 2-D Solver with Damping}
-\label{1D2D damping}
-\end{algorithm} 
-\newpage
-The pseudo code of complex support vector detector (CSVD) is shown in Appendix \ref{Pseudo code of CSVD}
-
-%\section{Hyperparameter Setting}
-\section{Computer Simulations}
-Computer simulations are launched to test the detection and run time performance of proposed dual channel complex support vector detection algorithm.
-For sake of brevity, the real case is tested first, all the experiments are made by C, compiled by gcc version 4.8.3 on 64 bit Fedora (release 19) Linux system.
-The experiment platform is a desktop computer with I5-4th generation CPU with quad processing cores, 3.2 GHz clock rate, 8 GB RAM.
-
-For sake of brevity, we consider a real uncoded spatial multiplex large MIMO system to simulate one channel of the proposed dual channel complex support vector detection algorithm.
-with $N_{r}$ received antennas and $N_{t}$ transmitted antennas.
-The propagation channel matrix is constructed by channel gain components that are identically independent distributed (i.i.d) Gaussian random variables with zero mean and unit variance.
-transmitted symbols are mutually independent modulated by $M$ PAM with normalized average energy $\frac{1}{N_{t}}$, transmitted over flat fading channel, the sample of noise is AWGN with zero mean and variance $\frac{1}{10^{SNR/10}}$, where $SNR$ denotes the signal to noise ratio.
-We make experiment to low loading factor system $100\times 40$ and full loading factor $100\times 100$, with at least $1e^{5}$ channel realizations and at least $500$ symbol errors accumulated.
-Fig.\ref{SER performance} shows the symbol error rate (SER) performance, Table.\ref{iteration time} shows the average iteration time of real SVD for different SNR.
-\begin{figure}[htb]
-\centering
-%\def\svgscale{0.5}
-\def\svgwidth{\columnwidth}
-\input{BER_curve_real_system.pdf_tex}
-\caption{SER performance of $100\times 100 $ and $100\times 40$ MIMO system}
-\label{SER performance}
-\end{figure}
-
-\begin{table}[htb]
-\renewcommand{\arraystretch}{1.3}
-\caption{Average Iteration Time of Real Support Vector Detector}
-\label{iteration time}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*} {\bfseries Array Size} & \multicolumn{9}{|c|}{\bfseries SNR}\\
-\cline{2-10}
- &6& 8 &10& 12& 14& 16& 18& 20& 22\\
-\hline
-$100\times 40$&682 &681 &681 &681& 680 &679 &678&677 & 680\\
-\hline
-$100\times 100$&1925 &1916& 1903& 1885& 1862& 1827& 1782&1723&1654 \\
-\hline
-\end{tabular}
-\end{table}
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-%\section{Complexity Analysis}
-
-%\section{Conclusion}
-%The conclusion goes here.
-
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-
-\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-\section{Pseudo Code of CSVD}\label{Pseudo code of CSVD}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{CSVD}{$\mathbf{y}$,$\mathbf{H}$}
-\State Step 1. Initialization
-\State $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ \Comment{kernel matrix}
-\State $\chi^{r}=0$, $\chi^{i}=0$ \Comment{risk function}
-\For{$i=1:N_{r}$}\Comment{initialize $\lambda^{r}$, $\lambda^{i}$, $\Phi^{r}$, $\Phi^{i}$, $\Psi^{r}$, $\Psi^{i}$ and duality gap $G$}
-\State $\lambda_{i}^{r}=0, \lambda_{i}^{i}=0$
-\State $\Phi_{i}^{r}=Re(y_{i}), \Phi_{i}^{i}=Im(y_{i})$
-\State $\Psi_{i}^{r}=0, \Psi_{i}^{i}=0$
-\If{$|\Phi^{r}_{i}|>\epsilon$}
-\State $\chi^{r}+=(|\Phi^{r}_{i}|-\epsilon)^{2}$
-\EndIf
-\If{$|\Phi^{i}_{i}|>\epsilon$}
-\State $\chi^{i}+=(|\Phi_{i}^{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor 
-\State $G=C(\chi^{r}+\chi^{i})$ \Comment{initialize duality gap}
-\State $\theta=-0.5G$ \Comment{initialize objective function}
-\State  Step 2. if $G>tol$, go to step 3, else go to Step 5
-\State Step 3.
-\State call combined 1-D searching solver in \textbf{Procedure 6} and \textbf{Procedure 7} \Comment{find and update two optimization variables in the real and imaginary channel} 
-\State Step 4. \textbf{Procedure 5} update $\frac{G}{G+\theta}$, go back to step 2.
-\State Step 5.
-\State $\tilde{\mathbf{x}}=\mathbf{H}^{H}(\Lambda^{r}+i\Lambda^{i})$ \Comment{reconstruct $\mathbf{x}$}
-\State $\mathbf{x}=\mathbb{Q}(\tilde{x})$\Comment{$\mathbb{Q}(\cdot)$ denotes quantization operation based on symbol constellation}
-\State Step 6. \textbf{Return} $\mathbf{x}$ 
-\EndProcedure
-\end{algorithmic}
-\label{CSVD algorithm}
-\caption{Dual Channel Complex Support Vector Detection Algorithm }
-\end{algorithm}
-%Appendix two text goes here.
-
-% use section* for acknowledgment
-%\section*{Acknowledgment}
-
-%The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-%\ifCLASSOPTIONcaptionsoff
-%  \newpage
-%\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%\end{thebibliography}
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-%\begin{IEEEbiography}{Michael Shell}
-%Biography text here.
-%\end{IEEEbiography}
-
-% if you will not have a photo at all:
-%\begin{IEEEbiographynophoto}{John Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-%\begin{IEEEbiographynophoto}{Jane Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
-%\end{spacing}
-
-\newpage
-\bibliographystyle{IEEEtran}
-\bibliography{citation}	
-\end{spacing}												
-\end{document}
+\section{The Algorithm}

### 2015-11-09 Thesis Draft Tianpei Chen/Thesis Draft/C-ChannelHardening.tex
Thesis Introduction

\resetdatestamp

\chapter{Theoretical Analysis of Channel Hardening Phenomenon}
\section{System Model}

### 2015-11-09 Thesis Draft Tianpei Chen/Thesis Draft/C-Intro.tex
Thesis Introduction

--- 2015-10-14 Report Aug 5 2015/Report Aug 2015.tex
@@
-%% bare_jrnl.tex
-%% V1.4a
-%% 2014/09/17
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8a or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
+\resetdatestamp
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_conf_compsoc.tex,
-%%                    bare_jrnl_compsoc.tex, bare_jrnl_transmag.tex
-%%*************************************************************************
+%\chapter{Thesis Organization}
 
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices and paper sizes can       ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
+%A thesis should present results in a scholarly fashion.
+%The following discusses the organization of a thesis, such as would be
+ %appropriate to presenting research results pertaining to Electrical \&
+% Computer Engineering.
 
-%\documentclass[journal]{IEEEtran}
-\documentclass[12pt, draftclsnofoot, onecolumn]{IEEEtran}
-%\documentclass[12pt,paper,final]{article}
-%
-%\documentclass[12pt, onecolummn]{report}
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
+%\section{Scope of a Thesis}
 
-\usepackage[latin1]{inputenc}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{fullpage}
-\usepackage{setspace}
-\usepackage{graphicx}
-%\usepackage[pdftex]{graphicx}
-\usepackage{psfrag}
-\usepackage{color}
-\usepackage{epsfig}
-%\usepackage{appendix}
-%\usepackage{caption}
-\usepackage{cite}
-\usepackage{ifpdf}
-\usepackage[cmex10]{amsmath}
-\usepackage{algorithm}
-\usepackage{array}
-\usepackage{stfloats}
-\usepackage{url}
-\usepackage{fixltx2e}
-\usepackage{setspace} 
-\usepackage{diagbox}
-\usepackage{subfigure}
-\usepackage{algpseudocode}
-\usepackage{multirow}
-\usepackage{calc}
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
+%The terms of reference differ for a Master's Thesis and a Doctoral Thesis.
+%For the Master's Thesis, the Faculty of Graduate Studies and Research at
+%McGill University \cite{McGillTG:P1994} gives the following guidelines.
 
-% *** MISC UTILITY PACKAGES ***
-%
-\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
+%The terms of reference state that ``In most disciplines, Master's theses will
+% not exceed 100 pages.''
 
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
+%==========  main content of thesis
+\chapter{Introduction}
+\section{Large MIMO system}
 
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/tex-archive/info/epslatex/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-
-% *** FLOAT PACKAGES ***
-%
-\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Do not use the stfloats baselinefloat ability as IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-\begin{spacing}{2}
-%\doublespacing
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Report: Complex Support Vector Detector for Large MIMO System}
-
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-\author{Tianpei Chen\\
-Department of Electrical and Computer Engineering\\
-McGill University\\
-\today}
-
-%\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
-%        John~Doe,~\IEEEmembership{Fellow,~OSA,}
-%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-%\thanks{M. Shell is with the Department
-%of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-%GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-%\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-%\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2014 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-%\begin{abstract}
-%The abstract goes here.
-%\end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-%\begin{IEEEkeywords}
-%IEEEtran, journal, \LaTeX, paper, template.
-%\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps.
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-%for IEEE journal papers produced under \LaTeX\ using
-%IEEEtran.cls version 1.8a and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-%I wish you the best of success.
-
-%\hfill mds
-
-%\hfill September 17, 2014
   One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment.
@@
 This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
-
+\section{Large MIMO detections}
+%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving ends.
@@
 Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams.
-However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with the number of transmitted antennas, which is prohibitive for practical applications.
+However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search over the transmit symbol vector space has a complexity that increases exponentially with the number of transmitted antennas, which is prohibitive for practical applications.
 
-As alternatives to MLD, linear detectors (LD) such as zero-forcing (ZF) and minimum mean square error (MMSE) with optimized ordering sequential interference cancellation (ZF-OSIC, MMSE-OSIC) are exploited in V-BLAST architecture\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast},  however the performance of ZF-OSIC and MMMSE-OSIC are inferior comparing to MLD.
+In order to alleviate this problem, linear detectors (LD) such as zero-forcing (ZF) and minimum mean square error (MMSE) aided by successive interference cancellation with optimal ordering (ZF-OSIC, MMSE-OSIC) are exploited in V-BLAST architecture\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast}, although ZF-OSIC and MMSE-OSIC can provide significant improvement comparing to their LD counterparts, a common drawback of SIC aided LD is the error propagation effect, which can not be eliminated by ordering.
+That results in inferior performances comparing to MLD\cite{loyka2004performance}\cite{prasad2004analysis}\cite{jiang2005asymptotic}.
 
@@
 %Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
-Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of metaheuristic based detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance.
-such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
-Tabu search based algorithms which have superior performances compared to LAS detectors because of the efficient local minima exit strategy (e.g.
-Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g.
-Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g.
-Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) .
-Moreover, element based Lattice Reduction (LR) aided algorithms were also proposed to  large MIMO systems.\cite{zhou2013element}.
+Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a variety of metaheuristic based local search algorithms invoked from machine learning field\cite{chockalingam2010low} have been proposed for large MIMO systems.
+These algorithms have complexities that are comparable or slightly higher comparing to MMSE detector and near-optimal performance.
+Such algorithms include likelihood ascend searching (LAS) algorithm and variants\cite{vardhan2008low}\cite{cerato2009hardware}\cite{li2010multiple} %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
+and Reactive Tabu search (RTS) algorithms and variants
+%which have superior performances compared to LAS detectors because of the efficient local minima exit strategy 
+(e.g.
+Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}).
+Additionally, there are other algorithms proposed for large MIMO systems including Message passing technique based algorithms (e.g.
+Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association (PDA) based algorithms \cite{mohammed2009low}, Monte Carlo sampling technique based algorithms (e.g.
+Multiple Restart- Mixed Gibbs Sampling (MR-MGS) algorithm\cite{datta2013novel}) and Element based Lattice Reduction (LR) aided algorithms\cite{zhou2013element}.
 
-Firmly grounded in framework of statistical learning theory, the Support Vector Machine (SVM) technique has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction.
-the SVM method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can provide good generalization performance\cite{scholkopf2002learning}.
+ Considering MIMO detection from a Combinatorial Optimization (CO) problem viewpoint, as powerful tool for solving CO problems, methoheuristic algorithms\cite{blum2003metaheuristics} are good choices for designing large MIMO detectors, driven by demand of achieving acceptable performance with significantly lower computational complexity.
+Besides the metaheuristic algorithms that based on local search strategies which use trajectory methods based on single solution, another class of metaheuristic algorithms is defined as population based.
+The population based metaheuristic algorithms deal with a population of candidate solutions.
+Intrinsically the population based metaheuristic algorithms can provide wider and more efficient exploration of search space.
+The major population based metaheuristic algorithms includes Evolutionary Computation (EC) and Ant Colony Optimization (ACO).
 
-Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
-Moreover, the kernel based methods\cite{scholkopf2002learning} were proposed which solve nonlinear learning tasks by mapping input data samples into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
-This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS).
-Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.
+ Genetic algorithm (GA) is one kind of EC algorithms, which are designed for CO problems.
+GA mimics the natural evolution process of a population and is powerful tool in searching a solution that is close enough to global optimum\cite{Goldberg:1989:GAS:534133}.
 
-Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual form, which can be solved by Quadratic Programming (QP).
-Decomposition methods were proposed to solve this QP problem by decomposing it into sub QP problems and solving them iteratively\cite{platt1999fast}.
-Therefore, the computational intensive numerical methods can be avoided.
-Decomposition is performed by sub set selection solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets S and N, S is the work set and N contains the remaining optimization variables.
+ \section{Support Vector Regression}
+
+ Firmly grounded in framework of statistical learning theory or VC (Vapnik--Chervonenkis) theory, the Support Vector (SV) technique has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction.
+The SV method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can provide good generalization performance\cite{scholkopf2002learning}.
+
+Interest in SV algorithms boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
+Moreover, the kernel based methods\cite{scholkopf2002learning} were proposed in order to extending the SV algorithms to nonlinear learning cases.
+The input data samples are mapped into some high dimensional feature space (also called Reproducing Kernel Hilbert Space (RKHS)) and then linear tools are applied to the feature mappings of the input data samples.
+This is equivalent to transforming the nonlinear learning tasks in the original space into the linear learning tasks in high dimensional feature space.
+The mathematical notion underlying kernel based methods is that of RKHS\cite{scholkopf2002learning}, in which the inner products of the feature mappings can be simply replaced by the computationally economical kernel functions.
+Because SV algorithms only deal with the inner products of the the feature mappings.
+Therefore, by kernel based methods, it is sufficient to use the specific kernel functions based on the RKHS discarding the actual structure of the feature space.
+
+Based on the principle of structural risk minimization\cite{vapnik1982estimation}, the $\epsilon$-SVR\cite{vapnik2013nature}\cite{smola2004tutorial} solves an original constraint optimization problem (primal objective problem) by transforming it into a Lagrange dual form (dual objective problem), which is a Quadratic Programming (QP) problem.
+
+Decomposition method is an efficient method to solve QP problems with large scale data sets, which decomposes a large QP problem into sub QP problems and solve them in an iterative manner\cite{osuna1997training}\cite{osuna1997improved}.
+Decomposition process is performed by sub set selection solver, which refers to a set of algorithms that separate the optimization variables into two sets S and N, S is the work set and N is the freezing set.
 In each iteration, only the optimization variables in the work set is updated while keeping other optimization variables fixed.
-The Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} is an extreme case of the decomposition solvers.
+Based on this principle, Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} was proposed, which can solve the sub QP problems analytically instead of using the time consuming numerical steps.
 An important issue of the sub set selection solvers is the selection of the work set.
@@
 The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
-
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
-
-\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
-\subsection{Regression Model}
-Suppose we are given a training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
-$y_{i}$ denotes output.
-Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Omega}$, $\Omega \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$, $\Omega=V$).
-The regression model (either linear or non-linear) is given by
-\begin{equation}
-y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1,2,\ldots, L
-\label{equation1}
-\end{equation}
-
-\begin{figure}
-\centering
-\def\svgwidth{\columnwidth}
-\input{epsilon-SVR.pdf_tex}
-\caption{$\epsilon$-Support Vector Regression and Risk Functional}
-\label{epsilon-SVR}
-\end{figure}
-
-We present the primal optimization problem directly
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}} f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-s.t. \left\{\begin{array}{ll}
-y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
-\epsilon_{i}, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
-\end{array}\right.
-\label{primal optimization problem}
-\end{IEEEeqnarray}
-In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the solid line represents the estimation of the input-output relation, the area between two dash lines ($\epsilon$-bound) is called $\epsilon$-tube.
-Only those data samples located outside $\epsilon$-tube contribute to the estimation error.
-Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with additive noise of observations, $R(u)$ denotes the cost function.
-The simplest cost function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}.
-For example if the noise is Gaussian distributed, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$.
-The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.
-
-In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
-Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-\label{definition of slack variable1}
-\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
-\label{definition of slack variable2}
-\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon).
-\end{IEEEeqnarray} 
-Because the distance between the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
-That is $\xi_{i}\hat{\xi}_{i}=0$.
-\subsection{Cost Function}\label{cost function}
-The optimal cost function in (\ref{primal optimization problem}) can be derived based on maximum likelihood (ML) principle.
-Assume the data samples $\mathbf{x}_{i}$ in data set are iid, Let $f_{true}(\mathbf{x}_{i}), i=1,2,\cdots L$ denotes true regression function.
-the underlying assumption is $y_{i}=f_{true}(\mathbf{x}_{i})+\xi_{i}, i=1,2,\cdots, L$, $\xi_{i}$ denotes additive noise of the $i$th data sample, with probability density function (pdf) $Pr(\cdot)$.
-Let $P(\cdot)$ denotes the pdf of $y_{i}$.
-Based on ML principle we want to
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{f}\quad \prod_{i=1}^{L}P(y_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}P(f(\mathbf{x}_{i})+\xi_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}Pr(\xi_{i})=\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))\\
-\label{cost function1}
-\end{IEEEeqnarray}
-Take the logarithm of $\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))$, we have
-\begin{IEEEeqnarray}[\relax]{l}
-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
-\label{cost function2}
-\end{IEEEeqnarray}
-maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i})))$, therefore (\ref{cost function1}) is equivalent to 
-\begin{equation}
-\min_{f}-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
-\label{cost function3}
-\end{equation}
-Let $c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))$ denotes the $i$th cost function, which is defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-\log(P(y_{i}-f(\mathbf{x}_{i}))).
-\label{cost function3}
-\end{IEEEeqnarray}
-Thus (\ref{cost function3}) can be rewritten as 
-\begin{equation}
-\min_{f}\quad  \sum_{i=1}^{L}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
-\label{Total risk function}
-\end{equation} 
-In $\epsilon$-SVR, in order to provide more flexibility to precision control, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{cost function3}).
-\begin{IEEEeqnarray}[\relax]{l}
-|u|_{\epsilon}=\left\{\begin{array}{ll}
-0   &if\quad |u|<\epsilon\\
-|u|-\epsilon  &otherwise\\
-\end{array}\right.
-\label{Vepsilon}
-\end{IEEEeqnarray}
-Thus the final form of cost function in $\epsilon$-SVR can be written as 
-\begin{equation}
-\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),
-\label{final cost function}
-\end{equation}
-Consider the cost function term in (\ref{primal optimization problem}),
-\begin{equation}
-\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))
-\end{equation}  
-the cost function term is determined according to the distribution of noise.  
-%where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as
-%\begin{equation}
-%minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f(\mathbf{x})),
-%\label{total cost function}
-%\end{equation} 
-%where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
-%\begin{equation}
-%minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
-%\label{final cost function}
-%\end{equation}
-%where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
-%\begin{eqnarray}
-%\nonumber
-%minimize \quad f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-%s.t. \left\{\begin{array}{ll}
-%y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
-%\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
-%\epsilon, \xi,\hat{\xi} &\geq 0\\
-%\end{array}\right.
-%\label{primal objective function}
-%\end{eqnarray}
-%where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered. 
-\subsection{Lagrange Duality}\label{section lagrange duality}
-According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier.
-The Lagrange function is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L(\mathbf{w}, b, \xi_{i}, \hat{\xi}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})=
-\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{L}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
-\nonumber
-+\sum_{i=1}^{L}\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\sum_{i=1}^{L}\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})\\
-s.t. \left\{\begin{array}{cc}
-\eta_{i}, \hat{\eta}_{i}, \alpha_{i}, \hat{\alpha}_{i}\geq 0, i=1,2,\cdots L\\
-\xi_{i}, \hat{\xi}_{i}\geq  0, i=1,2,\cdots L\\
-\end{array}\right.
-\label{lagrange duality1}
-\end{IEEEeqnarray}
-where $\eta_{i}$, $\hat{\eta}_{i}$, $\alpha_{i}$, $\hat{\alpha}_{i}$ are Lagrange multipliers.
-
-The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the primal constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
-Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.
-
-Assume a constraint optimization problem is given by 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}} \quad f(\mathbf{w})\\
-s.t. \quad c_{i}(\mathbf{w})\leq 0, i=1,2,\ldots L,
-\label{constraint optimization problem}
-\end{IEEEeqnarray}
-its Lagrange function is given by 
-\begin{equation}
-L(\mathbf{w}, \mathbf{a})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),
-\label{orginal Lagrange}
-\end{equation}
-where $\mathbf{a}=[a_{1},a_{2},\ldots, a_{L}]^{T}$ denotes the vector consist of Lagrange multipliers.
- Based on Theorem 6.21 in \cite{scholkopf2002learning}, a variable pair $[\bar{\mathbf{w}}, \bar{\mathbf{a}}]$ is the solution to (\ref{constraint optimization problem}) if and only if the following inequalities are satisfied
- \begin{equation}
- L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
- \label{KKT inequalities}
- \end{equation}
-This inequalities (also called saddle point conditions) yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{original KKT condition1}
-\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, \mathbf{a})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\
-\label{original KKT condition2}
-\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\
-\label{original KKT condition3}
-\bar{a}_{i}c_{i}(\bar{\mathbf{w}})=0, i=1,2,\ldots L
-\end{IEEEeqnarray}
-In order to satisfy the first inequality in (\ref{KKT inequalities}), (\ref{original KKT condition1}) has to hold,
-applying (\ref{original KKT condition1}) to (\ref{lagrange duality1}), which are  
-\begin{IEEEeqnarray}[\relax]{l}
-\label{partial1}
-\partial_{\mathbf{w}} L=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\
-\label{partial2}
-\partial_{\xi_{i}}L=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\
-\label{parial3}
-\partial_{\hat{\xi}_{i}}L=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\
-\label{partial4}
-\partial_{b}L=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber
-\end{IEEEeqnarray}
-Then by substituting (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}), (\ref{lagrange duality1}) can be rewritten as :
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha_{i}, \hat{\alpha}_{i})=\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[R(\xi_{i})+R(\hat{\xi}_{i})]-\sum_{i=1}^{L}[(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}\\
-\nonumber
-+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}[y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}]+\\
-\sum_{i=1}^{L}\hat{\alpha}_{i}[\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i}]
-\label{lagrange duality1 inter}
-\end{IEEEeqnarray}
-notice in (\ref{partial4}), $\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha}_{i})=0$, define $\tilde{R}(u)=R(u)-uR^{'}(u)$, (\ref{lagrange duality1 inter}) can be further simplified to
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i})]\\
-+\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
-\label{dual objective function1}
-\end{IEEEeqnarray}
-In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold.
-A $\mathbf{w}$ that satisfies the conditions in (\ref{original KKT condition2}) is in the feasible region defined by inequality constraints as mentioned (\ref{constraint optimization problem}).
-In $\epsilon$-SVR, this condition is satisfied by making use of the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ defined in (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}).
-Define that $\tilde{\mathbf{w}}$ is in the feasible region and satisfies the conditions in (\ref{original KKT condition1}), notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\tilde{\mathbf{w}}, \mathbf{a})$, thus yielding the dual optimization problem, which is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}}L(\tilde{\mathbf{w}},\mathbf{a})\equiv\max_{\alpha_{i}, \hat{\alpha}_{i}}\quad \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i}))\\
-+\sum_{i=i}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
-\label{dual optimization function2}
-\end{IEEEeqnarray}
-Define $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{L}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{L}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{L}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{L}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0, $\mathbf{R}_{\xi}=[\tilde{R}(\xi_{1}), \tilde{R}(\xi_{2}), \ldots, \tilde{R}(\xi_{L})]^{T}$, $\mathbf{R}_{\hat{\xi}}=[\tilde{R}(\hat{\xi}_{1}), \tilde{R}(\hat{\xi}_{2}), \ldots, \tilde{R}(\hat{\xi}_{L})]^{T}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes a component of data kernel matrix at $i$th row and $j$th column.
-An alternative vector form of (\ref{dual optimization function2}) can be written as
-\begin{equation}
-\max_{\mathbf{a}, \hat{\mathbf{a}}}\theta(\mathbf{a},\hat{\mathbf{a}})=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon \mathbf{e})^{T}\mathbf{a}+(-\mathbf{y}-\epsilon\mathbf{e})^{T}\mathbf{\hat{a}}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
-\label{dual objective alternative}
-\end{equation} 
-We define the following $2L$ vectors 
-$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2L}$, 
-\begin{IEEEeqnarray}[\relax]{l}
-[\mathbf{v}]_{i}=\left\{\begin{array}{ll}
-1\quad i=1,\ldots, l\\
--1\quad i=l+1,\ldots, 2l\\ 
-\end{array}\right.
-\end{IEEEeqnarray}
-(\ref{dual objective alternative}) can also be reformulate as 
-\newcommand{\mysmallarraydecl}{\renewcommand{%
-\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
-\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
-\renewcommand{\baselinestretch}{1.1}%
-\settowidth{\normalbaselineskip}{\scriptsize
-\hspace{\baselinestretch\baselineskip}}%
-\setlength{\baselineskip}{\normalbaselineskip}%
-\setlength{\jot}{0.25\normalbaselineskip}%
-\setlength{\arraycolsep}{2pt}}
-\begin{equation}
-\max_{\mathbf{a}^{*}}\quad \theta(\mathbf{a}^{*})=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\mathbf{K}& -\mathbf{K}\\
--\mathbf{K}& \mathbf{K}
-\end{IEEEeqnarraybox*}\right]
-\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
-\label{vectorize dual optimization function}
-\end{equation}
-
-Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor the proximity of the current solution and the optimal solution.
-Thus it can be used as a stopping criterion.
-In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
-(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
-(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
-\end{array}\right. 
-\label{KKT complimentary}
-\end{IEEEeqnarray}
-Based on the definitions of slack variables in (\ref{definition of slack variable1}) an (\ref{definition of slack variable2}), only when there is a outlier exists, $\xi_{i}$ or $\hat{\xi}_{i}$ can be non zero, that is
-\begin{equation}
-\xi_{i} or \hat{\xi}_{i}=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
-\label{definition of slack variable3}
-\end{equation} 
-because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $y_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig.
-\ref{epsilon-SVR}.
-Therefore at most one of $(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})$  and $(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})$ can be zero.
-In order to satisfy the KKT complementary conditions in (\ref{KKT complimentary}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
-
-Therefore the complete KKT complementary conditions of $\epsilon$-SVR is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
-(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
-(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
-\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots L
-\end{array}\right. 
-\label{complete KKT complimentary}
-\end{IEEEeqnarray}
-
-%The conditions in (\ref{KKT complimentary}) are called KKT complimentary condition. 
-%Obviously by taking partial derivations of (\ref{lagrange duality1}) with respect to $\mathbf{w}$, $\xi_{i}$, $\hat{\xi}_{i}$ and $b$, $\theta(\alpha_{i},\hat{\alpha}_{i})\leq \Theta(\mathbf{w},\alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})$, notice in $\theta(\alpha_{i}, \hat{\alpha}_{i})$ KKT conditions in (\ref{partial1}) to (\ref{partial4}) are satisfied.
-Therefore, KKT complimentary conditions (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
-Because
-%\begin{equation}
-%\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
-%\end{equation} 
-%where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
-%\begin{IEEEeqnarray}[\relax]{l}
-%g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
-%\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
-%l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
-%\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
-%\nonumber
-%\end{IEEEeqnarray}
-%Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$.
-when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied.
-hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds.
-Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.
-
-%In conclusion, the dual objective function can be written as
-
-\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
-\subsection{System Model}\label{system model}
-  Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna.
-The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
-Typically large MIMO systems have hundreds of antennas at the BS, as shown in Fig {\ref{large MIMO uplink model}}.
-  \begin{figure}[htb]
-  \centering
-  \def\svgwidth{\columnwidth}
-  %\includegraphics[scale=•]{•}
-  \input{largeMIMOuplink.pdf_tex}
-  \caption{Large MIMO uplink system }
-  \label{large MIMO uplink model}
-  \end{figure}
-
-Bit sequences, which are modulated to complex symbols, are transmitted by the users over a flat fading channel. The discrete time model of the system is given by:
-\begin{equation}
-\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{discrete time MIMO system}
-\end{equation}
-where $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
-BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
-The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian random variable with zero mean and unit variance.
-Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
-
-The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
-\subsection{Complex Regression Model}
- Based on the discrete time model of a large MIMO uplink system of (\ref{discrete time MIMO system}), our regression model is set such that the training data set at the detector are $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of matrix $\mathbf{H}$.
-This yields a regression task without offset $b$ in (\ref{equation1}) :
- \begin{IEEEeqnarray}[\relax]{l}
- y_{i}=f_{true}(\mathbf{h}_{i})+n_{i}, i=1,2\ldots L\\
- \label{regression part1a}
- f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\cdot\mathbf{s}, i=1,2,\ldots, L\\
- \label{regression part1b}
- \end{IEEEeqnarray}
- where $f_{true}()$ denotes the underlying true regression function, $n_{i}$ denotes discrete sample of additive noise.
-In this regression problem, received symbols $y_{i}$ are the observations, $\mathbf{h}_{i}$ are the input data samples, transmitted symbol vector $\mathbf{s}$ contains the regression coefficients.
-We employ complex support vector regression (CSVR) without offset term $b$.
-As shown in (\ref{original KKT condition1}) the first KKT condition is satisfied by finding the saddle point $\bar{\mathbf{w}}$ by taking paritial derivatives of $L(\mathbf{w},a_{i})$ with respect to $\mathbf{w}$.
-Mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) are employed to calculate partial derivatives of Lagrangian function of CSVR in complex manner\cite{bouboulis2011extension}.
-First we generalize our regression model by complex RKHS,
-Define a real RKHS $\mathcal{H}$, $<,>_{\mathcal{H}}$ denotes the corresponding inner product in $\mathcal{H}$.
-define complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $<,>_{\mathbb{H}}$ denotes the corresponding inner products in $\mathbb{H}$.
-Assume $\mathbf{x}, \mathbf{y},\mathbf{z}$ are complex vectors, $\mu$, $\chi$ $\in \mathbb{C}$, In general a complex Hilbert space $\mathbb{H}_{g}$ has the following properties
-\newtheorem{Lemma}{Lemma}
-\newtheorem{Property}{Property}
-\begin{Property}
- $<\mathbf{x},\mathbf{y}>_{\mathbb{H}_{g}}=(<{\mathbf{y},\mathbf{x}}>_{\mathbb{H}_{g}})^{*}$
-\label{CHSProperty1}
-\end{Property}
-
-\begin{Property}
-$<\mu\mathbf{x}+\chi\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}=\mu<\mathbf{x},\mathbf{z}>_{\mathbb{H}_{g}}+\chi<\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}$
-\label{CHSProperty2}
-\end{Property}
-
-\begin{Property}
-$<\mathbf{z}, \mu\mathbf{x}+\chi\mathbf{y}>_{\mathbb{H}_{g}}=\mu^{*}<\mathbf{z},\mathbf{x}>_{\mathbb{H}_{g}}+\chi^{*}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}_{g}}$
-\label{CHSProperty3}
-\end{Property}
-
-\begin{Lemma}
-Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{V}$, define a real RKHS $\mathcal{H}$ that satisfy $<\mathbf{a}, \mathbf{b}>_{\mathcal{H}}=\mathbf{a}^{T}\mathbf{b}$.
-For the corresponding complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $\mathbf{m}, \mathbf{l}\in \mathbb{C}^{V}$,
-$<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$
-\end{Lemma}
-
-\begin{proof} 
-$\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{V}$, and $\mathbf{g}=\Re{(\mathbf{g})}+\imath\Im{(\mathbf{g})}$, $\mathbf{h}=\Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}$.
-From Property \ref{CHSProperty1} and Property \ref{CHSProperty3},
-\begin{IEEEeqnarray}[\relax]{l}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(g)}+\imath\Im{(g)}, \Re{(h)}+\imath\Im{(h)}>_{\mathbb{H}}
-\label{CHSProperty4 inter1}
-\end{IEEEeqnarray}
-According to Property \ref{CHSProperty2}, (\ref{CHSProperty4 inter1}) can be rewritten as 
-\begin{equation}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath <\Im{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}},
-\label{CHSProperty4 inter2}
-\end{equation}
-According to Property \ref{CHSProperty3}
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-\imath <\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathbb{H}}+\imath (<\Im{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-
-\imath <\Im{(\mathbf{g})}, \\ \nonumber  \Im{(\mathbf{h})}>_{\mathbb{H}})
-=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}-<\Re{(\mathbf{g})},\\ \Im{(\mathbf{h})}>_{\mathbb{H}}]
-\label{CHSProperty4 inter2}
-\end{IEEEeqnarray}
-According to (\ref{CHSProperty4 inter2}), if $\mathbf{f}_{1}, \mathbf{f}_{2}\in \mathcal{H}$, we have  $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathbb{H}}=<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}$, furthermore because $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}=\mathbf{f}^{T}_{1}\mathbf{f}_{2}$, (\ref{CHSProperty4 inter2}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathcal{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}-<\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathcal{H}}]=\\
-\Re{(\mathbf{g})}^{T}\cdot \Re{(\mathbf{h})}+\Im{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}+\imath [\Im{(\mathbf{g})}^{T}\cdot  \Re{(\mathbf{h})}-\Re{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}]=\mathbf{g}\cdot \mathbf{h}^{*}
-\label{CHSequation2}
-\end{IEEEeqnarray}
-
-Therefore $<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}$.
-\end{proof}
-Therefore we have $<\mathbf{h}_{i}, \mathbf{s}^{*}>_{\mathbb{H}}=\mathbf{h}_{i}\cdot \mathbf{s}$, 
-For sake of simplicity we define $\mathbf{w}=\mathbf{s}^{*}$.
-Based on the same principle in the real case presented in section \ref{Introduce epsilon SVR}, the primal optimization problem of large MIMO detection in complex RKHS $\mathbb{H}$ defined by $<\mathbf{m}, \mathbf{l}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}^{*}$ can be formulated as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i}} \quad \frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]\\
-s.t. \left\{\begin{array}{ll}
-\Re{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{r}_{i}, i=1,2,\ldots, N_{r}\\
-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{r}_{i}, i=1,2,\ldots, N_{r}\\
-\Im{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{i}_{i}, i=1,2,\ldots, N_{r}\\
-\Im{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{i}_{i}, i=1,2,\ldots, N_{r}\\
-\xi^{r}_{i}, \hat{\xi}^{r}_{i},\xi^{i}_{i},\hat{\xi}^{i}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex objective function1}
-\end{IEEEeqnarray}
- Where $\Re{(\cdot)}$ and $\Im{(\cdot)}$ denote real and imaginary part of a complex variable and inequality constraints are set to real and imaginary part of the regression function separately.
-Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denote the kernel function, $\mathbf{K}=\Re{(\mathbf{K})}+\imath\Im{(\mathbf{K})}$, where $\Re{(\mathbf{K})}$ and $\Im{(\mathbf{K})}$ denote matrices of corresponding real and imaginary parts.
-Similar to the Lagrange duality rational in section \ref{section lagrange duality}, the Lagrange function associated with (\ref{complex objective function1}) is
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L=
-\frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]- \sum_{i=1}^{N_{r}}(\eta_{i}\xi^{r}_{i}+\hat{\eta}_{i}\hat{\xi}^{r}_{i}+\tau_{i}\xi^{i}_{i}\\\nonumber +\hat{\tau}_{i}\hat{\xi}^{i}_{i})
-+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{r}_{i})
-+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}(\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})\\
-\nonumber
-+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}(\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\Im{(y_{i})}-\epsilon-\hat{\xi}^{i}_{i})\\
-s.t. \left\{\begin{array}{ll}
-\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
-\xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i} \geq  0, i=1,2,\ldots, N_{r}
-\end{array}\right. 
-\label{complex lagrange duality1}
-\end{IEEEeqnarray}
-where $\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}$ are Lagrange multipliers.
-In order to calculate the partial derivations of $L$ with respect to $\mathbf{w}$ which is defined in complex domain, the Wirtinger's calculus is exploited\cite{bouboulis2011extension} , Therefore we have
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-\frac{\partial L}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{i=1}^{N_{r}}\alpha_{i}\mathbf{h}_{i}+\frac{1}{2}\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\mathbf{h}_{i}+\frac{\imath}{2}(\sum_{i=1}^{N_{r}}\beta_{i}\mathbf{h}_{i}-\sum_{i=1}^{N_{r}}\hat{\beta}_{i}\mathbf{h}_{i})=0\\
-\Rightarrow \mathbf{w}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-\imath\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\\
-\frac{\partial L}{\partial \xi^{r}_{i}}=CR^{'}(\xi^{r}_{i})-\eta_{i}-\alpha_{i}=0\Rightarrow \eta_{i}=CR^{'}(\xi^{r}_{i})-\alpha_{i}\\
-\frac{\partial L}{\partial \hat{\xi}^{r}_{i}}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\Rightarrow \hat{\eta}_{i}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\alpha}_{i}\\
-\frac{\partial L}{\partial \xi^{i}_{i}}=CR^{'}(\xi^{i}_{i})-\tau_{i}-\beta_{i}=0\Rightarrow \tau_{i}=CR^{'}(\xi^{i}_{i})-\beta_{i}\\
-\frac{\partial L}{\partial \hat{\xi}^{i}_{i}}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\tau}_{i}-\hat{\beta}_{i}=0\Rightarrow \hat{\tau}_{i}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\beta}_{i}\\
-
-\end{array}\right.
-\label{complex lagrange duality2}
-\end{IEEEeqnarray}
-Based on (\ref{complex lagrange duality2}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}\\
-\nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\\nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\\ \sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}),
-\label{complex duality regression function}
-\end{IEEEeqnarray}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
-+i(\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}-\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}\mathbf{h}^{H}_{i})
-\label{complex duality regularization1}
-\end{IEEEeqnarray}
-Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$. If we have $r_{i}$, $r_{j}$ $\in \mathbb{R}$, then 
-\begin{equation}
-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ji}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij},
-\end{equation}
-Therefore
-\begin{equation}
-\sum_{i,j}^{l}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=0,
-\label{conjugate1}
-\end{equation}
-Based on (\ref{conjugate1}), (\ref{complex duality regularization1}) can be changed to
-\begin{equation}
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}.
-\label{complex duality regularization2}
-\end{equation}
-Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), we have
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L=\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}]+\\
-\nonumber
-C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})]- \sum_{i=1}^{N_{r}}((CR^{'}(\xi^{r}_{i})-\alpha_{i})\xi^{r}_{i}+(CR^{'}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}^{r}_{i}+(CR^{'}-\beta_{i})\xi^{i}_{i}\\\nonumber +(CR^{'}(\hat{\xi}_{i})-\hat{\beta}_{i})\hat{\xi}^{i}_{i})+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\epsilon-\xi^{r}_{i})
-+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\\ \nonumber
-((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})
-+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\\ \nonumber
-\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\Im{(y_{i})}-\\
-\epsilon-\hat{\xi}^{i}_{i})
-\label{complex lagrange duality inter1}
-\end{IEEEeqnarray}
-
-Then simplify (\ref{complex lagrange duality inter1}), we obtain
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L\equiv\theta=-\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}]+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})-\xi_{i}^{r}R^{'}(\xi^{r}_{i})\\\nonumber
-+R(\hat{\xi}^{r}_{i})-\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})-\xi_{i}R^{'}(\xi_{i}^{i})+R(\hat{\xi}^{i}_{i})-\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]+\sum_{i=1}^{N_{r}}[\Re{(y_{i})}(\alpha_{i}-\hat{\alpha}_{i})+\Im{(y_{i})}(\beta_{i}-\hat{\beta}_{i})]-\\
-\epsilon\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta_{i}+\hat{\beta}_{i})
-\label{complex lagrange duality inter2}
-\end{IEEEeqnarray}
-define $\tilde{R}(u)=R(u)-uR^{'}(u)$. Similar to (\ref{dual optimization function2}), The dual optimization problem of a complex MIMO system is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}}\quad \theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
-\nonumber
--\sum_{i}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta+\hat{\beta}_{i})\epsilon+[\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})]\\
-\nonumber
-+C\sum_{i}^{N_{r}}(\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i}))\\ 
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{final complex lagrange duality}
-\end{IEEEeqnarray}
-Notice in (\ref{final complex lagrange duality}), there is no correlation term between $\alpha_{i}, \hat{\alpha}_{i}$ and $\beta_{i}, \hat{\beta}_{i}$, therefore, (\ref{final complex lagrange duality}) can be divided into two independent regression tasks, which are given by
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}} \quad \theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
-\nonumber
-+\tilde{R}(\hat{\xi}^{r}_{i}))\\
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{complex duality real part}
-\end{IEEEeqnarray}
-and 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\beta_{i}, \hat{\beta}_{i}} \quad \theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
-\nonumber
-+\tilde{R}(\hat{\xi}^{i}_{i}))\\
-\left\{\begin{array}{ll}
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{complex duality imaginary part}
-\end{IEEEeqnarray}
-Let $\mathbf{a}=[\alpha_{1}, \alpha_{2},\ldots, \alpha_{N_{r}}]^{T}$, $\mathbf{\hat{a}}=[\hat{\alpha}_{1}, \hat{\alpha}_{2},\ldots, \hat{\alpha}_{N_{r}}]^{T}$, $\mathbf{b}=[\beta_{1}, \beta_{2},\ldots, \beta_{N_{r}}]^{T}$,$\mathbf{\hat{b}}=[\hat{\beta}_{1}, \hat{\beta}_{2},\ldots, \hat{\beta}_{N_{r}}]^{T}$, $\mathbf{R}^{r}=[\tilde{R}(\xi^{r}_{1})+\tilde{R}(\hat{\xi}^{r}_{1}), \tilde{R}(\xi^{r}_{2})+\tilde{R}(\hat{\xi}^{r}_{2}), \ldots, \tilde{R}(\xi^{r}_{N_{r}})+\tilde{R}(\hat{\xi}^{r}_{N_{r}})]^{T}$, $\mathbf{R}^{i}=[\tilde{R}(\xi^{i}_{1})+\tilde{R}(\hat{\xi}^{i}_{1}), \tilde{R}(\xi^{i}_{2})+\tilde{R}(\hat{\xi}^{i}_{2}), \ldots, \tilde{R}(\xi^{i}_{N_{r}})+\tilde{R}(\hat{\xi}^{i}_{N_{r}})]^{T}$, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$.
-The alternate form can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a},\mathbf{\hat{\mathbf{a}}}} \quad \theta^{r}=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\Re{(\mathbf{K})}(\mathbf{a}-\mathbf{\hat{a}})+\Re{(\mathbf{y})}^{T}(\mathbf{a}-\mathbf{\hat{a}})-\epsilon(\mathbf{e}^{T}(\mathbf{a}+\mathbf{\hat{a}}))+C(\mathbf{e}^{T}\mathbf{R}^{r})\\
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex duality real part vectorizes}
-\end{IEEEeqnarray}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{b}, \mathbf{\hat{b}}} \quad \theta^{i}=-\frac{1}{2}(\mathbf{b}-\mathbf{\hat{b}})^{T}\Re{(\mathbf{K})}(\mathbf{b}-\mathbf{\hat{b}})+\Im{(\mathbf{y})}^{T}(\mathbf{b}-\mathbf{\hat{b}})-\epsilon(\mathbf{e}^{T}(\mathbf{b}+\mathbf{\hat{b}}))+C(\mathbf{e}^{T}\mathbf{R}^{i})\\
-\left\{\begin{array}{ll}
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex duality imaginary part vectorized}
-\end{IEEEeqnarray}
-
-Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), where only the real part of the kernel matrix is required for each channel.
-This can provide computational advantages for solving the dual optimization problems.
-\section{Work Set Selection and Solver}\label{WSS}
- As we can see, a quadratic optimization problem is formulated in (\ref{final complex lagrange duality}).
-The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with a large data set.
-
-Decomposition methods are a set of efficient algorithms that can help to ease this difficulty.
-Decomposition methods work iteratively, and are based on choosing a subset of optimization variables $S$ (named work set) to be updated in each iteration step, while keeping the rest variables $N$ fixed.
-Sequential Minimal Optimization (SMO) is an extreme case of decomposition method, where the work set size is 2, and an analytic quadratic programming (QP) step instead of numerical QP step can be performed in each iteration.
-
-Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) have the same structure, in this section we discuss the real part only.
-By dividing the variables into work set $S$ and fixed set $N$.
-Therefore, the vector $\mathbf{a}$ in (\ref{complex duality real part vectorizes}) can be divided into two sub vectors $[\mathbf{a}_{S}, \mathbf{a}_{N}]$.
-thereafter $\mathbf{a}_{S}$ denotes a vector that consists of the components of $\mathbf{a}$ that belongs to set $S$, the same modifications are applied to $\mathbf{\hat{a}}$ and $\mathbf{y}$.
-Thus (\ref{complex duality real part vectorizes}) can be rewritten as:
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}, \mathbf{a}_{N}, \hat{\mathbf{a}}_{N}} \theta= -\frac{1}{2}[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
-\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]+[\Re{(\mathbf{y}_{S})}^{T}, \Re{(\mathbf{y}_{N})}^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]-\\\nonumber\epsilon[\mathbf{e}^{T}_{S}, \mathbf{e}^{T}_{N}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}+\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]+C(\mathbf{e}^{T}, \mathbf{R}^{r})
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{real part decomposition inter1}
-\end{IEEEeqnarray}
-
-Where $\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
-\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of the components in $\Re(\mathbf{K})$ that belong to both of the rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\mathbf{K}$ is a Hermitian matrix, thus $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}, \mathbf{\hat{a}}}\quad \theta^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})+2(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]
-+\Re{(\mathbf{y}_{S}^{T})}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\
-\nonumber
-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S}))
--\frac{1}{2}(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NN}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})+\Re{(\mathbf{y}_{N}^{T})}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{N}+\mathbf{\hat{a}}_{N}))\\\nonumber+C(\mathbf{e}^{T}(\mathbf{R}^{r}),
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{real part decomposition}
-\end{IEEEeqnarray}
-In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is considered i.e 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}_{S}, \mathbf{\hat{a}}_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]+[Re(\mathbf{y}_{S}^{T})-(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\mathbf{K}_{NS}^{r}
-](\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\\nonumber\epsilon<\mathbf{e}^{T}, (\mathbf{a}_{S}+\mathbf{\hat{a}}_{S})>,
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}_{S}]_{i}([\hat{\mathbf{a}}_{S}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i\in S\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i\in S\\
-\end{array}\right.
-\label{subset optimization}
-\end{IEEEeqnarray}
-A proper work set selection strategy is required so that speed and performance requirement can be guaranteed.
-One idea is to perform update to optimization variables that violate the KKT complementary conditions, which, based on (\ref{complete KKT complimentary})
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
-\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, L\\
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, L\\
-\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots, L
-\end{array}\right.
-\label{complementary KKT condition1}
-\end{IEEEeqnarray}
-According to Osuna's theorem\cite{osuna1997improved}, the final convergence can be guaranteed.
-In SMO algorithm, heuristic methods are used to find a work set of size two in order to accelerate the decomposition process\cite{platt1999fast}.
-The heuristic method first searches among the non-bound variables (that is $0<\alpha_{i}<C\tilde{R}(\xi^{r}_{i})$ and $0<\hat{\alpha}_{i}<C\tilde{R}(\hat{\xi}_{i})$), which are more likely to violate the complementary KKT conditions, Then searching the whole dual variable set.
-The second dual variable that can maximize optimization step size is chosen.
-An approximate step size is used as evaluator for sake of reducing computational cost.
-
-Another idea for work set selection is to choose the optimization variables whose update can provide the maximum improvement to the sub dual objective functions.
-The improvement of the sub dual objective function is
-\begin{equation}
-\bigtriangledown \theta^{r}_{S}=\theta^{r}_{S}((\mathbf{a}_{S}+\Delta_{S}), (\hat{\mathbf{a}}_{S}+\hat{\Delta}_{S}))-\theta^{r}_{S}(\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}),
-\label{maximum gain work set selection}
-\end{equation} 
-where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\hat{\Delta}_{S}=\hat{\mathbf{a}}_{S}^{new}-\hat{\mathbf{a}}_{S}$, $\mathbf{a}^{new}_{S}$ and $\hat{\mathbf{a}}^{new}_{S}$ are the updates of $\mathbf{a}_{S}$ and $\hat{\mathbf{a}}_{S}$.
-$\bigtriangledown \theta_{S}^{r}$ in (\ref{maximum gain work set selection}),  based on (\ref{subset optimization}), can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\\\nonumber\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+\{\Re{(\mathbf{y}^{T}_{S})}-[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\\
-\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}]\}(\Delta_{S}-\hat{\Delta}_{S})
--\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S}),
-\label{gain work set selection1}
-\end{IEEEeqnarray} 
-where we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}=[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}\\
-\Re{(\mathbf{K})}_{NS}
-\end{IEEEeqnarraybox*}\right]=\\
-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S},
-\label{modification of gain work set selection}
-\end{IEEEeqnarray}
-where $\Re{(\mathbf{K})}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns corresponding to the work set $S$.
-Therefore, (\ref{gain work set selection1}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}]
-(\Delta_{S}-\hat{\Delta}_{S})
--\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta_{S}+\hat{\Delta}_{S}),
-\label{gain of work set selection1 inter}
-\end{IEEEeqnarray}
-define intermediate variable vector $\Phi^{r}, \Phi^{i}\in \mathbb{R}^{N_{r}}$, $\Phi^{r}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Phi^{i}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$.
-Let $\Phi_{S}$ denote the vector that consists of the components in $\Phi$ that corresponding to $S$.
-Thus (\ref{gain of work set selection1 inter}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+(\Phi^{r}_{S})^{T}(\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta_{S}+\hat{\Delta}_{S})
-\label{gain work set selection2}
-\end{IEEEeqnarray} 
-Because the offset term is omitted in the large MIMO regression model, therefore different from SMO type algorithms, there is no linear equality constraint, which is inducted by offset $b$, as shown in (\ref{partial4}).
-Therefore the size of work set can be less than two.
-However, more efficient work set selection strategies based on maximal sub dual objective gain selection, is proposed in \cite{steinwart2011training}.
-A work set of size two is updated in each iteration.
-The computational cost is reduced while maintaining the comparable performance with the model with offset term.
-In the CSVR large MIMO detector, the work set selection strategy in \cite{steinwart2011training} is exploited.
-Basically, in each iteration this strategy uses the combined single variable searchings, whose searching time is $O(n)$, where $n$ is the number of data samples, to determine a work set of size two.
-On the one hand, this strategy can find a work set of size two, whose update approximately maximize the gain of the dual sub objective function.
-On the other hand, the brute-force searching for the work size of two, whose update can maximize the gain of the sub dual objective function, requires $O(n^{2})$ searching time.
-The former strategy requires as few iterations as the latter one, since in each iteration, the latter strategy is more computationally expensive, the former one can enjoy significantly faster running speed.
-\subsection{Single Direction (1-D) Solver}\label{single direction solver}
-Recall the KKT complementary conditions 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{KKT complementary1}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary2}
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary3}
-\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary4}
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary5}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq R^{'}(\xi^{r}_{i})(R^{'}(\hat{\xi}_{i})), i=1,2,\ldots, N_{r} 
-\end{IEEEeqnarray}
-Recall the discussions of slack variables by (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}) in section \ref{section lagrange duality}.
-we have $\xi^{r}_{i}\hat{\xi}^{r}_{i}=0$.
-similar to the definitions in (\ref{definition of slack variable3}), we have
-\begin{equation}
-\xi^{r}_{i} or \hat{\xi}_{i}^{r}=|\Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}|_{\epsilon},
-\label{definition of complex slack variables}
-\end{equation} 
- therefore in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})$ and  $(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})$ can be non zero, therefore in order to satisfy equalities (\ref{KKT complementary3}) and (\ref{KKT complementary4}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
-
- Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is changed to the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.
-
-  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of the sub dual objective function is chosen as the work set in each iteration.
-Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]^{T}$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]^{T}$.
-Substitute $\mathbf{a}, \hat{\mathbf{a}}$ with $\Lambda$ and using $\Sigma$.
-Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2}) can be rewritten as
-  \begin{equation}
-\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y}_{S}^{T})}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
-]\Lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\Lambda_{S}|>,
-\label{subset optimization lambda}
-\end{equation}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
-\label{gain work set selection lambda}
-\end{IEEEeqnarray} 
-In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
-\begin{IEEEeqnarray}[\relax]{l}
- \max_{\tilde{\lambda}^{new}_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\tilde{\lambda}_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
-+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\tilde{\lambda}_{m}^{new}-\epsilon(|\tilde{\lambda}^{new}_{m}|),
- \label{optimization function 1-D}
- \end{IEEEeqnarray}
- where $\tilde{\lambda}^{new}_{m}$ is the update of $\lambda_{m}$.
- Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Phi^{r}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$ in the imaginary channel, $\Phi_{i}^{i}=\Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$.
-Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
-Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))
-\label{partial optimization function 1-D lambda}
-\end{IEEEeqnarray} 
-where $\Re(y_{m})-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re(\mathbf{K})_{mj}=\Re(y_{m})-\sum_{j=1}^{N_{r}}\lambda_{j}\Re(\mathbf{K}_{mj})=\Phi^{r}_{m}+\lambda_{m}\Re(\mathbf{K}_{mm})$
-and $\lambda_{m}$ denotes the $m$th optimization variable before update. Therefore (\ref{partial optimization function 1-D lambda}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\frac{\partial \theta^{r}_{m}}{\partial \tilde{\lambda}_{m}^{new}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
-\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Phi^{r}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
-\end{IEEEeqnarray}
- The update of $\tilde{\lambda}^{new}_{m}$ is completed by clipping based on (\ref{KKT complementary5})
-\begin{IEEEeqnarray}[\relax]{l}
-\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
-\label{clipped new dual variable}
-\end{IEEEeqnarray}
-
-where $[ ]_{a}^{b}$ denotes clipping function 
-\begin{IEEEeqnarray}[\relax]{l}
-[x]_{a}^{b}=\left\{\begin{array}{ll}
-a \quad if\quad  x\leq a\\
-x \quad if\quad a<x<b\\
-b \quad if\quad x\geq b\\
-\end{array}\right.
-\label{clipping function}
-\end{IEEEeqnarray}
-based on (\ref{gain work set selection lambda}), The maximal gain of the sub dual objective function with respect to the $m$th optimization variable is 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{m}^{r}=\theta_{m}^{r}(\lambda_{m}+\sigma_{m})-\theta_{m}^{r}(\lambda_{m})\\
-\nonumber
-=-\frac{1}{2}\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}\sigma_{m}-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)\\
-=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|),
-\label{gain of 1-D objective function}
-\end{IEEEeqnarray}
-In 1-D searching procedure, the optimization variable whose update can achieve the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, based on the this principle
-\begin{equation}
-k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r}.
-\label{1-D direction}
-\end{equation}
-Notice in (\ref{partial optimization function 1-D lambda}), $sgn(\tilde{\lambda}^{new}_{m})$ is unknown before $\lambda_{m}$ is updated, therefore two conditions $sgn(\tilde{\lambda}^{new}_{m})=1$ and $sgn(\tilde{\lambda}^{new}_{m})=-1$ are considered.
-The final decision of $sgn(\tilde{\lambda}_{m}^{new})$ is made by comparing the corresponding gains of the sub dual objective functions in (\ref{gain of 1-D objective function}).
-\subsection{Double Direction (2-D) Solver}\label{double direction solver}
-Although the omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however, recent work in \cite{steinwart2011training} shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained.
-The optimal 2-D solver uses the same principle as 1-D solver, $|S|=2$, assume the work set consists of the $m$th and $n$th optimization variables, that are $\Lambda_{S}=[\lambda_{m}, \lambda_{n}]$.
-Based on (\ref{gain work set selection lambda}), the sub dual objective function can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\lambda_{m}, 
-\lambda_{n}}\quad \theta^{r}_{m,n}=-\frac{1}{2}[(\tilde{\lambda}^{new}_{m})^{2}\Re{(\mathbf{K})}_{mm}+(\tilde{\lambda}^{new}_{n})^{2}\Re{(\mathbf{K})}_{nn}+2\tilde{\lambda}^{new}_{m}\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}]-\\
-\nonumber
-\tilde{\lambda}^{new}_{m}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\tilde{\lambda}^{new}_{n}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{m})}\tilde{\lambda}^{new}_{1}+\Re{(\mathbf{y}_{n})}\tilde{\lambda}^{2}_{n}\\
--\epsilon(|\lambda^{new}_{m}|+|\tilde{\lambda}_{n}^{new}|), 
-\label{2-D solver}
-\end{IEEEeqnarray}
-Based on (\ref{2-D solver}), the partial derivatives of $\theta^{r}_{m,n}$ with respect to $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}_{n}^{new}$ are 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\label{lambda1 partial}
-\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}+\Re{(\mathbf{y}_{m})}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=\\
--\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{m}+\lambda_{m}\Re{\mathbf{K}}_{mm}+\lambda_{n}\Re{(\mathbf{K})}_{mn}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=0\\
-\nonumber
-\label{lambda2 partial}
-\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{n}}=-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{n})}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=\\
--\tilde{\lambda}_{n}^{new}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{n}+\lambda_{m}\Re{(\mathbf{K})}_{mn}+\lambda_{n}\Re{(\mathbf{K})}_{nn}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=0\\
-\nonumber
-\label{partial derivative sample1}
-\end{IEEEeqnarray}
-where $\frac{\partial |x|}{\partial x}=sgn(x)$ denotes the sign of $x$. Based on (\ref{lambda1 partial}) and (\ref{lambda2 partial}) we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{post partial lambda1}
-(\tilde{\lambda}^{new}_{m}-\lambda_{n})\Re{(\mathbf{K})}_{mm}=\Phi^{r}_{m}-\epsilon sgn(\tilde{\lambda}^{new}_{m})-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{mn}\\
-\label{post partial lambda2}
-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{nn}=\Phi^{r}_{n}-\epsilon sgn(\tilde{\lambda}^{new}_{n})-(\tilde{\lambda}^{new}_{m}-\lambda_{m})\Re{(\mathbf{K})}_{mn}\\
-\nonumber
-\end{IEEEeqnarray}
-hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formulas of $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}^{new}_{n}$ are given by
-\begin{equation}
-\tilde{\lambda}^{new}_{m}=\lambda_{m}+\frac{\Phi^{r}_{m}\Re{(\mathbf{K})}_{nn}-\Phi^{r}_{n}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{nn}-sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
-\label{update lambda1}
-\end{equation}
-
-\begin{equation}
-\tilde{\lambda}^{new}_{n}=\lambda_{n}+\frac{\Phi^{r}_{n}\Re{(\mathbf{K})}_{mm}-\Phi^{r}_{m}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mm}-sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
-\label{update lambda2}
-\end{equation} 
-Then the updated optimization variables are clipped by constraint based on (\ref{KKT complementary5})
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\lambda_{i}^{new}=[\tilde{\lambda}_{i}^{new}]^{CR^{'}(\xi_{i})}_{-CR^{'}(\xi_{i})},\\
-i=m,n
-\label{cipped optimization variable}
-\end{IEEEeqnarray}
-Based on (\ref{gain work set selection2}),  the gain of the sub dual objective function can be written as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=-\frac{1}{2}[\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\sigma_{n}^{2}\Re{(\mathbf{K})}_{nn}+2\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn}]+\Phi^{r}_{m}\sigma_{m}+\Phi^{r}_{n}\sigma_{n}\\
--\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|+|\lambda^{new}_{n}|-|\lambda_{n}|),
-\label{gain of 2-D objective function1}
-\end{IEEEeqnarray}
-assume the $i$th and $j$th optimization variables are chosen, the optimization variables in 2-D solver have the same update rule as that of 1-D solver, that is 
-\begin{equation}
-[i,j]=\arg\max_{m,n=1,2,\ldots, N_{r}}\bigtriangledown \theta_{m,n}^{r}.
-\label{dual optimization variables}
-\end{equation}
-
-Similar to single direction solver, notice in (\ref{update lambda1}) and (\ref{update lambda2}), $sgn(\tilde{\lambda}^{new}_{m})$ and $sgn(\tilde{\lambda}^{new}_{n})$ are unknown before $\lambda_{m}$ and $\lambda_{n}$ are updated, therefore four conditions are considered
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=-1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=-1
-\label{four conditions of sign}
-\end{IEEEeqnarray} 
-The final decisions of $sgn(\tilde{\lambda}_{m}^{new})$ and $sgn(\tilde{\lambda}_{n}^{new})$ are made by comparing the corresponding possible gains of the sub objective functions in (\ref{gain of 2-D objective function1}).
-
-Modify (\ref{gain of 2-D objective function1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)+\sigma_{n}[-\frac{1}{2}\sigma_{n}\Re{(\mathbf{K})}_{nn}+\Phi^{r}_{n}]-\epsilon(|\lambda^{new}_{n}|-|\lambda_{n}|)\\
--\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn},
-\end{IEEEeqnarray}
-then recall the gain of the sub dual objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
- \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta^{r}_{ij}=\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}-\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij},
-\label{gain of 2-D objective function2}
-\end{IEEEeqnarray}
-where $\bigtriangledown \theta^{r}_{i}$, $\bigtriangledown \theta^{r}_{j}$ denote gains of the sub dual objective functions of 1-D solver with $i$th and $j$th optimization variables are updated. 
-\subsection{Approximation of Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
-From (\ref{gain of 2-D objective function1}), we can observe that the gain of the sub dual objective function of 2-D solver is a summation of the gains of the sub dual objective functions of two independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}$.
-
-The optimal 2-D work set $[i,j]$ can be determined by brute-force searching manner, which requires $O(n^{2})$ searching times.
-Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D searching strategy by the combinations of optimal 1-D searching approach, we will prove in the large MIMO systems, when $N_{t}$ is sufficient large, this approximation is very effective.
-Here we propose two types of combined 1-D searching strategy:
-\subsubsection{ One-shot 1-D combined Searching}
-do one round 1-D searching and calculate all the 1-D gains based on (\ref{gain of 1-D objective function}), then choose the two optimization variables indexed by $i$ and $j$, whose update can achieve the first and the second largest gain of the sub dual objective functions.
-\subsubsection{ Sequential 1-D combined Searching}
-do two rounds 1-D searchings, in the first round find optimization variable indexed by $i$ whose update can achieve the maximal 1-D gain of the sub dual objective functions based on (\ref{gain of 1-D objective function}), then update the $i$th optimization variable.
-In the second round, find $j$th optimization variable whose update can achieve the maximal 1-D gain of the sub dual objective functions.
-
- The effectiveness of 1-D approximation strategies are majorly determined by the ratio $\frac{\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}}{\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}}$.
-Hence we provide theoretical analyses based on the view of channel hardening phenomenon.
-It can be proved that in the large MIMO systems, the correlation term $\sigma_{i}\sigma_{j}\Re(\mathbf{K}_{ij})$is ignorable comparing to 1-D gains of the sub objective function.
-Prior to the theoretical analyse, we first investigate some mathematical properties of channel hardening (to be completed).
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
-%\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
-%\label{figure1}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
-%\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
-%\label{figure2}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[scale=0.6]{NtE.eps}
-%\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
-%\label{figure3}
-%\end{figure}
-
-\section{Stopping Criteria}\label{stopping criteria}
-As discussed in section\ref{section lagrange duality}, in dual objective function, the complementary KKT conditions are the measurement of the proximity of current solution to the optimal solution. 
-The feasibility gap, which is a effective stopping criteria used in SVR and SVM, can implicitly monitor whether the KKT complementary conditions are satisfied.
-The feasibility gap measures the gap between the values of primal objective function and dual objective function.
-To elaborate a little further, recall the saddle point conditions in section\ref{section lagrange duality}
- \begin{equation}
- L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
- \label{saddle point conditions}
- \end{equation}
-Where $(\bar{\mathbf{w}}, \bar{\mathbf{a}})$ are the solution to primal objective function, the KKT complementary conditions are satisfied, that is 
-\begin{equation}
-\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=0,
-\label{complementary KKT condition revisited}
-\end{equation}
-we have 
-\begin{equation}
-L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=f(\bar{\mathbf{w}})+\sum_{i=1}^{N_{r}}\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=f(\bar{\mathbf{w}})
-\end{equation} 
-Let $(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$ denote the variable pair that satisfies the first and second KKT conditions in (\ref{original KKT condition1} ) and (\ref{original KKT condition2})
-
-\begin{IEEEeqnarray}[\relax]{l}
-\label{original KKT condition revisited1}
-\partial_{\mathbf{w}}L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=\partial_{\mathbf{w}}f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{a}_{i}\partial_{\mathbf{w}}c_{i}(\tilde{\mathbf{w}})=0,\\
-\label{original KKT condition revisited2}
-c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots L
-\end{IEEEeqnarray}
-based on (\ref{original KKT condition revisited1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq f(\tilde{\mathbf{w}}),
-\end{IEEEeqnarray} 
-based on Theorem 6.27\cite{scholkopf2002learning}, the following equalities hold
-\begin{IEEEeqnarray}[\relax]{l}
-f(\tilde{\mathbf{w}})\geq f(\bar{\mathbf{w}})=L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})
-\label{inequality gap}
-\end{IEEEeqnarray}
-Therefore the feasibility gap is defined by the gap between the primal objective function $f(\tilde{\mathbf{w}})$ and the dual objective function $L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$   
-\begin{equation}
-f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\geq 0
-\label{original feasibility gap}
-\end{equation}
-If the feasibility gap is vanished, based on (\ref{inequality gap}), we have $f(\bar{\mathbf{w}})=f(\tilde{\mathbf{w}})$, thus $\tilde{\mathbf{w}}=\bar{\mathbf{w}}$, $\tilde{\mathbf{a}}=\bar{\mathbf{a}}$.
-Furthermore, because $f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})$, the vanish of feasibility gap indicates $\sum_{i=1}^{L}\tilde{\mathbf{a}}c_{i}(\tilde{\mathbf{w}})=0$.
-Because $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots, L$, we have $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})=0, i=1,2,\ldots, L$, the KKT complementary conditions are satisfied.
-
-In CSVR detector for the large MIMO systems, the primal objective function is
-\begin{equation}
-f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal inter}
-\end{equation}
-where $\tilde{\mathbf{w}}$ satisfies the KKT  conditions in (\ref{original KKT condition revisited1}) and (\ref{original KKT condition revisited2}).
-Define $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$, $\Lambda^{r}=[\lambda^{r}_{1}, \lambda^{r}_{2}, \ldots, \lambda^{r}_{L}]^{T}$ and $\Lambda^{i}=[\lambda^{i}_{1}, \lambda_{2}^{i}, \ldots, \lambda^{i}_{L}]^{T}$,
-(\ref{complex duality regularization1}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-2<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>,
-\label{simple regularization}
-\end{IEEEeqnarray}
-Therefore we obtain  
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+\\R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal}
-\end{IEEEeqnarray}
-Based on (\ref{final complex lagrange duality}), the dual objective function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\Lambda^{r}, \Lambda^{i})=-\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>-\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>+<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
-\label{simple dual function}
-\end{IEEEeqnarray}
-
-Based on (\ref{simple primal}) and (\ref{simple dual function}), the feasibility gap is obtained 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\lambda^{r}, \lambda^{i})=f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})-\theta(\Lambda^{r},\Lambda^{i})=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Re{(\mathbf{y}^{T})}, \Lambda^{r}>\\\nonumber
--<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-\\<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>.
-\label{simple duality gap}
-\end{IEEEeqnarray}
-As we explained in section \ref{cost function}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
-\begin{equation}
-R(u)=\frac{1}{2}u^{2},
-\label{risk function1}
-\end{equation} 
-hence 
-\begin{equation}
-\tilde{R}(u)=R(u)-u R{'}(u)=-\frac{1}{2}u^{2},
-\label{risk function2}
-\end{equation}
-In $\epsilon$-SVR, the objective to exploit slack variables is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by the noise.
-Therefore in $\epsilon$-SVR, $\xi^{r}_{i}$ and $\hat{\xi}^{r}$ are defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-\xi^{r}_{i}=\max(0, \Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\epsilon)\\
-\hat{\xi}^{r}_{i}=\max(0, \Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\Re{(\mathbf{y}_{i})}-\epsilon)
-\label{outlier2}
-\end{IEEEeqnarray} 
-Because the distance between the estimations $\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}$ and the observations $\Re{(\mathbf{y}_{i})}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi^{r}_{i}$ and $\hat{\xi}^{r}_{i}$ can be non zero that is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
-Therefore the risk function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{simple risk function1}
-R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}|\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|_{\epsilon}^{2}\\\label{simple risk function2}
-R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}|\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-where $|\cdot|_{\epsilon}$ denotes $\epsilon$ insensitive function as mentioned in section \ref{cost function}. Recall (\ref{complex duality regression function}),
-\begin{IEEEeqnarray}[\relax]{l}
-<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}
-=\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}),
-\end{IEEEeqnarray}
- we obtain 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function1a}
-\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re(\mathbf{K})_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im(\mathbf{K})_{ij}\\
-\label{intermediate function1b}
-\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re(\mathbf{K})_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Im(\mathbf{K})_{ij}
-\end{IEEEeqnarray}
-Two intermediate variables $\Phi$ and $\Psi$ are defined
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermedia function 2a}
-\Phi^{r}=\Re(\mathbf{y})-\Re(\mathbf{K})
-\lambda^{r};
-\Phi^{i}=\Im(\mathbf{y})-\Re(\mathbf{K})\lambda^{i}\\
-\label{intermediate function 2b}
-\Psi^{r}=\Im(\mathbf{K})\lambda^{i};
-\Psi^{i}=-\Im(\mathbf{K})\lambda^{r}\\
-\nonumber
-\end{IEEEeqnarray} 
-therefore (\ref{intermediate function1a}) and (\ref{intermediate function1b}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function3a}
-\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi^{r}_{i}+\Psi_{i}^{r}\\\label{intermediate function3b}
-\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Phi_{i}^{i}+\Psi_{i}^{i}
-\end{IEEEeqnarray}
-Therefore based on (\ref{intermediate function3a}) and (\ref{intermediate function3b}), 
-(\ref{simple risk function1}) and (\ref{simple risk function2}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function4a}
-R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})=\frac{1}{2}|\Phi^{r}_{i}+\Psi_{i}^{r}|^{2}_{\epsilon}\\
-\label{intermediate function4b}
-R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})=\frac{1}{2}|\Phi^{i}_{i}+\Psi_{i}^{i}|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-Thus based on (\ref{intermediate function4a}) and (\ref{intermediate function4b}), the feasibility gap in (\ref{simple duality gap}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\Lambda^{r}, \Lambda^{i})=<(\Lambda^{r})^{T}, \Re(\mathbf{K})\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re(\mathbf{K})\Lambda^{i}>-<\Re(\mathbf{y})^{T}, \Lambda^{r}>-<\Im(\mathbf{y})^{T}, \Lambda^{i}>\\
-+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.
-\label{simple duality gap final}
-\end{IEEEeqnarray}
-Based on dual objective function in (\ref{simple dual function}), (\ref{simple duality gap final}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\Lambda^{r}, \Lambda^{i})=<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im(\mathbf{y})^{T}, \Lambda^{i}>-\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>-2\theta(\Lambda_{i}, \Lambda_{j})\\
--<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.\label{simple duality gap1}
-\end{IEEEeqnarray}
-The following ratio of the feasibility gap $G(\Lambda^{r}, \Lambda^{i})$ is used to measure the proximity of current solution to the optimal solution.
-The algorithm stops when the ratio satisfies a certain tolerance.
-\begin{equation}
-\frac{G}{G+\theta}
-\label{simple duality gap ratio1}
-\end{equation}
-\subsection{Update $\Phi$, $\Psi$ and $G$}
-$\Phi$, $\Psi$ and $G$ are updated in each iteration along with the optimization variables updated. The pseudo code to update $\Phi$, $\Psi$ and $G$ is given.
-
-Based on the definitions of $\Phi$ and $\Psi$ in (\ref{intermedia function 2a}) and (\ref{intermediate function 2b}), we have the following procedure to update $\Phi$ and $\Psi$ in real channel and imaginary channel, assume the optimization variables updated in each channel are indexed by $1$ and $2$, let $\sigma^{r}_{i}=(\lambda^{r}_{i})^{new}-\lambda^{r}_{i}$ and $\sigma^{i}_{i}=(\lambda^{i}_{i})^{new}-\lambda^{i}_{i}$ denote the differences between the updated optimization variables and the old optimization variables.\\
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{1}. Update $\Phi^{r}$ and $\Psi^{i}$ in real channel}{}
-\For{$i=1:N_{r}$}
-\State $\Phi_{i}^{r}=\Phi_{i}^{r}-\sigma_{1}^{r}\mathbf{K}^{r}_{i1}-\sigma_{2}^{r}\mathbf{K}_{i2}^{r}$
-\State $\Psi_{i}^{i}=\Psi_{i}^{i}-\sigma_{1}^{r}\mathbf{K}^{i}_{i1}-\sigma_{2}^{r}\mathbf{K}^{i}_{i2}$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{2}. Update $\Phi^{i}$ and $\Psi^{r}$ in imaginary channel}{}
-\For{$i=1:N_{r}$}
-\State $\Phi_{i}^{i}=\Phi_{i}^{i}-\sigma_{1}^{i}\mathbf{K}^{r}_{i1}-\sigma_{2}^{i}\mathbf{K}_{i2}^{r}$
-\State $\Psi_{i}^{r}=\Psi_{i}^{r}+\sigma_{1}^{i}\mathbf{K}^{i}_{i1}+\sigma_{2}^{i}\mathbf{K}^{i}_{i2}$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-Then the cost function term in (\ref{simple duality gap final}) are updated by \textbf{Procedure 3} and \textbf{Procedure 4}.
-The cost function terms are denoted by $\chi^{r}$ in real channel and $\chi^{i}$ in imaginary channel.
-\begin{IEEEeqnarray}[\relax]{l}
-\label{cost function update1}
-\chi^{r}=\sum_{i}^{N_{r}}|\Phi^{r}_{i}+\Psi^{r}_{i}|^{2}_{\epsilon}\\
-\label{cost function update2}
-\chi^{i}=\sum_{i}^{N_{r}}|\Phi^{i}_{i}+\Psi^{i}_{i}|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{3}. Update cost function in real channel}{$\chi^{r}$}
-\State $\chi^{r}=0$  \Comment{initial risk term}
-\For{$i=1:N_{r}$}
-\If{$|\Phi^{r}_{i}+\Psi^{r}_{i}|>\epsilon$}
-\State $\chi^{r}+=(|\Phi^{r}_{i}+\Psi^{r}_{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{4}. Update cost function in imaginary channel}{$\chi^{i}$}
-\State $\chi^{i}=0$  \Comment{initial risk term}
-\For{$i=1:N_{r}$}
-\If{$|\Phi^{i}_{i}+\Psi^{i}_{i}|>\epsilon$}
-\State $\chi^{i}+=(|\Phi^{i}_{i}+\Psi^{i}_{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-The pseudo code to update duality gap $G$ based on (\ref{simple duality gap1}) is shown in \textbf{Procedure 5}.
-Assume the indexes of optimization variables updated in real channel is $i$ and $j$, the indexes of optimization variables updated in imaginary channel is $m$ and $f$.
-Define the work sets in real and imaginary channels $S^{r}=[i,j]$ and $S^{i}=[m,f]$.
-Define $(\chi^{r})^{new}$ and $(\chi^{i})^{new}$ are the updated cost function terms based on \textbf{Procedure 3} and \textbf{Procedure 4}, the update process for the term $\theta(\Lambda^{r}, \Lambda^{i})$ in (\ref{simple duality gap1}) can be written as
-\begin{equation}
-\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}})=\bigtriangledown \theta^{r}_{S^{r}}+\bigtriangledown \theta^{i}_{S^{i}}-\frac{C}{2}((\chi^{r})^{new}+(\chi^{i})^{new}-\chi^{r}-\chi^{i}),
-\label{update dual objective function}
-\end{equation}
-Where $\theta_{S}^{r}$ is the gain of the sub dual objective function as shown in (\ref{gain work set selection lambda}), 
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S^{r}}^{r}=-\frac{1}{2}(\Sigma^{r}_{S^{r}})^{T}\Re{(\mathbf{K})}_{S^{r}S^{r}}\Sigma^{r}_{S^{r}}+(\Phi^{r}_{S^{r}})^{T}\Sigma^{r}_{S^{r}}-\epsilon<\mathbf{e}^{T}_{S^{r}},|(\Lambda^{r}_{S^{r}})^{new}|-|\Lambda^{r}_{S^{r}}|>\\
-\bigtriangledown \theta_{S^{i}}^{i}=-\frac{1}{2}(\Sigma^{i}_{S^{i}})^{T}\Re{(\mathbf{K})}_{S^{i}S^{i}}\Sigma^{i}_{S^{i}}+(\Phi^{i}_{S^{i}})^{T}\Sigma^{i}_{S^{i}}-\epsilon<\mathbf{e}^{T}_{S^{i}},|(\Lambda^{i}_{S^{i}})^{new}|-|\Lambda^{i}_{S^{i}}|>
-\end{IEEEeqnarray}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{5}. Update $G$}{}
-\State $G+=Re(\mathbf{y}_{1})\sigma^{r}_{i}+Re(\mathbf{y}_{2})\sigma^{r}_{j}$
-\State $G+=Im(\mathbf{y}_{1})\sigma^{i}_{m}+Re(\mathbf{y}_{2})\sigma^{i}_{f}$
-\State $G-=\epsilon(|\lambda^{r}_{i}+\sigma^{r}_{i}|-|\lambda^{r}_{i}|+|\lambda^{r}_{j}+\sigma^{r}_{j}|-|\lambda^{r}_{j}|)$
-\State $G-=\epsilon(|\lambda^{i}_{m}+\sigma^{i}_{m}|-|\lambda^{i}_{m}|+|\lambda^{i}_{f}+\sigma^{i}_{f}|-|\lambda^{i}_{f}|)$
-\State $G-=2(\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}}))$ \Comment{Update sub objective function based on (\ref{update dual objective function})}
-
-\State $G-=(\Sigma^{r}_{S^{r}})^{T}\Im(\mathbf{K}_{S^{r}S^{i}})\Sigma^{i}_{S^{i}}+(\Sigma^{r}_{S^{r}})^{T}\Psi^{r}_{S^{r}}+(\Sigma^{i}_{S^{i}})^{T}\Psi^{i}_{S^{i}}$ \Comment{Update $<\Lambda^{r},\Im(\mathbf{K})\Lambda^{i}>$}
-\EndProcedure
-\label{update G Phi and Psi}
-\end{algorithmic}
-\end{algorithm}
-
-Pseudo code for two types of combined 1-D searching solver are given by \textbf{Procedure 6} and \textbf{Procedure 7}. 
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{6}. One-shot 1-D combined searching solver}{} 
-\State Step 1. Search for two optimization variables based on single direction solver
-\For{$i=1:N_{r}$}
-\State calculate $\bigtriangledown \theta^{r}_{i}(\bigtriangledown \theta_{i}^{i})$\Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the dual variable with first and the second largest gain of sub objective function, denoted as 1st and 2nd
-\State Step 2. Update 1st and 2nd optimization variables based on double direction solver 
-\State update $\lambda^{r}_{1st}(\lambda^{i}_{1st})$ and $\lambda^{r}_{2nd}(\lambda^{i}_{2nd})$\Comment{Based on double direction solver \ref{double direction solver}}
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
-\EndProcedure
-\end{algorithmic}
-%\caption{Sequential 2-D Solver without Damping}
-\label{1D2D Nodamping}
-\end{algorithm}
-
- \begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{7}. Sequential 1-D combined searching solver}{}
-\State Step 1. Search for two optimization variables based on single direction solver
-\For{$i=1:N_{r}$}\Comment{First round searching}
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the optimization variable with the largest gain of objective function as $1st_{1}$
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to $1st_{1}$
-\For{$i=1:N_{r}$} \Comment{Second round searching}
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the optimization variable with the largest gain of objective function as $1st_{2}$
-\State Step 2. Update $1st_{1}$ and $1st_{2}$ optimization variables based on double direction solver 
-\State update $\lambda^{r}_{1st_{1}}(\lambda^{i}_{1st_{1}})$ and $\lambda^{r}_{1st_{2}}(\lambda^{i}_{1st_{2}})$\Comment{Based on double direction solver \ref{double direction solver}}
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
-
-\EndProcedure
-\end{algorithmic}
-%\caption{Sequential 2-D Solver with Damping}
-\label{1D2D damping}
-\end{algorithm} 
-\newpage
-The pseudo code of complex support vector detector (CSVD) is shown in Appendix \ref{Pseudo code of CSVD}
-
-%\section{Hyperparameter Setting}
-\section{Computer Simulations}
-Computer simulations are launched to test the detection and run time performance of proposed dual channel complex support vector detection algorithm.
-For sake of brevity, the real case is tested first, all the experiments are made by C, compiled by gcc version 4.8.3 on 64 bit Fedora (release 19) Linux system.
-The experiment platform is a desktop computer with I5-4th generation CPU with quad processing cores, 3.2 GHz clock rate, 8 GB RAM.
-
-For sake of brevity, we consider a real uncoded spatial multiplex large MIMO system to simulate one channel of the proposed dual channel complex support vector detection algorithm.
-with $N_{r}$ received antennas and $N_{t}$ transmitted antennas.
-The propagation channel matrix is constructed by channel gain components that are identically independent distributed (i.i.d) Gaussian random variables with zero mean and unit variance.
-transmitted symbols are mutually independent modulated by $M$ PAM with normalized average energy $\frac{1}{N_{t}}$, transmitted over flat fading channel, the sample of noise is AWGN with zero mean and variance $\frac{1}{10^{SNR/10}}$, where $SNR$ denotes the signal to noise ratio.
-We make experiment to low loading factor system $100\times 40$ and full loading factor $100\times 100$, with at least $1e^{5}$ channel realizations and at least $500$ symbol errors accumulated.
-Fig.\ref{SER performance} shows the symbol error rate (SER) performance, Table.\ref{iteration time} shows the average iteration time of real SVD for different SNR.
-\begin{figure}[htb]
-\centering
-%\def\svgscale{0.5}
-\def\svgwidth{\columnwidth}
-\input{BER_curve_real_system.pdf_tex}
-\caption{SER performance of $100\times 100 $ and $100\times 40$ MIMO system}
-\label{SER performance}
-\end{figure}
-
-\begin{table}[htb]
-\renewcommand{\arraystretch}{1.3}
-\caption{Average Iteration Time of Real Support Vector Detector}
-\label{iteration time}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*} {\bfseries Array Size} & \multicolumn{9}{|c|}{\bfseries SNR}\\
-\cline{2-10}
- &6& 8 &10& 12& 14& 16& 18& 20& 22\\
-\hline
-$100\times 40$&682 &681 &681 &681& 680 &679 &678&677 & 680\\
-\hline
-$100\times 100$&1925 &1916& 1903& 1885& 1862& 1827& 1782&1723&1654 \\
-\hline
-\end{tabular}
-\end{table}
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
-%\section{Complexity Analysis}
-
-%\section{Conclusion}
-%The conclusion goes here.
-
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-
-\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-\section{Pseudo Code of CSVD}\label{Pseudo code of CSVD}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{CSVD}{$\mathbf{y}$,$\mathbf{H}$}
-\State Step 1. Initialization
-\State $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ \Comment{kernel matrix}
-\State $\chi^{r}=0$, $\chi^{i}=0$ \Comment{risk function}
-\For{$i=1:N_{r}$}\Comment{initialize $\lambda^{r}$, $\lambda^{i}$, $\Phi^{r}$, $\Phi^{i}$, $\Psi^{r}$, $\Psi^{i}$ and duality gap $G$}
-\State $\lambda_{i}^{r}=0, \lambda_{i}^{i}=0$
-\State $\Phi_{i}^{r}=Re(y_{i}), \Phi_{i}^{i}=Im(y_{i})$
-\State $\Psi_{i}^{r}=0, \Psi_{i}^{i}=0$
-\If{$|\Phi^{r}_{i}|>\epsilon$}
-\State $\chi^{r}+=(|\Phi^{r}_{i}|-\epsilon)^{2}$
-\EndIf
-\If{$|\Phi^{i}_{i}|>\epsilon$}
-\State $\chi^{i}+=(|\Phi_{i}^{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor 
-\State $G=C(\chi^{r}+\chi^{i})$ \Comment{initialize duality gap}
-\State $\theta=-0.5G$ \Comment{initialize objective function}
-\State  Step 2. if $G>tol$, go to step 3, else go to Step 5
-\State Step 3.
-\State call combined 1-D searching solver in \textbf{Procedure 6} and \textbf{Procedure 7} \Comment{find and update two optimization variables in the real and imaginary channel} 
-\State Step 4. \textbf{Procedure 5} update $\frac{G}{G+\theta}$, go back to step 2.
-\State Step 5.
-\State $\tilde{\mathbf{x}}=\mathbf{H}^{H}(\Lambda^{r}+i\Lambda^{i})$ \Comment{reconstruct $\mathbf{x}$}
-\State $\mathbf{x}=\mathbb{Q}(\tilde{x})$\Comment{$\mathbb{Q}(\cdot)$ denotes quantization operation based on symbol constellation}
-\State Step 6. \textbf{Return} $\mathbf{x}$ 
-\EndProcedure
-\end{algorithmic}
-\label{CSVD algorithm}
-\caption{Dual Channel Complex Support Vector Detection Algorithm }
-\end{algorithm}
-%Appendix two text goes here.
-
-% use section* for acknowledgment
-%\section*{Acknowledgment}
-
-%The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-%\ifCLASSOPTIONcaptionsoff
-%  \newpage
-%\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%\end{thebibliography}
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-%\begin{IEEEbiography}{Michael Shell}
-%Biography text here.
-%\end{IEEEbiography}
-
-% if you will not have a photo at all:
-%\begin{IEEEbiographynophoto}{John Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-%\begin{IEEEbiographynophoto}{Jane Doe}
-%Biography text here.
-%\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
-%\end{spacing}
-
-\newpage
-\bibliographystyle{IEEEtran}
-\bibliography{citation}	
-\end{spacing}												
-\end{document}
+\section{Thesis Contribution}
+\section{Thesis Outline}

### 2015-11-09 Thesis Draft Tianpei Chen/Thesis Template/C-2.tex
Thesis Introduction

\resetdatestamp

\newcommand\Dfrac[2]{\frac{\displaystyle #1}{\displaystyle #2}}
\newcommand{\mathBF}[1]{\mbox{\boldmath $#1$}}
\newcommand{\C}[1]{\mathBF{#1}}

\chapter{Mathematical Layout Styles}

\TeX{} does a marvelous job of setting mathematical formulas, most often
 choosing pleasing spacing.
However, on occasion one should intercede to improve the layout.
This chapter defines a few such occasions.
In addition, this chapter documents some features of the {\tt amsmath}
 package which overcome difficulties in typesetting some mathematical
 forms.
The {\tt amsmath} package is documented 
 in {\it The \LaTeX{} Companion} \cite{Goossens:1997}.

The modified setup is typeset as
\begin{equation}
  G(z) = \begin{cases}
           \Dfrac {P(z)}{1+z^{-1}} & \text{for $p$ even}, \\[1ex]
           P(z)                    & \text{for $p$ odd}.
         \end{cases}
\end{equation}

With the modified definitions, we get the following.
\def\hC#1{\C{\hat{#1}}\vphantom{\C{#1}}}           % hat vector
\def\htC#1{\C{\hat{\tilde{#1}}}\vphantom{\C{#1}}}  % hat, tilde vector
\def\tC#1{\C{\tilde{#1}}\vphantom{\C{#1}}}         % tilde vector
\begin{equation}
\begin{split}
  \C{d}^{(i)} &= \hC{v}^{(i)} - \htC{v}^{(i)} \\
  \C{n}^{(i)} &= \C{u}^{(i)} - \tC{v}^{(i)}
\end{split}
\end{equation}

### 2015-11-09 SVR for large MIMO/real SVR matlab/CSVR/CSVD.m

@@ -1,10 +1,10 @@
-function [ symOut ] = CSVD( y, H, SNRd, M, G_v )
+function [ symOut ] = CSVD( y, H, SNRd, M, pav, C, epsilon, tol )
 %omplex support vector detector
 %   Detailed explanation goes here
 %% hyperparameter settings
-epsilon=1e-2;
-tol=1e-2;
-C=1;
+% epsilon=1e-2;
+% tol=1e-2;
+% C=1;
 G_v=[];
 %% initialization 
 Nr=length(H(1,:));
@@ -35,7 +35,7 @@ Theta(1)=(-0.5)*C*(ChiR+ChiI);
 G(1)=-2*Theta;
 ratio(1)=abs(G(1))/(abs(G(1))+abs(Theta(1)));
 iteration=1;
-while (ratio(iteration)>=tol&&iteration<1e3)
+while (ratio(iteration)>=tol)
 %% double channel solver
 % LambdaR_new=zeros(Nr, 1);
 % LambdaI_new=zeros(Nr,1);
@@ -64,37 +64,64 @@ sigmaI1_a=0;
 sigmaI2_a=0;
 [m,n, sigmaI1, sigmaI2, sigmaI1_a, sigmaI2_a, LambdaI_new, PhiI_new, PsiR_new, DeltaThetaI]...
     =a2DSolver(Kr, Ki, LambdaI, PhiI, PsiR, epsilon, labelI);
+
+
+
+
+
 %% update G Theta and Phi Psi
-% sigmaR1=LambdaR_new(i)-LambdaR(i);  %calculate the sigma=lambda^{new}_{i}-lambda_{i}
-% sigmaR1_a=abs(LambdaR_new(i))-abs(LambdaR(i));
-% sigmaR2=LambdaR_new(j)-LambdaR(j);
-% sigmaR2_a=abs(LambdaR_new(j))-abs(LambdaR(j));
-% sigmaI1=LambdaI_new(m)-LambdaI(m);
-% sigmaI1_a=abs(LambdaI_new(m))-abs(LambdaI(m));
-% sigmaI2=LambdaI_new(n)-LambdaI(n);
-% sigmaI2_a=abs(LambdaI_new(n))-abs(LambdaI(n));
+Theta_testR(iteration)=DeltaThetaR;
+Theta_testI(iteration)=DeltaThetaI;
+
+%% real channel update
 ChiR_tmp=abs(PhiR_new+PsiR_new)-epsilon;   %update noise term
[…]

### 2015-11-09 SVR for large MIMO/real SVR matlab/CSVR/CSVD_modified.m

@@ -1,187 +1,36 @@
-function [ symOut ] = CSVD_modified( y, H, SNRd, M, G_v )
-%omplex support vector detector
-%   Detailed explanation goes here
-%% hyperparameter settings
-epsilon=1e-2;
-tol=1e-2;
-C=1;
-G_v=[];
-%% initialization 
-Nr=length(H(1,:));
-Nt=length(H(:,1));
+function [ symOut, MSE ] = CSVD_modified( y, H, SNRd, M, pav, C,  epsilon, tol, dataMod )
+% this routine implement complex Support vector detector for MIMO system
+% the global dual optimizaiton problem is divided into two separate dual
+% optimizaiton problems
 K=H*H';
+% y=y+conj(y);
+Nr=length(K(1,:));
 Kr=real(K);
 Ki=imag(K);
-Lambda=zeros(Nr,1);
+Yr=real(y);
+Yi=imag(y);
 LambdaR=zeros(Nr,1);
 LambdaI=zeros(Nr,1);
-Phi=zeros(Nr,1);
-PhiR=real(y);
-PhiI=imag(y);
-Phi=PhiR+1i*PhiI;
-% Psi=zeros(Nr,1);
-% PsiR=zeros(Nr,1);
-% PsiI=zeros(Nr,1);
-% Psi=PhiR+1i*PsiI;
-% ChiR=0;
-% ChiI=0;
-ChiR_tmp=abs(PhiR)-epsilon;
-ChiR_tmp=ChiR_tmp(find(ChiR_tmp>0));
-ChiR=norm(ChiR_tmp, 2)^(2);
-ChiI_tmp=abs(PhiI)-epsilon;
-ChiI_tmp=ChiI_tmp(find(ChiI_tmp>0));
-ChiI=norm(ChiI_tmp,2)^(2);
-ThetaR=(-C/2)*(ChiR);
-ThetaI=(-C/2)*(ChiI);
-GR=-2*ThetaR;
-GI=-2*ThetaI;
-ratioR=GR/(GR+ThetaR);
-iteration=0;
-%% double channel solver
-LambdaR_new=zeros(Nr, 1);
-LambdaI_new=zeros(Nr,1);
-PhiR_new=zeros(Nr,1);
-PhiI_new=zeros(Nr,1);
-i=0;
-j=0;
-m=0;
-n=0;
-%% real channel
-while (ratioR>=tol)
[…]

### 2015-11-09 SVR for large MIMO/real SVR matlab/CSVR/RSVR.m

@@ -1,4 +1,4 @@
-function [ symOut] = RSVR( H,  y, SNRd,  M, pav, C, tol , epsilon)
+function [ symOut, MSE] = RSVR( H,  y, SNRd,  M, pav, C, tol , epsilon,dataMod)
 %real SVR detection 
 %   Output
 % symOut: regression coefficiences estimation
@@ -163,6 +163,7 @@ Phi=Phi_new;
 
 end
 symOut_tmp=H'*lambda;
+MSE=norm(H*[real(dataMod);imag(dataMod)]-H*symOut_tmp);
 if(length(symOut_tmp)==2)
     symOut=symOut_tmp(1)+1i*symOut_tmp(2);
 else

### 2015-11-09 Thesis Draft Tianpei Chen/Thesis Draft/C-CSVR.tex
Thesis CSVR

@@
 \chapter{Complex Support Vector Preliminary Detector (CSVPD) for Large-Scale MIMO Uplink Systems}
+In this chapter, we proposed a complex support vector preliminary detector (CSVPD), which has a complexity  comparable with linear detectors but performs much better.
+The proposed CSVPD can work in the complex valued Large-Scale MIMO (LS-MIMO) systems in an elegant and efficient manner.
+We exploit the specific widely linear regression model without constant offset, which is suitable for LS-MIMO systems model.
+Furthermore, based on the analysis of channel hardening phenomenon from Chapter 2 and the recent advances in machine learning field concerning decomposition process for SVM\cite{steinwart2011training}, we propose a combined single direction searching strategy in CSVR training process which can approximately maximize the gain of the sub dual objective functions whose work set size are two.
+The combined single direction searching strategy proposed can achieve a much smaller searching times than the optimal double direction searching while make dual objective function converge using as few iterations as the latter one.
+
+  Furthermore, we show that channel hardening phenomenon can be further exploited in CSVPD to reduce the computational complexity and simplify the implementation of the algorithm for LS-MIMO systems.
+Finally, we compare the performance of CSVPD aided likelihood ascend search (LAS) detector and CSVPD aided parallel interference cancellation with ordering (OPIC) detector with MMSE-LAS and MMSE-OPIC.
+These results demonstrate the potential of CSVPD to be utilized as a preliminary detector that can improve the LS-MIMO detectors whose performances are influenced by the reliability of initial solutions.
+
+\section{Brief Introduction to $\epsilon$-Support Vector Regression ($\epsilon$-SVR)}
+  Suppose we are given a training data $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the size of the training data set, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
+$y_{i}$ denotes the output.
+Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the feature mapping of $\mathbf{x}_{i}$, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Omega}$, $\Omega \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$, $\Omega=V$).
+The regression estimate $g(\mathbf{x}_{i})$ (either linear or non-linear) is given by
+\begin{equation}
+g(\mathbf{x}_{i})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1,2,\ldots, L
+\label{regression estimates}
+\end{equation} 
+\begin{figure}
+\centering
+\def\svgwidth{\columnwidth}
+\input{regression_model.pdf_tex}
+\caption{Regression Model of $\epsilon$-SVR}
+\label{regression model}
+\end{figure}
+
+ In $\epsilon$-SVR, as shown in Fig \ref{regression model}, the solid line represents the regression estimate in \ref{regression estimates}, $\epsilon$ controls the precision of the regression, the area between two dash lines ($\epsilon$-bound) is called $\epsilon$-tube.
+Only the regression estimates that have the deviation larger than $\epsilon$ (the data points located outside $\epsilon$-tube in Fig.\ref{regression model}) denoted by $\xi_{i}$ and $\hat{\xi}_{i}$, contribute to the estimation errors.
+the goal of $\epsilon$-SVR is to minimize the risk introduced by estimate errors while keeping $\mathbf{w}$ small, which is also called regularized risk minimization principle, therefore, the primal constraint optimization problem is formulated as
+\begin{eqnarray}
+\nonumber
+\min_{\mathbf{w}, \xi, \hat{\xi}_{i}} f(\mathbf{w}, \xi_{i}, \hat{\xi}_{i})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
+s.t. \left\{\begin{array}{ll}
+y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
+\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
+\epsilon, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
+\end{array}\right.
+\label{primal optimization problem}
+\end{eqnarray} 
+In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model.
+ slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ are introduced based on the "soft margin" principle\cite{cortes1995support} that can cope with the infeasible constraints of the optimization problem and allows the existence of some additive noise to the observations.
+$R(u)$ denotes the cost function.
+The simplest cost function is $R(u)=u$, The choice of the cost function is determined by the statistical distribution of the additive noise\cite{smola2004tutorial}.
+For example if the noise is Gaussian distributed, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$.
+The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of the additive noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.
+
+In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
+Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
+\begin{eqnarray}
+\label{definition of slack variable1}
+\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
+\label{definition of slack variable2}
+\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon).
+\end{eqnarray} 
+Because the deviation between the estimates $g(\mathbf{x}_{i})$ and the observation $y_{i}$ as defined in \ref{regression estimates} can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
+That is $\xi_{i}\hat{\xi}_{i}=0$.
+
+\section{Combined Single Direction Searching Strategy}
 Decomposition methods were proposed to solve this QP problem by decomposing it into sub QP problems and solving them iteratively\cite{platt1999fast}.
@@
 The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
-\section{The Algorithm}
+\section{Complex Support Vector Preliminary Detector}
+\section{Channel Hardening Approximation}
+\section{CSVPD-LAS versus MMSE-LAS}
+\section{CSVPD-OPIC versus MMSE-OPIC}

### 2015-11-09 Thesis Draft Tianpei Chen/Thesis Draft/C-ChannelHardening.tex
Thesis CSVR

@@
 
-\chapter{Theoretical Analysis of Channel Hardening Phenomenon}
+\chapter{Theoretical Analysis of Channel Hardening Phenomenon}\label{Channel Hardening}
 \section{System Model}
+Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna.
+The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
+Typically large MIMO systems have hundreds of antennas at the BS, as shown in Fig {\ref{large MIMO uplink model}}.
+  \begin{figure}[htb]
+  \centering
+  \def\svgwidth{\columnwidth}
+  %\includegraphics[scale=•]{•}
+  \input{largeMIMOuplink.pdf_tex}
+  \caption{Large MIMO uplink system }
+  \label{large MIMO uplink model}
+  \end{figure}
+
+Bit sequences, which are modulated to complex symbols, are transmitted by the users over a flat fading channel. The discrete time model of the system is given by:
+\begin{equation}
+\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{discrete time MIMO system}
+\end{equation}
+where $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
+BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
+The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian random variable with zero mean and unit variance.
+Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
+
+The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.

### 2015-11-09 Thesis Draft Tianpei Chen/Thesis Draft/C-Intro.tex
Thesis CSVR

@@
 %==========  main content of thesis
-\chapter{Introduction}
+\chapter{Introduction} \label{introduction}
 \section{Large MIMO system}
@@
 Based on the principle of structural risk minimization\cite{vapnik1982estimation}, the $\epsilon$-SVR\cite{vapnik2013nature}\cite{smola2004tutorial} solves an original constraint optimization problem (primal objective problem) by transforming it into a Lagrange dual form (dual objective problem), which is a Quadratic Programming (QP) problem.
+Efficient methods for training SV algorithms which are based on large scale data sets were proposed, which is called decomposition.
+Decomposition process is performed by decomposing a large QP problem into a sequence of sub QP problems and solve them in an iterative manner\cite{osuna1997training}\cite{osuna1997improved}, Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} is one of well known representatives of decomposition methods.
 
-Decomposition method is an efficient method to solve QP problems with large scale data sets, which decomposes a large QP problem into sub QP problems and solve them in an iterative manner\cite{osuna1997training}\cite{osuna1997improved}.
-Decomposition process is performed by sub set selection solver, which refers to a set of algorithms that separate the optimization variables into two sets S and N, S is the work set and N is the freezing set.
-In each iteration, only the optimization variables in the work set is updated while keeping other optimization variables fixed.
-Based on this principle, Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} was proposed, which can solve the sub QP problems analytically instead of using the time consuming numerical steps.
-An important issue of the sub set selection solvers is the selection of the work set.
-One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring the final converge\cite{osuna1997improved}.
-The SMO algorithm restricts the size of the work set to two.
-A method to train SVM without offset was proposed In\cite{steinwart2011training}, with the comparable performance to the SVM with offset.
-A set of sequential single variable work set selection strategies, which require $O(n)$ searching time are proposed.
-The optimal double variable work set selection strategy, which performs exhaustively searching, however, requires $O(n^{2})$ searching time.
-The authors demonstrate that with the combination of two different proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.
+Complex valued signal arises in signal processing and digital communication areas etc.
+Therefore, developing signal processing algorithms which are suitable to be directly applied to complex valued systems is typically natural and concise choice.
+Furthermore, for MIMO systems, although one can transform the complex valued system model into an equivalent real valued system model, the detection algorithms built based on the complex valued model is more preferable due to the flexibility for signal constellation choice and hardware implementations\cite{fiftyYang2015}.
+In recent years, a mathematical framework for pure complex valued SV algorithms was developed which can deal with complex valued tasks in signal processing, digital communication and related areas in an elegant and computational efficient manner\cite{bouboulis2013complex}.
 
-The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets.
-In communication and signal processing area, the channel gains, signals, waveforms etc.
-are all represented in complex form.
-Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain.
-The results in\cite{bouboulis2013complex} demonstrate the better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernels.
-Based on this work, we derive a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR).
-The detector can work in two parallel real SVR channels which can be solved independently.
-Moreover, only the real part of kernel matrix is needed in both channels.
-This means a large amount of computation cost saving can be achieved.
-Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
-is constructed without offset, Therefore, for each real SVR without offset, 
-%in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed.
-By this strategy, two variables can be updated at each iteration, with much smaller searching time.
-Two types of combined single optimization variable selection strategy are proposed based on the work in \cite{steinwart2011training}.
-The proposed combined single optimization variable selection strategy can approximate optimal double optimization variable selection strategy.
-The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
 \section{Thesis Contribution}
+
 \section{Thesis Outline}

### 2015-11-13 Thesis Draft Tianpei Chen/Thesis Draft/C-CSVR.tex
Backup of the analysis of the SVR

@@
 \chapter{Complex Support Vector Preliminary Detector (CSVPD) for Large-Scale MIMO Uplink Systems}
+The key challenge in designing Large-Scale MIMO (LS-MIMO) detectors is to reduce complexities while maintaining high performances.
+Given the redundant diversity gain potential provided by LS-MIMO\cite{oestges2010mimo} that can only be achieved at very high Signal to Noise Ratio (SNR), one may consider to sacrifice the redundant diversity gains in order to reduce complexities.
+Furthermore, the ML criterion of MIMO detection stated in (\ref{MLD}) indicates MIMO detection can be naturally classified as a Combinatorial Optimization (CO) problem, that consist of the search for the optimal solution in a discrete and finite set.
+
+Based on the aforementioned situations, the metaheuristics algorithmic frameworks are of intense research interest in LS-MIMO detection in recent years.
+Metaheuristics refer to the high level algorithmic strategies that guide subordinate heuristics iteratively by combining different intelligent learning operations.
+Metaheuristics can explore and exploit the searching space efficiently and find near optimal solutions without costing high complexities.
+The class of algorithms includes but not restrict to Iterative Local Search (ILS), Tabu Search (TS), Simulated Annealing (SA), Genetic Algorithms (GA) and Ant Colony Optimization (ACO).
+
+The single solution based metaheuristics which are also defined as trajectory methods, start from an initial solution and the search process performs on a single solution at any time as a trajectory in the searching space.
+In resent years, several single solution based metaheuristics algorithms are applied to LS-MIMO detection problem, such as
+
+ One of the common characteristics shared by single solution based metaheuristics algorithms is their performances are influenced by initial solution, the performances are improved when starting from a promising region of searching space
+
 In this chapter, we proposed a complex support vector preliminary detector (CSVPD), which has a complexity  comparable with linear detectors but performs much better.
@@
 \section{Brief Introduction to $\epsilon$-Support Vector Regression ($\epsilon$-SVR)}
+\subsection{primal Objective Function}\label{DualityForm}
   Suppose we are given a training data $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the size of the training data set, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
@@
 In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
-Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
+
+\subsection{Cost Function}\label{cost function}
+The optimal cost function ($R(\xi_{i})+R(\hat{\xi}_{i})$) in (\ref{primal optimization problem}) can be derived based on maximum likelihood (ML) principle.
+Assume the data samples $\mathbf{x}_{i}$ in data set are iid, Let $f_{true}(\mathbf{x}_{i}), i=1,2,\cdots L$ denotes true regression function.
+the underlying assumption is $y_{i}=f_{true}(\mathbf{x}_{i})+\varepsilon_{i}, i=1,2,\cdots, L$, $\varepsilon_{i}$ denotes additive noise of the $i$th data sample, with probability density function (pdf) $Pr(\cdot)$.
+Let $P(\cdot)$ denotes the pdf of $y_{i}$.
+Based on ML principle we want to
+\begin{eqnarray}
+\nonumber
+\max_{f}\quad \prod_{i=1}^{L}P(y_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}P(f(\mathbf{x}_{i})+\varepsilon_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}Pr(\varepsilon_{i})=\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))\\
+\label{cost function1}
+\end{eqnarray}
+Take the logarithm of $\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))$, (\ref{cost function1}) is equivalent to 
+\begin{eqnarray}
+\max_{f} \sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
+\label{cost function2}
+\end{eqnarray}
+maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i})))$, therefore (\ref{cost function1}) is equivalent to 
+\begin{equation}
+\min_{f}-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
+\label{cost function3}
+\end{equation}
+Let $c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))$ denotes the cost function of $i$th input-out data sample, which is defined as  
+\begin{equation}
+c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))\varpropto -\log(P(y_{i}-f(\mathbf{x}_{i}))).
+\label{cost function4}
+\end{equation}
+Thus (\ref{cost function3}) is equivalent to 
+\begin{equation}
+\min_{f}\quad  \sum_{i=1}^{L}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
+\label{Total risk function}
+\end{equation} 
+In $\epsilon$-SVR, in order to provide more flexibility to precision control, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{cost function3}).
+\begin{eqnarray}
+|u|_{\epsilon}=\left\{\begin{array}{ll}
+0   &if\quad |u|<\epsilon\\
+|u|-\epsilon  &otherwise\\
+\end{array}\right.
+\label{Vepsilon}
+\end{eqnarray}
+Thus the final form of cost function in $\epsilon$-SVR can be written as 
+\begin{equation}
+\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))\varpropto -\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),
+\label{final cost function}
+\end{equation}  
+the cost function term is determined according to the distribution of noise.
+In discrete time model of LS-MIMO systems, noise is AWGN, that is $-\log(Pr(\varepsilon_{i}))\varpropto \frac{1}{2}\varepsilon^{2}_{i}$, based on (\ref{final cost function}), the cost function in LS-MIMO SVD defined as
+\begin{equation}
+c_{LS-MIMO}(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=\frac{(|y_{i}-f(\mathbf{x}_{i})|^{2}_{\epsilon})}{2}, 
+\label{cost function in LS-MIMO}
+\end{equation} 
+In $\epsilon$-SVR, the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ are used to cope with the outliers of $\epsilon$-tube caused by additive noise, that is  
 \begin{eqnarray}
@@
 \end{eqnarray} 
-Because the deviation between the estimates $g(\mathbf{x}_{i})$ and the observation $y_{i}$ as defined in \ref{regression estimates} can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
+Because the deviation between the estimates $g(\mathbf{x}_{i})$ and the observation $y_{i}$ in \ref{regression estimates} can only exceed the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
 That is $\xi_{i}\hat{\xi}_{i}=0$.
+
+In conclusion, the cost function term in (\ref{primal optimization problem}) can be defined as $R(u)=\frac{1}{2}u^{2}$, thus we have 
+\begin{equation}
+R(\xi_{i})+R(\hat{\xi}_{i})=\frac{1}{2}\xi^{2}_{i}+\frac{1}{2}\hat{\xi}^{2}_{i}=\frac{1}{2}|y_{i}-f(\mathbf{x}_{i})|^{2}_{\epsilon}
+\label{final form of cost function in LS-MIMO}
+\end{equation} 
+\subsection{Dual Objective Problem}
 

### 2015-11-13 Thesis Draft Tianpei Chen/Thesis Draft/C-GA.tex
Backup of the analysis of the SVR

\resetdatestamp

\chapter{Low Complexity Near Optimal Hybrid Detector based on Genetic Algorithm}
In the previous chapter, we introduce two CSVPD aided local search based algorithms, and show the improvement CSVD-LAS -OPIC comparing to MMSE-LAS -OPIC.    
a current trend is the hybridization of of single solution based metaheuristics algorithms in population-based ones, working as intelligent subordinate heuristic operators. In this chapter, we introduce Hybrid Genetic Algorithms which utilizes OPIC as a genetic operator and accelerate the revolution process comparing to random revolution, in addition the performance of the proposed algorithm can be further improved by the hybridization with the principle from neighbour variable search. 
\section{Genetic Algorithm}

### 2015-11-13 Thesis Draft Tianpei Chen/Thesis Draft/C-Intro.tex
Backup of the analysis of the SVR

@@
 The promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} and long-term evolution (LTE)\cite{3GLTE}.
-The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve spectrum efficiency) and diversity gain (better reliability of communication link) are obtained by exploiting the spatial domain.
-Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously.
-This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
+The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve spectrum efficiency) and diversity gain (better reliability of communication link) are obtained by exploiting the spatial domain\cite{oestges2010mimo}.
+Large-Scale MIMO system (LS-MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously.
+This technology can achieve full potential of conventional MIMO systems including significant link reliability and throughput benefits.
+Nonetheless, the LS-MIMO systems have been shown to enjoy some distinct advantages
+that are not available in small-scale MIMO systems such as additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
 \section{Large MIMO detections}
 %Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
- The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving ends.
+ The price paid for LS-MIMO system is the increased complexities for signal processing at both transmitting and receiving ends.
 The uplink detector is one of the key components in a large MIMO system.

### 2015-11-13 SVR for large MIMO/real SVR matlab/CSVR/CSVD_modified.m

@@ -19,17 +19,22 @@ LambdaI=zeros(Nr,1);
 
 %%Reconstruction
 Lambda=complex(LambdaR, LambdaI);
-% I=eye(Nr);
-% G=H'*(I/K);
-% G=(I/(H'*H))*H';
+I=eye(Nr);
+G=H'*(I/(K+SNRd^(-1)*I));
+% G=(I/(H'*H)+SNRd)*H';
 % symOut_mmse=G*y;
-% symOut_hat=2*G*Kr*Lambda;
-symOut_hat=H'*Lambda;
+symOut_hat=2*G*Kr*Lambda;
+U_conj=H'*Lambda;
+V_conj=H.'*Lambda;
+% symOut_hat=(H'+H.')*Lambda;
+% symOut_hat=U_conj+V_conj;
+
 % u_c=H'*Lambda;   %conjugate of u
 % v_c=H.'*Lambda;   %conjugate of v
 % H_c=complex(real(H), -imag(H));
 % symOut_hat=u_c+G*H_c*v_c;
-MSE=norm(H*dataMod-2*Kr*Lambda);
+MSE=norm(H*dataMod-H*symOut_hat);
+% MSE=norm(H*dataMod-2*Kr*Lambda);
 % MSE2=norm(H*dataMod-H*symOut_mmse);
 MSE3=norm(H*dataMod-H*symOut_hat);
 symOut=Rectangular_QAM_slicer(symOut_hat,M, pav);

### 2015-11-13 SVR for large MIMO/real SVR matlab/CSVR/RSVR.m

@@ -52,19 +52,21 @@ for count=1:Nr
 %       lambda_tmp2=lambda(count)*(K(count,count)/k)+(Phi(count)-epsilon*(1))/k;
   lambda_tmp1=lambda(count)+(Phi(count)-epsilon*(-1))/(K(count,count));
   lambda_tmp2=lambda(count)+(Phi(count)-epsilon*(1))/(K(count,count));
-%         clipping
-% xi_tmp=(abs(Phi(count))-epsilon);
-% clipper=C*xi_tmp;
-%     if(lambda_tmp1<-clipper)
-%         lambda_tmp1=-clipper;
-%     elseif(lambda_tmp1>clipper)
-%         lambda_tmp1=clipper;
+% %         clipping
+% xi_tmp_upper=max(0, Phi(count)-epsilon);
+% xi_tmp_lower=max(0, -Phi(count)-epsilon);
+% clipper_upper=C*xi_tmp_upper;
+% clipper_lower=-C*xi_tmp_lower;
+%     if(lambda_tmp1<-clipper_lower)
+%         lambda_tmp1=-clipper_lower;
+%     elseif(lambda_tmp1>clipper_upper)
+%         lambda_tmp1=clipper_upper;
 %     end
-% %        clipping
-%     if(lambda_tmp2<-clipper)
-%         lambda_tmp2=-clipper;
-%     elseif(lambda_tmp2>clipper)
-%         lambda_tmp2=clipper;
+% % clipping
+%     if(lambda_tmp2<-clipper_lower)
+%         lambda_tmp2=-clipper_lower;
+%     elseif(lambda_tmp2>clipper_upper)
+%         lambda_tmp2=clipper_upper;
 %     end
     delta1=(lambda_tmp1-lambda(count))*((-1/2)*(lambda_tmp1-lambda(count))*K(count,count)+Phi(count))-epsilon*(abs(lambda_tmp1)-abs(lambda(count)));
 %     -(1/C)*(lambda_tmp1^2-(lambda(count)^2));
@@ -99,13 +101,7 @@ K_tmp=K(First,First)*K(Second,Second)-(K(First,Second))^2;
 %update lambda(First)
 lambda_tmp1=lambda(First)+(Phi(First)*K(Second,Second)-Phi(Second)...
     *K(First,Second)-epsilon*(sgn(First)*K(Second,Second)-sgn(Second)*K(First,Second)))/K_tmp;
-% %clipping 
[…]

### 2015-11-13 SVR for large MIMO/real SVR matlab/CSVR/Verification Test/SVR_learning.m

@@ -1,0 +1,161 @@
+function [ W_e ] = SVR_learning(y ,x , SNRd,C ,epsilon, tol )
+%This subroutine implement the Support Vector regression 
+%   Detailed explanation goes here
+y=[real(y); imag(y)];
+x=[real(x), -imag(x); imag(x), real(x)];
+N=length(x(1,:));
+K=x*x';
+% Nt=length(x(1,:));
+M=length(K(1,:));
+% C=5;
+Phi=zeros(M,1);
+sigma=zeros(M,1);
+lambda=zeros(M,1);
+%% Initialization
+Phi=y; %intermediate variable
+G=[]; %duality gap
+G(1)=0;
+Theta(1)=0;
+Phi_tmp=abs(Phi)-epsilon;
+Phi_tmp=Phi_tmp(find(Phi_tmp>0));
+Chi(1)=norm(Phi_tmp)^(2);
+Theta(1)=-0.5*C*Chi(1);
+G(1)=-2*Theta(1);
+
+% G(1)=G(1)/abs(G(1)+Theta(1));
+%% update lambda
+ratio(1)=G(1)/(G(1)+Theta(1));
+iteration=1;
+while(ratio(iteration)>tol)
+
+delta=zeros(M,1);
+sigma_tmp=zeros(M, 1);
+NoiseTerm=0;
+sgn=zeros(M,1);
+K_tmp=0;
+ %% approximate 2-D work set selection (without damping-bubble sorting)
+for count=1:M
+%      k=(K(count,count)+1/C);
+%        lambda_tmp1=lambda(count)*(K(count,count)/k)+(Phi(count)-epsilon*(-1))/k;
+%       lambda_tmp2=lambda(count)*(K(count,count)/k)+(Phi(count)-epsilon*(1))/k;
+  lambda_tmp1=lambda(count)+(Phi(count)-epsilon*(-1))/(K(count,count));
+  lambda_tmp2=lambda(count)+(Phi(count)-epsilon*(1))/(K(count,count));
+%         clipping
+% xi_tmp=(abs(Phi(count))-epsilon);
+% clipper=C*xi_tmp;
+%     if(lambda_tmp1<-clipper)
+%         lambda_tmp1=-clipper;
+%     elseif(lambda_tmp1>clipper)
+%         lambda_tmp1=clipper;
+%     end
+% %        clipping
+%     if(lambda_tmp2<-clipper)
+%         lambda_tmp2=-clipper;
+%     elseif(lambda_tmp2>clipper)
[…]

### 2015-11-13 SVR for large MIMO/real SVR matlab/CSVR/Verification Test/Verification_2Dupdate.m

@@ -1,0 +1,28 @@
+%% this routine verify the 2-D  update rule with considering noise term in dual 
+% objective function
+
+%% parameter settings
+K11=2;
+K11_hat=3;
+K12=3;
+K22=3;
+K22_hat=4;
+m1=5;
+m2=7;
+lambda1=4;
+lambda2=6;
+
+
+S=K11_hat*K22_hat-K12^(2);
+lambda2_new=(K11_hat*K22-K12^(2))*lambda2+lambda1*K12*(K11_hat-K11)+m2*K11_hat-m1*K12;
+lambda2_new=lambda2_new/S;
+
+
+lambda1_new=(K22_hat*K11-K12^(2))*lambda1+lambda2*K12*(K22_hat-K22)+m1*K22_hat-m2*K12;
+lambda1_new=lambda1_new/S;
+
+%%verification of lambda1_new an lambda2_new
+lambda1_true=lambda1*K11+m1-(lambda2_new-lambda2)*K12;
+lambda1_true=lambda1_true/K11_hat;
+lambda2_true=lambda2*K22+m2-(lambda1_new-lambda1)*K12;
+lambda2_true=lambda2_true/K22_hat;

### 2015-11-13 SVR for large MIMO/real SVR matlab/CSVR/Verification Test/Verification_SNR.m

@@ -1,0 +1,210 @@
+%% verification test for SVD
+close all;
+clear all;
+tic
+SNR=2:2:40;   %receive signal to noise ratio in dB
+SNRd=10.^(SNR./10);   %receive signal to noise ratio decimal
+M=30;   %number of training data samples
+M_t=1000; %number of testing data samples
+N=30; %the number of features
+pav=1/N;      %the average power of the regression coefficiences
+w=complex(normrnd(0, sqrt(pav/2), [N,1]), normrnd(0, sqrt(pav/2),[N,1]));   %the true regression coeffeciences
+% Pt=norm(w)^(2);   %the total power of the true function 
+d_hat=zeros(M,1); %the true output of the linear function in training part
+d=zeros(M,1);   %the observations in training part
+w_svr=zeros(M,1); %the regression estimation coefficiences from SVR
+noiseV=1./SNRd;
+realization=1e2;  %the realization time
+epsilon=1e-7;
+C=1;
+tol=1e-3;
+MSE_training=zeros(length(SNR),1);  %training output MSE for SVR
+MSE_svrco_training=zeros(length(SNR),1);  %training MSE for coefficiences vector for SVR
+MSE_testing=zeros(length(SNR),1);   %testing output MSE for SVR
+MSE_mmse_training=zeros(length(SNR),1); %training of the output of MSE for MMSE
+MSE_mmseco_training=zeros(length(SNR),1); %training MSE for coefficiences vector for MMSE
+MSE_mmse_testing=zeros(length(SNR),1); %testing MSE for MMSE
+fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\Verification Test\Test Data\MSE_SNR.txt', 'a');
+fprintf(fid, '-------------\n');
+fprintf(fid, 'this document record the data of SVR from testing\n');
+fprintf(fid, 'this document compare the SVR and MMSE from the view of SNR');
+fprintf(fid, 'this document also record the MSE comparison of the regression coefficience vector (coefficience vector) of SVR and MMSE\n');
+fprintf(fid, 'all the result are based on %d realizations', realization);
[…]

### 2015-11-13 SVR for large MIMO/real SVR matlab/CSVR/Verification Test/Verification_SparseDataSetting.m

@@ -1,0 +1,215 @@
+%% verification test for SVD
+close all;
+clear all;
+tic
+SNR=20;   %receive signal to noise ratio in dB
+SNRd=10.^(SNR./10);   %receive signal to noise ratio decimal
+M=[30,40,60,100,150];   %number of training data samples
+M_t=1000; %number of testing data samples
+N=30; %the number of features
+realization=1e2;  %the realization time
+pav=1/N;      %the average power of the regression coefficiences
+w=complex(normrnd(0, sqrt(pav/2), [N,1]), normrnd(0, sqrt(pav/2),[N,1]));   %the true regression coeffeciences
+% Pt=norm(w)^(2);   %the total power of the true function 
+w_svr=zeros(N,1); %the regression estimation coefficiences from SVR
+noiseV=1./SNRd;
+epsilon=1e-7;
+C=1;
+tol=1e-3;
+MSE_training=zeros(length(SNR),1);  %training output MSE for SVR
+MSE_svrco_training=zeros(length(SNR),1); %training coefficience vector MSE for SVR
+MSE_testing=zeros(length(SNR),1);   %testing output MSE for SVR
+MSE_mmse_training=zeros(length(SNR),1); %training output MSE for MMSE
+MSE_mmseco_training=zeros(length(SNR),1); %training coefficience vector MSE for MMSE
+MSE_mmse_testing=zeros(length(SNR),1); %testing output MSE for MMSE
+fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\Verification Test\Test Data\MSE_sparse_data_setting.txt', 'a');
+fprintf(fid, '-------------\n');
+fprintf(fid, 'this document record the data of SVR from testing\n');
+fprintf(fid, 'this document compare the SVR and MMSE from the view of data sparseness under a given SNR\n');
+fprintf(fid, 'this document also records the MSE comparison between the coefficience vector of SVR and MMSE\n');
+fprintf(fid, 'all the result are based on %d realizations', realization);
+fprintf(fid, 'the given SNR(dB) are\n');
+for count=1:length(SNR)
+    fprintf(fid, '%d ', SNR(count));
+end
+fprintf(fid, '\n');
+
+fprintf(fid, '\n');
[…]

### 2015-11-13 SVR for large MIMO/real SVR matlab/CSVR/comunnicationLine_CSVD_test.m

@@ -8,7 +8,7 @@ M =4;         %size of constellation
 Nt=32;         %number of transmit antennas
 Nr=32;         %number of receive antennas
 % x=6;            %diversity gain that required
-SNR=[16];       %signal to noise ratio per bit in dB
+SNR=[26];       %signal to noise ratio per bit in dB
 SNRd=10.^(SNR.*0.1);   %SNR in dicimal
 noiseV=1./SNRd;   %noise variance of AWGN 
 BER=zeros(length(SNR),1);         %bit error rate
@@ -58,10 +58,10 @@ pav=1/Nt;  %average symbol power
 % hSpDec = comm.SphereDecoder('Constellation', constellation(hMod),...
 %         'BitTable', BitTable, 'DecisionType', 'Hard');
 %     hBER = comm.ErrorRate;
- fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\test data\BER_CSVD_test.txt', 'a');
+ fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\test data\BER_RegularizatonTest.txt', 'a');
  fprintf(fid, '\n');
  fprintf(fid, '-----------------\n');
- fprintf(fid ,'this file record the simulation results of CSVD\n');
+ fprintf(fid ,'this file record the simulation results to test the influence of from the regularizationTest\n');
 %  fprintf(fid, 'the population is %d\n', population);
 %  fprintf(fid, 'the number of generation is %d\n', maxGeneration);
 %  fprintf(fid, 'RSVD-GA with OMIC\n');
@@ -106,7 +106,7 @@ for count=1:length(SNR)     %under the SNR from 0 to 10
     channelRealization=0;          %number of channel realization
 %     bitOutput=zeros(nBits,1);
 %  fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\test data\BER_CSVD_test.txt', 'a');
- while(symError1<100||channelRealization<1e3)
+ while(channelRealization<1e2)
 % symOut=zeros(Nt,1);
 % for k=1:symNum/Nt
 % for i=1:Nt
[…]

### 2015-11-18 Thesis Draft Tianpei Chen/Thesis Draft/C-CSVR.tex
test the uniform dual objective function optimization

--- 2015-11-09 Thesis Draft Tianpei Chen/Thesis Draft/C-CSVR.tex
@@
 
-\chapter{Complex Support Vector Preliminary Detector (CSVPD) for Large-Scale MIMO Uplink Systems}
+\chapter{Complex Support Vector Preliminary Detector (CSVPD) for Large-Scale MIMO Uplink Systems}\label{Chapter CSVPD}
+
 In this chapter, we proposed a complex support vector preliminary detector (CSVPD), which has a complexity  comparable with linear detectors but performs much better.
+The proposed CSVPD can be widely used as the preliminary processor to generate initial solutions for the detectors whose performances are heavily depended on the initial solution.
  The proposed CSVPD can work in the complex valued Large-Scale MIMO (LS-MIMO) systems in an elegant and efficient manner.
-We exploit the specific widely linear regression model without constant offset, which is suitable for LS-MIMO systems model.
 Furthermore, based on the analysis of channel hardening phenomenon from Chapter 2 and the recent advances in machine learning field concerning decomposition process for SVM\cite{steinwart2011training}, we propose a combined single direction searching strategy in CSVR training process which can approximately maximize the gain of the sub dual objective functions whose work set size are two.
@@
   Furthermore, we show that channel hardening phenomenon can be further exploited in CSVPD to reduce the computational complexity and simplify the implementation of the algorithm for LS-MIMO systems.
-Finally, we compare the performance of CSVPD aided likelihood ascend search (LAS) detector and CSVPD aided parallel interference cancellation with ordering (OPIC) detector with MMSE-LAS and MMSE-OPIC.
-These results demonstrate the potential of CSVPD to be utilized as a preliminary detector that can improve the LS-MIMO detectors whose performances are influenced by the reliability of initial solutions.
+
+   Finally,  we compare the performance of CSVPD aided likelihood ascend search (LAS) detector (CSVPD-LAS) and CSVPD aided parallel interference cancellation with ordering (OPIC) detector (CSVPD-OPIC) with MMSE-LAS and MMSE-OPIC.
+The simulation results demonstrate the capability of CSVPD to be utilized as a preliminary detector to generate more reliable initial solutions.
 
 \section{Brief Introduction to $\epsilon$-Support Vector Regression ($\epsilon$-SVR)}
+\subsection{primal Objective Function}\label{DualityForm}
   Suppose we are given a training data $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the size of the training data set, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
@@
 In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
-Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
+
+\subsection{Cost Function}\label{cost function}
+The performance of SV regression is significantly depends on the choice of the cost functions$R(\xi_{i})+R(\hat{\xi}_{i})$ \cite{smola1998connection}\cite{muller1997predicting}, 
+The optimal cost function choice in (\ref{primal optimization problem}) can be determined based on maximum likelihood (ML) principle.
+Assume the data samples $\mathbf{x}_{i}$ in data set are iid, Let $f_{true}(\mathbf{x}_{i}), i=1,2,\cdots L$ denotes true regression function.
+the underlying assumption is $y_{i}=f_{true}(\mathbf{x}_{i})+\varepsilon_{i}, i=1,2,\cdots, L$, $\varepsilon_{i}$ denotes additive noise of the $i$th data sample, with probability density function (pdf) $Pr(\cdot)$.
+Let $P(\cdot)$ denotes the pdf of $y_{i}$.
+Based on ML principle we want to
+\begin{eqnarray}
+\nonumber
+\max_{f}\quad \prod_{i=1}^{L}P(y_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}P(f(\mathbf{x}_{i})+\varepsilon_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}Pr(\varepsilon_{i})=\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))\\
+\label{cost function1}
+\end{eqnarray}
+Take the logarithm of $\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))$, (\ref{cost function1}) is equivalent to 
+\begin{eqnarray}
+\max_{f} \sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
+\label{cost function2}
+\end{eqnarray}
+(\ref{cost function2}) is equivalent to 
+\begin{equation}
+\min_{f}-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
+\label{cost function3}
+\end{equation}
+Therefore, the cost function of $i$th input-out data sample, denoted by  $c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))$ can be defined as 
+\begin{equation}
+c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))\varpropto -\log(Pr(y_{i}-f(\mathbf{x}_{i}))).
+\label{cost function4}
+\end{equation}
+Thus (\ref{cost function3}) is equivalent to 
+\begin{equation}
+\min_{f}\quad  \sum_{i=1}^{L}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
+\label{Total risk function}
+\end{equation} 
+%In $\epsilon$-SVR, in order to provide more flexibility to precision control, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{cost function3}).
+%\begin{eqnarray}
+%|u|_{\epsilon}=\left\{\begin{array}{ll}
+%0   &if\quad |u|<\epsilon\\
+%|u|-\epsilon  &otherwise\\
+%\end{array}\right.
+%\label{Vepsilon}
+%\end{eqnarray}
+In the discrete time model of LS-MIMO systems in (\ref{discrete time MIMO systems}), the additive white noise is Gaussian distributed, thus $-\log(Pr(\varepsilon_{i}))\varpropto \frac{1}{2}\varepsilon^{2}_{i}$, based on (\ref{cost function4}), the final form of cost function in SVD can be written as
+\begin{equation}
+c_{LS-MIMO}(\mathbf{x}_{i}, y_{i} f(\mathbf{x}_{i}))= \frac{1}{2}(y_{i}-f(\mathbf{x}_{i}))^{2},
+\label{final cost function}
+\end{equation}  
+In $\epsilon$-SVR, the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ are used to cope with the outliers of $\epsilon$-tube caused by additive noise, that is  
 \begin{eqnarray}
@@
 \end{eqnarray} 
-Because the deviation between the estimates $g(\mathbf{x}_{i})$ and the observation $y_{i}$ as defined in \ref{regression estimates} can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
-That is $\xi_{i}\hat{\xi}_{i}=0$.
+If $\epsilon$ is set to be zero, that (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}) can be rewritten as 
+\begin{eqnarray}
+\label{definition2 of slack variable1}
+\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b)\\
+\label{definition2 of slack variable2}
+\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}).
+\end{eqnarray} 
+From (\ref{definition2 of slack variable1}) and (\ref{definition2 of slack variable2}), there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero. That is $\xi_{i}\hat{\xi}_{i}=0$. 
+By defining $R(u)=\frac{1}{2}u^{2}$ in (\ref{primal optimization problem}), we have  
+\begin{equation}
+R(\xi_{i})+R(\hat{\xi}_{i})=\frac{1}{2}\xi^{2}_{i}+\frac{1}{2}\hat{\xi}^{2}_{i}=\frac{1}{2}(y_{i}-f(\mathbf{x}_{i}))^{2}=c_{LS-MIMO}(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))
+\label{final form of cost function in LS-MIMO}
+\end{equation} 
+In conclusion, the cost function in LS-MIMO CSVD is defined as 
+\begin{equation}
+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))=\frac{1}{2}(y_{i}-f(\mathbf{x}_{i}))^{2},
+\label{LS-MIMO cost function}
+\end{equation}
+\subsection{Dual Objective Function}\label{dual objective Function}
+According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier.
+The Lagrange function is given by
+\begin{eqnarray}
+\nonumber
+L(\mathbf{w}, b, \xi_{i}, \hat{\xi}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})=
+\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{L}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
+\nonumber
++\sum_{i=1}^{L}\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\sum_{i=1}^{L}\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})\\
+s.t. \left\{\begin{array}{cc}
+\eta_{i}, \hat{\eta}_{i}, \alpha_{i}, \hat{\alpha}_{i}\geq 0, i=1,2,\cdots L\\
+\xi_{i}, \hat{\xi}_{i}\geq  0, i=1,2,\cdots L\\
+\end{array}\right.
+\label{lagrange duality1}
+\end{eqnarray}
+where $\eta_{i}$, $\hat{\eta}_{i}$, $\alpha_{i}$, $\hat{\alpha}_{i}$ are Lagrange multipliers.
+
+The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the primal constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
+Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.
+
+Assume a constraint optimization problem is given by 
+\begin{eqnarray}
+\nonumber
+\min_{\mathbf{w}} \quad f(\mathbf{w})\\
+s.t. \quad c_{i}(\mathbf{w})\leq 0, i=1,2,\ldots L,
+\label{constraint optimization problem}
+\end{eqnarray}
+its Lagrange function is given by 
+\begin{equation}
+L(\mathbf{w}, \mathbf{a})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),
+\label{orginal Lagrange}
+\end{equation}
+where $\mathbf{a}=[a_{1},a_{2},\ldots, a_{L}]^{T}$ denotes the vector consist of Lagrange multipliers.
+ Based on Theorem 6.21 in \cite{scholkopf2002learning}, a variable pair $[\bar{\mathbf{w}}, \bar{\mathbf{a}}]$ is the solution to (\ref{constraint optimization problem}) if and only if the following inequalities are satisfied
+ \begin{equation}
+ L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
+ \label{KKT inequalities}
+ \end{equation}
+These inequalities (also called saddle point conditions) holds if and only if KKT conditions holds (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
+\begin{eqnarray}
+\label{original KKT condition1}
+\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, \mathbf{a})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\
+\label{original KKT condition2}
+\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\
+\label{original KKT condition3}
+\bar{a}_{i}c_{i}(\bar{\mathbf{w}})=0, i=1,2,\ldots L
+\end{eqnarray}
+Therefore, KKT conditions are the necessary and sufficient conditions for optimality.
+In order to satisfy the first inequality in (\ref{KKT inequalities}), (\ref{original KKT condition1}) has to hold,
+applying (\ref{original KKT condition1}) to (\ref{lagrange duality1}), which are  
+\begin{eqnarray}
+\label{partial1}
+\partial_{\mathbf{w}} L=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\
+\label{partial2}
+\partial_{\xi_{i}}L=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\
+\label{parial3}
+\partial_{\hat{\xi}_{i}}L=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\
+\label{partial4}
+\partial_{b}L=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber
+\end{eqnarray}
+Then by substituting (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}), (\ref{lagrange duality1}) can be rewritten as :
+\begin{eqnarray}
+\nonumber
+\theta(\alpha_{i}, \hat{\alpha}_{i})=\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[R(\xi_{i})+R(\hat{\xi}_{i})]-\sum_{i=1}^{L}[(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}\\
+\nonumber
++(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}[y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}]+\\
+\sum_{i=1}^{L}\hat{\alpha}_{i}[\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i}]
+\label{lagrange duality1 inter}
+\end{eqnarray}
+notice in (\ref{partial4}), $\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha}_{i})=0$, define $\tilde{R}(u)=R(u)-uR^{'}(u)$, (\ref{lagrange duality1 inter}) can be further simplified to
+\begin{eqnarray}
+\nonumber
+\theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i})]\\
++\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
+\label{dual objective function1}
+\end{eqnarray}
+In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold.
+A $\mathbf{w}$ that satisfies the conditions in (\ref{original KKT condition2}) is in the feasible region defined by inequality constraints as mentioned (\ref{constraint optimization problem}).
+In $\epsilon$-SVR, this condition is satisfied by making use of the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ defined in (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}).
+Define that $\tilde{\mathbf{w}}$ is in the feasible region and satisfies the conditions in (\ref{original KKT condition1}), notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\tilde{\mathbf{w}}, \mathbf{a})$, thus yielding the dual optimization problem, which is given by
+\begin{eqnarray}
+\nonumber
+\max_{\mathbf{a}}L(\tilde{\mathbf{w}},\mathbf{a})\equiv\max_{\alpha_{i}, \hat{\alpha}_{i}}\quad \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i}))\\
++\sum_{i=i}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
+\label{dual optimization function2}
+\end{eqnarray}
+Define $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{L}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{L}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{L}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{L}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0, $\mathbf{R}_{\xi}=[\tilde{R}(\xi_{1}), \tilde{R}(\xi_{2}), \ldots, \tilde{R}(\xi_{L})]^{T}$, $\mathbf{R}_{\hat{\xi}}=[\tilde{R}(\hat{\xi}_{1}), \tilde{R}(\hat{\xi}_{2}), \ldots, \tilde{R}(\hat{\xi}_{L})]^{T}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes a component of data kernel matrix at $i$th row and $j$th column.
+An alternative vector form of (\ref{dual optimization function2}) can be written as
+\begin{equation}
+\max_{\mathbf{a}, \hat{\mathbf{a}}}\theta(\mathbf{a},\hat{\mathbf{a}})=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon \mathbf{e})^{T}\mathbf{a}+(-\mathbf{y}-\epsilon\mathbf{e})^{T}\mathbf{\hat{a}}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
+\label{dual objective alternative}
+\end{equation} 
+We define the following $2L$ vectors 
+$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2L}$, 
+\begin{eqnarray}
+[\mathbf{v}]_{i}=\left\{\begin{array}{ll}
+1\quad i=1,\ldots, l\\
+-1\quad i=l+1,\ldots, 2l\\ 
+\end{array}\right.
+\end{eqnarray}
+(\ref{dual objective alternative}) can also be reformulate as 
+%\newcommand{\mysmallarraydecl}{\renewcommand{%
+%\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
+%\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
+%\renewcommand{\baselinestretch}{1.1}%
+%\settowidth{\normalbaselineskip}{\scriptsize
+%\hspace{\baselinestretch\baselineskip}}%
+%\setlength{\baselineskip}{\normalbaselineskip}%
+%\setlength{\jot}{0.25\normalbaselineskip}%
+%\setlength{\arraycolsep}{2pt}}
+%\begin{equation}
+%\max_{\mathbf{a}^{*}}\quad \theta(\mathbf{a}^{*})=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+%\mathbf{K}& -\mathbf{K}\\
+%-\mathbf{K}& \mathbf{K}
+%\end{IEEEeqnarraybox*}\right]
+%\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
+%\label{vectorize dual optimization function}
+%\end{equation}
+
+Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor the proximity of the current solution and the optimal solution.
+Thus it can be used as a stopping criterion.
+In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by
+\begin{eqnarray}
+\left\{\begin{array}{cc}
+\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
+\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
+(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
+\end{array}\right. 
+\label{KKT complimentary}
+\end{eqnarray}
+Based on the definitions of slack variables in (\ref{definition of slack variable1}) an (\ref{definition of slack variable2}), only when there is a outlier exists, $\xi_{i}$ or $\hat{\xi}_{i}$ can be non zero, that is
+\begin{equation}
+\xi_{i} or \hat{\xi}_{i}=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
+\label{definition of slack variable3}
+\end{equation} 
+because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $y_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig.
+\ref{epsilon-SVR}.
+Therefore at most one of $(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})$  and $(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})$ can be zero.
+In order to satisfy the KKT complementary conditions in (\ref{KKT complimentary}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
+
+Therefore the complete KKT complementary conditions of $\epsilon$-SVR is given by
+\begin{eqnarray}
+\left\{\begin{array}{cc}
+\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
+\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
+(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
+\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots L
+\end{array}\right. 
+\label{complete KKT complimentary}
+\end{eqnarray}
 
@@
 \section{CSVPD-LAS versus MMSE-LAS}
+The single solution based metaheuristics which are also defined as trajectory methods, start from an initial solution and the search process performs on a single solution at any time as a trajectory in the searching space.
+In resent years, several single solution based metaheuristic algorithms are applied to LS-MIMO detection problem, such as likelihood ascend searching (LAS) algorithm and variants\cite{vardhan2008low}\cite{cerato2009hardware}\cite{li2010multiple} and Tabu search algorithms and variants\cite{srinidhi2011layered}\cite{datta2010random}.
 \section{CSVPD-OPIC versus MMSE-OPIC}

### 2015-11-18 Thesis Draft Tianpei Chen/Thesis Draft/C-GA.tex
test the uniform dual objective function optimization

@@
 
-\chapter{Low Complexity Near Optimal Hybrid Detector based on Genetic Algorithm}
+\chapter{Low Complexity Near Optimal Hybrid Detector based on Genetic Algorithm}\label{Chapter GA}
 In the previous chapter, we introduce two CSVPD aided local search based algorithms, and show the improvement CSVD-LAS -OPIC comparing to MMSE-LAS -OPIC.    
 a current trend is the hybridization of of single solution based metaheuristics algorithms in population-based ones, working as intelligent subordinate heuristic operators.
-In this chapter, we introduce Hybrid Genetic Algorithms which utilizes OPIC as a genetic operator and accelerate the revolution process comparing to random revolution, in addition the performance of the proposed algorithm can be further improved by the hybridization with the principle from neighbour variable search.
-\section{Genetic Algorithm}
+In this chapter, we introduce Hybrid Genetic Algorithms which utilizes OPIC as a genetic operator and accelerate the revolution process comparing to random revolution.
+Furthermore, instead of randomly generated initial population, the solution of the CSVPD is fed to Hybrid GA and the initial generation consists of the neighbour of the initial solution from CSVPD.
+\section{CSVPD aided Hybrid Genetic Algorithm}
+Genetic Algorithm (GA) is one of the population-based metaheuristic algorithms and can be viewed as a computational model of natural biological evolution process.
+GA works iteratively and in each iteration it handles a fixed size population of individuals.
+A number of intelligent genetic operators are used to update the population.
+Usually the individuals are a string of symbols that represent a candidate solution to the problems.
+GA has been applied in Code Division Multiple Access (CDMA) detection problem\cite{juntti1997genetic}\cite{ergun2000multiuser}.
+
+Figure (\ref{}) shows the flow chart of the proposed hybrid GA.
+In the beginning, the initial solution of CSVPD is fed to GA, a initial population of solutions are generated based on this initial solution, then in each iteration, each candidate solution is evaluated and selected by fitness function.
+The elites are selected as parents which can generate offspring.
+The offsprings are generated by recombining a pair of parents, this process is called crossover.
+Then mutation operates to offsprings with a given possibility.
+OPIC is integrated in GA as an operator that can accelerate the process that GA approximate to optimal solution.
+The populations is finally reconstructed by the parents and their offsprings.
+The best solution is chosen when the stopping criteria satisfied.
+
+\subsection{Initialization}
+\subsection{Selection}
+\subsection{Mutation}
+\subsection{OPIC} 
+\subsection{Stopping Criteria}

### 2015-11-18 Thesis Draft Tianpei Chen/Thesis Draft/C-Intro.tex
test the uniform dual objective function optimization

@@
 %Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
-Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a variety of metaheuristic based local search algorithms invoked from machine learning field\cite{chockalingam2010low} have been proposed for large MIMO systems.
+The key challenge in designing Large-Scale MIMO (LS-MIMO) detectors is to reduce complexities while maintaining high performances.
+Given the redundant diversity gain potential provided by LS-MIMO\cite{oestges2010mimo} that can only be achieved at very high Signal to Noise Ratio (SNR), one may consider to sacrifice the redundant diversity gains in order to reduce complexities.
+Furthermore, the ML criterion of MIMO detection stated in (\ref{MLD}) indicates MIMO detection can be naturally classified as a Combinatorial Optimization (CO) problem, that consist of the search for the optimal solution in a discrete and finite set.
+
+Based on the aforementioned situations, the metaheuristics algorithmic frameworks are of intense research interest in LS-MIMO detection in recent years.
+Metaheuristics refer to the high level algorithmic strategies that guide subordinate heuristics iteratively by combining different intelligent learning operations.
+Metaheuristics can explore and exploit the searching space efficiently and find near optimal solutions without costing high complexities.
+The class of algorithms includes but not restrict to Iterative Local Search (ILS), Tabu Search (TS), Simulated Annealing (SA), Genetic Algorithms (GA) and Ant Colony Optimization (ACO).
+
+Therefore besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a variety of metaheuristic based local search algorithms invoked from machine learning field\cite{chockalingam2010low} have been proposed for LS-MIMO systems.
 These algorithms have complexities that are comparable or slightly higher comparing to MMSE detector and near-optimal performance.

### 2015-11-18 SVR for large MIMO/RSVR Matlab Code documented/MMSE.m

@@ -1,4 +1,4 @@
-function [ symOut ] = MMSE( y, H, SNRd, M, pav )
+function [ symOut, outlier ] = MMSE( y, H, SNRd, M, pav )
 %Minimum Mean Square Error Detector
 % Rectangular_QAM_slicer performs slicing based on the symbol constellation
 % alphabet

### 2015-11-18 SVR for large MIMO/RSVR Matlab Code documented/RSVD.m

@@ -1,7 +1,8 @@
 function [ symOut] = RSVD( H,  y, SNRd,  M, pav, C, tol , epsilon)
 %real SVR detecor  
 %OUTPUT
-% symOut: the estimated regression coefficience vector (sliced by symbol constellation alphabet) 
+% symOut: the estimated regression coefficience vector (sliced by symbol constellation alphabet)
+% outlier: the number of extreme case before slicing
 
 
 %Input
@@ -13,7 +14,7 @@ function [ symOut] = RSVD( H,  y, SNRd,  M, pav, C, tol , epsilon)
 % C: constant to control the tradeoff between regularization term and
 % outlier penaty term
 % epsilon: epsilon for precision control 
-% tol: tolerance of the duality gap that determine when the algorithm stops  
+% tol: tolerance of the duality gap that determine when the algorithm stops 
 
 
 
@@ -116,6 +117,13 @@ Phi=Phi_new;  %update Phi
 end
 %% Reconstruct regression coefficience vector based on lambda
 symOut_tmp=H'*lambda;
+% if(M==2)
+%     d=sqrt(pav);
+% else
+% d=sqrt(3*pav/(2*(M-1)));
+% end
+% Q=ceil(sqrt(M));  % the size of one dimension of symbol constellation
+% outlier=length(find(symOut_tmp>(Q-1)*d))+length(find(symOut_tmp<-(Q-1)*d));
 if(length(symOut_tmp)==2)
     symOut=symOut_tmp(1)+1i*symOut_tmp(2);
 else

### 2015-11-18 SVR for large MIMO/real SVR matlab/CSVR/Clipping Test/RSVD_explicit.m

@@ -1,0 +1,177 @@
+function [ symOut] = RSVD_explicit( H,  y, SNRd,  M, pav, C, tol , epsilon)
+%real SVR detecor  
+%OUTPUT
+% symOut: the estimated regression coefficience vector (sliced by symbol constellation alphabet) 
+
+
+%Input
+% H: data sample matrix (input) 
+% y: data sample vector (output)
+% M: M-QAM 
+% pav: average power of the transmit symbols
+% SNRd: receive signal to noise ratio 
+% C: constant to control the tradeoff between regularization term and
+% outlier penaty term
+% epsilon: epsilon for precision control 
+% tol: tolerance of the duality gap that determine when the algorithm stops  
+
+
+
+
+N=length(H(1,:));  %the dimentsion of input 
+L=length(H(:,1));  %the number of input
+lambda=zeros(L,1);  %dual optimization variable vector
+sigma=zeros(L,1); %sigma=lambda_new-lambda
+Phi=zeros(L,1);   %intermediate variable Phi
+G=[]; %duality gap
+Theta=[]; %dual objective function
+Chi=[];  %noise Term
+ratio=[];  %ratio=abs(G)/(abs(G)+abs(Theta));
+iteration=1; %iteration time
+%% Initialization
+K=H*H';   %calculate kernle matrix
+Phi=y; %intermediate variable
+G(1)=0;
+Theta(1)=0;
+Phi_tmp=abs(Phi)-epsilon;
+Phi_tmp=Phi_tmp(find(Phi_tmp>0));
+Chi(1)=norm(Phi_tmp)^(2);
+Theta(1)=-0.5*C*Chi(1);
+G(1)=-2*Theta(1);
+ratio(1)=G(1)/(G(1)+Theta(1));
+%% Quadratic Programming of the dual objective function 
+while(ratio(iteration)>tol)   %performs update to dual optimization variables lambda until the duality gap satisfies the tolerance
+
+delta=zeros(L,1);  %gain of the sub dual objective function 
+sgn=zeros(L,1);  %record the sign of update value of dual optimizaition variables
+%% single direction searching 
+for count=1:L
[…]

### 2015-11-18 SVR for large MIMO/real SVR matlab/CSVR/Verification Test/Verification_SNR.m

@@ -4,9 +4,9 @@ clear all;
 tic
 SNR=2:2:60;   %receive signal to noise ratio in dB
 SNRd=10.^(SNR./10);   %receive signal to noise ratio decimal
-M=150;   %number of training data samples
+M=30;   %number of training data samples
 M_t=1000; %number of testing data samples
-N=150; %the dimensions of the linear function
+N=30; %the dimensions of the linear function
 pav=1/N;      %the average power of the regression coefficiences
 w=complex(normrnd(0, sqrt(pav/2), [N,1]), normrnd(0, sqrt(pav/2),[N,1]));   %the true regression coeffeciences
 % Pt=norm(w)^(2);   %the total power of the true function 
@@ -15,8 +15,8 @@ d=zeros(M,1);   %the observations in training part
 w_svr=zeros(M,1); %the regression estimation coefficiences from SVR
 noiseV=1./SNRd;
 realization=1e2;  %the realization time
-epsilon=1e-7;
-C=1;
+epsilon=0;
+C=10;
 tol=1e-3;
 MSE_training=zeros(length(SNR),1);  %training output MSE for SVR
 MSE_svrco_training=zeros(length(SNR),1);  %training MSE for coefficiences vector for SVR
@@ -26,11 +26,12 @@ MSE_mmseco_training=zeros(length(SNR),1); %training MSE for coefficiences vector
 MSE_mmse_testing=zeros(length(SNR),1); %testing MSE for MMSE
 
 %% generate the file to record the simulation results
-fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\Verification Test\Test Data\MSE_SNR.txt', 'a');
+fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\Verification Test\Test Data\MSE_coefficientVector.txt', 'a');
 fprintf(fid, '-------------\n');
 fprintf(fid, 'this document record the data of SVR from testing\n');
 fprintf(fid, 'this document compare the output of SVR and MMSE regression from the view of SNR\n');
 fprintf(fid, 'this document also record the MSE comparison of the regression coefficience vector (coefficience vector) of SVR and MMSE\n');
+fprintf(fid, 'this document consider the influence of the weight of regularization term to the estimation accuracy of coefficience vector\n');
[…]

### 2015-11-18 Thesis Draft Tianpei Chen/Thesis Draft/C-ChannelHardening.tex

@@
 BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
-The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
+The transmitted symbol vectors $\mathbf{s}\in |\mathbb{O}|^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
 Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian random variable with zero mean and unit variance.
@@
 The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
+
+The Optimal Maximum Likelihood Detector (MLD) for MIMO system is given by
+\begin{equation}
+\hat{\mathbf{s}}=\min_{\mathbf{s}\in |\mathbb{O}|^{N_{t}}}||\mathbf{y}-\mathbf{H}\mathbf{s}||^{2},
+\label{MLD}
+\end{equation}

### 2015-11-18 Thesis Draft Tianpei Chen/Thesis Template/A-A.tex

\resetdatestamp

\chapter{\LaTeX{} Macros}
\label{A:LaTeXmacros}

The \LaTeX{} commands and macros used in formatting the title page for
 this document are shown in this appendix.

\section{Thesis Preamble}

The commands used to create the title page for a thesis are shown
 below.
The McGill University crest is brought in via a macro \verb|McGillCrest|
 which allows for setting the size and colour of an imported PostScript
 file which contains the actual crest.
The title page also includes a red separator line.

### 2015-11-18 Thesis Draft Tianpei Chen/Thesis Template/C-Intro.tex

\resetdatestamp

\chapter{Thesis Organization}

A thesis should present results in a scholarly fashion.
The following discusses the organization of a thesis, such as would be
 appropriate to presenting research results pertaining to Electrical \&
 Computer Engineering.

\section{Scope of a Thesis}

The terms of reference differ for a Master's Thesis and a Doctoral Thesis.
For the Master's Thesis, the Faculty of Graduate Studies and Research at
McGill University \cite{McGillTG:P1994} gives the following guidelines.

The terms of reference state that ``In most disciplines, Master's theses will
 not exceed 100 pages.''

### 2015-11-20 Thesis Draft Tianpei Chen/Thesis Draft/C-GA.tex
update PL

@@
 Figure (\ref{}) shows the flow chart of the proposed hybrid GA.
-In the beginning, the initial solution of CSVPD is fed to GA, a initial population of solutions are generated based on this initial solution, then in each iteration, each candidate solution is evaluated and selected by fitness function.
+In the beginning, the initial solution of CSVPD is fed to GA, a initial population of solutions are generated based on this initial solution, then in each iteration, each candidate solution is evaluated and selected by the fitness function.
 The elites are selected as parents which can generate offspring.
@@
 The populations is finally reconstructed by the parents and their offsprings.
-The best solution is chosen when the stopping criteria satisfied.
+The best solution is chosen based on the fitness function when the stopping criteria satisfied.
 
 \subsection{Initialization}
+Let $\mathbb{P}_{i}$ denotes the $i$th generation set consists of $|\mathbb{P}|$ symbol vectors, which is fixed in different generations.
+The estimated symbol vector from SVPD serves as the generation seed for the initial generation.
+The initial generation is generated by flipping a fix number of symbols to the nearest point in the symbol constellation alphabet randomly.
+
+Let $\mathcal{F}$ denotes the number of symbols to be flipped.
+By flipping, a "$\mathcal{F}-coordinate-away$" neighbourhood symbol vector is generated, where "$\mathcal{F}-coordinate-away$" denotes the objective symbol vector has $\mathcal{F}$ coordinates different from the original symbol vector.
+
+We now use a binary sequence generated by SVPD to illustrate how the flipping process works, let $b_{SVPD}\in \mathbb{B}^{N_{t}}, \mathbb{B}=[+1, -1], N_{t}=8$ denotes the the binary sequence generated by SVPD,
+\begin{equation}
+b_{SVPD}=[1, -1, -1, 1, -1, 1, 1, -1],
+\end{equation}  
+$\mathcal{F}=1$, means there is one symbol difference between the original symbol vector and the objective symbol vector after flipping.
+Let $b_{1}, b_{2}, \ldots b_{|\mathbb{P}|-1}$ denotes the individuals in the initial generation which are generated by perturbing seed vector $b_{SVPD}$.
+Fig.\ref{random flipping} shows how this random flipping scheme works.
+\begin{figure}
+\centering
+\def\svgwidth{\columnwidth}
+\include{randomFlipping.tex_pdf}
+\caption{Random Flipping with $\mathcal{F}=1$}
+\label{random fipping}
+\end{figure}
+The initial generation is $\mathbb{P}=[b_{SVPD}, b_{1}, b_{2}, \ldots b_{|\mathbb{P}|-1}$.
 \subsection{Selection}
+The individuals in each generation are evaluated by the fitness function. In LS-MIMO detection problem. Euclidean distance is used as the fitness function, given by 
+\begin{equation}
+f(\mathbf{s_{i}})=||\mathbf{y}-\mathbf{H}\mathbf{s}_{i}||^{2}, 
+\label{fitness function}
+\end{equation}
+where $\mathbf{s}_{i}$ denotes the $i$th individual symbol vector in the generation, the individual with the smallest fitness function value is the fittest candidate (elite) in the generation.
+
+In each generation, the individuals with small $f(\mathbf{s}_{i})$ are chosen as the parents to generate offsprings, the offsprings are generated by recombining the parent symbol vectors, this process is recombination or crossover.
+In crossover process, crossover point is randomly chosen in parent symbol vectors and the subpart of a pair of parent symbol vectors up to that crossover point are interchanged.
+A simple cased of this process is shown in Fig.\ref{crossover}.
+\begin{figure}
+\centering
+\def\svgwidth{\columnwidth}
+\include{crossover.tex_pdf}
+\caption{Crossover operation to a pair of parent binary sequence}
+\label{crossover}
+\end{figure}
 \subsection{Mutation}
+The GA in operates in a sub searching space, which is initially, determined by the $\mathcal{F}$ neighbourhood of the seed symbol vector.
+The major difficulties in the revolution process in the convergence to the local minima of the sub searching space.
+Mutation is a strategy that helps GA to escape from local minima.
+Mutations operates by randomly perturbation of a small number of coordinates in offspring symbol vectors with a small possibility defined by the users.
+Fig.\ref{mutation} shows how mutation works.
+\begin{figure}
+\centering
+\def\svgwidth{\columnwidth}
+\include{mutation.tex_pdf}
+\caption{Mutation operation to one bit in binary sequence}
+\label{mutaion}
+\end{figure}
 \subsection{OPIC} 

### 2015-11-27 Report Nov 2015/Report Nov 2015.tex
Report Nov 2015

--- 2015-10-14 Report Aug 5 2015/Report Aug 2015.tex
@@
 %\documentclass[journal]{IEEEtran}
-\documentclass[12pt, draftclsnofoot, onecolumn]{IEEEtran}
+\documentclass[10pt, draftclsnofoot, onecolumn]{IEEEtran}
 %\documentclass[12pt,paper,final]{article}
@@
 \begin{document}
-\begin{spacing}{2}
-%\doublespacing
 %
@@
 % Do not put math or special symbols in the title.
-\title{Report: Complex Support Vector Detector for Large MIMO System}
-
+\title{Justification for Employing Support Vector Detector in Large-Scale MIMO Systems}
 %
@@
 %
-\author{Tianpei Chen\\
-Department of Electrical and Computer Engineering\\
-McGill University\\
-\today}
 
@@
 %\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
+
+\author{Tianpei Chen\\
+Department of Electrical and Computer Engineering\\
+McGill University, Montreal, Quebec, Canada\\
+\today}
 
@@
 % in the abstract or keywords.
-%\begin{abstract}
-%The abstract goes here.
-%\end{abstract}
+\begin{abstract}
+This report provides the justifications for employing support vector regression (SVR) in the detection problem of Large-Scale MIMO (LS-MIMO) systems, which have medium or full loading factor (number of transmit antennas is close or equal to the number of receive antennas).
+Under this condition, LS-MIMO detection in the view of statistical learning is a multidimensional linear regression problem, given a small training data set.
+We compare linear detectors (LD) (zero forcing (ZF) and minimum mean square error (MMSE)) with SVR in view of statistical learning theory and demonstrate the better performance that SVR possess over LD in the high spectrum efficiency LS-MIMO systems with medium and full loading factor.
+\end{abstract}
 
 % Note that keywords are not normally used for peerreview papers.
-%\begin{IEEEkeywords}
-%IEEEtran, journal, \LaTeX, paper, template.
-%\end{IEEEkeywords}
+\begin{IEEEkeywords}
+Large-Scale MIMO, full loading, statistical learning theory, support vector regression, linear detectors
+\end{IEEEkeywords}
 
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}
+%\IEEEpeerreviewmaketitle
+
+\section{Large-Scale MIMO System Model and Equivalent Regression Estimation Problem}
 % The very first letter is a 2 line initial drop letter followed
@@
 %\hfill September 17, 2014
-  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment.
-The promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} and long-term evolution (LTE)\cite{3GLTE}.
-The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve spectrum efficiency) and diversity gain (better reliability of communication link) are obtained by exploiting the spatial domain.
-Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously.
-This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
-
-  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving ends.
-The uplink detector is one of the key components in a large MIMO system.
-With orders magnitude more antennas at the BS, benefits and challenges coexist in designing of detection algorithms for the uplink communication of large MIMO systems.
-On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexities of the algorithms become crucial to make the system practical.
-
-Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams.
-However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with the number of transmitted antennas, which is prohibitive for practical applications.
-
-As alternatives to MLD, linear detectors (LD) such as zero-forcing (ZF) and minimum mean square error (MMSE) with optimized ordering sequential interference cancellation (ZF-OSIC, MMSE-OSIC) are exploited in V-BLAST architecture\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast},  however the performance of ZF-OSIC and MMMSE-OSIC are inferior comparing to MLD.
-
-Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes the lattice structure of MIMO systems, which can achieve optimal performance with relatively much lower complexity comparing to MLD.
-However, SD has two major shortages that make it problematic to be integrated into a practical systems.
-The first shortage is SD has various complexities under different signal to noise ratios (SNR), while a constant processing data rate is required for hardware.
-The second shortage is the complexity of SD still has a lower bound that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
-The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different values of SNR.
-The FCSD inherits the principle of list based searching algorithms, which first generate a list of candidate symbol vectors and then the best candidate is chosen as the solution.
-The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC (sel-MMSE-OSIC)\cite{radji2009interference}.
-However, all these list based searching algorithms have the same shortage - their complexities increase exponentially with the number of transmit antennas and the order of modulation scheme\cite{radji2009interference}.
-Therefore, such algorithms are prohibitive when it comes to a large number of antennas or a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.
-
-%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
-Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of metaheuristic based detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance.
-such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
-Tabu search based algorithms which have superior performances compared to LAS detectors because of the efficient local minima exit strategy (e.g.
-Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g.
-Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g.
-Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) .
-Moreover, element based Lattice Reduction (LR) aided algorithms were also proposed to  large MIMO systems.\cite{zhou2013element}.
-
-Firmly grounded in framework of statistical learning theory, the Support Vector Machine (SVM) technique has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction.
-the SVM method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can provide good generalization performance\cite{scholkopf2002learning}.
-
-Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
-Moreover, the kernel based methods\cite{scholkopf2002learning} were proposed which solve nonlinear learning tasks by mapping input data samples into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
-This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS).
-Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.
-
-Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual form, which can be solved by Quadratic Programming (QP).
-Decomposition methods were proposed to solve this QP problem by decomposing it into sub QP problems and solving them iteratively\cite{platt1999fast}.
-Therefore, the computational intensive numerical methods can be avoided.
-Decomposition is performed by sub set selection solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets S and N, S is the work set and N contains the remaining optimization variables.
-In each iteration, only the optimization variables in the work set is updated while keeping other optimization variables fixed.
-The Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} is an extreme case of the decomposition solvers.
-An important issue of the sub set selection solvers is the selection of the work set.
-One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring the final converge\cite{osuna1997improved}.
-The SMO algorithm restricts the size of the work set to two.
-A method to train SVM without offset was proposed In\cite{steinwart2011training}, with the comparable performance to the SVM with offset.
-A set of sequential single variable work set selection strategies, which require $O(n)$ searching time are proposed.
-The optimal double variable work set selection strategy, which performs exhaustively searching, however, requires $O(n^{2})$ searching time.
-The authors demonstrate that with the combination of two different proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.
-
-The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets.
-In communication and signal processing area, the channel gains, signals, waveforms etc.
-are all represented in complex form.
-Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain.
-The results in\cite{bouboulis2013complex} demonstrate the better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernels.
-Based on this work, we derive a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR).
-The detector can work in two parallel real SVR channels which can be solved independently.
-Moreover, only the real part of kernel matrix is needed in both channels.
-This means a large amount of computation cost saving can be achieved.
-Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
-is constructed without offset, Therefore, for each real SVR without offset, 
-%in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed.
-By this strategy, two variables can be updated at each iteration, with much smaller searching time.
-Two types of combined single optimization variable selection strategy are proposed based on the work in \cite{steinwart2011training}.
-The proposed combined single optimization variable selection strategy can approximate optimal double optimization variable selection strategy.
-The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
-
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
-
-\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
-\subsection{Regression Model}
-Suppose we are given a training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
-$y_{i}$ denotes output.
-Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Omega}$, $\Omega \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$, $\Omega=V$).
-The regression model (either linear or non-linear) is given by
-\begin{equation}
-y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1,2,\ldots, L
-\label{equation1}
-\end{equation}
-
-\begin{figure}
-\centering
-\def\svgwidth{\columnwidth}
-\input{epsilon-SVR.pdf_tex}
-\caption{$\epsilon$-Support Vector Regression and Risk Functional}
-\label{epsilon-SVR}
-\end{figure}
-
-We present the primal optimization problem directly
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}} f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-s.t. \left\{\begin{array}{ll}
-y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
-\epsilon_{i}, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
-\end{array}\right.
-\label{primal optimization problem}
-\end{IEEEeqnarray}
-In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the solid line represents the estimation of the input-output relation, the area between two dash lines ($\epsilon$-bound) is called $\epsilon$-tube.
-Only those data samples located outside $\epsilon$-tube contribute to the estimation error.
-Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with additive noise of observations, $R(u)$ denotes the cost function.
-The simplest cost function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}.
-For example if the noise is Gaussian distributed, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$.
-The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.
-
-In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
-Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-\label{definition of slack variable1}
-\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
-\label{definition of slack variable2}
-\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon).
-\end{IEEEeqnarray} 
-Because the distance between the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
-That is $\xi_{i}\hat{\xi}_{i}=0$.
-\subsection{Cost Function}\label{cost function}
-The optimal cost function in (\ref{primal optimization problem}) can be derived based on maximum likelihood (ML) principle.
-Assume the data samples $\mathbf{x}_{i}$ in data set are iid, Let $f_{true}(\mathbf{x}_{i}), i=1,2,\cdots L$ denotes true regression function.
-the underlying assumption is $y_{i}=f_{true}(\mathbf{x}_{i})+\xi_{i}, i=1,2,\cdots, L$, $\xi_{i}$ denotes additive noise of the $i$th data sample, with probability density function (pdf) $Pr(\cdot)$.
-Let $P(\cdot)$ denotes the pdf of $y_{i}$.
-Based on ML principle we want to
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{f}\quad \prod_{i=1}^{L}P(y_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}P(f(\mathbf{x}_{i})+\xi_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}Pr(\xi_{i})=\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))\\
-\label{cost function1}
-\end{IEEEeqnarray}
-Take the logarithm of $\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))$, we have
-\begin{IEEEeqnarray}[\relax]{l}
-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
-\label{cost function2}
-\end{IEEEeqnarray}
-maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i})))$, therefore (\ref{cost function1}) is equivalent to 
-\begin{equation}
-\min_{f}-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
-\label{cost function3}
-\end{equation}
-Let $c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))$ denotes the $i$th cost function, which is defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-\log(P(y_{i}-f(\mathbf{x}_{i}))).
-\label{cost function3}
-\end{IEEEeqnarray}
-Thus (\ref{cost function3}) can be rewritten as 
-\begin{equation}
-\min_{f}\quad  \sum_{i=1}^{L}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
-\label{Total risk function}
-\end{equation} 
-In $\epsilon$-SVR, in order to provide more flexibility to precision control, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{cost function3}).
-\begin{IEEEeqnarray}[\relax]{l}
-|u|_{\epsilon}=\left\{\begin{array}{ll}
-0   &if\quad |u|<\epsilon\\
-|u|-\epsilon  &otherwise\\
-\end{array}\right.
-\label{Vepsilon}
-\end{IEEEeqnarray}
-Thus the final form of cost function in $\epsilon$-SVR can be written as 
-\begin{equation}
-\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),
-\label{final cost function}
-\end{equation}
-Consider the cost function term in (\ref{primal optimization problem}),
-\begin{equation}
-\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))
-\end{equation}  
-the cost function term is determined according to the distribution of noise.  
-%where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as
-%\begin{equation}
-%minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f(\mathbf{x})),
-%\label{total cost function}
-%\end{equation} 
-%where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
-%\begin{equation}
-%minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
-%\label{final cost function}
-%\end{equation}
-%where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
-%\begin{eqnarray}
-%\nonumber
-%minimize \quad f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-%s.t. \left\{\begin{array}{ll}
-%y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
-%\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
-%\epsilon, \xi,\hat{\xi} &\geq 0\\
-%\end{array}\right.
-%\label{primal objective function}
-%\end{eqnarray}
-%where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered. 
-\subsection{Lagrange Duality}\label{section lagrange duality}
-According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier.
-The Lagrange function is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L(\mathbf{w}, b, \xi_{i}, \hat{\xi}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})=
-\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{L}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
-\nonumber
-+\sum_{i=1}^{L}\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\sum_{i=1}^{L}\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})\\
-s.t. \left\{\begin{array}{cc}
-\eta_{i}, \hat{\eta}_{i}, \alpha_{i}, \hat{\alpha}_{i}\geq 0, i=1,2,\cdots L\\
-\xi_{i}, \hat{\xi}_{i}\geq  0, i=1,2,\cdots L\\
-\end{array}\right.
-\label{lagrange duality1}
-\end{IEEEeqnarray}
-where $\eta_{i}$, $\hat{\eta}_{i}$, $\alpha_{i}$, $\hat{\alpha}_{i}$ are Lagrange multipliers.
-
-The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the primal constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
-Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.
-
-Assume a constraint optimization problem is given by 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}} \quad f(\mathbf{w})\\
-s.t. \quad c_{i}(\mathbf{w})\leq 0, i=1,2,\ldots L,
-\label{constraint optimization problem}
-\end{IEEEeqnarray}
-its Lagrange function is given by 
-\begin{equation}
-L(\mathbf{w}, \mathbf{a})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),
-\label{orginal Lagrange}
-\end{equation}
-where $\mathbf{a}=[a_{1},a_{2},\ldots, a_{L}]^{T}$ denotes the vector consist of Lagrange multipliers.
- Based on Theorem 6.21 in \cite{scholkopf2002learning}, a variable pair $[\bar{\mathbf{w}}, \bar{\mathbf{a}}]$ is the solution to (\ref{constraint optimization problem}) if and only if the following inequalities are satisfied
- \begin{equation}
- L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
- \label{KKT inequalities}
- \end{equation}
-This inequalities (also called saddle point conditions) yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{original KKT condition1}
-\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, \mathbf{a})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\
-\label{original KKT condition2}
-\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\
-\label{original KKT condition3}
-\bar{a}_{i}c_{i}(\bar{\mathbf{w}})=0, i=1,2,\ldots L
-\end{IEEEeqnarray}
-In order to satisfy the first inequality in (\ref{KKT inequalities}), (\ref{original KKT condition1}) has to hold,
-applying (\ref{original KKT condition1}) to (\ref{lagrange duality1}), which are  
-\begin{IEEEeqnarray}[\relax]{l}
-\label{partial1}
-\partial_{\mathbf{w}} L=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\
-\label{partial2}
-\partial_{\xi_{i}}L=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\
-\label{parial3}
-\partial_{\hat{\xi}_{i}}L=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\
-\label{partial4}
-\partial_{b}L=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber
-\end{IEEEeqnarray}
-Then by substituting (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}), (\ref{lagrange duality1}) can be rewritten as :
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha_{i}, \hat{\alpha}_{i})=\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[R(\xi_{i})+R(\hat{\xi}_{i})]-\sum_{i=1}^{L}[(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}\\
-\nonumber
-+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}[y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}]+\\
-\sum_{i=1}^{L}\hat{\alpha}_{i}[\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i}]
-\label{lagrange duality1 inter}
-\end{IEEEeqnarray}
-notice in (\ref{partial4}), $\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha}_{i})=0$, define $\tilde{R}(u)=R(u)-uR^{'}(u)$, (\ref{lagrange duality1 inter}) can be further simplified to
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i})]\\
-+\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
-\label{dual objective function1}
-\end{IEEEeqnarray}
-In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold.
-A $\mathbf{w}$ that satisfies the conditions in (\ref{original KKT condition2}) is in the feasible region defined by inequality constraints as mentioned (\ref{constraint optimization problem}).
-In $\epsilon$-SVR, this condition is satisfied by making use of the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ defined in (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}).
-Define that $\tilde{\mathbf{w}}$ is in the feasible region and satisfies the conditions in (\ref{original KKT condition1}), notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\tilde{\mathbf{w}}, \mathbf{a})$, thus yielding the dual optimization problem, which is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}}L(\tilde{\mathbf{w}},\mathbf{a})\equiv\max_{\alpha_{i}, \hat{\alpha}_{i}}\quad \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i}))\\
-+\sum_{i=i}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
-\label{dual optimization function2}
-\end{IEEEeqnarray}
-Define $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{L}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{L}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{L}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{L}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0, $\mathbf{R}_{\xi}=[\tilde{R}(\xi_{1}), \tilde{R}(\xi_{2}), \ldots, \tilde{R}(\xi_{L})]^{T}$, $\mathbf{R}_{\hat{\xi}}=[\tilde{R}(\hat{\xi}_{1}), \tilde{R}(\hat{\xi}_{2}), \ldots, \tilde{R}(\hat{\xi}_{L})]^{T}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes a component of data kernel matrix at $i$th row and $j$th column.
-An alternative vector form of (\ref{dual optimization function2}) can be written as
-\begin{equation}
-\max_{\mathbf{a}, \hat{\mathbf{a}}}\theta(\mathbf{a},\hat{\mathbf{a}})=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon \mathbf{e})^{T}\mathbf{a}+(-\mathbf{y}-\epsilon\mathbf{e})^{T}\mathbf{\hat{a}}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
-\label{dual objective alternative}
-\end{equation} 
-We define the following $2L$ vectors 
-$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2L}$, 
-\begin{IEEEeqnarray}[\relax]{l}
-[\mathbf{v}]_{i}=\left\{\begin{array}{ll}
-1\quad i=1,\ldots, l\\
--1\quad i=l+1,\ldots, 2l\\ 
-\end{array}\right.
-\end{IEEEeqnarray}
-(\ref{dual objective alternative}) can also be reformulate as 
+In this section, we present the system model of Large-Scale MIMO (LS-MIMO) systems and the equivalent regression estimation model in view of statistical learning.
+
+\subsection{System Model}
+Consider a uncoded complex LS-MIMO uplink spatial multiplexing (SM) system, uplink means the data streams are transmitted from users to base stations (BS).
+Let $N_{t}$ denotes the number of transmit antennas and $N_{r}$ denotes the number of receive antennas, $N_{r}\geq N_{t}$, define loading factor $\alpha=\frac{N_{t}}{N_{r}}$.
+Typically LS-MIMO systems have hundreds of receive antennas at BS.
+
+Independent bit sequences, which are modulated to complex symbols are transmitted over flat and slow fading channel. The discrete time model of LS-MIMO systems in the complex domain is given by 
+\begin{equation}
+\mathbf{y}_{c}=\mathbf{H}_{c}\mathbf{s}_{c}+\mathbf{n}_{c},
+\label{complex MIMO model}
+\end{equation}
+where $\mathbf{y}_{c}\in \mathbb{C}^{N_{r}\times 1}$ denotes the receive symbol vector, $\mathbf{H}_{c}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading propagation channel matrix.
+Each component of $\mathbf{H}_{c}$ is independent identically distributed (i.i.d), circularly symmetric complex Gaussian (CSCG) random variables with zero mean and unit variance.
+$\mathbf{s}_{c}\in \mathbb{C}^{N_{t}\times 1}$ denotes the transmit symbol vector.
+Each transmit symbol is equally probable and mutually independent, taken from a finite signal constellation alphabet $\mathbb{O}$ (4-QAM, 16-QAM and 64-QAM), $|\mathbb{O}|=M$.
+$\mathbf{s}_{c}\in \mathbb{O}^{N_{t}}$, satisfies $\mathbb{E}(\mathbf{s}_{c}\mathbf{s}^{H}_{c})=\xi_{s}\mathbf{I}_{N_{t}}$, where $\mathbb{E}(\cdot)$ denotes expectation operator, $(\cdot)^{H}$ denotes Hermitian transpose, $\xi_{s}$ denotes the average power of each component in $\mathbf{s}_{c}$, $\mathbf{I}_{N_{t}}\in \mathbb{C}^{N_{t}\times N_{t}}$ is an identity matrix.
+$\mathbf{n}_{c}\in \mathbb{C}^{N_{t}\times 1}$ denotes i.i.d additive white Gaussian noise with zeros mean and satisfies $\mathbb{E}(\mathbf{n}_{c}\mathbf{n}^{H}_{c})=N_{0}\mathbf{I}_{N_{r}}$.
+$N_{0}$ denotes the power spectrum density of each component in $\mathbf{n}_{c}$.
+The signal to noise ratio (SNR) is defined as $\frac{\xi_{s}}{N_{0}}$.
+
+The discrete time model in (\ref{complex MIMO model}) is defined in complex domain, one can transfer this model into an equivalent real-valued model.
+Let $\Re(\cdot)$ denotes the real part and $\Im(\cdot)$ denotes the imaginary part, $\mathbf{y}_{c}, \mathbf{H}_{c}, \mathbf{s}_{c}$ and $\mathbf{n}_{c}$ can be decomposed by
+
 \newcommand{\mysmallarraydecl}{\renewcommand{%
@@
 \setlength{\arraycolsep}{2pt}}
-\begin{equation}
-\max_{\mathbf{a}^{*}}\quad \theta(\mathbf{a}^{*})=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\mathbf{K}& -\mathbf{K}\\
--\mathbf{K}& \mathbf{K}
-\end{IEEEeqnarraybox*}\right]
-\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
-\label{vectorize dual optimization function}
-\end{equation}
-
-Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor the proximity of the current solution and the optimal solution.
-Thus it can be used as a stopping criterion.
-In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
-(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
-(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
-\end{array}\right. 
-\label{KKT complimentary}
-\end{IEEEeqnarray}
-Based on the definitions of slack variables in (\ref{definition of slack variable1}) an (\ref{definition of slack variable2}), only when there is a outlier exists, $\xi_{i}$ or $\hat{\xi}_{i}$ can be non zero, that is
-\begin{equation}
-\xi_{i} or \hat{\xi}_{i}=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
-\label{definition of slack variable3}
-\end{equation} 
-because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $y_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig.
-\ref{epsilon-SVR}.
-Therefore at most one of $(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})$  and $(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})$ can be zero.
-In order to satisfy the KKT complementary conditions in (\ref{KKT complimentary}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
-
-Therefore the complete KKT complementary conditions of $\epsilon$-SVR is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
-(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
-(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
-\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots L
-\end{array}\right. 
-\label{complete KKT complimentary}
-\end{IEEEeqnarray}
-
-%The conditions in (\ref{KKT complimentary}) are called KKT complimentary condition. 
-%Obviously by taking partial derivations of (\ref{lagrange duality1}) with respect to $\mathbf{w}$, $\xi_{i}$, $\hat{\xi}_{i}$ and $b$, $\theta(\alpha_{i},\hat{\alpha}_{i})\leq \Theta(\mathbf{w},\alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})$, notice in $\theta(\alpha_{i}, \hat{\alpha}_{i})$ KKT conditions in (\ref{partial1}) to (\ref{partial4}) are satisfied.
-Therefore, KKT complimentary conditions (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
-Because
-%\begin{equation}
-%\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
-%\end{equation} 
-%where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
-%\begin{IEEEeqnarray}[\relax]{l}
-%g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
-%\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
-%l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
-%\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
-%\nonumber
-%\end{IEEEeqnarray}
-%Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$.
-when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied.
-hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds.
-Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.
-
-%In conclusion, the dual objective function can be written as
-
-\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
-\subsection{System Model}\label{system model}
-  Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna.
-The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
-Typically large MIMO systems have hundreds of antennas at the BS, as shown in Fig {\ref{large MIMO uplink model}}.
-  \begin{figure}[htb]
-  \centering
-  \def\svgwidth{\columnwidth}
-  %\includegraphics[scale=•]{•}
-  \input{largeMIMOuplink.pdf_tex}
-  \caption{Large MIMO uplink system }
-  \label{large MIMO uplink model}
-  \end{figure}
-
-Bit sequences, which are modulated to complex symbols, are transmitted by the users over a flat fading channel. The discrete time model of the system is given by:
-\begin{equation}
-\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},   \label{discrete time MIMO system}
-\end{equation}
-where $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
-BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
-The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian random variable with zero mean and unit variance.
-Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
-
-The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
-\subsection{Complex Regression Model}
- Based on the discrete time model of a large MIMO uplink system of (\ref{discrete time MIMO system}), our regression model is set such that the training data set at the detector are $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of matrix $\mathbf{H}$.
-This yields a regression task without offset $b$ in (\ref{equation1}) :
- \begin{IEEEeqnarray}[\relax]{l}
- y_{i}=f_{true}(\mathbf{h}_{i})+n_{i}, i=1,2\ldots L\\
- \label{regression part1a}
- f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\cdot\mathbf{s}, i=1,2,\ldots, L\\
- \label{regression part1b}
- \end{IEEEeqnarray}
- where $f_{true}()$ denotes the underlying true regression function, $n_{i}$ denotes discrete sample of additive noise.
-In this regression problem, received symbols $y_{i}$ are the observations, $\mathbf{h}_{i}$ are the input data samples, transmitted symbol vector $\mathbf{s}$ contains the regression coefficients.
-We employ complex support vector regression (CSVR) without offset term $b$.
-As shown in (\ref{original KKT condition1}) the first KKT condition is satisfied by finding the saddle point $\bar{\mathbf{w}}$ by taking paritial derivatives of $L(\mathbf{w},a_{i})$ with respect to $\mathbf{w}$.
-Mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) are employed to calculate partial derivatives of Lagrangian function of CSVR in complex manner\cite{bouboulis2011extension}.
-First we generalize our regression model by complex RKHS,
-Define a real RKHS $\mathcal{H}$, $<,>_{\mathcal{H}}$ denotes the corresponding inner product in $\mathcal{H}$.
-define complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $<,>_{\mathbb{H}}$ denotes the corresponding inner products in $\mathbb{H}$.
-Assume $\mathbf{x}, \mathbf{y},\mathbf{z}$ are complex vectors, $\mu$, $\chi$ $\in \mathbb{C}$, In general a complex Hilbert space $\mathbb{H}_{g}$ has the following properties
-\newtheorem{Lemma}{Lemma}
-\newtheorem{Property}{Property}
-\begin{Property}
- $<\mathbf{x},\mathbf{y}>_{\mathbb{H}_{g}}=(<{\mathbf{y},\mathbf{x}}>_{\mathbb{H}_{g}})^{*}$
-\label{CHSProperty1}
-\end{Property}
-
-\begin{Property}
-$<\mu\mathbf{x}+\chi\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}=\mu<\mathbf{x},\mathbf{z}>_{\mathbb{H}_{g}}+\chi<\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}$
-\label{CHSProperty2}
-\end{Property}
-
-\begin{Property}
-$<\mathbf{z}, \mu\mathbf{x}+\chi\mathbf{y}>_{\mathbb{H}_{g}}=\mu^{*}<\mathbf{z},\mathbf{x}>_{\mathbb{H}_{g}}+\chi^{*}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}_{g}}$
-\label{CHSProperty3}
-\end{Property}
-
-\begin{Lemma}
-Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{V}$, define a real RKHS $\mathcal{H}$ that satisfy $<\mathbf{a}, \mathbf{b}>_{\mathcal{H}}=\mathbf{a}^{T}\mathbf{b}$.
-For the corresponding complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $\mathbf{m}, \mathbf{l}\in \mathbb{C}^{V}$,
-$<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$
-\end{Lemma}
-
-\begin{proof} 
-$\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{V}$, and $\mathbf{g}=\Re{(\mathbf{g})}+\imath\Im{(\mathbf{g})}$, $\mathbf{h}=\Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}$.
-From Property \ref{CHSProperty1} and Property \ref{CHSProperty3},
-\begin{IEEEeqnarray}[\relax]{l}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(g)}+\imath\Im{(g)}, \Re{(h)}+\imath\Im{(h)}>_{\mathbb{H}}
-\label{CHSProperty4 inter1}
-\end{IEEEeqnarray}
-According to Property \ref{CHSProperty2}, (\ref{CHSProperty4 inter1}) can be rewritten as 
-\begin{equation}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath <\Im{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}},
-\label{CHSProperty4 inter2}
-\end{equation}
-According to Property \ref{CHSProperty3}
+
 \begin{IEEEeqnarray}[\relax]{l}
 \nonumber
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-\imath <\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathbb{H}}+\imath (<\Im{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-
-\imath <\Im{(\mathbf{g})}, \\ \nonumber  \Im{(\mathbf{h})}>_{\mathbb{H}})
-=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}-<\Re{(\mathbf{g})},\\ \Im{(\mathbf{h})}>_{\mathbb{H}}]
-\label{CHSProperty4 inter2}
+\mathbf{y}_{c}=\Re{(\mathbf{y}_c)}+\jmath \Im{(\mathbf{y}_{c})}, \mathbf{H}_{c}=\Re{(\mathbf{H}_{c})}+\jmath \Im{(\mathbf{H}_{c})},\\
+\mathbf{s}_{c}=\Re{(\mathbf{s}_{c})}+\jmath \Im{(\mathbf{s}_{c})}, \mathbf{n}_{c}=\Re{(\mathbf{n}_{c})}+\jmath \Im{(\mathbf{n}_{c})},
+\label{complex decomposition}
 \end{IEEEeqnarray}
-According to (\ref{CHSProperty4 inter2}), if $\mathbf{f}_{1}, \mathbf{f}_{2}\in \mathcal{H}$, we have  $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathbb{H}}=<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}$, furthermore because $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}=\mathbf{f}^{T}_{1}\mathbf{f}_{2}$, (\ref{CHSProperty4 inter2}) can be rewritten as
+define
+
 \begin{IEEEeqnarray}[\relax]{l}
 \nonumber
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathcal{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}-<\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathcal{H}}]=\\
-\Re{(\mathbf{g})}^{T}\cdot \Re{(\mathbf{h})}+\Im{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}+\imath [\Im{(\mathbf{g})}^{T}\cdot  \Re{(\mathbf{h})}-\Re{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}]=\mathbf{g}\cdot \mathbf{h}^{*}
-\label{CHSequation2}
+\mathbf{y}=[\Re{(\mathbf{y}_{c})}^{T}, \Im{(\mathbf{y}_{c})}^{T}]^{T}, \mathbf{H}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\Re{(\mathbf{H}_{c})}& -\Im{(\mathbf{H}_{c})}\\
+\Im{(\mathbf{H}_{c})}& \Re{(\mathbf{H}_{c})}
+\end{IEEEeqnarraybox*}\right] \\
+\mathbf{s}=[\Re{(\mathbf{s}_{c})}^{T}, \Im{(\mathbf{s}_{c})}^{T}]^{T}, \mathbf{n}=[\Re{(\mathbf{n}_{c})}^{T}, \Im{(\mathbf{n}_{c})}^{T}]^{T},
+\label{real vectors}
 \end{IEEEeqnarray}
-
-Therefore $<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}$.
-\end{proof}
-Therefore we have $<\mathbf{h}_{i}, \mathbf{s}^{*}>_{\mathbb{H}}=\mathbf{h}_{i}\cdot \mathbf{s}$, 
-For sake of simplicity we define $\mathbf{w}=\mathbf{s}^{*}$.
-Based on the same principle in the real case presented in section \ref{Introduce epsilon SVR}, the primal optimization problem of large MIMO detection in complex RKHS $\mathbb{H}$ defined by $<\mathbf{m}, \mathbf{l}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}^{*}$ can be formulated as
+The complex model in (\ref{complex MIMO model}) can be transferred into an equivalent real-valued model, which is given by 
+\begin{equation}
+\mathbf{y}=\mathbf{H}\mathbf{s}+\mathbf{n},
+\label{real MIMO model}
+\end{equation}
+\subsection{MIMO Detection in view of Statistical Learning}
+Generally speaking, the task of LS-MIMO detection is to estimate the transmit symbol vector $\mathbf{s}$ based on the knowledge of receive symbol vector $\mathbf{y}$ and channel state information (CSI) $\mathbf{H}$.
+In view of statistical learning, LS-MIMO detection problem is a multidimensional ($N_{t}$) regression estimation problem with $N_{r}$ training data samples, which is given by
+\begin{equation}
+\mathbf{y}_{i}=f_{LS-MIMO}(\mathbf{h}_{i})+\mathbf{n}_{i}, i=1,2,\ldots, N_{r},
+\label{multidimensional regression estimation}
+\end{equation}
+where $\mathbf{h}_{i}$ denotes the $i$th row of $\mathbf{H}$, is the $i$th input data vector, $f_{LS-MIMO}(\mathbf{h}_{i})=\mathbf{h}_{i}\mathbf{s}$, is a $N_{t}$-dimensional linear function, $\mathbf{s}$ is the regression coefficient vector, $\mathbf{y}_{i}$ is the $i$th observation disrupted by additive noise (error) $\mathbf{n}_{i}$.
+
+The loss function $L(\mathbf{y}_{i}, f_{c}(\mathbf{h}_{i}))$ is a measure of the loss between the observations and the output of a candidate function $f_{c}{\cdot}$, the actual risk of a regression estimate $f_{c}(\cdot)$ is defined by\cite{vapnik1998statistical}
+\begin{equation}
+R(f_{c})=\int L(y, f_{c}(h))dP(y, \mathbf{h}), f_{c}\in \Lambda
+\label{actual risk}
+\end{equation} 
+where $\Lambda$ is the set of candidate functions, $P(y, \mathbf{h})$ is the joint probability density function (pdf) of input-output data set $(y, \mathbf{h})$ where $y$ is a real value and $\mathbf{h}$ is a vector, (\ref{actual risk}) is the expectation of loss function.
+The goal of regression estimation is to find the best function $f_{0}(\cdot)$ (e.g., the most accurate approximation to the regression coefficient vector $\mathbf{s}$ in (\ref{multidimensional regression estimation})) that minimize the actual risk, based on the training data set.
+
+The loss function for regression estimation, based on Huber's robust estimator principle\cite{huber2011robust} is given by 
+\begin{equation}
+L(y, f_{c}(\mathbf{h}))=-\ln(Pr(y-f_{c}(\mathbf{h}))),
+\label{robust loss function}
+\end{equation}  
+where $Pr(\cdot)$ denotes the pdf of additive noise, when the additive noise is Gaussian distributed, the robust loss function is given by 
+\begin{equation}
+L(y, f_{c}(h))=(y-f_{c}(h))^{2},
+\label{robust loss function normal}
+\end{equation}
+
+% needed in second column of first page if using \IEEEpubid
+%\IEEEpubidadjcol
+
+\section{Empirical Risk Minimization Principle and Its Correlation with Linear Detectors}
+The actual risk is a theoretical measure of the regression estimation performance with respect to all the data set $(y,\mathbf{h})$.
+However, in practical the training data set is a finite set of the samples in the data set space and the probability measure $P(y,\mathbf{h})$ is unknown, thus empirical risk is used as an alternative measure of the performance of regression estimation performance.
+Given a training data set $(y_{1}, \mathbf{h}_{1}), (y_{2}, \mathbf{h}_{2}), \ldots, (y_{l}, \mathbf{h}_{l})$, where $l$ is the number of training data, empirical risk is given by
+\begin{equation}
+R_{emp}(f_{c})=\frac{1}{l}\sum_{i=1}^{l}L(y_{i}, f_{c}(\mathbf{h}_{i})), f_{c}\in \Lambda
+\label{empirical risk}
+\end{equation}
+For regression estimation problems in LS-MIMO detection, use Huber's robust loss function in (\ref{robust loss function normal}), the empirical risk in LS-MIMO detection is given by 
+\begin{equation}
+R^{LS-MIMO}_{emp}(f_{c})=\frac{1}{N_{r}}\sum_{i=1}^{N_{r}}(\mathbf{y}_{i}-f_{c}(\mathbf{h}_{i}))^{2},
+\label{empirical risk MIMO}
+\end{equation}
+where $f_{c}(\mathbf{h}_{i})=\mathbf{h}_{i}\hat{\mathbf{s}}$, $\hat{\mathbf{s}}$ is the estimation of the regression coefficient vector.
+The empirical risk minimization principle (ERM) is to approximate the minimizer $f_{0}$ of actual risk $R(f_{c})$ by the minimizer $f_{emp}$ of the corresponding empirical risk $R_{emp}(f_{c})$.
+
+In MIMO detection, linear detectors (LD) (zeros forcing (ZF) and minimum mean square error (MMSE)) from the view of regression estimation, are the estimators designed based on ERM principle.
+We elaborate a little further here.
+
+ZF is derived from the principle of solving an unconstrained least square problem in a continuous vector space\cite{kailath2005mimo}, then slicing the results by symbol constellation alphabet (e.g., 4-QAM, 16-QAM or 64-QAM), the unconstrained least square problem is given by
+\begin{equation}
+\min_{\hat{\mathbf{s}}}||\mathbf{y}-\mathbf{H}\hat{\mathbf{s}}||^{2}=\min_{\hat{\mathbf{s}}}\sum_{i=1}^{N_{r}}(\mathbf{y}_{i}-\mathbf{h}_{i}\hat{\mathbf{s}})^{2},
+\label{ZF least square}
+\end{equation}
+where $||\cdot||$ denotes 2-norm operator. The solution of (\ref{ZF least square}) is given by 
+\begin{equation}
+\tilde{\mathbf{s}}=\mathbf{H}^{\dagger}\mathbf{y},
+\label{ZF solution}
+\end{equation}
+where $\mathbf{H}^{\dagger}=(\mathbf{H}^{T}\mathbf{H})^{-1}\mathbf{H}^{T}$ is the pseudo-inverse of $\mathbf{H}$.
+
+MMSE detector is designed based on the principle that minimizaing the mean square error between the transmit symbol vector and the estimated symbol vector, that is\cite{paulraj2003introduction} 
+\begin{equation}
+\min_{\hat{\mathbf{s}}}\mathbb{E}(||\mathbf{s}-\hat{\mathbf{s}}||^{2}),
+\label{MMSE criterison}
+\end{equation}
+where $\hat{\mathbf{s}}=\mathbf{G}\mathbf{y}$, $\mathbf{G}$ is the equalization matrix, given by 
+$\mathbf{G}=(\mathbf{H}^{T}\mathbf{H}+\rho^{-1}\mathbf{I})^{-1}\mathbf{H}^{T}$, $\rho=\frac{\xi_{s}}{N_{0}}$ denotes the SNR.
+Although ZF and MMSE are based on the different principles, the latter one can also be interpreted as solving the similar unconstrained least square problem as in (\ref{ZF least square}) for an augmented linear equation system.
+The augmented linear equation system takes into account the noise.
 \begin{IEEEeqnarray}[\relax]{l}
 \nonumber
-\min_{\mathbf{w}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i}} \quad \frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]\\
-s.t. \left\{\begin{array}{ll}
-\Re{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{r}_{i}, i=1,2,\ldots, N_{r}\\
-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{r}_{i}, i=1,2,\ldots, N_{r}\\
-\Im{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{i}_{i}, i=1,2,\ldots, N_{r}\\
-\Im{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{i}_{i}, i=1,2,\ldots, N_{r}\\
-\xi^{r}_{i}, \hat{\xi}^{r}_{i},\xi^{i}_{i},\hat{\xi}^{i}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex objective function1}
+\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\mathbf{y}\\
+0
+\end{IEEEeqnarraybox*}\right]= \left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\mathbf{H}\\
+\rho^{-1/2}\mathbf{I_{N_{t}}}
+\end{IEEEeqnarraybox*}\right]\mathbf{s}+\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
+\mathbf{n}\\
+-\rho^{-1/2}\mathbf{I_{N_{t}}\mathbf{s}}
+\end{IEEEeqnarraybox*}\right]
+\label{augmented linear equation system}
 \end{IEEEeqnarray}
- Where $\Re{(\cdot)}$ and $\Im{(\cdot)}$ denote real and imaginary part of a complex variable and inequality constraints are set to real and imaginary part of the regression function separately.
-Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denote the kernel function, $\mathbf{K}=\Re{(\mathbf{K})}+\imath\Im{(\mathbf{K})}$, where $\Re{(\mathbf{K})}$ and $\Im{(\mathbf{K})}$ denote matrices of corresponding real and imaginary parts.
-Similar to the Lagrange duality rational in section \ref{section lagrange duality}, the Lagrange function associated with (\ref{complex objective function1}) is
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L=
-\frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]- \sum_{i=1}^{N_{r}}(\eta_{i}\xi^{r}_{i}+\hat{\eta}_{i}\hat{\xi}^{r}_{i}+\tau_{i}\xi^{i}_{i}\\\nonumber +\hat{\tau}_{i}\hat{\xi}^{i}_{i})
-+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{r}_{i})
-+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}(\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})\\
-\nonumber
-+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}(\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\Im{(y_{i})}-\epsilon-\hat{\xi}^{i}_{i})\\
-s.t. \left\{\begin{array}{ll}
-\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
-\xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i} \geq  0, i=1,2,\ldots, N_{r}
-\end{array}\right. 
-\label{complex lagrange duality1}
-\end{IEEEeqnarray}
-where $\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}$ are Lagrange multipliers.
-In order to calculate the partial derivations of $L$ with respect to $\mathbf{w}$ which is defined in complex domain, the Wirtinger's calculus is exploited\cite{bouboulis2011extension} , Therefore we have
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-\frac{\partial L}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{i=1}^{N_{r}}\alpha_{i}\mathbf{h}_{i}+\frac{1}{2}\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\mathbf{h}_{i}+\frac{\imath}{2}(\sum_{i=1}^{N_{r}}\beta_{i}\mathbf{h}_{i}-\sum_{i=1}^{N_{r}}\hat{\beta}_{i}\mathbf{h}_{i})=0\\
-\Rightarrow \mathbf{w}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-\imath\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\\
-\frac{\partial L}{\partial \xi^{r}_{i}}=CR^{'}(\xi^{r}_{i})-\eta_{i}-\alpha_{i}=0\Rightarrow \eta_{i}=CR^{'}(\xi^{r}_{i})-\alpha_{i}\\
-\frac{\partial L}{\partial \hat{\xi}^{r}_{i}}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\Rightarrow \hat{\eta}_{i}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\alpha}_{i}\\
-\frac{\partial L}{\partial \xi^{i}_{i}}=CR^{'}(\xi^{i}_{i})-\tau_{i}-\beta_{i}=0\Rightarrow \tau_{i}=CR^{'}(\xi^{i}_{i})-\beta_{i}\\
-\frac{\partial L}{\partial \hat{\xi}^{i}_{i}}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\tau}_{i}-\hat{\beta}_{i}=0\Rightarrow \hat{\tau}_{i}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\beta}_{i}\\
-
-\end{array}\right.
-\label{complex lagrange duality2}
-\end{IEEEeqnarray}
-Based on (\ref{complex lagrange duality2}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}\\
-\nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\\nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\\ \sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}),
-\label{complex duality regression function}
-\end{IEEEeqnarray}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
-+i(\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}-\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}\mathbf{h}^{H}_{i})
-\label{complex duality regularization1}
-\end{IEEEeqnarray}
-Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$. If we have $r_{i}$, $r_{j}$ $\in \mathbb{R}$, then 
-\begin{equation}
-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ji}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij},
-\end{equation}
-Therefore
-\begin{equation}
-\sum_{i,j}^{l}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=0,
-\label{conjugate1}
-\end{equation}
-Based on (\ref{conjugate1}), (\ref{complex duality regularization1}) can be changed to
-\begin{equation}
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}.
-\label{complex duality regularization2}
-\end{equation}
-Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), we have
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L=\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}]+\\
-\nonumber
-C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})]- \sum_{i=1}^{N_{r}}((CR^{'}(\xi^{r}_{i})-\alpha_{i})\xi^{r}_{i}+(CR^{'}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}^{r}_{i}+(CR^{'}-\beta_{i})\xi^{i}_{i}\\\nonumber +(CR^{'}(\hat{\xi}_{i})-\hat{\beta}_{i})\hat{\xi}^{i}_{i})+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\epsilon-\xi^{r}_{i})
-+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\\ \nonumber
-((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})
-+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\\ \nonumber
-\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\Im{(y_{i})}-\\
-\epsilon-\hat{\xi}^{i}_{i})
-\label{complex lagrange duality inter1}
-\end{IEEEeqnarray}
-
-Then simplify (\ref{complex lagrange duality inter1}), we obtain
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L\equiv\theta=-\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}]+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})-\xi_{i}^{r}R^{'}(\xi^{r}_{i})\\\nonumber
-+R(\hat{\xi}^{r}_{i})-\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})-\xi_{i}R^{'}(\xi_{i}^{i})+R(\hat{\xi}^{i}_{i})-\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]+\sum_{i=1}^{N_{r}}[\Re{(y_{i})}(\alpha_{i}-\hat{\alpha}_{i})+\Im{(y_{i})}(\beta_{i}-\hat{\beta}_{i})]-\\
-\epsilon\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta_{i}+\hat{\beta}_{i})
-\label{complex lagrange duality inter2}
-\end{IEEEeqnarray}
-define $\tilde{R}(u)=R(u)-uR^{'}(u)$. Similar to (\ref{dual optimization function2}), The dual optimization problem of a complex MIMO system is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}}\quad \theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
-\nonumber
--\sum_{i}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta+\hat{\beta}_{i})\epsilon+[\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})]\\
-\nonumber
-+C\sum_{i}^{N_{r}}(\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i}))\\ 
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{final complex lagrange duality}
-\end{IEEEeqnarray}
-Notice in (\ref{final complex lagrange duality}), there is no correlation term between $\alpha_{i}, \hat{\alpha}_{i}$ and $\beta_{i}, \hat{\beta}_{i}$, therefore, (\ref{final complex lagrange duality}) can be divided into two independent regression tasks, which are given by
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}} \quad \theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
-\nonumber
-+\tilde{R}(\hat{\xi}^{r}_{i}))\\
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{complex duality real part}
-\end{IEEEeqnarray}
-and 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\beta_{i}, \hat{\beta}_{i}} \quad \theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
-\nonumber
-+\tilde{R}(\hat{\xi}^{i}_{i}))\\
-\left\{\begin{array}{ll}
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{complex duality imaginary part}
-\end{IEEEeqnarray}
-Let $\mathbf{a}=[\alpha_{1}, \alpha_{2},\ldots, \alpha_{N_{r}}]^{T}$, $\mathbf{\hat{a}}=[\hat{\alpha}_{1}, \hat{\alpha}_{2},\ldots, \hat{\alpha}_{N_{r}}]^{T}$, $\mathbf{b}=[\beta_{1}, \beta_{2},\ldots, \beta_{N_{r}}]^{T}$,$\mathbf{\hat{b}}=[\hat{\beta}_{1}, \hat{\beta}_{2},\ldots, \hat{\beta}_{N_{r}}]^{T}$, $\mathbf{R}^{r}=[\tilde{R}(\xi^{r}_{1})+\tilde{R}(\hat{\xi}^{r}_{1}), \tilde{R}(\xi^{r}_{2})+\tilde{R}(\hat{\xi}^{r}_{2}), \ldots, \tilde{R}(\xi^{r}_{N_{r}})+\tilde{R}(\hat{\xi}^{r}_{N_{r}})]^{T}$, $\mathbf{R}^{i}=[\tilde{R}(\xi^{i}_{1})+\tilde{R}(\hat{\xi}^{i}_{1}), \tilde{R}(\xi^{i}_{2})+\tilde{R}(\hat{\xi}^{i}_{2}), \ldots, \tilde{R}(\xi^{i}_{N_{r}})+\tilde{R}(\hat{\xi}^{i}_{N_{r}})]^{T}$, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$.
-The alternate form can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a},\mathbf{\hat{\mathbf{a}}}} \quad \theta^{r}=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\Re{(\mathbf{K})}(\mathbf{a}-\mathbf{\hat{a}})+\Re{(\mathbf{y})}^{T}(\mathbf{a}-\mathbf{\hat{a}})-\epsilon(\mathbf{e}^{T}(\mathbf{a}+\mathbf{\hat{a}}))+C(\mathbf{e}^{T}\mathbf{R}^{r})\\
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex duality real part vectorizes}
-\end{IEEEeqnarray}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{b}, \mathbf{\hat{b}}} \quad \theta^{i}=-\frac{1}{2}(\mathbf{b}-\mathbf{\hat{b}})^{T}\Re{(\mathbf{K})}(\mathbf{b}-\mathbf{\hat{b}})+\Im{(\mathbf{y})}^{T}(\mathbf{b}-\mathbf{\hat{b}})-\epsilon(\mathbf{e}^{T}(\mathbf{b}+\mathbf{\hat{b}}))+C(\mathbf{e}^{T}\mathbf{R}^{i})\\
-\left\{\begin{array}{ll}
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex duality imaginary part vectorized}
-\end{IEEEeqnarray}
-
-Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), where only the real part of the kernel matrix is required for each channel.
-This can provide computational advantages for solving the dual optimization problems.
-\section{Work Set Selection and Solver}\label{WSS}
- As we can see, a quadratic optimization problem is formulated in (\ref{final complex lagrange duality}).
-The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with a large data set.
-
-Decomposition methods are a set of efficient algorithms that can help to ease this difficulty.
-Decomposition methods work iteratively, and are based on choosing a subset of optimization variables $S$ (named work set) to be updated in each iteration step, while keeping the rest variables $N$ fixed.
-Sequential Minimal Optimization (SMO) is an extreme case of decomposition method, where the work set size is 2, and an analytic quadratic programming (QP) step instead of numerical QP step can be performed in each iteration.
-
-Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) have the same structure, in this section we discuss the real part only.
-By dividing the variables into work set $S$ and fixed set $N$.
-Therefore, the vector $\mathbf{a}$ in (\ref{complex duality real part vectorizes}) can be divided into two sub vectors $[\mathbf{a}_{S}, \mathbf{a}_{N}]$.
-thereafter $\mathbf{a}_{S}$ denotes a vector that consists of the components of $\mathbf{a}$ that belongs to set $S$, the same modifications are applied to $\mathbf{\hat{a}}$ and $\mathbf{y}$.
-Thus (\ref{complex duality real part vectorizes}) can be rewritten as:
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}, \mathbf{a}_{N}, \hat{\mathbf{a}}_{N}} \theta= -\frac{1}{2}[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
-\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]+[\Re{(\mathbf{y}_{S})}^{T}, \Re{(\mathbf{y}_{N})}^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]-\\\nonumber\epsilon[\mathbf{e}^{T}_{S}, \mathbf{e}^{T}_{N}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}+\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]+C(\mathbf{e}^{T}, \mathbf{R}^{r})
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{real part decomposition inter1}
-\end{IEEEeqnarray}
-
-Where $\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
-\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of the components in $\Re(\mathbf{K})$ that belong to both of the rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\mathbf{K}$ is a Hermitian matrix, thus $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}, \mathbf{\hat{a}}}\quad \theta^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})+2(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]
-+\Re{(\mathbf{y}_{S}^{T})}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\
-\nonumber
-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S}))
--\frac{1}{2}(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NN}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})+\Re{(\mathbf{y}_{N}^{T})}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{N}+\mathbf{\hat{a}}_{N}))\\\nonumber+C(\mathbf{e}^{T}(\mathbf{R}^{r}),
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{real part decomposition}
-\end{IEEEeqnarray}
-In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is considered i.e 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}_{S}, \mathbf{\hat{a}}_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]+[Re(\mathbf{y}_{S}^{T})-(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\mathbf{K}_{NS}^{r}
-](\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\\nonumber\epsilon<\mathbf{e}^{T}, (\mathbf{a}_{S}+\mathbf{\hat{a}}_{S})>,
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}_{S}]_{i}([\hat{\mathbf{a}}_{S}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i\in S\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i\in S\\
-\end{array}\right.
-\label{subset optimization}
-\end{IEEEeqnarray}
-A proper work set selection strategy is required so that speed and performance requirement can be guaranteed.
-One idea is to perform update to optimization variables that violate the KKT complementary conditions, which, based on (\ref{complete KKT complimentary})
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
-\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, L\\
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, L\\
-\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots, L
-\end{array}\right.
-\label{complementary KKT condition1}
-\end{IEEEeqnarray}
-According to Osuna's theorem\cite{osuna1997improved}, the final convergence can be guaranteed.
-In SMO algorithm, heuristic methods are used to find a work set of size two in order to accelerate the decomposition process\cite{platt1999fast}.
-The heuristic method first searches among the non-bound variables (that is $0<\alpha_{i}<C\tilde{R}(\xi^{r}_{i})$ and $0<\hat{\alpha}_{i}<C\tilde{R}(\hat{\xi}_{i})$), which are more likely to violate the complementary KKT conditions, Then searching the whole dual variable set.
-The second dual variable that can maximize optimization step size is chosen.
-An approximate step size is used as evaluator for sake of reducing computational cost.
-
-Another idea for work set selection is to choose the optimization variables whose update can provide the maximum improvement to the sub dual objective functions.
-The improvement of the sub dual objective function is
-\begin{equation}
-\bigtriangledown \theta^{r}_{S}=\theta^{r}_{S}((\mathbf{a}_{S}+\Delta_{S}), (\hat{\mathbf{a}}_{S}+\hat{\Delta}_{S}))-\theta^{r}_{S}(\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}),
-\label{maximum gain work set selection}
-\end{equation} 
-where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\hat{\Delta}_{S}=\hat{\mathbf{a}}_{S}^{new}-\hat{\mathbf{a}}_{S}$, $\mathbf{a}^{new}_{S}$ and $\hat{\mathbf{a}}^{new}_{S}$ are the updates of $\mathbf{a}_{S}$ and $\hat{\mathbf{a}}_{S}$.
-$\bigtriangledown \theta_{S}^{r}$ in (\ref{maximum gain work set selection}),  based on (\ref{subset optimization}), can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\\\nonumber\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+\{\Re{(\mathbf{y}^{T}_{S})}-[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\\
-\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}]\}(\Delta_{S}-\hat{\Delta}_{S})
--\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S}),
-\label{gain work set selection1}
-\end{IEEEeqnarray} 
-where we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}=[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}\\
-\Re{(\mathbf{K})}_{NS}
-\end{IEEEeqnarraybox*}\right]=\\
-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S},
-\label{modification of gain work set selection}
-\end{IEEEeqnarray}
-where $\Re{(\mathbf{K})}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns corresponding to the work set $S$.
-Therefore, (\ref{gain work set selection1}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}]
-(\Delta_{S}-\hat{\Delta}_{S})
--\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta_{S}+\hat{\Delta}_{S}),
-\label{gain of work set selection1 inter}
-\end{IEEEeqnarray}
-define intermediate variable vector $\Phi^{r}, \Phi^{i}\in \mathbb{R}^{N_{r}}$, $\Phi^{r}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Phi^{i}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$.
-Let $\Phi_{S}$ denote the vector that consists of the components in $\Phi$ that corresponding to $S$.
-Thus (\ref{gain of work set selection1 inter}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+(\Phi^{r}_{S})^{T}(\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta_{S}+\hat{\Delta}_{S})
-\label{gain work set selection2}
-\end{IEEEeqnarray} 
-Because the offset term is omitted in the large MIMO regression model, therefore different from SMO type algorithms, there is no linear equality constraint, which is inducted by offset $b$, as shown in (\ref{partial4}).
-Therefore the size of work set can be less than two.
-However, more efficient work set selection strategies based on maximal sub dual objective gain selection, is proposed in \cite{steinwart2011training}.
-A work set of size two is updated in each iteration.
-The computational cost is reduced while maintaining the comparable performance with the model with offset term.
-In the CSVR large MIMO detector, the work set selection strategy in \cite{steinwart2011training} is exploited.
-Basically, in each iteration this strategy uses the combined single variable searchings, whose searching time is $O(n)$, where $n$ is the number of data samples, to determine a work set of size two.
-On the one hand, this strategy can find a work set of size two, whose update approximately maximize the gain of the dual sub objective function.
-On the other hand, the brute-force searching for the work size of two, whose update can maximize the gain of the sub dual objective function, requires $O(n^{2})$ searching time.
-The former strategy requires as few iterations as the latter one, since in each iteration, the latter strategy is more computationally expensive, the former one can enjoy significantly faster running speed.
-\subsection{Single Direction (1-D) Solver}\label{single direction solver}
-Recall the KKT complementary conditions 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{KKT complementary1}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary2}
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary3}
-\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary4}
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary5}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq R^{'}(\xi^{r}_{i})(R^{'}(\hat{\xi}_{i})), i=1,2,\ldots, N_{r} 
-\end{IEEEeqnarray}
-Recall the discussions of slack variables by (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}) in section \ref{section lagrange duality}.
-we have $\xi^{r}_{i}\hat{\xi}^{r}_{i}=0$.
-similar to the definitions in (\ref{definition of slack variable3}), we have
-\begin{equation}
-\xi^{r}_{i} or \hat{\xi}_{i}^{r}=|\Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}|_{\epsilon},
-\label{definition of complex slack variables}
-\end{equation} 
- therefore in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})$ and  $(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})$ can be non zero, therefore in order to satisfy equalities (\ref{KKT complementary3}) and (\ref{KKT complementary4}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
-
- Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is changed to the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.
-
-  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of the sub dual objective function is chosen as the work set in each iteration.
-Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]^{T}$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]^{T}$.
-Substitute $\mathbf{a}, \hat{\mathbf{a}}$ with $\Lambda$ and using $\Sigma$.
-Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2}) can be rewritten as
-  \begin{equation}
-\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y}_{S}^{T})}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
-]\Lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\Lambda_{S}|>,
-\label{subset optimization lambda}
-\end{equation}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
-\label{gain work set selection lambda}
-\end{IEEEeqnarray} 
-In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
-\begin{IEEEeqnarray}[\relax]{l}
- \max_{\tilde{\lambda}^{new}_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\tilde{\lambda}_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
-+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\tilde{\lambda}_{m}^{new}-\epsilon(|\tilde{\lambda}^{new}_{m}|),
- \label{optimization function 1-D}
- \end{IEEEeqnarray}
- where $\tilde{\lambda}^{new}_{m}$ is the update of $\lambda_{m}$.
- Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Phi^{r}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$ in the imaginary channel, $\Phi_{i}^{i}=\Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$.
-Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
-Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))
-\label{partial optimization function 1-D lambda}
-\end{IEEEeqnarray} 
-where $\Re(y_{m})-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re(\mathbf{K})_{mj}=\Re(y_{m})-\sum_{j=1}^{N_{r}}\lambda_{j}\Re(\mathbf{K}_{mj})=\Phi^{r}_{m}+\lambda_{m}\Re(\mathbf{K}_{mm})$
-and $\lambda_{m}$ denotes the $m$th optimization variable before update. Therefore (\ref{partial optimization function 1-D lambda}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\frac{\partial \theta^{r}_{m}}{\partial \tilde{\lambda}_{m}^{new}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
-\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Phi^{r}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
-\end{IEEEeqnarray}
- The update of $\tilde{\lambda}^{new}_{m}$ is completed by clipping based on (\ref{KKT complementary5})
-\begin{IEEEeqnarray}[\relax]{l}
-\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
-\label{clipped new dual variable}
-\end{IEEEeqnarray}
-
-where $[ ]_{a}^{b}$ denotes clipping function 
-\begin{IEEEeqnarray}[\relax]{l}
-[x]_{a}^{b}=\left\{\begin{array}{ll}
-a \quad if\quad  x\leq a\\
-x \quad if\quad a<x<b\\
-b \quad if\quad x\geq b\\
-\end{array}\right.
-\label{clipping function}
-\end{IEEEeqnarray}
-based on (\ref{gain work set selection lambda}), The maximal gain of the sub dual objective function with respect to the $m$th optimization variable is 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{m}^{r}=\theta_{m}^{r}(\lambda_{m}+\sigma_{m})-\theta_{m}^{r}(\lambda_{m})\\
-\nonumber
-=-\frac{1}{2}\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}\sigma_{m}-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)\\
-=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|),
-\label{gain of 1-D objective function}
-\end{IEEEeqnarray}
-In 1-D searching procedure, the optimization variable whose update can achieve the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, based on the this principle
-\begin{equation}
-k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r}.
-\label{1-D direction}
-\end{equation}
-Notice in (\ref{partial optimization function 1-D lambda}), $sgn(\tilde{\lambda}^{new}_{m})$ is unknown before $\lambda_{m}$ is updated, therefore two conditions $sgn(\tilde{\lambda}^{new}_{m})=1$ and $sgn(\tilde{\lambda}^{new}_{m})=-1$ are considered.
-The final decision of $sgn(\tilde{\lambda}_{m}^{new})$ is made by comparing the corresponding gains of the sub dual objective functions in (\ref{gain of 1-D objective function}).
-\subsection{Double Direction (2-D) Solver}\label{double direction solver}
-Although the omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however, recent work in \cite{steinwart2011training} shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained.
-The optimal 2-D solver uses the same principle as 1-D solver, $|S|=2$, assume the work set consists of the $m$th and $n$th optimization variables, that are $\Lambda_{S}=[\lambda_{m}, \lambda_{n}]$.
-Based on (\ref{gain work set selection lambda}), the sub dual objective function can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\lambda_{m}, 
-\lambda_{n}}\quad \theta^{r}_{m,n}=-\frac{1}{2}[(\tilde{\lambda}^{new}_{m})^{2}\Re{(\mathbf{K})}_{mm}+(\tilde{\lambda}^{new}_{n})^{2}\Re{(\mathbf{K})}_{nn}+2\tilde{\lambda}^{new}_{m}\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}]-\\
-\nonumber
-\tilde{\lambda}^{new}_{m}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\tilde{\lambda}^{new}_{n}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{m})}\tilde{\lambda}^{new}_{1}+\Re{(\mathbf{y}_{n})}\tilde{\lambda}^{2}_{n}\\
--\epsilon(|\lambda^{new}_{m}|+|\tilde{\lambda}_{n}^{new}|), 
-\label{2-D solver}
-\end{IEEEeqnarray}
-Based on (\ref{2-D solver}), the partial derivatives of $\theta^{r}_{m,n}$ with respect to $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}_{n}^{new}$ are 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\label{lambda1 partial}
-\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}+\Re{(\mathbf{y}_{m})}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=\\
--\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{m}+\lambda_{m}\Re{\mathbf{K}}_{mm}+\lambda_{n}\Re{(\mathbf{K})}_{mn}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=0\\
-\nonumber
-\label{lambda2 partial}
-\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{n}}=-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{n})}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=\\
--\tilde{\lambda}_{n}^{new}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{n}+\lambda_{m}\Re{(\mathbf{K})}_{mn}+\lambda_{n}\Re{(\mathbf{K})}_{nn}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=0\\
-\nonumber
-\label{partial derivative sample1}
-\end{IEEEeqnarray}
-where $\frac{\partial |x|}{\partial x}=sgn(x)$ denotes the sign of $x$. Based on (\ref{lambda1 partial}) and (\ref{lambda2 partial}) we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{post partial lambda1}
-(\tilde{\lambda}^{new}_{m}-\lambda_{n})\Re{(\mathbf{K})}_{mm}=\Phi^{r}_{m}-\epsilon sgn(\tilde{\lambda}^{new}_{m})-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{mn}\\
-\label{post partial lambda2}
-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{nn}=\Phi^{r}_{n}-\epsilon sgn(\tilde{\lambda}^{new}_{n})-(\tilde{\lambda}^{new}_{m}-\lambda_{m})\Re{(\mathbf{K})}_{mn}\\
-\nonumber
-\end{IEEEeqnarray}
-hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formulas of $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}^{new}_{n}$ are given by
-\begin{equation}
-\tilde{\lambda}^{new}_{m}=\lambda_{m}+\frac{\Phi^{r}_{m}\Re{(\mathbf{K})}_{nn}-\Phi^{r}_{n}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{nn}-sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
-\label{update lambda1}
-\end{equation}
-
-\begin{equation}
-\tilde{\lambda}^{new}_{n}=\lambda_{n}+\frac{\Phi^{r}_{n}\Re{(\mathbf{K})}_{mm}-\Phi^{r}_{m}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mm}-sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
-\label{update lambda2}
-\end{equation} 
-Then the updated optimization variables are clipped by constraint based on (\ref{KKT complementary5})
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\lambda_{i}^{new}=[\tilde{\lambda}_{i}^{new}]^{CR^{'}(\xi_{i})}_{-CR^{'}(\xi_{i})},\\
-i=m,n
-\label{cipped optimization variable}
-\end{IEEEeqnarray}
-Based on (\ref{gain work set selection2}),  the gain of the sub dual objective function can be written as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=-\frac{1}{2}[\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\sigma_{n}^{2}\Re{(\mathbf{K})}_{nn}+2\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn}]+\Phi^{r}_{m}\sigma_{m}+\Phi^{r}_{n}\sigma_{n}\\
--\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|+|\lambda^{new}_{n}|-|\lambda_{n}|),
-\label{gain of 2-D objective function1}
-\end{IEEEeqnarray}
-assume the $i$th and $j$th optimization variables are chosen, the optimization variables in 2-D solver have the same update rule as that of 1-D solver, that is 
-\begin{equation}
-[i,j]=\arg\max_{m,n=1,2,\ldots, N_{r}}\bigtriangledown \theta_{m,n}^{r}.
-\label{dual optimization variables}
-\end{equation}
-
-Similar to single direction solver, notice in (\ref{update lambda1}) and (\ref{update lambda2}), $sgn(\tilde{\lambda}^{new}_{m})$ and $sgn(\tilde{\lambda}^{new}_{n})$ are unknown before $\lambda_{m}$ and $\lambda_{n}$ are updated, therefore four conditions are considered
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=-1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=-1
-\label{four conditions of sign}
-\end{IEEEeqnarray} 
-The final decisions of $sgn(\tilde{\lambda}_{m}^{new})$ and $sgn(\tilde{\lambda}_{n}^{new})$ are made by comparing the corresponding possible gains of the sub objective functions in (\ref{gain of 2-D objective function1}).
-
-Modify (\ref{gain of 2-D objective function1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)+\sigma_{n}[-\frac{1}{2}\sigma_{n}\Re{(\mathbf{K})}_{nn}+\Phi^{r}_{n}]-\epsilon(|\lambda^{new}_{n}|-|\lambda_{n}|)\\
--\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn},
-\end{IEEEeqnarray}
-then recall the gain of the sub dual objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
- \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta^{r}_{ij}=\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}-\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij},
-\label{gain of 2-D objective function2}
-\end{IEEEeqnarray}
-where $\bigtriangledown \theta^{r}_{i}$, $\bigtriangledown \theta^{r}_{j}$ denote gains of the sub dual objective functions of 1-D solver with $i$th and $j$th optimization variables are updated. 
-\subsection{Approximation of Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
-From (\ref{gain of 2-D objective function1}), we can observe that the gain of the sub dual objective function of 2-D solver is a summation of the gains of the sub dual objective functions of two independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}$.
-
-The optimal 2-D work set $[i,j]$ can be determined by brute-force searching manner, which requires $O(n^{2})$ searching times.
-Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D searching strategy by the combinations of optimal 1-D searching approach, we will prove in the large MIMO systems, when $N_{t}$ is sufficient large, this approximation is very effective.
-Here we propose two types of combined 1-D searching strategy:
-\subsubsection{ One-shot 1-D combined Searching}
-do one round 1-D searching and calculate all the 1-D gains based on (\ref{gain of 1-D objective function}), then choose the two optimization variables indexed by $i$ and $j$, whose update can achieve the first and the second largest gain of the sub dual objective functions.
-\subsubsection{ Sequential 1-D combined Searching}
-do two rounds 1-D searchings, in the first round find optimization variable indexed by $i$ whose update can achieve the maximal 1-D gain of the sub dual objective functions based on (\ref{gain of 1-D objective function}), then update the $i$th optimization variable.
-In the second round, find $j$th optimization variable whose update can achieve the maximal 1-D gain of the sub dual objective functions.
-
- The effectiveness of 1-D approximation strategies are majorly determined by the ratio $\frac{\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}}{\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}}$.
-Hence we provide theoretical analyses based on the view of channel hardening phenomenon.
-It can be proved that in the large MIMO systems, the correlation term $\sigma_{i}\sigma_{j}\Re(\mathbf{K}_{ij})$is ignorable comparing to 1-D gains of the sub objective function.
-Prior to the theoretical analyse, we first investigate some mathematical properties of channel hardening (to be completed).
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
-%\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
-%\label{figure1}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
-%\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
-%\label{figure2}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[scale=0.6]{NtE.eps}
-%\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
-%\label{figure3}
-%\end{figure}
-
-\section{Stopping Criteria}\label{stopping criteria}
-As discussed in section\ref{section lagrange duality}, in dual objective function, the complementary KKT conditions are the measurement of the proximity of current solution to the optimal solution. 
-The feasibility gap, which is a effective stopping criteria used in SVR and SVM, can implicitly monitor whether the KKT complementary conditions are satisfied.
-The feasibility gap measures the gap between the values of primal objective function and dual objective function.
-To elaborate a little further, recall the saddle point conditions in section\ref{section lagrange duality}
- \begin{equation}
- L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
- \label{saddle point conditions}
- \end{equation}
-Where $(\bar{\mathbf{w}}, \bar{\mathbf{a}})$ are the solution to primal objective function, the KKT complementary conditions are satisfied, that is 
-\begin{equation}
-\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=0,
-\label{complementary KKT condition revisited}
-\end{equation}
-we have 
-\begin{equation}
-L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=f(\bar{\mathbf{w}})+\sum_{i=1}^{N_{r}}\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=f(\bar{\mathbf{w}})
-\end{equation} 
-Let $(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$ denote the variable pair that satisfies the first and second KKT conditions in (\ref{original KKT condition1} ) and (\ref{original KKT condition2})
-
-\begin{IEEEeqnarray}[\relax]{l}
-\label{original KKT condition revisited1}
-\partial_{\mathbf{w}}L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=\partial_{\mathbf{w}}f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{a}_{i}\partial_{\mathbf{w}}c_{i}(\tilde{\mathbf{w}})=0,\\
-\label{original KKT condition revisited2}
-c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots L
-\end{IEEEeqnarray}
-based on (\ref{original KKT condition revisited1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq f(\tilde{\mathbf{w}}),
-\end{IEEEeqnarray} 
-based on Theorem 6.27\cite{scholkopf2002learning}, the following equalities hold
-\begin{IEEEeqnarray}[\relax]{l}
-f(\tilde{\mathbf{w}})\geq f(\bar{\mathbf{w}})=L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})
-\label{inequality gap}
-\end{IEEEeqnarray}
-Therefore the feasibility gap is defined by the gap between the primal objective function $f(\tilde{\mathbf{w}})$ and the dual objective function $L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$   
-\begin{equation}
-f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\geq 0
-\label{original feasibility gap}
-\end{equation}
-If the feasibility gap is vanished, based on (\ref{inequality gap}), we have $f(\bar{\mathbf{w}})=f(\tilde{\mathbf{w}})$, thus $\tilde{\mathbf{w}}=\bar{\mathbf{w}}$, $\tilde{\mathbf{a}}=\bar{\mathbf{a}}$.
-Furthermore, because $f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})$, the vanish of feasibility gap indicates $\sum_{i=1}^{L}\tilde{\mathbf{a}}c_{i}(\tilde{\mathbf{w}})=0$.
-Because $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots, L$, we have $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})=0, i=1,2,\ldots, L$, the KKT complementary conditions are satisfied.
-
-In CSVR detector for the large MIMO systems, the primal objective function is
-\begin{equation}
-f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal inter}
-\end{equation}
-where $\tilde{\mathbf{w}}$ satisfies the KKT  conditions in (\ref{original KKT condition revisited1}) and (\ref{original KKT condition revisited2}).
-Define $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$, $\Lambda^{r}=[\lambda^{r}_{1}, \lambda^{r}_{2}, \ldots, \lambda^{r}_{L}]^{T}$ and $\Lambda^{i}=[\lambda^{i}_{1}, \lambda_{2}^{i}, \ldots, \lambda^{i}_{L}]^{T}$,
-(\ref{complex duality regularization1}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-2<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>,
-\label{simple regularization}
-\end{IEEEeqnarray}
-Therefore we obtain  
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+\\R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal}
-\end{IEEEeqnarray}
-Based on (\ref{final complex lagrange duality}), the dual objective function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\Lambda^{r}, \Lambda^{i})=-\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>-\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>+<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
-\label{simple dual function}
-\end{IEEEeqnarray}
-
-Based on (\ref{simple primal}) and (\ref{simple dual function}), the feasibility gap is obtained 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\lambda^{r}, \lambda^{i})=f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})-\theta(\Lambda^{r},\Lambda^{i})=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Re{(\mathbf{y}^{T})}, \Lambda^{r}>\\\nonumber
--<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-\\<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>.
-\label{simple duality gap}
-\end{IEEEeqnarray}
-As we explained in section \ref{cost function}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
-\begin{equation}
-R(u)=\frac{1}{2}u^{2},
-\label{risk function1}
-\end{equation} 
-hence 
-\begin{equation}
-\tilde{R}(u)=R(u)-u R{'}(u)=-\frac{1}{2}u^{2},
-\label{risk function2}
-\end{equation}
-In $\epsilon$-SVR, the objective to exploit slack variables is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by the noise.
-Therefore in $\epsilon$-SVR, $\xi^{r}_{i}$ and $\hat{\xi}^{r}$ are defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-\xi^{r}_{i}=\max(0, \Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\epsilon)\\
-\hat{\xi}^{r}_{i}=\max(0, \Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\Re{(\mathbf{y}_{i})}-\epsilon)
-\label{outlier2}
-\end{IEEEeqnarray} 
-Because the distance between the estimations $\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}$ and the observations $\Re{(\mathbf{y}_{i})}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi^{r}_{i}$ and $\hat{\xi}^{r}_{i}$ can be non zero that is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
-Therefore the risk function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{simple risk function1}
-R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}|\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|_{\epsilon}^{2}\\\label{simple risk function2}
-R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}|\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-where $|\cdot|_{\epsilon}$ denotes $\epsilon$ insensitive function as mentioned in section \ref{cost function}. Recall (\ref{complex duality regression function}),
-\begin{IEEEeqnarray}[\relax]{l}
-<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}
-=\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}),
-\end{IEEEeqnarray}
- we obtain 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function1a}
-\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re(\mathbf{K})_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im(\mathbf{K})_{ij}\\
-\label{intermediate function1b}
-\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re(\mathbf{K})_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Im(\mathbf{K})_{ij}
-\end{IEEEeqnarray}
-Two intermediate variables $\Phi$ and $\Psi$ are defined
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermedia function 2a}
-\Phi^{r}=\Re(\mathbf{y})-\Re(\mathbf{K})
-\lambda^{r};
-\Phi^{i}=\Im(\mathbf{y})-\Re(\mathbf{K})\lambda^{i}\\
-\label{intermediate function 2b}
-\Psi^{r}=\Im(\mathbf{K})\lambda^{i};
-\Psi^{i}=-\Im(\mathbf{K})\lambda^{r}\\
-\nonumber
-\end{IEEEeqnarray} 
-therefore (\ref{intermediate function1a}) and (\ref{intermediate function1b}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function3a}
-\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi^{r}_{i}+\Psi_{i}^{r}\\\label{intermediate function3b}
-\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Phi_{i}^{i}+\Psi_{i}^{i}
-\end{IEEEeqnarray}
-Therefore based on (\ref{intermediate function3a}) and (\ref{intermediate function3b}), 
-(\ref{simple risk function1}) and (\ref{simple risk function2}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function4a}
-R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})=\frac{1}{2}|\Phi^{r}_{i}+\Psi_{i}^{r}|^{2}_{\epsilon}\\
-\label{intermediate function4b}
-R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})=\frac{1}{2}|\Phi^{i}_{i}+\Psi_{i}^{i}|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-Thus based on (\ref{intermediate function4a}) and (\ref{intermediate function4b}), the feasibility gap in (\ref{simple duality gap}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\Lambda^{r}, \Lambda^{i})=<(\Lambda^{r})^{T}, \Re(\mathbf{K})\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re(\mathbf{K})\Lambda^{i}>-<\Re(\mathbf{y})^{T}, \Lambda^{r}>-<\Im(\mathbf{y})^{T}, \Lambda^{i}>\\
-+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.
-\label{simple duality gap final}
-\end{IEEEeqnarray}
-Based on dual objective function in (\ref{simple dual function}), (\ref{simple duality gap final}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\Lambda^{r}, \Lambda^{i})=<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im(\mathbf{y})^{T}, \Lambda^{i}>-\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>-2\theta(\Lambda_{i}, \Lambda_{j})\\
--<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.\label{simple duality gap1}
-\end{IEEEeqnarray}
-The following ratio of the feasibility gap $G(\Lambda^{r}, \Lambda^{i})$ is used to measure the proximity of current solution to the optimal solution.
-The algorithm stops when the ratio satisfies a certain tolerance.
-\begin{equation}
-\frac{G}{G+\theta}
-\label{simple duality gap ratio1}
-\end{equation}
-\subsection{Update $\Phi$, $\Psi$ and $G$}
-$\Phi$, $\Psi$ and $G$ are updated in each iteration along with the optimization variables updated. The pseudo code to update $\Phi$, $\Psi$ and $G$ is given.
-
-Based on the definitions of $\Phi$ and $\Psi$ in (\ref{intermedia function 2a}) and (\ref{intermediate function 2b}), we have the following procedure to update $\Phi$ and $\Psi$ in real channel and imaginary channel, assume the optimization variables updated in each channel are indexed by $1$ and $2$, let $\sigma^{r}_{i}=(\lambda^{r}_{i})^{new}-\lambda^{r}_{i}$ and $\sigma^{i}_{i}=(\lambda^{i}_{i})^{new}-\lambda^{i}_{i}$ denote the differences between the updated optimization variables and the old optimization variables.\\
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{1}. Update $\Phi^{r}$ and $\Psi^{i}$ in real channel}{}
-\For{$i=1:N_{r}$}
-\State $\Phi_{i}^{r}=\Phi_{i}^{r}-\sigma_{1}^{r}\mathbf{K}^{r}_{i1}-\sigma_{2}^{r}\mathbf{K}_{i2}^{r}$
-\State $\Psi_{i}^{i}=\Psi_{i}^{i}-\sigma_{1}^{r}\mathbf{K}^{i}_{i1}-\sigma_{2}^{r}\mathbf{K}^{i}_{i2}$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{2}. Update $\Phi^{i}$ and $\Psi^{r}$ in imaginary channel}{}
-\For{$i=1:N_{r}$}
-\State $\Phi_{i}^{i}=\Phi_{i}^{i}-\sigma_{1}^{i}\mathbf{K}^{r}_{i1}-\sigma_{2}^{i}\mathbf{K}_{i2}^{r}$
-\State $\Psi_{i}^{r}=\Psi_{i}^{r}+\sigma_{1}^{i}\mathbf{K}^{i}_{i1}+\sigma_{2}^{i}\mathbf{K}^{i}_{i2}$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-Then the cost function term in (\ref{simple duality gap final}) are updated by \textbf{Procedure 3} and \textbf{Procedure 4}.
-The cost function terms are denoted by $\chi^{r}$ in real channel and $\chi^{i}$ in imaginary channel.
-\begin{IEEEeqnarray}[\relax]{l}
-\label{cost function update1}
-\chi^{r}=\sum_{i}^{N_{r}}|\Phi^{r}_{i}+\Psi^{r}_{i}|^{2}_{\epsilon}\\
-\label{cost function update2}
-\chi^{i}=\sum_{i}^{N_{r}}|\Phi^{i}_{i}+\Psi^{i}_{i}|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{3}. Update cost function in real channel}{$\chi^{r}$}
-\State $\chi^{r}=0$  \Comment{initial risk term}
-\For{$i=1:N_{r}$}
-\If{$|\Phi^{r}_{i}+\Psi^{r}_{i}|>\epsilon$}
-\State $\chi^{r}+=(|\Phi^{r}_{i}+\Psi^{r}_{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{4}. Update cost function in imaginary channel}{$\chi^{i}$}
-\State $\chi^{i}=0$  \Comment{initial risk term}
-\For{$i=1:N_{r}$}
-\If{$|\Phi^{i}_{i}+\Psi^{i}_{i}|>\epsilon$}
-\State $\chi^{i}+=(|\Phi^{i}_{i}+\Psi^{i}_{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-The pseudo code to update duality gap $G$ based on (\ref{simple duality gap1}) is shown in \textbf{Procedure 5}.
-Assume the indexes of optimization variables updated in real channel is $i$ and $j$, the indexes of optimization variables updated in imaginary channel is $m$ and $f$.
-Define the work sets in real and imaginary channels $S^{r}=[i,j]$ and $S^{i}=[m,f]$.
-Define $(\chi^{r})^{new}$ and $(\chi^{i})^{new}$ are the updated cost function terms based on \textbf{Procedure 3} and \textbf{Procedure 4}, the update process for the term $\theta(\Lambda^{r}, \Lambda^{i})$ in (\ref{simple duality gap1}) can be written as
-\begin{equation}
-\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}})=\bigtriangledown \theta^{r}_{S^{r}}+\bigtriangledown \theta^{i}_{S^{i}}-\frac{C}{2}((\chi^{r})^{new}+(\chi^{i})^{new}-\chi^{r}-\chi^{i}),
-\label{update dual objective function}
-\end{equation}
-Where $\theta_{S}^{r}$ is the gain of the sub dual objective function as shown in (\ref{gain work set selection lambda}), 
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S^{r}}^{r}=-\frac{1}{2}(\Sigma^{r}_{S^{r}})^{T}\Re{(\mathbf{K})}_{S^{r}S^{r}}\Sigma^{r}_{S^{r}}+(\Phi^{r}_{S^{r}})^{T}\Sigma^{r}_{S^{r}}-\epsilon<\mathbf{e}^{T}_{S^{r}},|(\Lambda^{r}_{S^{r}})^{new}|-|\Lambda^{r}_{S^{r}}|>\\
-\bigtriangledown \theta_{S^{i}}^{i}=-\frac{1}{2}(\Sigma^{i}_{S^{i}})^{T}\Re{(\mathbf{K})}_{S^{i}S^{i}}\Sigma^{i}_{S^{i}}+(\Phi^{i}_{S^{i}})^{T}\Sigma^{i}_{S^{i}}-\epsilon<\mathbf{e}^{T}_{S^{i}},|(\Lambda^{i}_{S^{i}})^{new}|-|\Lambda^{i}_{S^{i}}|>
-\end{IEEEeqnarray}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{5}. Update $G$}{}
-\State $G+=Re(\mathbf{y}_{1})\sigma^{r}_{i}+Re(\mathbf{y}_{2})\sigma^{r}_{j}$
-\State $G+=Im(\mathbf{y}_{1})\sigma^{i}_{m}+Re(\mathbf{y}_{2})\sigma^{i}_{f}$
-\State $G-=\epsilon(|\lambda^{r}_{i}+\sigma^{r}_{i}|-|\lambda^{r}_{i}|+|\lambda^{r}_{j}+\sigma^{r}_{j}|-|\lambda^{r}_{j}|)$
-\State $G-=\epsilon(|\lambda^{i}_{m}+\sigma^{i}_{m}|-|\lambda^{i}_{m}|+|\lambda^{i}_{f}+\sigma^{i}_{f}|-|\lambda^{i}_{f}|)$
-\State $G-=2(\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}}))$ \Comment{Update sub objective function based on (\ref{update dual objective function})}
-
-\State $G-=(\Sigma^{r}_{S^{r}})^{T}\Im(\mathbf{K}_{S^{r}S^{i}})\Sigma^{i}_{S^{i}}+(\Sigma^{r}_{S^{r}})^{T}\Psi^{r}_{S^{r}}+(\Sigma^{i}_{S^{i}})^{T}\Psi^{i}_{S^{i}}$ \Comment{Update $<\Lambda^{r},\Im(\mathbf{K})\Lambda^{i}>$}
-\EndProcedure
-\label{update G Phi and Psi}
-\end{algorithmic}
-\end{algorithm}
-
-Pseudo code for two types of combined 1-D searching solver are given by \textbf{Procedure 6} and \textbf{Procedure 7}. 
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{6}. One-shot 1-D combined searching solver}{} 
-\State Step 1. Search for two optimization variables based on single direction solver
-\For{$i=1:N_{r}$}
-\State calculate $\bigtriangledown \theta^{r}_{i}(\bigtriangledown \theta_{i}^{i})$\Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the dual variable with first and the second largest gain of sub objective function, denoted as 1st and 2nd
-\State Step 2. Update 1st and 2nd optimization variables based on double direction solver 
-\State update $\lambda^{r}_{1st}(\lambda^{i}_{1st})$ and $\lambda^{r}_{2nd}(\lambda^{i}_{2nd})$\Comment{Based on double direction solver \ref{double direction solver}}
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
-\EndProcedure
-\end{algorithmic}
-%\caption{Sequential 2-D Solver without Damping}
-\label{1D2D Nodamping}
-\end{algorithm}
-
- \begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{7}. Sequential 1-D combined searching solver}{}
-\State Step 1. Search for two optimization variables based on single direction solver
-\For{$i=1:N_{r}$}\Comment{First round searching}
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the optimization variable with the largest gain of objective function as $1st_{1}$
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to $1st_{1}$
-\For{$i=1:N_{r}$} \Comment{Second round searching}
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the optimization variable with the largest gain of objective function as $1st_{2}$
-\State Step 2. Update $1st_{1}$ and $1st_{2}$ optimization variables based on double direction solver 
-\State update $\lambda^{r}_{1st_{1}}(\lambda^{i}_{1st_{1}})$ and $\lambda^{r}_{1st_{2}}(\lambda^{i}_{1st_{2}})$\Comment{Based on double direction solver \ref{double direction solver}}
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
-
-\EndProcedure
-\end{algorithmic}
-%\caption{Sequential 2-D Solver with Damping}
-\label{1D2D damping}
-\end{algorithm} 
-\newpage
-The pseudo code of complex support vector detector (CSVD) is shown in Appendix \ref{Pseudo code of CSVD}
-
-%\section{Hyperparameter Setting}
-\section{Computer Simulations}
-Computer simulations are launched to test the detection and run time performance of proposed dual channel complex support vector detection algorithm.
-For sake of brevity, the real case is tested first, all the experiments are made by C, compiled by gcc version 4.8.3 on 64 bit Fedora (release 19) Linux system.
-The experiment platform is a desktop computer with I5-4th generation CPU with quad processing cores, 3.2 GHz clock rate, 8 GB RAM.
-
-For sake of brevity, we consider a real uncoded spatial multiplex large MIMO system to simulate one channel of the proposed dual channel complex support vector detection algorithm.
-with $N_{r}$ received antennas and $N_{t}$ transmitted antennas.
-The propagation channel matrix is constructed by channel gain components that are identically independent distributed (i.i.d) Gaussian random variables with zero mean and unit variance.
-transmitted symbols are mutually independent modulated by $M$ PAM with normalized average energy $\frac{1}{N_{t}}$, transmitted over flat fading channel, the sample of noise is AWGN with zero mean and variance $\frac{1}{10^{SNR/10}}$, where $SNR$ denotes the signal to noise ratio.
-We make experiment to low loading factor system $100\times 40$ and full loading factor $100\times 100$, with at least $1e^{5}$ channel realizations and at least $500$ symbol errors accumulated.
-Fig.\ref{SER performance} shows the symbol error rate (SER) performance, Table.\ref{iteration time} shows the average iteration time of real SVD for different SNR.
-\begin{figure}[htb]
-\centering
-%\def\svgscale{0.5}
-\def\svgwidth{\columnwidth}
-\input{BER_curve_real_system.pdf_tex}
-\caption{SER performance of $100\times 100 $ and $100\times 40$ MIMO system}
-\label{SER performance}
-\end{figure}
-
-\begin{table}[htb]
-\renewcommand{\arraystretch}{1.3}
-\caption{Average Iteration Time of Real Support Vector Detector}
-\label{iteration time}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*} {\bfseries Array Size} & \multicolumn{9}{|c|}{\bfseries SNR}\\
-\cline{2-10}
- &6& 8 &10& 12& 14& 16& 18& 20& 22\\
-\hline
-$100\times 40$&682 &681 &681 &681& 680 &679 &678&677 & 680\\
-\hline
-$100\times 100$&1925 &1916& 1903& 1885& 1862& 1827& 1782&1723&1654 \\
-\hline
-\end{tabular}
-\end{table}
+define $\bar{\mathbf{y}}=[\mathbf{y}^{T}, 0]^{T}$ and $\bar{\mathbf{H}}=[\mathbf{H}^{T}, \sqrt{N_{0}}\mathbf{I}_{N_{t}}]^{T}$, $\mathbf{I}_{N_{t}}$ denotes $N_{t}\times N_{t}$ identity matrix, $\bar{\mathbf{h}}_{i}$ denotes the $i$th row of $\bar{\mathbf{H}}$.
+The equivalent unconstrained least square problem is given by
+\begin{equation}
+\min_{\hat{\mathbf{s}}}||\bar{\mathbf{y}}-\bar{\mathbf{H}}\hat{\mathbf{s}}||^{2}=\min_{\hat{\mathbf{s}}}\sum_{i=1}^{N_{r}+N_{t}}(\bar{\mathbf{y}}_{i}-\bar{\mathbf{h}}_{i}\hat{\mathbf{s}})^{2},
+\label{MMSE least square}
+\end{equation}
+Similar to (\ref{ZF solution}), the solution of (\ref{MMSE least square}) is given by\cite{gore2002performance}\cite{wubben2003mmse}
+\begin{equation}
+\tilde{\mathbf{s}}=\bar{\mathbf{H}}^{\dagger}\bar{\mathbf{y}}=\mathbf{G}\mathbf{y},
+\label{MMSE solution}
+\end{equation} 
+From (\ref{empirical risk MIMO}), (\ref{ZF least square}) and (\ref{MMSE least square}), we can conclude ZF and MMSE are based on ERM principle.
+In view of statistical learning, when the VC-dimension of the regression function is finite\cite{vapnik1998statistical}, with the number of training data (in LS-MIMO it refers to $N_{r}$) increasing, empirical risk converges to actual risk rapidly, independent to the probability measure ($P(y, \mathbf{h})$)\cite{vapnik1998statistical}.
+The asymptotical consistence of empirical risk is achieved when the number of training data is large, this explains why the ERM based estimators (ZF and MMSE) can achieve near optimal performance in the LS-MIMO with low loading factor ($\alpha=\frac{N_{t}}{N_{r}}\ll 1$, $N_{t}\ll N_{r}$, the diversity gain of ZF/MMSE is $N_{r}-N_{t}+1$\cite{paulraj2003introduction}).
+This demonstrates the effectiveness of LDs (ZF/MMSE) for low loading LS-MIMO systems.
+However, in medium and full loading LS-MIMO, the diversity of ZF/MMSE is close to or equal to 1, this can be explained by the fact that ERM principle is not effective when the size of the training data set is small.
+
+\section{Structural Risk Minimization: why support vector regression}
+In this section, we present the explanation why support vector regression (SVR) are promising in the medium and full loading LS-MIMO.
+Based on the theoretical justifications of SVR based on the structural risk minimization (SRM) principle, we demonstrate the fitness of SVR based detector to be used as a preliminary estimator that can replace the traditional ZF/MMSE detectors.
+
+Given the situation that ZF/MMSE have inferior performance in full loading LS-MIMO systems because of the asymptotical consistence of ERM principle.
+We consider another principle in statistical learning theory that takes into account the small training data set size.
+Based on statistical learning theory, the actual risk is upper bounded in probability by\cite{vapnik1998statistical}
+\begin{equation}
+R(f_{c})\leq R_{emp}(f_{c})+\frac{B\epsilon}{2}(1+\sqrt{1+\frac{4R_{emp}(f_{c})}{B\epsilon}}),
+\label{bound of actual risk}
+\end{equation}
+if the loss function is bounded by 
+\begin{equation}
+0\leq L(y, f_{c}(\mathbf{h}))\leq B\quad f_{c}\in \Lambda, B>0
+\label{bound of loss function}
+\end{equation}
+$\epsilon$ in (\ref{bound of actual risk}) is 
+\begin{equation}
+\epsilon=4\frac{m(\ln(\frac{2l}{m})+1)}{l}
+\label{epsilon bound}
+\end{equation}
+where $l$ is the number of training data and $m$ is the VC-dimension of candidate function $f_{c}$.
+
+The second summand of the right hand side of (\ref{bound of actual risk}) is called confidence interval, which is determined by the complexity of the candidate function (VC-dimension) $f_{c}$\cite{vapnik1999overview}.
+From (\ref{bound of actual risk}) we can conclude that\\
+1.
+If $\frac{l}{m}$ is large (typically that is $\frac{l}{m}\geq 20$), the confidence interval in (\ref{bound of actual risk}) tends to be vanished, therefore a small empirical risk can guarantee a small actual risk, ERM principle is effective.\\
+2. If $\frac{l}{m}$ is small, a small empirical risk can not guarantee a small actual risk.\\
+In the medium or full loading LS-MIMO, where the number of training data $N_{r}$ is not very large comparing to the dimensionality of the regression function $N_{t}$, structural risk minimization (SRM) principle, which minimize the two terms in the right hand side of (\ref{bound of actual risk}) simultaneously is more effective to find a solution that guarantee a small actual risk.
+SRM principle aims to find a simplest function (small confidence interval) that minimize the training error (empirical risk).
+
+Based on the constructive SRM principle, SVR is designed by making a trade off between minimizing the complexity of function (regularization) and minimizing training error (risk functional).
+As to the full loading LS-MIMO systems, SVR based detector can guarantee a better regression performance (lower error probability of detection) than ZF/MMSE LDs in a feasible SNR region.
+Furthermore, By exploiting "channel hardening" phenomenon\cite{hochwald2004multiple}, a fast training algorithm can be developed in dual optimization process of SVR.
+
 % An example of a floating figure using the graphicx package.
@@
 % \fnbelowfloat command of the stfloats package.
-%\section{Complexity Analysis}
-
-%\section{Conclusion}
-%The conclusion goes here.
+
+\section{Conclusion}
+In conclusion, SVR is a suitable algorithmic framework for designing the preliminary detector in full loading LS-MIMO systems, which can replace traditional LD (ZF/MMSE) in the preprocessing stage of some searching algorithms such as likelihood ascend searching (LAS)\cite{vardhan2008low}\cite{li2010multiple} and genetic algorithm (GA)\cite{juntti1997genetic}\cite{ergun2000multiuser}.
+SVR based detectors have the following advantages:\\
+1. Better performance in the feasible SNR region (more accurate estimate of the regression coefficient vector $\mathbf{s}$ in (\ref{multidimensional regression estimation})).\\
+2. Lower computational complexity by exploiting the characteristic of high dimensional random channel matrix $\mathbf{H}$.\\ 
+3. Comparing with MMSE, SVR based detector do not require the information of noise variance.
 
@@
 
-\appendices
+%\appendices
 %\section{Proof of the First Zonklar Equation}
@@
 % if you want by leaving the argument blank
-\section{Pseudo Code of CSVD}\label{Pseudo code of CSVD}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{CSVD}{$\mathbf{y}$,$\mathbf{H}$}
-\State Step 1. Initialization
-\State $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ \Comment{kernel matrix}
-\State $\chi^{r}=0$, $\chi^{i}=0$ \Comment{risk function}
-\For{$i=1:N_{r}$}\Comment{initialize $\lambda^{r}$, $\lambda^{i}$, $\Phi^{r}$, $\Phi^{i}$, $\Psi^{r}$, $\Psi^{i}$ and duality gap $G$}
-\State $\lambda_{i}^{r}=0, \lambda_{i}^{i}=0$
-\State $\Phi_{i}^{r}=Re(y_{i}), \Phi_{i}^{i}=Im(y_{i})$
-\State $\Psi_{i}^{r}=0, \Psi_{i}^{i}=0$
-\If{$|\Phi^{r}_{i}|>\epsilon$}
-\State $\chi^{r}+=(|\Phi^{r}_{i}|-\epsilon)^{2}$
-\EndIf
-\If{$|\Phi^{i}_{i}|>\epsilon$}
-\State $\chi^{i}+=(|\Phi_{i}^{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor 
-\State $G=C(\chi^{r}+\chi^{i})$ \Comment{initialize duality gap}
-\State $\theta=-0.5G$ \Comment{initialize objective function}
-\State  Step 2. if $G>tol$, go to step 3, else go to Step 5
-\State Step 3.
-\State call combined 1-D searching solver in \textbf{Procedure 6} and \textbf{Procedure 7} \Comment{find and update two optimization variables in the real and imaginary channel} 
-\State Step 4. \textbf{Procedure 5} update $\frac{G}{G+\theta}$, go back to step 2.
-\State Step 5.
-\State $\tilde{\mathbf{x}}=\mathbf{H}^{H}(\Lambda^{r}+i\Lambda^{i})$ \Comment{reconstruct $\mathbf{x}$}
-\State $\mathbf{x}=\mathbb{Q}(\tilde{x})$\Comment{$\mathbb{Q}(\cdot)$ denotes quantization operation based on symbol constellation}
-\State Step 6. \textbf{Return} $\mathbf{x}$ 
-\EndProcedure
-\end{algorithmic}
-\label{CSVD algorithm}
-\caption{Dual Channel Complex Support Vector Detection Algorithm }
-\end{algorithm}
+%\section{}
 %Appendix two text goes here.
@@
 %\end{thebibliography}
-
+%\newpage 
+\bibliographystyle{IEEEtran}
+\bibliography{citation}
 % biography section
@@
 % that's all folks
-%\end{spacing}
-
-\newpage
-\bibliographystyle{IEEEtran}
-\bibliography{citation}	
-\end{spacing}												
 \end{document}

### 2015-11-27 SVR for large MIMO/real SVR matlab/CSVR/Verification Test/Verification_SNR.m

@@ -4,11 +4,10 @@ clear all;
 tic
 SNR=2:2:50;   %receive signal to noise ratio in dB
 SNRd=10.^(SNR./10);   %receive signal to noise ratio decimal
-M=120;   %number of training data samples
+M=30;   %number of training data samples
 M_t=1000; %number of testing data samples
-N=120; %the dimensions of the linear function
+N=30; %the dimensions of the linear function
 pav=1/N;      %the average power of the regression coefficiences
-w=complex(normrnd(0, sqrt(pav/2), [N,1]), normrnd(0, sqrt(pav/2),[N,1]));   %the true regression coeffeciences
 % Pt=norm(w)^(2);   %the total power of the true function 
 d_hat=zeros(M,1); %the true output of the linear function in training part
 d=zeros(M,1);   %the observations in training part
@@ -16,7 +15,7 @@ w_svr=zeros(M,1); %the regression estimation coefficiences from SVR
 noiseV=1./SNRd;
 realization=1e3;  %the realization time
 epsilon=0;
-C=1;
+C=0.1;
 tol=1e-3;
 MSE_training_svrV=zeros(length(SNR),1);  %training output MSE for SVR
 MSE_training_svr_coV=zeros(length(SNR),1);  %training MSE for coefficiences vector for SVR
@@ -26,11 +25,11 @@ MSE_training_mmse_coV=zeros(length(SNR),1); %training MSE for coefficiences vect
 MSE_testing_mmseV=zeros(length(SNR),1); %testing MSE for MMSE
 
 %% generate the file to record the simulation results
-fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\Verification Test\Test Data\Prediction_coefficintVector.txt', 'a');
+fid=fopen('F:\GitHub\Tianpei\SVR for large MIMO\real SVR matlab\CSVR\Verification Test\Test Data\FunctionEstimation_withoutNoise.txt', 'a');
 fprintf(fid, '=======================================\n');
-fprintf(fid, 'this document shows the results of the relation between prediction and MSE of coefficient vector\n');
-fprintf(fid, 'this document compare the output of SVR and MMSE regression from the view of SNR\n');
[…]

### 2015-12-13 Thesis Draft Tianpei Chen/Thesis Draft/C-CSVR.tex

@@
 \section{Channel Hardening Approximation}
-\section{CSVPD-LAS versus MMSE-LAS}
+\section{SVPD-LAS versus MMSE-LAS}
 The single solution based metaheuristics which are also defined as trajectory methods, start from an initial solution and the search process performs on a single solution at any time as a trajectory in the searching space.
 In resent years, several single solution based metaheuristic algorithms are applied to LS-MIMO detection problem, such as likelihood ascend searching (LAS) algorithm and variants\cite{vardhan2008low}\cite{cerato2009hardware}\cite{li2010multiple} and Tabu search algorithms and variants\cite{srinidhi2011layered}\cite{datta2010random}.
+Here we consider SVPD aided multi update- LAS algorithm (SVPD-MLAS), which utilizes SVPD to get the initial estimate of the transmit symbol vector, we compare its performance with MMSE aided multi-update LAS algorithm (MMSE-MLAS), simulation results demonstrate the performance improvement of SVPD-MLAS over MMSE-MLAS.
 \section{CSVPD-OPIC versus MMSE-OPIC}
+The Second post processing detector we consider is parallel interference cancellation (PIC).
+PIC works in a multi-stage manner, at the $l+1$th stage, PIC utilizes the decisions made for all the other users at $l$the stage to cancel the interference present in the received signal $\mathbf{y}$ for the desired substream.
+Comparing to successive interference cancellation (SIC), PIC has a lower processing delay and is more robust to inter stream error propagation\cite{chin2002parallel}.
+These two gains increase when the number of users increases.
+SVPD is used in the first stage of PIC algorithm, referred as SVPD-PIC, we compare the performance of SVPD-PIC with MMSE aided PIC (MMSE-PIC), and simulation results demonstrate a considerate performance improvement can be achieved in LS-MIMO systems.
+
+Fig.
+\ref{PIC scheme}, shows the structure of PIC scheme.
+In the first stage , the initial estimate of transmit symbol vector $\mathbf{s}$ is generated by preliminary detectors (e.g., SVPD, ZF, MMSE).
+In the following stages, as oppose to SIC, that cancels the interference from one substream at each stage, PIC cancels all the interference from the previous decisions of other substreams except the desired substream to be refined.
+This interference cancellation (IC) process can be applied to all the substreams in parallel, thus the processing delay can be reduced.
+After several stages refinement, the final solution is got.
+
+Let the superscript $l$ indexes the $l$th stage, the subscript $i$ indexes the $i$th substream and its residual observation after performing IC to received signal vector, $\mathbf{h}_{i}$ denotes the $i$th column of $\mathbf{H}$, corresponding to CSI of $i$th substream, at $l+1$ stage, the residual observation $\hat{\mathbf{y}}^{l+1}_{i}$ of the $i$th substream $\hat{\mathbf{s}}^{l+1}_{i}$ is given by
+\begin{equation}
+\mathbf{y}^{l+1}_{i}=\mathbf{y}-\sum_{m\neq i}^{N_{t}}\mathbf{h}_{m}\hat{\mathbf{s}}^{l}_{m}, \quad i=1,2,\ldots, N_{t} 
+\label{residual observation}
+\end{equation}
+
+$\hat{\mathbf{s}}^{l+1}_{i}$ then is refined by residual  observation $\mathbf{y}^{l+1}_{i}$ and CSI $\mathbf{h}_{i}$, 
+\begin{equation}
+\hat{\mathbf{s}}^{l+1}_{i}=\arg\min_{\tilde{\mathbf{s}}_{i}}\in \mathbb{O}||\mathbf{y}^{l+1}_{i}-\mathbf{h}_{i}\tilde{\mathbf{s}}_{i}||^{2},
+\label{refine PIC}
+\end{equation}
+
+(\ref{refine PIC}) can be performed by suboptimal detectors (e.g., SVPD, ZF, MMSE).
+In order to reduce the computational cost, the full residual observation $\mathbf{y}_{f}$ by cancelling the interference from all the substreams to the received signal vector is calculated first,
+\begin{equation}
+\mathbf{y}_{f}=\mathbf{y}-\sum_{m=1}^{N_{t}}\mathbf{h}_{m}\hat{\mathbf{s}}^{l}_{m},
+\label{full residual observation}
+\end{equation}  
+then (\ref{residual observation}) can be rewritten as 
+\begin{equation}
+\mathbf{y}^{l+1}_{i}=\mathbf{y}_{f}+\mathbf{h}_{i}\hat{\mathbf{s}}^{l}_{i} \quad i=1,2,\ldots, N_{t},
+\label{residual observation 2}
+\end{equation}

### 2015-12-13 Thesis Draft Tianpei Chen/Thesis Draft/C-GA.tex

@@
 Furthermore, instead of randomly generated initial population, the solution of the CSVPD is fed to Hybrid GA and the initial generation consists of the neighbour of the initial solution from CSVPD.
-\section{CSVPD aided Hybrid Genetic Algorithm}
+\section{SVPD aided Hybrid Genetic Algorithm}
 Genetic Algorithm (GA) is one of the population-based metaheuristic algorithms and can be viewed as a computational model of natural biological evolution process.
@@
 The best solution is chosen based on the fitness function when the stopping criteria satisfied.
-
 \subsection{Initialization}
@@
 \def\svgwidth{\columnwidth}
-\include{randomFlipping.tex_pdf}
+\input{randomFlipping.pdf_tex}
 \caption{Random Flipping with $\mathcal{F}=1$}
@@
 where $\mathbf{s}_{i}$ denotes the $i$th individual symbol vector in the generation, the individual with the smallest fitness function value is the fittest candidate (elite) in the generation.
-
 In each generation, the individuals with small $f(\mathbf{s}_{i})$ are chosen as the parents to generate offsprings, the offsprings are generated by recombining the parent symbol vectors, this process is recombination or crossover.
@@
 A simple cased of this process is shown in Fig.\ref{crossover}.
+
 \begin{figure}
@@
 \def\svgwidth{\columnwidth}
-\include{crossover.tex_pdf}
+\input{crossover.pdf_tex}
 \caption{Crossover operation to a pair of parent binary sequence}
@@
 \end{figure}
+
 \subsection{Mutation}
@@
 Fig.\ref{mutation} shows how mutation works.
+\iffalse
 \begin{figure}
@@
 \def\svgwidth{\columnwidth}
-\include{mutation.tex_pdf}
+\input{mutation.pdf_tex}
 \caption{Mutation operation to one bit in binary sequence}
@@
 \end{figure}
+\fi
+
+\begin{figure}
+\centering
+\def\svgwidth{\columnwidth}
+\input{mutation.pdf_tex}
+\caption{Mutation operation to one bit in binary sequence}
+\label{mutation}
+\end{figure}
+
 \subsection{OPIC} 

### 2015-12-18 Report Dec 2015/Report.tex
Report Dec imcomplete

--- 2015-10-14 Report Aug 5 2015/Report Aug 2015.tex
@@
 \documentclass[12pt, draftclsnofoot, onecolumn]{IEEEtran}
-%\documentclass[12pt,paper,final]{article}
-%
-%\documentclass[12pt, onecolummn]{report}
+%
 % If IEEEtran.cls has not been installed into the LaTeX system files,
@@
 % \documentclass[journal]{../sty/IEEEtran}
-
 \usepackage[latin1]{inputenc}
@@
 %\usepackage{caption}
-\usepackage{cite}
-\usepackage{ifpdf}
-\usepackage[cmex10]{amsmath}
+%\usepackage{cite}
+%\usepackage{ifpdf}
+%\usepackage[cmex10]{amsmath}
 \usepackage{algorithm}
-\usepackage{array}
-\usepackage{stfloats}
+%\usepackage{array}
+%\usepackage{stfloats}
 \usepackage{url}
-\usepackage{fixltx2e}
+%\usepackage{fixltx2e}
 \usepackage{setspace} 
@@
 \usepackage{calc}
+
 % Some very useful LaTeX packages include:
@@
 %
-\usepackage{fixltx2e}
+%\usepackage{fixltx2e}
 % fixltx2e, the successor to the earlier fix2col.sty, was written by
@@
 % Do not put math or special symbols in the title.
-\title{Report: Complex Support Vector Detector for Large MIMO System}
-
+\title{Progress Report}
 %
@@
 %\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
+
+\author{Tianpei Chen\\
+Department of Electrical and Computer Engineering\\
+McGill University\\
+Montreal, Quebec, Canada}
 
@@
 % in the abstract or keywords.
-%\begin{abstract}
-%The abstract goes here.
-%\end{abstract}
+\begin{abstract}
+The abstract goes here.
+\end{abstract}
 
 % Note that keywords are not normally used for peerreview papers.
-%\begin{IEEEkeywords}
-%IEEEtran, journal, \LaTeX, paper, template.
-%\end{IEEEkeywords}
+\begin{IEEEkeywords}
+IEEEtran, journal, \LaTeX, paper, template.
+\end{IEEEkeywords}
 
@@
 
-\section{Introduction}
+\section{System Model}
 % The very first letter is a 2 line initial drop letter followed
@@
 %\hfill September 17, 2014
-  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment.
-The promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} and long-term evolution (LTE)\cite{3GLTE}.
-The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve spectrum efficiency) and diversity gain (better reliability of communication link) are obtained by exploiting the spatial domain.
-Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously.
-This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.
-
-  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving ends.
-The uplink detector is one of the key components in a large MIMO system.
-With orders magnitude more antennas at the BS, benefits and challenges coexist in designing of detection algorithms for the uplink communication of large MIMO systems.
-On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexities of the algorithms become crucial to make the system practical.
-
-Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams.
-However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with the number of transmitted antennas, which is prohibitive for practical applications.
-
-As alternatives to MLD, linear detectors (LD) such as zero-forcing (ZF) and minimum mean square error (MMSE) with optimized ordering sequential interference cancellation (ZF-OSIC, MMSE-OSIC) are exploited in V-BLAST architecture\cite{wolniansky1998v}\cite{foschini1999simplified}\cite{benesty2003fast},  however the performance of ZF-OSIC and MMMSE-OSIC are inferior comparing to MLD.
-
-Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes the lattice structure of MIMO systems, which can achieve optimal performance with relatively much lower complexity comparing to MLD.
-However, SD has two major shortages that make it problematic to be integrated into a practical systems.
-The first shortage is SD has various complexities under different signal to noise ratios (SNR), while a constant processing data rate is required for hardware.
-The second shortage is the complexity of SD still has a lower bound that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
-The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different values of SNR.
-The FCSD inherits the principle of list based searching algorithms, which first generate a list of candidate symbol vectors and then the best candidate is chosen as the solution.
-The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC (sel-MMSE-OSIC)\cite{radji2009interference}.
-However, all these list based searching algorithms have the same shortage - their complexities increase exponentially with the number of transmit antennas and the order of modulation scheme\cite{radji2009interference}.
-Therefore, such algorithms are prohibitive when it comes to a large number of antennas or a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.
-
-%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}.
-Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of metaheuristic based detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance.
-such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
-Tabu search based algorithms which have superior performances compared to LAS detectors because of the efficient local minima exit strategy (e.g.
-Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g.
-Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g.
-Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) .
-Moreover, element based Lattice Reduction (LR) aided algorithms were also proposed to  large MIMO systems.\cite{zhou2013element}.
-
-Firmly grounded in framework of statistical learning theory, the Support Vector Machine (SVM) technique has become a powerful tool to solve real world supervised learning problems such as classification, regression and prediction.
-the SVM method is a nonlinear generalization of Generalized Portrait algorithm developed by Vapnik in 1960s\cite{vapnik1963pattern}\cite{vapnik1964note}, which can provide good generalization performance\cite{scholkopf2002learning}.
-
-Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
-Moreover, the kernel based methods\cite{scholkopf2002learning} were proposed which solve nonlinear learning tasks by mapping input data samples into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space.
-This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS).
-Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.
-
-Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual form, which can be solved by Quadratic Programming (QP).
-Decomposition methods were proposed to solve this QP problem by decomposing it into sub QP problems and solving them iteratively\cite{platt1999fast}.
-Therefore, the computational intensive numerical methods can be avoided.
-Decomposition is performed by sub set selection solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets S and N, S is the work set and N contains the remaining optimization variables.
-In each iteration, only the optimization variables in the work set is updated while keeping other optimization variables fixed.
-The Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} is an extreme case of the decomposition solvers.
-An important issue of the sub set selection solvers is the selection of the work set.
-One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring the final converge\cite{osuna1997improved}.
-The SMO algorithm restricts the size of the work set to two.
-A method to train SVM without offset was proposed In\cite{steinwart2011training}, with the comparable performance to the SVM with offset.
-A set of sequential single variable work set selection strategies, which require $O(n)$ searching time are proposed.
-The optimal double variable work set selection strategy, which performs exhaustively searching, however, requires $O(n^{2})$ searching time.
-The authors demonstrate that with the combination of two different proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.
-
-The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets.
-In communication and signal processing area, the channel gains, signals, waveforms etc.
-are all represented in complex form.
-Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain.
-The results in\cite{bouboulis2013complex} demonstrate the better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernels.
-Based on this work, we derive a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR).
-The detector can work in two parallel real SVR channels which can be solved independently.
-Moreover, only the real part of kernel matrix is needed in both channels.
-This means a large amount of computation cost saving can be achieved.
-Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
-is constructed without offset, Therefore, for each real SVR without offset, 
-%in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed.
-By this strategy, two variables can be updated at each iteration, with much smaller searching time.
-Two types of combined single optimization variable selection strategy are proposed based on the work in \cite{steinwart2011training}.
-The proposed combined single optimization variable selection strategy can approximate optimal double optimization variable selection strategy.
-The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.
-
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
-
-\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
-\subsection{Regression Model}
-Suppose we are given a training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$.
-$y_{i}$ denotes output.
-Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Omega}$, $\Omega \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$, $\Omega=V$).
-The regression model (either linear or non-linear) is given by
-\begin{equation}
-y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1,2,\ldots, L
-\label{equation1}
-\end{equation}
-
-\begin{figure}
-\centering
-\def\svgwidth{\columnwidth}
-\input{epsilon-SVR.pdf_tex}
-\caption{$\epsilon$-Support Vector Regression and Risk Functional}
-\label{epsilon-SVR}
-\end{figure}
-
-We present the primal optimization problem directly
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}} f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-s.t. \left\{\begin{array}{ll}
-y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
-\epsilon_{i}, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
-\end{array}\right.
-\label{primal optimization problem}
-\end{IEEEeqnarray}
-In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the solid line represents the estimation of the input-output relation, the area between two dash lines ($\epsilon$-bound) is called $\epsilon$-tube.
-Only those data samples located outside $\epsilon$-tube contribute to the estimation error.
-Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with additive noise of observations, $R(u)$ denotes the cost function.
-The simplest cost function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}.
-For example if the noise is Gaussian distributed, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$.
-The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.
-
-In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
-Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-\label{definition of slack variable1}
-\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
-\label{definition of slack variable2}
-\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon).
-\end{IEEEeqnarray} 
-Because the distance between the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero.
-That is $\xi_{i}\hat{\xi}_{i}=0$.
-\subsection{Cost Function}\label{cost function}
-The optimal cost function in (\ref{primal optimization problem}) can be derived based on maximum likelihood (ML) principle.
-Assume the data samples $\mathbf{x}_{i}$ in data set are iid, Let $f_{true}(\mathbf{x}_{i}), i=1,2,\cdots L$ denotes true regression function.
-the underlying assumption is $y_{i}=f_{true}(\mathbf{x}_{i})+\xi_{i}, i=1,2,\cdots, L$, $\xi_{i}$ denotes additive noise of the $i$th data sample, with probability density function (pdf) $Pr(\cdot)$.
-Let $P(\cdot)$ denotes the pdf of $y_{i}$.
-Based on ML principle we want to
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{f}\quad \prod_{i=1}^{L}P(y_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}P(f(\mathbf{x}_{i})+\xi_{i}|f(\mathbf{x}_{i}))=\prod_{i=1}^{L}Pr(\xi_{i})=\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))\\
-\label{cost function1}
-\end{IEEEeqnarray}
-Take the logarithm of $\prod_{i=1}^{L}Pr(y_{i}-f(\mathbf{x}_{i}))$, we have
-\begin{IEEEeqnarray}[\relax]{l}
-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
-\label{cost function2}
-\end{IEEEeqnarray}
-maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i})))$, therefore (\ref{cost function1}) is equivalent to 
-\begin{equation}
-\min_{f}-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),
-\label{cost function3}
-\end{equation}
-Let $c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))$ denotes the $i$th cost function, which is defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-\log(P(y_{i}-f(\mathbf{x}_{i}))).
-\label{cost function3}
-\end{IEEEeqnarray}
-Thus (\ref{cost function3}) can be rewritten as 
-\begin{equation}
-\min_{f}\quad  \sum_{i=1}^{L}c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i})),
-\label{Total risk function}
-\end{equation} 
-In $\epsilon$-SVR, in order to provide more flexibility to precision control, Vapnik's $\epsilon$-insensitive function, as shown in (\ref{Vepsilon}), is applied to (\ref{cost function3}).
-\begin{IEEEeqnarray}[\relax]{l}
-|u|_{\epsilon}=\left\{\begin{array}{ll}
-0   &if\quad |u|<\epsilon\\
-|u|-\epsilon  &otherwise\\
-\end{array}\right.
-\label{Vepsilon}
-\end{IEEEeqnarray}
-Thus the final form of cost function in $\epsilon$-SVR can be written as 
-\begin{equation}
-\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),
-\label{final cost function}
-\end{equation}
-Consider the cost function term in (\ref{primal optimization problem}),
-\begin{equation}
-\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))
-\end{equation}  
-the cost function term is determined according to the distribution of noise.  
-%where $m_{i}\in \mathbb{R}$, $m_{i}>0$ denotes the weight parameter, if $y_{i}>f_{estiamtion}(\mathbf{x})$, $m_{i}=m_{positive}$, else $m_{i}=m_{negative}$, Therefore the regularized risk function can written as
-%\begin{equation}
-%minimize\quad \lambda||\mathbf{w}||^{2}+\tilde{c}(\mathbf{x}, y, f(\mathbf{x})),
-%\label{total cost function}
-%\end{equation} 
-%where $\lambda$ denotes the weight of regularization term, divide (\ref{total cost function}) by $\frac{1}{2\lambda}$, we have the optimization problem  
-%\begin{equation}
-%minimize \quad \frac{1}{2}||\mathbf{w}||^{2}+\sum_{i=1}^{l}C_{i}(-log(P(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))),
-%\label{final cost function}
-%\end{equation}
-%where $C_{i}=\frac{m_{i}}{2\lambda l}$, based on (\ref{final cost function}), by introducing slack variables, we can easily derive the equivalent optimization problem as same as (\ref{primal optimization problem}):
-%\begin{eqnarray}
-%\nonumber
-%minimize \quad f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+\sum_{j=1}^{l}C_{i}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
-%s.t. \left\{\begin{array}{ll}
-%y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b &\leq \epsilon+\xi_{i}\\
-%\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} &\leq \epsilon+\hat{\xi}_{i}\\
-%\epsilon, \xi,\hat{\xi} &\geq 0\\
-%\end{array}\right.
-%\label{primal objective function}
-%\end{eqnarray}
-%where $R(x)=-log(P(x))$, by this way, the discontinuity of $\epsilon$-insensitive function is conquered. 
-\subsection{Lagrange Duality}\label{section lagrange duality}
-According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier.
-The Lagrange function is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L(\mathbf{w}, b, \xi_{i}, \hat{\xi}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})=
-\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))-\sum_{i=1}^{L}(\eta_{i}\xi_{i}+\hat{\eta}_{i}\hat{\xi}_{i})\\
-\nonumber
-+\sum_{i=1}^{L}\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\sum_{i=1}^{L}\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})\\
-s.t. \left\{\begin{array}{cc}
-\eta_{i}, \hat{\eta}_{i}, \alpha_{i}, \hat{\alpha}_{i}\geq 0, i=1,2,\cdots L\\
-\xi_{i}, \hat{\xi}_{i}\geq  0, i=1,2,\cdots L\\
-\end{array}\right.
-\label{lagrange duality1}
-\end{IEEEeqnarray}
-where $\eta_{i}$, $\hat{\eta}_{i}$, $\alpha_{i}$, $\hat{\alpha}_{i}$ are Lagrange multipliers.
-
-The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the primal constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions.
-Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.
-
-Assume a constraint optimization problem is given by 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}} \quad f(\mathbf{w})\\
-s.t. \quad c_{i}(\mathbf{w})\leq 0, i=1,2,\ldots L,
-\label{constraint optimization problem}
-\end{IEEEeqnarray}
-its Lagrange function is given by 
-\begin{equation}
-L(\mathbf{w}, \mathbf{a})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),
-\label{orginal Lagrange}
-\end{equation}
-where $\mathbf{a}=[a_{1},a_{2},\ldots, a_{L}]^{T}$ denotes the vector consist of Lagrange multipliers.
- Based on Theorem 6.21 in \cite{scholkopf2002learning}, a variable pair $[\bar{\mathbf{w}}, \bar{\mathbf{a}}]$ is the solution to (\ref{constraint optimization problem}) if and only if the following inequalities are satisfied
- \begin{equation}
- L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
- \label{KKT inequalities}
- \end{equation}
-This inequalities (also called saddle point conditions) yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{original KKT condition1}
-\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, \mathbf{a})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\
-\label{original KKT condition2}
-\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\
-\label{original KKT condition3}
-\bar{a}_{i}c_{i}(\bar{\mathbf{w}})=0, i=1,2,\ldots L
-\end{IEEEeqnarray}
-In order to satisfy the first inequality in (\ref{KKT inequalities}), (\ref{original KKT condition1}) has to hold,
-applying (\ref{original KKT condition1}) to (\ref{lagrange duality1}), which are  
-\begin{IEEEeqnarray}[\relax]{l}
-\label{partial1}
-\partial_{\mathbf{w}} L=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\
-\label{partial2}
-\partial_{\xi_{i}}L=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\
-\label{parial3}
-\partial_{\hat{\xi}_{i}}L=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\
-\label{partial4}
-\partial_{b}L=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber
-\end{IEEEeqnarray}
-Then by substituting (\ref{partial1})-(\ref{partial4}) to (\ref{lagrange duality1}), (\ref{lagrange duality1}) can be rewritten as :
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha_{i}, \hat{\alpha}_{i})=\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[R(\xi_{i})+R(\hat{\xi}_{i})]-\sum_{i=1}^{L}[(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}\\
-\nonumber
-+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}[y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}]+\\
-\sum_{i=1}^{L}\hat{\alpha}_{i}[\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i}]
-\label{lagrange duality1 inter}
-\end{IEEEeqnarray}
-notice in (\ref{partial4}), $\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha}_{i})=0$, define $\tilde{R}(u)=R(u)-uR^{'}(u)$, (\ref{lagrange duality1 inter}) can be further simplified to
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{i=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}[(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i})]\\
-+\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
-\label{dual objective function1}
-\end{IEEEeqnarray}
-In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold.
-A $\mathbf{w}$ that satisfies the conditions in (\ref{original KKT condition2}) is in the feasible region defined by inequality constraints as mentioned (\ref{constraint optimization problem}).
-In $\epsilon$-SVR, this condition is satisfied by making use of the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ defined in (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}).
-Define that $\tilde{\mathbf{w}}$ is in the feasible region and satisfies the conditions in (\ref{original KKT condition1}), notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\tilde{\mathbf{w}}, \mathbf{a})$, thus yielding the dual optimization problem, which is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}}L(\tilde{\mathbf{w}},\mathbf{a})\equiv\max_{\alpha_{i}, \hat{\alpha}_{i}}\quad \theta(\alpha_{i}, \hat{\alpha}_{i}) =-\frac{1}{2}\sum_{i=1}^{L}\sum_{j=1}^{L}(\alpha_{i}-\hat{\alpha_{i}})(\alpha_{j}-\hat{\alpha_{j}})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+C\sum_{i=1}^{L}(\tilde{R}(\xi_{i})+\tilde{R}(\hat{\xi}_{i}))\\
-+\sum_{i=i}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]
-\label{dual optimization function2}
-\end{IEEEeqnarray}
-Define $\mathbf{a}=[\alpha_{1},\alpha_{2}, \ldots, \alpha_{L}]^{T} $, $\mathbf{\hat{a}}=[\hat{\alpha}_{1},\hat{\alpha}_{2}, \ldots, \hat{\alpha}_{L}]^{T} $, $\mathbf{y}=[y_{1}, y_{2}, \ldots y_{L}]^{T}$, $ \mathbf{e}=[1,1,\ldots,1]^{T}\in \mathbb{R}^{L}$, $\mathbf{e}_{i}$ denotes the vector that only $i$th component is 1 while the rest are all 0, $\mathbf{R}_{\xi}=[\tilde{R}(\xi_{1}), \tilde{R}(\xi_{2}), \ldots, \tilde{R}(\xi_{L})]^{T}$, $\mathbf{R}_{\hat{\xi}}=[\tilde{R}(\hat{\xi}_{1}), \tilde{R}(\hat{\xi}_{2}), \ldots, \tilde{R}(\hat{\xi}_{L})]^{T}$, $\mathbf{K}_{ij}=\Phi(\mathbf{x}_{j})^{T}\Phi(\mathbf{x}_{i})$ denotes a component of data kernel matrix at $i$th row and $j$th column.
-An alternative vector form of (\ref{dual optimization function2}) can be written as
-\begin{equation}
-\max_{\mathbf{a}, \hat{\mathbf{a}}}\theta(\mathbf{a},\hat{\mathbf{a}})=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\mathbf{K}(\mathbf{a}-\mathbf{\hat{a}})+(\mathbf{y}-\epsilon \mathbf{e})^{T}\mathbf{a}+(-\mathbf{y}-\epsilon\mathbf{e})^{T}\mathbf{\hat{a}}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
-\label{dual objective alternative}
-\end{equation} 
-We define the following $2L$ vectors 
-$\mathbf{a}^{(*)}$= [$\mathbf{a} \atop \mathbf{\hat{a}}$], $\mathbf{v}\in \mathbb{R}^{2L}$, 
-\begin{IEEEeqnarray}[\relax]{l}
-[\mathbf{v}]_{i}=\left\{\begin{array}{ll}
-1\quad i=1,\ldots, l\\
--1\quad i=l+1,\ldots, 2l\\ 
-\end{array}\right.
-\end{IEEEeqnarray}
-(\ref{dual objective alternative}) can also be reformulate as 
-\newcommand{\mysmallarraydecl}{\renewcommand{%
-\IEEEeqnarraymathstyle}{\scriptscriptstyle}%
-\renewcommand{\IEEEeqnarraytextstyle}{\scriptsize}%
-\renewcommand{\baselinestretch}{1.1}%
-\settowidth{\normalbaselineskip}{\scriptsize
-\hspace{\baselinestretch\baselineskip}}%
-\setlength{\baselineskip}{\normalbaselineskip}%
-\setlength{\jot}{0.25\normalbaselineskip}%
-\setlength{\arraycolsep}{2pt}}
-\begin{equation}
-\max_{\mathbf{a}^{*}}\quad \theta(\mathbf{a}^{*})=-\frac{1}{2}(\mathbf{a}^{*})^{T}\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\mathbf{K}& -\mathbf{K}\\
--\mathbf{K}& \mathbf{K}
-\end{IEEEeqnarraybox*}\right]
-\mathbf{a}^{(*)}+[(\mathbf{y}-\epsilon)^{T}, (-\mathbf{y}-\epsilon)^{T}]\mathbf{a}^{(*)}+C\mathbf{e}^{T}(\mathbf{R}_{\xi}+\mathbf{R}_{\hat{\xi}}),
-\label{vectorize dual optimization function}
-\end{equation}
-
-Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor the proximity of the current solution and the optimal solution.
-Thus it can be used as a stopping criterion.
-In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
-(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
-(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
-\end{array}\right. 
-\label{KKT complimentary}
-\end{IEEEeqnarray}
-Based on the definitions of slack variables in (\ref{definition of slack variable1}) an (\ref{definition of slack variable2}), only when there is a outlier exists, $\xi_{i}$ or $\hat{\xi}_{i}$ can be non zero, that is
-\begin{equation}
-\xi_{i} or \hat{\xi}_{i}=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
-\label{definition of slack variable3}
-\end{equation} 
-because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $y_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig.
-\ref{epsilon-SVR}.
-Therefore at most one of $(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})$  and $(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})$ can be zero.
-In order to satisfy the KKT complementary conditions in (\ref{KKT complimentary}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
-
-Therefore the complete KKT complementary conditions of $\epsilon$-SVR is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{cc}
-\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
-\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L\\
-(CR^{'}(\xi_{i})-\alpha_{i})\xi_{i}=0, i=1,2,\ldots, L\\
-(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}=0, i=1,2,\ldots, L\\
-\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots L
-\end{array}\right. 
-\label{complete KKT complimentary}
-\end{IEEEeqnarray}
-
-%The conditions in (\ref{KKT complimentary}) are called KKT complimentary condition. 
-%Obviously by taking partial derivations of (\ref{lagrange duality1}) with respect to $\mathbf{w}$, $\xi_{i}$, $\hat{\xi}_{i}$ and $b$, $\theta(\alpha_{i},\hat{\alpha}_{i})\leq \Theta(\mathbf{w},\alpha_{i}, \hat{\alpha}_{i}, \eta_{i}, \hat{\eta}_{i})$, notice in $\theta(\alpha_{i}, \hat{\alpha}_{i})$ KKT conditions in (\ref{partial1}) to (\ref{partial4}) are satisfied.
-Therefore, KKT complimentary conditions (\ref{KKT complimentary}) is the only requirement to find global optimal point of original optimization problem.
-Because
-%\begin{equation}
-%\Theta(\mathbf{w},\alpha, \hat{\alpha}, \eta, \hat{\eta})=f(\mathbf{w})+\sum_{i}(\alpha_{i} g_{i}(\mathbf{w})+\hat{\alpha}_{i}\hat{g}_{i}(\mathbf{w}))+\sum_{i}(\eta_{i} l_{i}(\mathbf{w})+\hat{\eta}_{i}\hat{l}_{i}(\mathbf{w})),\label{Theta function}
-%\end{equation} 
-%where $g_{i}(\mathbf{w})$, $\hat{g_{i}(\mathbf{w})}$, $l_{i}(\mathbf{w})$, $\hat{l}_{i}(\mathbf{w})$ denote inequality constraints.
-%\begin{IEEEeqnarray}[\relax]{l}
-%g_{i}(\mathbf{w})=\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}\leq 0\\
-%\hat{g}_{i}(\mathbf{w})=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon-\hat{\xi}_{i}\leq 0\\
-%l_{i}(\mathbf{w})=-\xi_{i}\leq 0\\
-%\hat{l}_{i}(\mathbf{w})=-\hat{\xi}_{i}\leq 0\\
-%\nonumber
-%\end{IEEEeqnarray}
-%Hence $\Theta\leq f(\mathbf{w})$, we have $\theta\leq \Theta\leq f(\mathbf{w})$, therefore the upper bound of $\theta$ is determined by the original objective function $f(\mathbf{w})$.
-when $\theta=f(\mathbf{w})$,  according to (\ref{Theta function}), the linear combination term of inequality constraints equal to zero, that is, KKT complimentary conditions in (\ref{KKT complimentary}) satisfied.
-hence the global optimal point is found for both $\theta$ and $f(\mathbf{w})$ if and only if the equality holds.
-Therefore duality gap is defined as $G=f(\mathbf{w})-\theta$, which can be used as an evaluation for the closeness of one solution to the global optimal.
-
-%In conclusion, the dual objective function can be written as
-
-\section{Dual Channel Complex Support Vector detection for Large MIMO system}\label{dual channel CSVR}
-\subsection{System Model}\label{system model}
-  Consider a uncoded complex large MIMO uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with transmit antenna.
+Consider a uncoded complex Large-Scale MIMO (LS-MIMO) uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with one transmit antenna.
 The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
-Typically large MIMO systems have hundreds of antennas at the BS, as shown in Fig {\ref{large MIMO uplink model}}.
-  \begin{figure}[htb]
-  \centering
-  \def\svgwidth{\columnwidth}
+Typically LS-MIMO systems have hundreds of antennas at the BS,
+%as shown in Fig {\ref{large MIMO uplink model}}.
+ % \begin{figure}[htb]
+  %\centering
+  %\def\svgwidth{\columnwidth}
   %\includegraphics[scale=•]{•}
-  \input{largeMIMOuplink.pdf_tex}
-  \caption{Large MIMO uplink system }
-  \label{large MIMO uplink model}
-  \end{figure}
+ % \input{largeMIMOuplink.pdf_tex}
+  %\caption{Large MIMO uplink system }
+  %\label{large MIMO uplink model}
+  %\end{figure}
 
@@
 The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian random variable with zero mean and unit variance.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, $\mathbf{H}_{ij}$ denotes the component of $\mathbf{H}$ at $i$th row and $j$th column, representing the channel response from $i$th receive antenna to the $j$th transmit antenna.
+Each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian (CSCG) random variable with unit variance.
 Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
@@
 The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
-\subsection{Complex Regression Model}
- Based on the discrete time model of a large MIMO uplink system of (\ref{discrete time MIMO system}), our regression model is set such that the training data set at the detector are $(\mathbf{h}_{1}, y_{1})(\mathbf{h}_{2}, y_{2}), \ldots, (\mathbf{h}_{N_{r}}, y_{N_{r}})$, where $\mathbf{h}_{i}$ denotes $i$th row of matrix $\mathbf{H}$.
-This yields a regression task without offset $b$ in (\ref{equation1}) :
- \begin{IEEEeqnarray}[\relax]{l}
- y_{i}=f_{true}(\mathbf{h}_{i})+n_{i}, i=1,2\ldots L\\
- \label{regression part1a}
- f_{true}(\mathbf{h}_{i})=\mathbf{h}_{i}\cdot\mathbf{s}, i=1,2,\ldots, L\\
- \label{regression part1b}
- \end{IEEEeqnarray}
- where $f_{true}()$ denotes the underlying true regression function, $n_{i}$ denotes discrete sample of additive noise.
-In this regression problem, received symbols $y_{i}$ are the observations, $\mathbf{h}_{i}$ are the input data samples, transmitted symbol vector $\mathbf{s}$ contains the regression coefficients.
-We employ complex support vector regression (CSVR) without offset term $b$.
-As shown in (\ref{original KKT condition1}) the first KKT condition is satisfied by finding the saddle point $\bar{\mathbf{w}}$ by taking paritial derivatives of $L(\mathbf{w},a_{i})$ with respect to $\mathbf{w}$.
-Mathematical results of Wirtinger's calculus in Reproducing Kernel Hilbert Space (RKHS) are employed to calculate partial derivatives of Lagrangian function of CSVR in complex manner\cite{bouboulis2011extension}.
-First we generalize our regression model by complex RKHS,
-Define a real RKHS $\mathcal{H}$, $<,>_{\mathcal{H}}$ denotes the corresponding inner product in $\mathcal{H}$.
-define complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $<,>_{\mathbb{H}}$ denotes the corresponding inner products in $\mathbb{H}$.
-Assume $\mathbf{x}, \mathbf{y},\mathbf{z}$ are complex vectors, $\mu$, $\chi$ $\in \mathbb{C}$, In general a complex Hilbert space $\mathbb{H}_{g}$ has the following properties
-\newtheorem{Lemma}{Lemma}
-\newtheorem{Property}{Property}
-\begin{Property}
- $<\mathbf{x},\mathbf{y}>_{\mathbb{H}_{g}}=(<{\mathbf{y},\mathbf{x}}>_{\mathbb{H}_{g}})^{*}$
-\label{CHSProperty1}
-\end{Property}
-
-\begin{Property}
-$<\mu\mathbf{x}+\chi\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}=\mu<\mathbf{x},\mathbf{z}>_{\mathbb{H}_{g}}+\chi<\mathbf{y},\mathbf{z}>_{\mathbb{H}_{g}}$
-\label{CHSProperty2}
-\end{Property}
-
-\begin{Property}
-$<\mathbf{z}, \mu\mathbf{x}+\chi\mathbf{y}>_{\mathbb{H}_{g}}=\mu^{*}<\mathbf{z},\mathbf{x}>_{\mathbb{H}_{g}}+\chi^{*}<\mathbf{z}, \mathbf{y}>_{\mathbb{H}_{g}}$
-\label{CHSProperty3}
-\end{Property}
-
-\begin{Lemma}
-Assume $\mathbf{a}$, $\mathbf{b}$ $\in \mathbb{R}^{V}$, define a real RKHS $\mathcal{H}$ that satisfy $<\mathbf{a}, \mathbf{b}>_{\mathcal{H}}=\mathbf{a}^{T}\mathbf{b}$.
-For the corresponding complex RKHS $\mathbb{H}=\{f=f^{r}+\imath f^{i}, f^{r}, f^{i}\in \mathcal{H}\}$, $\mathbf{m}, \mathbf{l}\in \mathbb{C}^{V}$,
-$<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}\cdot \mathbf{l}$
-\end{Lemma}
-
-\begin{proof} 
-$\mathbf{g}$,$\mathbf{h}$ $\in \mathbb{C}^{V}$, and $\mathbf{g}=\Re{(\mathbf{g})}+\imath\Im{(\mathbf{g})}$, $\mathbf{h}=\Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}$.
-From Property \ref{CHSProperty1} and Property \ref{CHSProperty3},
-\begin{IEEEeqnarray}[\relax]{l}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(g)}+\imath\Im{(g)}, \Re{(h)}+\imath\Im{(h)}>_{\mathbb{H}}
-\label{CHSProperty4 inter1}
-\end{IEEEeqnarray}
-According to Property \ref{CHSProperty2}, (\ref{CHSProperty4 inter1}) can be rewritten as 
-\begin{equation}
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath <\Im{(\mathbf{g})}, \Re{(\mathbf{h})}+\imath\Im{(\mathbf{h})}>_{\mathbb{H}},
-\label{CHSProperty4 inter2}
-\end{equation}
-According to Property \ref{CHSProperty3}
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-\imath <\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathbb{H}}+\imath (<\Im{(\mathbf{g})}, \Re{(\mathbf{h})}>_{\mathbb{H}}-
-\imath <\Im{(\mathbf{g})}, \\ \nonumber  \Im{(\mathbf{h})}>_{\mathbb{H}})
-=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathbb{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathbb{H}}-<\Re{(\mathbf{g})},\\ \Im{(\mathbf{h})}>_{\mathbb{H}}]
-\label{CHSProperty4 inter2}
-\end{IEEEeqnarray}
-According to (\ref{CHSProperty4 inter2}), if $\mathbf{f}_{1}, \mathbf{f}_{2}\in \mathcal{H}$, we have  $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathbb{H}}=<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}$, furthermore because $<\mathbf{f}_{1}, \mathbf{f}_{2}>_{\mathcal{H}}=\mathbf{f}^{T}_{1}\mathbf{f}_{2}$, (\ref{CHSProperty4 inter2}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{g},\mathbf{h}>_{\mathbb{H}}=<\Re{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}+<\Im{(\mathbf{g})},\Im{(\mathbf{h})}>_{\mathcal{H}}+\imath [<\Im{(\mathbf{g})},\Re{(\mathbf{h})}>_{\mathcal{H}}-<\Re{(\mathbf{g})}, \Im{(\mathbf{h})}>_{\mathcal{H}}]=\\
-\Re{(\mathbf{g})}^{T}\cdot \Re{(\mathbf{h})}+\Im{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}+\imath [\Im{(\mathbf{g})}^{T}\cdot  \Re{(\mathbf{h})}-\Re{(\mathbf{g})}^{T}\cdot \Im{(\mathbf{h})}]=\mathbf{g}\cdot \mathbf{h}^{*}
-\label{CHSequation2}
-\end{IEEEeqnarray}
-
-Therefore $<\mathbf{m},\mathbf{l}^{*}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}$.
-\end{proof}
-Therefore we have $<\mathbf{h}_{i}, \mathbf{s}^{*}>_{\mathbb{H}}=\mathbf{h}_{i}\cdot \mathbf{s}$, 
-For sake of simplicity we define $\mathbf{w}=\mathbf{s}^{*}$.
-Based on the same principle in the real case presented in section \ref{Introduce epsilon SVR}, the primal optimization problem of large MIMO detection in complex RKHS $\mathbb{H}$ defined by $<\mathbf{m}, \mathbf{l}>_{\mathbb{H}}=\mathbf{m}^{T}\mathbf{l}^{*}$ can be formulated as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\min_{\mathbf{w}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i}} \quad \frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]\\
-s.t. \left\{\begin{array}{ll}
-\Re{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{r}_{i}, i=1,2,\ldots, N_{r}\\
-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{r}_{i}, i=1,2,\ldots, N_{r}\\
-\Im{(y_{i}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}\leq \epsilon+\xi^{i}_{i}, i=1,2,\ldots, N_{r}\\
-\Im{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-y_{i})}\leq \epsilon+\hat{\xi}^{i}_{i}, i=1,2,\ldots, N_{r}\\
-\xi^{r}_{i}, \hat{\xi}^{r}_{i},\xi^{i}_{i},\hat{\xi}^{i}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex objective function1}
-\end{IEEEeqnarray}
- Where $\Re{(\cdot)}$ and $\Im{(\cdot)}$ denote real and imaginary part of a complex variable and inequality constraints are set to real and imaginary part of the regression function separately.
-Let $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ denote the kernel function, $\mathbf{K}=\Re{(\mathbf{K})}+\imath\Im{(\mathbf{K})}$, where $\Re{(\mathbf{K})}$ and $\Im{(\mathbf{K})}$ denote matrices of corresponding real and imaginary parts.
-Similar to the Lagrange duality rational in section \ref{section lagrange duality}, the Lagrange function associated with (\ref{complex objective function1}) is
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L=
-\frac{1}{2}||\mathbf{w}||_{\mathbb{H}}^{2}+C\sum_{i=1}^{N_{r}}[(R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i}))]- \sum_{i=1}^{N_{r}}(\eta_{i}\xi^{r}_{i}+\hat{\eta}_{i}\hat{\xi}^{r}_{i}+\tau_{i}\xi^{i}_{i}\\\nonumber +\hat{\tau}_{i}\hat{\xi}^{i}_{i})
-+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{r}_{i})
-+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}(\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})\\
-\nonumber
-+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}(\Im{(<\mathbf{h}_{k},\mathbf{w}>_{\mathbb{H}})}-\Im{(y_{i})}-\epsilon-\hat{\xi}^{i}_{i})\\
-s.t. \left\{\begin{array}{ll}
-\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}\geq 0, i=1,2,\ldots, N_{r}\\
-\xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}^{i}_{i} \geq  0, i=1,2,\ldots, N_{r}
-\end{array}\right. 
-\label{complex lagrange duality1}
-\end{IEEEeqnarray}
-where $\eta_{i}, \hat{\eta}_{i}, \tau_{i}, \hat{\tau}_{i}, \alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}$ are Lagrange multipliers.
-In order to calculate the partial derivations of $L$ with respect to $\mathbf{w}$ which is defined in complex domain, the Wirtinger's calculus is exploited\cite{bouboulis2011extension} , Therefore we have
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-\frac{\partial L}{\partial \mathbf{w}^{*}}=\frac{1}{2}\mathbf{w}-\frac{1}{2}\sum_{i=1}^{N_{r}}\alpha_{i}\mathbf{h}_{i}+\frac{1}{2}\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\mathbf{h}_{i}+\frac{\imath}{2}(\sum_{i=1}^{N_{r}}\beta_{i}\mathbf{h}_{i}-\sum_{i=1}^{N_{r}}\hat{\beta}_{i}\mathbf{h}_{i})=0\\
-\Rightarrow \mathbf{w}=\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}-\imath\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\\
-\frac{\partial L}{\partial \xi^{r}_{i}}=CR^{'}(\xi^{r}_{i})-\eta_{i}-\alpha_{i}=0\Rightarrow \eta_{i}=CR^{'}(\xi^{r}_{i})-\alpha_{i}\\
-\frac{\partial L}{\partial \hat{\xi}^{r}_{i}}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0\Rightarrow \hat{\eta}_{i}=CR^{'}(\hat{\xi}^{r}_{i})-\hat{\alpha}_{i}\\
-\frac{\partial L}{\partial \xi^{i}_{i}}=CR^{'}(\xi^{i}_{i})-\tau_{i}-\beta_{i}=0\Rightarrow \tau_{i}=CR^{'}(\xi^{i}_{i})-\beta_{i}\\
-\frac{\partial L}{\partial \hat{\xi}^{i}_{i}}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\tau}_{i}-\hat{\beta}_{i}=0\Rightarrow \hat{\tau}_{i}=CR^{'}(\hat{\xi}^{i}_{i})-\hat{\beta}_{i}\\
-
-\end{array}\right.
-\label{complex lagrange duality2}
-\end{IEEEeqnarray}
-Based on (\ref{complex lagrange duality2}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})<\mathbf{h}_{i},\mathbf{h}_{j}>_{\mathbb{H}}\\
-\nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+i\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\\nonumber
-=\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\\ \sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}),
-\label{complex duality regression function}
-\end{IEEEeqnarray}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{i}-\hat{\alpha}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{i}-\hat{\beta}_{i})\mathbf{h}_{i}\mathbf{h}^{H}_{j}\\
-+i(\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{i}\mathbf{h}^{H}_{j}-\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{h}_{j}\mathbf{h}^{H}_{i})
-\label{complex duality regularization1}
-\end{IEEEeqnarray}
-Because $\mathbf{K}$ is Hermitian, thus $\mathbf{K}_{ij}=\mathbf{K}^{*}_{ji}$. If we have $r_{i}$, $r_{j}$ $\in \mathbb{R}$, then 
-\begin{equation}
-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ji}=-\sum_{i,j}^{L}r_{i}r_{j}\Im{(\mathbf{K})}_{ij},
-\end{equation}
-Therefore
-\begin{equation}
-\sum_{i,j}^{l}r_{i}r_{j}\Im{(\mathbf{K})}_{ij}=0,
-\label{conjugate1}
-\end{equation}
-Based on (\ref{conjugate1}), (\ref{complex duality regularization1}) can be changed to
-\begin{equation}
-||\mathbf{w}||^{2}_{\mathbb{H}}=\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}.
-\label{complex duality regularization2}
-\end{equation}
-Apply (\ref{complex lagrange duality2}), (\ref{complex duality regression function}), (\ref{conjugate1}) and (\ref{complex duality regularization2}) to (\ref{complex lagrange duality1}), we have
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L=\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-2\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij}]+\\
-\nonumber
-C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})]- \sum_{i=1}^{N_{r}}((CR^{'}(\xi^{r}_{i})-\alpha_{i})\xi^{r}_{i}+(CR^{'}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}^{r}_{i}+(CR^{'}-\beta_{i})\xi^{i}_{i}\\\nonumber +(CR^{'}(\hat{\xi}_{i})-\hat{\beta}_{i})\hat{\xi}^{i}_{i})+\sum_{i=1}^{N_{r}}\alpha_{i}(\Re{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\epsilon-\xi^{r}_{i})
-+\sum_{i=1}^{N_{r}}\hat{\alpha}_{i}\\ \nonumber
-((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Im{(\mathbf{K})}_{ij})-\Re{(y_{i})}-\epsilon-\hat{\xi}^{r}_{i})
-+\sum_{i=1}^{N_{r}}\beta_{i}(\Im{(y_{i})}-(\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\\ \nonumber
-\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\epsilon-\xi^{i}_{i})+\sum_{i=1}^{N_{r}}\hat{\beta}_{i}((\sum_{j=1}^{N_{r}}(\alpha_{j}-\hat{\alpha}_{j})\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij})-\Im{(y_{i})}-\\
-\epsilon-\hat{\xi}^{i}_{i})
-\label{complex lagrange duality inter1}
-\end{IEEEeqnarray}
-
-Then simplify (\ref{complex lagrange duality inter1}), we obtain
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-L\equiv\theta=-\frac{1}{2}[\sum_{i,j=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}+\sum_{i,j=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}]+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})-\xi_{i}^{r}R^{'}(\xi^{r}_{i})\\\nonumber
-+R(\hat{\xi}^{r}_{i})-\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})-\xi_{i}R^{'}(\xi_{i}^{i})+R(\hat{\xi}^{i}_{i})-\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]+\sum_{i=1}^{N_{r}}[\Re{(y_{i})}(\alpha_{i}-\hat{\alpha}_{i})+\Im{(y_{i})}(\beta_{i}-\hat{\beta}_{i})]-\\
-\epsilon\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta_{i}+\hat{\beta}_{i})
-\label{complex lagrange duality inter2}
-\end{IEEEeqnarray}
-define $\tilde{R}(u)=R(u)-uR^{'}(u)$. Similar to (\ref{dual optimization function2}), The dual optimization problem of a complex MIMO system is given by
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}, \beta_{i}, \hat{\beta}_{i}}\quad \theta=-\frac{1}{2}[\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\mathbf{K}^{r}_{ij}+\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\mathbf{K}^{r}_{ij}]\\
-\nonumber
--\sum_{i}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i}+\beta+\hat{\beta}_{i})\epsilon+[\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})]\\
-\nonumber
-+C\sum_{i}^{N_{r}}(\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i}))\\ 
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{final complex lagrange duality}
-\end{IEEEeqnarray}
-Notice in (\ref{final complex lagrange duality}), there is no correlation term between $\alpha_{i}, \hat{\alpha}_{i}$ and $\beta_{i}, \hat{\beta}_{i}$, therefore, (\ref{final complex lagrange duality}) can be divided into two independent regression tasks, which are given by
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\alpha_{i}, \hat{\alpha}_{i}} \quad \theta^{r}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})(\alpha_{j}-\hat{\alpha}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\alpha_{i}+\hat{\alpha}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\alpha_{i}-\hat{\alpha}_{i})Re(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{r}_{i})\\
-\nonumber
-+\tilde{R}(\hat{\xi}^{r}_{i}))\\
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, L\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{complex duality real part}
-\end{IEEEeqnarray}
-and 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\beta_{i}, \hat{\beta}_{i}} \quad \theta^{i}= -\frac{1}{2}\sum_{i,j}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})(\beta_{j}-\hat{\beta}_{j})\Re{(\mathbf{K})}_{ij}-\sum_{i=1}^{N_{r}}(\beta_{i}+\hat{\beta}_{i})\epsilon+\sum_{i=1}^{N_{r}}(\beta_{i}-\hat{\beta}_{i})Im(y_{i})+C\sum_{i=1}^{N_{r}}(\tilde{R}(\xi^{i}_{i})\\
-\nonumber
-+\tilde{R}(\hat{\xi}^{i}_{i}))\\
-\left\{\begin{array}{ll}
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, L\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, L\\
-\end{array}\right.
-\label{complex duality imaginary part}
-\end{IEEEeqnarray}
-Let $\mathbf{a}=[\alpha_{1}, \alpha_{2},\ldots, \alpha_{N_{r}}]^{T}$, $\mathbf{\hat{a}}=[\hat{\alpha}_{1}, \hat{\alpha}_{2},\ldots, \hat{\alpha}_{N_{r}}]^{T}$, $\mathbf{b}=[\beta_{1}, \beta_{2},\ldots, \beta_{N_{r}}]^{T}$,$\mathbf{\hat{b}}=[\hat{\beta}_{1}, \hat{\beta}_{2},\ldots, \hat{\beta}_{N_{r}}]^{T}$, $\mathbf{R}^{r}=[\tilde{R}(\xi^{r}_{1})+\tilde{R}(\hat{\xi}^{r}_{1}), \tilde{R}(\xi^{r}_{2})+\tilde{R}(\hat{\xi}^{r}_{2}), \ldots, \tilde{R}(\xi^{r}_{N_{r}})+\tilde{R}(\hat{\xi}^{r}_{N_{r}})]^{T}$, $\mathbf{R}^{i}=[\tilde{R}(\xi^{i}_{1})+\tilde{R}(\hat{\xi}^{i}_{1}), \tilde{R}(\xi^{i}_{2})+\tilde{R}(\hat{\xi}^{i}_{2}), \ldots, \tilde{R}(\xi^{i}_{N_{r}})+\tilde{R}(\hat{\xi}^{i}_{N_{r}})]^{T}$, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$.
-The alternate form can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a},\mathbf{\hat{\mathbf{a}}}} \quad \theta^{r}=-\frac{1}{2}(\mathbf{a}-\mathbf{\hat{a}})^{T}\Re{(\mathbf{K})}(\mathbf{a}-\mathbf{\hat{a}})+\Re{(\mathbf{y})}^{T}(\mathbf{a}-\mathbf{\hat{a}})-\epsilon(\mathbf{e}^{T}(\mathbf{a}+\mathbf{\hat{a}}))+C(\mathbf{e}^{T}\mathbf{R}^{r})\\
-\left\{\begin{array}{ll}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex duality real part vectorizes}
-\end{IEEEeqnarray}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{b}, \mathbf{\hat{b}}} \quad \theta^{i}=-\frac{1}{2}(\mathbf{b}-\mathbf{\hat{b}})^{T}\Re{(\mathbf{K})}(\mathbf{b}-\mathbf{\hat{b}})+\Im{(\mathbf{y})}^{T}(\mathbf{b}-\mathbf{\hat{b}})-\epsilon(\mathbf{e}^{T}(\mathbf{b}+\mathbf{\hat{b}}))+C(\mathbf{e}^{T}\mathbf{R}^{i})\\
-\left\{\begin{array}{ll}
-0\leq \beta_{i}(\hat{\beta}_{i})\leq C\tilde{R}(\xi_{i}^{i})(\tilde{R}(\hat{\xi}_{i}^{i})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{i}(\hat{\xi}_{i}^{i})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{complex duality imaginary part vectorized}
-\end{IEEEeqnarray}
-
-Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), where only the real part of the kernel matrix is required for each channel.
-This can provide computational advantages for solving the dual optimization problems.
-\section{Work Set Selection and Solver}\label{WSS}
- As we can see, a quadratic optimization problem is formulated in (\ref{final complex lagrange duality}).
-The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with a large data set.
-
-Decomposition methods are a set of efficient algorithms that can help to ease this difficulty.
-Decomposition methods work iteratively, and are based on choosing a subset of optimization variables $S$ (named work set) to be updated in each iteration step, while keeping the rest variables $N$ fixed.
-Sequential Minimal Optimization (SMO) is an extreme case of decomposition method, where the work set size is 2, and an analytic quadratic programming (QP) step instead of numerical QP step can be performed in each iteration.
-
-Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) have the same structure, in this section we discuss the real part only.
-By dividing the variables into work set $S$ and fixed set $N$.
-Therefore, the vector $\mathbf{a}$ in (\ref{complex duality real part vectorizes}) can be divided into two sub vectors $[\mathbf{a}_{S}, \mathbf{a}_{N}]$.
-thereafter $\mathbf{a}_{S}$ denotes a vector that consists of the components of $\mathbf{a}$ that belongs to set $S$, the same modifications are applied to $\mathbf{\hat{a}}$ and $\mathbf{y}$.
-Thus (\ref{complex duality real part vectorizes}) can be rewritten as:
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}, \mathbf{a}_{N}, \hat{\mathbf{a}}_{N}} \theta= -\frac{1}{2}[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
-\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]+[\Re{(\mathbf{y}_{S})}^{T}, \Re{(\mathbf{y}_{N})}^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]-\\\nonumber\epsilon[\mathbf{e}^{T}_{S}, \mathbf{e}^{T}_{N}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S})\\
-(\mathbf{a}_{N}+\hat{\mathbf{a}}_{N})
-\end{IEEEeqnarraybox*}\right]+C(\mathbf{e}^{T}, \mathbf{R}^{r})
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{real part decomposition inter1}
-\end{IEEEeqnarray}
-
-Where $\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
-\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
-\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of the components in $\Re(\mathbf{K})$ that belong to both of the rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\mathbf{K}$ is a Hermitian matrix, thus $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}, \mathbf{\hat{a}}}\quad \theta^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})+2(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]
-+\Re{(\mathbf{y}_{S}^{T})}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\
-\nonumber
-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S}))
--\frac{1}{2}(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NN}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})+\Re{(\mathbf{y}_{N}^{T})}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{N}+\mathbf{\hat{a}}_{N}))\\\nonumber+C(\mathbf{e}^{T}(\mathbf{R}^{r}),
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
-\end{array}\right.
-\label{real part decomposition}
-\end{IEEEeqnarray}
-In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is considered i.e 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\mathbf{a}_{S}, \mathbf{\hat{a}}_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]+[Re(\mathbf{y}_{S}^{T})-(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\mathbf{K}_{NS}^{r}
-](\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\\nonumber\epsilon<\mathbf{e}^{T}, (\mathbf{a}_{S}+\mathbf{\hat{a}}_{S})>,
-\\
-\left\{\begin{array}{ll}
-0\leq [\mathbf{a}_{S}]_{i}([\hat{\mathbf{a}}_{S}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i\in S\\
-\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i\in S\\
-\end{array}\right.
-\label{subset optimization}
-\end{IEEEeqnarray}
-A proper work set selection strategy is required so that speed and performance requirement can be guaranteed.
-One idea is to perform update to optimization variables that violate the KKT complementary conditions, which, based on (\ref{complete KKT complimentary})
-\begin{IEEEeqnarray}[\relax]{l}
-\left\{\begin{array}{ll}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
-\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, L\\
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, L\\
-\xi_{i}\hat{\xi}_{i}=0, \alpha_{i}\hat{\alpha}_{i}=0, i=1,2,\ldots, L
-\end{array}\right.
-\label{complementary KKT condition1}
-\end{IEEEeqnarray}
-According to Osuna's theorem\cite{osuna1997improved}, the final convergence can be guaranteed.
-In SMO algorithm, heuristic methods are used to find a work set of size two in order to accelerate the decomposition process\cite{platt1999fast}.
-The heuristic method first searches among the non-bound variables (that is $0<\alpha_{i}<C\tilde{R}(\xi^{r}_{i})$ and $0<\hat{\alpha}_{i}<C\tilde{R}(\hat{\xi}_{i})$), which are more likely to violate the complementary KKT conditions, Then searching the whole dual variable set.
-The second dual variable that can maximize optimization step size is chosen.
-An approximate step size is used as evaluator for sake of reducing computational cost.
-
-Another idea for work set selection is to choose the optimization variables whose update can provide the maximum improvement to the sub dual objective functions.
-The improvement of the sub dual objective function is
-\begin{equation}
-\bigtriangledown \theta^{r}_{S}=\theta^{r}_{S}((\mathbf{a}_{S}+\Delta_{S}), (\hat{\mathbf{a}}_{S}+\hat{\Delta}_{S}))-\theta^{r}_{S}(\mathbf{a}_{S}, \hat{\mathbf{a}}_{S}),
-\label{maximum gain work set selection}
-\end{equation} 
-where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\hat{\Delta}_{S}=\hat{\mathbf{a}}_{S}^{new}-\hat{\mathbf{a}}_{S}$, $\mathbf{a}^{new}_{S}$ and $\hat{\mathbf{a}}^{new}_{S}$ are the updates of $\mathbf{a}_{S}$ and $\hat{\mathbf{a}}_{S}$.
-$\bigtriangledown \theta_{S}^{r}$ in (\ref{maximum gain work set selection}),  based on (\ref{subset optimization}), can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\\\nonumber\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+\{\Re{(\mathbf{y}^{T}_{S})}-[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\\
-\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}]\}(\Delta_{S}-\hat{\Delta}_{S})
--\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S}),
-\label{gain work set selection1}
-\end{IEEEeqnarray} 
-where we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}=[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}, (\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}]\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
-\Re{(\mathbf{K})}_{SS}\\
-\Re{(\mathbf{K})}_{NS}
-\end{IEEEeqnarraybox*}\right]=\\
-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S},
-\label{modification of gain work set selection}
-\end{IEEEeqnarray}
-where $\Re{(\mathbf{K})}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns corresponding to the work set $S$.
-Therefore, (\ref{gain work set selection1}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}]
-(\Delta_{S}-\hat{\Delta}_{S})
--\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta_{S}+\hat{\Delta}_{S}),
-\label{gain of work set selection1 inter}
-\end{IEEEeqnarray}
-define intermediate variable vector $\Phi^{r}, \Phi^{i}\in \mathbb{R}^{N_{r}}$, $\Phi^{r}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Phi^{i}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$.
-Let $\Phi_{S}$ denote the vector that consists of the components in $\Phi$ that corresponding to $S$.
-Thus (\ref{gain of work set selection1 inter}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+(\Phi^{r}_{S})^{T}(\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}\\
-(\Delta_{S}+\hat{\Delta}_{S})
-\label{gain work set selection2}
-\end{IEEEeqnarray} 
-Because the offset term is omitted in the large MIMO regression model, therefore different from SMO type algorithms, there is no linear equality constraint, which is inducted by offset $b$, as shown in (\ref{partial4}).
-Therefore the size of work set can be less than two.
-However, more efficient work set selection strategies based on maximal sub dual objective gain selection, is proposed in \cite{steinwart2011training}.
-A work set of size two is updated in each iteration.
-The computational cost is reduced while maintaining the comparable performance with the model with offset term.
-In the CSVR large MIMO detector, the work set selection strategy in \cite{steinwart2011training} is exploited.
-Basically, in each iteration this strategy uses the combined single variable searchings, whose searching time is $O(n)$, where $n$ is the number of data samples, to determine a work set of size two.
-On the one hand, this strategy can find a work set of size two, whose update approximately maximize the gain of the dual sub objective function.
-On the other hand, the brute-force searching for the work size of two, whose update can maximize the gain of the sub dual objective function, requires $O(n^{2})$ searching time.
-The former strategy requires as few iterations as the latter one, since in each iteration, the latter strategy is more computationally expensive, the former one can enjoy significantly faster running speed.
-\subsection{Single Direction (1-D) Solver}\label{single direction solver}
-Recall the KKT complementary conditions 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{KKT complementary1}
-(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary2}
-(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary3}
-\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary4}
-\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, N_{r}\\
-\label{KKT complementary5}
-0\leq \alpha_{i}(\hat{\alpha}_{i})\leq R^{'}(\xi^{r}_{i})(R^{'}(\hat{\xi}_{i})), i=1,2,\ldots, N_{r} 
-\end{IEEEeqnarray}
-Recall the discussions of slack variables by (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}) in section \ref{section lagrange duality}.
-we have $\xi^{r}_{i}\hat{\xi}^{r}_{i}=0$.
-similar to the definitions in (\ref{definition of slack variable3}), we have
-\begin{equation}
-\xi^{r}_{i} or \hat{\xi}_{i}^{r}=|\Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}|_{\epsilon},
-\label{definition of complex slack variables}
-\end{equation} 
- therefore in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})$ and  $(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})$ can be non zero, therefore in order to satisfy equalities (\ref{KKT complementary3}) and (\ref{KKT complementary4}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.
-
- Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is changed to the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.
-
-  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of the sub dual objective function is chosen as the work set in each iteration.
-Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]^{T}$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]^{T}$.
-Substitute $\mathbf{a}, \hat{\mathbf{a}}$ with $\Lambda$ and using $\Sigma$.
-Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2}) can be rewritten as
-  \begin{equation}
-\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y}_{S}^{T})}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
-]\Lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\Lambda_{S}|>,
-\label{subset optimization lambda}
-\end{equation}
-
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
-\label{gain work set selection lambda}
-\end{IEEEeqnarray} 
-In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
-\begin{IEEEeqnarray}[\relax]{l}
- \max_{\tilde{\lambda}^{new}_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\tilde{\lambda}_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
-+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\tilde{\lambda}_{m}^{new}-\epsilon(|\tilde{\lambda}^{new}_{m}|),
- \label{optimization function 1-D}
- \end{IEEEeqnarray}
- where $\tilde{\lambda}^{new}_{m}$ is the update of $\lambda_{m}$.
- Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Phi^{r}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$ in the imaginary channel, $\Phi_{i}^{i}=\Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$.
-Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
-Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))
-\label{partial optimization function 1-D lambda}
-\end{IEEEeqnarray} 
-where $\Re(y_{m})-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re(\mathbf{K})_{mj}=\Re(y_{m})-\sum_{j=1}^{N_{r}}\lambda_{j}\Re(\mathbf{K}_{mj})=\Phi^{r}_{m}+\lambda_{m}\Re(\mathbf{K}_{mm})$
-and $\lambda_{m}$ denotes the $m$th optimization variable before update. Therefore (\ref{partial optimization function 1-D lambda}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\frac{\partial \theta^{r}_{m}}{\partial \tilde{\lambda}_{m}^{new}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
-\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Phi^{r}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
-\end{IEEEeqnarray}
- The update of $\tilde{\lambda}^{new}_{m}$ is completed by clipping based on (\ref{KKT complementary5})
-\begin{IEEEeqnarray}[\relax]{l}
-\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
-\label{clipped new dual variable}
-\end{IEEEeqnarray}
-
-where $[ ]_{a}^{b}$ denotes clipping function 
-\begin{IEEEeqnarray}[\relax]{l}
-[x]_{a}^{b}=\left\{\begin{array}{ll}
-a \quad if\quad  x\leq a\\
-x \quad if\quad a<x<b\\
-b \quad if\quad x\geq b\\
-\end{array}\right.
-\label{clipping function}
-\end{IEEEeqnarray}
-based on (\ref{gain work set selection lambda}), The maximal gain of the sub dual objective function with respect to the $m$th optimization variable is 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta_{m}^{r}=\theta_{m}^{r}(\lambda_{m}+\sigma_{m})-\theta_{m}^{r}(\lambda_{m})\\
-\nonumber
-=-\frac{1}{2}\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}\sigma_{m}-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)\\
-=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|),
-\label{gain of 1-D objective function}
-\end{IEEEeqnarray}
-In 1-D searching procedure, the optimization variable whose update can achieve the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, based on the this principle
-\begin{equation}
-k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r}.
-\label{1-D direction}
-\end{equation}
-Notice in (\ref{partial optimization function 1-D lambda}), $sgn(\tilde{\lambda}^{new}_{m})$ is unknown before $\lambda_{m}$ is updated, therefore two conditions $sgn(\tilde{\lambda}^{new}_{m})=1$ and $sgn(\tilde{\lambda}^{new}_{m})=-1$ are considered.
-The final decision of $sgn(\tilde{\lambda}_{m}^{new})$ is made by comparing the corresponding gains of the sub dual objective functions in (\ref{gain of 1-D objective function}).
-\subsection{Double Direction (2-D) Solver}\label{double direction solver}
-Although the omission of offset in the CSVR-MIMO detector makes 1-D solver possible, however, recent work in \cite{steinwart2011training} shows training SVM without offset by 2-D solver with special work set selection strategies has more rapid training speed while the comparable performance is retained.
-The optimal 2-D solver uses the same principle as 1-D solver, $|S|=2$, assume the work set consists of the $m$th and $n$th optimization variables, that are $\Lambda_{S}=[\lambda_{m}, \lambda_{n}]$.
-Based on (\ref{gain work set selection lambda}), the sub dual objective function can be written as
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\max_{\lambda_{m}, 
-\lambda_{n}}\quad \theta^{r}_{m,n}=-\frac{1}{2}[(\tilde{\lambda}^{new}_{m})^{2}\Re{(\mathbf{K})}_{mm}+(\tilde{\lambda}^{new}_{n})^{2}\Re{(\mathbf{K})}_{nn}+2\tilde{\lambda}^{new}_{m}\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}]-\\
-\nonumber
-\tilde{\lambda}^{new}_{m}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\tilde{\lambda}^{new}_{n}\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{m})}\tilde{\lambda}^{new}_{1}+\Re{(\mathbf{y}_{n})}\tilde{\lambda}^{2}_{n}\\
--\epsilon(|\lambda^{new}_{m}|+|\tilde{\lambda}_{n}^{new}|), 
-\label{2-D solver}
-\end{IEEEeqnarray}
-Based on (\ref{2-D solver}), the partial derivatives of $\theta^{r}_{m,n}$ with respect to $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}_{n}^{new}$ are 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\label{lambda1 partial}
-\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}+\Re{(\mathbf{y}_{m})}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=\\
--\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{m}+\lambda_{m}\Re{\mathbf{K}}_{mm}+\lambda_{n}\Re{(\mathbf{K})}_{mn}-\epsilon sgn(\tilde{\lambda}^{new}_{m})=0\\
-\nonumber
-\label{lambda2 partial}
-\frac{\partial \theta^{r}_{m,n}}{\partial \tilde{\lambda}^{new}_{n}}=-\tilde{\lambda}^{new}_{n}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}-\sum_{j\neq m, n}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{nj}+\Re{(\mathbf{y}_{n})}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=\\
--\tilde{\lambda}_{n}^{new}\Re{(\mathbf{K})}_{nn}-\tilde{\lambda}^{new}_{m}\Re{(\mathbf{K})}_{mn}+\Phi^{r}_{n}+\lambda_{m}\Re{(\mathbf{K})}_{mn}+\lambda_{n}\Re{(\mathbf{K})}_{nn}-\epsilon sgn(\tilde{\lambda}^{new}_{n})=0\\
-\nonumber
-\label{partial derivative sample1}
-\end{IEEEeqnarray}
-where $\frac{\partial |x|}{\partial x}=sgn(x)$ denotes the sign of $x$. Based on (\ref{lambda1 partial}) and (\ref{lambda2 partial}) we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{post partial lambda1}
-(\tilde{\lambda}^{new}_{m}-\lambda_{n})\Re{(\mathbf{K})}_{mm}=\Phi^{r}_{m}-\epsilon sgn(\tilde{\lambda}^{new}_{m})-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{mn}\\
-\label{post partial lambda2}
-(\tilde{\lambda}^{new}_{n}-\lambda_{n})\Re{(\mathbf{K})}_{nn}=\Phi^{r}_{n}-\epsilon sgn(\tilde{\lambda}^{new}_{n})-(\tilde{\lambda}^{new}_{m}-\lambda_{m})\Re{(\mathbf{K})}_{mn}\\
-\nonumber
-\end{IEEEeqnarray}
-hence based on (\ref{post partial lambda1}) and (\ref{post partial lambda2}), the update formulas of $\tilde{\lambda}^{new}_{m}$ and $\tilde{\lambda}^{new}_{n}$ are given by
-\begin{equation}
-\tilde{\lambda}^{new}_{m}=\lambda_{m}+\frac{\Phi^{r}_{m}\Re{(\mathbf{K})}_{nn}-\Phi^{r}_{n}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{nn}-sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
-\label{update lambda1}
-\end{equation}
-
-\begin{equation}
-\tilde{\lambda}^{new}_{n}=\lambda_{n}+\frac{\Phi^{r}_{n}\Re{(\mathbf{K})}_{mm}-\Phi^{r}_{m}\Re{(\mathbf{K})}_{mn}-\epsilon[sgn(\tilde{\lambda}^{new}_{n})\Re{(\mathbf{K})}_{mm}-sgn(\tilde{\lambda}^{new}_{m})\Re{(\mathbf{K})}_{mn}]}{\Re{(\mathbf{K})}_{mm}\Re{(\mathbf{K})}_{nn}-(\Re{(\mathbf{K})}_{mn})^{2}}
-\label{update lambda2}
-\end{equation} 
-Then the updated optimization variables are clipped by constraint based on (\ref{KKT complementary5})
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\lambda_{i}^{new}=[\tilde{\lambda}_{i}^{new}]^{CR^{'}(\xi_{i})}_{-CR^{'}(\xi_{i})},\\
-i=m,n
-\label{cipped optimization variable}
-\end{IEEEeqnarray}
-Based on (\ref{gain work set selection2}),  the gain of the sub dual objective function can be written as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=-\frac{1}{2}[\sigma_{m}^{2}\Re{(\mathbf{K})}_{mm}+\sigma_{n}^{2}\Re{(\mathbf{K})}_{nn}+2\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn}]+\Phi^{r}_{m}\sigma_{m}+\Phi^{r}_{n}\sigma_{n}\\
--\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|+|\lambda^{new}_{n}|-|\lambda_{n}|),
-\label{gain of 2-D objective function1}
-\end{IEEEeqnarray}
-assume the $i$th and $j$th optimization variables are chosen, the optimization variables in 2-D solver have the same update rule as that of 1-D solver, that is 
-\begin{equation}
-[i,j]=\arg\max_{m,n=1,2,\ldots, N_{r}}\bigtriangledown \theta_{m,n}^{r}.
-\label{dual optimization variables}
-\end{equation}
-
-Similar to single direction solver, notice in (\ref{update lambda1}) and (\ref{update lambda2}), $sgn(\tilde{\lambda}^{new}_{m})$ and $sgn(\tilde{\lambda}^{new}_{n})$ are unknown before $\lambda_{m}$ and $\lambda_{n}$ are updated, therefore four conditions are considered
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=1, sgn(\tilde{\lambda}^{new}_{n})=-1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=1\\
-\nonumber
-sgn(\tilde{\lambda}^{new}_{m})=-1, sgn(\tilde{\lambda}^{new}_{n})=-1
-\label{four conditions of sign}
-\end{IEEEeqnarray} 
-The final decisions of $sgn(\tilde{\lambda}_{m}^{new})$ and $sgn(\tilde{\lambda}_{n}^{new})$ are made by comparing the corresponding possible gains of the sub objective functions in (\ref{gain of 2-D objective function1}).
-
-Modify (\ref{gain of 2-D objective function1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\bigtriangledown \theta^{r}_{mn}=\sigma_{m}[-\frac{1}{2}\sigma_{m}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}]-\epsilon(|\lambda^{new}_{m}|-|\lambda_{m}|)+\sigma_{n}[-\frac{1}{2}\sigma_{n}\Re{(\mathbf{K})}_{nn}+\Phi^{r}_{n}]-\epsilon(|\lambda^{new}_{n}|-|\lambda_{n}|)\\
--\sigma_{m}\sigma_{n}\Re{(\mathbf{K})}_{mn},
-\end{IEEEeqnarray}
-then recall the gain of the sub dual objective function of 1-D solver in (\ref{gain of 1-D objective function}), we obtain
- \begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta^{r}_{ij}=\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}-\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij},
-\label{gain of 2-D objective function2}
-\end{IEEEeqnarray}
-where $\bigtriangledown \theta^{r}_{i}$, $\bigtriangledown \theta^{r}_{j}$ denote gains of the sub dual objective functions of 1-D solver with $i$th and $j$th optimization variables are updated. 
-\subsection{Approximation of Optimal Double Direction Solver based on Single Direction Solver}\label{approximate 2D solver}
-From (\ref{gain of 2-D objective function1}), we can observe that the gain of the sub dual objective function of 2-D solver is a summation of the gains of the sub dual objective functions of two independent 1-D solver and a correlation term $\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}$.
-
-The optimal 2-D work set $[i,j]$ can be determined by brute-force searching manner, which requires $O(n^{2})$ searching times.
-Based on (\ref{gain of 2-D objective function1}), we can approximate optimal 2-D searching strategy by the combinations of optimal 1-D searching approach, we will prove in the large MIMO systems, when $N_{t}$ is sufficient large, this approximation is very effective.
-Here we propose two types of combined 1-D searching strategy:
-\subsubsection{ One-shot 1-D combined Searching}
-do one round 1-D searching and calculate all the 1-D gains based on (\ref{gain of 1-D objective function}), then choose the two optimization variables indexed by $i$ and $j$, whose update can achieve the first and the second largest gain of the sub dual objective functions.
-\subsubsection{ Sequential 1-D combined Searching}
-do two rounds 1-D searchings, in the first round find optimization variable indexed by $i$ whose update can achieve the maximal 1-D gain of the sub dual objective functions based on (\ref{gain of 1-D objective function}), then update the $i$th optimization variable.
-In the second round, find $j$th optimization variable whose update can achieve the maximal 1-D gain of the sub dual objective functions.
-
- The effectiveness of 1-D approximation strategies are majorly determined by the ratio $\frac{\sigma_{i}\sigma_{j}\Re{(\mathbf{K})}_{ij}}{\bigtriangledown \theta^{r}_{i}+\bigtriangledown \theta^{r}_{j}}$.
-Hence we provide theoretical analyses based on the view of channel hardening phenomenon.
-It can be proved that in the large MIMO systems, the correlation term $\sigma_{i}\sigma_{j}\Re(\mathbf{K}_{ij})$is ignorable comparing to 1-D gains of the sub objective function.
-Prior to the theoretical analyse, we first investigate some mathematical properties of channel hardening (to be completed).
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_em.eps}
-%\caption{Empirical Estimation $E[\ln(\phi_{om})]_{em}$}
-%\label{figure1}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.7\textwidth, height=5cm]{logE_om_t.eps}
-%\caption{Theoretical $E[\ln(\phi_{om})]_{t}$}
-%\label{figure2}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[scale=0.6]{NtE.eps}
-%\caption{Relation between $N_{t}$ and $E[\ln(\phi_{om})]_{t}$}
-%\label{figure3}
-%\end{figure}
-
-\section{Stopping Criteria}\label{stopping criteria}
-As discussed in section\ref{section lagrange duality}, in dual objective function, the complementary KKT conditions are the measurement of the proximity of current solution to the optimal solution. 
-The feasibility gap, which is a effective stopping criteria used in SVR and SVM, can implicitly monitor whether the KKT complementary conditions are satisfied.
-The feasibility gap measures the gap between the values of primal objective function and dual objective function.
-To elaborate a little further, recall the saddle point conditions in section\ref{section lagrange duality}
- \begin{equation}
- L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})
- \label{saddle point conditions}
- \end{equation}
-Where $(\bar{\mathbf{w}}, \bar{\mathbf{a}})$ are the solution to primal objective function, the KKT complementary conditions are satisfied, that is 
-\begin{equation}
-\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=0,
-\label{complementary KKT condition revisited}
-\end{equation}
-we have 
-\begin{equation}
-L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=f(\bar{\mathbf{w}})+\sum_{i=1}^{N_{r}}\bar{\alpha}_{i}c_{i}(\bar{\mathbf{w}})=f(\bar{\mathbf{w}})
-\end{equation} 
-Let $(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$ denote the variable pair that satisfies the first and second KKT conditions in (\ref{original KKT condition1} ) and (\ref{original KKT condition2})
-
-\begin{IEEEeqnarray}[\relax]{l}
-\label{original KKT condition revisited1}
-\partial_{\mathbf{w}}L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=\partial_{\mathbf{w}}f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{a}_{i}\partial_{\mathbf{w}}c_{i}(\tilde{\mathbf{w}})=0,\\
-\label{original KKT condition revisited2}
-c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots L
-\end{IEEEeqnarray}
-based on (\ref{original KKT condition revisited1}), we have 
-\begin{IEEEeqnarray}[\relax]{l}
-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq f(\tilde{\mathbf{w}}),
-\end{IEEEeqnarray} 
-based on Theorem 6.27\cite{scholkopf2002learning}, the following equalities hold
-\begin{IEEEeqnarray}[\relax]{l}
-f(\tilde{\mathbf{w}})\geq f(\bar{\mathbf{w}})=L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=f(\tilde{\mathbf{w}})+\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})
-\label{inequality gap}
-\end{IEEEeqnarray}
-Therefore the feasibility gap is defined by the gap between the primal objective function $f(\tilde{\mathbf{w}})$ and the dual objective function $L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})$   
-\begin{equation}
-f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\geq 0
-\label{original feasibility gap}
-\end{equation}
-If the feasibility gap is vanished, based on (\ref{inequality gap}), we have $f(\bar{\mathbf{w}})=f(\tilde{\mathbf{w}})$, thus $\tilde{\mathbf{w}}=\bar{\mathbf{w}}$, $\tilde{\mathbf{a}}=\bar{\mathbf{a}}$.
-Furthermore, because $f(\tilde{\mathbf{w}})-L(\tilde{\mathbf{w}}, \tilde{\mathbf{a}})=-\sum_{i=1}^{L}\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})$, the vanish of feasibility gap indicates $\sum_{i=1}^{L}\tilde{\mathbf{a}}c_{i}(\tilde{\mathbf{w}})=0$.
-Because $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})\leq 0, i=1,2,\ldots, L$, we have $\tilde{\alpha}_{i}c_{i}(\tilde{\mathbf{w}})=0, i=1,2,\ldots, L$, the KKT complementary conditions are satisfied.
-
-In CSVR detector for the large MIMO systems, the primal objective function is
-\begin{equation}
-f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal inter}
-\end{equation}
-where $\tilde{\mathbf{w}}$ satisfies the KKT  conditions in (\ref{original KKT condition revisited1}) and (\ref{original KKT condition revisited2}).
-Define $\lambda^{r}=\alpha-\hat{\alpha}$, $|\lambda^{r}|=\alpha+\hat{\alpha}$ and $\lambda^{i}=\beta-\hat{\beta}$, $|\lambda^{i}|=\beta+\hat{\beta}$, $\Lambda^{r}=[\lambda^{r}_{1}, \lambda^{r}_{2}, \ldots, \lambda^{r}_{L}]^{T}$ and $\Lambda^{i}=[\lambda^{i}_{1}, \lambda_{2}^{i}, \ldots, \lambda^{i}_{L}]^{T}$,
-(\ref{complex duality regularization1}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-||\tilde{\mathbf{w}}||^{2}_{\mathbb{H}}=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-2<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>,
-\label{simple regularization}
-\end{IEEEeqnarray}
-Therefore we obtain  
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})=\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>+C\sum_{i=1}^{N_{r}}[R(\xi^{r}_{i})+\\R(\hat{\xi}^{r}_{i})+R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})],
-\label{simple primal}
-\end{IEEEeqnarray}
-Based on (\ref{final complex lagrange duality}), the dual objective function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-\theta(\Lambda^{r}, \Lambda^{i})=-\frac{1}{2}<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>-\frac{1}{2}<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>+<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>\\
--\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\tilde{R}(\xi^{r}_{i})+\tilde{R}(\hat{\xi}^{r}_{i})+\tilde{R}(\xi^{i}_{i})+\tilde{R}(\hat{\xi}^{i}_{i})],
-\label{simple dual function}
-\end{IEEEeqnarray}
-
-Based on (\ref{simple primal}) and (\ref{simple dual function}), the feasibility gap is obtained 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\lambda^{r}, \lambda^{i})=f(\tilde{\mathbf{w}}, \xi^{r}_{i}, \hat{\xi}^{r}_{i}, \xi^{i}_{i}, \hat{\xi}_{i}^{i})-\theta(\Lambda^{r},\Lambda^{i})=<(\Lambda^{r})^{T}, \Re{(\mathbf{K})}\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re{(\mathbf{K})}\Lambda^{i}>-<\Re{(\mathbf{y}^{T})}, \Lambda^{r}>\\\nonumber
--<\Im{(\mathbf{y})}^{T}, \Lambda^{i}>+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[\xi^{r}_{i}R^{'}(\xi^{r}_{i})+\hat{\xi}^{r}_{i}R^{'}(\hat{\xi}^{r}_{i})+\xi^{i}_{i}R^{'}(\xi^{i}_{i})+\hat{\xi}^{i}_{i}R^{'}(\hat{\xi}^{i}_{i})]-\\<\Lambda^{r}, \Im{(\mathbf{K})}\Lambda^{i}>.
-\label{simple duality gap}
-\end{IEEEeqnarray}
-As we explained in section \ref{cost function}, the choice of risk function is determined by distribution of noise, as to Gaussian noise, the risk function is 
-\begin{equation}
-R(u)=\frac{1}{2}u^{2},
-\label{risk function1}
-\end{equation} 
-hence 
-\begin{equation}
-\tilde{R}(u)=R(u)-u R{'}(u)=-\frac{1}{2}u^{2},
-\label{risk function2}
-\end{equation}
-In $\epsilon$-SVR, the objective to exploit slack variables is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by the noise.
-Therefore in $\epsilon$-SVR, $\xi^{r}_{i}$ and $\hat{\xi}^{r}$ are defined as  
-\begin{IEEEeqnarray}[\relax]{l}
-\xi^{r}_{i}=\max(0, \Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\epsilon)\\
-\hat{\xi}^{r}_{i}=\max(0, \Re{(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})}-\Re{(\mathbf{y}_{i})}-\epsilon)
-\label{outlier2}
-\end{IEEEeqnarray} 
-Because the distance between the estimations $\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}$ and the observations $\Re{(\mathbf{y}_{i})}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi^{r}_{i}$ and $\hat{\xi}^{r}_{i}$ can be non zero that is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$.
-Therefore the risk function can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{simple risk function1}
-R(\xi_{i}^{r})+R(\hat{\xi}_{i}^{r})=\frac{1}{2}|\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|_{\epsilon}^{2}\\\label{simple risk function2}
-R(\xi_{i}^{i})+R(\hat{\xi}_{i}^{i})=\frac{1}{2}|\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-where $|\cdot|_{\epsilon}$ denotes $\epsilon$ insensitive function as mentioned in section \ref{cost function}. Recall (\ref{complex duality regression function}),
-\begin{IEEEeqnarray}[\relax]{l}
-<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}}
-=\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Re{(\mathbf{K})}_{ij}-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im{(\mathbf{K})}_{ij}+i(\sum_{j=1}^{N_{r}}\lambda_{j}^{r}\Im{(\mathbf{K})}_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}),
-\end{IEEEeqnarray}
- we obtain 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function1a}
-\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Re(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re(\mathbf{K})_{ij}+\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Im(\mathbf{K})_{ij}\\
-\label{intermediate function1b}
-\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Im(\mathbf{y}_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re(\mathbf{K})_{ij}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Im(\mathbf{K})_{ij}
-\end{IEEEeqnarray}
-Two intermediate variables $\Phi$ and $\Psi$ are defined
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermedia function 2a}
-\Phi^{r}=\Re(\mathbf{y})-\Re(\mathbf{K})
-\lambda^{r};
-\Phi^{i}=\Im(\mathbf{y})-\Re(\mathbf{K})\lambda^{i}\\
-\label{intermediate function 2b}
-\Psi^{r}=\Im(\mathbf{K})\lambda^{i};
-\Psi^{i}=-\Im(\mathbf{K})\lambda^{r}\\
-\nonumber
-\end{IEEEeqnarray} 
-therefore (\ref{intermediate function1a}) and (\ref{intermediate function1b}) can be rewritten as
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function3a}
-\Re(\mathbf{y}_{i})-\Re(<\mathbf{h}_{i}, \mathbf{W}>_{\mathbb{H}})=\Phi^{r}_{i}+\Psi_{i}^{r}\\\label{intermediate function3b}
-\Im(\mathbf{y}_{i})-\Im(<\mathbf{h}_{i}, \mathbf{w}>_{\mathbb{H}})=\Phi_{i}^{i}+\Psi_{i}^{i}
-\end{IEEEeqnarray}
-Therefore based on (\ref{intermediate function3a}) and (\ref{intermediate function3b}), 
-(\ref{simple risk function1}) and (\ref{simple risk function2}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\label{intermediate function4a}
-R(\xi^{r}_{i})+R(\hat{\xi}^{r}_{i})=\frac{1}{2}|\Phi^{r}_{i}+\Psi_{i}^{r}|^{2}_{\epsilon}\\
-\label{intermediate function4b}
-R(\xi^{i}_{i})+R(\hat{\xi}^{i}_{i})=\frac{1}{2}|\Phi^{i}_{i}+\Psi_{i}^{i}|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-Thus based on (\ref{intermediate function4a}) and (\ref{intermediate function4b}), the feasibility gap in (\ref{simple duality gap}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\Lambda^{r}, \Lambda^{i})=<(\Lambda^{r})^{T}, \Re(\mathbf{K})\Lambda^{r}>+<(\Lambda^{i})^{T}, \Re(\mathbf{K})\Lambda^{i}>-<\Re(\mathbf{y})^{T}, \Lambda^{r}>-<\Im(\mathbf{y})^{T}, \Lambda^{i}>\\
-+\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>+C\sum_{i=1}^{N_{r}}[(|\Phi^{r}_{i}+\Psi^{r}_{i}|)^{2}_{\epsilon}+(|\Phi^{i}_{i}+\Psi^{i}_{i}|)^{2}_{\epsilon}]-<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.
-\label{simple duality gap final}
-\end{IEEEeqnarray}
-Based on dual objective function in (\ref{simple dual function}), (\ref{simple duality gap final}) can be rewritten as 
-\begin{IEEEeqnarray}[\relax]{l}
-\nonumber
-G(\Lambda^{r}, \Lambda^{i})=<\Re(\mathbf{y})^{T}, \Lambda^{r}>+<\Im(\mathbf{y})^{T}, \Lambda^{i}>-\epsilon<\mathbf{e}^{T}, (|\Lambda^{r}|+|\Lambda^{i}|)>-2\theta(\Lambda_{i}, \Lambda_{j})\\
--<\Lambda^{r}, \Im(\mathbf{K})\Lambda^{i}>.\label{simple duality gap1}
-\end{IEEEeqnarray}
-The following ratio of the feasibility gap $G(\Lambda^{r}, \Lambda^{i})$ is used to measure the proximity of current solution to the optimal solution.
-The algorithm stops when the ratio satisfies a certain tolerance.
-\begin{equation}
-\frac{G}{G+\theta}
-\label{simple duality gap ratio1}
-\end{equation}
-\subsection{Update $\Phi$, $\Psi$ and $G$}
-$\Phi$, $\Psi$ and $G$ are updated in each iteration along with the optimization variables updated. The pseudo code to update $\Phi$, $\Psi$ and $G$ is given.
-
-Based on the definitions of $\Phi$ and $\Psi$ in (\ref{intermedia function 2a}) and (\ref{intermediate function 2b}), we have the following procedure to update $\Phi$ and $\Psi$ in real channel and imaginary channel, assume the optimization variables updated in each channel are indexed by $1$ and $2$, let $\sigma^{r}_{i}=(\lambda^{r}_{i})^{new}-\lambda^{r}_{i}$ and $\sigma^{i}_{i}=(\lambda^{i}_{i})^{new}-\lambda^{i}_{i}$ denote the differences between the updated optimization variables and the old optimization variables.\\
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{1}. Update $\Phi^{r}$ and $\Psi^{i}$ in real channel}{}
-\For{$i=1:N_{r}$}
-\State $\Phi_{i}^{r}=\Phi_{i}^{r}-\sigma_{1}^{r}\mathbf{K}^{r}_{i1}-\sigma_{2}^{r}\mathbf{K}_{i2}^{r}$
-\State $\Psi_{i}^{i}=\Psi_{i}^{i}-\sigma_{1}^{r}\mathbf{K}^{i}_{i1}-\sigma_{2}^{r}\mathbf{K}^{i}_{i2}$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{2}. Update $\Phi^{i}$ and $\Psi^{r}$ in imaginary channel}{}
-\For{$i=1:N_{r}$}
-\State $\Phi_{i}^{i}=\Phi_{i}^{i}-\sigma_{1}^{i}\mathbf{K}^{r}_{i1}-\sigma_{2}^{i}\mathbf{K}_{i2}^{r}$
-\State $\Psi_{i}^{r}=\Psi_{i}^{r}+\sigma_{1}^{i}\mathbf{K}^{i}_{i1}+\sigma_{2}^{i}\mathbf{K}^{i}_{i2}$
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-Then the cost function term in (\ref{simple duality gap final}) are updated by \textbf{Procedure 3} and \textbf{Procedure 4}.
-The cost function terms are denoted by $\chi^{r}$ in real channel and $\chi^{i}$ in imaginary channel.
-\begin{IEEEeqnarray}[\relax]{l}
-\label{cost function update1}
-\chi^{r}=\sum_{i}^{N_{r}}|\Phi^{r}_{i}+\Psi^{r}_{i}|^{2}_{\epsilon}\\
-\label{cost function update2}
-\chi^{i}=\sum_{i}^{N_{r}}|\Phi^{i}_{i}+\Psi^{i}_{i}|^{2}_{\epsilon}
-\end{IEEEeqnarray}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{3}. Update cost function in real channel}{$\chi^{r}$}
-\State $\chi^{r}=0$  \Comment{initial risk term}
-\For{$i=1:N_{r}$}
-\If{$|\Phi^{r}_{i}+\Psi^{r}_{i}|>\epsilon$}
-\State $\chi^{r}+=(|\Phi^{r}_{i}+\Psi^{r}_{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{4}. Update cost function in imaginary channel}{$\chi^{i}$}
-\State $\chi^{i}=0$  \Comment{initial risk term}
-\For{$i=1:N_{r}$}
-\If{$|\Phi^{i}_{i}+\Psi^{i}_{i}|>\epsilon$}
-\State $\chi^{i}+=(|\Phi^{i}_{i}+\Psi^{i}_{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-The pseudo code to update duality gap $G$ based on (\ref{simple duality gap1}) is shown in \textbf{Procedure 5}.
-Assume the indexes of optimization variables updated in real channel is $i$ and $j$, the indexes of optimization variables updated in imaginary channel is $m$ and $f$.
-Define the work sets in real and imaginary channels $S^{r}=[i,j]$ and $S^{i}=[m,f]$.
-Define $(\chi^{r})^{new}$ and $(\chi^{i})^{new}$ are the updated cost function terms based on \textbf{Procedure 3} and \textbf{Procedure 4}, the update process for the term $\theta(\Lambda^{r}, \Lambda^{i})$ in (\ref{simple duality gap1}) can be written as
-\begin{equation}
-\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}})=\bigtriangledown \theta^{r}_{S^{r}}+\bigtriangledown \theta^{i}_{S^{i}}-\frac{C}{2}((\chi^{r})^{new}+(\chi^{i})^{new}-\chi^{r}-\chi^{i}),
-\label{update dual objective function}
-\end{equation}
-Where $\theta_{S}^{r}$ is the gain of the sub dual objective function as shown in (\ref{gain work set selection lambda}), 
-\begin{IEEEeqnarray}[\relax]{l}
-\bigtriangledown \theta_{S^{r}}^{r}=-\frac{1}{2}(\Sigma^{r}_{S^{r}})^{T}\Re{(\mathbf{K})}_{S^{r}S^{r}}\Sigma^{r}_{S^{r}}+(\Phi^{r}_{S^{r}})^{T}\Sigma^{r}_{S^{r}}-\epsilon<\mathbf{e}^{T}_{S^{r}},|(\Lambda^{r}_{S^{r}})^{new}|-|\Lambda^{r}_{S^{r}}|>\\
-\bigtriangledown \theta_{S^{i}}^{i}=-\frac{1}{2}(\Sigma^{i}_{S^{i}})^{T}\Re{(\mathbf{K})}_{S^{i}S^{i}}\Sigma^{i}_{S^{i}}+(\Phi^{i}_{S^{i}})^{T}\Sigma^{i}_{S^{i}}-\epsilon<\mathbf{e}^{T}_{S^{i}},|(\Lambda^{i}_{S^{i}})^{new}|-|\Lambda^{i}_{S^{i}}|>
-\end{IEEEeqnarray}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{5}. Update $G$}{}
-\State $G+=Re(\mathbf{y}_{1})\sigma^{r}_{i}+Re(\mathbf{y}_{2})\sigma^{r}_{j}$
-\State $G+=Im(\mathbf{y}_{1})\sigma^{i}_{m}+Re(\mathbf{y}_{2})\sigma^{i}_{f}$
-\State $G-=\epsilon(|\lambda^{r}_{i}+\sigma^{r}_{i}|-|\lambda^{r}_{i}|+|\lambda^{r}_{j}+\sigma^{r}_{j}|-|\lambda^{r}_{j}|)$
-\State $G-=\epsilon(|\lambda^{i}_{m}+\sigma^{i}_{m}|-|\lambda^{i}_{m}|+|\lambda^{i}_{f}+\sigma^{i}_{f}|-|\lambda^{i}_{f}|)$
-\State $G-=2(\bigtriangledown \theta(\Lambda^{r}_{S^{r}}, \Lambda^{i}_{S^{i}}))$ \Comment{Update sub objective function based on (\ref{update dual objective function})}
-
-\State $G-=(\Sigma^{r}_{S^{r}})^{T}\Im(\mathbf{K}_{S^{r}S^{i}})\Sigma^{i}_{S^{i}}+(\Sigma^{r}_{S^{r}})^{T}\Psi^{r}_{S^{r}}+(\Sigma^{i}_{S^{i}})^{T}\Psi^{i}_{S^{i}}$ \Comment{Update $<\Lambda^{r},\Im(\mathbf{K})\Lambda^{i}>$}
-\EndProcedure
-\label{update G Phi and Psi}
-\end{algorithmic}
-\end{algorithm}
-
-Pseudo code for two types of combined 1-D searching solver are given by \textbf{Procedure 6} and \textbf{Procedure 7}. 
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{6}. One-shot 1-D combined searching solver}{} 
-\State Step 1. Search for two optimization variables based on single direction solver
-\For{$i=1:N_{r}$}
-\State calculate $\bigtriangledown \theta^{r}_{i}(\bigtriangledown \theta_{i}^{i})$\Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the dual variable with first and the second largest gain of sub objective function, denoted as 1st and 2nd
-\State Step 2. Update 1st and 2nd optimization variables based on double direction solver 
-\State update $\lambda^{r}_{1st}(\lambda^{i}_{1st})$ and $\lambda^{r}_{2nd}(\lambda^{i}_{2nd})$\Comment{Based on double direction solver \ref{double direction solver}}
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
-\EndProcedure
-\end{algorithmic}
-%\caption{Sequential 2-D Solver without Damping}
-\label{1D2D Nodamping}
-\end{algorithm}
-
- \begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{\textbf{7}. Sequential 1-D combined searching solver}{}
-\State Step 1. Search for two optimization variables based on single direction solver
-\For{$i=1:N_{r}$}\Comment{First round searching}
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the optimization variable with the largest gain of objective function as $1st_{1}$
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ with respect to $1st_{1}$
-\For{$i=1:N_{r}$} \Comment{Second round searching}
-\State calculate $\bigtriangledown \theta_{i}^{r}(\bigtriangledown \theta_{i}^{i})$ \Comment{Based on single direction solver \ref{single direction solver}}
-\EndFor
-\State choose the optimization variable with the largest gain of objective function as $1st_{2}$
-\State Step 2. Update $1st_{1}$ and $1st_{2}$ optimization variables based on double direction solver 
-\State update $\lambda^{r}_{1st_{1}}(\lambda^{i}_{1st_{1}})$ and $\lambda^{r}_{1st_{2}}(\lambda^{i}_{1st_{2}})$\Comment{Based on double direction solver \ref{double direction solver}}
-\State update $\Phi^{r}(\Phi^{i})$ and $\Psi^{r}(\Psi^{i})$ by \textbf{Procedure 1} and \textbf{Procedure 2}
-
-\EndProcedure
-\end{algorithmic}
-%\caption{Sequential 2-D Solver with Damping}
-\label{1D2D damping}
-\end{algorithm} 
-\newpage
-The pseudo code of complex support vector detector (CSVD) is shown in Appendix \ref{Pseudo code of CSVD}
-
-%\section{Hyperparameter Setting}
-\section{Computer Simulations}
-Computer simulations are launched to test the detection and run time performance of proposed dual channel complex support vector detection algorithm.
-For sake of brevity, the real case is tested first, all the experiments are made by C, compiled by gcc version 4.8.3 on 64 bit Fedora (release 19) Linux system.
-The experiment platform is a desktop computer with I5-4th generation CPU with quad processing cores, 3.2 GHz clock rate, 8 GB RAM.
-
-For sake of brevity, we consider a real uncoded spatial multiplex large MIMO system to simulate one channel of the proposed dual channel complex support vector detection algorithm.
-with $N_{r}$ received antennas and $N_{t}$ transmitted antennas.
-The propagation channel matrix is constructed by channel gain components that are identically independent distributed (i.i.d) Gaussian random variables with zero mean and unit variance.
-transmitted symbols are mutually independent modulated by $M$ PAM with normalized average energy $\frac{1}{N_{t}}$, transmitted over flat fading channel, the sample of noise is AWGN with zero mean and variance $\frac{1}{10^{SNR/10}}$, where $SNR$ denotes the signal to noise ratio.
-We make experiment to low loading factor system $100\times 40$ and full loading factor $100\times 100$, with at least $1e^{5}$ channel realizations and at least $500$ symbol errors accumulated.
-Fig.\ref{SER performance} shows the symbol error rate (SER) performance, Table.\ref{iteration time} shows the average iteration time of real SVD for different SNR.
-\begin{figure}[htb]
-\centering
-%\def\svgscale{0.5}
-\def\svgwidth{\columnwidth}
-\input{BER_curve_real_system.pdf_tex}
-\caption{SER performance of $100\times 100 $ and $100\times 40$ MIMO system}
-\label{SER performance}
-\end{figure}
-
-\begin{table}[htb]
-\renewcommand{\arraystretch}{1.3}
-\caption{Average Iteration Time of Real Support Vector Detector}
-\label{iteration time}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
-\hline
-\multirow{2}{*} {\bfseries Array Size} & \multicolumn{9}{|c|}{\bfseries SNR}\\
-\cline{2-10}
- &6& 8 &10& 12& 14& 16& 18& 20& 22\\
-\hline
-$100\times 40$&682 &681 &681 &681& 680 &679 &678&677 & 680\\
-\hline
-$100\times 100$&1925 &1916& 1903& 1885& 1862& 1827& 1782&1723&1654 \\
-\hline
-\end{tabular}
-\end{table}
+
+The Optimal (in a sense of lowest average error probability) Maximum Likelihood Detector (MLD) for MIMO system is given by
+\begin{equation}
+\hat{\mathbf{s}}^{ML}=\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{y}-\mathbf{H}\mathbf{s}||^{2},
+\label{MLD}
+\end{equation}
+where $||\cdot||$ denotes the 2-norm operation, therefore from (\ref{MLD}), the solution of MLD is the $\hat{\mathbf{s}}$ that can generate the minimum Euclidean distance between vector $\mathbf{y}$ and $\mathbf{H}\mathbf{s}$.
+
+Consider an alternative representation of MLD principle, let $\mathbf{H}_{1}\in \mathbb{C}^{N_{r}\times N}$ denotes a sub matrix composed of $N$ columns from $\mathbf{H}$, let $\mathbf{s}_{1}\in \mathbb{C}^{N}$ denote the sub symbol vector whose components are transmitted from the users corresponding to $\mathbf{H}_{1}$.
+Similarly, let $\mathbf{H}_{2}\in \mathbb{C}^{N_{r}\times (N_{t}-N)}$ denotes the sub matrix composed of the remaining columns from $\mathbf{H}$ and $\mathbf{s}_{2}\in \mathbb{C}^{(N_{t}-N)}$ is the sub symbol vector whose components are transmitted by the users corresponding to $\mathbf{H}_{2}$.
+Thus (\ref{discrete time MIMO system}) can be rewritten as
+\begin{equation}
+\mathbf{y}=\mathbf{H}_{1}\mathbf{s}_{1}+\mathbf{H}_{2}\mathbf{s}_{2}+\mathbf{n}.
+\label{alternative MIMO system}
+\end{equation}  
+Let $\hat{\mathbf{s}}_{1}, \hat{\mathbf{s}}_{2}$ denote the estimations of $\mathbf{s}_{1}, \mathbf{s}_{2}$, we have $\hat{\mathbf{s}}_{1}\in [\hat{\mathbf{s}}^{1}_{1}, \hat{\mathbf{s}}^{2}_{1}, \cdots \hat{\mathbf{s}}^{K}_{1}],, K=M^{N}$ and $\hat{\mathbf{s}}_{2}\in [\hat{\mathbf{s}}^{1}_{2}, \hat{\mathbf{s}}^{2}_{2}, \cdots \hat{\mathbf{s}}^{Q}_{2}], Q=M^{N_{t}-N}$, MLD in (\ref{MLD}) can be rewritten as
+\begin{equation}
+[\tilde{k}, \tilde{q}]=\min_{k\in [1,2\ldots K]}\min_{q\in [1,2,\ldots, Q]}||\mathbf{y}-\mathbf{H}_{1}\hat{\mathbf{s}}^{k}_{1}-\mathbf{H}_{2}\hat{\mathbf{s}}^{q}_{2}||^{2},\\
+\mathbf{s}^{ML}_{1}=\hat{\mathbf{s}}^{\tilde{k}}_{1}, \mathbf{s}^{ML}_{2}=\hat{\mathbf{s}}^{\tilde{q}}_{2},
+\label{alternative MLD}
+\end{equation}
+(\ref{alternative MLD}) can be divided into three steps, first define 
+\begin{equation}
+\mathbf{y}^{k}=\mathbf{y}-\mathbf{H}_{1}\hat{\mathbf{s}}^{k}_{1}\quad k\in [1,2,\ldots, K],
+\label{first step alternative MLD}
+\end{equation}
+Then solve 
+\begin{equation}
+\hat{\mathbf{x}}_{2}^{k}=\min_{\hat{\mathbf{s}}_{2}^{q}\in [\hat{\mathbf{s}}_{2}^{1},\hat{\mathbf{s}}_{2}^{3}\ldots, \hat{\mathbf{s}}_{2}^{Q}]}||\mathbf{y}^{k}-\mathbf{H}_{2}\hat{\mathbf{s}}_{2}^{q}||^{2},
+\label{second step alternative MLD}
+\end{equation}
+\begin{equation}
+\tilde{k}=\min_{k\in [1,2,\ldots, K]}||\mathbf{y}^{k}-\mathbf{H}_{2}\hat{\mathbf{x}}_{2}^{k}||^{2},
+\label{third step alternative MLD}
+\end{equation}
+Finally we have $\mathbf{s}_{1}^{ML}=\hat{\mathbf{s}}_{1}^{\tilde{k}}, \mathbf{s}_{2}^{ML}=\hat{\mathbf{x}}_{2}^{\tilde{k}}=\hat{\mathbf{s}}_{2}^{\tilde{q}}$.
+% needed in second column of first page if using \IEEEpubid
+%\IEEEpubidadjcol
+
 % An example of a floating figure using the graphicx package.
@@
 % \fnbelowfloat command of the stfloats package.
-%\section{Complexity Analysis}
-
-%\section{Conclusion}
-%The conclusion goes here.
+
+\section{Minimum Achievable Diversity based Channel Partition}
+\subsection{Diversity Maximization Selection}
+Based on the alternative form of MLD in (\ref{alternative MLD})-(\ref{third step alternative MLD}), General Parallel Interference Cancellation (GPIC) algorithm first generate a list of symbol vector candidates and then choose the candidate with the minimum Euclidean distance as the solution.
+To elaborate further, GPIC first generate a list of symbol vector candidate by exhaustive search for all the possible $\hat{\mathbf{s}}_{1}$, then rather than performing exhaustive search in (\ref{second step alternative MLD}), GPIC exploit low complexity sub optimal linear detectors (i.e., zeros forcing (ZF) and minimum mean square error (MMSE)) and their successive interference cancellation (SIC) counterparts to get the estimation of $\mathbf{s}_{2}$, for sake of simplicity, hereinafter we use LD/SIC.
+Then the best candidate in the list with the minimum Euclidean distance is chosen as the solution.
+
+Performance analysis of GPIC algorithm is provided in \cite{radji2009interference}, here we briefly conclude the main results in \cite{radji2009interference}, at the receiving side, the frame error is defined as there is at least one erroneous symbol in the estimation of transmitted symbol vector.
+Let $P_{e}$ denotes the average frame error probability.
+The diversity order, denoted by $d$ is defined as the slope of the $P_{e}$ in log-scale in high SNR region, which is given by\cite{zheng2003diversity}
+\begin{equation}
+d=-\lim_{SNR\to\infty}\frac{\log{P_{e}}}{\log(SNR)},
+\label{diversity}
+\end{equation}
+Let $P_{e}^{ML}$ denotes the average frame error probability of MLD, and $P_{e2}=\mathbb{E}_{\mathbf{H}_{2}, \mathbf{s}_{2}}(Pr(\hat{\mathbf{s}}^{k_{1}}_{2}\neq \mathbf{s}_{2}|\mathbf{H}_{2}, \mathbf{s}_{2}))$, where $P_{r}(A)$ denotes the probability that a event A occurs, $\hat{\mathbf{s}}_{1}^{k_{1}}=\mathbf{s}_{1}$, therefore $P_{e2}$ is the average frame error probability of the LD/SICs for the sub system in which the interference from the users that transmitted $\mathbf{s}_{1}$ are perfectly cancelled from the observation $\mathbf{y}$.
+given by
+\begin{equation}
+\mathbf{y}^{k_{1}}=\mathbf{y}-\mathbf{H}_{1}\hat{\mathbf{s}}_{1}^{k_{1}},
+\label{perfect IC}
+\end{equation} 
+because $\hat{\mathbf{s}}^{k1}_{1}=\mathbf{s}_{1}$, we have
+\begin{equation}
+\mathbf{y}^{k1}=\mathbf{H}_{2}\mathbf{s}_{2}+\mathbf{n},
+\label{sub MIMO system}
+\end{equation} 
+The average frame error probability of GPIC algorithm $P_{et}$ is bounded by 
+\begin{equation}
+\max(P^{ML}_{e}, P_{e2})\leq P_{et}\leq P^{ML}_{e}+P_{e2}, 
+\label{average frame error probability of GPIC}
+\end{equation}
+in (\ref{average frame error probability of GPIC}), the diversity order of MLD is $N_{r}$, $P_{e2}$ is the average frame error probability of sub optimal LD/SICs, let $d_{2}$ denotes the diversity order of LD/SICs, based on (\ref{diversity}), we have
+\begin{equation}
+\lim_{SNR\to\infty}P^{ML}_{e}\propto SNR^{-N_{r}},
+\label{MLD diversity}
+\end{equation}
+\begin{equation}
+\lim_{SNR\to\infty}P_{e2}\propto SNR^{-d_{2}},
+\label{LD diversity}
+\end{equation}
+Let $d_{t}$ denotes the diversity order of GPIC algorithm, now consider the following conditions
+\begin{itemize}
+\item $d_{2}>N_{r}$,
+\begin{equation}
+\lim_{SNR\to\infty}\frac{P_{e2}}{P^{ML}_{e}}=SNR^{N_{r}-d_{2}}=0,
+\label{condition1sub1}
+\end{equation}
+based on (\ref{average frame error probability of GPIC}), we have
+\begin{equation}
+\lim_{SNR\to\infty}\frac{P_{et}}{P^{ML}_{e}}=1,
+\label{condition1sub2}
+\end{equation}
+thus $d_{t}=N_{r}$.
+\item $d_2=N_{r}$,
+we have 
+\begin{equation}
+\lim_{SNR\to\infty}P_{et}\propto SNR^{-N_{r}},
+\label{condition2sub1}
+\end{equation}
+thus $d_{t}=N_{r}$.
+\item $d_{2}<N_{r}$,
+\begin{equation}
+\lim_{SNR\to\infty}\frac{P^{ML}_{e}}{P_{e2}}=SNR^{d_{2}-N_{r}}=0,
+\label{condition3sub1}
+\end{equation}
+based on (\ref{average frame error probability of GPIC}), we have  
+\begin{equation}
+\lim_{SNR\to\infty}P_{et}=P_{e2}\propto SNR^{-d_{2}},
+\label{condition3sub2}
+\end{equation}
+thus 
+$d_{t}=d_{2}$.
+\end{itemize} 
+Therefore when $d_{2}\geq N_{r}$, GPIC algorithm can achieve ML performance asymptotically, when $d_{2}<N_{r}$, the diversity order that GPIC can achieve at high SNR region is equal to that of LD/SICs, in \cite{radji2009interference}, the authors employ diversity maximization selection (DMS) scheme for channel partition, which is proposed in \cite{zhang2006diversity}.
+The optimum diversity order can be guaranteed with low complexity.
+
+To elaborate further, for a given number of antennas chosen at the channel partition stage $N$, there is $N_{u}=\left[\begin{array}{l}N_{t}\\N\end{array}\right]$ possible combinations of $[\mathbf{H}_{1}, \mathbf{H}_{2}]$, according to DMS principle, the maximum diversity order of LD/SIC is achieved by choosing the subset $\mathbf{H}_{2}$ that has the strongest weakest substream, in a sense of post processing SNR.
+Therefore, when using MMSE/SIC as the sub optimal detector, the subset $\mathbf{H}^{opt}_{2}$ selected based on DMS principle should be\cite{zhang2006diversity}
+\begin{IEEEeqnarray}[\relax]{l}
+\mathbf{H}^{opt}_{2}=\mathbf{H}^{p}_{2},\\
+p=\min_{j=1,2,\ldots, N_{u}}\theta_{j},\\
+\theta_{j}=\max_{k=1,2,\ldots, N_{t}-N}((\mathbf{H}_{2}^{j})^{H}\mathbf{H}_{2}^{j}+SNR^{-1}\mathbf{I})_{kk}^{-1},\quad \mathbf{H}_{2}^{j}\in[\mathbf{H}_{2}^{1}, \mathbf{H}_{2}^{2}, \ldots, \mathbf{H}_{2}^{N_{u}}];
+\label{DMS principle}
+\end{IEEEeqnarray}   
+Where $\mathbf{A}_{kk}$ denotes the $k$th diagonal component of matrix $\mathbf{A}$. The diversity order of LD/SIC detector after DMS channel partition process is given by 
+$d_{2DMS}=(N+1)(N_{r}-N_{t}+N+1)$.
+In \cite{radji2009interference}, the authors derive the minimum number of antennas $N_{min}$ at channel partition stage that can guarantee $d_{2DMS}\geq N_{r}$, which is given by
+\begin{equation}
+N_{min}=\lceil \sqrt{\frac{(N_{r}-N_{t})^{2}}{4}+N_{r}}-\frac{N_{r}-N_{t}}{2}-1\rceil,
+\label{Nmin DMS}
+\end{equation}
+where $\lceil\alpha\rceil$ denotes the minimum integer no less than $\alpha$.
+\subsection{Minimum Achievable Diversity: How many antennas do we need for LS-MIMO?}
+In LS-MIMO V-BLAS systems, the maximum diversity order is $N_{r}$, which is extremely large under the condition that there is tens to hundreds of receive antennas.
+On the one hand, diversity order is achieved at high SNR region, however, in practical, such a high diversity order is not necessary, because the SNR region of interest is the range in which the bit error rate (BER) or symbol error rate (SER) can be $10^{-5}$ to $10^{-7}$.
+On the other hand, the computational complexity to guarantee ML performance by DMS channel partition is excessive in LS-MIMO, for example, when $N_{r}=N_{t}$, based on (\ref{Nmin DMS}), the $N_{min}=\lceil\sqrt{N_{r}}-1\rceil$, the number of the symbol vector candidates in the list generated by exhaustive search for $\mathbf{s}_{1}$ is $M^{N_{min}}$.
+
+Therefore, here we consider minimum achievable diversity (MAD) principle, which sacrifices redundant diversity gain in LS-MIMO, in order to reduce the complexity.
+Let $d_{2MAD}$ denotes the diversity order of LD/SIC detectors, $\tilde{N}_{min}$ denotes the minimum number of antennas chosen by MAD principle.
+Our goal is to guarantee the overall diversity is no less than a given minimum diversity while keep $\tilde{N}_{min}$ small.
+Let $1\leq g<N_{r}$ denote the given minimum achievable diversity order, based on (\ref{condition3sub2}), we have
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+ if \quad d_{2MAD}<N_{r}\quad and\quad d_{2MAD}\geq g\\
+  d_{t}=d_{2MAD}\geq g.
+\end{IEEEeqnarray}
+Therefore we can guarantee that the overall diversity order of GPIC algorithm is no less than $g$, in order to derive the minimum number of antennas required based on MAD principle, we define function
+\begin{IEEEeqnarray}[\relax]{l}
+f(N)=d_{2MAD}-g=(N+1)(N_{r}-N_{t}+N+1)-g,\label{diversity function}
+\end{IEEEeqnarray}    
+where $N\in [1,2,\ldots, N_{t}]$, our goal is to find minimum $N$, denoted by $\tilde{N}_{min}$, that satisfy $f(N)\geq 0$. The two zeros points of quadratic function $f(N)$ are 
+\begin{IEEEeqnarray}[\relax]{l}
+N_{1}=-\sqrt{\frac{(N_{r}-N_{t})^{2}}{4}+g}-\frac{N_{r}-N_{t}}{2}-1,\\
+N_{2}=\sqrt{\frac{(N_{r}-N_{t})^{2}}{4}+g}-\frac{N_{r}-N_{t}}{2}-1
+\label{zeros points}
+\end{IEEEeqnarray}
+when $N<N_{1}$ or $N>N_{2}$, $f(N)\geq 0$, obviously $N_{1}<0$, there is no effective $N$ exits that satisfy the former condition, thus, we have 
+\begin{equation}
+\tilde{N}_{min}=\lceil \sqrt{\frac{(N_{r}-N_{t})^{2}}{4}+g}-\frac{N_{r}-N_{t}}{2}-1\rceil
+\label{Nmin MAD}
+\end{equation}
+\section{Theoretical Analysis of Channel Hardening}
+\subsection{Preliminary}
+Orthogonality deficiency $\phi_{od}$ measures  how orthogonal a matrix is \cite{ma2008performance}, which is defined by
+\begin{equation}
+\phi_{od}=1-\frac{det(\mathbf{W})}{\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||^{2}},
+\label{OD}
+\end{equation}
+where $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$ denotes Wishart matrix, $\mathbf{h}_{i}$ denotes the $i$ th column of $\mathbf{H}$, $det(\cdot)$ denotes determinant operation, $||\cdot||$ denotes 2-norm operation.
+Based on Hadamard's inequality $\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||\geq det(\mathbf{H})$, we have $0\leq\phi_{od}\leq 1$, if $\mathbf{H}$ is singular, $\phi_{od}=1$, if $\mathbf{H}$ is orthogonal, then $\phi_{od}=0$.
+
+$||\mathbf{h}_{i}||^{2}=\sum_{j=1}^{N_{r}}|\mathbf{H}_{ji}|^{2}$, where $|\cdot|$ denotes magnitude operation.
+$\mathbf{H}_{ij}\sim \mathbb{C}N(0,1)$, where $\mathbb{C}N(0, \sigma^{2})$ denotes CSCG distribution with variance $\sigma^{2}$, thus $|\mathbf{H}_{ji}|\sim Rayleigh(1/\sqrt{2})$, where $Rayleigh(\sigma)$ denotes the Rayleigh distribution with shape parameter $\sigma$, therefore $||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},1)$\cite{papoulis2002probability}.
+$Gamma(k,\theta)$ denotes Gamma distribution, with $k$ degrees of freedom and scale parameter $\theta$.
+
+For sake of simplicity, we define orthogonality measure $\phi_{om}$, which is given by 
+\begin{equation}
+\phi_{om}=\frac{det(\mathbf{W})}{\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||^{2}},
+\label{OM}
+\end{equation}
+$0\leq \phi_{om}\leq 1$, if $\phi_{om}$ is closer to 1, $\mathbf{H}$ is more closer to an orthogonal matrix. 
+\subsection{Introduction to Channel Hardening Phenomenon}
+\subsection{Logarithmic Expectation of Orthogonality Measure}
+Based on (\ref{OM}), The logarithm of $\phi_{om}$ can be written as 
+\begin{equation}
+\ln(\phi_{om})=\ln(det(\mathbf{W}))-\sum_{i=1}^{N_{t}}\ln(||\mathbf{h}_{i}||^{2}),
+\label{log OM}
+\end{equation}
+Taking expectation of (\ref{log OM}), we have 
+\begin{equation}
+\mathbb{E}[\ln(\phi_{om})]=\mathbb{E}[\ln(det(\mathbf{W}))]-\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(||\mathbf{h}_{i}||^{2})].
+\label{log expectation OM}
+\end{equation}
+First we consider the first summand on the right hand of (\ref{log expectation OM}) $\mathbb{E}[\ln(det(\mathbf{W}))]$.
+Let $\mathbb{C}W_{m}(n, \Sigma)$ denotes complex Wishart distribution, which is the joint distribution of sample covariance matrix from multivariate complex Gaussian random variable\cite{goodman1963statistical}.
+$n$ is the degree of freedom and $\Sigma\in \mathbb{C}^{m\times m}$ is the covariance matrix.
+Let $\Pi_{i}$ denotes the $i$th row of $\mathbf{H}$.
+$\Pi_{i}$ is a $N_{t}$-variate complex Gaussian random variable so does $\Pi_{i}^{H}$.
+Therefore $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}=\sum_{i=1}^{N_{r}}\Pi_{i}^{H}\Pi_{i}\sim \mathbb{C}W_{N_{t}}(N_{r}, \mathbf{I})$.
+The logarithmic expectation of $det(\mathbf{W})$ is
+\begin{equation}
+\mathbb{E}[\ln(det(\mathbf{W}))]=\sum_{i=1}^{N_{t}}\psi(N_{r}-i+1),
+\label{log expectation of wishart}
+\end{equation}
+where $\psi(n)$ denotes Digamma function, which is given by\cite{papoulis2002probability}
+\begin{equation}
+\psi(n)=\frac{\Gamma^{'}(n)}{\Gamma(n)},
+\label{Digmma function}
+\end{equation}
+$\Gamma(n)$ denotes Gamma function.
+Proof: see Appendix \ref{log expectation of OM}.
+
+Now we consider the second summand on the right hand of (\ref{log expectation OM}) $\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(||\mathbf{h}_{i}||^{2})]$.
+$||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r}, 1)$, the logarithmic expectation of a Gamma random variable $\gamma\sim Gamma(n, \theta)$ can be written as:
+\begin{equation}
+\mathbb{E}[\ln(\gamma)]=\psi(n)+\ln(\theta),
+\label{log expectation of gamma}
+\end{equation}
+Thus (\ref{log expectation of gamma}), we have
+\begin{equation}
+\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(||\mathbf{h}_{i}||^{2})]=\sum_{i=1}^{N_{t}}\psi(N_{r}),
+\label{sum of log expectation gamma}
+\end{equation}
+proof: see Appendix \ref{proof log expectation gamma}.
+
+Based on (\ref{log expectation of wishart}) and (\ref{sum of log expectation gamma}), the logarithmic expectation of orthogonality measure $\phi_{om}$ is 
+\begin{equation}
+\mathbb{E}[\ln(\phi_{om})]=\sum_{i=1}^{N_{t}}[\psi(N_{r}-i+1)-\psi(N_{r})],
+\label{final log expectation OM}
+\end{equation}
+\subsection{Probability Density Function of Orthogonality Measure}
+\section{Simplified Channel Partition based on Orthogonality Measure}
+\section{Computer Simulations}
+\subsection{Full Loaded Systems}
+\subsection{Systems with Different Loading Factors}
+
+\section{Conclusion}
+The conclusion goes here.
 
@@
 \appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
+\section{}\label{log expectation of OM}
+Let $\mathbf{A}\in \mathbb{C}^{m\times m}$, $A\sim \mathbb{C}W_{m}(n, \mathbf{\Sigma})$, According to the definition of complex Wishart matrix, it is obvious $\mathbf{A}$ is Hermition positive definite matrix (i.e., $\mathbf{A}=\mathbf{A}^{H}>0$).
+
+The pdf of $\mathbf{A}$ can be written as\cite{nagar2011expectations}:
+\begin{equation}
+f(\mathbf{A})=\{\tilde{\Gamma}_{m}(n)det(\mathbf{\Sigma})^{n} \}^{-1}det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A}),
+\label{Appendequa1}
+\end{equation}
+where $\tilde{\Gamma}_{m}(\beta)$ denotes multivariate complex Gamma function defined by\cite{nagar2011expectations}:
+\begin{equation}
+\tilde{\Gamma}_{m}(\beta)=\pi^{\frac{m(m-1)}{2}}\prod_{i=1}^{m}\Gamma(\beta-i+1)\quad Re(\beta)>m-1.
+\label{Appendequa2}
+\end{equation}
+Furthermore, from \cite{nagar2011expectations}, we have 
+\begin{equation}
+\tilde{\Gamma}_{m}(\beta)=\int_{\mathbf{X}=\mathbf{X}^{H}>0}etr(-\mathbf{X})det(\mathbf{X})^{\beta-m}d
+\mathbf{X} \quad Re(\beta)>m-1.
+\label{Appendequa3}
+\end{equation}
+We derive logarithmic expectation of $det(\mathbf{A})$
+\begin{eqnarray}
+\nonumber
+\mathbb{E}[\ln(det(\mathbf{A}))]&=&\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))f(\mathbf{A})d\mathbf{A}\\
+\nonumber
+&=&\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))\{\tilde{\Gamma}_{m}(n)det(\mathbf{\Sigma})^{n} \}^{-1}det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A})d\mathbf{A}\\
+&=&\frac{det(\mathbf{\Sigma})^{-n}}{\tilde{\Gamma}_{m}(n)}\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}etr(-\mathbf{\Sigma}^{-1}\mathbf{A})d\mathbf{A},
+\label{Appendequa4}
+\end{eqnarray}
+if $\mathbf{\Sigma}=\mathbf{I}$, (\ref{Appendequa4}) can be written as 
+\begin{equation}
+\mathbb{E}[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\int_{\mathbf{A}=\mathbf{A}^{H}>0}\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}etr(-\mathbf{A})d\mathbf{A}.
+\label{Appendequa5}
+\end{equation}
+Because $\frac{d}{dn}[det(\mathbf{A})]^{n-m}=\ln(det(\mathbf{A}))det(\mathbf{A})^{n-m}$, (\ref{Appendequa5}) can be rewritten as
+\begin{equation}
+\mathbf{E}[\ln(det(\mathbf{A}))]=\frac{1}{\tilde{\Gamma}_{m}(n)}\frac{d}{dn}\int_{\mathbf{A}=\mathbf{A}^{H}>0}etr(-\mathbf{A})det(\mathbf{A})^{n-m}d\mathbf{A},
+\label{Appendequa6}
+\end{equation}
+Based on (\ref{Appendequa3}), in (\ref{Appendequa6}), we have  
+\begin{equation}
+\tilde{\Gamma}^{'}_{m}(n)=\frac{d}{dn}\int_{\mathbf{A}=\mathbf{A}^{H}>0}etr(-\mathbf{A})det(\mathbf{A})^{n-m}d\mathbf{A},
+\label{Appendequa7}
+\end{equation} 
+Therefore (\ref{Appendequa6}) can be rewritten as 
+\begin{equation}
+\mathbf{E}[\ln(\mathbf{A})]=\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}.
+\label{Appendequa8}
+\end{equation}
+Based on (\ref{Appendequa2}), we have 
+\begin{equation}
+\tilde{\Gamma}^{'}_{m}(n)=\pi^{\frac{m(m-1)}{2}}\sum_{i=1}^{m}[\Gamma^{'}(n-i+1)\prod_{j\neq i }^{m}\Gamma(n-j+1)],
+\label{Appendeqau9}
+\end{equation}
+Using (\ref{Appendequa2}) and (\ref{Appendeqau9}), we have 
+\begin{IEEEeqnarray}[\relax]{l}
+\nonumber
+\frac{\tilde{\Gamma}^{'}_{m}(n)}{\tilde{\Gamma}_{m}(n)}=\frac{\sum_{i=1}^{m}[\Gamma^{'}(n-i+1)\prod_{j\neq i }^{m}\Gamma(n-j+1)]}{\prod_{k=1}^{m}\Gamma(n-k+1)}\\
+=\sum_{i=1}^{m}[\frac{\Gamma^{'}(n-i+1)\prod_{j\neq i }^{m}\Gamma(n-j+1)}{\prod_{k=1}^{m}\Gamma(n-k+1)}]
+=\sum_{i=1}^{m}\frac{\Gamma^{'}(n-i+1)}{\Gamma(n-i+1)},
+\label{Appendequa10}
+\end{IEEEeqnarray}
+
+Therefore (\ref{Appendequa8}) can be rewritten as
+\begin{equation}
+\mathbf{E}[\ln(det(\mathbf{A}))]=\sum_{i=1}^{m}\psi(n-i+1),
+\label{Appendequa11}
+\end{equation}
+where $\psi(n)=\frac{\Gamma^{'}(n)}{\Gamma(n)}$ denotes Digamma function.
 
@@
 % if you want by leaving the argument blank
-\section{Pseudo Code of CSVD}\label{Pseudo code of CSVD}
-\begin{algorithm}[htb]
-\begin{algorithmic}
-\Procedure{CSVD}{$\mathbf{y}$,$\mathbf{H}$}
-\State Step 1. Initialization
-\State $\mathbf{K}=\mathbf{H}\mathbf{H}^{H}$ \Comment{kernel matrix}
-\State $\chi^{r}=0$, $\chi^{i}=0$ \Comment{risk function}
-\For{$i=1:N_{r}$}\Comment{initialize $\lambda^{r}$, $\lambda^{i}$, $\Phi^{r}$, $\Phi^{i}$, $\Psi^{r}$, $\Psi^{i}$ and duality gap $G$}
-\State $\lambda_{i}^{r}=0, \lambda_{i}^{i}=0$
-\State $\Phi_{i}^{r}=Re(y_{i}), \Phi_{i}^{i}=Im(y_{i})$
-\State $\Psi_{i}^{r}=0, \Psi_{i}^{i}=0$
-\If{$|\Phi^{r}_{i}|>\epsilon$}
-\State $\chi^{r}+=(|\Phi^{r}_{i}|-\epsilon)^{2}$
-\EndIf
-\If{$|\Phi^{i}_{i}|>\epsilon$}
-\State $\chi^{i}+=(|\Phi_{i}^{i}|-\epsilon)^{2}$
-\EndIf
-\EndFor 
-\State $G=C(\chi^{r}+\chi^{i})$ \Comment{initialize duality gap}
-\State $\theta=-0.5G$ \Comment{initialize objective function}
-\State  Step 2. if $G>tol$, go to step 3, else go to Step 5
-\State Step 3.
-\State call combined 1-D searching solver in \textbf{Procedure 6} and \textbf{Procedure 7} \Comment{find and update two optimization variables in the real and imaginary channel} 
-\State Step 4. \textbf{Procedure 5} update $\frac{G}{G+\theta}$, go back to step 2.
-\State Step 5.
-\State $\tilde{\mathbf{x}}=\mathbf{H}^{H}(\Lambda^{r}+i\Lambda^{i})$ \Comment{reconstruct $\mathbf{x}$}
-\State $\mathbf{x}=\mathbb{Q}(\tilde{x})$\Comment{$\mathbb{Q}(\cdot)$ denotes quantization operation based on symbol constellation}
-\State Step 6. \textbf{Return} $\mathbf{x}$ 
-\EndProcedure
-\end{algorithmic}
-\label{CSVD algorithm}
-\caption{Dual Channel Complex Support Vector Detection Algorithm }
-\end{algorithm}
-%Appendix two text goes here.
+\section{}\label{proof log expectation gamma}
+If $x\sim Gamma(n, \theta)$, with shape parameter $k$ and scale parameter $\theta$, $x>0$, $\Gamma(k)$ denotes Gamma function, the density function of Gamma distribution is
+\begin{equation}
+f(x,k,\theta)=\frac{x^{k-1}e^{-x/\theta}}{\Gamma(k)\theta^{k}}.
+\label{AppendixB1}
+\end{equation}
+where $\Gamma(n)$ satisfies\cite{papoulis2002probability}
+\begin{equation}
+\Gamma(n)=\int_{0}^{\infty}x^{n-1}e^{-x}dx,
+\label{AppendixB2}
+\end{equation}
+Thus the logarithmic expectation of $x$ can be written as
+\begin{equation}
+\mathbf{E}[\ln(x)]=\frac{1}{\Gamma(k)}\int_{0}^{\infty}\ln(x)x^{k-1}e^{-x/\theta}\theta^{-k}dx,
+\label{AppendixB3}
+\end{equation}
+define $z=x/\theta$ and based on (\ref{AppendixB2}), (\ref{AppendixB3}) can be rewritten as
+\begin{equation}
+\mathbf{E}[\ln(x)]=\ln(\theta)+\frac{1}{\Gamma(k)}\int_{0}^{\infty}\ln(z)z^{k-1}e^{-z}dz.
+\label{AppendixB4}
+\end{equation}
+Because $\frac{d(z^{k-1})}{dk}=\ln(z)z^{k-1}$, (\ref{AppendixB4}) can be rewritten as
+\begin{equation}
+\mathbf{E}[\ln(x)]=\ln(\theta)+\frac{1}{\Gamma(k)}\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz,
+\label{AppendixB5}
+\end{equation}
+Based on (\ref{AppendixB2}), we have
+\begin{equation}
+\Gamma^{'}(k)=\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz,
+\label{AppendixB6}
+\end{equation}
+Thus (\ref{AppendixB5}) can be rewritten as
+\begin{equation}
+\mathbf{E}(\ln(x))=\ln(\theta)+\frac{\Gamma^{'}(k)}{\Gamma(k)}=\ln(\theta)+\psi(k),
+\label{AppendixB6}
+\end{equation}
+where $\psi(k)$ denotes Digamma function.
 
@@
 % by themselves when using endfloat and the captionsoff option.
-%\ifCLASSOPTIONcaptionsoff
-%  \newpage
-%\fi
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
 
@@
 %\enlargethispage{-5in}
-
-% that's all folks
-%\end{spacing}
-
-\newpage
 \bibliographystyle{IEEEtran}
 \bibliography{citation}
-\end{spacing}												
+
+% that's all folks
 \end{document}

### 2015-12-18 Report revised May 12 2015/Report_draft.tex
Reorganized Report Record
Report Dec imcomplete

--- 2015-05-13 Lattice Reduction/Report April 2015/Report revised May 12 2015/Report_draft.tex
@@
 \end{equation}
-where $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$ denotes Wishart matrix, $\mathbf{h}_{i}$ denotes the $i$ th column of $\mathbf{H}$, $det(\cdot)$ denotes determinant operation, $||\cdot||^{2}$ denotes 2-norm operation.
+where $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$ denotes Wishart matrix, $\mathbf{h}_{i}$ denotes the $i$ th column of $\mathbf{H}$, $det(\cdot)$ denotes determinant operation, $||\cdot||$ denotes 2-norm operation.
+Based on Hadamard's inequality $\prod_{i=1}^{N_{t}}||\mathbf{h}_{i}||\geq det(\mathbf{H})$, we have $0\leq\phi_{od}\leq 1$.
 In (\ref{formula1}), $||\mathbf{h}_{i}||^{2}=\sum_{j=1}^{N_{r}}|\mathbf{H}_{ji}|^{2}$, $\mathbf{H}_{ji}$ denotes the component of $\mathbf{H}$ at $j$ th row and $i$ th column.
-$|\mathbf{H}_{ji}|\sim Rayleigh(1/\sqrt{2})$, therefore $||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},1)$\cite{papoulis1996stochastic}.
-$Gamma(k,\theta)$ denotes Gamma distribution, with $k$ degrees of freedom and scale $\theta$.
+$\mathbf{H}_{ij}\sim \mathbb{C}N(0,1)$, where $\mathbb{C}N(0, \sigma^{2})$ denotes CSCG distribution with variance $\sigma^{2}$, let $|\cdot|$ denotes magnitude operation, $|\mathbf{H}_{ji}|\sim Rayleigh(1/\sqrt{2})$, where $Rayleigh(\sigma)$ denotes the Rayleigh distribution with shape parameter $\sigma$, therefore $||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r},1)$\cite{papoulis1996stochastic}.
+$Gamma(k,\theta)$ denotes Gamma distribution, with $k$ degrees of freedom and scale parameter $\theta$.
 Furthermore, we have:
@@
 \section{Logarithmic Expectation of Orthogonality Measurement}\label{log expectation of om}
-
 Taking expectation of (\ref{formula4}), we have 
@@
 \end{equation}
-Thus we have 
+where $\Gamma(n)$ satisfies\cite{papoulis2002probability}
+\begin{equation}
+\Gamma(n)=\int_{0}^{\infty}x^{n-1}e^{-x}dx,
+\label{AppendequaAdditional}
+\end{equation}
+Thus the logarithmic expectation of $x$ can be written as
 \begin{equation}
@@
 \end{equation}
-define $z=x/\theta$ and since $\Gamma(k)=\int_{0}^{\infty}x^{k-1}e^{-x}dx$, (\ref{Appendequa10}) can be rewritten as
+define $z=x/\theta$ and based on (\ref{AppendequaAdditional}), (\ref{Appendequa10}) can be rewritten as
 \begin{equation}
@@
 Because $\frac{d(z^{k-1})}{dk}=\ln(z)z^{k-1}$, (\ref{Appendequa11}) can be rewritten as
-\begin{eqnarray}
-\nonumber
-E[\ln(z)]&=&\ln(\theta)+\frac{1}{\Gamma(k)}\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz\\
-\nonumber
-&=&\ln(\theta)+\frac{\Gamma^{'}(k)}{\Gamma(k)}\\
-\nonumber
-&=&\ln(\theta)+\psi(k),
+\begin{equation}
+E[\ln(x)]=\ln(\theta)+\frac{1}{\Gamma(k)}\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz,
 \label{Appendequa12}
-\end{eqnarray}
+\end{equation}
+Based on (\ref{AppendequaAdditional}), we have
+\begin{equation}
+\Gamma^{'}(k)=\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz,
+\label{AppendequaAdditional2}
+\end{equation}
+Thus (\ref{Appendequa12}) can be rewritten as
+\begin{equation}
+E(\ln(x))=\ln(\theta)+\frac{\Gamma^{'}(k)}{\Gamma(k)}=\ln(\theta)+\psi(k),
+\label{AppendequaAdditional3}
+\end{equation}
 where $\psi(k)$ denotes Digamma function.

### 2015-12-22 Report Dec 2015/Report.tex
Report Dec initial

@@
 \end{itemize} 
-Therefore when $d_{2}\geq N_{r}$, GPIC algorithm can achieve ML performance asymptotically, when $d_{2}<N_{r}$, the diversity order that GPIC can achieve at high SNR region is equal to that of LD/SICs, in \cite{radji2009interference}, the authors employ diversity maximization selection (DMS) scheme for channel partition, which is proposed in \cite{zhang2006diversity}.
-The optimum diversity order can be guaranteed with low complexity.
-
-To elaborate further, for a given number of antennas chosen at the channel partition stage $N$, there is $N_{u}=\left[\begin{array}{l}N_{t}\\N\end{array}\right]$ possible combinations of $[\mathbf{H}_{1}, \mathbf{H}_{2}]$, according to DMS principle, the maximum diversity order of LD/SIC is achieved by choosing the subset $\mathbf{H}_{2}$ that has the strongest weakest substream, in a sense of post processing SNR.
+Therefore when $d_{2}\geq N_{r}$, GPIC algorithm can achieve ML performance asymptotically, when $d_{2}<N_{r}$, the diversity order that GPIC can achieve at high SNR region is equal to that of LD/SICs, in \cite{radji2009interference}, the authors employ diversity maximization selection (MDS) scheme for channel partition, which is proposed in \cite{zhang2006diversity}.
+The optimal diversity order can be guaranteed with low complexity for conventional MIMO systems.
+
+To elaborate further, for a given number of antennas chosen at the channel partition stage $N$, there is $N_{u}={N_{t}\choose N}$ possible combinations of $[\mathbf{H}_{1}, \mathbf{H}_{2}]$, according to MDS principle, the maximum diversity order of LD/SIC is achieved by choosing the subset $\mathbf{H}_{2}$ that has the strongest weakest substream, in a sense of post processing SNR.
 Therefore, when using MMSE/SIC as the sub optimal detector, the subset $\mathbf{H}^{opt}_{2}$ selected based on DMS principle should be\cite{zhang2006diversity}
@@
 \end{IEEEeqnarray}
-when $N<N_{1}$ or $N>N_{2}$, $f(N)\geq 0$, obviously $N_{1}<0$, there is no effective $N$ exits that satisfy the former condition, thus, we have 
+when $N\leq N_{1}$ or $N\geq N_{2}$, $f(N)\geq 0$, obviously $N_{1}<0$, there is no feasible $N$ exits that can make the former condition satisfied. Thus, we have 
 \begin{equation}
@@
 \end{equation}
-\section{Theoretical Analysis of Channel Hardening}
+\subsection{Computer Simulations}
+In this section, computer simulation results for the bit error rate (BER) performances of MAD principle based GPIC algorithm are presented.
+As comparisons, Sel-MMSE-OSIC algorithm in \cite{radji2009interference}, which is based on maximum diversity selection (MDS) principle is also considered.
+The software testbed is build by C, compiled by GCC compiler version 4.9.2 on 64 bit Debian (release 8.2) Linux systems, the experiments are performed on two desktops, one with Intel I5-4th generation CPU, quad cores, 3.2GHz clock rate and the other one with Intel I7-5th generation CPU, six cores, 3.5GHz clock rate.
+
+We consider uncoded complex spatial multiplexing LS-MIMO systems, For each receive SNR point, the BER are calculated with minimum $10^{5}$ independent channel realizations achieved and minimum 300 symbol errors accumulated.
+The modulation schemes considered are rectangular M-QAM(4-QAM and 16-QAM) with Gray code labeling.
+In each channel realization, $N_{t}$ mutually independent randomly generated bit sequences are modulated to complex symbols.
+$N_{t}$ complex symbols are transmitted over randomly generated Rayleigh flat fading channel, each channel matrix component is CSCG random variable with unit variance.
+The receive symbol vector are corrupted by AWGN.
+
+For sake of simplicity, we use MAD-n to present the results for minimum achievable diversity selection, where $n$ denotes the minimum achievable diversity.
+The minimum number of antennas selected by channel partition for a given minimum achievable diversity is given by (\ref{Nmin MAD}).
+Maximum diversity selection (MDS) is used to present the Sel-MMSE-OSIC that can achieve ML diversity asymptotically.
+The minimum number of antennas selected by channel partition is given by (\ref{Nmin DMS}).
+
+First, we consider $16\times 16$ system with $4$-QAM modulation, Table.\ref{t16MIMO4QAM} shows the schemes considered, the corresponding results are presented in Fig.\ref{f16MIMO4QAM}, 
+\begin{table}[htb]
+\renewcommand{\arraystretch}{1.3}
+\caption{$16\times 16$ system $4$-QAM}
+\label{t16MIMO4QAM}
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+Scheme&number of antennas selected&Asymptotic diversity\\
+\hline 
+MDS&3&16\\
+\hline
+MAD-9&2&9\\
+\hline
+MAD-4&1&4\\
+\hline
+\end{tabular}
+\end{table}
+
+As shown in Fig.\ref{f16MIMO4QAM}, compared with MDS which can achieve ML performance asymptotically, MAD-9 has a small performance loss, while MAD-4's performance is inferior, at BER $10^{-5}$, the MAD-9 is about $0.8$dB worse than MDS, MAD-4 is about $1.8$dB worse than MDS, let $\kappa(\cdot)$ denote the number of list candidate generated by GPIC algorithm\cite{radji2009interference}, from Table.\ref{t16MIMO4QAM},
+we have $\frac{\kappa(MAD-9)}{\kappa(DMS)}=1/4$ and $\frac{\kappa(MAD-4)}{\kappa(DMS)}=1/16$.
+
+\begin{figure}[htb]
+\centering
+%\includegraphics[width=\textwidth]{16MIMO4QAM.eps}
+\def\svgwidth{\columnwidth}
+\input{16MIMO4QAM.pdf_tex}
+\caption{$16\times 16$ system $4$-QAM}
+\label{f16MIMO4QAM}
+\end{figure}
+
+The results for $16\times 16$ system with $16$-QAM modulation is shown in Fig.\ref{f16MIMO16QAM}, the information of the schemes considered is as the same as that in Talbe.\ref{t16MIMO4QAM}, From Fig.\ref{f16MIMO16QAM}, we can see that similar to the case of $4$-QAM system, MAD-9 has a very small performance loss comparing to DMS, at BER $2\times 10^{-5}$, MAD-9 is about $1.1$dB worse than MDS, while MAD-4 has about $3$dB  performance loss comparing to DMS.
+
+Furthermore,comparing to $4$-QAM system, the reduction of the number of list candidates provided by MAD scheme is more significant in $16$-QAM, $\frac{\kappa(MAD-9)}{\kappa(DMS)}=1/16$ and $\frac{\kappa(MAD-4)}{\kappa(DMS)}=1/256$.
+\begin{figure}[htb]
+\centering
+\def\svgwidth{\columnwidth}
+\input{16MIMO16QAM.pdf_tex}
+\caption{$16\times 16$ system $16$-QAM}
+\label{f16MIMO16QAM}
+\end{figure}
+
+\begin{table}[htb]
+\renewcommand{\arraystretch}{1.3}
+\caption{$32\times 32$ system $4$-QAM}
+\label{t32MIMO4QAM}
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+Scheme&number of antennas selected&Asymptotic diversity\\
+\hline 
+MAD-4&1&4\\
+\hline
+MAD-9&2&9\\
+\hline
+MAD-16&3&16\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{figure}[htb]
+\centering
+\def\svgwidth{\columnwidth}
+\input{32MIMO4QAM.pdf_tex}
+\caption{$32\times 32$ system $4$-QAM}
+\label{f32MIMO4QAM}
+\end{figure}
+Now we consider the performance of MAD in large systems, Fig.\ref{f32MIMO4QAM} shows the results for $32\times 32$ system with $4$-QAM.
+Table.\ref{t32MIMO4QAM} shows the information of the schemes, due to the time limitation, we just provide the results for MAD.
+As we can see in Fig\ref{f32MIMO4QAM}, although the asymptotic diversity of MAD-16 is much higher than that of MAD-9, at the BER region of interest, their performance difference is negligible, at BER=$3\times 10^{-4}$, the performance of MAD-9 is about $0.3$dB worse comparing to MAD-16, at BER=$3\times 10^{-5}$, the performance loss of MAD-9 is about $0.5$dB comparing to MAD-16.
+
+\section{Theoretical Analysis of Channel Hardening Phenomenon}
 \subsection{Preliminary}
@@
 \end{equation}
-$0\leq \phi_{om}\leq 1$, if $\phi_{om}$ is closer to 1, $\mathbf{H}$ is more closer to an orthogonal matrix. 
-\subsection{Introduction to Channel Hardening Phenomenon}
+$0\leq \phi_{om}\leq 1$, $\forall \mathbf{H}$, if $\phi_{om}$ is closer to 1, $\mathbf{H}$ is more closer to an orthogonal matrix. 
+%\subsection{Introduction to Channel Hardening Phenomenon}
 \subsection{Logarithmic Expectation of Orthogonality Measure}
@@
 Let $\Pi_{i}$ denotes the $i$th row of $\mathbf{H}$.
-$\Pi_{i}$ is a $N_{t}$-variate complex Gaussian random variable so does $\Pi_{i}^{H}$.
+$\Pi_{i}$ is a $N_{t}$-variate complex Gaussian random variable, so does $\Pi_{i}^{H}$.
 Therefore $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}=\sum_{i=1}^{N_{r}}\Pi_{i}^{H}\Pi_{i}\sim \mathbb{C}W_{N_{t}}(N_{r}, \mathbf{I})$.
@@
 \subsection{Probability Density Function of Orthogonality Measure}
-\section{Simplified Channel Partition based on Orthogonality Measure}
-\section{Computer Simulations}
-\subsection{Full Loaded Systems}
-\subsection{Systems with Different Loading Factors}
+In this section, we derive the probability distribution of $\phi_{om}$.
+First, let's consider an alternative form of (\ref{OM}), do QR factorization to $\mathbf{H}$, $\mathbf{H}=\mathbf{Q}\mathbf{R}$\cite{watkins2004fundamentals}, where $\mathbf{Q}\in\mathbb{C}^{N_{r}\times N_{t}}$ is a unitary matrix and $\mathbf{R}\in\mathbb{C}^{N_{t}\times N_{t}}$ is an upper triangular matrix.
+Thus $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}=\mathbf{R}^{H}\mathbf{R}$.
+Let $r_{ji}, j\leq i$ denote the component of $\mathbf{R}$ at $j$th row and $i$th column, $r^{*}_{ji}$ denotes the conjugate of $r_{ji}$, we have
+\begin{equation}
+det(\mathbf{W})=det(\mathbf{R}^{H}\mathbf{R})=det(\mathbf{R}^{H})det(\mathbf{R})\\=\prod_{i=1}^{N_{t}}r_{ii}^{*}\prod_{i=1}^{N_{t}}r_{ii}=\prod_{i=1}^{N_{t}}|r_{ii}|^{2},
+\label{alternative wishart}
+\end{equation}
+Furthermore, let $\mathbf{R}_{i}$ denote the $i$th column of $\mathbf{R}$, $\mathbf{W}_{ii}$ denote the $i$th diagonal component of $\mathbf{W}$, we have
+\begin{equation}
+\mathbf{W}_{ii}=||\mathbf{h}_{i}||^{2}=||\mathbf{R}_{i}||^{2}=\sum_{j<i}|r_{ji}|^{2}+|r_{ii}|^{2},
+\label{alternative wishart diagonal}
+\end{equation}
+based on (\ref{alternative wishart}) and (\ref{alternative wishart diagonal}), (\ref{OM}) can be rewritten as 
+\begin{equation}
+\phi_{om}=\prod_{i=1}^{N_{t}}(\frac{|r_{ii}|^{2}}{|r_{ii}|^{2}+\sum_{j<i}|r_{ji}|^{2}}).
+\label{alternative OM}
+\end{equation}
+Based on \cite{nagar2011expectations}, given $\mathbf{W}\sim \mathbb{C}W_{N_{t}}(N_{r}, \mathbf{I}_{N_{t}})$ and $\mathbf{W}=\mathbf{R}^{H}\mathbf{R}$, we have $1\leq j\leq i\leq N_{t}$, $r_{ji}$ are mutually independent distributed.
+Furthermore $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma(N_{r}-i+1,1)$ .
+Because $|r_{ji}|\sim Rayleigh(1/\sqrt{2})$, $\sum_{j<i}|r_{ji}|^{2}\sim Gamma(i-1, 1)$.
+Define
+\begin{IEEEeqnarray}[\relax]{l}
+\alpha_{i}=|r_{ii}|^{2}\sim Gamma(k_{1}^{i},1),\quad k_{1}^{i}=N_{r}-i+1,\quad i=1,2\ldots N_{t}\\
+\beta_{i}=\sum_{j<i}|r_{ji}|^{2}\sim Gamma(k_{2}^{i},1),\quad k_{2}^{i}=i-1, \quad i=1,2\ldots N_{t}
+\end{IEEEeqnarray}
+$\alpha_{i}$ and $\beta_{i}$ are independent Gamma random variables, from \cite{gupta2004handbook}, if $X\sim Gamma(k_{1},\theta)$ and $Y\sim Gamma(k_{2},\theta)$, then $\frac{X}{X+Y}\sim Beta(k_{1},k_{2})$, where $Beta(k_{1}, k_{2})$ denotes Beta distribution with shape parameters $k_{1}$ and $k_{2}$.
+Therefore $\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}\sim Beta(k^{i}_{1}, k^{i}_{2})$.
+Define $\eta_{i}=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}, i=1,2,\ldots, N_{t}$, $\eta_{i}$ are mutually independent Beta random variables, Therefore (\ref{alternative OM}) can be rewritten as
+  \begin{equation}
+  \phi_{om}=\prod_{i=1}^{N_{t}}\eta_{i},
+  \label{product beta OM}
+  \end{equation}
+Thus $\phi_{om}$ is the product of $N_{t}$ independent Beta random variables, the pdf of $\phi_{om}$ is given by 
+\begin{equation}
+f_{\phi_{om}}(\rho)=\sum_{\mathbf{j}}\{[\prod_{i=1}^{N_{t}}c(k_{1}^{i},k_{2}^{i}, j_{i})]U(\rho|\mathbf{k}_{1}+\mathbf{j})\},
+\label{pdf of OM}
+\end{equation}
+where $\sum_{\mathbf{j}}=\sum_{j_{1}}\sum_{j_{2}}\ldots\sum_{j_{N_{t}}}$, $j_{i}\in [0,1,\ldots, k_{2}^{i}-1]$.
+$c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j_{i}}$ $k_{2}^{i}-1\choose j_{i}$ $[(k_{1}^{i}+j_{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes Beta function with parameters $\alpha$ and $\beta$.
+$\mathbf{k}_{1}+\mathbf{j}=[k_{1}^{1}+j_{1}, k_{1}^{2}+j_{2},\ldots, k_{1}^{N_{t}}+j_{N_{t}}]$,
+\begin{equation}
+U(\rho|\mathbf{k}_{1}+\mathbf{j})=\rho^{-1}\prod_{i=1}^{N_{t}}(k_{1}^{i}+j_{i})\sum_{i=1}^{N_{t}}[\rho^{k_{1}^{i}+j_{i}}/\prod_{j\neq i}^{N_{t}}(k_{1}^{j}+j_{j}-k_{1}^{i}-j_{i})],
+\label{auxiliary pdf of OM}
+\end{equation}
+Proof: see Appendix \ref{proof pdf of OM}.
+
+If a Beta random variable $\nu\sim Beta(k_{1}, k_{2})$, then $\mathbb{E}[\ln(\nu)]=\psi(k_{1})-\psi(k_{1}+k_{2})$\cite{papoulis2002probability}, take logarithmic expectation of (\ref{product beta OM}), we have
+\begin{equation}
+\mathbb{E}[\ln(\phi_{om})]=\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(\eta_{i})]=\sum_{i=1}^{N_{t}}[\psi(k^{i}_{1})-\psi(k^{i}_{1}+k^{i}_{2})]=\sum_{i=1}^{N_{t}}[\psi(N_{r}-i+1)-\psi(N_{r})],
+\label{final log expectation OM beta}
+\end{equation}
+which is consistent with (\ref{final log expectation OM}).
+
+\subsection{Computer Simulations}
+Computer simulations are made to demonstrate the correctness of $\mathbb{E}[\ln(\phi_{om})]$ in (\ref{final log expectation OM}).
+The experiments are performed by Matlab, on a desktop with I5-4th generation CPU, quad cores, 3.2GHz clock rate.
+
+Different sizes of channel matrices are considered, with $5\leq N_{r}\leq 200$ and $5\leq N_{t}\leq N_{r}$.
+The theoretical logarithmic expectation of $\phi_{om}$, denoted by $\mathbb{E}[\ln(\phi_{om})]_{t}$ is calculated based on (\ref{final log expectation OM}), the result is shown in Fig.\ref{flogOMt}.
+The empirical estimation of the logarithmic expectation of $\phi_{om}$, denoted by $\mathbb{E}[\ln(\phi_{om})]_{em}$, are calculated based on taking average over $10^{5}$ independent channel realizations of each size of channel matrix.
+In each realization, the channel matrix are generated randomly, each component of the channel matrix is CSCG random variable with unit variance.
+The result is shown in Fig.\ref{flogOMem}.
+\begin{figure}[htb]
+\centering
+\def\svgwidth{\columnwidth}
+\input{logOMt.pdf_tex}
+\caption{Theoretical logarithmic expectation of $\phi_{om}$}
+\label{flogOMt}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\def\svgwidth{\columnwidth}
+\input{logOMem.pdf_tex}
+\caption{Empirical estimation of the logarithmic expectation of $\phi_{om}$}
+\label{flogOMem}
+\end{figure}
+
+The variance between $\mathbb{E}[\ln(\phi_{om})]_{t}$ and $\mathbb{E}[\ln(\phi_{om})]_{t}$, denoted by $\upsilon$, is also calculated by \begin{equation}
+\upsilon=\frac{1}{m}\sum_{i=1}^{m}(\mathbb{E}[\ln(\phi_{om})]^{i}_{em}-\mathbb{E}[\ln(\phi_{om})]^{i}_{t})^{2},
+\label{variance OM}
+\end{equation} 
+where $m$ is the number of the different sizes of channel matrix considered. By simulation $\upsilon=8.0116\times 10^{-4}$.
+%\section{Simplified Channel Partition based on Orthogonality Measure}
+%\section{Computer Simulations}
+%\subsection{Full Loaded Systems}
+%\subsection{Systems with Different Loading Factors}
 
@@
 The conclusion goes here.
+\newpage
 
@@
 Let $\mathbf{A}\in \mathbb{C}^{m\times m}$, $A\sim \mathbb{C}W_{m}(n, \mathbf{\Sigma})$, According to the definition of complex Wishart matrix, it is obvious $\mathbf{A}$ is Hermition positive definite matrix (i.e., $\mathbf{A}=\mathbf{A}^{H}>0$).
+Define $etr(\mathbf{A})=e^{tr(\mathbf{A})}$, $tr(\mathbf{A})=\mathbf{A}_{11}+\mathbf{A}_{22}+\cdots+\mathbf{A}_{mm}$.
 
@@
 where $\psi(k)$ denotes Digamma function.
-
+\section{}\label{proof pdf of OM}
+Define $x=\prod_{i=1}^{n}x_{i}$,
+$x_{1}, x_{2}, \ldots, x_{n}$ are independent Beta random variables, where $x_{i}\sim Beta(k_{1}^{i}, k_{2}^{i})$, the pdf of $x_{i}$ is given by 
+\begin{equation}
+f_{x_{i}}(\rho)=\frac{1}{\mathbb{B}(k_{1}^{i}, k_{2}^{i})}\rho^{k_{1}^{i}-1}(1-\rho)^{k_{2}^{i}-1},
+\label{pdf beta}
+\end{equation}
+where $\mathbb{B}(k^{i}_{1}, k_{2}^{i})$ denotes Beta function with parameters $k_{1}^{i}$ and $k_{2}^{i}$.
+Define $y_{i}=-\ln(x_{i})=g(x_{i})$, Based on Jacobian transformation, we have 
+\begin{equation}
+f_{y_{i}}(\rho)=|\frac{dy_{i}}{dx_{i}}|^{-1}f_{x_{i}}(g^{-1}(\rho))=\frac{1}{\mathbb{B}(k_{1}^{i},k_{2}^{i})}e^{-k_{1}^{i}\rho}(1-e^{-\rho})^{k_{2}^{i}-1}.
+\label{pdf log beta}
+\end{equation}
+(\ref{pdf log beta}) can be alternatively expressed as \cite{bhargava1981distribution}
+\begin{equation}
+f_{y_{i}}(\rho)=\sum_{j_{i}=0}^{k_{2}^{i}-1}c(k_{1}^{i},k_{2}^{i}, j_{i})(k_{1}^{i}+j_{i})e^{-(k_{1}^{i}+j_{i})\rho},
+\label{pdf log beta alternative}
+\end{equation} 
+where $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j_{i}}$ $k_{2}^{i}-1\choose j_{i}$ $[(k_{1}^{i}+j_{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $j_{i}\in [0,1,\ldots, k_{2}^{i}-1]$,
+From (\ref{pdf log beta alternative}), one can conclude that $f_{y_{i}}(\rho)$ is a weighted summation of the pdf of exponential distributions.
+
+If $\tau_{1}, \tau_{2}, \ldots, \tau_{n}$ are independent exponential random variables, where $\tau_{i}\sim exp(t_{i})$, the pdf of $\tau_{i}$ is given by 
+\begin{equation}
+f_{\tau_{i}}(\rho)=t_{i}e^{-t_{i}\rho}, \quad\rho\geq 0, 
+\label{pdf exp}
+\end{equation}
+define $\tau=\sum_{i=1}^{n}\tau_{i}$, by induction, the pdf of $\tau$ is given by\cite{bhargava1981distribution}
+\begin{equation}
+f_{\tau}(\rho)=f(\rho|\mathbf{t})=\prod_{i=1}^{n}t_{i}\sum_{i=1}^{n}[exp(-t_{i}\rho)/\prod_{j\neq i}^{j=n}(t_{j}-t_{i})],
+\label{pdf of sum exp}
+\end{equation}
+where $\mathbf{t}=[t_{1}, t_{2}, \ldots, t_{n}]$.
+Define $y=\sum_{i=1}^{n}y_{i}=-\ln(\prod_{i=1}^{n}x_{i})=-\ln(x)$.
+Based on (\ref{pdf log beta alternative}) and (\ref{pdf of sum exp}), the pdf of $y$ is given by\cite{bhargava1981distribution}
+\begin{equation}
+f_{y}(\rho)=\sum_{\mathbf{j}}\{[\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i}, j_{i})]f(\rho|\mathbf{k_{1}}+\mathbf{j})\},
+\label{pdf of y}
+\end{equation}
+where $\sum_{\mathbf{j}}=\sum_{j_{1}}\sum_{j_{2}}\ldots \sum_{j_{n}}$, $j_{i}\in [0,1,\ldots, k^{i}_{2}-1]$, $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j_{1}, k_{1}^{2}+j_{2} \ldots k_{1}^{n}+j_{n}]$.
+Based on (\ref{pdf of y}) and $x=e^{-y}=G(y)$, using Jacobian transformation, the pdf of $x$ is given by
+\begin{equation}
+f_{x}(\rho)=f_{y}(G^{-1}(\rho))|\frac{dx}{dy}|^{-1}=f_{y}(-\ln(\rho))\rho^{-1}=\sum_{\mathbf{j}}\{[\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i}, j_{i})]f(-\ln(\rho)|\mathbf{k}_{1}+\mathbf{j})\rho^{-1}\},
+\label{pdf of x1}
+\end{equation} 
+define 
+\begin{equation}
+U(\rho|\mathbf{k}_{1}+\mathbf{j})=f(-\ln(\rho)|\mathbf{k}_{1}+\mathbf{j})\rho^{-1},
+\label{definition of U}
+\end{equation}
+Thus (\ref{pdf of x1}) can be rewritten as 
+\begin{equation}
+f_{x}(\rho)=\sum_{\mathbf{j}}\{[\prod_{i=1}^{n}c(k_{1}^{i},k_{2}^{i}, j_{i})]U(\rho|\mathbf{k}_{1}+\mathbf{j})\}.
+\label{final pdf of x}
+\end{equation}
 % use section* for acknowledgment
@@
 % by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
+%\ifCLASSOPTIONcaptionsoff
+ % \newpage
+%\fi
 
@@
 %\enlargethispage{-5in}
+\newpage
 \bibliographystyle{IEEEtran}

### 2015-12-22 Report revised May 12 2015/Report_draft.tex
Report Dec initial

@@
 
-Because $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$, do QR factorization to $\mathbf{H}$ 
+Because $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}$, do QR factorization to $\mathbf{H}$\cite{watkins2004fundamentals}
 \begin{equation}
@@
  \end{equation}
-where $\mathbf{Q}\in\mathbb{C}^{N_{r}\times N_{t}}$ is a unitary matrix and $\mathbf{R}\in\mathbb{C}^{N_{t}\times N_{t}}$ is the upper triangular matrix.
+where $\mathbf{Q}\in\mathbb{C}^{N_{r}\times N_{t}}$ is a unitary matrix and $\mathbf{R}\in\mathbb{C}^{N_{t}\times N_{t}}$ is an upper triangular matrix.
 Using (\ref{formula5}), we have $\mathbf{W}=\mathbf{R}^{H}\mathbf{R}$.
-$r_{ii}$ denotes the $i$ th diagonal component of $\mathbf{R}$, thus $det(\mathbf{W})$ can be rewritten as:
+$r_{ij}$ denotes the component of $\mathbf{R}$ at $i$th row and $j$th column, thus $det(\mathbf{W})$ can be rewritten as:
 \begin{equation}
-det(\mathbf{W})=det(\mathbf{R}^{H}\mathbf{R})=det(\mathbf{R}^{H})det(\mathbf{R})\\=\prod_{i=1}^{N_{t}}r_{ii}^{H}\prod_{i=1}^{N_{t}}r_{ii}=\prod_{i=1}^{N_{t}}|r_{ii}|^{2}.
+det(\mathbf{W})=det(\mathbf{R}^{H}\mathbf{R})=det(\mathbf{R}^{H})det(\mathbf{R})\\=\prod_{i=1}^{N_{t}}r_{ii}^{*}\prod_{i=1}^{N_{t}}r_{ii}=\prod_{i=1}^{N_{t}}|r_{ii}|^{2},
 \label{formula6}
 \end{equation} 
+where $(\cdot)^{*}$ denotes conjugate operation. 
 Notice that $\mathbf{R}$ can be viewed as the Cholesky factorization of $\mathbf{W}$. Therefore, we have
@@
 \end{equation}
-All the components in $\mathbf{R}$ are independently distributed and $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma(N_{r}-i+1,1)$ \cite{nagar2011expectations}.
+Based on \cite{nagar2011expectations}, for $1\leq j\leq i\leq N_{t}$, $r_{ji}$ are mutually independent distributed.
+Furthermore $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma(N_{r}-i+1,1)$ .
 Because $|r_{ji}|\sim Rayleigh(1/\sqrt{2})$, $\sum_{j<i}|r_{ji}|^{2}\sim Gamma(i-1, 1)$.
@@
 \begin{equation}
-f_{y_{i}}(\rho)=\sum_{j^{i}=0}^{k_{2}^{i}-1}c(k_{1}^{i},k_{2}^{i}, j^{i})(k_{1}^{i}+j^{i})exp(-(k_{1}^{i}+j^{i})\rho),
+f_{y_{i}}(\rho)=\sum_{j_{i}=0}^{k_{2}^{i}-1}c(k_{1}^{i},k_{2}^{i}, j_{i})(k_{1}^{i}+j_{i})e^{-(k_{1}^{i}+j_{i})\rho},
 \label{Appendequal15}
 \end{equation} 
-where $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j^{i}}$ $k_{2}^{i}-1\choose j^{i}$ $[(k_{1}^{i}+k_{2}^{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
+where $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j_{i}}$ $k_{2}^{i}-1\choose j_{i}$ $[(k_{1}^{i}+j_{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes beta function.
+The pdf of $y_{i}$ can be viewed as the weighted summation of pdf of exponential distribution.
 Based on the lemma 1 of \cite{bhargava1981distribution}, if $a_{1}, a_{2}, \cdots a_{n}$ are independent exponentially distributed random variables, with pdf given by
@@
 \end{equation}
-where $t=[t_{1}, t_{2}, \cdots t_{n}]$.
-The pdf of $y_{i}$ can be viewed as the weighting summation of exponential distribution functions, define $y=\sum_{i=1}^{n}y_{i}$, based on (\ref{Appendequal17}), the pdf of $y$ is given by
+where $t=[t_{1}, t_{2}, \cdots t_{n}]$. define $y=\sum_{i=1}^{n}y_{i}$, based on (\ref{Appendequal17}), the pdf of $y$ is given by
 \begin{equation}
@@
  \end{equation}
-
 \end{appendices}

### 2015-12-22 Report Dec 2015/Figures/Figure.m

@@ -30,37 +30,37 @@ BER_MAD_32_4_16=[0.229358, 0.190434, 0.146927, 0.0955453, 0.0448656, 0.0129797, 
 
 %% Figure plotting
 figure (1)
-semilogy([0:2:16], BER_MDS_16_4, '-*', 'MarkerSize', 5), xlabel('SNR (dB)'), ylabel('BER');
+semilogy([0:2:16], BER_MDS_16_4, '-*', 'MarkerSize', 8), xlabel('SNR (dB)'), ylabel('BER');
 hold on;
-semilogy([0:2:18], BER_MAD_16_4_4, '-^', 'MarkerSize', 5), xlabel('SNR (dB)'), ylabel('BER');
+semilogy([0:2:18], BER_MAD_16_4_4, '-^', 'MarkerSize', 8), xlabel('SNR (dB)'), ylabel('BER');
 hold on;
-semilogy([0:2:16], BER_MAD_16_4_9, '-+', 'MarkerSize',5), xlabel('SNR (dB)'), ylabel('BER');
+semilogy([0:2:16], BER_MAD_16_4_9, '-+', 'MarkerSize',8), xlabel('SNR (dB)'), ylabel('BER');
 hold on;
-title('16X16 system 4QAM');
-hold on;
-legend('MDS', 'MAD (4)', 'MAD (9)');
+% title('16X16 system 4QAM');
+% hold on;
+legend('MDS', 'MAD-4', 'MAD-9');
 hold off;
 
 figure (2)
-semilogy([8:2:22], BER_MDS_16_16, '-*', 'MarkerSize', 5), xlabel('SNR (dB)'), ylabel('BER');
+semilogy([8:2:22], BER_MDS_16_16, '-*', 'MarkerSize', 8), xlabel('SNR (dB)'), ylabel('BER');
 hold on;
-semilogy([8:2:26], BER_MAD_16_16_4, '-^', 'MarkerSize', 5), xlabel('SNR (dB)'), ylabel('BER');
+semilogy([8:2:26], BER_MAD_16_16_4, '-^', 'MarkerSize', 8), xlabel('SNR (dB)'), ylabel('BER');
 hold on;
-semilogy([8:2:24], BER_MAD_16_16_9, '-+', 'MarkerSize',5), xlabel('SNR (dB)'), ylabel('BER');
[…]

### 2015-12-23 Report Dec 2015/Report.tex
Report Dec first revision

@@
 %\hfill September 17, 2014
-Consider a uncoded complex Large-Scale MIMO (LS-MIMO) uplink spatial multiplexing (SM) system with $N_{t}$ users, where each is equipped with one transmit antenna.
+Consider an uncoded complex Large-Scale MIMO (LS-MIMO) uplink spatial multiplexing (SM) system with $N_{t}$ users, each is equipped with one transmit antenna.
 The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
@@
 BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
-The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{r}\times N_{t}$.
+The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{t}\times N_{t}$.
 Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, $\mathbf{H}_{ij}$ denotes the component of $\mathbf{H}$ at $i$th row and $j$th column, representing the channel response from $i$th receive antenna to the $j$th transmit antenna.
-Each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian (CSCG) random variable with unit variance.
+Each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian (CSCG) random variable with unit variance, denoted by $\mathbf{H}_{ij}\sim \mathbb{C}N(0,1)$.
 Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
@@
 
-The Optimal (in a sense of lowest average error probability) Maximum Likelihood Detector (MLD) for MIMO system is given by
-\begin{equation}
-\hat{\mathbf{s}}^{ML}=\min_{\mathbf{s}\in \mathbb{O}^{N_{t}}}||\mathbf{y}-\mathbf{H}\mathbf{s}||^{2},
+The optimal (in a sense of lowest average error probability) Maximum Likelihood Detector (MLD) for MIMO system is given by
+\begin{equation}
+\hat{\mathbf{s}}^{ML}=\arg\min_{\hat{\mathbf{s}}\in \mathbb{O}^{N_{t}}}||\mathbf{y}-\mathbf{H}\hat{\mathbf{s}}||^{2},
 \label{MLD}
 \end{equation}
-where $||\cdot||$ denotes the 2-norm operation, therefore from (\ref{MLD}), the solution of MLD is the $\hat{\mathbf{s}}$ that can generate the minimum Euclidean distance between vector $\mathbf{y}$ and $\mathbf{H}\mathbf{s}$.
-
-Consider an alternative representation of MLD principle, let $\mathbf{H}_{1}\in \mathbb{C}^{N_{r}\times N}$ denotes a sub matrix composed of $N$ columns from $\mathbf{H}$, let $\mathbf{s}_{1}\in \mathbb{C}^{N}$ denote the sub symbol vector whose components are transmitted from the users corresponding to $\mathbf{H}_{1}$.
+where $||\cdot||$ denotes the 2-norm operation.
+From (\ref{MLD}), the solution of MLD is the $\hat{\mathbf{s}}$ that can generate the minimum Euclidean distance between vector $\mathbf{y}$ and $\mathbf{H}\mathbf{s}$.
+
+Consider an alternative representation of MLD principle, let $\mathbf{H}_{1}\in \mathbb{C}^{N_{r}\times N}$ denotes a sub matrix composed of $N$ columns from $\mathbf{H}$, where $1\leq N\leq N_{t}$, let $\mathbf{s}_{1}\in \mathbb{C}^{N}$ denote the sub symbol vector whose components are transmitted from the users corresponding to $\mathbf{H}_{1}$.
 Similarly, let $\mathbf{H}_{2}\in \mathbb{C}^{N_{r}\times (N_{t}-N)}$ denotes the sub matrix composed of the remaining columns from $\mathbf{H}$ and $\mathbf{s}_{2}\in \mathbb{C}^{(N_{t}-N)}$ is the sub symbol vector whose components are transmitted by the users corresponding to $\mathbf{H}_{2}$.
@@
 \begin{equation}
-[\tilde{k}, \tilde{q}]=\min_{k\in [1,2\ldots K]}\min_{q\in [1,2,\ldots, Q]}||\mathbf{y}-\mathbf{H}_{1}\hat{\mathbf{s}}^{k}_{1}-\mathbf{H}_{2}\hat{\mathbf{s}}^{q}_{2}||^{2},\\
+[\tilde{k}, \tilde{q}]=\arg\min_{k\in [1,2\ldots K]}\min_{q\in [1,2,\ldots, Q]}||\mathbf{y}-\mathbf{H}_{1}\hat{\mathbf{s}}^{k}_{1}-\mathbf{H}_{2}\hat{\mathbf{s}}^{q}_{2}||^{2},\\
 \mathbf{s}^{ML}_{1}=\hat{\mathbf{s}}^{\tilde{k}}_{1}, \mathbf{s}^{ML}_{2}=\hat{\mathbf{s}}^{\tilde{q}}_{2},
@@
 \begin{equation}
-\hat{\mathbf{x}}_{2}^{k}=\min_{\hat{\mathbf{s}}_{2}^{q}\in [\hat{\mathbf{s}}_{2}^{1},\hat{\mathbf{s}}_{2}^{3}\ldots, \hat{\mathbf{s}}_{2}^{Q}]}||\mathbf{y}^{k}-\mathbf{H}_{2}\hat{\mathbf{s}}_{2}^{q}||^{2},
+\hat{\mathbf{x}}_{2}^{k}=\arg\min_{\hat{\mathbf{s}}_{2}^{q}\in [\hat{\mathbf{s}}_{2}^{1},\hat{\mathbf{s}}_{2}^{3}\ldots, \hat{\mathbf{s}}_{2}^{Q}]}||\mathbf{y}^{k}-\mathbf{H}_{2}\hat{\mathbf{s}}_{2}^{q}||^{2},
 \label{second step alternative MLD}
@@
 \begin{equation}
-\tilde{k}=\min_{k\in [1,2,\ldots, K]}||\mathbf{y}^{k}-\mathbf{H}_{2}\hat{\mathbf{x}}_{2}^{k}||^{2},
+\tilde{k}=\arg\min_{k\in [1,2,\ldots, K]}||\mathbf{y}^{k}-\mathbf{H}_{2}\hat{\mathbf{x}}_{2}^{k}||^{2},
 \label{third step alternative MLD}
@@
 Based on the alternative form of MLD in (\ref{alternative MLD})-(\ref{third step alternative MLD}), General Parallel Interference Cancellation (GPIC) algorithm first generate a list of symbol vector candidates and then choose the candidate with the minimum Euclidean distance as the solution.
-To elaborate further, GPIC first generate a list of symbol vector candidate by exhaustive search for all the possible $\hat{\mathbf{s}}_{1}$, then rather than performing exhaustive search in (\ref{second step alternative MLD}), GPIC exploit low complexity sub optimal linear detectors (i.e., zeros forcing (ZF) and minimum mean square error (MMSE)) and their successive interference cancellation (SIC) counterparts to get the estimation of $\mathbf{s}_{2}$, for sake of simplicity, hereinafter we use LD/SIC.
+To elaborate further, GPIC first generates a list of symbol vector candidate by exhaustive search for all the possible $\hat{\mathbf{s}}_{1}$ as shown in (\ref{first step alternative MLD}), then rather than performing exhaustive search in (\ref{second step alternative MLD}), GPIC exploits low complexity sub optimal linear detectors (i.e., zeros forcing (ZF) and minimum mean square error (MMSE)) and their successive interference cancellation (SIC) counterparts to get the estimation of $\mathbf{s}_{2}$.
+For sake of simplicity, hereinafter we use LD/SIC.
 Then the best candidate in the list with the minimum Euclidean distance is chosen as the solution.
 
-Performance analysis of GPIC algorithm is provided in \cite{radji2009interference}, here we briefly conclude the main results in \cite{radji2009interference}, at the receiving side, the frame error is defined as there is at least one erroneous symbol in the estimation of transmitted symbol vector.
+Performance analysis of GPIC algorithm is provided in \cite{radji2009interference}, here we briefly conclude the main results in \cite{radji2009interference}.
+At the receiving side, the frame error is defined as there is at least one erroneous symbol in the estimation of transmitted symbol vector.
 Let $P_{e}$ denotes the average frame error probability.
@@
 \end{equation}
-Let $P_{e}^{ML}$ denotes the average frame error probability of MLD, and $P_{e2}=\mathbb{E}_{\mathbf{H}_{2}, \mathbf{s}_{2}}(Pr(\hat{\mathbf{s}}^{k_{1}}_{2}\neq \mathbf{s}_{2}|\mathbf{H}_{2}, \mathbf{s}_{2}))$, where $P_{r}(A)$ denotes the probability that a event A occurs, $\hat{\mathbf{s}}_{1}^{k_{1}}=\mathbf{s}_{1}$, therefore $P_{e2}$ is the average frame error probability of the LD/SICs for the sub system in which the interference from the users that transmitted $\mathbf{s}_{1}$ are perfectly cancelled from the observation $\mathbf{y}$.
+Let $P_{e}^{ML}$ denotes the average frame error probability of MLD, The average frame error probability of GPIC algorithm $P_{et}=\mathbb{E}_{\mathbf{H}, \mathbf{s}}[Pr(\hat{\mathbf{s}}\neq \mathbf{s}|\mathbf{H}, \mathbf{s})]$ and $P_{e2}=\mathbb{E}_{\mathbf{H}_{2}, \mathbf{s}_{2}}(Pr(\hat{\mathbf{s}}^{k_{1}}_{2}\neq \mathbf{s}_{2}|\mathbf{H}_{2}, \mathbf{s}_{2}))$, where $P_{r}(A)$ denotes the probability that a event A occurs, $\hat{\mathbf{s}}_{1}^{k_{1}}=\mathbf{s}_{1}$, therefore $P_{e2}$ is the average frame error probability of the LD/SICs for the sub system in which the interference from the users that transmitted $\mathbf{s}_{1}$ are perfectly cancelled from the observation $\mathbf{y}$.
 given by
@@
 \begin{equation}
-\mathbf{y}^{k1}=\mathbf{H}_{2}\mathbf{s}_{2}+\mathbf{n},
+\mathbf{y}^{k1}=\mathbf{H}_{2}\mathbf{s}_{2}+\mathbf{H}_{1}(\mathbf{s}_{1}-\hat{\mathbf{s}}_{1}^{k1})+\mathbf{n}=\mathbf{H}_{2}\mathbf{s}_{2}+\mathbf{n},
 \label{sub MIMO system}
 \end{equation} 
-The average frame error probability of GPIC algorithm $P_{et}$ is bounded by 
+Based on \cite{radji2009interference}, $P_{et}$ is bounded by 
 \begin{equation}
@@
 \end{equation}
-Let $d_{t}$ denotes the diversity order of GPIC algorithm, now consider the following conditions
+Let $d_{t}$ denotes the overall diversity order of GPIC algorithm, now consider the following conditions
 \begin{itemize}
@@
 \end{itemize} 
-Therefore when $d_{2}\geq N_{r}$, GPIC algorithm can achieve ML performance asymptotically, when $d_{2}<N_{r}$, the diversity order that GPIC can achieve at high SNR region is equal to that of LD/SICs, in \cite{radji2009interference}, the authors employ diversity maximization selection (MDS) scheme for channel partition, which is proposed in \cite{zhang2006diversity}.
-The optimal diversity order can be guaranteed with low complexity for conventional MIMO systems.
-
-To elaborate further, for a given number of antennas chosen at the channel partition stage $N$, there is $N_{u}={N_{t}\choose N}$ possible combinations of $[\mathbf{H}_{1}, \mathbf{H}_{2}]$, according to MDS principle, the maximum diversity order of LD/SIC is achieved by choosing the subset $\mathbf{H}_{2}$ that has the strongest weakest substream, in a sense of post processing SNR.
-Therefore, when using MMSE/SIC as the sub optimal detector, the subset $\mathbf{H}^{opt}_{2}$ selected based on DMS principle should be\cite{zhang2006diversity}
+Therefore when $d_{2}\geq N_{r}$, GPIC algorithm can achieve ML performance asymptotically, when $d_{2}<N_{r}$, the diversity order that GPIC can achieve at high SNR region is equal to that of LD/SICs.
+In \cite{radji2009interference}, the authors employ diversity maximization selection (DMS) scheme for channel partition, which is proposed in \cite{zhang2006diversity}.
+The optimal diversity order can be guaranteed with low complexity for conventional small MIMO systems.
+
+To elaborate further, for a given number of antennas chosen at the channel partition stage $N$, there is $N_{u}={N_{t}\choose N}$ possible combinations of $[\mathbf{H}_{1}, \mathbf{H}_{2}]$.
+According to DMS principle, the maximum diversity order of LD/SIC is achieved by choosing the subset $\mathbf{H}_{2}$ that has the strongest weakest substream, in a sense of post processing SNR.
+Therefore, when using LD/SIC detectors as the sub optimal detector, the subset $\mathbf{H}^{opt}_{2}$ selected based on DMS principle should be\cite{zhang2006diversity}
 \begin{IEEEeqnarray}[\relax]{l}
 \mathbf{H}^{opt}_{2}=\mathbf{H}^{p}_{2},\\
-p=\min_{j=1,2,\ldots, N_{u}}\theta_{j},\\
+p=\arg\min_{j=1,2,\ldots, N_{u}}\theta_{j},\\
 \theta_{j}=\max_{k=1,2,\ldots, N_{t}-N}((\mathbf{H}_{2}^{j})^{H}\mathbf{H}_{2}^{j}+SNR^{-1}\mathbf{I})_{kk}^{-1},\quad \mathbf{H}_{2}^{j}\in[\mathbf{H}_{2}^{1}, \mathbf{H}_{2}^{2}, \ldots, \mathbf{H}_{2}^{N_{u}}];
@@
 
-Therefore, here we consider minimum achievable diversity (MAD) principle, which sacrifices redundant diversity gain in LS-MIMO, in order to reduce the complexity.
+Therefore, here we consider minimum achievable diversity (MAD) principle, which can reduce the detection complexity by sacrificing redundant asymptotic diversity gain in LS-MIMO.
 Let $d_{2MAD}$ denotes the diversity order of LD/SIC detectors, $\tilde{N}_{min}$ denotes the minimum number of antennas chosen by MAD principle.
@@
 \end{IEEEeqnarray}    
-where $N\in [1,2,\ldots, N_{t}]$, our goal is to find minimum $N$, denoted by $\tilde{N}_{min}$, that satisfy $f(N)\geq 0$. The two zeros points of quadratic function $f(N)$ are 
+where $N\in [1,2,\ldots, N_{t}]$, our goal is to find minimum $N$, that satisfy $f(N)\geq 0$. The two zeros points of quadratic function $f(N)$ are 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 
-First, we consider $16\times 16$ system with $4$-QAM modulation, Table.\ref{t16MIMO4QAM} shows the schemes considered, the corresponding results are presented in Fig.\ref{f16MIMO4QAM}, 
+First, we consider $16\times 16$ system with $4$-QAM modulation, Table.\ref{t16MIMO4QAM} shows the information of the schemes considered, the corresponding results are presented in Fig.\ref{f16MIMO4QAM},
 \begin{table}[htb]
 \renewcommand{\arraystretch}{1.3}
-\caption{$16\times 16$ system $4$-QAM}
+\caption{$16\times 16$ system}
 \label{t16MIMO4QAM}
@@
 
-Furthermore,comparing to $4$-QAM system, the reduction of the number of list candidates provided by MAD scheme is more significant in $16$-QAM, $\frac{\kappa(MAD-9)}{\kappa(DMS)}=1/16$ and $\frac{\kappa(MAD-4)}{\kappa(DMS)}=1/256$.
+Furthermore, compared with $4$-QAM systems, the reduction of the number of list candidates provided by MAD scheme is more significant in $16$-QAM systems, $\frac{\kappa(MAD-9)}{\kappa(DMS)}=1/16$ and $\frac{\kappa(MAD-4)}{\kappa(DMS)}=1/256$.
 \begin{figure}[htb]
@@
 Table.\ref{t32MIMO4QAM} shows the information of the schemes, due to the time limitation, we just provide the results for MAD.
-As we can see in Fig\ref{f32MIMO4QAM}, although the asymptotic diversity of MAD-16 is much higher than that of MAD-9, at the BER region of interest, their performance difference is negligible, at BER=$3\times 10^{-4}$, the performance of MAD-9 is about $0.3$dB worse comparing to MAD-16, at BER=$3\times 10^{-5}$, the performance loss of MAD-9 is about $0.5$dB comparing to MAD-16.
+As we can see in Fig.\ref{f32MIMO4QAM}, although the asymptotic diversity of MAD-16 is much higher than that of MAD-9, at the BER region of interest, their performance difference is negligible, at BER=$3\times 10^{-4}$, the performance of MAD-9 is about $0.3$dB worse comparing to MAD-16, at BER=$3\times 10^{-5}$, the performance loss of MAD-9 is about $0.5$dB comparing to MAD-16.
 
@@
 \subsection{Preliminary}
-Orthogonality deficiency $\phi_{od}$ measures  how orthogonal a matrix is \cite{ma2008performance}, which is defined by
+Orthogonality deficiency $\phi_{od}$ measures the orthogonality of a matrix\cite{ma2008performance}, which is defined by
 \begin{equation}
@@
 First we consider the first summand on the right hand of (\ref{log expectation OM}) $\mathbb{E}[\ln(det(\mathbf{W}))]$.
-Let $\mathbb{C}W_{m}(n, \Sigma)$ denotes complex Wishart distribution, which is the joint distribution of sample covariance matrix from multivariate complex Gaussian random variable\cite{goodman1963statistical}.
+Let $\mathbb{C}W_{m}(n, \Sigma)$ denote complex Wishart distribution, which is the joint distribution of sample covariance matrix from multivariate complex Gaussian random variable\cite{goodman1963statistical}.
 $n$ is the degree of freedom and $\Sigma\in \mathbb{C}^{m\times m}$ is the covariance matrix.
@@
 $\Pi_{i}$ is a $N_{t}$-variate complex Gaussian random variable, so does $\Pi_{i}^{H}$.
-Therefore $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}=\sum_{i=1}^{N_{r}}\Pi_{i}^{H}\Pi_{i}\sim \mathbb{C}W_{N_{t}}(N_{r}, \mathbf{I})$.
+Therefore $\mathbf{W}=\mathbf{H}^{H}\mathbf{H}=\sum_{i=1}^{N_{r}}\Pi_{i}^{H}\Pi_{i}\sim \mathbb{C}W_{N_{t}}(N_{r}, \mathbf{I}_{N_{t}})$.
 The logarithmic expectation of $det(\mathbf{W})$ is
@@
 \end{equation}
-$\Gamma(n)$ denotes Gamma function.
-Proof: see Appendix \ref{log expectation of OM}.
+$\Gamma(n)$ denotes Gamma function\cite{papoulis2002probability}.
+\proof: see Appendix \ref{log expectation of OM}.
 
@@
 \end{equation}
-proof: see Appendix \ref{proof log expectation gamma}.
-
-Based on (\ref{log expectation of wishart}) and (\ref{sum of log expectation gamma}), the logarithmic expectation of orthogonality measure $\phi_{om}$ is 
+\proof: see Appendix \ref{proof log expectation gamma}.
+
+Based on (\ref{log expectation OM}), (\ref{log expectation of wishart}) and (\ref{sum of log expectation gamma}), the logarithmic expectation of orthogonality measure $\phi_{om}$ is 
 \begin{equation}
@@
   \end{equation}
-Thus $\phi_{om}$ is the product of $N_{t}$ independent Beta random variables, the pdf of $\phi_{om}$ is given by 
+Thus $\phi_{om}$ is the product of $N_{t}$ independent Beta random variables, the p.d.f of $\phi_{om}$ is given by 
 \begin{equation}
@@
 \end{equation}
-Proof: see Appendix \ref{proof pdf of OM}.
+\proof{}: see Appendix \ref{proof pdf of OM}.
 
@@
 \subsection{Computer Simulations}
-Computer simulations are made to demonstrate the correctness of $\mathbb{E}[\ln(\phi_{om})]$ in (\ref{final log expectation OM}).
+Computer simulations are made to demonstrate the correctness of the results in this section.
 The experiments are performed by Matlab, on a desktop with I5-4th generation CPU, quad cores, 3.2GHz clock rate.
 
-Different sizes of channel matrices are considered, with $5\leq N_{r}\leq 200$ and $5\leq N_{t}\leq N_{r}$.
-The theoretical logarithmic expectation of $\phi_{om}$, denoted by $\mathbb{E}[\ln(\phi_{om})]_{t}$ is calculated based on (\ref{final log expectation OM}), the result is shown in Fig.\ref{flogOMt}.
+Different sizes of channel matrices are considered, with $5\leq N_{r}\leq 100$ and $5\leq N_{t}\leq N_{r}$.
+The theoretical logarithmic expectation of $\phi_{om}$, denoted by $\mathbb{E}[\ln(\phi_{om})]_{t}$ are calculated based on (\ref{final log expectation OM}), the result is shown in Fig.\ref{flogOMt}.
 The empirical estimation of the logarithmic expectation of $\phi_{om}$, denoted by $\mathbb{E}[\ln(\phi_{om})]_{em}$, are calculated based on taking average over $10^{5}$ independent channel realizations of each size of channel matrix.
@@
 
-The pdf of $\mathbf{A}$ can be written as\cite{nagar2011expectations}:
+The p.d.f. of $\mathbf{A}$ can be written as\cite{nagar2011expectations}:
 \begin{equation}
@@
 \end{equation}
-define $z=x/\theta$ and based on (\ref{AppendixB2}), (\ref{AppendixB3}) can be rewritten as
+define $z=x/\theta$, (\ref{AppendixB3}) can be rewritten as
+\begin{equation}
+\mathbb{E}[\ln(x)]=\ln(\theta)\frac{1}{\Gamma(k)}\int_{0}^{\infty}z^{k-1}e^{-z}dz+\frac{1}{\Gamma(k)}\int_{0}^{\infty}\ln(z)z^{k-1}e^{-z}dz,
+\label{AppendixB4}
+\end{equation}
+Based on (\ref{AppendixB2}), (\ref{AppendixB4}) can be rewritten as
 \begin{equation}
 \mathbf{E}[\ln(x)]=\ln(\theta)+\frac{1}{\Gamma(k)}\int_{0}^{\infty}\ln(z)z^{k-1}e^{-z}dz.
-\label{AppendixB4}
-\end{equation}
-Because $\frac{d(z^{k-1})}{dk}=\ln(z)z^{k-1}$, (\ref{AppendixB4}) can be rewritten as
+\label{AppendixB5}
+\end{equation}
+Because $\frac{d(z^{k-1})}{dk}=\ln(z)z^{k-1}$, (\ref{AppendixB5}) can be rewritten as
 \begin{equation}
 \mathbf{E}[\ln(x)]=\ln(\theta)+\frac{1}{\Gamma(k)}\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz,
-\label{AppendixB5}
+\label{AppendixB6}
 \end{equation}
@@
 \Gamma^{'}(k)=\frac{d}{dk}\int_{0}^{\infty}z^{k-1}e^{-z}dz,
-\label{AppendixB6}
-\end{equation}
-Thus (\ref{AppendixB5}) can be rewritten as
+\label{AppendixB7}
+\end{equation}
+Thus (\ref{AppendixB6}) can be rewritten as
 \begin{equation}
 \mathbf{E}(\ln(x))=\ln(\theta)+\frac{\Gamma^{'}(k)}{\Gamma(k)}=\ln(\theta)+\psi(k),
-\label{AppendixB6}
+\label{AppendixB8}
 \end{equation}
@@
 Define $x=\prod_{i=1}^{n}x_{i}$,
-$x_{1}, x_{2}, \ldots, x_{n}$ are independent Beta random variables, where $x_{i}\sim Beta(k_{1}^{i}, k_{2}^{i})$, the pdf of $x_{i}$ is given by 
+$x_{1}, x_{2}, \ldots, x_{n}$ are independent Beta random variables, where $x_{i}\sim Beta(k_{1}^{i}, k_{2}^{i})$, the p.d.f. of $x_{i}$ is given by 
 \begin{equation}
@@
 where $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j_{i}}$ $k_{2}^{i}-1\choose j_{i}$ $[(k_{1}^{i}+j_{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $j_{i}\in [0,1,\ldots, k_{2}^{i}-1]$,
-From (\ref{pdf log beta alternative}), one can conclude that $f_{y_{i}}(\rho)$ is a weighted summation of the pdf of exponential distributions.
-
-If $\tau_{1}, \tau_{2}, \ldots, \tau_{n}$ are independent exponential random variables, where $\tau_{i}\sim exp(t_{i})$, the pdf of $\tau_{i}$ is given by 
+From (\ref{pdf log beta alternative}), one can conclude that $f_{y_{i}}(\rho)$ is a weighted summation of the p.d.f. of exponential distributions.
+
+If $\tau_{1}, \tau_{2}, \ldots, \tau_{n}$ are independent exponential random variables, where $\tau_{i}\sim exp(t_{i})$, the p.d.f. of $\tau_{i}$ is given by 
 \begin{equation}
@@
 \end{equation}
-define $\tau=\sum_{i=1}^{n}\tau_{i}$, by induction, the pdf of $\tau$ is given by\cite{bhargava1981distribution}
-\begin{equation}
-f_{\tau}(\rho)=f(\rho|\mathbf{t})=\prod_{i=1}^{n}t_{i}\sum_{i=1}^{n}[exp(-t_{i}\rho)/\prod_{j\neq i}^{j=n}(t_{j}-t_{i})],
+define $\tau=\sum_{i=1}^{n}\tau_{i}$, by induction, the p.d.f of $\tau$ is given by\cite{bhargava1981distribution}
+\begin{equation}
+f_{\tau}(\rho)=f(\rho|\mathbf{t})=\prod_{i=1}^{n}t_{i}\sum_{i=1}^{n}[e^{-t_{i}\rho}/\prod_{j\neq i}^{j=n}(t_{j}-t_{i})],
 \label{pdf of sum exp}
@@
 Define $y=\sum_{i=1}^{n}y_{i}=-\ln(\prod_{i=1}^{n}x_{i})=-\ln(x)$.
-Based on (\ref{pdf log beta alternative}) and (\ref{pdf of sum exp}), the pdf of $y$ is given by\cite{bhargava1981distribution}
+Based on (\ref{pdf log beta alternative}) and (\ref{pdf of sum exp}), the p.d.f.
+of $y$ is given by\cite{bhargava1981distribution}
 \begin{equation}
@@
 where $\sum_{\mathbf{j}}=\sum_{j_{1}}\sum_{j_{2}}\ldots \sum_{j_{n}}$, $j_{i}\in [0,1,\ldots, k^{i}_{2}-1]$, $\mathbf{k_{1}}+\mathbf{j}=[k_{1}^{1}+j_{1}, k_{1}^{2}+j_{2} \ldots k_{1}^{n}+j_{n}]$.
-Based on (\ref{pdf of y}) and $x=e^{-y}=G(y)$, using Jacobian transformation, the pdf of $x$ is given by
+Based on (\ref{pdf of y}) and $x=e^{-y}=G(y)$, using Jacobian transformation, the p.d.f.
+of $x$ is given by
 \begin{equation}

### 2015-12-25 Report Dec 2015/Report.tex
Report Dec 2015 second revision

@@
 Consider an uncoded complex Large-Scale MIMO (LS-MIMO) uplink spatial multiplexing (SM) system with $N_{t}$ users, each is equipped with one transmit antenna.
-The number of receive antennas at the Base Station (BS) is $N_{r}$, $N_{r}\geq N_{t}$.
+The number of receive antennas at the Base Station (BS) is $N_{r}$.
 Typically LS-MIMO systems have hundreds of antennas at the BS,
@@
 \end{equation}
-where $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{s}\in \mathbb{C}^{N_{t}}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g.
-BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
+where $\mathbf{y}\in\mathbb{C}^{N_{r}\times 1}$ is the received symbol vector, $\mathbf{s}\in \mathbb{C}^{N_{t}\times 1}$ is the transmitted symbol vector, with components that are mutually independent and taken from a finite signal constellation alphabet $\mathbb{O}$ (e.g., BPSK, 4-QAM, 16-QAM, 64-QAM), $|\mathbb{O}|=M$.
 The transmitted symbol vectors $\mathbf{s}\in \mathbb{O}^{N_{t}}$, satisfy $\mathbb{E}[\mathbf{s}\mathbf{s}^{H}]=\mathbf{I}_{N_t}E_{s}$, where $E_{s}$ denotes the symbol average energy, $\mathbb{E}[\cdot]$ denotes the expectation operation, $\mathbf{I}_{N_{t}}$ denotes identity matrix of size $N_{t}\times N_{t}$.
-Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix, $\mathbf{H}_{ij}$ denotes the component of $\mathbf{H}$ at $i$th row and $j$th column, representing the channel response from $i$th receive antenna to the $j$th transmit antenna.
+Furthermore $\mathbf{H}\in \mathbb{C}^{N_{r}\times N_{t}}$ denotes the Rayleigh fading channel propagation matrix.
+$\mathbf{H}_{ij}$ denotes the component of $\mathbf{H}$ at $i$th row and $j$th column, representing the channel response from $i$th receive antenna to the $j$th transmit antenna.
 Each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian (CSCG) random variable with unit variance, denoted by $\mathbf{H}_{ij}\sim \mathbb{C}N(0,1)$.
-Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the signal to noise ratio (SNR).
-
-The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel matrix $\mathbf{H}$.
-
-The optimal (in a sense of lowest average error probability) Maximum Likelihood Detector (MLD) for MIMO system is given by
+Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the symbol signal to noise ratio (SNR).
+
+The task of a MIMO detector is to estimate the transmit symbol vector $\mathbf{s}$, based on the knowledge of receive symbol vector $\mathbf{y}$ and channel state information (CSI) $\mathbf{H}$.
+Then a constellation demapper maps each component of $\hat{\mathbf{s}}$ to the corresponding bit sequences.
+The resulting $N_{t}$ substreams are finally multiplexed to obtain the reconstructed information sequence.
+
+The optimal (in a sense of lowest average frame error probability) Maximum Likelihood Detector (MLD) for MIMO system is given by
 \begin{equation}
@@
 where $||\cdot||$ denotes the 2-norm operation.
-From (\ref{MLD}), the solution of MLD is the $\hat{\mathbf{s}}$ that can generate the minimum Euclidean distance between vector $\mathbf{y}$ and $\mathbf{H}\mathbf{s}$.
+From (\ref{MLD}), the solution of MLD is the $\hat{\mathbf{s}}$ that can generate the minimum Euclidean distance between vector $\mathbf{y}$ and $\mathbf{H}\hat{\mathbf{s}}$.
 
@@
 \section{Minimum Achievable Diversity based Channel Partition}
-\subsection{Diversity Maximization Selection}
+\subsection{Diversity Maximization Selection}\label{DMS analysis}
 Based on the alternative form of MLD in (\ref{alternative MLD})-(\ref{third step alternative MLD}), General Parallel Interference Cancellation (GPIC) algorithm first generate a list of symbol vector candidates and then choose the candidate with the minimum Euclidean distance as the solution.
-To elaborate further, GPIC first generates a list of symbol vector candidate by exhaustive search for all the possible $\hat{\mathbf{s}}_{1}$ as shown in (\ref{first step alternative MLD}), then rather than performing exhaustive search in (\ref{second step alternative MLD}), GPIC exploits low complexity sub optimal linear detectors (i.e., zeros forcing (ZF) and minimum mean square error (MMSE)) and their successive interference cancellation (SIC) counterparts to get the estimation of $\mathbf{s}_{2}$.
+To elaborate further, GPIC detectors first generate a list of symbol vector candidate by exhaustive search for all the possible $\hat{\mathbf{s}}_{1}$ as shown in (\ref{first step alternative MLD}), then rather than performing exhaustive search in (\ref{second step alternative MLD}), GPIC detectors exploit the low complexity sub optimal linear detectors (i.e., zeros forcing (ZF) and minimum mean square error (MMSE)) and their successive interference cancellation (SIC) counterparts to get the estimation of $\mathbf{s}^{k}_{2}$, $k=[1,2,\ldots, K]$.
 For sake of simplicity, hereinafter we use LD/SIC.
@@
 Performance analysis of GPIC algorithm is provided in \cite{radji2009interference}, here we briefly conclude the main results in \cite{radji2009interference}.
-At the receiving side, the frame error is defined as there is at least one erroneous symbol in the estimation of transmitted symbol vector.
+At the receiving side, the frame error (detection error) is defined as there is at least one erroneous symbol in the estimation of transmitted symbol vector.
 Let $P_{e}$ denotes the average frame error probability.
@@
 \end{equation}
-in (\ref{average frame error probability of GPIC}), the diversity order of MLD is $N_{r}$, $P_{e2}$ is the average frame error probability of sub optimal LD/SICs, let $d_{2}$ denotes the diversity order of LD/SICs, based on (\ref{diversity}), we have
+in (\ref{average frame error probability of GPIC}), the diversity order of MLD is $N_{r}$.
+Let $d_{t}$ denote the overall diversity order of GPIC detectors and $d_{2}$ denote the diversity order of LD/SICs with the interferences from $\mathbf{s}_{1}$ perfectly cancelled, based on (\ref{diversity}), we have
 \begin{equation}
@@
 \begin{equation}
+\lim_{SNR\to\infty}P_{et}\propto SNR^{-d_{t}},
+\label{GPIC diversity}
+\end{equation}
+\begin{equation}
 \lim_{SNR\to\infty}P_{e2}\propto SNR^{-d_{2}},
@@
 \end{equation}
-Let $d_{t}$ denotes the overall diversity order of GPIC algorithm, now consider the following conditions
+ now consider the following conditions
 \begin{itemize}
@@
 Therefore when $d_{2}\geq N_{r}$, GPIC algorithm can achieve ML performance asymptotically, when $d_{2}<N_{r}$, the diversity order that GPIC can achieve at high SNR region is equal to that of LD/SICs.
-In \cite{radji2009interference}, the authors employ diversity maximization selection (DMS) scheme for channel partition, which is proposed in \cite{zhang2006diversity}.
+In \cite{radji2009interference}, the authors employ diversity maximization selection (DMS) scheme for channel partition, which is originally proposed in \cite{zhang2006diversity}.
 The optimal diversity order can be guaranteed with low complexity for conventional small MIMO systems.
 
-To elaborate further, for a given number of antennas chosen at the channel partition stage $N$, there is $N_{u}={N_{t}\choose N}$ possible combinations of $[\mathbf{H}_{1}, \mathbf{H}_{2}]$.
+To elaborate further, for a given number of antennas chosen at the channel partition stage $N$, there are $N_{u}={N_{t}\choose N}$ possible combinations of $[\mathbf{H}_{1}, \mathbf{H}_{2}]$.
 According to DMS principle, the maximum diversity order of LD/SIC is achieved by choosing the subset $\mathbf{H}_{2}$ that has the strongest weakest substream, in a sense of post processing SNR.
@@
 where $\lceil\alpha\rceil$ denotes the minimum integer no less than $\alpha$.
-\subsection{Minimum Achievable Diversity: How many antennas do we need for LS-MIMO?}
-In LS-MIMO V-BLAS systems, the maximum diversity order is $N_{r}$, which is extremely large under the condition that there is tens to hundreds of receive antennas.
+\subsection{Minimum Achievable Diversity: How many transmit antennas do we need to chose in LS-MIMO?}
+In LS-MIMO V-BLAS systems, where the substreams are transmitted independently, the maximum diversity order is $N_{r}$, which is extremely large under the condition that there are tens to hundreds of receive antennas.
 On the one hand, diversity order is achieved at high SNR region, however, in practical, such a high diversity order is not necessary, because the SNR region of interest is the range in which the bit error rate (BER) or symbol error rate (SER) can be $10^{-5}$ to $10^{-7}$.
-On the other hand, the computational complexity to guarantee ML performance by DMS channel partition is excessive in LS-MIMO, for example, when $N_{r}=N_{t}$, based on (\ref{Nmin DMS}), the $N_{min}=\lceil\sqrt{N_{r}}-1\rceil$, the number of the symbol vector candidates in the list generated by exhaustive search for $\mathbf{s}_{1}$ is $M^{N_{min}}$.
+On the other hand, the computational complexity to guarantee ML performance by DMS channel partition is excessive in LS-MIMO, for example, when $N_{r}=N_{t}$, based on (\ref{Nmin DMS}), the $N_{min}=\lceil\sqrt{N_{r}}-1\rceil$, the number of the symbol vector candidates in the list is $M^{N_{min}}$.
 
 Therefore, here we consider minimum achievable diversity (MAD) principle, which can reduce the detection complexity by sacrificing redundant asymptotic diversity gain in LS-MIMO.
-Let $d_{2MAD}$ denotes the diversity order of LD/SIC detectors, $\tilde{N}_{min}$ denotes the minimum number of antennas chosen by MAD principle.
+Let $d_{2MAD}$ denote the diversity order achieved by the suboptimal detectors after the MAD principle based channel partition, $\tilde{N}_{min}$ denote the minimum number of antennas chosen by MAD principle.
 Our goal is to guarantee the overall diversity is no less than a given minimum diversity while keep $\tilde{N}_{min}$ small.
-Let $1\leq g<N_{r}$ denote the given minimum achievable diversity order, based on (\ref{condition3sub2}), we have
+Let $1\leq g<N_{r}$ denote the given minimum achievable diversity order, based on (\ref{condition3sub2}) and the corresponding analysis in section \ref{DMS analysis}, we have
 \begin{IEEEeqnarray}[\relax]{l}
@@
 \end{IEEEeqnarray}    
-where $N\in [1,2,\ldots, N_{t}]$, our goal is to find minimum $N$, that satisfy $f(N)\geq 0$. The two zeros points of quadratic function $f(N)$ are 
+where $N\in [1,2,\ldots, N_{t}]$, our goal is to find minimum $N$, that satisfy $f(N)\geq 0$. The two zero points of quadratic function $f(N)$ are 
 \begin{IEEEeqnarray}[\relax]{l}
@@
 In this section, computer simulation results for the bit error rate (BER) performances of MAD principle based GPIC algorithm are presented.
-As comparisons, Sel-MMSE-OSIC algorithm in \cite{radji2009interference}, which is based on maximum diversity selection (MDS) principle is also considered.
-The software testbed is build by C, compiled by GCC compiler version 4.9.2 on 64 bit Debian (release 8.2) Linux systems, the experiments are performed on two desktops, one with Intel I5-4th generation CPU, quad cores, 3.2GHz clock rate and the other one with Intel I7-5th generation CPU, six cores, 3.5GHz clock rate.
+As a comparison, Sel-MMSE-OSIC algorithm in \cite{radji2009interference} is also considered, denoted by maximum diversity selection (MDS) scheme.
+The software testbed is built by C, compiled by GCC compiler version 4.9.2 on 64 bit Debian (release 8.2) Linux systems, the experiments are performed on two desktops, one with Intel I5-4th generation CPU, quad cores, 3.2GHz clock rate and the other one with Intel I7-5th generation CPU, six cores, 3.5GHz clock rate.
 
@@
 $N_{t}$ complex symbols are transmitted over randomly generated Rayleigh flat fading channel, each channel matrix component is CSCG random variable with unit variance.
-The receive symbol vector are corrupted by AWGN.
+The receive symbol vector is corrupted by AWGN.
 
 For sake of simplicity, we use MAD-n to present the results for minimum achievable diversity selection, where $n$ denotes the minimum achievable diversity.
-The minimum number of antennas selected by channel partition for a given minimum achievable diversity is given by (\ref{Nmin MAD}).
+The minimum number of antennas selected by channel partition for a given minimum achievable diversity $g$ is given by (\ref{Nmin MAD}).
 Maximum diversity selection (MDS) is used to present the Sel-MMSE-OSIC that can achieve ML diversity asymptotically.
-The minimum number of antennas selected by channel partition is given by (\ref{Nmin DMS}).
+The minimum number of antennas selected in MDS is given by (\ref{Nmin DMS}).
 
@@
 \hline
-Scheme&number of antennas selected&Asymptotic diversity\\
+Scheme&number of antennas selected ($N$)&Asymptotic diversity\\
 \hline 
@@
 
-As shown in Fig.\ref{f16MIMO4QAM}, compared with MDS which can achieve ML performance asymptotically, MAD-9 has a small performance loss, while MAD-4's performance is inferior, at BER $10^{-5}$, the MAD-9 is about $0.8$dB worse than MDS, MAD-4 is about $1.8$dB worse than MDS, let $\kappa(\cdot)$ denote the number of list candidate generated by GPIC algorithm\cite{radji2009interference}, from Table.\ref{t16MIMO4QAM},
+As shown in Fig.\ref{f16MIMO4QAM}, compared with MDS which can achieve ML performance asymptotically, MAD-9 has a small performance loss.
+While MAD-4's performance is inferior compared to MDS.
+At BER $10^{-5}$, the MAD-9 is about $0.8$dB worse than MDS, MAD-4 is about $1.8$dB worse than MDS, let $\kappa(\cdot)$ denote the number of symbol vector candidates in the list generated by GPIC algorithm\cite{radji2009interference}, from Table.\ref{t16MIMO4QAM},
 we have $\frac{\kappa(MAD-9)}{\kappa(DMS)}=1/4$ and $\frac{\kappa(MAD-4)}{\kappa(DMS)}=1/16$.
@@
 
-The results for $16\times 16$ system with $16$-QAM modulation is shown in Fig.\ref{f16MIMO16QAM}, the information of the schemes considered is as the same as that in Talbe.\ref{t16MIMO4QAM}, From Fig.\ref{f16MIMO16QAM}, we can see that similar to the case of $4$-QAM system, MAD-9 has a very small performance loss comparing to DMS, at BER $2\times 10^{-5}$, MAD-9 is about $1.1$dB worse than MDS, while MAD-4 has about $3$dB  performance loss comparing to DMS.
+The results for $16\times 16$ system with $16$-QAM modulation are shown in Fig.\ref{f16MIMO16QAM}, the information of the schemes considered is as the same as that in Talbe.\ref{t16MIMO4QAM}.
+From Fig.\ref{f16MIMO16QAM}, we can see that similar to the case of $4$-QAM system, MAD-9 has a very small performance loss comparing to DMS, at BER $2\times 10^{-5}$, MAD-9 is about $1.1$dB worse than MDS, while MAD-4 has about $3$dB  performance loss comparing to DMS.
 
@@
 \end{figure}
-Now we consider the performance of MAD in large systems, Fig.\ref{f32MIMO4QAM} shows the results for $32\times 32$ system with $4$-QAM.
-Table.\ref{t32MIMO4QAM} shows the information of the schemes, due to the time limitation, we just provide the results for MAD.
-As we can see in Fig.\ref{f32MIMO4QAM}, although the asymptotic diversity of MAD-16 is much higher than that of MAD-9, at the BER region of interest, their performance difference is negligible, at BER=$3\times 10^{-4}$, the performance of MAD-9 is about $0.3$dB worse comparing to MAD-16, at BER=$3\times 10^{-5}$, the performance loss of MAD-9 is about $0.5$dB comparing to MAD-16.
+Now we consider the performance of MAD in large systems, Fig.\ref{f32MIMO4QAM} shows the results for $32\times 32$ system with $4$-QAM, Table.\ref{t32MIMO4QAM} shows the information of the schemes.
+Due to the time limitation, we just provide the results for MAD.
+As we can see in Fig.\ref{f32MIMO4QAM}, although the asymptotic diversity of MAD-16 is much higher than that of MAD-9, at the BER region of interest, their performance difference is negligible.
+At BER=$3\times 10^{-4}$, the performance of MAD-9 is about $0.3$dB worse comparing to MAD-16, at BER=$3\times 10^{-5}$, the performance loss of MAD-9 is about $0.5$dB comparing to MAD-16.
 
@@
 \end{equation}
-First we consider the first summand on the right hand of (\ref{log expectation OM}) $\mathbb{E}[\ln(det(\mathbf{W}))]$.
+First we consider the first summand on the right hand of (\ref{log expectation OM}), $\mathbb{E}[\ln(det(\mathbf{W}))]$.
 Let $\mathbb{C}W_{m}(n, \Sigma)$ denote complex Wishart distribution, which is the joint distribution of sample covariance matrix from multivariate complex Gaussian random variable\cite{goodman1963statistical}.
@@
 
-Now we consider the second summand on the right hand of (\ref{log expectation OM}) $\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(||\mathbf{h}_{i}||^{2})]$.
+Now we consider the second summand on the right hand of (\ref{log expectation OM}), $\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(||\mathbf{h}_{i}||^{2})]$.
 $||\mathbf{h}_{i}||^{2}\sim Gamma(N_{r}, 1)$, the logarithmic expectation of a Gamma random variable $\gamma\sim Gamma(n, \theta)$ can be written as:
@@
 \end{equation}
-Based on \cite{nagar2011expectations}, given $\mathbf{W}\sim \mathbb{C}W_{N_{t}}(N_{r}, \mathbf{I}_{N_{t}})$ and $\mathbf{W}=\mathbf{R}^{H}\mathbf{R}$, we have $1\leq j\leq i\leq N_{t}$, $r_{ji}$ are mutually independent distributed.
-Furthermore $r_{ji}\sim \mathbb{C}N(0,1)$, $|r_{ii}|^{2}\sim Gamma(N_{r}-i+1,1)$ .
-Because $|r_{ji}|\sim Rayleigh(1/\sqrt{2})$, $\sum_{j<i}|r_{ji}|^{2}\sim Gamma(i-1, 1)$.
+Based on \cite{nagar2011expectations}, given $\mathbf{W}\sim \mathbb{C}W_{N_{t}}(N_{r}, \mathbf{I}_{N_{t}})$ and $\mathbf{W}=\mathbf{R}^{H}\mathbf{R}$, $r_{ji}$ are mutually independent distributed.
+Furthermore, for $1\leq i\leq N_{t}$, $|r_{ii}|^{2}\sim Gamma(N_{r}-i+1,1)$, for $1\leq j<i\leq N_{t}$, $r_{ji}\sim \mathbb{C}N(0,1)$.
+Because $|r_{ji}|\sim Rayleigh(1/\sqrt{2})$, $\sum_{j<i}|r_{ji}|^{2}\sim Gamma(i-1, 1)$ ($i\geq 2$).
 Define
@@
 \alpha_{i}=|r_{ii}|^{2}\sim Gamma(k_{1}^{i},1),\quad k_{1}^{i}=N_{r}-i+1,\quad i=1,2\ldots N_{t}\\
-\beta_{i}=\sum_{j<i}|r_{ji}|^{2}\sim Gamma(k_{2}^{i},1),\quad k_{2}^{i}=i-1, \quad i=1,2\ldots N_{t}
+\beta_{i}=\left\{\begin{array}{l}
+0\quad i=1\\
+\sum_{j<i}|r_{ji}|^{2}\sim Gamma(k_{2}^{i},1),\quad k_{2}^{i}=i-1, \quad i=2\ldots N_{t}
+\end{array}
+\right.
 \end{IEEEeqnarray}
-$\alpha_{i}$ and $\beta_{i}$ are independent Gamma random variables, from \cite{gupta2004handbook}, if $X\sim Gamma(k_{1},\theta)$ and $Y\sim Gamma(k_{2},\theta)$, then $\frac{X}{X+Y}\sim Beta(k_{1},k_{2})$, where $Beta(k_{1}, k_{2})$ denotes Beta distribution with shape parameters $k_{1}$ and $k_{2}$.
-Therefore $\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}\sim Beta(k^{i}_{1}, k^{i}_{2})$.
-Define $\eta_{i}=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}, i=1,2,\ldots, N_{t}$, $\eta_{i}$ are mutually independent Beta random variables, Therefore (\ref{alternative OM}) can be rewritten as
-  \begin{equation}
-  \phi_{om}=\prod_{i=1}^{N_{t}}\eta_{i},
+(\ref{alternative OM}) can be rewritten as
+\begin{equation}
+\phi_{om}=\prod_{i=1}^{N_{t}}\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}},
+\label{alternative OM2}
+\end{equation}
+$\alpha_{i}$ and $\beta_{i}$ ($i\geq 2$) are independent Gamma random variables, from \cite{gupta2004handbook}, if $X\sim Gamma(k_{1},\theta)$ and $Y\sim Gamma(k_{2},\theta)$, then $\frac{X}{X+Y}\sim Beta(k_{1},k_{2})$, where $Beta(k_{1}, k_{2})$ denotes Beta distribution with shape parameters $k_{1}, k_{2}>0$.
+Consider (\ref{alternative OM2}), if $i=1$, $\beta_{i}=0$, therefore $\frac{\alpha_{1}}{\alpha_{1}+\beta_{1}}=1$.
+Thus, we have $\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}\sim Beta(k^{i}_{1}, k^{i}_{2})$ when $i\geq 2$.
+Define $\eta_{i}=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}, i=1,2,\ldots, N_{t}$, $\eta_{1}=1$, and when $i\geq 2$, $\eta_{i}$ are mutually independent Beta random variables.
+Therefore (\ref{alternative OM}) can be rewritten as
+  \begin{equation}
+  \phi_{om}=\prod_{i=1}^{N_{t}}\eta_{i}=\prod_{i=2}^{N_{t}}\eta_{i},
   \label{product beta OM}
@@
 \begin{equation}
-f_{\phi_{om}}(\rho)=\sum_{\mathbf{j}}\{[\prod_{i=1}^{N_{t}}c(k_{1}^{i},k_{2}^{i}, j_{i})]U(\rho|\mathbf{k}_{1}+\mathbf{j})\},
+f_{\phi_{om}}(\rho)=\sum_{\mathbf{j}}\{[\prod_{i=2}^{N_{t}}c(k_{1}^{i},k_{2}^{i}, j_{i})]U(\rho|\mathbf{k}_{1}+\mathbf{j})\},
 \label{pdf of OM}
 \end{equation}
-where $\sum_{\mathbf{j}}=\sum_{j_{1}}\sum_{j_{2}}\ldots\sum_{j_{N_{t}}}$, $j_{i}\in [0,1,\ldots, k_{2}^{i}-1]$.
+where $\sum_{\mathbf{j}}=\sum_{j_{2}}\sum_{j_{3}}\ldots\sum_{j_{N_{t}}}$, $j_{i}\in [0,1,\ldots, k_{2}^{i}-1]$.
 $c(k_{1}^{i}, k_{2}^{i}, j_{i})=(-1)^{j_{i}}$ $k_{2}^{i}-1\choose j_{i}$ $[(k_{1}^{i}+j_{i})\mathbb{B}(k_{1}^{i},k_{2}^{i})]^{-1}$, $\mathbb{B}(\alpha, \beta)$ denotes Beta function with parameters $\alpha$ and $\beta$.
-$\mathbf{k}_{1}+\mathbf{j}=[k_{1}^{1}+j_{1}, k_{1}^{2}+j_{2},\ldots, k_{1}^{N_{t}}+j_{N_{t}}]$,
-\begin{equation}
-U(\rho|\mathbf{k}_{1}+\mathbf{j})=\rho^{-1}\prod_{i=1}^{N_{t}}(k_{1}^{i}+j_{i})\sum_{i=1}^{N_{t}}[\rho^{k_{1}^{i}+j_{i}}/\prod_{j\neq i}^{N_{t}}(k_{1}^{j}+j_{j}-k_{1}^{i}-j_{i})],
+$\mathbf{k}_{1}+\mathbf{j}=[k_{1}^{2}+j_{1}, k_{1}^{3}+j_{2},\ldots, k_{1}^{N_{t}}+j_{N_{t}}]$,
+\begin{equation}
+U(\rho|\mathbf{k}_{1}+\mathbf{j})=\rho^{-1}\prod_{i=2}^{N_{t}}(k_{1}^{i}+j_{i})\sum_{i=2}^{N_{t}}[\rho^{k_{1}^{i}+j_{i}}/\prod_{j\neq i}^{N_{t}}(k_{1}^{j}+j_{j}-k_{1}^{i}-j_{i})],
 \label{auxiliary pdf of OM}
@@
 \begin{equation}
-\mathbb{E}[\ln(\phi_{om})]=\sum_{i=1}^{N_{t}}\mathbb{E}[\ln(\eta_{i})]=\sum_{i=1}^{N_{t}}[\psi(k^{i}_{1})-\psi(k^{i}_{1}+k^{i}_{2})]=\sum_{i=1}^{N_{t}}[\psi(N_{r}-i+1)-\psi(N_{r})],
+\mathbb{E}[\ln(\phi_{om})]=\sum_{i=2}^{N_{t}}\mathbb{E}[\ln(\eta_{i})]=\sum_{i=2}^{N_{t}}[\psi(k^{i}_{1})-\psi(k^{i}_{1}+k^{i}_{2})]=\sum_{i=2}^{N_{t}}[\psi(N_{r}-i+1)-\psi(N_{r})]\\
+=\sum_{i=1}^{N_{t}}[\psi(N_{r}-i+1)-\psi(N_{r})],
 \label{final log expectation OM beta}
@@
 
-The variance between $\mathbb{E}[\ln(\phi_{om})]_{t}$ and $\mathbb{E}[\ln(\phi_{om})]_{t}$, denoted by $\upsilon$, is also calculated by \begin{equation}
+The variance between $\mathbb{E}[\ln(\phi_{om})]_{em}$ and $\mathbb{E}[\ln(\phi_{om})]_{t}$, denoted by $\upsilon$, is also calculated by \begin{equation}
 \upsilon=\frac{1}{m}\sum_{i=1}^{m}(\mathbb{E}[\ln(\phi_{om})]^{i}_{em}-\mathbb{E}[\ln(\phi_{om})]^{i}_{t})^{2},
@@
 \end{equation} 
-where $m$ is the number of the different sizes of channel matrix considered. By simulation $\upsilon=8.0116\times 10^{-4}$.
+where $m$ is the number of the different sizes of channel matrix considered.
+By simulation $\upsilon=8.0116\times 10^{-4}$, which demonstrates the correctness of the result in (\ref{final log expectation OM}).
 %\section{Simplified Channel Partition based on Orthogonality Measure}
@@
 \end{equation}
-(\ref{pdf log beta}) can be alternatively expressed as \cite{bhargava1981distribution}
+Based on Taylor series, (\ref{pdf log beta}) can be alternatively expressed as \cite{bhargava1981distribution}
 \begin{equation}

### 2016-01-01 Report Dec 2015/Report.tex
SENIA-1 simulation results
Neumann series expansion refined by 1-time Newton Iteration

@@
 \begin{abstract}
-The abstract goes here.
+This report consists of two major parts.
+In the first part, based on the performance analysis of list based algorithm, minimum achievable diversity (MAD) channel selection principle for Large-Scale MIMO (LS-MIMO) systems is presented.
+MAD principle can reduce the detection complexity by sacrificing redundant asymptotic diversity gain in LS-MIMO.
+Computer simulation results for the performance of MAD principle are presented for different MIMO system configurations.
+In the second part, theoretical analysis are provided for channel hardening phenomenon, including logarithmic expectation and probability distribution of orthogonality measure, which is defined to evaluate the orthogonality of the channel matrix.
 \end{abstract}
@@
 % Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-IEEEtran, journal, \LaTeX, paper, template.
-\end{IEEEkeywords}
+%\begin{IEEEkeywords}
+%IEEEtran, journal, \LaTeX, paper, template.
+%\end{IEEEkeywords}
 
@@
 Each component is independent identically distributed (i.i.d) circularly symmetric complex Gaussian (CSCG) random variable with unit variance, denoted by $\mathbf{H}_{ij}\sim \mathbb{C}N(0,1)$.
-Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the symbol signal to noise ratio (SNR).
+Finally, $\mathbf{n}\in \mathbb{C}^{N_{r}\times 1}$ is the additive white Gaussian noise (AWGN) vector with zero mean components and $\mathbb{E}[\mathbf{n}\mathbf{n}^{H}]=\mathbf{I}_{N_{r}}N_{0}$, where $N_{0}$ denotes the noise power spectrum density, and hence $\frac{E_{s}}{N_{0}}$ is the symbol signal to noise ratio (SNR).
 
@@
 
-Consider an alternative representation of MLD principle, let $\mathbf{H}_{1}\in \mathbb{C}^{N_{r}\times N}$ denotes a sub matrix composed of $N$ columns from $\mathbf{H}$, where $1\leq N\leq N_{t}$, let $\mathbf{s}_{1}\in \mathbb{C}^{N}$ denote the sub symbol vector whose components are transmitted from the users corresponding to $\mathbf{H}_{1}$.
-Similarly, let $\mathbf{H}_{2}\in \mathbb{C}^{N_{r}\times (N_{t}-N)}$ denotes the sub matrix composed of the remaining columns from $\mathbf{H}$ and $\mathbf{s}_{2}\in \mathbb{C}^{(N_{t}-N)}$ is the sub symbol vector whose components are transmitted by the users corresponding to $\mathbf{H}_{2}$.
+Consider an alternative representation of MLD principle, let $\mathbf{H}_{1}\in \mathbb{C}^{N_{r}\times N}$ denotes a sub matrix composed of $N$ columns from $\mathbf{H}$, where $1\leq N\leq N_{t}$, let $\mathbf{s}_{1}\in \mathbb{C}^{N\times 1}$ denote the sub symbol vector whose components are transmitted from the users corresponding to $\mathbf{H}_{1}$.
+Similarly, let $\mathbf{H}_{2}\in \mathbb{C}^{N_{r}\times (N_{t}-N)}$ denotes the sub matrix composed of the remaining columns from $\mathbf{H}$ and $\mathbf{s}_{2}\in \mathbb{C}^{(N_{t}-N)\times 1}$ is the sub symbol vector whose components are transmitted by the users corresponding to $\mathbf{H}_{2}$.
 Thus (\ref{discrete time MIMO system}) can be rewritten as
@@
 \end{equation}  
-Let $\hat{\mathbf{s}}_{1}, \hat{\mathbf{s}}_{2}$ denote the estimations of $\mathbf{s}_{1}, \mathbf{s}_{2}$, we have $\hat{\mathbf{s}}_{1}\in [\hat{\mathbf{s}}^{1}_{1}, \hat{\mathbf{s}}^{2}_{1}, \cdots \hat{\mathbf{s}}^{K}_{1}],, K=M^{N}$ and $\hat{\mathbf{s}}_{2}\in [\hat{\mathbf{s}}^{1}_{2}, \hat{\mathbf{s}}^{2}_{2}, \cdots \hat{\mathbf{s}}^{Q}_{2}], Q=M^{N_{t}-N}$, MLD in (\ref{MLD}) can be rewritten as
+Let $\hat{\mathbf{s}}_{1}, \hat{\mathbf{s}}_{2}$ denote the estimations of $\mathbf{s}_{1}, \mathbf{s}_{2}$, we have $\hat{\mathbf{s}}_{1}\in [\hat{\mathbf{s}}^{1}_{1}, \hat{\mathbf{s}}^{2}_{1}, \cdots \hat{\mathbf{s}}^{K}_{1}], K=M^{N}$ and $\hat{\mathbf{s}}_{2}\in [\hat{\mathbf{s}}^{1}_{2}, \hat{\mathbf{s}}^{2}_{2}, \cdots \hat{\mathbf{s}}^{Q}_{2}], Q=M^{N_{t}-N}$, then MLD in (\ref{MLD}) can be rewritten as
 \begin{equation}
@@
 Based on the alternative form of MLD in (\ref{alternative MLD})-(\ref{third step alternative MLD}), General Parallel Interference Cancellation (GPIC) algorithm first generate a list of symbol vector candidates and then choose the candidate with the minimum Euclidean distance as the solution.
-To elaborate further, GPIC detectors first generate a list of symbol vector candidate by exhaustive search for all the possible $\hat{\mathbf{s}}_{1}$ as shown in (\ref{first step alternative MLD}), then rather than performing exhaustive search in (\ref{second step alternative MLD}), GPIC detectors exploit the low complexity sub optimal linear detectors (i.e., zeros forcing (ZF) and minimum mean square error (MMSE)) and their successive interference cancellation (SIC) counterparts to get the estimation of $\mathbf{s}^{k}_{2}$, $k=[1,2,\ldots, K]$.
+To elaborate further, GPIC detectors first obtain $\mathbf{H}_{2}$ by a certain channel partition rule, then generate a list of symbol vector candidate by exhaustive search for all the possible $\hat{\mathbf{s}}_{1}$ as shown in (\ref{first step alternative MLD}), then rather than performing exhaustive search in (\ref{second step alternative MLD}), GPIC detectors exploit the low complexity sub optimal linear detectors (i.e., zeros forcing (ZF) and minimum mean square error (MMSE)) and their successive interference cancellation (SIC) counterparts to get the estimation of $\mathbf{s}^{k}_{2}$, $k=[1,2,\ldots, K]$.
 For sake of simplicity, hereinafter we use LD/SIC.
-Then the best candidate in the list with the minimum Euclidean distance is chosen as the solution.
+Finally the best candidate in the list with the minimum Euclidean distance is chosen as the solution.
 
 Performance analysis of GPIC algorithm is provided in \cite{radji2009interference}, here we briefly conclude the main results in \cite{radji2009interference}.
-At the receiving side, the frame error (detection error) is defined as there is at least one erroneous symbol in the estimation of transmitted symbol vector.
+At the receive side, the frame error (detection error) is defined as there is at least one erroneous symbol in the estimation of transmitted symbol vector.
 Let $P_{e}$ denotes the average frame error probability.
@@
 \end{equation}
-Let $P_{e}^{ML}$ denotes the average frame error probability of MLD, The average frame error probability of GPIC algorithm $P_{et}=\mathbb{E}_{\mathbf{H}, \mathbf{s}}[Pr(\hat{\mathbf{s}}\neq \mathbf{s}|\mathbf{H}, \mathbf{s})]$ and $P_{e2}=\mathbb{E}_{\mathbf{H}_{2}, \mathbf{s}_{2}}(Pr(\hat{\mathbf{s}}^{k_{1}}_{2}\neq \mathbf{s}_{2}|\mathbf{H}_{2}, \mathbf{s}_{2}))$, where $P_{r}(A)$ denotes the probability that a event A occurs, $\hat{\mathbf{s}}_{1}^{k_{1}}=\mathbf{s}_{1}$, therefore $P_{e2}$ is the average frame error probability of the LD/SICs for the sub system in which the interference from the users that transmitted $\mathbf{s}_{1}$ are perfectly cancelled from the observation $\mathbf{y}$.
+Let $P_{e}^{ML}$ denotes the average frame error probability of MLD.
+Define the average frame error probability of GPIC algorithm $P_{et}=\mathbb{E}_{\mathbf{H}, \mathbf{s}}[Pr(\hat{\mathbf{s}}\neq \mathbf{s}|\mathbf{H}, \mathbf{s})]$ and $P_{e2}=\mathbb{E}_{\mathbf{H}_{2}, \mathbf{s}_{2}}(Pr(\hat{\mathbf{s}}^{k_{1}}_{2}\neq \mathbf{s}_{2}|\mathbf{H}_{2}, \mathbf{s}_{2}))$, where $P_{r}(A)$ denotes the probability that a event A occurs.
+$\hat{\mathbf{s}}_{1}^{k_{1}}=\mathbf{s}_{1}$, therefore $P_{e2}$ is the average frame error probability of the LD/SICs for the sub system $[\mathbf{H}_{2}, \mathbf{s}_{2}]$ in which the interference from the users that transmitted $\mathbf{s}_{1}$ are perfectly cancelled from the observation $\mathbf{y}$.
 given by
@@
 \end{IEEEeqnarray}   
-Where $\mathbf{A}_{kk}$ denotes the $k$th diagonal component of matrix $\mathbf{A}$. The diversity order of LD/SIC detector after DMS channel partition process is given by 
-$d_{2DMS}=(N+1)(N_{r}-N_{t}+N+1)$.
+Where $\mathbf{A}_{kk}$ denotes the $k$th diagonal component of matrix $\mathbf{A}$. The diversity order of LD/SIC detectors after DMS channel partition process is given by 
+$d_{2DMS}=(N+1)(N_{r}-N_{t}+N+1)$\cite{jalden2007maximal}.
 In \cite{radji2009interference}, the authors derive the minimum number of antennas $N_{min}$ at channel partition stage that can guarantee $d_{2DMS}\geq N_{r}$, which is given by
@@
 Therefore, here we consider minimum achievable diversity (MAD) principle, which can reduce the detection complexity by sacrificing redundant asymptotic diversity gain in LS-MIMO.
-Let $d_{2MAD}$ denote the diversity order achieved by the suboptimal detectors after the MAD principle based channel partition, $\tilde{N}_{min}$ denote the minimum number of antennas chosen by MAD principle.
+Let $d_{2MAD}$ denote the diversity order achieved by the suboptimal detectors after the MAD based channel partition, $\tilde{N}_{min}$ denote the minimum number of antennas chosen by MAD principle.
 Our goal is to guarantee the overall diversity is no less than a given minimum diversity while keep $\tilde{N}_{min}$ small.
@@
 \subsection{Computer Simulations}
-In this section, computer simulation results for the bit error rate (BER) performances of MAD principle based GPIC algorithm are presented.
-As a comparison, Sel-MMSE-OSIC algorithm in \cite{radji2009interference} is also considered, denoted by maximum diversity selection (MDS) scheme.
-The software testbed is built by C, compiled by GCC compiler version 4.9.2 on 64 bit Debian (release 8.2) Linux systems, the experiments are performed on two desktops, one with Intel I5-4th generation CPU, quad cores, 3.2GHz clock rate and the other one with Intel I7-5th generation CPU, six cores, 3.5GHz clock rate.
-
-We consider uncoded complex spatial multiplexing LS-MIMO systems, For each receive SNR point, the BER are calculated with minimum $10^{5}$ independent channel realizations achieved and minimum 300 symbol errors accumulated.
+In this section, computer simulation results for the bit error rate (BER) performances of MAD based GPIC algorithm are presented.
+As comparisons, Sel-MMSE-OSIC algorithm in \cite{radji2009interference} is also considered, denoted by maximum diversity selection (MDS) scheme.
+The software testbed is built by C, compiled by GCC compiler version 4.9.2 on 64 bit Debian (release 8.2) Linux systems.
+The experiments are performed on two desktops, one has Intel I5-4th generation CPU, quad cores, 3.2GHz clock rate and the other one has Intel I7-5th generation CPU, six cores, 3.5GHz clock rate.
+
+We consider uncoded complex spatial multiplexing LS-MIMO systems, For each receive SNR level, the BER are calculated with minimum $10^{5}$ independent channel realizations achieved and minimum 300 symbol errors accumulated.
 The modulation schemes considered are rectangular M-QAM(4-QAM and 16-QAM) with Gray code labeling.
@@
 
-For sake of simplicity, we use MAD-n to present the results for minimum achievable diversity selection, where $n$ denotes the minimum achievable diversity.
+For sake of simplicity, we use MAD-$g$ to present the results for minimum achievable diversity selection, where $g$ denotes the minimum achievable diversity.
 The minimum number of antennas selected by channel partition for a given minimum achievable diversity $g$ is given by (\ref{Nmin MAD}).
@@
 The minimum number of antennas selected in MDS is given by (\ref{Nmin DMS}).
-
-First, we consider $16\times 16$ system with $4$-QAM modulation, Table.\ref{t16MIMO4QAM} shows the information of the schemes considered, the corresponding results are presented in Fig.\ref{f16MIMO4QAM},
 \begin{table}[htb]
@@
 
-As shown in Fig.\ref{f16MIMO4QAM}, compared with MDS which can achieve ML performance asymptotically, MAD-9 has a small performance loss.
-While MAD-4's performance is inferior compared to MDS.
-At BER $10^{-5}$, the MAD-9 is about $0.8$dB worse than MDS, MAD-4 is about $1.8$dB worse than MDS, let $\kappa(\cdot)$ denote the number of symbol vector candidates in the list generated by GPIC algorithm\cite{radji2009interference}, from Table.\ref{t16MIMO4QAM},
-we have $\frac{\kappa(MAD-9)}{\kappa(DMS)}=1/4$ and $\frac{\kappa(MAD-4)}{\kappa(DMS)}=1/16$.
-
+First, we consider $16\times 16$ system with $4$-QAM modulation, Table.\ref{t16MIMO4QAM} shows the information of the schemes considered, the corresponding results are presented in Fig.\ref{f16MIMO4QAM}.
 \begin{figure}[htb]
@@
 \def\svgwidth{\columnwidth}
+%\def\svgscale{1}
 \input{16MIMO4QAM.pdf_tex}
@@
 
-The results for $16\times 16$ system with $16$-QAM modulation are shown in Fig.\ref{f16MIMO16QAM}, the information of the schemes considered is as the same as that in Talbe.\ref{t16MIMO4QAM}.
-From Fig.\ref{f16MIMO16QAM}, we can see that similar to the case of $4$-QAM system, MAD-9 has a very small performance loss comparing to DMS, at BER $2\times 10^{-5}$, MAD-9 is about $1.1$dB worse than MDS, while MAD-4 has about $3$dB  performance loss comparing to DMS.
-
-Furthermore, compared with $4$-QAM systems, the reduction of the number of list candidates provided by MAD scheme is more significant in $16$-QAM systems, $\frac{\kappa(MAD-9)}{\kappa(DMS)}=1/16$ and $\frac{\kappa(MAD-4)}{\kappa(DMS)}=1/256$.
+As shown in Fig.\ref{f16MIMO4QAM}, compared with MDS which can achieve ML performance asymptotically, MAD-9 has a small performance loss, while MAD-4's performance is inferior compared to MDS.
+At BER=$10^{-5}$, the MAD-9 is about $0.8$dB worse than MDS, MAD-4 is about $1.8$dB worse than MDS.
+Let $\kappa(\cdot)$ denote the number of symbol vector candidates in the list generated by GPIC algorithm\cite{radji2009interference}, from Table.\ref{t16MIMO4QAM}, we have $\frac{\kappa(MAD-9)}{\kappa(MDS)}=1/4$ and $\frac{\kappa(MAD-4)}{\kappa(MDS)}=1/16$.\newpage
 \begin{figure}[htb]
@@
 
+The results for $16\times 16$ system with $16$-QAM modulation are shown in Fig.\ref{f16MIMO16QAM}, the information of the schemes considered is as the same as that in Talbe.\ref{t16MIMO4QAM}.
+From Fig.\ref{f16MIMO16QAM}, we can see that similar to the case of $4$-QAM system, MAD-9 has a very small performance loss comparing to MDS, at BER=$2\times 10^{-5}$, MAD-9 is about $1.1$dB worse than MDS, while MAD-4 has about $3$dB  performance loss comparing to MDS.
+
+Furthermore, compared with $4$-QAM systems, the reduction of the number of list candidates provided by MAD scheme is more significant in $16$-QAM systems, $\frac{\kappa(MAD-9)}{\kappa(MDS)}=1/16$ and $\frac{\kappa(MAD-4)}{\kappa(MDS)}=1/256$.\newpage
+
 \begin{table}[htb]
@@
 \def\svgwidth{\columnwidth}
+%\def\svgscale{1}
 \input{32MIMO4QAM.pdf_tex}
@@
 \end{figure}
-Now we consider the performance of MAD in large systems, Fig.\ref{f32MIMO4QAM} shows the results for $32\times 32$ system with $4$-QAM, Table.\ref{t32MIMO4QAM} shows the information of the schemes.
+
+Now we consider larger systems, Fig.\ref{f32MIMO4QAM} shows the results for $32\times 32$ system with $4$-QAM, Table.\ref{t32MIMO4QAM} shows the information of the schemes.
 Due to the time limitation, we just provide the results for MAD.
@@
 At BER=$3\times 10^{-4}$, the performance of MAD-9 is about $0.3$dB worse comparing to MAD-16, at BER=$3\times 10^{-5}$, the performance loss of MAD-9 is about $0.5$dB comparing to MAD-16.
-
+\begin{table}[htb]
+\renewcommand{\arraystretch}{1.3}
+\caption{$16\times 20$ system $4$-QAM}
+\label{t1620MIMO4QAM}
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+Scheme&number of antennas selected ($N$)&Asymptotic diversity\\
+\hline 
+MDS&6&16\\
+\hline
+MAD-5&4&5\\
+\hline
+MAD-12&5&12\\
+\hline
+\end{tabular}
+\end{table}
+
+Define system loading factor $\alpha=\frac{N_{t}}{N_{r}}$.
+Compared with the other list based detection algorithms such as fixed complexity sphere decoder (FCSD), an advantage that Sel-MMSE-OSIC can provide is it can handle the over loaded systems (i.e., $\alpha>1$).
+Fig.\ref{f1620MIMO4QAM} presents the performances of MAD in $16\times 20$ system with $4$-QAM, Table.\ref{t1620MIMO4QAM} shows the information of the schemes considered.
+
+\begin{figure}
+\centering
+\def\svgwidth{\columnwidth}
+\input{1620MIMO4QAM.pdf_tex}
+\caption{$16\times 20$ system $4$-QAM}
+\label{f1620MIMO4QAM}
+\end{figure}
+As shown in Fig.\ref{f1620MIMO4QAM}, compared with MDS, MAD-$12$ has a small performance degradation no greater than 0.5dB at all SNR levels, at BER=$5\times 10^{-5}$, MAD-$12$ is about 0.2dB worse than MDS.
+MAD-$5$ performs inferior comparing to MDS and MAD-$12$, at BER=$4\times 10^{-4}$, MAD-$5$ is about 1dB worse than MDS, at BER=$4\times 10^{-5}$, MAD-$5$ is about 1.5dB worse than MAD-$12$.
+\newpage
 \section{Theoretical Analysis of Channel Hardening Phenomenon}
@@
 Define $\eta_{i}=\frac{\alpha_{i}}{\alpha_{i}+\beta_{i}}, i=1,2,\ldots, N_{t}$, $\eta_{1}=1$, and when $i\geq 2$, $\eta_{i}$ are mutually independent Beta random variables.
-Therefore (\ref{alternative OM}) can be rewritten as
+Therefore (\ref{alternative OM2}) can be rewritten as
   \begin{equation}
@@
   \end{equation}
-Thus $\phi_{om}$ is the product of $N_{t}$ independent Beta random variables, the p.d.f of $\phi_{om}$ is given by 
+Thus $\phi_{om}$ is the product of $N_{t}-1$ independent Beta random variables, the p.d.f of $\phi_{om}$ is given by 
 \begin{equation}
@@
 \subsection{Computer Simulations}
+\begin{figure}[htb]
+\centering
+\def\svgwidth{\columnwidth}
+%\def\svgscale{0.8}
+\input{logOMt.pdf_tex}
+\caption{Theoretical logarithmic expectation of $\phi_{om}$}
+\label{flogOMt}
+\end{figure}
+\begin{figure}[htb]
+\centering
+\def\svgwidth{\columnwidth}
+%\def\svgscale{0.8}
+\input{logOMem.pdf_tex}
+\caption{Empirical estimation of the logarithmic expectation of $\phi_{om}$}
+\label{flogOMem}
+\end{figure}
 Computer simulations are made to demonstrate the correctness of the results in this section.
@@
 The result is shown in Fig.\ref{flogOMem}.
-\begin{figure}[htb]
-\centering
-\def\svgwidth{\columnwidth}
-\input{logOMt.pdf_tex}
-\caption{Theoretical logarithmic expectation of $\phi_{om}$}
-\label{flogOMt}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\def\svgwidth{\columnwidth}
-\input{logOMem.pdf_tex}
-\caption{Empirical estimation of the logarithmic expectation of $\phi_{om}$}
-\label{flogOMem}
-\end{figure}
 
@@
 By simulation $\upsilon=8.0116\times 10^{-4}$, which demonstrates the correctness of the result in (\ref{final log expectation OM}).
+
 %\section{Simplified Channel Partition based on Orthogonality Measure}
@@
 %\subsection{Systems with Different Loading Factors}
-
-\section{Conclusion}
-The conclusion goes here.
-\newpage
 
@@
 %
-
 \appendices

### 2016-01-01 Matrix inversion approximation/Matlab Test/Figures/Figure.m

@@ -1,0 +1,76 @@
+%% This the m file for the figure plotting 
+% The test of the performances of linear detectors (LD) (MMSE) that exploiting Neumann series expansion 1-Newton Iteration
+% Approximation (SENIA-1)
+% MMSE with exact matrix inversion (EMI) is also considered as comparison
+% The performance metric considered here are bit error rate (BER) versus average receive signal to noise ratio (SNR)
+% the data come from the corresponding file in the same folder
+
+%% Data example
+% BER_E_128_8_16: BER of MMSE exploiting exact matrix inversion for 128X8
+% system with 16QAM modulation
+% BER_A_128_8_16: BER of MMSE exploiting SENIA-1 matrix inversion
+
+%% 16QAM
+%The expectation of OM is 0.79999356
+BER_E_128_8_16=[3.365625e-02, 1.137500e-02,2.956481e-03,2.557492e-04,8.469799e-06]; %snr 0-8
+BER_A_128_8_16=[3.456250e-02,1.153125e-02,2.986045e-03, 2.915541e-04,1.058725e-05 ];  %snr 0-8
+
+%The expectation of OM is 1.442349e-02
+BER_E_128_32_16=[1.738750e-01,1.280547e-01,8.495313e-02,4.814844e-02,1.981250e-02,6.234375e-03,...
+    8.750000e-04,4.112059e-05,7.034182e-07]; %snr 0-16
+BER_A_128_32_16=[1.855859e-01, 1.506328e-01,1.253672e-01,1.051875e-01,8.781250e-02,7.839844e-02,6.975781e-02,...
+    6.941813e-02,6.686763e-02];  %snr 0-16
+
+%The expectation of OM is 0.63402790
+BER_E_64_8_16=[9.053125e-02,5.409375e-02,2.393750e-02,7.093750e-03,1.249011e-03,1.131467e-04,2.449150e-06]; %snr 0-12
+BER_A_64_8_16=[9.365625e-02,5.718750e-02,2.718750e-02,8.906250e-03,2.473288e-03,5.510247e-04,1.884621e-04];  %snr 0-12
+
+%The expectation of OM is 1.800414e-13
[…]

### 2016-01-01 Matrix inversion approximation/Matlab Test/MMSE.m

@@ -1,0 +1,10 @@
+function [ symOut ] = MMSE( y, H, SNRd, M, pav )
+%Minimum Mean Square Error Detector
+% Rectangular_QAM_slicer performs slicing based on the symbol constellation
+% alphabet
+Nt=length(H(1,:));
+I=eye(Nt);
+G=(I/(H'*H+(SNRd)^(-1)*I))*H';
+symOut_tmp=G*y;
+symOut=Rectangular_QAM_slicer(symOut_tmp, M, pav);
+end

### 2016-01-01 Matrix inversion approximation/Matlab Test/MMSE_A.m

@@ -1,0 +1,13 @@
+function [ symOut ] = MMSE_A( y, H, SNRd, M, pav )
+%Minimum Mean Square Error Detector
+% Rectangular_QAM_slicer performs slicing based on the symbol constellation
+% alphabet
+Nt=length(H(1,:));
+I=eye(Nt);
+% G=(I/(H'*H+(SNRd)^(-1)*I))*H';
+G_inter=H'*H+SNRd^(-1)*I;
+[G_interI, nonOfuse]=SENIA(G_inter);
+G=G_interI*H';
+symOut_tmp=G*y;
+symOut=Rectangular_QAM_slicer(symOut_tmp, M, pav);
+end

### 2016-01-01 Matrix inversion approximation/Matlab Test/SENIA.m

@@ -1,0 +1,38 @@
+function [ W_inverse, W_inter1 ] = SENIA( W )
+% This function implements the series expansion (2) Newton Iteration matrix
+% inversion appproximation 
+%INPUT:
+% W: quasi-diagonal matrix
+%OUTPUT:
+% W_inverse: matrix inversion approximation
+n=length(W(1,:));   %length of W
+W_diag=zeros(n,1);   %diagonal elements of W   D
+W_offdiag=zeros(n); %off diagonal matrix of W  E  
+W_diagI=zeros(n,1);  %the elements of the inverse of the diagonal matrix D^(-1)
+W_inter1=zeros(n);  %the intermediate matrix D^(-1)E
+W_inter2=zeros(n);   %the intermediate matrix W_inter1*D^(-1)
+W_inter3=zeros(n);   %the intermediate matrix W_inter2*E
+W_inter4=zeros(n);   %the inermediate matrix 
+W_diag=diag(W);    %get the diagonal elements of W
+W_diagI=1./(W_diag); %get the vector of the elements which is the inverse of the diagonal matrix
+W_offdiag=W;
+for count=1:n
+    W_offdiag(count,count)=0;
+end
+for count=1:n
+    W_inter1(count,:)=W_offdiag(count,:)*W_diagI(count);
+end
+for count=1:n
+    W_inter2(:,count)=W_inter1(:,count)*W_diagI(count);
+end
+W_inter3=W_inter2*W_offdiag;  
+for count=1:n
+    W_inter3(count,count)=W_inter3(count,count)+1;
+end
+W_inter4=-W_inter2;
+for count=1:n
+W_inter4(count,count)=W_inter4(count,count)+W_diagI(count);
+end
+W_inverse=W_inter3*W_inter4;
+end
+

### 2016-01-01 Matrix inversion approximation/Matlab Test/communicationLink.m

@@ -1,0 +1,151 @@
+%% Main System File for Bit Error Rate Monte-Carlo Simulation 
+%=============
+%Author: Tianpei Chen
+% Introduction:
+% this routine performs the Monte-Carlo Simulation of the bit error rate of
+% proposed detectors in Large Scale-MIMO (LS-MIMO) systems. A set of signal
+% to noise ratio (SNR) points are considered, (Notice: the SNR in Monte-Carlo simulation is defined
+% as the average receive SNR generally, however here we use the difinition in Dejelili's thesis that is, SNR of each symbol). 
+% For each SNR point, the
+% simulations works in the step of channel realizations, symbol error rate
+% and bit error rate of the detectors are calculated when both a certain number
+% of symbol errors are accumulated and adequate channel realization times
+% is reached.
+% this routine output the BER or SER or related simulation results to txt
+% files.
+%Date: Dec 02 20015
+%=============
+%% Function Description
+% grayEncoder: generate gray code list
+% symbolConstellation: generate symbol constellation alphabet 
+% sel_MMSE_OSIC: selection MMSE OSIC detector
+% grayDecoder: decoding symbol estimations to corresponding gray code
+% checkBitError: comparing the output bit sequence and the original
+% transmit bit sequence, then calculate bit errors
+
+close all
+clear all
+tic
+
+%% System Configuration
+M =16;         %size of the signal constellation alphabet  (rectangular M-QAM)
+Nt=32;         %number of transmit antennas
+Nr=32;         %number of receive antennas
+SNR=[30:2:50];       %average receive signal to noie ratio (SNR) in (dB) 
+SNRd=10.^(SNR.*0.1);   %SNR in dicimal 
+pav=1/Nt;  %average power of the transmitted symbols
+% noiseV=pav./SNRd;   %noise variance of  Additive White Gaussian Noise (AWGN)
+noiseV=1./SNRd;  
+Eom=1;  %the expectation of orthogonality measure
+for count=2:Nt 
+    Eom=Eom*(Nr-count+1)/Nr;
+end
[…]

### 2016-01-01 Matrix inversion approximation/Matlab Test/grayEncoder.m

@@ -1,0 +1,11 @@
+function [ graycode ] = grayEncoder( M )
+%gray encoder 
+%M is the constellation size
+if(M==4)
+    graycode=[0,1,2,3];
+elseif(M==16)
+    graycode=[0,1,3,2,4,5,7,6,12,13,15,14,8,9,11,10];
+end
+
+
+end

### 2016-01-01 Matrix inversion approximation/Matlab Test/symbolConstellation.m

@@ -1,0 +1,22 @@
+function [ symConstell ] = symbolConstellation( M, pav )
+%Generage symbol constellation
+%   Detailed explanation goes here
+Q=sqrt(M);
+symConstell=zeros(M,1);
+symConstellReal=zeros(Q,1);
+symReal=zeros(Q,1);
+symImag=zeros(Q,1);
+if(M==2)
+  d=sqrt(pav);  
+else
+    d=sqrt(3*pav/(2*(M-1)));
+end
+
+for count=1:Q
+    symConstellReal(count)=-(Q-1)*d+(count-1)*2*d;
+end
+for count=1:M
+    symReal(count)=symConstellReal(fix((count-1)/Q)+1);
+    symImag(count)=symConstellReal(Q-mod(count-1,Q));
+    symConstell(count)=complex(symReal(count),symImag(count));
+end

### 2016-01-01 Report Dec 2015/Figures/Figure.m

@@ -25,7 +25,9 @@ BER_MAD_32_4_9=[0.229477, 0.19105, 0.148106,0.10018, 0.0492078,0.0160859,0.00328
 BER_MAD_32_4_16=[0.229358, 0.190434, 0.146927, 0.0955453, 0.0448656, 0.0129797, 0.00223281, 0.000287571, 1.92706e-05 ]; %snr 0-16
 
 
-
+BER_MDS_16_20_4=[0.0850475, 0.0274025, 0.0042425, 0.000479125 ];%snr 8-14
+BER_MAD_16_20_4_5=[0.0926625,0.03786,0.00904,0.0014525, 0.000158027 , 1.45423e-05 ]; %snr 8-18
+BER_MAD_16_20_4_12=[0.0878775,0.03081, 0.006365,0.000675, 3.79123e-05 ]; %snr 8-16
 
 
 %% Figure plotting
@@ -63,4 +65,17 @@ hold on;
 % title('32X32 system 4QAM');
 % hold on;
 legend( 'MAD-4', 'MAD-9', 'MAD-16');
+hold off;
+
+
+figure (4)
+semilogy([8:2:14], BER_MDS_16_20_4, '-*', 'MarkerSize', 8), xlabel('SNR (dB)'), ylabel('BER');
+hold on;
+semilogy([8:2:18], BER_MAD_16_20_4_5, '-^', 'MarkerSize', 8), xlabel('SNR (dB)'), ylabel('BER');
+hold on;
+semilogy([8:2:16], BER_MAD_16_20_4_12, '-+', 'MarkerSize',8), xlabel('SNR (dB)'), ylabel('BER');
+hold on;
+% title('16X16 system 4QAM');
+% hold on;
+legend('MDS', 'MAD-5', 'MAD-12');
 hold off;
